### 2020-09-21 cusp_j/paper/paper.tex
added stuffs

\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amsmath,amssymb,amsfonts,physics,mhchem,xspace,subfigure}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\definecolor{darkgreen}{HTML}{009900}
\usepackage[normalem]{ulem}
\newcommand{\sphi}[1]{\hat{{\bf S}}_{#1}}
\newcommand{\overlap}[2]{\langle #1 | #2 \rangle}
\newcommand{\matelem}[3]{\langle #1 | #2 | #3 \rangle}
\newcommand{\deriv}[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand{\bd}[1]{{\bf {#1}}}
\newcommand{\br}[0]{{\bf {r}}}
\newcommand{\bs}[0]{{\bf {s}}}
\newcommand{\dr}[1]{\text{d}{\bf {#1}}}
\newcommand{\psiex}[0]{\Psi^{\text{ex}}_0}
\newcommand{\phiex}[0]{\Phi^{\text{ex}}_0}
\newcommand{\phimu}[0]{\Phi^{\text{ex},\mu}_0}
\newcommand{\energyex}[0]{E^{\text{ex}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\identity}{\mathds{1}}

\begin{document}

\title{A new form of transcorrelated Hamiltonian inspired by range-separated DFT}

\author{Emmanuel Giner}
\email{emmanuel.giner@lct.jussieu.fr}

\begin{abstract}
blabla

\end{abstract}

\maketitle
\section{Introduction}
Two formulation : the "pseudo orbital" (\textit{i.e.} usual common set of orbitals for bra and ket) and "biorthonormal orbitals" (\textit{i.e.} a different set of orbitals for bra and ket having the biorthonormal property). 
In the limit of the FCI wave function, these two formulations coincide, therefore we keep the "pseudo orbital" theory for the sake of simplicity.

\section{Brief overview of mathematical properties of similarity transformed Hamiltonian}
\subsection{Definition of the similarity transformation}
Assume an \textit{Hermitian operator} $H$ whose spectral representation reads 
\begin{equation}
 \label{eq:h_spectr}
 H  = \sum_n E_n \ket{\Psi_n}\bra{\Psi_n}
\end{equation}
with $\ket{\Psi_n}$ being its orthonormal eigenvectors 
\begin{equation}
 \bra{\Psi_n} \Psi_m \rangle = \delta_{mn},
\end{equation}
and $E_n \in \R$ its real eigenvalues.

Let us consider now an \textit{Hermitian} and \textit{invertible} operator $U$, \textit{i.e.} an operator $U$ such that there exists $U^{-1}$ such that 
\begin{equation}
 \label{eq:u_def_1}
 U^{-1} U = U \, U^{-1} = 1,
\end{equation}
and that 
\begin{equation}
 \begin{aligned}
 \label{eq:u_def_2}
 & U^\dagger = U \\
 & \big(U^{-1}\big)^{\dagger} = U^{-1}.
 \end{aligned}
\end{equation}
Then, the similarity transformed Hamiltonian $\tilde{H}$ is defined as
\begin{equation}
 \label{eq:def_htilde}
 \tilde{H} = U^{-1}\, H \, U.
\end{equation}
\subsection{Eigenvalues ans eigenvectors of $\tilde{H}$}
\subsubsection{Definition of left and right eigenvectors}
Regarding the properties of $\tilde{H}$, a first remark is that it is not Hermitian anymore
\begin{equation}
 \begin{aligned}
 \tilde{H}^\dagger & = \bigg(  U^{-1} \, H \,U \bigg)^\dagger \\
                   & = U\, H \, U^{-1}  \\
                   & \ne \tilde{H}.
 \end{aligned}
\end{equation}
Even though $\tilde{H}$ is not hermitian, it conserves the same eigenvalues than the original Hamiltonian $H$. 
The main difference with the original Hamiltonian are its eigenvectors: because $\tilde{H}$ is not Hermitian anymore, it possesses \textit{right} eigenvectors and \textit{left} eigenvectors. 
The right eigenvectors of a given operator $A$ are defined by
\begin{equation}
 A \ket{\Phi_n} = A_n \ket{\Phi_n}, 
\end{equation}
whereas the left eigenvectors of such operator are defined through
\begin{equation}
 A^{\dagger} \ket{X_n} = A_n \ket{X_n}.
\end{equation}
Therefore, if $A$ is hermitian, $A = A^{\dagger}$ and therefore $\ket{\Phi_n} = \ket{X_n} $, but for a non hermitian operator, the left and right eigenvectors do not coincide.

To find the right and left eigenvectors of $\tilde{H}$, one can insert the definition of $\tilde{H}$ (see Eq. \eqref{eq:def_htilde}) in Eq. \eqref{eq:h_spectr}
\begin{equation}
 \label{eq:tilde_1}
 \begin{aligned}
 \tilde{H} & = \sum_n E_n \, U^{-1} \, \ket{\Psi_n} \bra{\Psi_n}U.
 \end{aligned}
\end{equation}
We can define the right eigenvectors $\ket{\Phi_n}$ as
\begin{equation}
 \label{eq:def_right}
 \ket{\Phi_n} = U^{-1} \ket{\Psi_n},
\end{equation}
 because  from Eq. \eqref{eq:tilde_1}, we notice that the $\ket{\Phi_n}$ fulfil the right eigenvector relationship
\begin{equation}
 \begin{aligned}
 \tilde{H} \ket{\Phi_n} & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U\ket{\Phi_n} \\
                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U \bigg( U^{-1} \ket{\Psi_n} \bigg) \\
                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} \Psi_n \rangle \\
                        & = E_n          U^{-1} \ket{\Psi_n} \\
                        & = E_n  \ket{\Phi_n} \\
 \end{aligned}
\end{equation}
In a similar way, we can define the left eigenvectors $\ket{X_n}$ as 
\begin{equation}
 \label{eq:def_left}
 \ket{X_n} = U \ket{\Psi_n},
\end{equation}
because they fulfil the left eigenvalue equation
\begin{equation}
 \begin{aligned}
 \tilde{H}^{\dagger} \ket{X_n}  = E_n \, \ket{X_n}. 
 \end{aligned}
\end{equation}
\subsubsection{Biorthogonality, spectral representation and loose of the variational principle}
The left and right eigenvectors fulfill the so-called \textit{biorthogonal} property, as 
from Eqs. \eqref{eq:def_right} and \eqref{eq:def_left} one obtains 
\begin{equation}
 \overlap{X_j}{\Phi_i} = \bigg(U \ket{\Psi_n} \bigg)^\dagger \bigg(U^{-1}\ket{\Psi_J}\bigg)
\end{equation}
which, according to the Hermitian property of $U$ (see Eq.\eqref{eq:u_def_2}) simply becomes 
\begin{equation}
 \begin{aligned}
 \overlap{X_j}{\Phi_i} &= \matelem{\Psi_j}{U\,U^{-1}}{\Psi_i} \\
                       &= \overlap{\Psi_j}{\Psi_i} \\
                       &= \delta_{ji}.
 \end{aligned}
\end{equation}
Nevertheless, the right and left eigenvectors among themselves are not orthonormal as 
\begin{equation}
 \begin{aligned}
  \overlap{\Phi_j}{\Phi_i} & = \matelem{\Psi_j}{U^{-1}\,U^{-1}}{\Psi_i} \\
                           & = \matelem{\Psi_j}{U^{-2}}{\Psi_i},  
 \end{aligned}
\end{equation}
and 
\begin{equation}
 \begin{aligned}
  \overlap{X_j}{X_i} & = \matelem{\Psi_j}{U\,U}{\Psi_i} \\
                           & = \matelem{\Psi_j}{U^{2}}{\Psi_i}.  
 \end{aligned}
\end{equation}
Having obtained biorthonormal left and right eigenvectors, one can then obtain a spectral representation of the similarity transformed Hamiltonian 
\begin{equation}
 \tilde{H} = \sum_i E_i \ket{\Phi_i} \bra{X_i}, 
\end{equation}
which is very useful to study the variational principle, an important aspect of quantum chemistry. 
Let us consider a wave function $\Psi$ developed on the eigenvectors of $H$
\begin{equation}
 \ket{\Psi} = \sum_i c_i \ket{\Psi_i}.
\end{equation}
The expectation value of $H$ over $\Psi$ is then 
\begin{equation}
 \begin{aligned}
  \matelem{\Psi}{H}{\Psi} & = \sum_{i,j} c_i c_j \matelem{\Psi_j}{H}{\Psi_i} \\
                          & = \sum_{i,j} c_i c_j  E_i \overlap{\Psi_j}{\Psi_i} \\
                          & = \sum_{i} |c_i|^2 E_i \\
                          & \ge E_0
 \end{aligned}
\end{equation}
which gives the variational principle because of the orthogonality of eigenvectors of an \textit{Hermitian} operator. 
Now let us decompose the same wave function $\Psi$ on the right-eigenvectors of $\tilde{H}$ 
\begin{equation}
 \ket{\Psi} = \sum_i \tilde{c}_i \ket{\Phi_i},
\end{equation}
and consider the expectation value of $\tilde{H}$ over $\Psi$
\begin{equation}
 \begin{aligned}
  \matelem{\Psi}{\tilde{H}}{\Psi} & = \sum_{i,j} \tilde{c}_i \tilde{c}_j \matelem{\Phi_j}{\tilde{H}}{\Phi_i} \\
                                  & = \sum_{i,j} \tilde{c}_i \tilde{c}_j E_i \overlap{\Phi_j}{\Phi_i} 
 \end{aligned}
\end{equation}
which has no reason to be an upper bound to $E_0$ as $\overlap{\Phi_j}{\Phi_i} \ne \delta_{i,j}$. 
Therefore, we see that we cannot apply straightforwardly the variational principle 
to similarity transformed Hamiltonians, because of the lack of orthonormality of the right eigenvectors.

\section{A new form of Jastrow factor for transcorrelated Hamiltonian}
\subsection{The similarity transformed Hamiltonian}
Let us write the Hamiltonian of the He atom in the ${\bf r}_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
\begin{equation}
 H  = h_c + \frac{1}{r_{12}},
\end{equation}
where 
\begin{equation}
 \begin{aligned}
 h_c = &-\frac{1}{2} \sum_{i=1}^2 \bigg(\deriv{}{r_i}{2} + \frac{2}{r_i} \deriv{}{r_i}{} + \frac{2 Z}{r_i}\bigg) \\
     &-\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg) \\
     &-\bigg( \frac{\bd{r_1}}{r_1} \cdot \frac{\bd{r_{12}} }{r_{12}}  \deriv{}{r_1}{} + 
                \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg),
 \end{aligned}
\end{equation}
\label{sec:he_j}
Now let us consider the Similarity transformed Hamiltonian $\tilde{H}[j]$
\begin{equation}
 \label{eq:ht_0}
 \begin{aligned}
 \tilde{H}[j]&= e^{-j(r_{12})} H e^{j(r_{12})},
 \end{aligned}
\end{equation}
where $j(r_{12})$ is a general Jastrow factor depending only on $r_{12}$. 
Therefore, the only new terms arising in $\tilde{H}[j]$ with respect to $H$ are those coming from the differential operator in $r_{12}$,
\begin{equation}
 \mathcal{T}[j] =  -e^{-j(r_{12})}\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg)e^{j(r_{12})}.  
\end{equation}
Let us compute the action of $\mathcal{T}[j]$ on a general function $\phi(\br{}_1,\br{}_2)$ 
\begin{equation}
 \begin{aligned}
 \mathcal{T}[j]\phi(\br{}_1,\br{}_2) & =- e^{-j(r_{12})} \bigg[ \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{}\bigg]  e^{j(r_{12})} \phi(\br{}_1,\br{}_2) \\ 
                            &=  -\deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{2} - \frac{2}{r_{12}} \deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{} \\
  &- 2 \deriv{j(r_{12})}{r_{12}}{} \deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{} \\ 
  &- \bigg[ \frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  + \deriv{j(r_{12})}{r_{12}}{2} + \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2\bigg] \phi(r_{12}). 
 \end{aligned}
\end{equation}
Now, by defining the following operators 
\begin{equation}
 \label{eq:def_tt}
 \tilde{t}[j] = -2 \deriv{j}{r_{12}}{} \deriv{}{r_{12}}{},
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{W}[j] = -\frac{2}{r_{12}} \deriv{j}{r_{12}}{}  , 
\end{equation}
\begin{equation}
 \label{eq:def_wt}
 \tilde{w}[j] = -\deriv{j}{r_{12}}{2} - \bigg( \deriv{j}{r_{12}}{} \bigg)^2. 
\end{equation}
one can write the Similarity transformed Hamiltonian  as
\begin{equation}
 \label{eq:ht_phi}
 \tilde{H}[j] = h_c + \frac{1}{r_{12}}  + \tilde{W}[j] + \tilde{t}[j] + \tilde{w}[j] ,
\end{equation}
ore more explicitly 
\begin{equation}
 \tilde{H}[j] = h_c + \frac{1}{r_{12}}\bigg( 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg) + \tilde{t}[j] + \tilde{w}[j] .
\end{equation}
$\tilde{H}[j]$, because of the first-order differential operator in $\tilde{t}[j]$, is then non-hermitian.

\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
\label{sec:cusp}
The exact ground state wave function $\psiex$ of the usual Hamiltonian must satisfy the Schroedinger equation in real space 
\begin{equation}
 H \psiex(\br{}_1,\br{}_2) = E_0 \psiex(\br{}_1,\br{}_2)\quad \forall (\br{}_1,\br{}_2).
\end{equation}
When looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which translates into
\begin{equation}
 \label{eq:cusp_0}
 \lim_{r_{12}\rightarrow \infty}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
\end{equation}
or equivalently by multiplying by $r_{12}$
\begin{equation}
 \lim_{r_{12}\rightarrow \infty}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
\end{equation}
which translates into the famous cusp condition of Kato\cite{Kat-CPAM-57}, 
\begin{equation}
 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
\end{equation} 
For a pedagogical and general introduction to the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.

Regarding now the similarity transformed Hamiltonians, their exact eigenvectors must also satisfy an eigenvalue equation. For instance, the right ground-state eigenvector becomes  
\begin{equation}
 \label{eq:hpi0_ex}
 \tilde{H}[j] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
\end{equation}
Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[j]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
which involves also the term $\tilde{W}[j]$ in $\tilde{H}[j]$ (see Eq.\eqref{eq:def_wt} and \eqref{eq:ht_phi}. Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
\begin{equation}
 \label{eq:cusp_phi_0}
 \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
\end{equation}
Interestingly, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{j(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction modified by the presence of the Jastrow factor in $\tilde{H}[j]$. 
Therefore, as long as one imposes that 
\begin{equation}
 \label{eq:cusp_phi_1}
  \deriv{j(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
\end{equation}
which is nothing but the cusp condition for the Jastrow factor $j(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then obtain a non-divergent effective electron-electron interaction. 
Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
\begin{equation}
 \label{eq:cusp_phi_2}
 \deriv{\phiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
\end{equation}
which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[j]$ are cuspless. 
For instance, a simple Jastrow factor of the form $j(r_{12}) = \frac{1}{2} r_{12}$ release $\phiex(\br{}_1,\br{}_2)$ from 
the constraint of fulfilling the cusp condition. 
%Another way to phrase Eq.\eqref{eq:cusp_phi_1} and Eq.\eqref{eq:cusp_phi_2} is that because of the Jastrow factor, the similarity transformed Hamiltonian exhibits an effective non-divergent electron-electron interaction, which does not impose any cusp condition to the eigenfunctions of $\tilde{H}[j]$.

Another form of effective Hamiltonians leading to cuspless eigenfunctions are those obtained from RS-DFT 
where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively. 
The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ gives back the usual Kohn-Sham theory.  
In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
Applied to a two electron system and looking in regions where $r_{12}\approx 0$, the leading terms of the self-consistent Schroedinger-like equation of RS-DFT reads 
\begin{equation}
 \label{eq:cusp_psi_mu_0}
 \lim_{r_{12}\rightarrow \infty}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
\end{equation}
and as the long-range interaction is non divergent at $r_{12}=0$ as long as $\mu$ remains finite 
\begin{equation}
 \lim_{r_{12} \rightarrow 0} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{2 \mu}{\sqrt{\pi}} , 
\end{equation}
one obtains that 
\begin{equation}
 \label{eq:cusp_psi_mu_1}
 \deriv{\Psi^\mu(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
\end{equation}
which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.

\subsection{A new form of Jastrow factor $j(\mu,r_{12})$ mimicking a long-range interaction}
In section \ref{sec:cusp} we reviewed the forms of limit conditions at $r_{12}=0$ involved in different eigenvalue equations, which of course depends on the nature of the interaction at $r_{12}=0$. 
In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order. 
\subsubsection{The working equation for $j(\mu,r_{12})$ }
Eq. \eqref{eq:ht_phi} gives the similarity transformed Hamiltonian for an arbitrary Jastrow factor, 
and with respect to the usual Hamiltonian, $\tilde{H}[j]$ contains two new classes of terms: 
a new electron-electron potential $\tilde{w}[j]+ \tilde{W}[j]$ and a new differential operator  $\tilde{t}[j]$. 
Of course, these new terms depends on the explicit form of the Jastrow factor $j(r_{12})$ chosen. 
Now, we impose the form of $j(r_{12})$ such that it mimics, at leading order, the long-range effective interaction of RS-DFT. 
Mathematically, this conditions implies that 
\begin{equation}
 \begin{aligned}
 \label{def_j_00}
 \tilde{W}[j] + \frac{1}{r_{12}}&= \frac{\text{erf}(\mu r_{12})}{r_{12}} \\ 
\Leftrightarrow -\frac{2}{r_{12}} \deriv{j(r_{12},\mu)}{r_{12}}{} + \frac{1}{r_{12}} & = \frac{\text{erf}(\mu r_{12})}{r_{12}}, 
 \end{aligned}
\end{equation}
which is equivalent to 
\begin{equation}
 \label{def_j_0}
 \deriv{j(r_{12},\mu)}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2}.
\end{equation}
The solution to Eq. \eqref{def_j_0} is 
\begin{equation}
 \label{eq:def_j}
 j(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2},
\end{equation}
which depends on a unique parameter $\mu$, 
and the associated transcorrelated Hamiltonians obtained with $j(r_{12};\mu)$ is also controlled by $\mu$
\begin{equation}
 \label{eq:def_ht_mu}
 \tilde{H}[\mu] = e^{-j(r_{12};\mu)} H e^{j(r_{12};\mu)}. 
\end{equation}
Therefore, the right eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the ground state eigenvector is defined by 
\begin{equation}
 \tilde{H}[\mu] \phimu(\br{}_{1},\br{}_{2}) = E_0 \phimu(\br{}_{1},\br{}_{2}), 
\end{equation}
where $E_0$ is the exact ground state energy.

\subsubsection{A few properties of $j(r_{12};\mu)$}
The new Jastrow $j(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which controls the value of the leading term of the effective interaction at $r_{12}=0$ (see Eq.\eqref{def_j_00}). 
To understand the physical content together with the mathematical properties of $j(r_{12};\mu)$, 
one must keep in mind that the complete correlating factor $\mathcal{J}(r_{12},\mu)$ is 
\begin{equation}
 \mathcal{J}(r_{12},\mu) = \text{exp}\bigg(j(r_{12};\mu)\bigg),
\end{equation}
and that the exact wave function $\psiex(\br{}_1,\br{}_2)$ is formally expressed as 
\begin{equation}
 \psiex(\br{}_1,\br{}_2) = \mathcal{J}(r_{12},\mu) \phimu(\br{}_{1},\br{}_{2}).  
\end{equation}
From Eq.\eqref{eq:def_j} we can notice that 
\begin{equation}
 \lim_{r_{12} \rightarrow \infty}j(r_{12};\mu) = 0,
\end{equation}
which means that 
\begin{equation}
 \lim_{r_{12} \rightarrow \infty}\mathcal{J}(r_{12};\mu) = 1,
\end{equation}
and therefore $j(r_{12};\mu)$ impacts only the small $r_{12}$ behaviour,  
which is expected since the equation determining $j(r_{12},\mu)$ is obtained from the small $r_{12}$ limit of the Schroedinger equation (see Eq.\eqref{def_j_00}).

To better understand the physical content of at $r_{12}\approx 0$,  
let us Taylor expand the function $j(r_{12};\mu)$ 
\begin{equation}
 \label{eq:j_dl}
 j(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + o(r_{12}^4).
\end{equation}
which leads for $\mathcal{J}(r_{12},\mu)$
\begin{equation}
 \label{eq:bigJ_dl}
 \mathcal{J}(r_{12};\mu) = e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2} + o(r_{12}^4) .
\end{equation}
Therefore, one can Taylor expand the exact wave function in the vicinity of $\br{}_1$ for small $r_{12}$ 
\begin{equation}
 \label{eq:psi0_ex_dl}
 \psiex(\br{}_1,\br{}_2) = \phiex(\br{}_1,\br{}_1)e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2} + o(r_{12}^4) .
\end{equation}
As one can see from Eq.\eqref{eq:bigJ_dl} and Eq.\eqref{eq:psi0_ex_dl}, the first term $e^{-\frac{1}{2\sqrt{\pi}\mu}}$ defines the depth of the Coulomb hole induced by the correlating factor $\mathcal{J}(r_{12};\mu)$ at $r_{12}=0$. 
This term is imposed by the term $- \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2}$ in the Jastrow factor. 
Therefore, the probability of finding two electrons at $r_{12}=0$ (\textit{i.e.} the on-top pair density) is larger for $\phiex(\br{}_1,\br{}_2)$ than for $\psiex(\br{}_1,\br{}_2)$.  
This can be easily understood noticing that, by construction, $\tilde{H}[\mu]$ does not contain any divergent potential term at $r_{12}=0$, and therefore the electrons repels less each other.

The second term in \eqref{eq:bigJ_dl} is linked to the cusp condition. 
Indeed, as shown in section \ref{sec:cusp}, $\phiex(\br{}_1,\br{}_2)$ does not have a cusp, and therefore $\mathcal{J}(r_{12};\mu)$ mus restore it. This term is imposed by the term $\frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg)$ in the Jastrow factor. 
The last term in Eq.\eqref{eq:bigJ_dl} modifies the curvature of the Coulomb hole.

Coming now to the behaviour of $j(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12},\mu)$. 
\begin{figure*}
 \label{fig_j_mu}
        \includegraphics[width=0.60\linewidth]{small_mu_j.pdf}\\
        \includegraphics[width=0.60\linewidth]{small_mu_exp_j.pdf}\\
        \caption{Shape of $j(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(j(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
\end{figure*}
From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $j(r_{12};\mu)$, ii) the larger the $\mu$, the closer $j(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function.

\subsubsection{The explicit form of  $\tilde{H}[\mu]$ and some of its properties}
Having established the explicit form of $j(r_{12};\mu)$ and some of its properties, one can now 
look at the explicit form of the transcorrelated Hamiltonian obtained with $j(r_{12};\mu)$,  
which, by injecting the form of \eqref{eq:def_j} in Eq.\eqref{eq:ht_phi}, reads 
\begin{equation}
  \begin{aligned}
 \label{eq:exp_ht_mu}
   \tilde{H}[\mu] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
  \end{aligned}
\end{equation}
From Eq.\eqref{eq:exp_ht_mu}, one can define an effective scalar electron-electron interaction $\tilde{\mathcal{W}}_{ee}(r_{12}) $ 
\begin{equation}
 \label{eq:deff_w_new}
 \tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4},
\end{equation}
whose shape is illustrated in Fig\ref{fig_wee_mu}. 
\begin{figure*}
 \label{fig_wee_mu}
        \includegraphics[width=0.60\linewidth]{w_ee.pdf}\\
        \includegraphics[width=0.60\linewidth]{w_ee_bis.pdf}\\
        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (up) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (bottom) for different values of $\mu$.}
\end{figure*}
From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential 
is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT. 
Nevertheless, as observed from Fig.\ref{fig_wee_mu}, it is significantly different 
from the long-range interaction at small $r_{12}$, 
%\begin{equation}
% \label{eq:lim_mu_2}
% \lim_{r_{12} \rightarrow 0} \tilde{\mathcal{W}}_{ee}(r_{12}) = \frac{3 \mu}{\sqrt{\pi}} - \frac{1}{4}. 
%\end{equation}
%
and it is not monotonic as it can be even slightly attractive for small values of $\mu$. 
This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $j(r_{12},\mu)$ (see Eqs.\eqref{def_j_00} and \eqref{def_j_0}). 
If one desires to impose that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}}$, one would have to solve the non-linear differential equation 
\begin{equation}
 2 \deriv{j(r_{12})}{r_{12}}{} + r_{12} \bigg( \deriv{j(r_{12})}{r_{12}}{2} + \bigg[ \deriv{j(r_{12})}{r_{12}}{} \bigg]^2\bigg) = 1 - \text{erf}(\mu r_{12}), 
\end{equation}
whose solution is unknown to the best of the author knowledge. 
%To illustrate the shape of 
%which does not diverge at $r_{12} = 0$
%\end{equation}

Coming now to the limits of $\tilde{H}[\mu]$ when $\mu \rightarrow \infty$, one expects that as
\begin{equation}
 \label{eq:lim_mu_0}
 \lim_{\mu  \rightarrow \infty }j(\mu,r_{12}) = 0, 
\end{equation}
one recovers the usual Hamiltonian in that limit
\begin{equation}
 \label{eq:lim_mu_1}
 \lim_{\mu \rightarrow \infty} \tilde{H}[\mu] = H.
\end{equation}
Nevertheless, in the large $\mu$ limit, one can notice that 
\begin{equation}
 \label{eq:lim_mu_3}
 \lim_{\mu \rightarrow \infty} \tilde{\mathcal{W}}_{ee}(r_{12})  = \frac{1}{r_{12}} + \delta(r_{12}) 
\end{equation}
where $\delta(r_{12})$ is the Dirac distribution, and as the firs-order differential term vanishes in the large $\mu$ limit (see Eq.\eqref{eq:exp_ht_mu}), one could be tempted to write that 
\begin{equation}
 \begin{aligned}
 \label{eq:lim_mu_4}
 \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = h_c + \frac{1}{r_{12}} + \delta(r_{12}) \\
                                             & = H + \delta(r_{12})  \\
                                             & \ne H,
 \end{aligned}
\end{equation}
which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}. 
Nevertheless, as the right hand side of Eq.\eqref{eq:lim_mu_4} contains a Delta distribution, it must be considered in the sense of distributions an not point wise. 
Therefore, considering $f(\br{}_1,\br{}_2)$, a bounded generic square integrable function in $\R^6$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality 
\begin{equation}
 \label{eq:lim_mu_5}
 \begin{aligned}
& \matelem{f}{H}{f} = \lim_{\mu \rightarrow \infty} \matelem{f}{\tilde{H}[\mu]}{f} \\
& \Leftrightarrow H = \tilde{H}[\mu],
 \end{aligned}
\end{equation}
and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
\begin{equation}
 \label{eq:lim_mu_6}
 \int \text{d}\br{}_1 \text{d}\br{}_2 f(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
\end{equation}
To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$ and show that 
\begin{equation}
 \int \text{d}\br{}_1 \text{d}\br{}_2 f(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{f}(r_{12}) \delta(r_{12}) r_{12}^2 
\end{equation}
where $\tilde{f}(x)$ is the function $f(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
$|\br{}_1-\br{}_2| = x$. 
As the $f(\br{}_1,\br{}_2)$ remain finite for all $(\br{}_1,\br{}_2)$, the function $\tilde{f}(x)$ 
do not diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
\begin{equation}
 \int \text{d}r{}_{12}  \tilde{f}(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
\end{equation}
and therefore Eq.\eqref{eq:lim_mu_6} which implies Eq.\eqref{eq:lim_mu_1}.

\section{General formulation of similarity transformed Hamiltonian}
\subsection{General equations for a two-electron system}
According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
\begin{equation}
 \label{ht_def_g}
 e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
\end{equation}
where $\hat{\tau} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j \frac{1}{r_{ij}}}$. Of course, only the differential terms do not commute in Eq. \eqref{ht_def_g}. 
Let us compute each terms, beginning with the action of $\big[ H,\hat{\tau} \big]$ on a function $\phi(\br{}_1,\hdots \br{}_N)$.
\begin{equation}
 \label{eq:com1_1}
 \begin{aligned}
 \bigg[ H,\hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
  & = -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\
  & +  \frac{1}{2} \sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \nabla^2_i \phi(\br{}_1,\hdots \br{}_N). 
 \end{aligned}
\end{equation}
The first term in the right-hand side of Eq. \eqref{eq:com1_1} is 
\begin{equation}
 \label{eq:com1_2}
 \begin{aligned}
&  -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\ 
= &-\frac{1}{2}\sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \bigg( \nabla^2_i \phi(\br{}_1,\hdots \br{}_N)\bigg) \\
  &-\frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
  &-\sum_i \bigg(\nabla_i \sum_{j>k}u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).
 \end{aligned}
\end{equation}
Inserting Eq. \eqref{eq:com1_2} in Eq. \eqref{eq:com1_1} leads to cancellation of the terms involving $\nabla^2_i \phi(\br{}_1,\hdots \br{}_N)$
\begin{equation}
 \label{eq:com1_3}
  \begin{aligned}
 \big[ H,\hat{\tau} \big]\phi(\br{}_1,\hdots \br{}_N) & =  \frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
  & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg)
 \end{aligned}
\end{equation}
and therefore one can write the first commutator of Eq. \eqref{ht_def_g} as 
\begin{equation}
 \label{eq:com1_4}
 \begin{aligned}
  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
                            & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i  \bigg),
 \end{aligned}
\end{equation}
and as $\nabla_i f(\br{}_j) = \delta_{ij} \nabla_i f(\br{}_i)$ one obtains 
\begin{equation}
 \label{eq:com1_5}
 \begin{aligned}
  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg) \\
                            & -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) \\
                            & -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg).  
 \end{aligned}
\end{equation}
Then, one has to compute the second-order commutator in Eq. \eqref{ht_def_g}: 
\begin{equation}
 \label{eq:com2_1}
 \begin{aligned}
 & \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] \phi(\br{}_1,\hdots \br{}_N) = \\
 & \bigg[ -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg), \sum_{j>k} u(\br{}_j,\br{}_k)  \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
+& \bigg[ -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
+& \bigg[ -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N). 
 \end{aligned}
\end{equation}
The first term in Eq. \eqref{eq:com2_1} is actually a potential term and therefore it cancels out, then it comes
\begin{equation}
 \label{eq:com2_2}
 \begin{aligned}
  \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 - \sum_j \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 
 \end{aligned}
\end{equation}
and so the two commutators become
\begin{equation}
 \begin{aligned}
 \label{eq:comtot}
& \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\
   &\sum_{i>j} -\frac{1}{2} \bigg( \nabla^2_i u(\br{}_i,\br{}_j) +  \nabla^2_j u(\br{}_i,\br{}_j) 
    + \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 + \bigg( \nabla_j u(\br{}_i, \br{}_j) \bigg)^2  \bigg) \\
   & -\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) -\bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg). 
 \end{aligned}
\end{equation}

\section{Computations of integrals}
\subsection{$\nabla_i u(\br{}_i,\br{}_j)$}
\begin{equation}
 \nabla_1 u(\br{}_1,\br{}_2) = \deriv{}{x_1}{}u(r_{12}) {\bf e}_{x1} + \deriv{}{y_1}{}u(r_{12}) {\bf e}_{y1} + \deriv{}{z_1}{}u(r_{12}) {\bf e}_{z1},
\end{equation}
and 
\begin{equation}
 \deriv{}{x_1}{}u(r_{12}) = \deriv{}{r_{12}}{}u(r_{12}) \deriv{r_{12}}{x_1}{},
\end{equation}
and as $r_{12} = \sqrt{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2} $ one has
\begin{equation}
 \deriv{r_{12}}{x_1}{} = \frac{x_1 - x_2}{r_{12}} = -\deriv{r_{12}}{x_2}{},
\end{equation}
and according to Eq. \eqref{def_j_0}
\begin{equation}
 \deriv{u}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2},
\end{equation}
one obtains 
\begin{equation}
 \label{eq:dx1_u}
 \deriv{}{x_1}{}u(r_{12}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
\end{equation}
Similarly, 
\begin{equation}
 \label{eq:dx2_u}
 \deriv{}{x_2}{}u(r_{12}) = \frac{\text{erf}(\mu r_{12})}{2 r_{12} -1 } \bigg(x_1 - x_2 \bigg).
\end{equation}
Therefore, 
\begin{equation}
 \label{eq:nabla_u}
 \begin{aligned}
 \nabla_1 u(\br{}_1,\br{}_2) = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
 & \bigg( (x_1 - x_2) {\bf e}_{x1} + (y_1 - y_2) {\bf e}_{y1} + (z_1 - z_2) {\bf e}_{z1}\bigg) \\
 &=  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big)
 \end{aligned}
\end{equation}

\subsection{$\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg)^2$}
According to Eq. \eqref{eq:nabla_u}, one obtains 
\begin{equation}
 \label{eq:nabla_u2_0}
 \begin{aligned}
 \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2 & = \bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg)^2\\
 & \bigg( (x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2 \bigg) \\
                                           &  \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4 \big(r_{12}\big)^2} \times \big(r_{12}\big)^2 \\
                                           & = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
 \end{aligned}
\end{equation}
and therefore 
\begin{equation}
 \label{eq:nabla_u2}
 \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2  + \bigg(\nabla_2 u(\br{}_1,\br{}_2)\bigg)^2 = 2 \times \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
\end{equation}

\subsection{$\nabla_i u(\br{}_i,\br{}_j) \cdot \bigg( \nabla_i   \bigg)$}
According to Eq. \eqref{eq:nabla_u}, one obtains 
Therefore, 
\begin{equation}
 \begin{aligned}
 \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg).
 \end{aligned}
\end{equation}
And noticing the minus sign coming from the derivative in $\br{}_2$, the total operator can be written as 
\begin{equation}
 \begin{aligned}
& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big) +
         (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg),
 \end{aligned}
\end{equation}
but as 
\begin{equation}
 \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
\end{equation}
one can rewrite as 
\begin{equation}
 \begin{aligned}
 \label{eq:nabla_i_nabla0}
& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
 \end{aligned}
\end{equation}
Then, introducing ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$, can notice that 
\begin{equation}
 \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
\end{equation}
and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
\begin{equation}
 \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
\end{equation}
and therefore 
\begin{equation}
 \begin{aligned}
 \label{eq:nabla_i_nabla1}
& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
 = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{}. 
 \end{aligned}
\end{equation}

\subsection{$\nabla^2_i u(\br{}_i,\br{}_j)$}
\begin{equation}
 \begin{aligned}
 &\nabla^2_1 u(\br{}_1,\br{}_2) =  \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{y_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{z_{1}}{2}  u(\br{}_1,\br{}_2) \\
                                 = & \deriv{}{x_{1}}{}\bigg( \deriv{}{x_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
                                   \deriv{}{y_{1}}{}\bigg( \deriv{}{y_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
                                   \deriv{}{z_{1}}{}\bigg( \deriv{}{z_{1}}{}u(\br{}_1,\br{}_2) \bigg). 
 \end{aligned}
\end{equation}
But according to Eq. \eqref{eq:dx1_u}, one obtains 
\begin{equation}
 \begin{aligned}
 \label{eq:d2_x1_0}
& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{}\bigg(\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
& = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
 \end{aligned}
\end{equation}
Similarly, according to Eq. \eqref{eq:dx2_u} one obtains for the second order derivative in $x_2$
\begin{equation}
 \begin{aligned}
 \label{eq:d2_x2_0}
& \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{2}}{}\bigg(\frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) -  \frac{\text{erf}(\mu r_{12}) -1}{2 r_{12}} \\
& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12}}. 
 \end{aligned}
\end{equation}
Also
\begin{equation}
 \label{eq:d2_x1_1}
 \begin{aligned}
 \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = & \deriv{}{r_{12}}{}\bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) \deriv{r_{12}}{x_1}{} \\
      = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} 
 \end{aligned}
\end{equation}
and similarly
\begin{equation}
 \label{eq:d2_x2_1}
 \begin{aligned}
 \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -  1}{2 r_{12}}  = &\deriv{}{r_{12}}{}\bigg( \frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}}\bigg) \deriv{r_{12}}{x_2}{} \\
              = & (-1) \frac{x_1 - x_2}{r_{12}} (-1)  \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
              = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
              = & \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}},
 \end{aligned}
\end{equation}
which implies that 
\begin{equation}
  \label{eq:d2_x2_2}
 \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2).
\end{equation}

To continue, as 
\begin{equation}
 \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = -\frac{1}{r_{12}}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg), 
\end{equation}
one obtains 
\begin{equation}
 \label{eq:d2_x1_2}
 \begin{aligned}
 \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} & = \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
 & =  -\frac{(x_1 - x_2)}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg). 
 \end{aligned}
\end{equation}

Therefore, Eq. \eqref{eq:d2_x1_0} becomes 
\begin{equation}
 \begin{aligned}
 \label{eq:d2_x1_2}
& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}  \\
& = -\frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
& = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) 
- \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} 
 \end{aligned}
\end{equation}
and so 
\begin{equation}
 \begin{aligned}
 \label{eq:lapl_u_final}
 \bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} \bigg) u(\br{}_1,\br{}_2) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
&- 2 \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}.
 \end{aligned}
\end{equation}
Therefore, 
\begin{equation}
 \begin{aligned}
 \label{eq:d2_x1_2}
 &\bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{y_{2}}{2} + \deriv{}{z_{1}}{2} + \deriv{}{z_{2}}{2} \bigg) u(\br{}_1,\br{}_2) \\ 
 & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
&- 2 \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
 & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2} \bigg) 
- 2 \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
 & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \times 2 - 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
 & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
 \end{aligned}
\end{equation}
\subsection{Sum of all terms}
According to Eq. \eqref{eq:comtot}, Eq. \eqref{eq:nabla_i_nabla1}, Eq. \eqref{eq:nabla_u2} and Eq. \eqref{eq:lapl_u_final}, the additional terms arising from the commutators in $\tilde{H}[j]$ are (for a two-electron system) 
\begin{equation}
 \begin{aligned}
 \label{eq:comtot2}
 & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
 & -\frac{1}{2} 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}  \bigg) \\
   &- \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
 \end{aligned}
\end{equation}
or equivalently
\begin{equation}
 \begin{aligned}
 \label{eq:comtot2}
 & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
 & -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
   & + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
 \end{aligned}
\end{equation}
Therefore, the full similarity transformed Hamiltonian can be written as
\begin{equation}
  \begin{aligned}
   \tilde{H}[j] = & \sum_{i = 1,2} \bigg( -\frac{1}{2} \big(\nabla_i\big)^2 + v(\br{}_i)  \bigg) + \frac{1}{r_{12}} \\
&   -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
  \end{aligned}
\end{equation}
or equivalently 
\begin{equation}
  \begin{aligned}
   \tilde{H}[j] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
  \end{aligned}
\end{equation}
which corresponds precisely to Eq. \eqref{eq:h_tilde_r12}.

\section{Numerical computation of integrals}
\subsection{Fit of functions}
\subsubsection{Fit of $1-\text{erf}(x)$}
At some point we would like to fit the following function
\begin{equation}
 g(x) = 1-\text{erf}(x)
\end{equation}
which can be done, for instance by 
\begin{equation}
 h(x,\alpha,\beta,c) = e^{-\alpha x - \beta x^2}
\end{equation}
with $\alpha=1.09529$ and $\beta = 0.756023$. 
So by posing $y=\mu x$, $x=y/\mu$ then
\begin{equation}
 \label{fit_erf}
 \begin{aligned}
  g(x,\mu)  =& 1 - \text{erf}(\mu x) \approx e^{-\alpha \mu x - \beta (\mu x)^2}\\ 
        =& e^{-\alpha \mu x } e^{-\beta \mu^2 x^2} \\
        =& h(x,\alpha \mu, \beta \mu^2).
 \end{aligned}
\end{equation}
Therefore, one can fit $g(x)^2$ as 
\begin{equation}
 \begin{aligned}
 g(x,\mu)^2 = \bigg( 1 - \text{erf}(\mu x) \bigg)^2\\
           &= \bigg( e^{-\alpha \mu x } e^{-\beta \mu^2 x^2}\bigg)^2 \\
           &= e^{-2\alpha  \mu x } e^{-2 \beta \mu^2 x^2} \\
           &= h(x,2 \alpha \mu, 2 \beta \mu^2).
 \end{aligned}
\end{equation}

\subsubsection{Fit of $e^{-x}$}
The fit of $1 - \text{erf}(\mu x)$ in Eq. \eqref{fit_erf} involves a Slater function, which is always rather complex to integrate. 
Nevertheless, we can fit a Slater function with Gaussian functions (that is what quantum chemistry is about):
\begin{equation}
 e^{-X} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m X^2}, 
\end{equation}
and, by posing $X=\gamma x$ one can fit any Slater function as
\begin{equation}
 e^{-\gamma x} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m \gamma^2 x^2}. 
\end{equation}
To find the $\{c_m,\zeta_m\}$ parameters, I performed a Hartree Fock calculation on the Hydrogen atom using the $s$ functions of the ANO-RCC basis set which contains 8 gaussians.

\subsection{Computation of integrals with $\text{exp}(-\alpha r_{12}^2)$}
As essentially all functions of $r_{12}$ involve directly or indirectly (\textit{i.e.} through a fit) gaussian functions, we will have to evaluate such integrals
\begin{equation}
 \begin{aligned}
  \int \text{d}\br{}_1  \text{d}\br{}_2& \big( x_1 - A_x \big)^{a_x}  \big( x_2 - B_x \big)^{b_x} 
                                         \big( y_1 - A_y \big)^{a_y}  \big( y_2 - B_y \big)^{b_y} 
                                         \big( z_1 - A_z \big)^{a_z}  \big( z_2 - B_z \big)^{b_z} \\
                                       & \text{exp}(-\alpha \big(\br{}_1 - {\bf A} \big)^2)
                                         \text{exp}(-\beta  \big(\br{}_2 - {\bf B} \big)^2)
                                         \text{exp}(-\delta \big(\br{}_1 - \br{}_2 \big)^2)
 \end{aligned}
\end{equation}
which can be transformed into product of types 
\begin{equation}
 \begin{aligned}
  \int \text{d}x_1 \text{d}x_2 & \big( x_1 - A_x \big)^{a_x} \big( x_2 - B_x \big)^{b_x} \\ 
  & \text{exp}(-\alpha \big(x_1 - A_x \big)^2) \text{exp}(-\alpha \big(x_2 - B_x \big)^2) \text{exp}(-\delta \big(x_1 - x_2 \big)^2)
 \end{aligned}
\end{equation}

\section{New form of jastrow factor}
We want the jastrow factor $j(r_{12})$ to fulfil such equation
\begin{equation}
 - \bigg[ \frac{2}{r_{12}} \deriv{j}{r_{12}}{}  + \deriv{j}{r_{12}}{2} \bigg] + \frac{1}{r_{12}} = \frac{\text{erf}\big( \mu r_{12} \big)}{r_{12}}.
\end{equation}
The solution for such an equation is 
\begin{equation}
 j(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2} + \frac{1}{4 r_{12}} \bigg(c_1 - \frac{\text{erf}\big(\mu r_{12} \big)}{\mu^2} \bigg).
\end{equation}
The constant $c_1$ can be found to impose that 
\begin{equation}
 \lim_{r_{12} \rightarrow 0 } j(r_{12}) < \infty,
\end{equation}
which means $c_1 = 0$. Therefore the new jastrow factor is 
\begin{equation}
 j(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2}  - \frac{\text{erf}\big(\mu r_{12} \big)}{4 \mu^2 r_{12}}.
\end{equation}

\section{One body term jastrow}
\subsection{The case of the Hydrogen atom}
We want to find a Jastrow factor which will take care of the nuclear-electron cusp condition, and we will begin by the Hydrogen atom.

Let us write the Hamiltonian of the hydrogenoid atom in the radial coordinate for the $l=0$ sector 
\begin{equation}
 H = -\frac{1}{2} \big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\big) - \frac{Z}{r}.
\end{equation}
To do so, we have to compute the kinetic part acting on the Jastrow factor acting on a function depending only on the radial coordinate $\phi( r)$
\begin{equation}
 \label{eq:h_atom_j}
 \begin{aligned}
 & -\frac{1}{2}e^{-j(r)}\big(\deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) e^{j(r)}\phi(r)  = \\
 & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) \phi(r) \\
 &-\deriv{j(r)}{r}{}\deriv{}{r}{}\phi(r) \\
 &-\frac{1}{r}\deriv{j(r)}{r}{}\phi(r)  - \frac{1}{2}\deriv{j(r)}{r}{2}\phi(r)  -  \frac{1}{2}\bigg(\deriv{j(r)}{r}{} \bigg)^2 \phi(r).
 \end{aligned}
\end{equation}
Therefore the full similarity transformed Hamiltonian $\tilde{H}[j]$ is 
\begin{equation}
 \begin{aligned}
 \label{eq:one_e_0}
 & e^{-j(r)}H\,e^{j(r)} = \\
 & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) -\deriv{j(r)}{r}{}\deriv{}{r}{}\\
 &-\frac{1}{r}\bigg(\deriv{j(r)}{r}{} + Z \bigg) \\ 
 & - \frac{1}{2}\deriv{j(r)}{r}{2} -  \frac{1}{2}\bigg(\deriv{j(r)}{r}{} \bigg)^2.
 \end{aligned}
\end{equation}
Similarly to what have been proposed in Section \ref{sec:he_j}, we want to find the Jastrow factor $j(r,\mu,Z)$ such that 
\begin{equation}
 \label{eq:one_e_01}
 -\frac{1}{r}\bigg(\deriv{j(r,\mu,Z)}{r}{} + Z \bigg) = -Z\frac{\text{erf}(\mu r)}{r},
\end{equation}
or equivalently
\begin{equation}
 \label{eq:one_e_1}
 \deriv{}{r}{}j(r,\mu,Z) = Z\bigg( \text{erf}(\mu r) - 1\bigg).
\end{equation}
The Jastrow factor fulfilling Eq. \eqref{eq:one_e_1} is 
\begin{equation}
 \label{eq:one_e_2}
 j(r,\mu,Z) = -Z r \bigg( 1 - \text{erf}\big(\mu r\big) \bigg) + \frac{Z}{\sqrt{\pi}\mu} e^{-\big(\mu r \big)^2}. 
\end{equation}
Now, we can plug $j(r,\mu,Z)$ into Eq. \eqref{eq:one_e_0} in order to compute the explicit form of the similarity transformed Hamiltonian. 
To do so, we use Eq. \eqref{eq:one_e_1}, and also that 
\begin{equation}
 \deriv{}{r}{2}j(r) = \frac{2 \mu Z }{\sqrt{\pi}} e^{-(\mu r)^2}.
\end{equation}
One obtains then the similarity transformed Hamiltonian 
\begin{equation}
 \begin{aligned}
 \tilde{H}[j] = & e^{-j(r)} H e^{j(r)} \\
              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) - \frac{Z}{r}  \\
                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{} \\
                & - Z \frac{\text{erf}(\mu r) - 1}{r} \\
                & -Z \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
                & - \frac{1}{2}Z^2 \bigg( \text{erf}(\mu r) -1 \bigg)^2,
 \end{aligned}
\end{equation}
and one can notice that the $\frac{-Z}{r}$ interaction cancels out to give
\begin{equation}
 \label{eq:one_e_3}
 \begin{aligned}
 \tilde{H}[j] = & e^{-j(r)} H e^{j(r)} \\
              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big)  \\
                & -Z \bigg[ \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} + \frac{\text{erf}(\mu r)}{r} + \frac{1}{2}Z \bigg( \text{erf}(\mu r) -1 \bigg)^2 \bigg] \\
                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{}. 
 \end{aligned}
\end{equation}
Therefore, compared to the usual Hamiltonian, the similarity transformed Hamiltonian contains a different local interaction which is clearly non divergent, but also a new short-range differential operator.

\subsection{General equation}
Now that we know the general form of the one-body Jastrow factor for a one electron system, we can generalize it 
to an $N$-electron system and an $M$ nucleus system by just taking the following form 
\begin{equation}
 e^{\hat{\tau}({\bf r}_1,\hdots , {\bf r}_i,{\bf r}_N)} = e^{-\sum_i^N J({\bf r}_i)} 
\end{equation}
where $J({\bf r}_i)$ has the following form 
\begin{equation}
 J({\bf r}_i) = \sum_{A} j(r_{iA},\mu,Z_A) 
\end{equation}
where $j(r,\mu,Z)$ is given by Eq. \eqref{eq:one_e_2} and $r_{iA} = \big|{\bf r}_i - {\bf R}_A \big|$. 
According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the equation of the similarity transformed Hamiltonian is similar  
to that of Eq. \eqref{ht_def_g} but with a new form of Jastrow factor. 
Therefore one needs to compute $\big[ H,\hat{\tau} \big]$ and $\frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]$. 
Let us begin by $\big[ H,\hat{\tau} \big]$, and as before, we apply it to a general function $\phi(\br{}_1,\hdots \br{}_N)$:
\begin{equation}
 \label{eq:one_com1_1}
 \begin{aligned}
 \bigg[ H, \hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{j} J(\br{}_j) \bigg]      \phi(\br{}_1,\hdots \br{}_N) \\    
                                                        & = -\frac{1}{2} \sum_i \bigg( \big(\nabla^2_i J({\bf r}_i)\big) + 2\nabla_i J({\bf r}_i) \cdot \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).  
 \end{aligned}
\end{equation}
Therefore, one can write that term as
\begin{equation}
 \label{eq:one_com1_2}
 \begin{aligned}
  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg) \\
                            & -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg).
 \end{aligned}
\end{equation}
After some math, the second-order commutator is simply 
\begin{equation}
 \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
\end{equation}
So eventually, the similarity transformed operator becomes 
\begin{equation}
 \begin{aligned}
& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg)    
                                                                   -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
                                                                   -\frac{1}{2}\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
 \end{aligned}
\end{equation}
Therefore, the addition of the jastrow operator does not add extra two-body terms. 
\subsection{Computation of the total operator}
\subsubsection{Computation of $\nabla_i J(\br{}_i)$}
\begin{equation}
 \begin{aligned}
&\nabla_i J(\br{}_i) = \sum_A \nabla_i J(r_{iA},Z_A) \\
                    &= \sum_A \deriv{}{x_i}{} J(r_{iA},Z_A) {\bf e}_{x_i} + \deriv{}{y_i}{} J(r_{iA},Z_A) {\bf e}_{y_i} + \deriv{}{z_i}{} J(r_{iA},Z_A) {\bf e}_{z_i}, 
 \end{aligned}
\end{equation}
and 
\begin{equation}
 \deriv{}{x_i}{}J(r_{iA}) = \deriv{}{r_{iA}}{}J(r_{iA}) \deriv{r_{iA}}{x_i}{},
\end{equation}
and as $r_{iA} = \sqrt{(x_1 - x_A)^2 + (y_1 - y_A)^2 + (z_1 - z_A)^2} $ 
one has                                                              
\begin{equation}
 \deriv{r_{iA}}{x_1}{} = \frac{x_1 - x_A}{r_{iA}}
\end{equation}
and therefore according to Eq. \eqref{eq:one_e_1}, one has 
\begin{equation}
 \deriv{}{x_i}{} J(r_{iA},Z_A) = -\sum_A Z_A \big( x_i - x_A \big) \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}.
\end{equation}
\subsubsection{Computation of $\nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i)$}
The computation of $\nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i)$ leads to 
\begin{equation}
 \begin{aligned}
  \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) =  \sum_{A,B} Z_B &Z_A \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
                                                                      & +  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\ 
                                                                      & +  \big( z_i - z_A \big) \big( z_i - z_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}}.
 \end{aligned}
\end{equation}
The diagonal part of such integrals is simply
\begin{equation}
 \begin{aligned}
 &  \sum_{A} (Z_A)^2 \bigg(\big( x_i - x_A \big)^2 +  \big( y_i - y_A \big)^2 + \big( z_i - z_A \big)^2\bigg) \frac{\bigg(\text{erf}(\mu r_{iA}) - 1\bigg)^2}{\big(r_{iA}\big)^2}\\ 
  = & \sum_{A} (Z_A)^2 \bigg( \text{erf}(\mu r_{iA}) -1 \bigg)^2
 \end{aligned}
\end{equation}

\subsubsection{Computation of $\nabla^2_i J(\br{}_i) $}
We need to compute 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_{i}}{2} J(\br{}_i) & = -\sum_A Z_A \deriv{}{x_i}{} \bigg[(x_i - x_A) \frac{1 - \text{erf}(\mu r)}{r_{iA}} \bigg] \\
                               & = -\sum_A Z_A \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
 \end{aligned}
\end{equation}
But, one has that
\begin{equation}
 \begin{aligned}
 \deriv{}{x_i}{} \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
 \end{aligned}
\end{equation}
Therefore, 
\begin{equation}
 \label{eq:lapl_important}
 (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
\end{equation}.
Therefore, the Laplacian is 
\begin{equation}
 \begin{aligned}
 \label{eq:lapl_interm_1}
&  \deriv{}{x_{i}}{2} J(\br{}_i) + \deriv{}{y_{i}}{2} J(\br{}_i) + \deriv{}{z_{i}}{2} J(\br{}_i) =  - \sum_{A} Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \\
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
 \end{aligned}
\end{equation}
But according to Eq. \eqref{eq:lapl_important}, one has that 
\begin{equation}
 \begin{aligned}
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
 &- \frac{(x_i - x_A)^2 + (y_i - y_A)^2 + (z_i - z_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
 \end{aligned}
\end{equation}
which is simply 
\begin{equation}
 \begin{aligned}
 \label{eq:lapl_interm_2}
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
 &- \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
 \end{aligned}
\end{equation}
Then, coming back to Eq. \eqref{eq:lapl_interm_1} with Eq. \eqref{eq:lapl_interm_2} one has 
\begin{equation}
 \Delta_i J(\br{}_i) = - \sum_{A}  Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg) \bigg]
\end{equation}
which becomes 
\begin{equation}
 \Delta_i J(\br{}_i) = - \sum_{A}  2 \, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg]
\end{equation}
\subsubsection{Computation of the total operator}
\begin{equation}
 \begin{aligned}
& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],J\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg)    
                                                                   -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
                                                                   -\frac{1}{2}\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
 \end{aligned}
\end{equation}
which becomes
\begin{equation}
 \begin{aligned}
  \tilde{H} = H +&  \sum_i \sum_{A}\, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg] \\
           &+  \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \bigg[ (x_i - x_A) \deriv{}{x_i}{} + (y_i - y_A) \deriv{}{y_i}{} + (z_i - z_A) \deriv{}{z_i}{}\bigg] \\
           - \frac{1}{2}\sum_{B} Z_B &\bigg[ \big( x_1 - x_A \big) \big( x_1 - x_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\
           &+  \big( y_1 - y_A \big) \big( y_1 - y_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\ 
           &+  \big( z_1 - z_A \big) \big( z_1 - z_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB} } \bigg].
 \end{aligned}
\end{equation}
and as $H = \sum_i -\frac{1}{2} \Delta_i - \sum_A \frac{Z_A}{r_{iA}} + \sum_{i>j} \frac{1}{r_{ij}} $ the total interaction becomes 
\begin{equation}
 \label{eq:final_one_e_h}
 \tilde{H} =  \sum_i -\frac{1}{2} \Delta_i + \sum_A Z_A \tilde{v}_A({\bf r}_i)  + \sum_{i>j} \frac{1}{r_{ij}}
\end{equation}
where the new effective potential is 
\begin{equation}
 \label{eq:final_one_e_v}
 \begin{aligned}
  \tilde{v}_A({\bf r}_i) = & -\frac{\text{erf}(\mu r_{iA})}{r_{iA}} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} \\
           &+  \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \bigg[ (x_i - x_A) \deriv{}{x_i}{} + (y_i - y_A) \deriv{}{y_i}{} + (z_i - z_A) \deriv{}{z_i}{}\bigg] \\
           - \frac{1}{2}\sum_{B} Z_B\bigg[& \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\
           +&  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\ 
           +&  \big( z_i - z_A \big) \big( z_i - z_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}}\bigg].
 \end{aligned}
\end{equation}
\subsubsection{Verification with the Hydrogen atom}
Let us apply the general equations (see Eqs. \eqref{eq:final_one_e_h} and \eqref{eq:final_one_e_v}) to the case of the Hydrogen atom, which is supposed to be in the center of the frame of reference (\textit{i.e.} ${\bf r}_A = \vec{0}$)
\begin{equation}
 \begin{aligned}
  \tilde{v}({\bf r}) = & -\frac{\text{erf}(\mu r)}{r} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
           &+  \frac{1 - \text{erf}(\mu r)}{r} \bigg[ x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{}\bigg] \\
           &- \frac{1}{2}Z \big(x^2 + y^2 + z^2 \big)  \frac{\big(\text{erf}(\mu r) - 1\big)^2}{r^2},
 \end{aligned}
\end{equation}
but as $r^2 = x^2+y^2+z^2$ one obtains that 
\begin{equation}
 - \frac{1}{2}Z \big(x^2 + y^2 + z^2 \big)  \frac{\big(\text{erf}(\mu r) - 1\big)^2}{r^2} = - \frac{1}{2}Z\big(\text{erf}(\mu r) - 1\big)^2
\end{equation}
and also as 
\begin{equation}
 \begin{aligned}
 x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{} & = {\bf r} \cdot \nabla \\
                                                     & = r \deriv{}{r}{},
 \end{aligned}
\end{equation}
one obtains 
\begin{equation}
           +  \frac{1 - \text{erf}(\mu r)}{r} \bigg[ x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{}\bigg] = \bigg(1 - \text{erf}(\mu r)\bigg)\deriv{}{r}{},
\end{equation}
and therefore the total potential is 
\begin{equation}
 \begin{aligned}
  \tilde{v}({\bf r}) = & -\frac{\text{erf}(\mu r)}{r} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
           &+  \bigg(1 - \text{erf}(\mu r)\bigg)\deriv{}{r}{} \\
           &- \frac{1}{2}Z\big(\text{erf}(\mu r) - 1\big)^2,
 \end{aligned}
\end{equation}
which coincides with Eq. \eqref{eq:one_e_3}. 
\bibliography{srDFT_SC}
\end{document}

### 2020-09-21 dev/coll_salv_fun/coll_salv_fun.irp.f

@@ -38,8 +38,10 @@ end
 subroutine print_energy
  implicit none
  print*,'************************************************'
- print*,'************************************************'
+ print*,'psi_energy             = ',psi_energy
  print*,'psi_energy_two_e       = ',psi_energy_two_e
+ print*,''
+ print*,'************************************************'
 ! print*,'psi_wee_mu_of_r        = ',psi_wee_mu_of_r
  print*,'---------> '
 ! print*,'psi_wee_mu_of_r_sr     = ',psi_wee_mu_of_r_sr
@@ -47,16 +49,21 @@ subroutine print_energy
  print*,'coulomb_n2_jastrow     = ',coulomb_n2_jastrow
  print*,'Delta                  = ',coulomb_n2_jastrow  - psi_energy_two_e
  print*,'0.5 * Delta            = ',0.5d0*(coulomb_n2_jastrow  - psi_energy_two_e)
+ print*,'E_FCI + correction     = ',psi_energy + 0.5d0*(coulomb_n2_jastrow  - psi_energy_two_e)
  print*,''
  print*,'coulomb_n2_jastrow_reno= ',coulomb_n2_jastrow_renorm
  print*,'Delta                  = ',coulomb_n2_jastrow_renorm  - psi_energy_two_e
  print*,'0.5 * Delta            = ',0.5d0*(coulomb_n2_jastrow_renorm  - psi_energy_two_e)
+ print*,'E_FCI + correction     = ',psi_energy + 0.5d0*(coulomb_n2_jastrow_renorm  - psi_energy_two_e)
  print*,''
  print*,'norm_n2_jastrow        = ',norm_n2_jastrow
  print*,'coulomb_n2_jastrow/norm= ',coulomb_n2_jastrow/norm_n2_jastrow
  print*,'Delta                  = ',coulomb_n2_jastrow/norm_n2_jastrow  - psi_energy_two_e
  print*,'0.5 * Delta            = ',0.5d0*(coulomb_n2_jastrow/norm_n2_jastrow  - psi_energy_two_e)
+ print*,'E_FCI + correction     = ',psi_energy + 0.5d0*(coulomb_n2_jastrow/norm_n2_jastrow  - psi_energy_two_e)
  print*,''
+ print*,''
+ print*,'E_FCI + PBEoTSu        = ',psi_energy + ecmd_pbe_on_top_su_mu_of_r
[…]

### 2020-09-21 dev/coll_salv_fun/print_hole.irp.f

@@ -31,7 +31,7 @@ program print_hole
  io_ao_two_e_integrals = "None"
  touch io_ao_two_e_integrals
  !! integral of the effective potential 
- call routine_print
+! call routine_print
  call routine_print_2
 end
 !
@@ -171,18 +171,13 @@ subroutine routine_print_2
  print*,''
  print*,''
  print*,''
-! mu = mu_erf_dft 
- mu = mu_of_r
-! mu = -1.d0/(2.d0*dsqrt(pi)*dlog(g0_exact))
+ mu = mu_erf_dft 
  a0 = 2.d0 * dsqrt(pi) * mu
  g0_jastrow = full_jastrow_mu(mu,0.d0)
  psi0_j = dabs(psi0 * g0_jastrow)
- g0_new     = dexp(f_mu_new(mu,0.d0))
- psi0_j_new = dabs(psi0 * g0_new)
  g0_rsdft   = 1.d0/(1.d0+ 1.d0/a0)
  print*,'mu = ',mu
  print*,'g0 jastrow / Psi   = ',g0_jastrow, g0_jastrow*dabs(psi0)
- print*,'g0 new     / Psi   = ',g0_new    , g0_new    *dabs(psi0)
  print*,'g0 rsdft   / Psi   = ',g0_rsdft  , g0_rsdft  *dabs(psi0)
  print*,'g0 exact   / Psi   = ',g0_exact  , psi0_ex 
 
@@ -192,7 +187,6 @@ subroutine routine_print_2
   r2(2) = r * dsin(theta)
   call get_two_e_psi_at_r1r2(r1,r2,psi)
   r12 = dsqrt( (r1(1) - r2(1))**2.d0 +  (r1(2) - r2(2))**2.d0 + (r1(3) - r2(2))**2.d0 )
-  write(32,'(100(F16.10,X))')theta,r12, psi_ex_array(i),dabs(psi),dabs(psi)*full_jastrow_mu(mu,r12)
-  write(33,'(100(F16.10,X))')r12, dabs(psi)*full_jastrow_mu(mu,r12)/psi0_j,psi_ex_array(i)/psi0_ex,dabs(psi)*dexp(f_mu_new(mu,r12))/psi0_j_new
+  write(32,'(100(F16.10,X))')theta,r12, psi_ex_array(i),dabs(psi),dabs(psi)*full_jastrow_mu(mu,r12), dabs(psi)*full_jastrow_mu(mu,r12)/psi0_j,psi_ex_array(i)/psi0_ex
  enddo
 end

### 2020-09-21 dev/slat_rules_trans/slat_rules_trans.irp.f

@@ -70,7 +70,13 @@ subroutine single_htilde_mat(key_j,key_i,hmono,herf,heff,hderiv,htot)
   endif
   call bitstring_to_list_ab(key_i,occ,Ne,N_int)
   call get_single_excitation(key_i,key_j,exc,phase,N_int)
+!  print*,'in get single '
+!  print*,'key_i :: ket '
+!  call debug_det(key_i,N_int)
+!  print*,'key_j :: bra '
+!  call debug_det(key_j,N_int)
   call decode_exc(exc,1,h1,p1,h2,p2,s1,s2)
+!  print*,'h1,p1',h1,p1
 
   hmono = mo_one_e_integrals(h1,p1) * phase
   
@@ -142,7 +148,12 @@ subroutine htilde_mat(key_j,key_i,hmono,herf,heff,hderiv,htot)
   integer(bit_kind), intent(in)  :: key_j(N_int,2),key_i(N_int,2)
   double precision, intent(out)  :: hmono,herf,heff,hderiv,htot
   integer                        :: degree
-  call get_excitation_degree(key_i,key_j,degree,N_int)
+  call get_excitation_degree(key_j,key_i,degree,N_int)
+!  print*,'-----'
+!  print*,'key_i :: ket '
+!  call debug_det(key_i,N_int)
+!  print*,'key_j :: bra '
+!  call debug_det(key_j,N_int)
   hmono = 0.d0
   herf = 0.d0
   heff = 0.d0
@@ -156,4 +167,5 @@ subroutine htilde_mat(key_j,key_i,hmono,herf,heff,hderiv,htot)
   else if(degree == 0)then
    call diag_htilde_mat(key_i,hmono,herf,heff,hderiv,htot)
   endif
+!  print*,'-----'
 end

### 2020-09-21 dev/slat_rules_trans/test_slat.irp.f

@@ -4,11 +4,13 @@ program pouet
  touch read_wf
 ! call routine
 ! call test_pert
- call test_eigv
+! call test_eigv
  integer :: ith
  ith = 1
 ! call test_left_right_eigenvalues(ith)
 ! call test_overlap_matrix
+! provide htilde_matrix_elmt
+  provide mo_two_e_eff_dr12_pot_array
 end
 
 subroutine routine
@@ -73,55 +75,174 @@ subroutine test_pert
  implicit none
  integer :: i,j
  double precision :: accu,hmono,herf,heff,hderiv,htot
- double precision :: accu_mono,accu_double
+ double precision :: accu_mono,accu_double,accu2
  double precision :: pert_mono,pert_double
- double precision :: h00,hii,htotbis,phase
+ double precision :: h00,hii,htotbis,phase,h0i,hi0
  integer          :: degree,exc(0:2,2,2)
  integer          :: h1, p1, h2, p2, s1, s2
+ double precision :: norm_t1,norm_t2
+ provide reigvec_trans
  accu = 0.d0
+ accu2= 0.d0
  accu_mono = 0.d0
  accu_double = 0.d0
  pert_mono = 0.d0
  pert_double = 0.d0
+ norm_t1 = 0.d0
+ norm_t2 = 0.d0
  call htilde_mat(psi_det(1,1,1),psi_det(1,1,1),hmono,herf,heff,hderiv,h00)
- do i = 1, N_det
-  ! <i|H|0>
-  call htilde_mat(psi_det(1,1,i),psi_det(1,1,1),hmono,herf,heff,hderiv,htot)
+! print*,'Printing the connection '
+! do i = 1, N_det
+!  ! <0|H|i>
+!  print*,'******************'
+!  print*,'i = ',i
+!  call htilde_mat(psi_det(1,1,1),psi_det(1,1,i),hmono,herf,heff,hderiv,h0i)
+!
+!  ! <i|H|i>
+!  call htilde_mat(psi_det(1,1,i),psi_det(1,1,i),hmono,herf,heff,hderiv,hii)
+!
+!  ! <i|H|0>
+!  call htilde_mat(psi_det(1,1,i),psi_det(1,1,1),hmono,herf,heff,hderiv,hi0)
+!
[…]

### 2020-09-30 cusp_j/paper/paper.tex
working on eigenvectors

@@
 \newcommand{\phimu}[0]{\Phi^{\text{ex},\mu}_0}
+\newcommand{\phimub}[0]{\Phi^{\mathcal{B},\mu}_0}
+\newcommand{\psimub}[0]{\Psi^{\mathcal{B},\mu}_0}
+\newcommand{\phiimub}[0]{\Phi^{\mathcal{B},\mu}_i}
+\newcommand{\basis}[0]{\mathcal{B}}
 \newcommand{\energyex}[0]{E^{\text{ex}}}
@@
 \newcommand{\identity}{\mathds{1}}
+\newcommand{\mur}[1]{\mu({\bf r_{#1}})}
 
@@
  \label{fig_j_mu}
-        \includegraphics[width=0.60\linewidth]{small_mu_j.pdf}\\
-        \includegraphics[width=0.60\linewidth]{small_mu_exp_j.pdf}\\
+        \includegraphics[width=0.45\linewidth]{small_mu_j.pdf}
+        \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
         \caption{Shape of $j(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(j(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
@@
 
-\subsubsection{The explicit form of  $\tilde{H}[\mu]$ and some of its properties}
+\subsection{Explicit form of  $\tilde{H}[\mu]$ and some of its properties}
+\subsubsection{Explicit form of $\tilde{H}[\mu]$ }
 Having established the explicit form of $j(r_{12};\mu)$ and some of its properties, one can now 
@@
  \label{fig_wee_mu}
-        \includegraphics[width=0.60\linewidth]{w_ee.pdf}\\
-        \includegraphics[width=0.60\linewidth]{w_ee_bis.pdf}\\
+        \includegraphics[width=0.45\linewidth]{w_ee.pdf}
+        \includegraphics[width=0.45\linewidth]{w_ee_bis.pdf}\\
         \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (up) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (bottom) for different values of $\mu$.}
@@
 from the long-range interaction at small $r_{12}$, 
-%\begin{equation}
-% \label{eq:lim_mu_2}
-% \lim_{r_{12} \rightarrow 0} \tilde{\mathcal{W}}_{ee}(r_{12}) = \frac{3 \mu}{\sqrt{\pi}} - \frac{1}{4}. 
-%\end{equation}
-%
 and it is not monotonic as it can be even slightly attractive for small values of $\mu$. 
@@
 whose solution is unknown to the best of the author knowledge. 
-%To illustrate the shape of 
-%which does not diverge at $r_{12} = 0$
-%\end{equation}
-
+\subsubsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
+\label{sec:h_mu_lim}
 Coming now to the limits of $\tilde{H}[\mu]$ when $\mu \rightarrow \infty$, one expects that as
@@
 and therefore Eq.\eqref{eq:lim_mu_6} which implies Eq.\eqref{eq:lim_mu_1}.
+
+In the $\mu \rightarrow 0$ limit, the transcorrelated Hamiltonian $\tilde{H}[\mu]$ becomes simply 
+\begin{equation}
+ \lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \partial{}{r_{12}}{}, 
+\end{equation}
+which means that all scalar electron-electron interaction have been replaced by a differential operator.
+
+At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent but can be either repulsive or attractive at small $r_{12}$.
+One can therefore notice the diversity of physical content of $\tilde{H}[\mu]$ as a function of a unique parameter, $\mu$.
+Nevertheless, due to the property of the similarity transformation, in the limit of a complete basis set, the eigenvalues of $\tilde{H}[\mu]$, whatever the value of $\mu$ chosen, coincide with that of the physical Hamiltonian.
+An important point then is the convergence with respect to the basis set of the family of $\tilde{H}[\mu]$ for different values of $\mu$.
+
+\subsubsection{The eigenvectors of $\tilde{H}[\mu]$}
+As shown in the previous section, the form of $\tilde{H}[\mu]$ depends on $\mu$, going from the usual repulsive hermitian Hamiltonian to a non hermitian operator which can have
+
+\section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
+The first part of our study concerns the convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence. 
+Therefore, considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected in a given basis set by
+\begin{equation}
+ \tilde{H}[\mu]^{\basis} = P_\basis \tilde{H}[\mu] P_\basis,
+\end{equation}
+and its right eigenvectors and eigenvalues satisfy of course
+\begin{equation}
+ \tilde{H}[\mu]^{\basis} \ket{\phimub} = E_i^{\basis}[\mu] \ket{\phimub}. 
+\end{equation}
+
+As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  
+its projection into a basis set $\tilde{H}[\mu]^{\basis}$ will behave differently as a function of $\mu$ 
+and so will $\ket{\phimub}$ and $E_i^{\basis}[\mu]$. 
+Therefore, we would like to study the mathematical behaviour of $\ket{\phimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $j(r_{12},\mu)$ can improve the convergence toward the exact ground state energy and eigenfunction.
+\subsection{$\mu$ dependence of the convergence of the total energy with respect to the basis set }
+\subsubsection{Computational details}
+We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual orbital basis set (see annexes for more details) in the case of an atomic two electron systems, together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+All implementation was done as a plugin of the program quantum package\cite{QP2}. 
+Once the matrix elements of $\tilde{H}[\mu]$ are built on a given MO basis, we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} it is expressed as a linear combination of all possible Slater determinants within a given Hilbert space defined with a MO basis) and use an non hermitian eigensolver to obtain both right and left eigenvectors.
+If not explicitly mentioned, the canonical RHF MOs are used in this work.
+The study was performed using the augmented Dunning basis aug-cc-pVXZ (X=D,T,Q,5), hereafter referred as AVXZ.
+
+\subsubsection{Numerical results: ground state energies}
+\label{sec:total_e}
+We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_0^\mu$ of $\tilde{H}[\mu]$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
+Several observations can be done from these data.
+First, because of the loose of the variational principle, $E_0^{\mu}$ can take values below the exact non relativistic energy, and the smaller the $\mu$, the more pronounced is such effect.
+Nevertheless, one can also observe that, for each $\mu$, the error with respect to the reference energy gets smaller  
+when enlarging the basis set.
+Also, qualitatively, one can observe that there are two regimes of $\mu$: that ranging from $\mu=0.05$ and $\mu=0.3$ where the $E_0^\mu$ is always below $E_0$ and those larger than $\mu=0.35$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
+Second, as $\mu$ increases, the difference between $E_0^\mu$ and $E_0^\text{FCI}$ in a given basis set diminishes, 
+which is expected as in the limit $\mu \rightarrow \infty$, one obtains that  $\tilde{H}[\mu] \rightarrow H$. 
+Coming now to the speed of convergence of $E_0^\mu$ with respect to the basis set, it is always faster than that of $E_0^\text{FCI}$ as long as $\mu \ge 0.2$. 
+To quantify better such observations, one can look at the basis set from which the error with respect to the exact non relativistic energy is smaller, in absolute value, than 1mH. 
+For $0.3\ge\mu\ge0.4$ one can see that the error with respect to $E_0$ is never larger, in absolute value, than 1mH whatever the basis set used.
+For $0.5\ge \mu \ge 1.0$ such accuracy is reached at the aug-cc-pVTZ level.
+For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
+Therefore one can conclude that the use of the Jastrow factor $j(r_{12};\mu)$ in the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom, specially for $\mu \in [0.4, 1.0]$ where an error below 1mH is reached within the aug-cc-pVTZ basis set, whereas such an error is reached at the aug-cc-pV5Z basis set.
+\begin{figure*}
+ \label{fig_conv_e_mu}
+        \includegraphics[width=0.45\linewidth]{E_conv_basis_small_mu.pdf}
+        \includegraphics[width=0.45\linewidth]{E_conv_basis_large_mu.pdf}\\
+        \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$.}
+\end{figure*}
+
+\begin{table*}
+\label{table_conv_e_mu}
+\caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.}
+\begin{ruledtabular}
+\begin{tabular}{llllllllllll}
+ Basis/$\mu$&0.05                 & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                   \\
+\hline
+ AVDZ       &  -2.909031 (-5.31)  &    -2.906309 (-2.58)  &    -2.904172 (-0.45)  &    -2.903317 (0.41)   &    -2.901420 (2.3)   &    -2.899516 (4.21)   \\
+ AVTZ       &  -2.905898 (-2.17)  &    -2.905278 (-1.55)  &    -2.904691 (-0.97)  &    -2.904468 (-0.74)  &    -2.903969 (-0.24) &    -2.903488 (0.24)   \\
+ AVQZ       &  -2.904621 (-0.9)   &    -2.904325 (-0.6)   &    -2.903986 (-0.26)  &    -2.903879 (-0.15)  &    -2.903702 (0.02)  &    -2.903620 (0.1)     \\
+ AV5Z       &  -2.904428 (-0.7)   &    -2.904229 (-0.51)  &    -2.903928 (-0.2)   &    -2.903834 (-0.11)  &    -2.903702 (0.02)  &    -2.903676 (0.05)   \\
+\hline
+ Basis/$\mu$ & 1.0                  & 1.6                  & 2.0                  & 3.0                  & $\infty$ (FCI)        & Exact NR              \\
+\hline
+ AVDZ        &    -2.896734 (6.99)  &    -2.892773 (10.95) &    -2.891477 (12.25) &    -2.890212 (13.51) &    -2.889548 (14.18)  & -2.903724             \\
+ AVTZ        &    -2.903069 (0.66)  &    -2.902421 (1.3)   &    -2.901932 (1.79)  &    -2.901159 (2.56)  &    -2.900598 (3.13)   &                       \\
+ AVQZ        &    -2.903558 (0.17)  &    -2.903359 (0.36)  &    -2.903244 (0.48)  &    -2.902951 (0.77)  &    -2.902534 (1.19)   &                       \\
+ AV5Z        &    -2.903675 (0.05)  &    -2.903634 (0.09)  &    -2.903592 (0.13)  &    -2.903479 (0.24)  &    -2.903201 (0.52)   &                       \\
+\end{tabular}
+\end{ruledtabular}
+\end{table*}
+
+\subsubsection{Numerical results: ground state eigenvectors}
+In Sec.\ref{sec:total_e} we shown the strong improvement of the speed of convergence of the total energy for the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
+Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
+Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = H$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
+If one focusses now on the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$, it is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $j(r_{12},\mu)$ through
+\begin{equation}
+ \psiex(\br{}_1,\br{}_2) = e^{j(r_{12},\mu)} \phimu(\br{}_1,\br{}_2). 
+\end{equation}
+Therefore, having obtained in a given basis set $\basis$ the right eigenvector $\phimub$, one can estimate the exact ground state eigenvector by 
+\begin{equation}
+ \psimub(\br{}_1,\br{}_2) = \frac{1}{\sqrt{\mathcal{N}_{\basis}^{\mu}}}e^{j(r_{12},\mu)}\phimub(\br{}_1,\br{}_2)
+\end{equation}
+where the normalization factor $\mathcal{N}_{\basis}^{\mu}$ is imply
+\begin{equation}
+  \mathcal{N}_{\basis}^{\mu} = \matelem{\phimub}{e^{2 j(r_{12},\mu)}}{\phimub}.
+\end{equation}
 
@@
  \label{eq:dx2_u}
- \deriv{}{x_2}{}u(r_{12}) = \frac{\text{erf}(\mu r_{12})}{2 r_{12} -1 } \bigg(x_1 - x_2 \bigg).
+ \deriv{}{x_2}{}u(r_{12}) = -\frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12} } \bigg(x_1 - x_2 \bigg).
 \end{equation}
@@
 \bibliography{srDFT_SC}
+
+\section{Derivation with a varying $\mu({\bf r})$}
+Let us assume one has a range separation parameter varying in space $\mur{}$ and that one knows its gradients and Laplacian. 
+Therefore, one would like to derive the same equations as for the constant $\mu$. 
+The Jastrow factor is therefore expressed as
+\begin{equation}
+ \tilde{j}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( j(r_{12};\mur{1}) + j(r_{12};\mur{2}) \bigg)
+\end{equation}
+where $j(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
+To derive properly the equations for such a new Jastrow factor, one needs to derive the different terms involving gradients and so on. 
+\subsection{Gradients of $\tilde{j}(\bd{r_1},\bd{r_2})$}
+A fundamental quantity is the gradient of $\tilde{j}(\bd{r_1},\bd{r_2})$ which is 
+\begin{equation}
+ \nabla_1 \tilde{j}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
+\end{equation}
+Therefore one needs to compute $\deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2})$
+\begin{equation}
+ \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} j(r_{12};\mur{1}) 
+                                               +\frac{1}{2}\deriv{}{x_1}{} j(r_{12};\mur{2}) .
+\end{equation}
+Applying the chain rule 
+\begin{equation}
+ \deriv{}{x_1}{} j(r_{12};\mur{2}) = \deriv{}{r_{12}}{} j(r_{12};\mur{2})\deriv{r_{12}}{x_1}{} + \deriv{}{\mur{2}}{}j(r_{12};\mur{2}) \deriv{\mur{2}}{x_1}{},
+\end{equation}
+and as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
+of the condition determining $j(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
+\begin{equation}
+ \deriv{}{x_1}{} j(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
+\end{equation}
+Then, 
+\begin{equation}
+ \deriv{}{x_1}{} j(r_{12};\mur{1}) = \deriv{}{r_{12}}{} j(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} + \deriv{}{\mur{1}}{}j(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
+\end{equation}
+and as 
+\begin{equation}
+ \label{eq:d_dmu_j}
+ \deriv{}{\mu}{}j(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2\sqrt{\pi} \mu^2},
+\end{equation}
+one obtains 
+\begin{equation}
+ \deriv{}{x_1}{} j(r_{12};\mur{1}) = \frac{1 - \text{erf}(\mur{1} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg) + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{}.
+\end{equation}
+Therefore, one obtains finally that 
+\begin{equation}
+ \label{eq:d_dx1_jtilde}
+ \begin{aligned}
+ \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
+ \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
+                 & + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{},
+ \end{aligned}
+\end{equation}
+and similarly,
+\begin{equation}
+ \label{eq:d_dx2_jtilde}
+ \begin{aligned}
+ \deriv{}{x_2}{} \tilde{j}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
+ \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
+                 & + \frac{e^{-(\mur{2} r_{12})^2}}{2\sqrt{\pi} \mur{2}^2} \deriv{\mur{2}}{x_2}{},
+ \end{aligned}
+\end{equation}
+
+\subsection{Computation of $\bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2$}
+Then one needs to compute 
+\begin{equation}
+ \begin{aligned}
+& \bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
+& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
+& \bigg(\deriv{}{y_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{y_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
+& \bigg(\deriv{}{z_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{z_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2.
+ \end{aligned}
+\end{equation}
+According to Eq.\eqref{eq:d_dx1_jtilde}, 
+and defining the complementary error function as 
+\begin{equation}
+ \text{erfc}(x) = 1 - \text{erf}(x)
+\end{equation}
+one has that 
+\begin{equation}
+ \begin{aligned}
+& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+ = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{1} r_{12}\big) \bigg)^2  \\
+ + & \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 \\
+ + & \frac{\big(x_1 - x_2\big)}{r_{12}} \frac{e^{-\big(\mur{1} r_{12}\big)^2}}{2\sqrt{\pi} \big(\mur{1}\big)^2} \deriv{}{x_1}{}\mur{1} 
+ \frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{2}.
+ \end{aligned}
+\end{equation}
+Similarly 
+\begin{equation}
+ \begin{aligned}
+& \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+ = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
+ + & \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2 \\
+ + & \frac{\big(x_2 - x_1\big)}{r_{12}} \frac{e^{-\big(\mur{2} r_{12}\big)^2}}{2\sqrt{\pi} \big(\mur{2}\big)^2} \deriv{}{x_2}{}\mur{2} 
+ \frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{2}.
+ \end{aligned}
+\end{equation}
+Therefore, 
+\begin{equation}
+ \begin{aligned}
+& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+ = & \frac{1}{2}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
+ + & \frac{\big(x_1 - x_2\big)}{2 \sqrt{\pi}r_{12}}  \frac{\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)}{2} \\
+&\bigg(   \frac{e^{-\big(\mur{1} r_{12}\big)^2}}{\big(\mur{1}\big)^2} \deriv{}{x_1}{}\mur{1} 
+- \frac{e^{-\big(\mur{2} r_{12}\big)^2}}{\big(\mur{2}\big)^2} \deriv{}{x_2}{}\mur{2} \bigg) \\
+ + & \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
+ + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
+ \end{aligned}
+\end{equation}
+
+Summing all terms and noticing that $\bigg(x_1 - x_2\bigg)^2 + \bigg(y_1 - y_2\bigg)^2 + \bigg(z_1 - z_2\bigg)^2 = \bigg(r_{12}\bigg)^2$ leads to 
+\begin{equation}
+ \begin{aligned}
+& \bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
+& \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{1} r_{12}\big) \bigg)^2 
+ \end{aligned}
+\end{equation}
+
 \end{document}

### 2020-09-30 cusp_j/paper/paper.tex
pouet

@@
 \newcommand{\phimub}[0]{\Phi^{\mathcal{B},\mu}_0}
+\newcommand{\xhimub}[0]{X^{\mathcal{B},\mu}_0}
 \newcommand{\psimub}[0]{\Psi^{\mathcal{B},\mu}_0}
@@
 
-\subsubsection{The eigenvectors of $\tilde{H}[\mu]$}
-As shown in the previous section, the form of $\tilde{H}[\mu]$ depends on $\mu$, going from the usual repulsive hermitian Hamiltonian to a non hermitian operator which can have
-
 \section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
-The first part of our study concerns the convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence. 
-Therefore, considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected in a given basis set by
+In the present paper, we study the behaviour of $\tilde{H}[\mu]$ in the case of the isoelectronic series of the helium atom, and in that section we focus on the helium atom itself. 
+The first part of our study concerns the convergence of the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
+
+Considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected on $\basis$ by
 \begin{equation}
@@
 \end{equation}
-and its right eigenvectors and eigenvalues satisfy of course
+and its eigenvalues $E_i^{\basis}[\mu]$ and left/right eigenvectors satisfy of course
 \begin{equation}
@@
 \end{equation}
-
-As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+\begin{equation}
+ \bigg(\tilde{H}[\mu]^{\basis}\bigg)^\dagger \ket{\xhimub} = E_i^{\basis}[\mu] \ket{\xhimub}. 
+\end{equation}
+
+As pointed in section \ref{sec:h_mu_lim}, even though $\tilde{H}[\mu]$ is still non hermitian as long as $\mu < \infty$, by varying $\mu$ one can change the nature of the electron-electron interaction in $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ from a repulsive and non divergent interaction at large $\mu$ (an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
 Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  

### 2020-10-01 cusp_j/paper/paper.tex
psi exact works

--- 2020-09-30 cusp_j/paper/paper.tex
@@
 \section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
-The first part of our study concerns the convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence. 
+The first part of our study concerns the convergence of the eigenvalues of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence. 
 Therefore, considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected in a given basis set by
@@
 \end{equation}
-and its right eigenvectors and eigenvalues satisfy of course
+whose right eigenvectors and eigenvalues satisfy 
 \begin{equation}
@@
 
-As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian at large $\mu$ (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
 Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  
 its projection into a basis set $\tilde{H}[\mu]^{\basis}$ will behave differently as a function of $\mu$ 
-and so will $\ket{\phimub}$ and $E_i^{\basis}[\mu]$. 
-Therefore, we would like to study the mathematical behaviour of $\ket{\phimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $j(r_{12},\mu)$ can improve the convergence toward the exact ground state energy and eigenfunction.
-\subsection{$\mu$ dependence of the convergence of the total energy with respect to the basis set }
+and so will the right eigenvectors $\ket{\phiimub}$ and the corresponding eigenvalues $E_i^{\basis}[\mu]$. 
+Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $j(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
+\subsection{$\mu$ dependence of the convergence of the ground state eigenvalue with respect to the basis set }
 \subsubsection{Computational details}
-We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual orbital basis set (see annexes for more details) in the case of an atomic two electron systems, together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual gaussian orbital basis set (see annexes for more details) in the case of an atomic two electron systems, together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
-Once the matrix elements of $\tilde{H}[\mu]$ are built on a given MO basis, we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} it is expressed as a linear combination of all possible Slater determinants within a given Hilbert space defined with a MO basis) and use an non hermitian eigensolver to obtain both right and left eigenvectors.
+Once the matrix elements of $\tilde{H}[\mu]$ are built on a given MO basis, we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} $\Phi_\mu$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
 If not explicitly mentioned, the canonical RHF MOs are used in this work.
@@
 when enlarging the basis set.
-Also, qualitatively, one can observe that there are two regimes of $\mu$: that ranging from $\mu=0.05$ and $\mu=0.3$ where the $E_0^\mu$ is always below $E_0$ and those larger than $\mu=0.35$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
-Second, as $\mu$ increases, the difference between $E_0^\mu$ and $E_0^\text{FCI}$ in a given basis set diminishes, 
-which is expected as in the limit $\mu \rightarrow \infty$, one obtains that  $\tilde{H}[\mu] \rightarrow H$. 
+Also, qualitatively, one can observe that there are two regimes of $\mu$: $\mu \in[0.05,0.7]$ where the $E_0^\mu$ is always below $E_0$ and $\mu\ge 0.7$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
+As $\mu$ increases, the difference between $E_0^\mu$ and $E_0^\text{FCI}$ in a given basis set diminishes, 
+which is expected as in the $\mu \rightarrow \infty$ limit, one obtains that  $\tilde{H}[\mu] \rightarrow H$.
+
 Coming now to the speed of convergence of $E_0^\mu$ with respect to the basis set, it is always faster than that of $E_0^\text{FCI}$ as long as $\mu \ge 0.2$. 
-To quantify better such observations, one can look at the basis set from which the error with respect to the exact non relativistic energy is smaller, in absolute value, than 1mH. 
-For $0.3\ge\mu\ge0.4$ one can see that the error with respect to $E_0$ is never larger, in absolute value, than 1mH whatever the basis set used.
-For $0.5\ge \mu \ge 1.0$ such accuracy is reached at the aug-cc-pVTZ level.
+To quantify better such observations, one can identify the basis set from which the error with respect to the exact non relativistic energy is smaller, in absolute value, than 1mH. 
+For $0.3\ge\mu\ge0.4$ one can see that the error with respect to $E_0$ is never larger, in absolute value, than 1mH whatever the basis set used, which represents a strong improvement with respect to the FCI.
+For $0.5\ge \mu \ge 1.0$ such the 1mH error threshold is reached at the aug-cc-pVTZ level and the accuracy are comparable to the FCI in the aug-cc-pV5Z basis set.
 For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
-Therefore one can conclude that the use of the Jastrow factor $j(r_{12};\mu)$ in the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom, specially for $\mu \in [0.4, 1.0]$ where an error below 1mH is reached within the aug-cc-pVTZ basis set, whereas such an error is reached at the aug-cc-pV5Z basis set.
+Therefore one can conclude that the use of the Jastrow factor $j(r_{12};\mu)$ in the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$.
 \begin{figure*}
@@
 
-\subsubsection{Numerical results: ground state eigenvectors}
+\subsection{Study of the ground state eigenvector}
 In Sec.\ref{sec:total_e} we shown the strong improvement of the speed of convergence of the total energy for the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
@@
 \begin{equation}
- \psiex(\br{}_1,\br{}_2) = e^{j(r_{12},\mu)} \phimu(\br{}_1,\br{}_2). 
-\end{equation}
-Therefore, having obtained in a given basis set $\basis$ the right eigenvector $\phimub$, one can estimate the exact ground state eigenvector by 
+ \psiex(\br{}_1,\br{}_2) =  \frac{1}{\sqrt{\mathcal{N}^{\mu}}} e^{j(r_{12},\mu)} \phimu(\br{}_1,\br{}_2), 
+\end{equation}
+where the normalization factor $\mathcal{N}^{\mu}$ is simply 
+\begin{equation}
+  \mathcal{N}^{\mu} = \matelem{\phimu}{e^{2 j(r_{12},\mu)}}{\phimu}.
+\end{equation}
+Therefore, having obtained in a given basis set $\basis$ the right eigenvector $\phimub$, one can estimate the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$ by 
 \begin{equation}
@@
 \end{equation}
-where the normalization factor $\mathcal{N}_{\basis}^{\mu}$ is imply
+where the normalization factor $\mathcal{N}_{\basis}^{\mu}$ is simply
 \begin{equation}

### 2020-10-01 dev/deriv_r12_ints/big_array_ao.irp.f

@@ -8,6 +8,9 @@ BEGIN_PROVIDER [double precision, ao_two_e_eff_dr12_pot_array, (ao_num,ao_num,ao
  double precision :: mu_in,d_dr12(3),d_dr12_large(3),accu
  double precision, allocatable :: ao_ints(:)
  mu_in = mu_erf
+ double precision :: wall0,wall1
+ call wall_time(wall0)
+ print*,'Providing ao_two_e_eff_dr12_pot_array ...'
  PROVIDE ao_two_e_integrals_in_map ao_integrals_map
  !$OMP PARALLEL & 
  !$OMP DEFAULT(NONE) &
@@ -41,6 +44,8 @@ BEGIN_PROVIDER [double precision, ao_two_e_eff_dr12_pot_array, (ao_num,ao_num,ao
  enddo
  !$OMP END DO
  !$OMP END PARALLEL
+ call wall_time(wall1)
+ print*,'ao_two_e_eff_dr12_pot_array provided in ',wall1 - wall0
 END_PROVIDER 
 
 BEGIN_PROVIDER [double precision, ao_two_e_eff_dr12_pot_array_no_cycle, (ao_num,ao_num,ao_num,ao_num)]
@@ -87,6 +92,10 @@ BEGIN_PROVIDER [double precision, mo_two_e_eff_dr12_pot_array_old, (mo_num,mo_nu
  END_DOC
  integer :: i,j,k,l,m,n,p,q
  double precision, allocatable :: mo_tmp_1(:,:,:,:),mo_tmp_2(:,:,:,:),mo_tmp_3(:,:,:,:)
+ double precision :: wall0,wall1
+ provide ao_two_e_eff_dr12_pot_array
+ call wall_time(wall0)
+ print*,'Providing mo_two_e_eff_dr12_pot_array ...'
  mo_two_e_eff_dr12_pot_array_old = 0.d0
  allocate(mo_tmp_1(ao_num,ao_num,ao_num,mo_num))
  mo_tmp_1 = 0.d0
@@ -150,6 +159,8 @@ BEGIN_PROVIDER [double precision, mo_two_e_eff_dr12_pot_array_old, (mo_num,mo_nu
   enddo
  enddo
  deallocate(mo_tmp_3)
+ call wall_time(wall1)
+ print*,'mo_two_e_eff_dr12_pot_array provided in ',wall1 - wall0
 
 END_PROVIDER 
 

### 2020-10-01 dev/slat_rules_trans/htilde_matrix.irp.f

@@ -47,17 +47,24 @@ END_PROVIDER
  if(read_rl_eigv)then
   reigvec_trans = 0.d0 
   leigvec_trans = 0.d0 
-  double precision, allocatable :: reigvec_trans_tmp(:,:),leigvec_trans(:,:)
+  double precision, allocatable :: reigvec_trans_tmp(:,:),leigvec_trans_tmp(:,:)
   allocate(reigvec_trans_tmp(N_det,N_states),leigvec_trans_tmp(N_det,N_states))
+  print*,'Reading the right/left eigenvectors in the EZFIO....'
    call ezfio_get_slat_rules_trans_reigvec_trans(reigvec_trans_tmp)
    call ezfio_get_slat_rules_trans_leigvec_trans(leigvec_trans_tmp)
+   reigvec_trans_norm = 0.d0
+   leigvec_trans_norm = 0.d0
    do i = 1, N_states
     do j = 1, N_det
      reigvec_trans(j,i) = reigvec_trans_tmp(j,i)
      leigvec_trans(j,i) = leigvec_trans_tmp(j,i)
+     reigvec_trans_norm(i) += reigvec_trans_tmp(j,i) * reigvec_trans_tmp(j,i)
+     leigvec_trans_norm(i) += leigvec_trans_tmp(j,i) * leigvec_trans_tmp(j,i)
+!     print*,j,reigvec_trans(j,i),leigvec_trans(j,i)
     enddo
    enddo
  else
+  print*,'Computing the left/right eigenvectors ...'
   character*1 :: JOBVL,JOBVR
   JOBVL = "V" ! computes the left  eigenvectors 
   JOBVR = "V" ! computes the right eigenvectors 

### 2020-10-01 dev/slat_rules_trans/norm_full_psi.irp.f

@@ -29,6 +29,7 @@
      enddo
     enddo
    enddo
+!   print*,norm_n2_jastrow_cst_mu_on_grid(ipoint,istate)
    norm_n2_jastrow_cst_mu(istate) += norm_n2_jastrow_cst_mu_on_grid(ipoint,istate) * weight
   enddo
  enddo

### 2020-10-01 dev/slat_rules_trans/psi_exact.irp.f

@@ -5,7 +5,7 @@ END_PROVIDER
 
 BEGIN_PROVIDER [integer, nr1_psi_ex]
  implicit none
- nr1_psi_ex = 5
+ nr1_psi_ex = 7
 END_PROVIDER 
 
 BEGIN_PROVIDER [double precision, r1_psi_ex, (3,nr1_psi_ex)]
@@ -16,6 +16,8 @@ BEGIN_PROVIDER [double precision, r1_psi_ex, (3,nr1_psi_ex)]
  r1_psi_ex(1,3) = 0.50d0
  r1_psi_ex(1,4) = 0.75d0
  r1_psi_ex(1,5) = 1.00d0
+ r1_psi_ex(1,6) = 1.50d0
+ r1_psi_ex(1,7) = 2.00d0
 END_PROVIDER 
 
 
@@ -30,6 +32,7 @@ END_PROVIDER
   do i = 1, ntheta_psi_ex
    r2_psi_ex(3,i,j) = r1_psi_ex(3,j)
    theta = theta_array_psi_ex(i,j)
+   r = r1_psi_ex(1,j) 
    r2_psi_ex(1,i,j) = r * dcos(theta)
    r2_psi_ex(2,i,j) = r * dsin(theta)
    r12_psi_ex(i,j) = dsqrt( (r1_psi_ex(1,j) - r2_psi_ex(1,i,j))**2.d0 +  (r1_psi_ex(2,j) - r2_psi_ex(2,i,j))**2.d0 + (r1_psi_ex(3,j) - r2_psi_ex(3,i,j))**2.d0 )
@@ -42,12 +45,7 @@ END_PROVIDER
 BEGIN_PROVIDER [double precision, psi_fci_array, (ntheta_psi_ex,nr1_psi_ex)]
  implicit none
  integer :: i , j
- do i = 1, N_states
-  do j = 1, N_det
-   psi_coef(j,i) =  CI_eigenvectors(j,i)
-  enddo
- enddo
- touch psi_coef
+ call diagonalize_CI
  double precision :: psi
  do j = 1, nr1_psi_ex
   do i = 1, ntheta_psi_ex
@@ -93,8 +91,9 @@ BEGIN_TEMPLATE
  print*,'output = ',trim(output)
  i_unit_output = getUnitAndOpen(output,'w')
  do i = 1, ntheta_psi_ex
[…]

### 2020-10-01 cusp_j/paper/paper.tex

@@
 
-\subsubsection{The eigenvectors of $\tilde{H}[\mu]$}
-As shown in the previous section, the form of $\tilde{H}[\mu]$ depends on $\mu$, going from the usual repulsive hermitian Hamiltonian to a non hermitian operator which can have
-
 \section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
@@
 whose right eigenvectors and eigenvalues satisfy 
-\begin{equation}
- \tilde{H}[\mu]^{\basis} \ket{\phimub} = E_i^{\basis}[\mu] \ket{\phimub}. 
+In the present paper, we study the behaviour of $\tilde{H}[\mu]$ in the case of the isoelectronic series of the helium atom, and in that section we focus on the helium atom itself. 
+The first part of our study concerns the convergence of the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
+
+Considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected on $\basis$ by
+\begin{equation}
+ \tilde{H}[\mu]^{\basis} = P_\basis \tilde{H}[\mu] P_\basis,
+\end{equation}
+and its eigenvalues $E_i^{\basis}[\mu]$ and right eigenvectors $\phiimub$ satisfy 
+\begin{equation}
+ \tilde{H}[\mu]^{\basis} \ket{\phimub} = E_i^{\basis}[\mu] \ket{\phiimub}. 
 \end{equation}
@@
 As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian at large $\mu$ (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+As pointed in section \ref{sec:h_mu_lim}, even though $\tilde{H}[\mu]$ is still non hermitian as long as $\mu < \infty$, by varying $\mu$ one can change the nature of the electron-electron interaction in $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ from a repulsive and non divergent interaction at large $\mu$ (an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
 Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  

### 2020-10-02 cusp_j/paper/paper.tex
pouet

@@
 
+Knowing that, one can directly compare $\psimub(\br{}_1,\br{}_2) $ in real space to the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$, which is approximated in the case of the helium atom by the wave function developed by Umrigar \textit{et.
+al.}\cite{UmrGon-PRA-94} which contains explicitly the $r_{12}$ coordinate and which provides a total energy accurate up to twelve digits.
+Therefore, we plotted cuttings of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
+The cuttings used are the following: we set two electrons on a circle of radius $r$ from the nucleus, and use increasing values of $r$.
+We report in Figs \ref{fig:mu_0.3_dz_3} and \ref{fig:mu_1.0_dz_3} the plot of the right eigenvector $\phimub(\br{}_1,\br{}_2)$, estimated exact wave function $\psimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ and $\mu=1.0$ (respectively) and compared to the exact wave function $\psiex(\br{}_1,\br{}_2)$ and FCI wave function for $r=0.5\,a.u.$.
+From these figure, one can notice that: i) the right eigenvector $\phimub(\br{}_1,\br{}_2)$ converges faster than the FCI wave function with respect to the basis set, ii) that $\psimub(\br{}_1,\br{}_2)$ provides a remarkably good approximation to $\psiex(\br{}_1,\br{}_2)$ from the AVTZ basis set, iii) that for $\mu=0.3$ the wave function $\phimub(\br{}_1,\br{}_2)$ increases while getting toward $r_{12}=0$, whereas it decreases for $\mu=1.0$ just as the FCI wave function, iii) the wave function $\phimub(\br{}_1,\br{}_2)$ is always larger that the FCI one when $r_{12}\approx 0$.
+
+\begin{figure*}
+ \label{fig:mu_0.3_dz_3}
+        \includegraphics[width=0.45\linewidth]{He_mu_0_3_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+        \caption{
+        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
+Comparison with the FCI wave function in the same basis sets and the estimated exact wave function $\psiex(\br{}_1,\br{}_2)$.
+}
+\end{figure*}
+
+\begin{figure*}
+ \label{fig:mu_1.0_dz_3}
+        \includegraphics[width=0.45\linewidth]{He_mu_1_0_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \caption{
+        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=1.0$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
+Comparison with the FCI wave function in the same basis sets and the estimated exact wave function $\psiex(\br{}_1,\br{}_2)$.
+}
+\end{figure*}
+
 \section{General formulation of similarity transformed Hamiltonian}

### 2020-10-05 cusp_j/paper/paper.tex
Ouepoupouetett  Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit. lkfvn:::

@@
 We report in Figs \ref{fig:mu_0.3_dz_3} and \ref{fig:mu_1.0_dz_3} the plot of the right eigenvector $\phimub(\br{}_1,\br{}_2)$, estimated exact wave function $\psimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ and $\mu=1.0$ (respectively) and compared to the exact wave function $\psiex(\br{}_1,\br{}_2)$ and FCI wave function for $r=0.5\,a.u.$.
-From these figure, one can notice that: i) the right eigenvector $\phimub(\br{}_1,\br{}_2)$ converges faster than the FCI wave function with respect to the basis set, ii) that $\psimub(\br{}_1,\br{}_2)$ provides a remarkably good approximation to $\psiex(\br{}_1,\br{}_2)$ from the AVTZ basis set, iii) that for $\mu=0.3$ the wave function $\phimub(\br{}_1,\br{}_2)$ increases while getting toward $r_{12}=0$, whereas it decreases for $\mu=1.0$ just as the FCI wave function, iii) the wave function $\phimub(\br{}_1,\br{}_2)$ is always larger that the FCI one when $r_{12}\approx 0$.
-
 \begin{figure*}
  \label{fig:mu_0.3_dz_3}
-        \includegraphics[width=0.45\linewidth]{He_mu_0_3_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He_mu_0_3_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
  \label{fig:mu_1.0_dz_3}
-        \includegraphics[width=0.45\linewidth]{He_mu_1_0_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
 \end{figure*}
+
+From these figure, one can notice that: 
+i) the right eigenvector $\phimub(\br{}_1,\br{}_2)$ converges faster than the FCI wave function with respect to the basis set, 
+ii) that for $\mu=0.3$ the wave function $\phimub(\br{}_1,\br{}_2)$ present a maximum at $r_{12}=0$, whereas for $\mu=1.0$ and the FCI wave function it has a minimum, 
+iii) the wave function $\phimub(\br{}_1,\br{}_2)$ is always larger that the FCI one when $r_{12}\approx 0$. 
+iv) that $\psimub(\br{}_1,\br{}_2)$ provides a remarkably good approximation to $\psiex(\br{}_1,\br{}_2)$ from the AVTZ basis set,
+
+The understanding of such observations can be provided by the mathematical and physical investigation of the construction of $\tilde{H}[\mu]$. 
+i) The shape of the Jastrow factor $j(r_{12};\mu)$ leading to the transcorrelated Hamiltonian is such that as long as $\mu \infty$, the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ in $\tilde{H}[\mu]$ is non divergent, and therefore its eigenfunction do not have to fulfill the cusp condition which leads to a faster convergence with $\basis$.
+Nevertheless, one can also remark that for $\mu > 0.5$, the speed of convergence deteriorates as $\mu$ increases, even though it remains finite.
+This can be explained by the fact that even if $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ remains bounded from above, when $\mu$ is large such operator is poorly represented in a finite basis set.
+
+ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is attractive for $\mu=0.3$ when $r_{12}\approx 0$ whereas it is repulsive when $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+\begin{figure*}
+ \label{fig_wee_compare}
+        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \caption{
+        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
+\end{figure*}
+iii) Similarly, as for any $\mu < \infty$ one has that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) <\frac{1}{r_{12}}$, the value of the eigenvector of $\phimub(\br{}_1,\br{}_2)$ is necessary larger than the FCI wave function at $r_{12}=0$ as in the latter the interaction is more repulsive.
+iv)
 

### 2020-10-05 cusp_j/paper/prog_bis.f90

@@ -4,7 +4,7 @@ program prog_bis
  integer :: i,nx
  double precision :: mu0,mu1,mu2,mu3,mu4,mu5,mu6
  double precision :: mu7, mu8, mu9,mu10,mu11, mu12, mu13, mu14
- xmax = 5.d0
+ xmax = 15.d0
  nx = 1000
  dx = xmax/dble(nx)
  x = dx

### 2020-10-05 dev/slat_rules_trans/local_energy.irp.f

@@ -1,0 +1,140 @@
+subroutine local_energy_htilde(r1,r2,mu_in,nstates,psi_occ,coefs,ndet,e_loc,kin_e,pot_ee,pot_en,non_hermit_e,psi)
+ implicit none
+ use bitmasks
+ include 'utils/constants.include.F'
+ double precision, intent(out):: kin_e(nstates),pot_ee,pot_en,non_hermit_e(nstates),e_loc(nstates),psi(nstates)
+ double precision, intent(in) :: r1(3), r2(3), mu_in
+ integer, intent(in) :: ndet,nstates,psi_occ(2,ndet)
+ double precision, intent(in) :: coefs(ndet,nstates)
+
+
+ double precision :: grad_psi(3,nstates), lapl_psi(3,nstates), d_d_r12(nstates)
+ call get_two_e_general_grad_lapl_psi_at_r1r2(r1,r2,mu_in,coefs,nstates,psi_occ,ndet,psi,grad_psi,lapl_psi,d_d_r12)
+ do istate = 1, nstates
+  kin_e(istate) = -0.5d0 * ( lapl_psi(1,istate) + lapl_psi(2,istate) + lapl_psi(3,istate) ) 
+  non_hermit_e(istate) = - d_d_r12(istate)
+ enddo
+ double precision :: r12,r,w_ee_eff
+ r12 = (r1(1) - r2(1))**2.D0 + (r1(2) - r2(2))**2.D0 + (r1(3) - r2(3))**2.D0
+ r12 = dsqrt(r12)
+ pot_ee = w_ee_eff(r12,mu_in)
+ r = 0.d0
+ integer :: i,istate
+ pot_en = 0.d0
+ do i = 1, nucl_num
+  r = dsqrt((r1(1) - nucl_coord_transp(1,i))**2.D0 + (r1(2) - nucl_coord_transp(2,i))**2.D0 + (r1(3) - nucl_coord_transp(3,i))**2.D0)
+  pot_en += -nucl_charge(i) / r
+  r = dsqrt((r2(1) - nucl_coord_transp(1,i))**2.D0 + (r2(2) - nucl_coord_transp(2,i))**2.D0 + (r2(3) - nucl_coord_transp(3,i))**2.D0)
+  pot_en += -nucl_charge(i) / r
+ enddo
+
+ do istate = 1, nstates
+  e_loc(istate) = pot_en + pot_ee + (non_hermit_e(istate) + kin_e(istate))/psi(istate)
+ enddo
+end
+
+
[…]

### 2020-10-05 dev/slat_rules_trans/print_eloc.irp.f

@@ -1,0 +1,62 @@
+program pouet
+ implicit none
+ read_wf = .True. 
+ touch read_wf
+ call print_local_energy
+
+end
+
+ BEGIN_PROVIDER [double precision, kin_e_array, (N_states,ntheta_psi_ex,nr1_psi_ex)]
+&BEGIN_PROVIDER [double precision, non_hermit_e_array, (N_states,ntheta_psi_ex,nr1_psi_ex)]
+&BEGIN_PROVIDER [double precision, pot_ee_array, (ntheta_psi_ex,nr1_psi_ex)]
+&BEGIN_PROVIDER [double precision, pot_en_array, (ntheta_psi_ex,nr1_psi_ex)]
+&BEGIN_PROVIDER [double precision, loc_e_array, (N_states,ntheta_psi_ex,nr1_psi_ex)]
+&BEGIN_PROVIDER [double precision, psi_in_r1_r2_array, (N_states,ntheta_psi_ex,nr1_psi_ex)]
+ implicit none
+ integer :: i,j
+ double precision :: kin_e(n_states),pot_ee,pot_en,non_hermit_e(n_states),e_loc(n_states),psi(n_states),loc_e(n_states),mu_in
+ mu_in = mu_erf
+ integer :: psi_occ(2, N_det)
+ call give_occ_two_e_psi(psi_det,N_det,psi_occ)
+ do j = 1, nr1_psi_ex
+  do i = 1, ntheta_psi_ex
+   call local_energy_htilde(r1_psi_ex(1,j),r2_psi_ex(1,i,j),mu_in,n_states,psi_occ,reigvec_trans(1,1),N_det,loc_e,kin_e,pot_ee,pot_en,non_hermit_e,psi)
+   kin_e_array(:,i,j) = kin_e(:)
+   non_hermit_e_array(:,i,j) = non_hermit_e(:)
+   loc_e_array(:,i,j) = loc_e(:)
+   psi_in_r1_r2_array(:,i,j) = psi(:)
+   pot_ee_array(i,j) = pot_ee
+   pot_en_array(i,j) = pot_en
+  enddo
+ enddo
+END_PROVIDER 
+
+
+subroutine print_local_energy
+ implicit none
+ integer :: i
+ integer                        :: i_unit_output,getUnitAndOpen
+ character*(128)                :: output
+ PROVIDE ezfio_filename
+
+BEGIN_TEMPLATE
+ output=trim(ezfio_filename)//'.cusp_eloc_$X'
[…]

### 2020-10-05 dev/slat_rules_trans/routines_to_print.irp.f

@@ -191,36 +191,36 @@ subroutine print_mos
 end
 
 subroutine non_hermit_term(r1,r2,i,j,mu_in,d_d_r12)
-implicit none
-integer, intent(in) :: i,j
-double precision, intent(in) :: r1(3), r2(3) , mu_in
-double precision, intent(out):: d_d_r12
-double precision :: mos_array_r1(mo_num),mos_grad_array_r1(3,mo_num)
-double precision :: mos_array_r2(mo_num),mos_grad_array_r2(3,mo_num)
-double precision :: r12(3), dist_r12, dist_vec(3),poly(3)
-double precision :: erf_mu_r12,derf_mu_x,poly_tot(3)
-integer :: k
-call give_all_mos_and_grad_at_r(r1,mos_array_r1,mos_grad_array_r1)
-call give_all_mos_and_grad_at_r(r2,mos_array_r2,mos_grad_array_r2)
-dist_r12 = 0.d0
-do k = 1, 3
- r12(k) = r1(k) - r2(k) 
- dist_r12 += r12(k)*r12(k)
-enddo
-dist_r12 = dsqrt(dist_r12)
-dist_vec(1) = dsqrt(r12(2)*r12(2) + r12(3)*r12(3))
-dist_vec(2) = dsqrt(r12(1)*r12(1) + r12(3)*r12(3))
-dist_vec(3) = dsqrt(r12(1)*r12(1) + r12(2)*r12(2))
-erf_mu_r12 = derf_mu_x(mu_in,dist_r12)
-call inv_r_times_poly(r12, dist_r12, dist_vec, poly)
-! poly_tot(1) = (1 - erf(mu * r12))/(2 * r12) (x1 - x2)
-do k = 1, 3
- poly_tot(k) = 0.5d0 * (poly(k) - erf_mu_r12 * r12(k) )
-enddo
-d_d_r12 = 0.d0
-do k = 1, 3
- d_d_r12 += poly_tot(k) * (mos_grad_array_r1(k,i) - mos_grad_array_r2(k,j) )
-enddo
+ implicit none
+ integer, intent(in) :: i,j
+ double precision, intent(in) :: r1(3), r2(3) , mu_in
+ double precision, intent(out):: d_d_r12
+ double precision :: mos_array_r1(mo_num),mos_grad_array_r1(3,mo_num)
[…]

### 2020-10-09 cusp_j/paper/paper.tex
pouet

@@
  \begin{aligned}
+ \label{def:h_c}
  h_c = &-\frac{1}{2} \sum_{i=1}^2 \bigg(\deriv{}{r_i}{2} + \frac{2}{r_i} \deriv{}{r_i}{} + \frac{2 Z}{r_i}\bigg) \\
@@
   &- 2 \deriv{j(r_{12})}{r_{12}}{} \deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{} \\ 
-  &- \bigg[ \frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  + \deriv{j(r_{12})}{r_{12}}{2} + \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2\bigg] \phi(r_{12}). 
+  &- \bigg[ \frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  + \deriv{j(r_{12})}{r_{12}}{2} + \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2\bigg] \phi(\br{}_1,\br{}_2). 
  \end{aligned}
@@
  \label{eq:def_tt}
- \tilde{t}[j] = -2 \deriv{j}{r_{12}}{} \deriv{}{r_{12}}{},
+ \tilde{t}[j] = -2 \deriv{j(r_{12})}{r_{12}}{} \deriv{}{r_{12}}{},
 \end{equation}
@@
  \label{eq:def_wt}
- \tilde{W}[j] = -\frac{2}{r_{12}} \deriv{j}{r_{12}}{}  , 
+ \tilde{W}[j] = -\frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  , 
 \end{equation}
@@
  \label{eq:def_wt}
- \tilde{w}[j] = -\deriv{j}{r_{12}}{2} - \bigg( \deriv{j}{r_{12}}{} \bigg)^2. 
+ \tilde{w}[j] = -\deriv{j(r_{12})}{r_{12}}{2} - \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2. 
 \end{equation}
@@
 \end{equation}
-$\tilde{H}[j]$, because of the first-order differential operator in $\tilde{t}[j]$, is then non-hermitian.
+$\tilde{H}[j]$, because of the first-order differential operator in $\tilde{t}[j]$, is then non-hermitian,   
+and the effective potential $ \frac{1}{r_{12}}  + \tilde{W}[j] + \tilde{w}[j]$ in $\tilde{H}[j]$ only depends on the shape of $j(r_{12})$.
 
@@
 \label{sec:cusp}
-The exact ground state wave function $\psiex$ of the usual Hamiltonian must satisfy the Schroedinger equation in real space 
+Having established the general form of the transcorrelated Hamiltonian $\tilde{H}[j]$, in the case of the helium atom, one can then study the behaviour of the latter when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
+The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different conditions that the eigenvectors of such operators must fulfill.
+For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are general for any bounded eigenvectors.
+
+In the case of the usual Hamiltonian, the exact ground state wave function $\psiex$ must satisfy the Schroedinger equation in real space 
 \begin{equation}
@@
 \end{equation}
-When looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which translates into
+When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
 \begin{equation}
  \label{eq:cusp_0}
- \lim_{r_{12}\rightarrow \infty}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
 \end{equation}
@@
 \begin{equation}
- \lim_{r_{12}\rightarrow \infty}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
-\end{equation}
-which translates into the famous cusp condition of Kato\cite{Kat-CPAM-57}, 
+ \lim_{r_{12}\rightarrow 0}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
+\end{equation}
+which translates into the famous cusp condition for antiparallel spins of Kato\cite{Kat-CPAM-57}, 
 \begin{equation}
@@
 
-Regarding now the similarity transformed Hamiltonians, their exact eigenvectors must also satisfy an eigenvalue equation. For instance, the right ground-state eigenvector becomes  
+Regarding now the similarity transformed Hamiltonians, the exact ground state eigenvector must also satisfy an eigenvalue equation in real-space,
 \begin{equation}
@@
  \label{eq:cusp_phi_0}
- \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
-\end{equation}
-Interestingly, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{j(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction modified by the presence of the Jastrow factor in $\tilde{H}[j]$.
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
+\end{equation}
+Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{j(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction modified by the presence of the Jastrow factor in $\tilde{H}[j]$.
 Therefore, as long as one imposes that 
@@
  \label{eq:cusp_psi_mu_0}
- \lim_{r_{12}\rightarrow \infty}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
 \end{equation}
@@
 which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.
+
+Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
 
@@
 Of course, these new terms depends on the explicit form of the Jastrow factor $j(r_{12})$ chosen. 
-Now, we impose the form of $j(r_{12})$ such that it mimics, at leading order, the long-range effective interaction of RS-DFT. 
+Now, we impose the form of $j(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction of RS-DFT. 
 Mathematically, this conditions implies that 
@@
 where $E_0$ is the exact ground state energy. 
+As $\tilde{H}[\mu]$ originates from a similarity transformation, it conserves the same spectrum as $H$ as long as it is developed in a complete basis set.
 
@@
 To understand the physical content together with the mathematical properties of $j(r_{12};\mu)$, 
-one must keep in mind that the complete correlating factor $\mathcal{J}(r_{12},\mu)$ is 
-\begin{equation}
- \mathcal{J}(r_{12},\mu) = \text{exp}\bigg(j(r_{12};\mu)\bigg),
+one must keep in mind that the complete correlating factor $\mathcal{J}(r_{12};\mu)$ is 
+\begin{equation}
+ \mathcal{J}(r_{12};\mu) = \text{exp}\bigg(j(r_{12};\mu)\bigg),
 \end{equation}
@@
 \begin{equation}
- \psiex(\br{}_1,\br{}_2) = \mathcal{J}(r_{12},\mu) \phimu(\br{}_{1},\br{}_{2}).  
+ \psiex(\br{}_1,\br{}_2) = \mathcal{J}(r_{12};\mu) \phimu(\br{}_{1},\br{}_{2}).  
 \end{equation}
@@
 \end{equation}
-Therefore, one can Taylor expand the exact wave function in the vicinity of $\br{}_1$ for small $r_{12}$ 
+Therefore, one can Taylor expand the exact wave function in the vicinity of $\br{}_1$ for small $r_{12}$, and noticing that $\phiex(\br{}_1,\br{}_2) $ is cusp less, one obtains 
 \begin{equation}
@@
 
-Coming now to the behaviour of $j(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12},\mu)$.
+Coming now to the behaviour of $j(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$.
 \begin{figure*}
@@
 \end{figure*}
-From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $j(r_{12};\mu)$, ii) the larger the $\mu$, the closer $j(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function.
+From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $j(r_{12};\mu)$, ii) the larger the $\mu$, the closer $j(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
 
@@
 \end{equation}
+As long as the basis set $\basis$ is incomplete, because of its non hermitian nature, $\tilde{H}[\mu]^{\basis}$ looses the variational principle and therefore its eigenvalues have no reasons to be bounded from below.
 
@@
 The understanding of such observations can be provided by the mathematical and physical investigation of the construction of $\tilde{H}[\mu]$.
-i) The shape of the Jastrow factor $j(r_{12};\mu)$ leading to the transcorrelated Hamiltonian is such that as long as $\mu \infty$, the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ in $\tilde{H}[\mu]$ is non divergent, and therefore its eigenfunction do not have to fulfill the cusp condition which leads to a faster convergence with $\basis$.
+
+i) The shape of the Jastrow factor $j(r_{12};\mu)$ leading to the transcorrelated Hamiltonian is such that as long as $\mu < \infty$, the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ in $\tilde{H}[\mu]$ is non divergent, and therefore its eigenfunctions do not have to fulfill the cusp condition which leads to a faster convergence with $\basis$.
 Nevertheless, one can also remark that for $\mu > 0.5$, the speed of convergence deteriorates as $\mu$ increases, even though it remains finite.
@@
 
-ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is attractive for $\mu=0.3$ when $r_{12}\approx 0$ whereas it is repulsive when $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+
+iii) Similarly, as for any $\mu < \infty$ one has that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) <\frac{1}{r_{12}}$, the value of the eigenvector of $\phimub(\br{}_1,\br{}_2)$ is necessary larger than the FCI wave function at $r_{12}=0$ as in the latter the interaction is more repulsive.
+
+iv) 
 \begin{figure*}
@@
         \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
-%        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
 \end{figure*}
-iii) Similarly, as for any $\mu < \infty$ one has that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) <\frac{1}{r_{12}}$, the value of the eigenvector of $\phimub(\br{}_1,\br{}_2)$ is necessary larger than the FCI wave function at $r_{12}=0$ as in the latter the interaction is more repulsive.
-iv)
 

### 2020-10-09 cusp_j/paper/prog_bis.f90

@@ -2,7 +2,7 @@ program prog_bis
  implicit none
  double precision :: x,dx,xmax,mu,w_ee_eff,derf_mu_x
  integer :: i,nx
- double precision :: mu0,mu1,mu2,mu3,mu4,mu5,mu6
+ double precision :: mu0,mu1,mu2,mu3,mu4,mu5,mu6,mu_tmp_5,mu_tmp_10
  double precision :: mu7, mu8, mu9,mu10,mu11, mu12, mu13, mu14
  xmax = 15.d0
  nx = 1000
@@ -22,6 +22,8 @@ program prog_bis
  mu11= 1.5d0
  mu12= 3.0d0
  mu13= 5.0d0
+ mu_tmp_5 = 0.5284432686368106d0
+ mu_tmp_10 = 1.27844d0
  do i = 1, nx
   write(38,'(100(F16.10,X))')x, w_ee_eff(x,mu0),w_ee_eff(x,mu1),w_ee_eff(x,mu2)& 
                               ,w_ee_eff(x,mu3),w_ee_eff(x,mu4),w_ee_eff(x,mu5),w_ee_eff(x,mu6)&
@@ -31,6 +33,7 @@ program prog_bis
                               ,derf_mu_x(x,mu3),derf_mu_x(x,mu4),derf_mu_x(x,mu5),derf_mu_x(x,mu6)&
                               ,derf_mu_x(x,mu7),derf_mu_x(x,mu8),derf_mu_x(x,mu9),derf_mu_x(x,mu10)& 
                               ,derf_mu_x(x,mu11),derf_mu_x(x,mu12),derf_mu_x(x,mu13),derf_mu_x(x,mu14) 
+  write(40,'(100(F16.10,X))')x, derf_mu_x(x,mu_tmp_5),w_ee_eff(x,mu5),derf_mu_x(x,mu_tmp_10),w_ee_eff(x,mu10)
   x = x + dx
  enddo
 end
@@ -57,3 +60,18 @@ double precision function derf_mu_x(x,mu)
   endif
 end
 
+double precision function mu_rs_from_mu_h(mu_h)
+ implicit none
+ double precision, intent(in) :: mu_h
+ double precision :: sq_pi 
+ sq_pi = dsqrt(dacos(-1.d0))
+ mu_rs_from_mu_h = 1.5d0 * mu_h - sq_pi/8.d0
+end
+
+double precision function mu_h_from_mu_rs(mu_rs)
[…]

### 2020-10-09 dev/coll_salv_fun/two_elec_wf.irp.f

@@ -8,7 +8,7 @@ BEGIN_PROVIDER [integer, occ_two_e_psi, (2, N_det)]
   stop
  endif
  do i = 1, N_det
-  call bitstring_to_list_ab(psi_det_sorted(1,1,i), occ, n_occ_ab, N_int)
+  call bitstring_to_list_ab(psi_det(1,1,i), occ, n_occ_ab, N_int)
   occ_two_e_psi(1,i) = occ(1,1)
   occ_two_e_psi(2,i) = occ(1,2)
  enddo
@@ -29,7 +29,7 @@ subroutine get_two_e_psi_at_r1r2(r1,r2,psi)
   do i = 1, N_det
    i_up   = occ_two_e_psi(1,i)
    i_down = occ_two_e_psi(2,i)
-   psi(istate) += mos_array_r1(i_up) * mos_array_r2(i_down) * psi_coef_sorted(i,istate)
+   psi(istate) += mos_array_r1(i_up) * mos_array_r2(i_down) * psi_coef(i,istate)
   enddo
  enddo
 

### 2020-10-09 dev/slat_rules_trans/htilde_matrix.irp.f

@@ -273,3 +273,19 @@ subroutine test_overlap_matrix
   write(*,'(1000(F16.12,X))')overlap_lr(i,:)
  enddo
 end
+
+BEGIN_PROVIDER [double precision, overlap_psi_det_r_eigevec, (N_states)]
+ implicit none
+ double precision :: accu
+ BEGIN_DOC
+! overlap between psi_det and the right eigenvectors of Htilde
+ END_DOC
+ integer :: i,j
+ do i = 1, N_states
+  accu = 0.d0
+  do j = 1, N_det
+   accu += psi_coef(j,i) * reigvec_trans(j,i)
+  enddo
+  overlap_psi_det_r_eigevec(i) = accu
+ enddo
+END_PROVIDER 

### 2020-10-09 dev/slat_rules_trans/print_eloc.irp.f

@@ -2,7 +2,9 @@ program pouet
  implicit none
  read_wf = .True. 
  touch read_wf
-! call print_local_energy
+ read_rl_eigv = .True.
+ touch read_rl_eigv
+ call print_local_energy
  call routine
 end
 
@@ -28,12 +30,12 @@ subroutine routine
  integer :: j
  j = 3
  r1(:) = r1_psi_ex(:,j)
- mu_in = 1.d+9
  do i = 1, ntheta_psi_ex
   r2(:) = r2_psi_ex(:,i,j)
   r12 = dsqrt( (r1(1) - r2(1))**2.d0 + (r1(2) - r2(2))**2.d0 + (r1(3) - r2(3))**2.d0 )
+  mu_in = 1.d+9
   call local_energy_htilde(r1,r2,mu_in,n_states,psi_occ,psi_coef,N_det,loc_e,kin_e,pot_ee,pot_en,non_hermit_e,psi)
-  !                                     1               2    3     4     5      6     7            8
+  !                                     1               2    3         4     5      6         7            8
   write(33,'(X,100(F16.10,X))')theta_array_psi_ex(i,j),r12,loc_e,kin_e/psi,pot_ee,pot_en,non_hermit_e/psi,psi
  enddo
  j = 3
@@ -41,9 +43,9 @@ subroutine routine
  do i = 1, ntheta_psi_ex
   r2(:) = r2_psi_ex(:,i,j)
   r12 = dsqrt( (r1(1) - r2(1))**2.d0 + (r1(2) - r2(2))**2.d0 + (r1(3) - r2(3))**2.d0 )
-  !                                     1               2    3     4     5      6     7            8
   call local_energy_htilde(r1,r2,mu_in,n_states,psi_occ,reigvec_trans(1,1),N_det,loc_e,kin_e,pot_ee,pot_en,non_hermit_e,psi)
-  write(34,'(X,100(F16.10,X))')theta_array_psi_ex(i,j),r12,loc_e,kin_e,pot_ee,pot_en,non_hermit_e,psi
+  !                                     1               2    3         4     5      6     7                8
+  write(34,'(X,100(F16.10,X))')theta_array_psi_ex(i,j),r12,loc_e,kin_e/psi,pot_ee,pot_en,non_hermit_e/psi,psi
  enddo
 end
 
[…]

### 2020-10-09 dev/slat_rules_trans/psi_exact.irp.f

@@ -45,7 +45,7 @@ END_PROVIDER
 BEGIN_PROVIDER [double precision, psi_fci_array, (ntheta_psi_ex,nr1_psi_ex)]
  implicit none
  integer :: i , j
- call diagonalize_CI
+!call diagonalize_CI
  double precision :: psi
  do j = 1, nr1_psi_ex
   do i = 1, ntheta_psi_ex

### 2020-10-09 dev/slat_rules_trans/psi_in_r.irp.f

@@ -1,0 +1,19 @@
+subroutine get_two_e_psi_general_at_r1r2(r1,r2,ndet,nstates,occ_psi,coefs,psi)
+ implicit none
+ double precision, intent(in) :: r1(3),r2(3),coefs(ndet,nstates)
+ integer, intent(in) :: occ_psi(2,ndet),ndet,nstates
+ double precision, intent(out):: psi(N_states)
+ double precision, allocatable :: mos_array_r2(:),mos_array_r1(:)
+ allocate(mos_array_r1(mo_num),mos_array_r2(mo_num))
+ call give_all_mos_at_r(r1,mos_array_r1)  
+ call give_all_mos_at_r(r2,mos_array_r2)  
+ integer :: i,istate,i_up,i_down
+ psi = 0.d0
+ do istate = 1, nstates
+  do i = 1, ndet
+   i_up   = occ_psi(1,i)
+   i_down = occ_psi(2,i)
+   psi(istate) += mos_array_r1(i_up) * mos_array_r2(i_down) * coefs(i,istate)
+  enddo
+ enddo
+end

### 2020-10-09 dev/slat_rules_trans/routines_to_print.irp.f

@@ -22,6 +22,7 @@ subroutine print_eigv
  print*,'******************'
  print*,'******************'
  print*,'******************'
+ print*,'Overlap betwwen psi_coef and the right eigenvector = ',overlap_psi_det_r_eigevec
  print*,'Eigenvectors '
  print*,'******************'
  print*,'Right eigenvector             Left eigenvector               psi_coef'

### 2020-10-09 dev/slat_rules_trans/test_density.irp.f

@@ -1,0 +1,99 @@
+program test_density
+  implicit none
+  BEGIN_DOC
+! TODO : Put the documentation of the program here
+  END_DOC
+  print *, 'Hello world'
+  read_wf = .True.
+  touch read_wf
+  read_rl_eigv = .True.
+  touch read_rl_eigv
+  call routine_write
+end
+
+subroutine routine_write
+ implicit none
+ integer :: i,npts
+ double precision :: xmax,dx,x
+ double precision, allocatable :: dm_hf_array(:), dm_array(:), g0_array(:), on_top_hf(:),on_top_psi(:),on_top_g0(:),mu_hf(:)
+ double precision, allocatable :: on_top_exact(:)
+ double precision :: sqpi
+ sqpi = dsqrt(dacos(-1.d0))
+ npts = 500
+ xmax = 5.d0
+ allocate( dm_hf_array(npts), dm_array(npts), g0_array(npts), on_top_psi(npts), on_top_hf(npts), on_top_g0(npts), mu_hf(npts), on_top_exact(npts))
+ call routine_psi_hf(dm_hf_array,dm_array,g0_array,on_top_psi,on_top_hf,on_top_g0, mu_hf, npts,xmax)
+ call routine_exact(on_top_exact,npts,xmax)
+ dx = xmax/dble(npts)
+ x = 0.d0
+ do i = 1, npts
+  !                          1     2             3             4                5            
+  write(33,'(100(F16.10,X))')x,on_top_psi(i),on_top_hf(i), on_top_g0(i), on_top_exact(i), &  
+                             !                    6 
+                               on_top_exact(i) * (1.d0 + 2.d0/(sqpi * mu_hf(i)))        , & 
+                             g0_array(i), 2.d0 * on_top_exact(i)/ dm_array(i)**2.d0, dm_hf_array(i),dm_array(i)
+  x += dx
+ enddo
+end
+
+subroutine routine_psi_hf(dm_hf_array,dm_array,g0_array,on_top_psi,on_top_hf,on_top_g0, mu_hf,  npts,xmax)
+ implicit none
+ double precision, intent(in) :: xmax
+ integer, intent(in) :: npts
[…]

### 2020-10-15 cusp_j/paper/paper.tex
added iso files

@@
  \label{fig:mu_0.3_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He_mu_0_3_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He//He_mu_0_3_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
  \label{fig:mu_1.0_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
 iv) 
+\begin{figure*}
+ \label{fig_wee_compare}
+        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
+        \caption{
+        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
+\end{figure*}
+
+\section{Study of the helium isoelectronic series}
 \begin{figure*}

### 2020-10-28 dev/pot_ecmd/print_z_dipole.irp.f
added print_z_dipole

@@ -1,0 +1,7 @@
+program print_z_dipole
+ implicit none
+ read_wf = .True.
+ touch read_wf 
+ call print_z_dipole_moment_only
+
+end

### 2020-10-28 script_mu.sh

@@ -11,7 +11,7 @@ for i in $basis
  cd $dir
  ezfio=H_$dir
  qp set_file $ezfio
- qp run test_density | tee ${ezfio}.mu_av.out 
+ qp run mu_lda_average | tee ${ezfio}.mu_av.out 
  mu_av=`grep "average_mu_lda ="  ${ezfio}.mu_av.out | cut -d "=" -f 2`
  mu_av=${mu_av:0:10}
  mu_av="$(echo -e "${mu_av}" | tr -d '[:space:]')"

### 2020-10-28 cusp_j/paper/paper.tex

@@
 
-\subsection{Study of the ground state eigenvector}
-In Sec.\ref{sec:total_e} we shown the strong improvement of the speed of convergence of the total energy for the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
+\subsection{Study of the ground state eigenvector in real space}
+In Sec.\ref{sec:total_e} we shown the strong improvement of the speed of convergence of the total energy for the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
+To answer that question, we investigate some properties of the ground state eigenvectors of different types of Hamiltonians in real space.
+
 Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = H$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
@@
 \end{equation}
-Therefore, having obtained in a given basis set $\basis$ the right eigenvector $\phimub$, one can estimate the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$ by 
+Therefore, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to can estimate the exact ground state wave function $\psiex$ through 
 \begin{equation}
@@
 
-ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
 
 iii) Similarly, as for any $\mu < \infty$ one has that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) <\frac{1}{r_{12}}$, the value of the eigenvector of $\phimub(\br{}_1,\br{}_2)$ is necessary larger than the FCI wave function at $r_{12}=0$ as in the latter the interaction is more repulsive.
-
-iv) 
+This implies that the on-top pair density (\textit{i.e.} the probability of finding two electrons at the same position) is necessary larger for the eigenvectors of $\tilde{H}[\mu]$ than that for the eigenvectors of $H$.
+
+iv) The fact that $\psimub(\br{}_1,\br{}_2)$ provides  such a good approximation of $\psiex(\br{}_1,\br{}_2)$ in real space can be investigate through the prism of the local energy. 
+The local energy $E_{\text{loc}}[\psi](\br{}_1,\br{}_2)$ associated to a given wave function $\psi$ is defined as 
+\begin{equation}
+ E_{\text{loc}}[\psi](\br{}_1,\br{}_2) = \frac{H\psi(\br{}_1,\br{}_2)}{\psi(\br{}_1,\br{}_2)},
+\end{equation}
+and is such that 
+\begin{equation}
+ \int \text{d}\br{}_1\,\,\text{d}\br{}_2\,\, E_{\text{loc}}[\psi](\br{}_1,\br{}_2) \big|\psi(\br{}_1,\br{}_2)\big|^2= \matelem{\psi}{H}{\psi}.
+\end{equation}
+Therefore, one can 
 \begin{figure*}
@@
 \section{Study of the helium isoelectronic series}
-\begin{figure*}
- \label{fig_wee_compare}
-        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
-        \caption{
-        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
-\end{figure*}
+%\begin{figure*}
+% \label{fig_wee_compare}
+%        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
+%        \caption{
+%        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
+%\end{figure*}
 
@@
 & = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) 
-- \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} 
- \end{aligned}
-\end{equation}
-and so 
+- \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
+ \end{aligned}
+\end{equation}
+implying that 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_3}
+ \bigg( \deriv{}{x_{1}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{z_{1}}{2} \bigg)  u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12}\big)^2},
+ \end{aligned}
+\end{equation}
+and therefore 
 \begin{equation}

### 2020-11-10 cusp_j/paper/paper.tex
working on the paper

@@
 \section{Study of the helium isoelectronic series}
-%\begin{figure*}
-% \label{fig_wee_compare}
-%        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
-%        \caption{
-%        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
-%\end{figure*}
+\begin{table}
+\label{table_conv_e_mu}
+\caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
+For H$^{-}$ and He, the basis sets used are the aug-cc-pVXZ series (X=D,T,Q) and for the Li$^+$-Ne$^{8+}$ series, the cc-pCVXZ (X=D,T,Q) basis sets with core-valence functions were used.}
+\begin{ruledtabular}
+\begin{tabular}{l|ccc|}
+H-           &         &          &          \\
+FCI          &   DZ    &  TZ      &   QZ     \\               
+LDA          &   3.72  &    1.19  &   0.61   \\      
+RSC          &   1.69  &    0.6   &   0.38   \\      
+RSC/LDA      &   2.3   &    0.67  &   0.39   \\      
+\hline       &   2.03  &    0.64  &   0.39   \\      
+He           &         &          &          \\                              
+ FCI         &         &          &          \\        
+ LDA         &  14.18  &   3.13   &  1.19    \\     
+ RSC         &  5.28   &   0.44   &  0.12    \\     
+ RSC/LDA     &  4.87   &   0.37   &  0.12    \\     
+\hline       &  5.07   &   0.4    &  0.12    \\     
+Li+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  10.72  &   3.35   &  1.58    \\     
+ RSC         &  0.9    &   0.09   & -0.02    \\     
+ RSC/LDA     &  -0.82  &  -0.38   & -0.14    \\     
+\hline       &  0.04   &  -0.12   & -0.08    \\     
+Be2+         &         &          &          \\                                  
+ FCI         &         &          &          \\        
+ LDA         &  11.35  &   3.62   & 1.41     \\     
+ RSC         &  1.2    &   0.17   & -0.02    \\     
+ RSC/LDA     &  -1.5   &  -0.53   & -0.17    \\     
+\hline       &  -0.08  &  -0.15   & -0.09    \\     
+B3+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  11.91  &   4.21   &  1.53    \\     
+ RSC         &  1.41   &   0.43   &  -0.01   \\      
+ RSC/LDA     &  -2.16  &  -0.34   &  -0.22   \\      
+\hline       &  -0.18  &   0.09   &  -0.11   \\      
+C4+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  12.46  &   4.76   &  1.67    \\     
+ RSC         &  1.67   &   0.37   &  0.01    \\     
+ RSC/LDA     &  -2.69  &  -0.4    & -0.25    \\     
+\hline       &  -0.19  &   0.01   &  -0.1    \\     
+N5+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  13.1   &   5.71   &  1.79    \\     
+ RSC         &  2.06   &   0.45   &  0.01    \\     
+ RSC/LDA     &  -2.97  &  -0.64   &  -0.26   \\      
+\hline       &  -0.01  &  -0.15   &  -0.09   \\      
+O6+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  13.84  &   6.47   &  2.02    \\     
+ RSC         &  2.54   &   0.77   & -0.02    \\     
+ RSC/LDA     &  -3.13  &  -0.7    & -0.31    \\     
+\hline       &  0.27   &  -0.04   & -0.12    \\     
+F7+          &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  14.68  &   7.06   &  2.25    \\     
+ RSC         &  3.14   &   1.15   & -0.02    \\     
+ RSC/LDA     &  -3.1   &  -0.54   & -0.36    \\     
+\hline       &  0.69   &   0.23   & -0.14    \\     
+Ne8+         &         &          &          \\                               
+ FCI         &         &          &          \\        
+ LDA         &  15.66  &   7.61   &  2.36    \\     
+ RSC         &  3.89   &   1.57   &  0.03    \\     
+ RSC/LDA     &  -2.85  &  -0.28   & -0.35    \\     
+\hline       &  1.26   &   0.57   & -0.1     \\     
+\end{tabular}
+\end{ruledtabular}
+\end{table}
 

### 2020-11-10 stable/yuan_plugins/example.irp.f

@@ -37,12 +37,12 @@ subroutine routine_active_only_test(two_rdm)
 
 
        rdmab   =  two_rdm(l,k,j,i)
-!      if(dabs(rdmab).gt.1.d-10)then
-!        print*,i,j,k,l
-!        print*,iorb,jorb,korb,lorb
-!        print*,rdmab
-!        print*,vijkl
-!      endif
+       if(dabs(rdmab).gt.1.d-10)then
+         print*,i,j,k,l
+         print*,iorb,jorb,korb,lorb
+         print*,rdmab
+         print*,vijkl
+       endif
 
 
        wee_ab(istate)     += vijkl * rdmab

### 2020-11-10 stable/yuan_plugins/get_one_rdm.irp.f

@@ -5,8 +5,7 @@ BEGIN_PROVIDER [ double precision, one_rdm_from_two_rdm, (mo_num, mo_num)]
  do i = 1, mo_num
   do j = 1, mo_num
    do k = 1, mo_num
-!    one_rdm_from_two_rdm(j,i) += 2.d0 * full_occ_2_rdm_spin_trace_mo(j,k,i,k,1) / (dble(elec_num)-1.d0)
-    one_rdm_from_two_rdm(j,i) += 2.d0 * full_occ_2_rdm_ab_mo(j,k,i,k,1) / (dble(elec_num)-1.d0)
+    one_rdm_from_two_rdm(j,i) += 2.d0 * full_occ_2_rdm_spin_trace_mo(j,k,i,k,1) / (dble(elec_num)-1.d0)
    enddo
   enddo
  enddo

### 2020-11-10 stable/yuan_plugins/read_and_write_rdm.irp.f

@@ -1,55 +1,4 @@
 
-subroutine read_two_rdm_yuan_uniq_and_write_to_ezfio(n,n_mo_tmp)
- implicit none
- integer, intent(in) :: n,n_mo_tmp
-
- double precision, allocatable :: two_rdm(:,:,:,:)
- allocate(two_rdm(n_mo_tmp,n_mo_tmp,n_mo_tmp,n_mo_tmp))
- integer :: i,j,k,l,m
- double precision :: value_rdm
- character*(1) :: coma
- two_rdm = 0.d0
- open(1, file = 'two_rdm') 
- do m = 1, n
-   ! a^{k}a^{l} a_j a_i = <kl|ij>
-  read(1,'(4(I3,A1),F16.13)')k,coma, l, coma, i, coma, j,coma,value_rdm
-  k += 1
-  l += 1
-  i += 1
-  j += 1
-  two_rdm(k,l,i,j) = value_rdm
-  two_rdm(l,k,j,i) = value_rdm
-  two_rdm(i,j,k,l) = value_rdm
-  two_rdm(j,i,l,k) = value_rdm
- enddo
- close(1)
-
- open(1, file = 'two_rdm_read') 
- do i = 1, n_act_orb
-  do j = 1, n_act_orb
-   do k = 1, n_act_orb
-    do l = 1, n_act_orb
-     value_rdm = two_rdm(l,k,j,i)
-     write(1,'(4(I3,A1),F16.13)')l,coma, k, coma, j, coma, i, coma, value_rdm
-    enddo
-   enddo
-  enddo
- enddo
- close(1)
-
-
-
- ! Writting the two rdm on the alpha/beta
- call ezfio_set_two_body_rdm_two_rdm_ab_disk(two_rdm)
- call ezfio_set_two_body_rdm_io_two_body_rdm_ab("Read")
-
- ! Writting the two rdm on the spin trace
- call ezfio_set_two_body_rdm_two_rdm_spin_trace_disk(two_rdm)
- call ezfio_set_two_body_rdm_io_two_body_rdm_spin_trace("Read")
-
- deallocate(two_rdm)
-end
-
 subroutine read_two_rdm_and_write_to_ezfio(n,n_mo_tmp)
  implicit none
  integer, intent(in) :: n,n_mo_tmp
@@ -80,93 +29,6 @@ subroutine read_two_rdm_and_write_to_ezfio(n,n_mo_tmp)
  deallocate(two_rdm)
 end
 
-
[…]

### 2020-11-10 stable/yuan_plugins/read_and_write_rdm_trash.irp.f

@@ -1,192 +1,0 @@
-
-subroutine read_two_rdm_yuan_uniq_and_write_to_ezfio(n,n_mo_tmp)
- implicit none
- integer, intent(in) :: n,n_mo_tmp
-
- double precision, allocatable :: two_rdm(:,:,:,:)
- allocate(two_rdm(n_mo_tmp,n_mo_tmp,n_mo_tmp,n_mo_tmp))
- integer :: i,j,k,l,m
- double precision :: value_rdm
- character*(1) :: coma
- two_rdm = 0.d0
- open(1, file = 'two_rdm') 
- do m = 1, n
-   ! a^{k}a^{l} a_j a_i = <kl|ij>
-  read(1,'(4(I3,A1),F16.13)')k,coma, l, coma, i, coma, j,coma,value_rdm
-  k += 1
-  l += 1
-  i += 1
-  j += 1
-  two_rdm(k,l,i,j) = value_rdm
-  two_rdm(l,k,j,i) = value_rdm
-  two_rdm(i,j,k,l) = value_rdm
-  two_rdm(j,i,l,k) = value_rdm
- enddo
- close(1)
-
- open(1, file = 'two_rdm_read') 
- do i = 1, n_act_orb
-  do j = 1, n_act_orb
-   do k = 1, n_act_orb
-    do l = 1, n_act_orb
-     value_rdm = two_rdm(l,k,j,i)
-     write(1,'(4(I3,A1),F16.13)')l,coma, k, coma, j, coma, i, coma, value_rdm
-    enddo
-   enddo
-  enddo
- enddo
- close(1)
-
-
-
- ! Writting the two rdm on the alpha/beta
- call ezfio_set_two_body_rdm_two_rdm_ab_disk(two_rdm)
- call ezfio_set_two_body_rdm_io_two_body_rdm_ab("Read")
-
- ! Writting the two rdm on the spin trace
- call ezfio_set_two_body_rdm_two_rdm_spin_trace_disk(two_rdm)
- call ezfio_set_two_body_rdm_io_two_body_rdm_spin_trace("Read")
-
- deallocate(two_rdm)
-end
-
-subroutine read_two_rdm_yuan_and_write_to_ezfio(n,n_mo_tmp)
- implicit none
- integer, intent(in) :: n,n_mo_tmp
-
- double precision, allocatable :: two_rdm(:,:,:,:)
[…]

### 2020-11-10 stable/yuan_plugins/write_mat.irp.f

@@ -1,0 +1,294 @@
+
+
+subroutine write_rotation_matrix_total_one_e_rdm_uniq
+ implicit none
+ integer :: i,j,k,l
+ integer :: iorb,jorb
+ double precision :: eigvalues(mo_num),rot_mat_tmp(mo_num,mo_num), mo_array(mo_num, mo_num)
+ double precision :: rot_mat_act(n_act_orb, n_act_orb)
+ double precision :: vijkl,get_two_e_integral
+
+! !!!!!!!!!!!!
+! ! identity rotation matrix 
+ rot_mat_tmp = 0.d0
+ do i = 1, mo_num
+  rot_mat_tmp(i,i) = 1.d0
+ enddo
+
+! mo_array = -one_e_dm_mo
+ print*,'Write rotation matrix from current orbitals to natural orbitals '
+! call lapack_diagd(eigvalues,rot_mat_tmp,mo_array,mo_num,mo_num) 
+ !!!!!!!!!!!!
+ do i = 1, n_act_orb
+  iorb = list_act(i)
+  do j = 1, n_act_orb
+   jorb = list_act(j)
+   rot_mat_act(j,i) = rot_mat_tmp(jorb,iorb)
+  enddo
+ enddo
+ open(1, file = 'rotation_matrix') 
+ do i = 1, n_act_orb
+  write(1,*)rot_mat_act(i,1:n_act_orb)
+ enddo
+ close(1) 
+ double precision :: new_mo_coef_tmp(ao_num, mo_num)
+ ! <AO_k| new_mo_j> = \sum_i U_ij <AO_k| old_mo_i>
+ new_mo_coef_tmp = 0.d0
+ do j = 1, mo_num ! 
+  do i = 1, mo_num
+   do k = 1, ao_num
+     new_mo_coef_tmp(k,j) += mo_coef(k,i) * rot_mat_tmp(i,j) 
+   enddo
+  enddo
+ enddo
+ open(1, file = 'new_mo_coef') 
+ do i = 1, mo_num
+  write(1,'(100(F16.10,X))')new_mo_coef_tmp(i,1:mo_num)
+ enddo
+ close(1) 
+ double precision :: mo_overlap_tmp(mo_num, mo_num)
+ double precision :: one_e_rdm(n_act_orb, n_act_orb)
+ print*,'Computing the new overlap '
+ call new_one_e_mat(ao_overlap, new_mo_coef_tmp, mo_overlap_tmp)
[…]

### 2020-11-10 stable/yuan_plugins/write_rotation_matrix.irp.f

@@ -5,542 +5,3 @@ program write_rot_mat
 ! call routine_active_only_test(act_2_rdm_ab_mo)
  call write_rotation_matrix_total_one_e_rdm_uniq
 end
-
-subroutine write_rotation_matrix_total_one_e_rdm_uniq
- implicit none
- integer :: i,j,k,l
- integer :: iorb,jorb
- double precision :: eigvalues(mo_num),rot_mat_tmp(mo_num,mo_num), mo_array(mo_num, mo_num)
- double precision :: rot_mat_act(n_act_orb, n_act_orb)
- double precision :: vijkl,get_two_e_integral
-
-! !!!!!!!!!!!!
-! ! identity rotation matrix 
- rot_mat_tmp = 0.d0
- do i = 1, mo_num
-  rot_mat_tmp(i,i) = 1.d0
- enddo
-
-! mo_array = -one_e_dm_mo
- print*,'Write rotation matrix from current orbitals to natural orbitals '
-! call lapack_diagd(eigvalues,rot_mat_tmp,mo_array,mo_num,mo_num) 
- !!!!!!!!!!!!
- do i = 1, n_act_orb
-  iorb = list_act(i)
-  do j = 1, n_act_orb
-   jorb = list_act(j)
-   rot_mat_act(j,i) = rot_mat_tmp(jorb,iorb)
-  enddo
- enddo
- open(1, file = 'rotation_matrix') 
- do i = 1, n_act_orb
-  write(1,*)rot_mat_act(i,1:n_act_orb)
- enddo
- close(1) 
- double precision :: new_mo_coef_tmp(ao_num, mo_num)
- ! <AO_k| new_mo_j> = \sum_i U_ij <AO_k| old_mo_i>
- new_mo_coef_tmp = 0.d0
- do j = 1, mo_num ! 
-  do i = 1, mo_num
-   do k = 1, ao_num
-     new_mo_coef_tmp(k,j) += mo_coef(k,i) * rot_mat_tmp(i,j) 
-   enddo
-  enddo
- enddo
- open(1, file = 'new_mo_coef') 
- do i = 1, mo_num
-  write(1,'(100(F16.10,X))')new_mo_coef_tmp(i,1:mo_num)
- enddo
- close(1) 
- double precision :: mo_overlap_tmp(mo_num, mo_num)
- double precision :: one_e_rdm(n_act_orb, n_act_orb)
- print*,'Computing the new overlap '
[…]

### 2020-11-10 cusp_j/paper/paper.tex
added the iso electronic series data in paper

--- 2020-10-28 cusp_j/paper/paper.tex
@@
 \newcommand{\mur}[1]{\mu({\bf r_{#1}})}
+\newcommand{\muueg}{\langle \mu_{\text{UEG}}\rangle}
+\newcommand{\mursc}{\langle \mu_{r_{s,c}}\rangle}
+\newcommand{\mursclda}{\langle \mu_{r_{s,c}^{\text{UEG}}}\rangle}
 
@@
 \section{Study of the helium isoelectronic series}
-%\begin{figure*}
-% \label{fig_wee_compare}
-%        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
-%        \caption{
-%        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
-%\end{figure*}
-
+%\begin{table*}
+%\label{table_conv_e_mu}
+%\caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
+For H$^{-}$ and He, the basis sets used are the aug-cc-pVXZ series (X=D,T,Q) and for the Li$^+$-Ne$^{8+}$ series, the cc-pCVXZ (X=D,T,Q) basis sets with core-valence functions were used.}
+%\begin{ruledtabular}
+%\begin{tabular}{l|ccc|}
+%H-           &         &          &          \\
+%FCI          &   DZ    &  TZ      &   QZ     \\               
+%LDA          &   3.72  &    1.19  &   0.61   \\      
+%RSC          &   1.69  &    0.6   &   0.38   \\      
+%RSC/LDA      &   2.3   &    0.67  &   0.39   \\      
+%\hline       &   2.03  &    0.64  &   0.39   \\      
+%He           &         &          &          \\                              
+% FCI         &         &          &          \\        
+% LDA         &  14.18  &   3.13   &  1.19    \\     
+% RSC         &  5.28   &   0.44   &  0.12    \\     
+% RSC/LDA     &  4.87   &   0.37   &  0.12    \\     
+%\hline       &  5.07   &   0.4    &  0.12    \\     
+%Li+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  10.72  &   3.35   &  1.58    \\     
+% RSC         &  0.9    &   0.09   & -0.02    \\     
+% RSC/LDA     &  -0.82  &  -0.38   & -0.14    \\     
+%\hline       &  0.04   &  -0.12   & -0.08    \\     
+%Be2+         &         &          &          \\                                  
+% FCI         &         &          &          \\        
+% LDA         &  11.35  &   3.62   & 1.41     \\     
+% RSC         &  1.2    &   0.17   & -0.02    \\     
+% RSC/LDA     &  -1.5   &  -0.53   & -0.17    \\     
+%\hline       &  -0.08  &  -0.15   & -0.09    \\     
+%B3+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  11.91  &   4.21   &  1.53    \\     
+% RSC         &  1.41   &   0.43   &  -0.01   \\      
+% RSC/LDA     &  -2.16  &  -0.34   &  -0.22   \\      
+%\hline       &  -0.18  &   0.09   &  -0.11   \\      
+%C4+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  12.46  &   4.76   &  1.67    \\     
+% RSC         &  1.67   &   0.37   &  0.01    \\     
+% RSC/LDA     &  -2.69  &  -0.4    & -0.25    \\     
+%\hline       &  -0.19  &   0.01   &  -0.1    \\     
+%N5+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  13.1   &   5.71   &  1.79    \\     
+% RSC         &  2.06   &   0.45   &  0.01    \\     
+% RSC/LDA     &  -2.97  &  -0.64   &  -0.26   \\      
+%\hline       &  -0.01  &  -0.15   &  -0.09   \\      
+%O6+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  13.84  &   6.47   &  2.02    \\     
+% RSC         &  2.54   &   0.77   & -0.02    \\     
+% RSC/LDA     &  -3.13  &  -0.7    & -0.31    \\     
+%\hline       &  0.27   &  -0.04   & -0.12    \\     
+%F7+          &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  14.68  &   7.06   &  2.25    \\     
+% RSC         &  3.14   &   1.15   & -0.02    \\     
+% RSC/LDA     &  -3.1   &  -0.54   & -0.36    \\     
+%\hline       &  0.69   &   0.23   & -0.14    \\     
+%Ne8+         &         &          &          \\                               
+% FCI         &         &          &          \\        
+% LDA         &  15.66  &   7.61   &  2.36    \\     
+% RSC         &  3.89   &   1.57   &  0.03    \\     
+% RSC/LDA     &  -2.85  &  -0.28   & -0.35    \\     
+%\hline       &  1.26   &   0.57   & -0.1     \\     
+%\end{tabular}
+%\end{ruledtabular}
+%\end{table*}
+
+\begin{table*}
+\label{table_conv_e_mu}
+\caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
+For H$^{-}$ and He, the basis sets used are the aug-cc-pVXZ series (X=D,T,Q) and for the Li$^+$-Ne$^{8+}$ series, the cc-pCVXZ (X=D,T,Q) basis sets with core-valence functions were used.
+The mean absolute deviation (MAD) and mean signed deviation (MSD) are also reported for each basis set and method.
+}
+\begin{ruledtabular}
+\begin{tabular}{l|rrr||rrr||rrr|}
+             &\multicolumn{3}{c}{H$^-$}      & \multicolumn{3}{c}{He}       & \multicolumn{3}{c}{Li$^+$}    \\
+             &   DZ    &  TZ      &   QZ     &  DZ     &   TZ     &  QZ     &   DZ    &   TZ     &  QZ      \\                   
+\hline
+ FCI         &   3.72  &    1.19  &   0.61   &  14.18  &   3.13   &  1.19   &  10.72  &   3.35   &  1.58    \\      
+$\muueg$     &   1.69  &    0.60  &   0.38   &  5.28   &   0.44   &  0.12   &  0.9    &   0.09   & -0.02    \\      
+$\mursc$     &   2.30  &    0.67  &   0.39   &  4.87   &   0.37   &  0.12   &  -0.82  &  -0.38   & -0.14    \\      
+$\mursclda$  &   2.03  &    0.64  &   0.39   &  5.07   &   0.40   &  0.12   &  0.04   &  -0.12   & -0.08    \\      
+\hline
+             &\multicolumn{3}{c}{Be$^{2+}$}  & \multicolumn{3}{c}{B$^{3+}$} & \multicolumn{3}{c}{C$^{4+}$}    \\
+ FCI         &  11.35  &   3.62   &  1.41    &  11.91  &   4.21   &  1.53   &  12.46  &   4.76   &  1.67    \\  
+$\muueg$     &  1.2    &   0.17   & -0.02    &  1.41   &   0.43   &  -0.01  &  1.67   &   0.37   &  0.01    \\  
+$\mursc$     &  -1.5   &  -0.53   & -0.17    &  -2.16  &  -0.34   &  -0.22  &  -2.69  &  -0.4    & -0.25    \\  
+$\mursclda$  &  -0.08  &  -0.15   & -0.09    &  -0.18  &   0.09   &  -0.11  &  -0.19  &   0.01   &  -0.1    \\  
+\hline
+             &\multicolumn{3}{c}{N$^{5+}$}   & \multicolumn{3}{c}{O$^{6+}$} & \multicolumn{3}{c}{F$^{7+}$}    \\
+ FCI         &  13.1   &   5.71   &  1.79    &  13.84  &   6.47   &  2.02   &  14.68  &   7.06   &  2.25    \\  
+$\muueg$     &  2.06   &   0.45   &  0.01    &  2.54   &   0.77   & -0.02   &  3.14   &   1.15   & -0.02    \\  
+$\mursc$     &  -2.97  &  -0.64   &  -0.26   &  -3.13  &  -0.7    & -0.31   &  -3.1   &  -0.54   & -0.36    \\  
+$\mursclda$  &  -0.01  &  -0.15   &  -0.09   &  0.27   &  -0.04   & -0.12   &  0.69   &   0.23   & -0.14    \\  
+\hline
+             &\multicolumn{3}{c}{Ne$^{8+}$}  & \multicolumn{3}{c}{MAD} & \multicolumn{3}{c}{MSD}    \\
+ FCI         &  15.66  &   7.61   &  2.36    & 12.16   &    4.71  &    1.64   &  12.16   &   4.71   &    1.64   \\   
+$\muueg$     &  3.89   &   1.57   &  0.03    & 4.23    &    1.11  &    0.13   &   4.23   &   1.11   &    0.13   \\   
+$\mursc$     &  -2.85  &  -0.28   & -0.35    & 2.64    &    0.48  &    0.26   &  -1.21   &  -0.28   &   -0.16   \\   
+$\mursclda$  &  1.26   &   0.57   & -0.1     & 2.38    &    0.60  &    0.07   &   2.38   &   0.60   &    0.05   \\   
+\end{tabular}
+\end{ruledtabular}
+\end{table*}
 \section{General formulation of similarity transformed Hamiltonian}

### 2020-11-10 cusp_j/paper/paper.tex
modified script for only one macro iteration

@@
 Therefore, the probability of finding two electrons at $r_{12}=0$ (\textit{i.e.} the on-top pair density) is larger for $\phiex(\br{}_1,\br{}_2)$ than for $\psiex(\br{}_1,\br{}_2)$.  
-This can be easily understood noticing that, by construction, $\tilde{H}[\mu]$ does not contain any divergent potential term at $r_{12}=0$, and therefore the electrons repels less each other.
+This can be easily understood noticing that, by construction, $\tilde{H}[\mu]$ does not contain any divergent potential term at $r_{12}=0$, and therefore the electrons repels less each other in  $\tilde{H}[\mu]$.
 
@@
 From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential 
-is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT. 
+is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT at large $r_{12}$. 
 Nevertheless, as observed from Fig.\ref{fig_wee_mu}, it is significantly different 
@@
 The first part of our study concerns the convergence of the eigenvalues of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
-Therefore, considering a given basis set $\basis$ and the corresponding projector $P_\basis$, one can define the transcorrelated Hamiltonian projected in a given basis set by
-\begin{equation}
- \tilde{H}[\mu]^{\basis} = P_\basis \tilde{H}[\mu] P_\basis,
-\end{equation}
-whose right eigenvectors and eigenvalues satisfy 
-In the present paper, we study the behaviour of $\tilde{H}[\mu]$ in the case of the isoelectronic series of the helium atom, and in that section we focus on the helium atom itself. 
-The first part of our study concerns the convergence of the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
 
@@
 \subsubsection{Computational details}
-We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual gaussian orbital basis set (see annexes for more details) in the case of an atomic two electron systems, together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual gaussian orbital basis set (see annexes for more details) together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
-Once the matrix elements of $\tilde{H}[\mu]$ are built on a given MO basis, we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} $\Phi_\mu$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
-If not explicitly mentioned, the canonical RHF MOs are used in this work.
-The study was performed using the augmented Dunning basis aug-cc-pVXZ (X=D,T,Q,5), hereafter referred as AVXZ.
+We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} $\Phi_\mu$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
+%The study was performed using the augmented Dunning basis aug-cc-pVXZ (X=D,T,Q,5), hereafter referred as AVXZ.
 
@@
 For $0.3\ge\mu\ge0.4$ one can see that the error with respect to $E_0$ is never larger, in absolute value, than 1mH whatever the basis set used, which represents a strong improvement with respect to the FCI.
-For $0.5\ge \mu \ge 1.0$ such the 1mH error threshold is reached at the aug-cc-pVTZ level and the accuracy are comparable to the FCI in the aug-cc-pV5Z basis set.
+For $0.5\ge \mu \ge 1.0$ the 1mH error threshold is reached at the aug-cc-pVTZ level and the accuracy are comparable to the FCI in the aug-cc-pV5Z basis set.
 For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
@@
 \end{equation}
-Therefore, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to can estimate the exact ground state wave function $\psiex$ through 
+Therefore, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to estimate the exact ground state wave function $\psiex$ through 
 \begin{equation}
@@
 \end{equation}
-
-Knowing that, one can directly compare $\psimub(\br{}_1,\br{}_2) $ in real space to the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$, which is approximated in the case of the helium atom by the wave function developed by Umrigar \textit{et.
+Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also observed from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$. 
+For this study, we approximate the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$ of the helium atom by the wave function developed by Umrigar \textit{et.
 al.}\cite{UmrGon-PRA-94} which contains explicitly the $r_{12}$ coordinate and which provides a total energy accurate up to twelve digits.
-Therefore, we plotted cuttings of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
+We plotted cuttings of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
 The cuttings used are the following: we set two electrons on a circle of radius $r$ from the nucleus, and use increasing values of $r$.

### 2020-11-12 cusp_j/paper/paper.tex
restructuration

@@
 \newcommand{\br}[0]{{\bf {r}}}
+\newcommand{\bri}[1]{{\bf r}_{#1}}
 \newcommand{\bs}[0]{{\bf {s}}}
-\newcommand{\dr}[1]{\text{d}{\bf {#1}}}
+\newcommand{\dr}[1]{\text{d}{\bf r_{#1}}}
 \newcommand{\psiex}[0]{\Psi^{\text{ex}}_0}
@@
 \newcommand{\mur}[1]{\mu({\bf r_{#1}})}
-\newcommand{\muueg}{\langle \mu_{\text{UEG}}\rangle}
-\newcommand{\mursc}{\langle \mu_{r_{s,c}}\rangle}
+\newcommand{\muueg}{\mu_{\text{UEG}}}
+\newcommand{\muuegav}{\langle \mu_{\text{UEG}}\rangle}
+\newcommand{\mursc}{ \mu_{r_{s,c}}}
+\newcommand{\murscav}{\langle \mu_{r_{s,c}}\rangle}
 \newcommand{\mursclda}{\langle \mu_{r_{s,c}^{\text{UEG}}}\rangle}
@@
 
-\section{Brief overview of mathematical properties of similarity transformed Hamiltonian}
-\subsection{Definition of the similarity transformation}
-Assume an \textit{Hermitian operator} $H$ whose spectral representation reads 
-\begin{equation}
- \label{eq:h_spectr}
- H  = \sum_n E_n \ket{\Psi_n}\bra{\Psi_n}
-\end{equation}
-with $\ket{\Psi_n}$ being its orthonormal eigenvectors 
-\begin{equation}
- \bra{\Psi_n} \Psi_m \rangle = \delta_{mn},
-\end{equation}
-and $E_n \in \R$ its real eigenvalues.
-
-Let us consider now an \textit{Hermitian} and \textit{invertible} operator $U$, \textit{i.e.} an operator $U$ such that there exists $U^{-1}$ such that 
-\begin{equation}
- \label{eq:u_def_1}
- U^{-1} U = U \, U^{-1} = 1,
-\end{equation}
-and that 
-\begin{equation}
- \begin{aligned}
- \label{eq:u_def_2}
- & U^\dagger = U \\
- & \big(U^{-1}\big)^{\dagger} = U^{-1}.
- \end{aligned}
-\end{equation}
-Then, the similarity transformed Hamiltonian $\tilde{H}$ is defined as
-\begin{equation}
- \label{eq:def_htilde}
- \tilde{H} = U^{-1}\, H \, U.
-\end{equation}
-\subsection{Eigenvalues ans eigenvectors of $\tilde{H}$}
-\subsubsection{Definition of left and right eigenvectors}
-Regarding the properties of $\tilde{H}$, a first remark is that it is not Hermitian anymore
-\begin{equation}
- \begin{aligned}
- \tilde{H}^\dagger & = \bigg(  U^{-1} \, H \,U \bigg)^\dagger \\
-                   & = U\, H \, U^{-1}  \\
-                   & \ne \tilde{H}.
- \end{aligned}
-\end{equation}
-Even though $\tilde{H}$ is not hermitian, it conserves the same eigenvalues than the original Hamiltonian $H$. 
-The main difference with the original Hamiltonian are its eigenvectors: because $\tilde{H}$ is not Hermitian anymore, it possesses \textit{right} eigenvectors and \textit{left} eigenvectors. 
-The right eigenvectors of a given operator $A$ are defined by
-\begin{equation}
- A \ket{\Phi_n} = A_n \ket{\Phi_n}, 
-\end{equation}
-whereas the left eigenvectors of such operator are defined through
-\begin{equation}
- A^{\dagger} \ket{X_n} = A_n \ket{X_n}.
-\end{equation}
-Therefore, if $A$ is hermitian, $A = A^{\dagger}$ and therefore $\ket{\Phi_n} = \ket{X_n} $, but for a non hermitian operator, the left and right eigenvectors do not coincide.
-
-To find the right and left eigenvectors of $\tilde{H}$, one can insert the definition of $\tilde{H}$ (see Eq. \eqref{eq:def_htilde}) in Eq. \eqref{eq:h_spectr}
-\begin{equation}
- \label{eq:tilde_1}
- \begin{aligned}
- \tilde{H} & = \sum_n E_n \, U^{-1} \, \ket{\Psi_n} \bra{\Psi_n}U.
- \end{aligned}
-\end{equation}
-We can define the right eigenvectors $\ket{\Phi_n}$ as
-\begin{equation}
- \label{eq:def_right}
- \ket{\Phi_n} = U^{-1} \ket{\Psi_n},
-\end{equation}
- because  from Eq. \eqref{eq:tilde_1}, we notice that the $\ket{\Phi_n}$ fulfil the right eigenvector relationship
-\begin{equation}
- \begin{aligned}
- \tilde{H} \ket{\Phi_n} & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U\ket{\Phi_n} \\
-                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U \bigg( U^{-1} \ket{\Psi_n} \bigg) \\
-                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} \Psi_n \rangle \\
-                        & = E_n          U^{-1} \ket{\Psi_n} \\
-                        & = E_n  \ket{\Phi_n} \\
- \end{aligned}
-\end{equation}
-In a similar way, we can define the left eigenvectors $\ket{X_n}$ as 
-\begin{equation}
- \label{eq:def_left}
- \ket{X_n} = U \ket{\Psi_n},
-\end{equation}
-because they fulfil the left eigenvalue equation
-\begin{equation}
- \begin{aligned}
- \tilde{H}^{\dagger} \ket{X_n}  = E_n \, \ket{X_n}. 
- \end{aligned}
-\end{equation}
-\subsubsection{Biorthogonality, spectral representation and loose of the variational principle}
-The left and right eigenvectors fulfill the so-called \textit{biorthogonal} property, as 
-from Eqs. \eqref{eq:def_right} and \eqref{eq:def_left} one obtains 
-\begin{equation}
- \overlap{X_j}{\Phi_i} = \bigg(U \ket{\Psi_n} \bigg)^\dagger \bigg(U^{-1}\ket{\Psi_J}\bigg)
-\end{equation}
-which, according to the Hermitian property of $U$ (see Eq.\eqref{eq:u_def_2}) simply becomes 
-\begin{equation}
- \begin{aligned}
- \overlap{X_j}{\Phi_i} &= \matelem{\Psi_j}{U\,U^{-1}}{\Psi_i} \\
-                       &= \overlap{\Psi_j}{\Psi_i} \\
-                       &= \delta_{ji}.
- \end{aligned}
-\end{equation}
-Nevertheless, the right and left eigenvectors among themselves are not orthonormal as 
-\begin{equation}
- \begin{aligned}
-  \overlap{\Phi_j}{\Phi_i} & = \matelem{\Psi_j}{U^{-1}\,U^{-1}}{\Psi_i} \\
-                           & = \matelem{\Psi_j}{U^{-2}}{\Psi_i},  
- \end{aligned}
-\end{equation}
-and 
-\begin{equation}
- \begin{aligned}
-  \overlap{X_j}{X_i} & = \matelem{\Psi_j}{U\,U}{\Psi_i} \\
-                           & = \matelem{\Psi_j}{U^{2}}{\Psi_i}.  
- \end{aligned}
-\end{equation}
-Having obtained biorthonormal left and right eigenvectors, one can then obtain a spectral representation of the similarity transformed Hamiltonian 
-\begin{equation}
- \tilde{H} = \sum_i E_i \ket{\Phi_i} \bra{X_i}, 
-\end{equation}
-which is very useful to study the variational principle, an important aspect of quantum chemistry. 
-Let us consider a wave function $\Psi$ developed on the eigenvectors of $H$
-\begin{equation}
- \ket{\Psi} = \sum_i c_i \ket{\Psi_i}.
-\end{equation}
-The expectation value of $H$ over $\Psi$ is then 
-\begin{equation}
- \begin{aligned}
-  \matelem{\Psi}{H}{\Psi} & = \sum_{i,j} c_i c_j \matelem{\Psi_j}{H}{\Psi_i} \\
-                          & = \sum_{i,j} c_i c_j  E_i \overlap{\Psi_j}{\Psi_i} \\
-                          & = \sum_{i} |c_i|^2 E_i \\
-                          & \ge E_0
- \end{aligned}
-\end{equation}
-which gives the variational principle because of the orthogonality of eigenvectors of an \textit{Hermitian} operator. 
-Now let us decompose the same wave function $\Psi$ on the right-eigenvectors of $\tilde{H}$ 
-\begin{equation}
- \ket{\Psi} = \sum_i \tilde{c}_i \ket{\Phi_i},
-\end{equation}
-and consider the expectation value of $\tilde{H}$ over $\Psi$
-\begin{equation}
- \begin{aligned}
-  \matelem{\Psi}{\tilde{H}}{\Psi} & = \sum_{i,j} \tilde{c}_i \tilde{c}_j \matelem{\Phi_j}{\tilde{H}}{\Phi_i} \\
-                                  & = \sum_{i,j} \tilde{c}_i \tilde{c}_j E_i \overlap{\Phi_j}{\Phi_i} 
- \end{aligned}
-\end{equation}
-which has no reason to be an upper bound to $E_0$ as $\overlap{\Phi_j}{\Phi_i} \ne \delta_{i,j}$. 
-Therefore, we see that we cannot apply straightforwardly the variational principle 
-to similarity transformed Hamiltonians, because of the lack of orthonormality of the right eigenvectors.
+The paper is organized as follows. 
+In the first section, we derive the analytical form of a new Jastrow factor and the corresponding transcorrelated Hamiltonian. 
+The, we perform a detailed numerical study of the behaviour of the solution of $\tilde{H}[\mu]$ on the helium atom: 
+in the first part we analyze the speed of convergence of the ground state energy with respect to the basis set and the parameter $\mu$, 
+then we study the behaviour of the right eigenvectors in real space and compare it with the exact ground state wave function. 
+We show that the rapid convergence of the total energies coincides with a rapid convergence of the right eigenvectors in real space. 
+Based on such encouraging results, we study the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
+a value of $\mu$ which depends on the system and still provides a fast convergence of the total energies. 
+Eventually, we study the H$_2$ molecule and compare different regimes of correlation.
 
 \section{A new form of Jastrow factor for transcorrelated Hamiltonian}
-\subsection{The similarity transformed Hamiltonian}
+This section is dedicated to the derivation of a new form of Jastrow factor mimicking at short range the correlation effects of RS-DFT. 
+For the sake of simplicity and to remain as close as possible to the physical picture of the electronic correlation problem, 
+we derive the equations of the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
+Thanks to the simplicity of the equations, we focus on the behaviour at small $r_{12}$ of different flavours of Hamiltonians 
+and the corresponding discontinuity in their eigenvectors. 
+We browse three different types of Hamiltonians: the usual physical Hamiltonian, the transcorrelated Hamiltonian together with the effective Hamiltonian used in RS-DFT.
+Then, we derive the general analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$, and its dependence as function of the parameter $\mu$.
+
+\subsection{A simple physical picture: the case of the helium atom}
+\subsubsection{The transcorrelated Hamiltonian for helium atom}
 Let us write the Hamiltonian of the He atom in the ${\bf r}_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
@@
 
-\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
+\subsubsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
 \label{sec:cusp}
@@
 the constraint of fulfilling the cusp condition.
-%Another way to phrase Eq.\eqref{eq:cusp_phi_1} and Eq.\eqref{eq:cusp_phi_2} is that because of the Jastrow factor, the similarity transformed Hamiltonian exhibits an effective non-divergent electron-electron interaction, which does not impose any cusp condition to the eigenfunctions of $\tilde{H}[j]$.
 
@@
 
-\subsection{Explicit form of  $\tilde{H}[\mu]$ and some of its properties}
+\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
 \subsubsection{Explicit form of $\tilde{H}[\mu]$ }
-Having established the explicit form of $j(r_{12};\mu)$ and some of its properties, one can now 
-look at the explicit form of the transcorrelated Hamiltonian obtained with $j(r_{12};\mu)$,  
-which, by injecting the form of \eqref{eq:def_j} in Eq.\eqref{eq:ht_phi}, reads 
+Having established the analytical expression of $j(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
+According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
+\begin{equation}
+ \label{ht_def_g}
+ e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
+\end{equation}
+where $\hat{\hat{\tau}} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j} \frac{1}{r_{ij}}$. 
+This leads to the following similarity transformed Hamiltonian 
+\begin{equation}
+ \begin{aligned}
+ \label{ht_def_gu}
+ \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
+           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
+                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
+                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1  \\
+ \end{aligned}
+\end{equation}
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{L}(\bri{1},\bri{2},\bri{3}) ) = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
+                                     + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
+ \end{aligned}
+\end{equation}
+Therefore, to obtain the general formulation of the $\tilde{H}[\mu]$ one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = j(r_{12},\mu)$.
+
+\subsection{Explicit form for the operators $\hat{K}(\bri{1},\bri{2}) )$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ }
+\subsubsection{Intermediate quantities}
+To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $j(r_{12},\mu)$ with respect to a $\bri{1}$ which, after some derivation reads
+\begin{equation}
+ \label{eq:nabla_u}
+ \begin{aligned}
+ \nabla_1 u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
+ \end{aligned}
+\end{equation}
+Then, the terms $\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2$ is simply 
+\begin{equation}
+ \begin{aligned}
+ \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_2 u(\bri{1},\bri{2}) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
+ \end{aligned}
+\end{equation}
+Then, to compute the  non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ one needs to compute 
+\begin{equation}
+ \begin{aligned}
+ \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
+                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg),
+ \end{aligned}
+\end{equation}
+and as $\nabla_1 u(\br{}_1,\br{}_2) = - \nabla_2 u(\br{}_1,\br{}_2)$,   
+the total non hermitian operator in $\hat{K}(\bri{1},\bri{2})$ can be written as 
+\begin{equation}
+ \begin{aligned}
+ \label{def_non_hermit}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
+         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big)  \\
+&  +      (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg).
+ \end{aligned}
+\end{equation}
+One can notice that the form of Eq. \eqref{def_non_hermit} provides an explicit form to compute analytical integrals with Gaussian types functions. 
+Nevertheless, one can notice that as 
+\begin{equation}
+ \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
+\end{equation}
+one can write 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla0}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
+ \end{aligned}
+\end{equation}
+Then, introducing the spherical coordinate system for $\br{}_1 - \br{}_2$ in terms of ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$ and the angle $\theta$ and $\phi$, one can write 
+\begin{equation}
+ \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
+\end{equation}
+and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
+\begin{equation}
+ \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
+\end{equation}
+and therefore 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla1}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
+ = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
+ \end{aligned}
+\end{equation}
+which is a more compact expression than Eq.\eqref{def_non_hermit}
+
+The computation of the Laplacian is a little more tedious, but after some derivations it comes  
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_2}
+ &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})\\ 
+ & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
+ \end{aligned}
+\end{equation}
+\subsubsection{Explicit form of $\tilde{H}[\mu]$}
+Summing all terms to recombine $\hat{K}(\bri{1},\bri{2})$ reads 
+\begin{equation}
+ \label{eq:k_final}
+  \begin{aligned}
+   \hat{K}(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
+& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
+  \end{aligned}
+\end{equation}
+Similarly, the computation of $\hat{L}(\bri{1},\bri{2},\bri{3}) $ 
+\begin{equation}
+ \label{eq:l_final}
+ \begin{aligned}
+ \hat{L}_\mu(\bri{1},\bri{2},\bri{3}) = & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{12} \cdot \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{13} \\
+                                      + & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{21} \cdot \frac{1 - \text{erf}(\mu r_{23})}{2 r_{23}} \bri{23} \\
+                                      + & \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{31} \cdot \frac{1 - \text{erf}(\mu r_{32})}{2 r_{32}} \bri{32}
+ \end{aligned}                    
+\end{equation}
+
+Having established the explicit form of $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
+look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $j(r_{12};\mu)$,  
+which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, which gives
 \begin{equation}
@@
  \label{eq:exp_ht_mu}
-   \tilde{H}[\mu] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
-  \end{aligned}
-\end{equation}
-From Eq.\eqref{eq:exp_ht_mu}, one can define an effective scalar electron-electron interaction $\tilde{\mathcal{W}}_{ee}(r_{12}) $ 
-\begin{equation}
- \label{eq:deff_w_new}
- \tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4},
-\end{equation}
-whose shape is illustrated in Fig\ref{fig_wee_mu}. 
+   \tilde{H}[\mu] = & h_c + \sum_{i<j} \bigg( \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) + \tilde{t}[\mu] \bigg) - \sum_{i<j<k} \hat{L}_\mu(\bri{1},\bri{2},\bri{3})
+  \end{aligned}
+\end{equation}
+where $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ is a scalar effective two-body potential
+\begin{equation}
+ \begin{aligned}
+ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)  =  \frac{\text{erf}(\mu r_{ij})}{r_{ij}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{ij} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{ij}) \bigg)^2}{4}, 
+ \end{aligned}
+\end{equation}
+and $\tilde{t}[\mu]$ is non hermitian two-body differential operator 
+\begin{equation}
+ \begin{aligned}
+ \tilde{t}[\mu] =  \bigg( \text{erf}(\mu r_{ij}) - 1\bigg) \deriv{}{r_{ij}}{}.
+ \end{aligned}
+\end{equation}
+
+In order to have a pictorial representation of $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$, we illustrate in Fig\ref{fig_wee_mu} its shape for different values of $\mu$. 
 \begin{figure*}
@@
 \end{figure*}
-From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential 
+From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ 
 is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT at large $r_{12}$. 
@@
 \label{sec:h_mu_lim}
-Coming now to the limits of $\tilde{H}[\mu]$ when $\mu \rightarrow \infty$, one expects that as
+Regarding now the variation of $\tilde{H}[\mu]$, one expects as 
 \begin{equation}
@@
 \end{equation}
-one recovers the usual Hamiltonian in that limit
+one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit
 \begin{equation}
@@
 \begin{equation}
- \lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \partial{}{r_{12}}{}, 
-\end{equation}
-which means that all scalar electron-electron interaction have been replaced by a differential operator.
+ \label{eq:htilde_mu_low}
+ \begin{aligned}
+&\lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \sum_{i<j}\deriv{}{r_{ij}}{} \\
+ & - \sum_{i<j<k}  \bigg(\frac{1}{2 r_{ij}} \frac{1}{2 r_{ik}} \bri{ij} \cdot \bri{ik} + \frac{1}{2 r_{ji}} \frac{1}{2 r_{jk}} \bri{ji} \cdot \bri{jk}  + \frac{1}{2 r_{ki}} \frac{1}{2 r_{kj}} \bri{ki} \cdot \bri{kj} \bigg)
+ \end{aligned}
+\end{equation}
+which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and an attractive three electron interaction. 
+It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ of Eq.
+\eqref{eq:htilde_mu_low} is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
 
@@
 al.}\cite{UmrGon-PRA-94} which contains explicitly the $r_{12}$ coordinate and which provides a total energy accurate up to twelve digits.
-We plotted cuttings of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
-The cuttings used are the following: we set two electrons on a circle of radius $r$ from the nucleus, and use increasing values of $r$.
+We plotted a cutting of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
+The cutting used is the following: we set two electrons on a circle of radius $r=0.5$ a.u.
+from the nucleus and look at the wave functions as a function of the angle $\theta_{12}$ between the electrons.
+
 We report in Figs \ref{fig:mu_0.3_dz_3} and \ref{fig:mu_1.0_dz_3} the plot of the right eigenvector $\phimub(\br{}_1,\br{}_2)$, estimated exact wave function $\psimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ and $\mu=1.0$ (respectively) and compared to the exact wave function $\psiex(\br{}_1,\br{}_2)$ and FCI wave function for $r=0.5\,a.u.$.
@@
 \section{Study of the helium isoelectronic series}
-%\begin{table*}
-%\label{table_conv_e_mu}
-%\caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
-For H$^{-}$ and He, the basis sets used are the aug-cc-pVXZ series (X=D,T,Q) and for the Li$^+$-Ne$^{8+}$ series, the cc-pCVXZ (X=D,T,Q) basis sets with core-valence functions were used.}
-%\begin{ruledtabular}
-%\begin{tabular}{l|ccc|}
-%H-           &         &          &          \\
-%FCI          &   DZ    &  TZ      &   QZ     \\               
-%LDA          &   3.72  &    1.19  &   0.61   \\      
-%RSC          &   1.69  &    0.6   &   0.38   \\      
-%RSC/LDA      &   2.3   &    0.67  &   0.39   \\      
-%\hline       &   2.03  &    0.64  &   0.39   \\      
-%He           &         &          &          \\                              
-% FCI         &         &          &          \\        
-% LDA         &  14.18  &   3.13   &  1.19    \\     
-% RSC         &  5.28   &   0.44   &  0.12    \\     
-% RSC/LDA     &  4.87   &   0.37   &  0.12    \\     
-%\hline       &  5.07   &   0.4    &  0.12    \\     
-%Li+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  10.72  &   3.35   &  1.58    \\     
-% RSC         &  0.9    &   0.09   & -0.02    \\     
-% RSC/LDA     &  -0.82  &  -0.38   & -0.14    \\     
-%\hline       &  0.04   &  -0.12   & -0.08    \\     
-%Be2+         &         &          &          \\                                  
-% FCI         &         &          &          \\        
-% LDA         &  11.35  &   3.62   & 1.41     \\     
-% RSC         &  1.2    &   0.17   & -0.02    \\     
-% RSC/LDA     &  -1.5   &  -0.53   & -0.17    \\     
-%\hline       &  -0.08  &  -0.15   & -0.09    \\     
-%B3+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  11.91  &   4.21   &  1.53    \\     
-% RSC         &  1.41   &   0.43   &  -0.01   \\      
-% RSC/LDA     &  -2.16  &  -0.34   &  -0.22   \\      
-%\hline       &  -0.18  &   0.09   &  -0.11   \\      
-%C4+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  12.46  &   4.76   &  1.67    \\     
-% RSC         &  1.67   &   0.37   &  0.01    \\     
-% RSC/LDA     &  -2.69  &  -0.4    & -0.25    \\     
-%\hline       &  -0.19  &   0.01   &  -0.1    \\     
-%N5+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  13.1   &   5.71   &  1.79    \\     
-% RSC         &  2.06   &   0.45   &  0.01    \\     
-% RSC/LDA     &  -2.97  &  -0.64   &  -0.26   \\      
-%\hline       &  -0.01  &  -0.15   &  -0.09   \\      
-%O6+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  13.84  &   6.47   &  2.02    \\     
-% RSC         &  2.54   &   0.77   & -0.02    \\     
-% RSC/LDA     &  -3.13  &  -0.7    & -0.31    \\     
-%\hline       &  0.27   &  -0.04   & -0.12    \\     
-%F7+          &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  14.68  &   7.06   &  2.25    \\     
-% RSC         &  3.14   &   1.15   & -0.02    \\     
-% RSC/LDA     &  -3.1   &  -0.54   & -0.36    \\     
-%\hline       &  0.69   &   0.23   & -0.14    \\     
-%Ne8+         &         &          &          \\                               
-% FCI         &         &          &          \\        
-% LDA         &  15.66  &   7.61   &  2.36    \\     
-% RSC         &  3.89   &   1.57   &  0.03    \\     
-% RSC/LDA     &  -2.85  &  -0.28   & -0.35    \\     
-%\hline       &  1.26   &   0.57   & -0.1     \\     
-%\end{tabular}
-%\end{ruledtabular}
-%\end{table*}
+Having investigated the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with $\mu$ and basis set used on the helium atom, we now study the ground state energies of the isoelectronic series of the helium atom H$^{-}$ to Ne$^{8+}$.
+As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depend on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which  they  converge significantly faster with the basis set with respect to the usual Hamiltonian.
+Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on the isoelectronic series of the helium atom.
+All these systems are weakly correlated, but they cover a quite wide range of densities.
+
+\subsection{A systematic way to find an optimal value of $\mu$ }
+In order to find a systematic way to determine a reasonable value of $\mu$, one must keep in mind the physical meaning of such quantity: it has the unit of an inverse distance, and determines, at leading order, the depth of the hole imposed by the Jastrow factor.
+Therefore, it must have the typical scale of the inverse of correlation effects, which of course strongly depends on the system.
+In the context of RS-DFT, Toulouse \textit{et.
+al.}\cite{TouColSav-JCP-05} have investigated different flavour of $\mu$ varying in space through the density of the system in a given point in space.
+More specifically, they introduced (see Eq. (12) of \onlinecite{TouColSav-JCP-05}) a range separation parameter typical for correlation effects in the uniform electron gas (UEG) 
+\begin{equation}
+ \mursc({\bf r}) =  \frac{2\sqrt{\alpha / \pi}}{\sqrt{r_s({\bf r})}},
+\end{equation}
+with $\alpha = (9 \pi/4)^{-1/3}$ and $r_s = (4 \pi n/3)^{-1/3}$. 
+Such function $\mursc({\bf r})$ depends on the system and on the position in space through the density $n({\bf r})$ of the system at a given point ${\bf r}$. 
+Therefore, we propose here to use the average value of $\mursc({\bf r})$ over the Hartree Fock electronic density to define the value of $\mu$ for a specific system in a given basis set:
+\begin{equation}
+ \murscav = \frac{1}{N_e}\int \text{d}{\bf r} \mursc({\bf r}) n_{\text{HF}}({\bf r}) 
+\end{equation}
+where $n_{\text{HF}}({\bf r})$ is the HF density and $N_e$ the number of electrons in the system. 
+We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ as value of $\mu$ in $\tilde{H}[\mu]$.
+As one can observe from  Table \ref{table_conv_e_mu_iso}, the ground state energies of $\tilde{H}[\murscav]$ converge much faster than that of the usual Hamiltonian as the MAD for the ground state energies is of 2.64 mH, 0.48 mH and 0.26 mH in the double-, triple- and quadruple zeta quality basis sets (respectively) whereas it is of 12.16 mH, 4.71 mH and 1.64 mH for the usual Hamiltonian.
+Also, one can observe that, except for the low density systems such as the H${^-}$ and He species, it converges from below the exact ground state energy.
+
+In the present context, we propose the derivation of another value of $\mu$ based on the mapping of the on-top pair density of the UEG and a model built with the Jastrow factor defined by \eqref{eq:def_j}.
+For a given point in space ${\bf r}$, we estimate the 
+Assuming a single Slater determinant ansatz for a Jastrow Slater wave function with a Jastrow factor defined in \eqref{eq:def_j}, the on-top pair density is 
+\begin{equation}
+ n_2^\mu({\bf r}) = \frac{1}{2}\big(n({\bf r})\big)^2 e^{-\frac{1}{\sqrt{\pi}\mu}}
+\end{equation}
+and the exact on-top pair density can be estimated from the UEG through 
+\begin{equation}
+ n_2^{\text{UEG}}({\bf r}) = \big(n({\bf r})\big)^2g_0(n({\bf r}))
+\end{equation}
+where $g_0( n)$ is the structure factor of the UEG at a given density $n$. 
+Therefore, one can then find the value $\mu$ such that the two on-top pair density coincide
+\begin{equation}
+ \muueg({\bf r}) = \frac{\text{log}\bigg(2 g_0(n({\bf r}))\bigg) }{\sqrt{\pi}}.
+\end{equation}
+Therefore one can define an average UEG value of $\mu$.
 
 \begin{table*}
-\label{table_conv_e_mu}
+\label{table_conv_e_mu_iso}
 \caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
@@
 $\muueg$     &   1.69  &    0.60  &   0.38   &  5.28   &   0.44   &  0.12   &  0.9    &   0.09   & -0.02    \\      
-$\mursc$     &   2.30  &    0.67  &   0.39   &  4.87   &   0.37   &  0.12   &  -0.82  &  -0.38   & -0.14    \\      
+$\murscav$   &   2.30  &    0.67  &   0.39   &  4.87   &   0.37   &  0.12   &  -0.82  &  -0.38   & -0.14    \\      
 $\mursclda$  &   2.03  &    0.64  &   0.39   &  5.07   &   0.40   &  0.12   &  0.04   &  -0.12   & -0.08    \\      
@@
 $\muueg$     &  1.2    &   0.17   & -0.02    &  1.41   &   0.43   &  -0.01  &  1.67   &   0.37   &  0.01    \\  
-$\mursc$     &  -1.5   &  -0.53   & -0.17    &  -2.16  &  -0.34   &  -0.22  &  -2.69  &  -0.4    & -0.25    \\  
+$\murscav$   &  -1.5   &  -0.53   & -0.17    &  -2.16  &  -0.34   &  -0.22  &  -2.69  &  -0.4    & -0.25    \\  
 $\mursclda$  &  -0.08  &  -0.15   & -0.09    &  -0.18  &   0.09   &  -0.11  &  -0.19  &   0.01   &  -0.1    \\  
@@
 $\muueg$     &  2.06   &   0.45   &  0.01    &  2.54   &   0.77   & -0.02   &  3.14   &   1.15   & -0.02    \\  
-$\mursc$     &  -2.97  &  -0.64   &  -0.26   &  -3.13  &  -0.7    & -0.31   &  -3.1   &  -0.54   & -0.36    \\  
+$\murscav$   &  -2.97  &  -0.64   &  -0.26   & -3.13   &  -0.70   & -0.31   & -3.10   &  -0.54   & -0.36    \\  
 $\mursclda$  &  -0.01  &  -0.15   &  -0.09   &  0.27   &  -0.04   & -0.12   &  0.69   &   0.23   & -0.14    \\  
@@
 $\muueg$     &  3.89   &   1.57   &  0.03    & 4.23    &    1.11  &    0.13   &   4.23   &   1.11   &    0.13   \\   
-$\mursc$     &  -2.85  &  -0.28   & -0.35    & 2.64    &    0.48  &    0.26   &  -1.21   &  -0.28   &   -0.16   \\   
+$\murscav$   &  -2.85  &  -0.28   & -0.35    & 2.64    &    0.48  &    0.26   &  -1.21   &  -0.28   &   -0.16   \\   
 $\mursclda$  &  1.26   &   0.57   & -0.1     & 2.38    &    0.60  &    0.07   &   2.38   &   0.60   &    0.05   \\   
@@
 \section{General formulation of similarity transformed Hamiltonian}
-\subsection{General equations for a two-electron system}
-According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
-\begin{equation}
- \label{ht_def_g}
- e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
-\end{equation}
-where $\hat{\tau} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j \frac{1}{r_{ij}}}$.
-Of course, only the differential terms do not commute in Eq.
-\eqref{ht_def_g}.
-Let us compute each terms, beginning with the action of $\big[ H,\hat{\tau} \big]$ on a function $\phi(\br{}_1,\hdots \br{}_N)$.
-\begin{equation}
- \label{eq:com1_1}
- \begin{aligned}
- \bigg[ H,\hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
-  & = -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\
-  & +  \frac{1}{2} \sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \nabla^2_i \phi(\br{}_1,\hdots \br{}_N). 
- \end{aligned}
-\end{equation}
-The first term in the right-hand side of Eq. \eqref{eq:com1_1} is 
-\begin{equation}
- \label{eq:com1_2}
- \begin{aligned}
-&  -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\ 
-= &-\frac{1}{2}\sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \bigg( \nabla^2_i \phi(\br{}_1,\hdots \br{}_N)\bigg) \\
-  &-\frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
-  &-\sum_i \bigg(\nabla_i \sum_{j>k}u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).
- \end{aligned}
-\end{equation}
-Inserting Eq. \eqref{eq:com1_2} in Eq. \eqref{eq:com1_1} leads to cancellation of the terms involving $\nabla^2_i \phi(\br{}_1,\hdots \br{}_N)$
-\begin{equation}
- \label{eq:com1_3}
-  \begin{aligned}
- \big[ H,\hat{\tau} \big]\phi(\br{}_1,\hdots \br{}_N) & =  \frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
-  & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg)
- \end{aligned}
-\end{equation}
-and therefore one can write the first commutator of Eq. \eqref{ht_def_g} as 
-\begin{equation}
- \label{eq:com1_4}
- \begin{aligned}
-  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
-                            & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i  \bigg),
- \end{aligned}
-\end{equation}
-and as $\nabla_i f(\br{}_j) = \delta_{ij} \nabla_i f(\br{}_i)$ one obtains 
-\begin{equation}
- \label{eq:com1_5}
- \begin{aligned}
-  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg) \\
-                            & -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) \\
-                            & -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg).  
- \end{aligned}
-\end{equation}
-Then, one has to compute the second-order commutator in Eq. \eqref{ht_def_g}: 
-\begin{equation}
- \label{eq:com2_1}
- \begin{aligned}
- & \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] \phi(\br{}_1,\hdots \br{}_N) = \\
- & \bigg[ -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg), \sum_{j>k} u(\br{}_j,\br{}_k)  \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
-+& \bigg[ -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
-+& \bigg[ -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N). 
- \end{aligned}
-\end{equation}
-The first term in Eq. \eqref{eq:com2_1} is actually a potential term and therefore it cancels out, then it comes
-\begin{equation}
- \label{eq:com2_2}
- \begin{aligned}
-  \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 - \sum_j \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 
- \end{aligned}
-\end{equation}
-and so the two commutators become
-\begin{equation}
- \begin{aligned}
- \label{eq:comtot}
-& \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\
-   &\sum_{i>j} -\frac{1}{2} \bigg( \nabla^2_i u(\br{}_i,\br{}_j) +  \nabla^2_j u(\br{}_i,\br{}_j) 
-    + \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 + \bigg( \nabla_j u(\br{}_i, \br{}_j) \bigg)^2  \bigg) \\
-   & -\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) -\bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg). 
- \end{aligned}
-\end{equation}
-
-\section{Computations of integrals}
-\subsection{$\nabla_i u(\br{}_i,\br{}_j)$}
-\begin{equation}
- \nabla_1 u(\br{}_1,\br{}_2) = \deriv{}{x_1}{}u(r_{12}) {\bf e}_{x1} + \deriv{}{y_1}{}u(r_{12}) {\bf e}_{y1} + \deriv{}{z_1}{}u(r_{12}) {\bf e}_{z1},
+\subsection{General equations for a $N$-electron system}
+\subsubsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
+We need to compute the following integral 
+\begin{equation}
+ \label{eq:l_ijmkln}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
+ \end{aligned}
+\end{equation}
+where 
+\begin{equation}
+ \hat{L}_1(\bri{1},\bri{2},\bri{3}) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
+\end{equation}
+with 
+\begin{equation}
+ w_\mu(\bri{13}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
+\end{equation}
+Let us compute the first term of Eq. \eqref{eq:l_ijmkln}:
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
+ \end{aligned}
+\end{equation}
+Such matrix element can be further decomposed into
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
+ =& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
+ \end{aligned}
+\end{equation}
+where 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:l_1x}
+& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+ = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
+ \end{aligned}
+\end{equation}
+If we define the following function 
+\begin{equation}
+ W_{mn}^x({\bf r})  = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}) (x - x'),  
+\end{equation}
+it can be calculated easily by
+\begin{equation}
+ W_{mn}^x({\bf r})  = x \, w_{mn}({\bf r}) - w_{mn}^x({\bf r})
+\end{equation}
+with 
+\begin{equation}
+ w_{mn}({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}), 
 \end{equation}
@@
 \begin{equation}
- \deriv{}{x_1}{}u(r_{12}) = \deriv{}{r_{12}}{}u(r_{12}) \deriv{r_{12}}{x_1}{},
-\end{equation}
-and as $r_{12} = \sqrt{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2} $ one has
-\begin{equation}
- \deriv{r_{12}}{x_1}{} = \frac{x_1 - x_2}{r_{12}} = -\deriv{r_{12}}{x_2}{},
-\end{equation}
-and according to Eq. \eqref{def_j_0}
-\begin{equation}
- \deriv{u}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2},
-\end{equation}
-one obtains 
-\begin{equation}
- \label{eq:dx1_u}
- \deriv{}{x_1}{}u(r_{12}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
-\end{equation}
-Similarly, 
-\begin{equation}
- \label{eq:dx2_u}
- \deriv{}{x_2}{}u(r_{12}) = -\frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12} } \bigg(x_1 - x_2 \bigg).
-\end{equation}
-Therefore, 
-\begin{equation}
- \label{eq:nabla_u}
- \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
- & \bigg( (x_1 - x_2) {\bf e}_{x1} + (y_1 - y_2) {\bf e}_{y1} + (z_1 - z_2) {\bf e}_{z1}\bigg) \\
- &=  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big)
- \end{aligned}
-\end{equation}
-
-\subsection{$\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg)^2$}
-According to Eq. \eqref{eq:nabla_u}, one obtains 
-\begin{equation}
- \label{eq:nabla_u2_0}
- \begin{aligned}
- \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2 & = \bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg)^2\\
- & \bigg( (x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2 \bigg) \\
-                                           &  \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4 \big(r_{12}\big)^2} \times \big(r_{12}\big)^2 \\
-                                           & = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
- \end{aligned}
-\end{equation}
-and therefore 
-\begin{equation}
- \label{eq:nabla_u2}
- \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2  + \bigg(\nabla_2 u(\br{}_1,\br{}_2)\bigg)^2 = 2 \times \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
-\end{equation}
-
-\subsection{$\nabla_i u(\br{}_i,\br{}_j) \cdot \bigg( \nabla_i   \bigg)$}
-According to Eq. \eqref{eq:nabla_u}, one obtains 
-Therefore, 
-\begin{equation}
- \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
-                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg).
- \end{aligned}
-\end{equation}
-And noticing the minus sign coming from the derivative in $\br{}_2$, the total operator can be written as 
-\begin{equation}
- \begin{aligned}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
-         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big) +
-         (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg),
- \end{aligned}
-\end{equation}
-but as 
-\begin{equation}
- \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
-\end{equation}
-one can rewrite as 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla0}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
- \end{aligned}
-\end{equation}
-Then, introducing ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$, can notice that 
-\begin{equation}
- \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
-\end{equation}
-and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
-\begin{equation}
- \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
-\end{equation}
-and therefore 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla1}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
- = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{}. 
- \end{aligned}
-\end{equation}
-
-\subsection{$\nabla^2_i u(\br{}_i,\br{}_j)$}
-\begin{equation}
- \begin{aligned}
- &\nabla^2_1 u(\br{}_1,\br{}_2) =  \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{y_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{z_{1}}{2}  u(\br{}_1,\br{}_2) \\
-                                 = & \deriv{}{x_{1}}{}\bigg( \deriv{}{x_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
-                                   \deriv{}{y_{1}}{}\bigg( \deriv{}{y_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
-                                   \deriv{}{z_{1}}{}\bigg( \deriv{}{z_{1}}{}u(\br{}_1,\br{}_2) \bigg). 
- \end{aligned}
-\end{equation}
-But according to Eq. \eqref{eq:dx1_u}, one obtains 
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_0}
-& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{}\bigg(\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
-& = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
- \end{aligned}
-\end{equation}
-Similarly, according to Eq. \eqref{eq:dx2_u} one obtains for the second order derivative in $x_2$
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x2_0}
-& \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{2}}{}\bigg(\frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
-& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) -  \frac{\text{erf}(\mu r_{12}) -1}{2 r_{12}} \\
-& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12}}. 
- \end{aligned}
-\end{equation}
-Also
-\begin{equation}
- \label{eq:d2_x1_1}
- \begin{aligned}
- \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = & \deriv{}{r_{12}}{}\bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) \deriv{r_{12}}{x_1}{} \\
-      = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} 
- \end{aligned}
-\end{equation}
-and similarly
-\begin{equation}
- \label{eq:d2_x2_1}
- \begin{aligned}
- \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -  1}{2 r_{12}}  = &\deriv{}{r_{12}}{}\bigg( \frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}}\bigg) \deriv{r_{12}}{x_2}{} \\
-              = & (-1) \frac{x_1 - x_2}{r_{12}} (-1)  \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-              = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-              = & \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}},
- \end{aligned}
-\end{equation}
-which implies that 
-\begin{equation}
-  \label{eq:d2_x2_2}
- \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2).
-\end{equation}
-
-To continue, as 
-\begin{equation}
- \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = -\frac{1}{r_{12}}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg),
-\end{equation}
-one obtains 
-\begin{equation}
- \label{eq:d2_x1_2}
- \begin{aligned}
- \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} & = \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
- & =  -\frac{(x_1 - x_2)}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg). 
- \end{aligned}
-\end{equation}
-
-Therefore, Eq. \eqref{eq:d2_x1_0} becomes 
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_2}
-& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}  \\
-& = -\frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-& = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) 
-- \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
- \end{aligned}
-\end{equation}
-implying that 
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_3}
- \bigg( \deriv{}{x_{1}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{z_{1}}{2} \bigg)  u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12}\big)^2},
- \end{aligned}
-\end{equation}
-and therefore 
-\begin{equation}
- \begin{aligned}
- \label{eq:lapl_u_final}
- \bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} \bigg) u(\br{}_1,\br{}_2) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
-&- 2 \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}.
- \end{aligned}
-\end{equation}
-Therefore, 
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_2}
- &\bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{y_{2}}{2} + \deriv{}{z_{1}}{2} + \deriv{}{z_{2}}{2} \bigg) u(\br{}_1,\br{}_2) \\ 
- & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
-&- 2 \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
- & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2} \bigg) 
-- 2 \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
- & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \times 2 - 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
- & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
- \end{aligned}
-\end{equation}
-\subsection{Sum of all terms}
+  w_{mn}^x({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'})  x'.
+\end{equation}
+Then, one can rewrite the matrix element of Eq. \eqref{eq:l_1x} as
+\begin{equation}
+ \begin{aligned}
+ \label{eq:l_1x_2}
+& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
+ \end{aligned}
+\end{equation}
+which can be easily evaluated numerically. 
+Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3})$ is simply 
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
+ \end{aligned}
+\end{equation}
+which can be numerically evaluated easily. 
+The total matrix element of the full operator is then 
+\begin{equation}
+ \label{eq:l_ijmkln_final}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
+ + & \int \text{d}{\bf r}\phi_j({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
+ + & \int \text{d}{\bf r} \phi_m({\bf r})  \phi_n({\bf r}) \bigg( W_{jl}^x({\bf r}) W_{ik}^x({\bf r}) + W_{jl}^y({\bf r}) W_{ik}^y({\bf r}) + W_{jl}^z({\bf r}) W_{ik}^z({\bf r})\bigg), 
+ \end{aligned}
+\end{equation}
+which can be computed on the fly through a simple numerical integration.
+
 According to Eq.
@@
 which coincides with Eq. \eqref{eq:one_e_3}.
-\bibliography{srDFT_SC}
 
@@
 \end{equation}
+\bibliography{srDFT_SC}
 

### 2020-11-19 cusp_j/paper/paper.tex
modified paper

@@
 The paper is organized as follows. 
-In the first section, we derive the analytical form of a new Jastrow factor and the corresponding transcorrelated Hamiltonian. 
-The, we perform a detailed numerical study of the behaviour of the solution of $\tilde{H}[\mu]$ on the helium atom: 
+In the first section, inspired by the short-range behaviour of RS-DFT effective wave functions,  
+we derive the analytical form of a new Jastrow factor tuned by a unique parameter $\mu$, and discuss the physical content of such a simple Jastrow factor. 
+We show then that the corresponding transcorrelated Hamiltonian has a straightforward analytical structure, which is briefly reviewed as a function of the $\mu$ parameter. 
+Then, we perform a numerical study of the behaviour of the ground state eigenpair of $\tilde{H}[\mu]$ for the helium atom: 
 in the first part we analyze the speed of convergence of the ground state energy with respect to the basis set and the parameter $\mu$, 
-then we study the behaviour of the right eigenvectors in real space and compare it with the exact ground state wave function. 
-We show that the rapid convergence of the total energies coincides with a rapid convergence of the right eigenvectors in real space. 
-Based on such encouraging results, we study the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
+then we study the behaviour of the right eigenvectors in real space and compare it with the numerically exact ground state wave function. 
+We show that the rapid convergence of the total energies coincides with a rapid convergence of the right eigenvectors in real space, and how to recover a very good approximation of the exact ground state wave function.
+Based on such encouraging results, we study the ground state energy of the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
 a value of $\mu$ which depends on the system and still provides a fast convergence of the total energies. 
@@
 This section is dedicated to the derivation of a new form of Jastrow factor mimicking at short range the correlation effects of RS-DFT. 
-For the sake of simplicity and to remain as close as possible to the physical picture of the electronic correlation problem, 
-we derive the equations of the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
-Thanks to the simplicity of the equations, we focus on the behaviour at small $r_{12}$ of different flavours of Hamiltonians 
+For the sake of simplicity, we derive the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
+Then we focus on the behaviour at small $r_{12}$ of different flavours of Hamiltonians 
 and the corresponding discontinuity in their eigenvectors. 
 We browse three different types of Hamiltonians: the usual physical Hamiltonian, the transcorrelated Hamiltonian together with the effective Hamiltonian used in RS-DFT.
-Then, we derive the general analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$, and its dependence as function of the parameter $\mu$.
+Based on such consideration, we propose a new Jastrow factor mimicking RS-DFT Hamiltonian at small $r_{12}$. 
+Then, we derive the analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$ in the case of a general $N$-electron system, and study its physical content as a  function of the parameter $\mu$.
 
@@
 \subsubsection{The transcorrelated Hamiltonian for helium atom}
-Let us write the Hamiltonian of the He atom in the ${\bf r}_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
+Let us write the Hamiltonian of the helium atom in the $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
 \begin{equation}
@@
 \label{sec:he_j}
-Now let us consider the Similarity transformed Hamiltonian $\tilde{H}[j]$
+Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a general Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
 \begin{equation}
@@
  \begin{aligned}
- \tilde{H}[j]&= e^{-j(r_{12})} H e^{j(r_{12})},
- \end{aligned}
-\end{equation}
-where $j(r_{12})$ is a general Jastrow factor depending only on $r_{12}$. 
-Therefore, the only new terms arising in $\tilde{H}[j]$ with respect to $H$ are those coming from the differential operator in $r_{12}$,
-\begin{equation}
- \mathcal{T}[j] =  -e^{-j(r_{12})}\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg)e^{j(r_{12})}.  
-\end{equation}
-Let us compute the action of $\mathcal{T}[j]$ on a general function $\phi(\br{}_1,\br{}_2)$ 
-\begin{equation}
- \begin{aligned}
- \mathcal{T}[j]\phi(\br{}_1,\br{}_2) & =- e^{-j(r_{12})} \bigg[ \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{}\bigg]  e^{j(r_{12})} \phi(\br{}_1,\br{}_2) \\ 
-                            &=  -\deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{2} - \frac{2}{r_{12}} \deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{} \\
-  &- 2 \deriv{j(r_{12})}{r_{12}}{} \deriv{\phi(\br{}_1,\br{}_2)}{r_{12}}{} \\ 
-  &- \bigg[ \frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  + \deriv{j(r_{12})}{r_{12}}{2} + \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2\bigg] \phi(\br{}_1,\br{}_2). 
- \end{aligned}
-\end{equation}
-Now, by defining the following operators 
+ \tilde{H}[u]&= e^{-u(r_{12})} H e^{u(r_{12})}.
+ \end{aligned}
+\end{equation}
+The only additional terms arising in $\tilde{H}[u]$ with respect to $H$ are those coming from the action of the differential operator in $r_{12}$,
+\begin{equation}
+ \mathcal{T}[u] =  -e^{-u(r_{12})}\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} \bigg)e^{u(r_{12})}.  
+\end{equation}
+After some derivation, one can notice that by defining the following operators 
 \begin{equation}
  \label{eq:def_tt}
- \tilde{t}[j] = -2 \deriv{j(r_{12})}{r_{12}}{} \deriv{}{r_{12}}{},
+ \tilde{t}[u] = -2 \deriv{u(r_{12})}{r_{12}}{} \deriv{}{r_{12}}{},
 \end{equation}
@@
  \label{eq:def_wt}
- \tilde{W}[j] = -\frac{2}{r_{12}} \deriv{j(r_{12})}{r_{12}}{}  , 
+ \tilde{W}[u] = -\frac{2}{r_{12}} \deriv{u(r_{12})}{r_{12}}{}  , 
 \end{equation}
@@
  \label{eq:def_wt}
- \tilde{w}[j] = -\deriv{j(r_{12})}{r_{12}}{2} - \bigg( \deriv{j(r_{12})}{r_{12}}{} \bigg)^2. 
+ \tilde{w}[u] = -\deriv{u(r_{12})}{r_{12}}{2} - \bigg( \deriv{u(r_{12})}{r_{12}}{} \bigg)^2, 
 \end{equation}
@@
 \begin{equation}
- \label{eq:ht_phi}
- \tilde{H}[j] = h_c + \frac{1}{r_{12}}  + \tilde{W}[j] + \tilde{t}[j] + \tilde{w}[j] ,
-\end{equation}
-ore more explicitly 
-\begin{equation}
- \tilde{H}[j] = h_c + \frac{1}{r_{12}}\bigg( 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg) + \tilde{t}[j] + \tilde{w}[j] .
-\end{equation}
-$\tilde{H}[j]$, because of the first-order differential operator in $\tilde{t}[j]$, is then non-hermitian,   
-and the effective potential $ \frac{1}{r_{12}}  + \tilde{W}[j] + \tilde{w}[j]$ in $\tilde{H}[j]$ only depends on the shape of $j(r_{12})$.
+ \label{eq:ht_general}
+ \tilde{H}[u] = h_c + \frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] + \tilde{t}[u] ,
+\end{equation}
+Therefore, one can see from Eq.
+\eqref{eq:ht_general} that the two electrons experience a modified scalar potential given by $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u]$, and an additional differential operator $\tilde{t}[u]$,
+the latter making $\tilde{H}[u]$ non-hermitian.
 
@@
 \label{sec:cusp}
-Having established the general form of the transcorrelated Hamiltonian $\tilde{H}[j]$, in the case of the helium atom, one can then study the behaviour of the latter when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
-The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different conditions that the eigenvectors of such operators must fulfill.
+Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
+The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill.
 For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are general for any bounded eigenvectors.
@@
 \end{equation}
-or equivalently by multiplying by $r_{12}$
+or equivalently by multiplying Eq. \eqref{eq:cusp_0} by $r_{12}$
 \begin{equation}
@@
 \end{equation} 
-For a pedagogical and general introduction to the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.
+For an excellent pedagogical and general derivation of the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.
 
@@
  \label{eq:hpi0_ex}
- \tilde{H}[j] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
-\end{equation}
-Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[j]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
-which involves also the term $\tilde{W}[j]$ in $\tilde{H}[j]$ (see Eq.\eqref{eq:def_wt} and \eqref{eq:ht_phi}.
-Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
+ \tilde{H}[u] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
+\end{equation}
+Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
+which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
 \begin{equation}
  \label{eq:cusp_phi_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{j(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
-\end{equation}
-Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{j(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction modified by the presence of the Jastrow factor in $\tilde{H}[j]$.
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{u(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
+\end{equation}
+Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
 Therefore, as long as one imposes that 
@@
  \label{eq:cusp_phi_1}
-  \deriv{j(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
-\end{equation}
-which is nothing but the cusp condition for the Jastrow factor $j(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then obtain a non-divergent effective electron-electron interaction.
+  \deriv{u(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
+\end{equation}
+which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
 Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
@@
 \end{equation}
-which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[j]$ are cuspless. 
-For instance, a simple Jastrow factor of the form $j(r_{12}) = \frac{1}{2} r_{12}$ release $\phiex(\br{}_1,\br{}_2)$ from 
+which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[u]$ is cuspless. 
+For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
 the constraint of fulfilling the cusp condition.
@@
 where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively.
-The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ gives back the usual Kohn-Sham theory.
+The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ it gives back the usual Kohn-Sham theory.
 In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
@@
 \end{equation}
-and as the long-range interaction is non divergent at $r_{12}=0$ as long as $\mu$ remains finite 
+and as the effective interaction $\frac{\text{erf}(\mu r_{12})}{r_{12}}$ is non divergent at $r_{12}=0$ for finite values of $\mu$
 \begin{equation}
@@
 
-\subsection{A new form of Jastrow factor $j(\mu,r_{12})$ mimicking a long-range interaction}
+\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
 In section \ref{sec:cusp} we reviewed the forms of limit conditions at $r_{12}=0$ involved in different eigenvalue equations, which of course depends on the nature of the interaction at $r_{12}=0$. 
-In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order.
-\subsubsection{The working equation for $j(\mu,r_{12})$ }
-Eq. \eqref{eq:ht_phi} gives the similarity transformed Hamiltonian for an arbitrary Jastrow factor, 
-and with respect to the usual Hamiltonian, $\tilde{H}[j]$ contains two new classes of terms: 
-a new electron-electron potential $\tilde{w}[j]+ \tilde{W}[j]$ and a new differential operator  $\tilde{t}[j]$. 
-Of course, these new terms depends on the explicit form of the Jastrow factor $j(r_{12})$ chosen. 
-Now, we impose the form of $j(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction of RS-DFT. 
+In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order in $1/r_{12}$.
+\subsubsection{The working equation for $u(\mu,r_{12})$ }
+Eq. \eqref{eq:ht_general} gives the similarity transformed Hamiltonian for an arbitrary Jastrow factor, 
+and with respect to the usual Hamiltonian, $\tilde{H}[u]$ contains two new classes of terms: 
+a new electron-electron potential $1/r_{12} + \tilde{w}[u]+ \tilde{W}[u]$ and a new differential operator  $\tilde{t}[u]$. 
+Of course, these new terms depends on the explicit form of the Jastrow factor $u(r_{12})$ chosen. 
+Now, we impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction of RS-DFT. 
 Mathematically, this conditions implies that 
@@
  \label{def_j_00}
- \tilde{W}[j] + \frac{1}{r_{12}}&= \frac{\text{erf}(\mu r_{12})}{r_{12}} \\ 
-\Leftrightarrow -\frac{2}{r_{12}} \deriv{j(r_{12},\mu)}{r_{12}}{} + \frac{1}{r_{12}} & = \frac{\text{erf}(\mu r_{12})}{r_{12}}, 
+ \tilde{W}[u] + \frac{1}{r_{12}}&= \frac{\text{erf}(\mu r_{12})}{r_{12}} \\ 
+\Leftrightarrow -\frac{2}{r_{12}} \deriv{u(r_{12},\mu)}{r_{12}}{} + \frac{1}{r_{12}} & = \frac{\text{erf}(\mu r_{12})}{r_{12}}, 
  \end{aligned}
@@
  \label{def_j_0}
- \deriv{j(r_{12},\mu)}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2}.
+ \deriv{u(r_{12},\mu)}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2}.
 \end{equation}
@@
  \label{eq:def_j}
- j(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2},
+ u(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2},
 \end{equation}
 which depends on a unique parameter $\mu$, 
-and the associated transcorrelated Hamiltonians obtained with $j(r_{12};\mu)$ is also controlled by $\mu$
+and the associated transcorrelated Hamiltonians obtained with $u(r_{12};\mu)$ is also controlled by $\mu$
 \begin{equation}
  \label{eq:def_ht_mu}
- \tilde{H}[\mu] = e^{-j(r_{12};\mu)} H e^{j(r_{12};\mu)}. 
+ \tilde{H}[\mu] = e^{-u(r_{12};\mu)} H e^{u(r_{12};\mu)}. 
 \end{equation}
@@
 
-\subsubsection{A few properties of $j(r_{12};\mu)$}
-The new Jastrow $j(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which controls the value of the leading term of the effective interaction at $r_{12}=0$ (see Eq.\eqref{def_j_00}). 
-To understand the physical content together with the mathematical properties of $j(r_{12};\mu)$, 
+\subsubsection{A few properties of $u(r_{12};\mu)$}
+The new Jastrow $u(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which controls the value of the leading term of the effective interaction at $r_{12}=0$ (see Eq.\eqref{def_j_00}). 
+To understand the physical content together with the mathematical properties of $u(r_{12};\mu)$, 
 one must keep in mind that the complete correlating factor $\mathcal{J}(r_{12};\mu)$ is 
 \begin{equation}
- \mathcal{J}(r_{12};\mu) = \text{exp}\bigg(j(r_{12};\mu)\bigg),
+ \mathcal{J}(r_{12};\mu) = \text{exp}\big(u(r_{12};\mu)\big),
 \end{equation}
@@
 \begin{equation}
- \lim_{r_{12} \rightarrow \infty}j(r_{12};\mu) = 0,
+ \lim_{r_{12} \rightarrow \infty}u(r_{12};\mu) = 0,
 \end{equation}
@@
 \end{equation}
-and therefore $j(r_{12};\mu)$ impacts only the small $r_{12}$ behaviour,  
-which is expected since the equation determining $j(r_{12},\mu)$ is obtained from the small $r_{12}$ limit of the Schroedinger equation (see Eq.\eqref{def_j_00}).
+and therefore $u(r_{12};\mu)$ impacts only the small $r_{12}$ behaviour,  
+which is expected since the equation determining $u(r_{12},\mu)$ is obtained from the small $r_{12}$ limit of the Schroedinger equation (see Eq.\eqref{def_j_00}).
 
 To better understand the physical content of at $r_{12}\approx 0$,  
-let us Taylor expand the function $j(r_{12};\mu)$ 
+let us Taylor expand the function $u(r_{12};\mu)$ 
 \begin{equation}
  \label{eq:j_dl}
- j(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + o(r_{12}^4).
+ u(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + o(r_{12}^4).
 \end{equation}
@@
 \end{equation}
-Therefore, one can Taylor expand the exact wave function in the vicinity of $\br{}_1$ for small $r_{12}$, and noticing that $\phiex(\br{}_1,\br{}_2) $ is cusp less, one obtains 
-\begin{equation}
- \label{eq:psi0_ex_dl}
- \psiex(\br{}_1,\br{}_2) = \phiex(\br{}_1,\br{}_1)e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2} + o(r_{12}^4) .
-\end{equation}
-As one can see from Eq.\eqref{eq:bigJ_dl} and Eq.\eqref{eq:psi0_ex_dl}, the first term $e^{-\frac{1}{2\sqrt{\pi}\mu}}$ defines the depth of the Coulomb hole induced by the correlating factor $\mathcal{J}(r_{12};\mu)$ at $r_{12}=0$.
-This term is imposed by the term $- \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2}$ in the Jastrow factor. 
-Therefore, the probability of finding two electrons at $r_{12}=0$ (\textit{i.e.} the on-top pair density) is larger for $\phiex(\br{}_1,\br{}_2)$ than for $\psiex(\br{}_1,\br{}_2)$.  
-This can be easily understood noticing that, by construction, $\tilde{H}[\mu]$ does not contain any divergent potential term at $r_{12}=0$, and therefore the electrons repels less each other in  $\tilde{H}[\mu]$.
-
-The second term in \eqref{eq:bigJ_dl} is linked to the cusp condition. 
-Indeed, as shown in section \ref{sec:cusp}, $\phiex(\br{}_1,\br{}_2)$ does not have a cusp, and therefore $\mathcal{J}(r_{12};\mu)$ mus restore it.
-This term is imposed by the term $\frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg)$ in the Jastrow factor.
-The last term in Eq.\eqref{eq:bigJ_dl} modifies the curvature of the Coulomb hole.
-
-Coming now to the behaviour of $j(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$.
+From Eq.
+\eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, the effective wave function  $\phiex(\br{}_1,\br{}_2)$ has necessary a larger value at coalescence (\textit{i.e.} $\br{}_1=\br{}_2)$), which can be intuitively understood as the electrons in $\tilde{H}[\mu]$ experience an effective non divergent interaction;
+b) the term in $e^{ \frac{1}{2}r_{12}} $ restores exactly the lack of cusp of $\phiex(\br{}_1,\br{}_2)$ (see Eq.
+\eqref{eq:cusp_phi_2}); and eventually last term reshapes the curvature of the $\phiex(\br{}_1,\br{}_2)$.
+
+Coming now to the behaviour of $u(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$.
 \begin{figure*}
@@
         \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
-        \caption{Shape of $j(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(j(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
+        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
 \end{figure*}
-From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $j(r_{12};\mu)$, ii) the larger the $\mu$, the closer $j(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
+From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
 
@@
 \subsubsection{Explicit form of $\tilde{H}[\mu]$ }
-Having established the analytical expression of $j(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
+Having established the analytical expression of $u(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
 According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
@@
 \end{equation}
-where $\hat{\hat{\tau}} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j} \frac{1}{r_{ij}}$. 
+where $\hat{\tau} = \sum_{i<j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
 This leads to the following similarity transformed Hamiltonian 
@@
  \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
-           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
- \end{aligned}
-\end{equation}
-where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
+           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{u}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{u},\bri{k}),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{u})$ and $\hat{L}(\bri{i},\bri{u},\bri{k})$ are defined as
 \begin{equation}
@@
                                                + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
-                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1  \\
+                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1,
  \end{aligned}
@@
 \end{equation}
-Therefore, to obtain the general formulation of the $\tilde{H}[\mu]$ one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = j(r_{12},\mu)$.
+Therefore, to obtain the analytical expression of the $\tilde{H}[\mu]$ for a general $N$-electron system, 
+one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = u(r_{12},\mu)$.
 
@@
 \subsubsection{Intermediate quantities}
-To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $j(r_{12},\mu)$ with respect to a $\bri{1}$ which, after some derivation reads
+To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to a $\bri{1}$ which reads 
 \begin{equation}
@@
 \end{equation}
-Then, the terms $\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2$ is simply 
+Then, the term $\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2$ is simply 
 \begin{equation}
@@
 \end{equation}
-Then, to compute the  non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ one needs to compute 
+Then, the non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ contains 
 \begin{equation}
@@
  \label{eq:nabla_i_nabla1}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
+ \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
  = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
@@
  &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})\\ 
- & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
+ & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
  \end{aligned}
@@
 Having established the explicit form of $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
-look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $j(r_{12};\mu)$,  
+look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $u(r_{12};\mu)$,  
 which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, which gives
@@
 \end{equation}
-where $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ is a scalar effective two-body potential
+where $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ is the scalar effective two-body potential of  $\tilde{H}[\mu]$
 \begin{equation}
@@
 \end{equation}
-and $\tilde{t}[\mu]$ is non hermitian two-body differential operator 
+and $\tilde{t}[\mu]$ is a non hermitian two-body differential operator 
 \begin{equation}
@@
 from the long-range interaction at small $r_{12}$, 
-and it is not monotonic as it can be even slightly attractive for small values of $\mu$. 
-This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $j(r_{12},\mu)$ (see Eqs.\eqref{def_j_00} and \eqref{def_j_0}).
+and it is not monotonic and attractive (\textit{i.e.} $\lim_{r_{12} \rightarrow 0} \deriv{}{r_{12}}{} \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) >0 $). 
+This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $u(r_{12},\mu)$ (see Eqs.\eqref{def_j_00} and \eqref{def_j_0}).
 If one desires to impose that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}}$, one would have to solve the non-linear differential equation 
 \begin{equation}
- 2 \deriv{j(r_{12})}{r_{12}}{} + r_{12} \bigg( \deriv{j(r_{12})}{r_{12}}{2} + \bigg[ \deriv{j(r_{12})}{r_{12}}{} \bigg]^2\bigg) = 1 - \text{erf}(\mu r_{12}), 
+ 2 \deriv{u(r_{12})}{r_{12}}{} + r_{12} \bigg( \deriv{u(r_{12})}{r_{12}}{2} + \bigg[ \deriv{u(r_{12})}{r_{12}}{} \bigg]^2\bigg) = 1 - \text{erf}(\mu r_{12}), 
 \end{equation}
@@
 \label{sec:h_mu_lim}
-Regarding now the variation of $\tilde{H}[\mu]$, one expects as 
+Regarding now the variation of $\tilde{H}[\mu]$, one expects that as 
 \begin{equation}
  \label{eq:lim_mu_0}
- \lim_{\mu  \rightarrow \infty }j(\mu,r_{12}) = 0, 
-\end{equation}
-one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit
+ \lim_{\mu  \rightarrow \infty }u(\mu,r_{12}) = 0, 
+\end{equation}
+one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit:
 \begin{equation}
@@
 which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
+
 Nevertheless, as the right hand side of Eq.\eqref{eq:lim_mu_4} contains a Delta distribution, it must be considered in the sense of distributions an not point wise. 
-Therefore, considering $f(\br{}_1,\br{}_2)$, a bounded generic square integrable function in $\R^6$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
+Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
 \begin{equation}
@@
  \begin{aligned}
-& \matelem{f}{H}{f} = \lim_{\mu \rightarrow \infty} \matelem{f}{\tilde{H}[\mu]}{f} \\
+& \matelem{\psi}{H}{\psi} = \lim_{\mu \rightarrow \infty} \matelem{\psi}{\tilde{H}[\mu]}{\psi} \\
 & \Leftrightarrow H = \tilde{H}[\mu],
@@
  \label{eq:lim_mu_6}
- \int \text{d}\br{}_1 \text{d}\br{}_2 f(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
-\end{equation}
-To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$ and show that
-\begin{equation}
- \int \text{d}\br{}_1 \text{d}\br{}_2 f(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{f}(r_{12}) \delta(r_{12}) r_{12}^2 
-\end{equation}
-where $\tilde{f}(x)$ is the function $f(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
+\end{equation}
+To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
+\begin{equation}
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 
+\end{equation}
+where $\tilde{n_2}(x)$ is the function $n_2(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
 $|\br{}_1-\br{}_2| = x$. 
-As the $f(\br{}_1,\br{}_2)$ remain finite for all $(\br{}_1,\br{}_2)$, the function $\tilde{f}(x)$ 
-do not diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
-\begin{equation}
- \int \text{d}r{}_{12}  \tilde{f}(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
-\end{equation}
-and therefore Eq.\eqref{eq:lim_mu_6} which implies Eq.\eqref{eq:lim_mu_1}.
+As the pair density $n_2(\br{}_1,\br{}_2)$ remains finite and is integrable, the function $\tilde{n}_2(x)$ 
+cannot diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
+\begin{equation}
+ \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
+\end{equation}
+which implies Eq.\eqref{eq:lim_mu_1}.
 
@@
 &\lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \sum_{i<j}\deriv{}{r_{ij}}{} \\
- & - \sum_{i<j<k}  \bigg(\frac{1}{2 r_{ij}} \frac{1}{2 r_{ik}} \bri{ij} \cdot \bri{ik} + \frac{1}{2 r_{ji}} \frac{1}{2 r_{jk}} \bri{ji} \cdot \bri{jk}  + \frac{1}{2 r_{ki}} \frac{1}{2 r_{kj}} \bri{ki} \cdot \bri{kj} \bigg)
- \end{aligned}
-\end{equation}
-which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and an attractive three electron interaction. 
-It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ of Eq.
-\eqref{eq:htilde_mu_low} is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
-
-At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent but can be either repulsive or attractive at small $r_{12}$.
+ & - \frac{1}{4}\sum_{i<j<k}  \bigg(\frac{\bri{ij} }{ r_{ij}} \cdot \frac{\bri{ik} }{ r_{ik}} + \frac{\bri{ji} }{ r_{ji}} \cdot \frac{\bri{jk}  }{ r_{jk}} + \frac{\bri{ki} }{ r_{ki}} \cdot  \frac{\bri{kj} }{ r_{kj}} \bigg),
+ \end{aligned}
+\end{equation}
+which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and a three electron interaction. 
+It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
+
+At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent, and can be repulsive or attractive at small $r_{12}$.
 One can therefore notice the diversity of physical content of $\tilde{H}[\mu]$ as a function of a unique parameter, $\mu$.
 Nevertheless, due to the property of the similarity transformation, in the limit of a complete basis set, the eigenvalues of $\tilde{H}[\mu]$, whatever the value of $\mu$ chosen, coincide with that of the physical Hamiltonian.
-An important point then is the convergence with respect to the basis set of the family of $\tilde{H}[\mu]$ for different values of $\mu$.
+An important point then is the convergence with respect to the basis set of the family of $\tilde{H}[\mu]$ for different values of $\mu$, which is tested for wide variety of two-electron systems in the next sections.
 
@@
 and so will the right eigenvectors $\ket{\phiimub}$ and the corresponding eigenvalues $E_i^{\basis}[\mu]$. 
-Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $j(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
+Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $u(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
 \subsection{$\mu$ dependence of the convergence of the ground state eigenvalue with respect to the basis set }
@@
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
-We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\Phi_\mu$ (\textit{i.e.} $\Phi_\mu$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
+We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
 %The study was performed using the augmented Dunning basis aug-cc-pVXZ (X=D,T,Q,5), hereafter referred as AVXZ.
@@
 \label{sec:total_e}
-We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_0^\mu$ of $\tilde{H}[\mu]$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
+We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_i^{\basis}[\mu]$ of $\tilde{H}[\mu]^{\basis}$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
 Several observations can be done from these data.
 First, because of the loose of the variational principle, $E_0^{\mu}$ can take values below the exact non relativistic energy, and the smaller the $\mu$, the more pronounced is such effect.
-Nevertheless, one can also observe that, for each $\mu$, the error with respect to the reference energy gets smaller  
+Nevertheless, one can also observe that, for each $\mu$, the error with respect to the exact energy gets smaller  
 when enlarging the basis set.
@@
 For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
-Therefore one can conclude that the use of the Jastrow factor $j(r_{12};\mu)$ in the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$.
+Therefore one can conclude that the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$.
 \begin{figure*}
@@
 \subsection{Study of the ground state eigenvector in real space}
-In Sec.\ref{sec:total_e} we shown the strong improvement of the speed of convergence of the total energy for the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
+In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_i^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
@@
 
-Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = H$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
-If one focusses now on the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$, it is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $j(r_{12},\mu)$ through
-\begin{equation}
- \psiex(\br{}_1,\br{}_2) =  \frac{1}{\sqrt{\mathcal{N}^{\mu}}} e^{j(r_{12},\mu)} \phimu(\br{}_1,\br{}_2), 
+Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = \tilde{H}[\mu]$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
+If one focusses now on the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$, it is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through
+\begin{equation}
+ \psiex(\br{}_1,\br{}_2) =  \frac{1}{\sqrt{\mathcal{N}^{\mu}}} e^{u(r_{12},\mu)} \phimu(\br{}_1,\br{}_2), 
 \end{equation}
@@
 \begin{equation}
-  \mathcal{N}^{\mu} = \matelem{\phimu}{e^{2 j(r_{12},\mu)}}{\phimu}.
-\end{equation}
-Therefore, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to estimate the exact ground state wave function $\psiex$ through 
-\begin{equation}
- \psimub(\br{}_1,\br{}_2) = \frac{1}{\sqrt{\mathcal{N}_{\basis}^{\mu}}}e^{j(r_{12},\mu)}\phimub(\br{}_1,\br{}_2)
+  \mathcal{N}^{\mu} = \matelem{\phimu}{e^{2 u(r_{12},\mu)}}{\phimu}.
+\end{equation}
+Therefore, in a given basis set $\basis$, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to estimate the exact ground state wave function $\psiex$ through 
+\begin{equation}
+ \psimub(\br{}_1,\br{}_2) = \frac{1}{\sqrt{\mathcal{N}_{\basis}^{\mu}}}e^{u(r_{12},\mu)}\phimub(\br{}_1,\br{}_2),
 \end{equation}
@@
 \begin{equation}
-  \mathcal{N}_{\basis}^{\mu} = \matelem{\phimub}{e^{2 j(r_{12},\mu)}}{\phimub}.
-\end{equation}
-Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also observed from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$. 
+  \mathcal{N}_{\basis}^{\mu} = \matelem{\phimub}{e^{2 u(r_{12},\mu)}}{\phimub}.
+\end{equation}
+Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$, in the $L^2$ sense for instance.
 For this study, we approximate the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$ of the helium atom by the wave function developed by Umrigar \textit{et.
@@
 The cutting used is the following: we set two electrons on a circle of radius $r=0.5$ a.u.
-from the nucleus and look at the wave functions as a function of the angle $\theta_{12}$ between the electrons.
+from the nucleus and look at the wave functions as a function of the angle $\theta_{12}$ between the $\bri{1}$ and $\bri{2}$.
 
@@
 i) the right eigenvector $\phimub(\br{}_1,\br{}_2)$ converges faster than the FCI wave function with respect to the basis set, 
-ii) that for $\mu=0.3$ the wave function $\phimub(\br{}_1,\br{}_2)$ present a maximum at $r_{12}=0$, whereas for $\mu=1.0$ and the FCI wave function it has a minimum, 
+ii) that for $\mu=0.3$ the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$, whereas for $\mu=1.0$ it has a minimum at coalescence just as the FCI wave function, 
 iii) the wave function $\phimub(\br{}_1,\br{}_2)$ is always larger that the FCI one when $r_{12}\approx 0$. 
@@
 
-i) The shape of the Jastrow factor $j(r_{12};\mu)$ leading to the transcorrelated Hamiltonian is such that as long as $\mu < \infty$, the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ in $\tilde{H}[\mu]$ is non divergent, and therefore its eigenfunctions do not have to fulfill the cusp condition which leads to a faster convergence with $\basis$.
+i) The shape of the Jastrow factor $u(r_{12};\mu)$ leading to the transcorrelated Hamiltonian is such that as long as $\mu < \infty$, the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ in $\tilde{H}[\mu]$ is non divergent, and therefore its eigenfunctions do not have to fulfill the cusp condition which leads to a faster convergence with $\basis$.
 Nevertheless, one can also remark that for $\mu > 0.5$, the speed of convergence deteriorates as $\mu$ increases, even though it remains finite.
@@
 \begin{equation}
+ \label{eq:mu_av_rsc}
  \murscav = \frac{1}{N_e}\int \text{d}{\bf r} \mursc({\bf r}) n_{\text{HF}}({\bf r}) 
@@
 In the present context, we propose the derivation of another value of $\mu$ based on the mapping of the on-top pair density of the UEG and a model built with the Jastrow factor defined by \eqref{eq:def_j}.
-For a given point in space ${\bf r}$, we estimate the 
 Assuming a single Slater determinant ansatz for a Jastrow Slater wave function with a Jastrow factor defined in \eqref{eq:def_j}, the on-top pair density is 
@@
 \end{equation}
-Therefore one can define an average UEG value of $\mu$.
+Therefore one can define an average UEG value of $\mu$ 
+\begin{equation}
+ \label{eq:mu_av_ueg}
+ \muuegav = \frac{1}{N_e}\int \text{d}{\bf r} \muueg({\bf r}) n_{\text{HF}}({\bf r}).
+\end{equation}
+We report in Table \ref{table_conv_e_mu_iso} for different basis sets the error with respect to the exact ground state energy of $E_0^{\basis}[\muuegav]$ for the isoelectronic series studied here. 
+From these data, one can see that MAD is sensibly the same than that with the $\murscav$ but with a MSD of opposite sign with respect to the latter.
+This implies that the values of $\muuegav$ are in general larger than that of $\murscav$, which was observed in the present calculations.
+Because the MAD are essentially the same but that the MSD are of opposite sign, it means that there exists an optimal value of $\mu$ between $\murscav$ and $\muuegav$ which might be optimal. 
+Therefore, we propose to define the average between $\murscav$ and $\muuegav$ 
+\begin{equation}
+ \label{eq:mu_av_ueg_rsc}
+  \mursclda = \frac{\murscav   +   \muuegav }{2},
+\end{equation}
+and the results obtained are represented in Table \ref{table_conv_e_mu_iso}.
+From this data, one can clearly see that $\mursclda$ gives a better MAD and MSD as it is below 1 mH from the aug-cc-pVDZ basis set and still improve when enlarging the basis set.
 
@@
  FCI         &  15.66  &   7.61   &  2.36    & 12.16   &    4.71  &    1.64   &  12.16   &   4.71   &    1.64   \\   
-$\muueg$     &  3.89   &   1.57   &  0.03    & 4.23    &    1.11  &    0.13   &   4.23   &   1.11   &    0.13   \\   
+$\muueg$     &  3.89   &   1.57   &  0.03    & 2.38    &    0.60  &    0.07   &   2.38   &   0.60   &    0.07   \\   
 $\murscav$   &  -2.85  &  -0.28   & -0.35    & 2.64    &    0.48  &    0.26   &  -1.21   &  -0.28   &   -0.16   \\   
-$\mursclda$  &  1.26   &   0.57   & -0.1     & 2.38    &    0.60  &    0.07   &   2.38   &   0.60   &    0.05   \\   
+$\mursclda$  &  1.26   &   0.57   & -0.1     & 0.98    &    0.24  &    0.13   &   0.89   &   0.15   &   -0.03   \\   
 \end{tabular}
@@
 \end{table*}
-\section{General formulation of similarity transformed Hamiltonian}
-\subsection{General equations for a $N$-electron system}
-\subsubsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
+
+\section{Computation of integrals}
+\subsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
 We need to compute the following integral 
@@
  & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
  &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
@@
 & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
  &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
@@
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
- + & \int \text{d}{\bf r}\phi_j({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
+ + & \int \text{d}{\bf r}\phi_u({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
  + & \int \text{d}{\bf r} \phi_m({\bf r})  \phi_n({\bf r}) \bigg( W_{jl}^x({\bf r}) W_{ik}^x({\bf r}) + W_{jl}^y({\bf r}) W_{ik}^y({\bf r}) + W_{jl}^z({\bf r}) W_{ik}^z({\bf r})\bigg), 
@@
 \eqref{eq:nabla_u2} and Eq.
-\eqref{eq:lapl_u_final}, the additional terms arising from the commutators in $\tilde{H}[j]$ are (for a two-electron system)
+\eqref{eq:lapl_u_final}, the additional terms arising from the commutators in $\tilde{H}[u]$ are (for a two-electron system)
 \begin{equation}
@@
   \begin{aligned}
-   \tilde{H}[j] = & \sum_{i = 1,2} \bigg( -\frac{1}{2} \big(\nabla_i\big)^2 + v(\br{}_i)  \bigg) + \frac{1}{r_{12}} \\
+   \tilde{H}[u] = & \sum_{i = 1,2} \bigg( -\frac{1}{2} \big(\nabla_i\big)^2 + v(\br{}_i)  \bigg) + \frac{1}{r_{12}} \\
 &   -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
@@
   \begin{aligned}
-   \tilde{H}[j] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
+   \tilde{H}[u] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
 & + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
@@
 \section{New form of jastrow factor}
-We want the jastrow factor $j(r_{12})$ to fulfil such equation
-\begin{equation}
- - \bigg[ \frac{2}{r_{12}} \deriv{j}{r_{12}}{}  + \deriv{j}{r_{12}}{2} \bigg] + \frac{1}{r_{12}} = \frac{\text{erf}\big( \mu r_{12} \big)}{r_{12}}.
+We want the jastrow factor $u(r_{12})$ to fulfil such equation
+\begin{equation}
+ - \bigg[ \frac{2}{r_{12}} \deriv{u}{r_{12}}{}  + \deriv{u}{r_{12}}{2} \bigg] + \frac{1}{r_{12}} = \frac{\text{erf}\big( \mu r_{12} \big)}{r_{12}}.
 \end{equation}
@@
 \begin{equation}
- j(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2} + \frac{1}{4 r_{12}} \bigg(c_1 - \frac{\text{erf}\big(\mu r_{12} \big)}{\mu^2} \bigg).
+ u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2} + \frac{1}{4 r_{12}} \bigg(c_1 - \frac{\text{erf}\big(\mu r_{12} \big)}{\mu^2} \bigg).
 \end{equation}
@@
 \begin{equation}
- \lim_{r_{12} \rightarrow 0 } j(r_{12}) < \infty,
+ \lim_{r_{12} \rightarrow 0 } u(r_{12}) < \infty,
 \end{equation}
@@
 \begin{equation}
- j(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2}  - \frac{\text{erf}\big(\mu r_{12} \big)}{4 \mu^2 r_{12}}.
+ u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2}  - \frac{\text{erf}\big(\mu r_{12} \big)}{4 \mu^2 r_{12}}.
 \end{equation}
@@
  \begin{aligned}
- & -\frac{1}{2}e^{-j(r)}\big(\deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) e^{j(r)}\phi(r)  = \\
+ & -\frac{1}{2}e^{-u(r)}\big(\deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) e^{u(r)}\phi(r)  = \\
  & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) \phi(r) \\
- &-\deriv{j(r)}{r}{}\deriv{}{r}{}\phi(r) \\
- &-\frac{1}{r}\deriv{j(r)}{r}{}\phi(r)  - \frac{1}{2}\deriv{j(r)}{r}{2}\phi(r)  -  \frac{1}{2}\bigg(\deriv{j(r)}{r}{} \bigg)^2 \phi(r).
- \end{aligned}
-\end{equation}
-Therefore the full similarity transformed Hamiltonian $\tilde{H}[j]$ is 
+ &-\deriv{u(r)}{r}{}\deriv{}{r}{}\phi(r) \\
+ &-\frac{1}{r}\deriv{u(r)}{r}{}\phi(r)  - \frac{1}{2}\deriv{u(r)}{r}{2}\phi(r)  -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2 \phi(r).
+ \end{aligned}
+\end{equation}
+Therefore the full similarity transformed Hamiltonian $\tilde{H}[u]$ is 
 \begin{equation}
@@
  \label{eq:one_e_0}
- & e^{-j(r)}H\,e^{j(r)} = \\
- & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) -\deriv{j(r)}{r}{}\deriv{}{r}{}\\
- &-\frac{1}{r}\bigg(\deriv{j(r)}{r}{} + Z \bigg) \\ 
- & - \frac{1}{2}\deriv{j(r)}{r}{2} -  \frac{1}{2}\bigg(\deriv{j(r)}{r}{} \bigg)^2.
- \end{aligned}
-\end{equation}
-Similarly to what have been proposed in Section \ref{sec:he_j}, we want to find the Jastrow factor $j(r,\mu,Z)$ such that 
+ & e^{-u(r)}H\,e^{u(r)} = \\
+ & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) -\deriv{u(r)}{r}{}\deriv{}{r}{}\\
+ &-\frac{1}{r}\bigg(\deriv{u(r)}{r}{} + Z \bigg) \\ 
+ & - \frac{1}{2}\deriv{u(r)}{r}{2} -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2.
+ \end{aligned}
+\end{equation}
+Similarly to what have been proposed in Section \ref{sec:he_j}, we want to find the Jastrow factor $u(r,\mu,Z)$ such that 
 \begin{equation}
  \label{eq:one_e_01}
- -\frac{1}{r}\bigg(\deriv{j(r,\mu,Z)}{r}{} + Z \bigg) = -Z\frac{\text{erf}(\mu r)}{r},
+ -\frac{1}{r}\bigg(\deriv{u(r,\mu,Z)}{r}{} + Z \bigg) = -Z\frac{\text{erf}(\mu r)}{r},
 \end{equation}
@@
  \label{eq:one_e_1}
- \deriv{}{r}{}j(r,\mu,Z) = Z\bigg( \text{erf}(\mu r) - 1\bigg).
+ \deriv{}{r}{}u(r,\mu,Z) = Z\bigg( \text{erf}(\mu r) - 1\bigg).
 \end{equation}
@@
  \label{eq:one_e_2}
- j(r,\mu,Z) = -Z r \bigg( 1 - \text{erf}\big(\mu r\big) \bigg) + \frac{Z}{\sqrt{\pi}\mu} e^{-\big(\mu r \big)^2}. 
-\end{equation}
-Now, we can plug $j(r,\mu,Z)$ into Eq. \eqref{eq:one_e_0} in order to compute the explicit form of the similarity transformed Hamiltonian. 
+ u(r,\mu,Z) = -Z r \bigg( 1 - \text{erf}\big(\mu r\big) \bigg) + \frac{Z}{\sqrt{\pi}\mu} e^{-\big(\mu r \big)^2}. 
+\end{equation}
+Now, we can plug $u(r,\mu,Z)$ into Eq. \eqref{eq:one_e_0} in order to compute the explicit form of the similarity transformed Hamiltonian. 
 To do so, we use Eq. \eqref{eq:one_e_1}, and also that 
 \begin{equation}
- \deriv{}{r}{2}j(r) = \frac{2 \mu Z }{\sqrt{\pi}} e^{-(\mu r)^2}.
+ \deriv{}{r}{2}u(r) = \frac{2 \mu Z }{\sqrt{\pi}} e^{-(\mu r)^2}.
 \end{equation}
@@
  \begin{aligned}
- \tilde{H}[j] = & e^{-j(r)} H e^{j(r)} \\
+ \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
               = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) - \frac{Z}{r}  \\
@@
  \begin{aligned}
- \tilde{H}[j] = & e^{-j(r)} H e^{j(r)} \\
+ \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
               = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big)  \\
@@
 \begin{equation}
- e^{\hat{\tau}({\bf r}_1,\hdots , {\bf r}_i,{\bf r}_N)} = e^{-\sum_i^N J({\bf r}_i)} 
-\end{equation}
-where $J({\bf r}_i)$ has the following form 
-\begin{equation}
- J({\bf r}_i) = \sum_{A} j(r_{iA},\mu,Z_A) 
-\end{equation}
-where $j(r,\mu,Z)$ is given by Eq. \eqref{eq:one_e_2} and $r_{iA} = \big|{\bf r}_i - {\bf R}_A \big|$. 
+ e^{\hat{\tau}({\bf r}_1,\hdots , {\bf r}_i,{\bf r}_N)} = e^{-\sum_i^N u({\bf r}_i)} 
+\end{equation}
+where $u({\bf r}_i)$ has the following form 
+\begin{equation}
+ u({\bf r}_i) = \sum_{A} u(r_{iA},\mu,Z_A) 
+\end{equation}
+where $u(r,\mu,Z)$ is given by Eq. \eqref{eq:one_e_2} and $r_{iA} = \big|{\bf r}_i - {\bf R}_A \big|$. 
 According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the equation of the similarity transformed Hamiltonian is similar  
@@
  \begin{aligned}
- \bigg[ H, \hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{j} J(\br{}_j) \bigg]      \phi(\br{}_1,\hdots \br{}_N) \\    
-                                                        & = -\frac{1}{2} \sum_i \bigg( \big(\nabla^2_i J({\bf r}_i)\big) + 2\nabla_i J({\bf r}_i) \cdot \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).  
+ \bigg[ H, \hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{u} u(\br{}_j) \bigg]      \phi(\br{}_1,\hdots \br{}_N) \\    
+                                                        & = -\frac{1}{2} \sum_i \bigg( \big(\nabla^2_i u({\bf r}_i)\big) + 2\nabla_i u({\bf r}_i) \cdot \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).  
  \end{aligned}
@@
  \begin{aligned}
-  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg) \\
-                            & -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg).
+  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg) \\
+                            & -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg).
  \end{aligned}
@@
 \begin{equation}
- \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
+ \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
 \end{equation}
@@
  \begin{aligned}
-& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg)    
-                                                                   -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
-                                                                   -\frac{1}{2}\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
+& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
+                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
+                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
  \end{aligned}
@@
 \subsection{Computation of the total operator}
-\subsubsection{Computation of $\nabla_i J(\br{}_i)$}
-\begin{equation}
- \begin{aligned}
-&\nabla_i J(\br{}_i) = \sum_A \nabla_i J(r_{iA},Z_A) \\
-                    &= \sum_A \deriv{}{x_i}{} J(r_{iA},Z_A) {\bf e}_{x_i} + \deriv{}{y_i}{} J(r_{iA},Z_A) {\bf e}_{y_i} + \deriv{}{z_i}{} J(r_{iA},Z_A) {\bf e}_{z_i}, 
+\subsubsection{Computation of $\nabla_i u(\br{}_i)$}
+\begin{equation}
+ \begin{aligned}
+&\nabla_i u(\br{}_i) = \sum_A \nabla_i u(r_{iA},Z_A) \\
+                    &= \sum_A \deriv{}{x_i}{} u(r_{iA},Z_A) {\bf e}_{x_i} + \deriv{}{y_i}{} u(r_{iA},Z_A) {\bf e}_{y_i} + \deriv{}{z_i}{} u(r_{iA},Z_A) {\bf e}_{z_i}, 
  \end{aligned}
@@
 \begin{equation}
- \deriv{}{x_i}{}J(r_{iA}) = \deriv{}{r_{iA}}{}J(r_{iA}) \deriv{r_{iA}}{x_i}{},
+ \deriv{}{x_i}{}u(r_{iA}) = \deriv{}{r_{iA}}{}u(r_{iA}) \deriv{r_{iA}}{x_i}{},
 \end{equation}
@@
 \begin{equation}
- \deriv{}{x_i}{} J(r_{iA},Z_A) = -\sum_A Z_A \big( x_i - x_A \big) \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}.
-\end{equation}
-\subsubsection{Computation of $\nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i)$}
-The computation of $\nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i)$ leads to 
-\begin{equation}
- \begin{aligned}
-  \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) =  \sum_{A,B} Z_B &Z_A \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
+ \deriv{}{x_i}{} u(r_{iA},Z_A) = -\sum_A Z_A \big( x_i - x_A \big) \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}.
+\end{equation}
+\subsubsection{Computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$}
+The computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$ leads to 
+\begin{equation}
+ \begin{aligned}
+  \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) =  \sum_{A,B} Z_B &Z_A \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
                                                                       & +  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
@@
 
-\subsubsection{Computation of $\nabla^2_i J(\br{}_i) $}
+\subsubsection{Computation of $\nabla^2_i u(\br{}_i) $}
 We need to compute 
@@
  \begin{aligned}
- \deriv{}{x_{i}}{2} J(\br{}_i) & = -\sum_A Z_A \deriv{}{x_i}{} \bigg[(x_i - x_A) \frac{1 - \text{erf}(\mu r)}{r_{iA}} \bigg] \\
+ \deriv{}{x_{i}}{2} u(\br{}_i) & = -\sum_A Z_A \deriv{}{x_i}{} \bigg[(x_i - x_A) \frac{1 - \text{erf}(\mu r)}{r_{iA}} \bigg] \\
                                & = -\sum_A Z_A \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
@@
  \label{eq:lapl_interm_1}
-&  \deriv{}{x_{i}}{2} J(\br{}_i) + \deriv{}{y_{i}}{2} J(\br{}_i) + \deriv{}{z_{i}}{2} J(\br{}_i) =  - \sum_{A} Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \\
+&  \deriv{}{x_{i}}{2} u(\br{}_i) + \deriv{}{y_{i}}{2} u(\br{}_i) + \deriv{}{z_{i}}{2} u(\br{}_i) =  - \sum_{A} Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \\
  & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
@@
 \begin{equation}
- \Delta_i J(\br{}_i) = - \sum_{A}  Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg) \bigg]
+ \Delta_i u(\br{}_i) = - \sum_{A}  Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg) \bigg]
 \end{equation}
@@
 \begin{equation}
- \Delta_i J(\br{}_i) = - \sum_{A}  2 \, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg]
+ \Delta_i u(\br{}_i) = - \sum_{A}  2 \, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg]
 \end{equation}
@@
  \begin{aligned}
-& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],J\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i J(\br{}_i) \bigg)    
-                                                                   -\sum_i \bigg(\nabla_i J(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
-                                                                   -\frac{1}{2}\sum_i \nabla_i J({\bf r}_i) \cdot \nabla_i J({\bf r}_i) 
+& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],J\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
+                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
+                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
  \end{aligned}
@@
 \begin{equation}
- \tilde{j}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( j(r_{12};\mur{1}) + j(r_{12};\mur{2}) \bigg)
-\end{equation}
-where $j(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
+ \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( u(r_{12};\mur{1}) + u(r_{12};\mur{2}) \bigg)
+\end{equation}
+where $u(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
 To derive properly the equations for such a new Jastrow factor, one needs to derive the different terms involving gradients and so on. 
-\subsection{Gradients of $\tilde{j}(\bd{r_1},\bd{r_2})$}
-A fundamental quantity is the gradient of $\tilde{j}(\bd{r_1},\bd{r_2})$ which is 
-\begin{equation}
- \nabla_1 \tilde{j}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
-\end{equation}
-Therefore one needs to compute $\deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2})$
-\begin{equation}
- \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} j(r_{12};\mur{1}) 
-                                               +\frac{1}{2}\deriv{}{x_1}{} j(r_{12};\mur{2}) .
-\end{equation}
-Applying the chain rule 
-\begin{equation}
- \deriv{}{x_1}{} j(r_{12};\mur{2}) = \deriv{}{r_{12}}{} j(r_{12};\mur{2})\deriv{r_{12}}{x_1}{} + \deriv{}{\mur{2}}{}j(r_{12};\mur{2}) \deriv{\mur{2}}{x_1}{},
-\end{equation}
-and as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
-of the condition determining $j(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
-\begin{equation}
- \deriv{}{x_1}{} j(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
-\end{equation}
-Then, 
-\begin{equation}
- \deriv{}{x_1}{} j(r_{12};\mur{1}) = \deriv{}{r_{12}}{} j(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} + \deriv{}{\mur{1}}{}j(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
-\end{equation}
-and as 
-\begin{equation}
- \label{eq:d_dmu_j}
- \deriv{}{\mu}{}j(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2\sqrt{\pi} \mu^2},
+\subsection{Gradients of $\tilde{u}(\bd{r_1},\bd{r_2})$}
+A fundamental quantity is the gradient of $\tilde{u}(\bd{r_1},\bd{r_2})$ which is 
+\begin{equation}
+ \nabla_1 \tilde{u}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
+\end{equation}
+Therefore one needs to compute $\deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2})$
+\begin{equation}
+ \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{1}) 
+                                               +\frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{2}) .
+\end{equation}
+Let us begin with the first term 
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{x_1}{} u(r_{12};\mur{1})=& \deriv{}{r_{12}}{} u(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} \\ 
+                                  +& \deriv{}{\mur{1}}{}u(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
+ \end{aligned}
+\end{equation}
+but as 
+\begin{equation}
+ \deriv{}{\mu}{}u(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2 \sqrt{\pi} \mu^2}
 \end{equation}
@@
 \begin{equation}
- \deriv{}{x_1}{} j(r_{12};\mur{1}) = \frac{1 - \text{erf}(\mur{1} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg) + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{}.
+ \begin{aligned}
+ \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
+                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
+ \end{aligned}
+\end{equation}
+Similarly, as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
+of the condition determining $u(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
+\begin{equation}
+ \deriv{}{x_1}{} u(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
 \end{equation}
@@
  \begin{aligned}
- \deriv{}{x_1}{} \tilde{j}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
+ \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
  \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
@@
  \begin{aligned}
- \deriv{}{x_2}{} \tilde{j}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
+ \deriv{}{x_2}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
  \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
@@
 
-\subsection{Computation of $\bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2$}
+\subsection{Computation of $\bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2$}
 Then one needs to compute 
@@
  \begin{aligned}
-& \bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
-& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
-& \bigg(\deriv{}{y_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{y_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
-& \bigg(\deriv{}{z_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{z_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2.
+& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
+& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
+& \bigg(\deriv{}{y_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{y_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
+& \bigg(\deriv{}{z_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{z_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2.
  \end{aligned}
@@
  \begin{aligned}
-& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
- = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{1} r_{12}\big) \bigg)^2  \\
+& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+ = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
  + & \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 \\
@@
  \begin{aligned}
-& \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+& \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
  = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
@@
  \begin{aligned}
-& \bigg(\deriv{}{x_1}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{j}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
+& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
  = & \frac{1}{2}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
@@
  \begin{aligned}
-& \bigg(\nabla_1\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{j}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
-& \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{1} r_{12}\big) \bigg)^2 
+& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = 
+  \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
+&+\frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{4 \sqrt{\pi}r_{12}}  \\
+& \big( \bri{1} - \bri{2}\big)\cdot
+\bigg(\frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
+  -   \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
+  &+ \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
+ + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
  \end{aligned}

### 2020-11-25 cusp_j/paper/paper.tex
working on the intro of the paper

@@
 \section{Introduction}
-Two formulation : the "pseudo orbital" (\textit{i.e.} usual common set of orbitals for bra and ket) and "biorthonormal orbitals" (\textit{i.e.} a different set of orbitals for bra and ket having the biorthonormal property).
-In the limit of the FCI wave function, these two formulations coincide, therefore we keep the "pseudo orbital" theory for the sake of simplicity.
+One of the most challenging problem in modern computational chemistry is the accurate simulation of the electronic structure of atomic and molecular systems, which implies solving the Schroedinger equation for a general $N$-body system.
+At the heart of the complexity of such a task relies the rapidly prohibitive computational cost of the wave function methods (WFT), which is induced by the exponential growth with the system size of the Hilbert space involved in the linear eigenvalue problem to be solved.
+
+In usual WFT, the computational bottleneck is mainly determined by two factors: the level of complexity of the wave function which is imposed by the amount of strong correlation effects in the system, and the convergence of the computed quantities with respect to the size of the one-electron basis used to project the Hamiltonian into a finite eigenvalue problem.
+Typically, strong correlation effects appear when the two-electron coulomb interaction can no longer be considered as a small perturbation over a mean field Hamiltonian.
+Treating such effects in a black box way involves the use of very flexible wave functions such as
+selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+%selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 
+full configuration Quantum Monte Carlo\cite{BooThoAla-JCP-09,BooAla-JCP-10,BooCleThoAla-JCP-11,GhaLozAla-JCP-19,VitAlaKat-JCTC-20} (FCI-QMC) or tensor product states\cite{ChaSha-AR-11,BaiRei-JCP-20}.
+These methods all have one thing in common: they manage to select, although through different mathematical forms, the dominant part of the exponentially growing Hilbert space that resulting from a $N$-electron problem among a given finite basis set.
+
+Even if these selection schemes are extremely efficient to obtain a qualitative description of the wave function, a quantitative description is often out of reach as it implies the use of very large one-electron basis sets which are needed to recover the slowly converging correlation effects near the electron-electron coalescence point.
+These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance: the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
+As shown by the seminal works of Hylleraas \cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the size of the basis set is mainly due to the impossibility to represent the cusp in a finite basis set.
+To tackle this problem, the introduction of functions explicitly depending on the inter-electronic coordinate (F12) have emerged\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18}.
+In the F12 schemes, the geminal function depending on the inter-electronic coordinate is used to describe short-range correlation effects which are absent from the finite basis set.
+Thanks to strong orthogonality,
+all redundant correlation effects of the geminal function are projected out of the wave function, 
+and therefore the geminal function only deals with correlation orthonormal to the basis set. 
+The resulting F12 theories, mainly based on perturbation theory and coupled cluster theory, are therefore 
+extremely close to their parent theory, with additional integrals two- and three-body terms resulting from the use of the geminal function. 
+It is important to notice that because of the orthogonalization between the geminal and the basis set, 
+the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and their usual parent.
+Therefore, no strong compression of the electronic wave function is obtained by the F12 theory,
+but a fast convergence toward the complete basis set limit (CBS) is nevertheless obtained.
+
+An alternative point of view using a geminal function is the so-called transcorrelated (TC) approach where the full effect of the geminal function is incorporated into the calculation through a similarity transformation of the original Hamiltonian.
+The pioneers of such theory were Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} where they derive the equations of the general form of the TC Hamiltonian which is non hermitian and contains explicitly three-body interaction.
+Despite the loss of variational principle due to the non hermitian nature of the TC Hamiltonian, the parameters optimized by Boys and Handy were mainly the orbitals of a single Slater determinant together with the mathematical form of the geminal function with which one performs the similarity transformation of the Hamiltonian to obtain the TC Hamiltonian.
+
+Later on, Ten-No\cite{Ten-No-CPL-00} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the geminal function, one uses a more elaborate many body theory (Moller-Plesset at second order in Refs.\onlinecite{Ten-No-CPL-00,HinTanTen-JCP-01} and coupled cluster in later works\cite{HinTanTen-CPL-02}) with a fixed universal geminal function.
+Such a geminal function, developed as a linear combination of gaussian functions, is optimized in order to remove the divergent character of the coulomb potential within the TC framework.
+In Ref.\onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
+which allows to treat the non-hermitian TC Hamiltonian in a many-body framework which is therefore more suited 
+to develop many-body perturbation theory approaches. 
+It is also noteworthy that the eigenfunctions of the TC Hamiltonian are invariant by orbital rotation, 
+and therefore in the limit where one gives full flexibility to the wave function, 
+the biorthogonal and usual orthogonal approaches give the same results. 
+Nevertheless, as approximations are necessary made in the wave function ansatz in realistic systems, 
+the biorthogonal approach might improve the quality of the results.
+
+In latter works, Umezawa \textit{et.
+al.}\cite{UmeTsu-JCP-03,UmeTsuOhnShiChi-JCP-05} introduced a scheme to couple TC equations with the usual variational Monte Carlo (VMC) scheme in order to optimise the Jastrow factor through a variance miminization.
+An attempt to make TC equations variational have been proposed by Luo\cite{Luo-JCP-10,Luo-JCP-11} based on the empirical experience that in the original single determinant TC approach of Boys and Handy, the orbital optimization seemed to be the source of loss of the variational property.
+Luo therefore proposed to replace the original TC equations to optimize the orbitals by that of a general Jastrow-Slater ansatz.
+
+Yanai and Chan
+
+More recently, Alavi \textit{et.
+al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations to elaborate geminal functions explicitly taking into account for electron-electron correlation together with electron-electron-nucleus distance.
+The geminal function used in such work were obtained from the optimized Jastrow factors for He to Ne of Moskowitz \textit{et.
+al.}\cite{SchMos-JCP-90}.
+The main advantage of Alavi work relies on the fact that they allow a full flexibility to the Slater part of the wave function to adapt to the elaborated geminal functions.
+This is done through the use of a projective technique, the FCI-QMC, which allows to obtain the ground state of an operator, hermitian or not, through a stochastic sampling of the Hilbert space.
+Their approach share common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions,
+even though the FCIQMC is certainly more flexible than the coupled cluster ansatz of Ten-No used in Ref. \onlinecite{HinTanTen-JCP-01}.
 

### 2020-12-02 dev/slat_rules_trans/mu_lda_average.irp.f
modified qp_sc_basis_corr

@@ -12,6 +12,7 @@ program test_density
    print*,'average_mu_lda       = ',average_mu_lda
    print*,'average_mu_rs        = ',average_mu_rs 
    print*,'average_mu_rs_c      = ',average_mu_rs_c
+   print*,'average_mu_rs_c_lda  = ',average_mu_rs_c_lda
    print*,'average_mu_grad_n    = ',average_mu_grad_n
    print*,'average_mu_lda * 1/2 = ',average_mu_lda * 0.5d0
 end
@@ -139,6 +140,7 @@ end
  BEGIN_PROVIDER [double precision, average_mu_lda      ]
 &BEGIN_PROVIDER [double precision, average_mu_rs       ]
 &BEGIN_PROVIDER [double precision, average_mu_rs_c     ]
+&BEGIN_PROVIDER [double precision, average_mu_rs_c_lda ]
 &BEGIN_PROVIDER [double precision, average_mu_grad_n   ]
  implicit none
  integer :: ipoint,i,m
@@ -186,5 +188,7 @@ end
  average_mu_rs     = average_mu_rs    / dble(elec_alpha_num + elec_beta_num)
  average_mu_rs_c   = average_mu_rs_c  / dble(elec_alpha_num + elec_beta_num)
  average_mu_grad_n = average_mu_grad_n/ dble(elec_alpha_num + elec_beta_num)
+
+ average_mu_rs_c_lda = 0.5d0 * (average_mu_lda + average_mu_rs_c)
 
 END_PROVIDER 

### 2020-12-02 cusp_j/paper/draft.tex

--- 2020-11-12 cusp_j/paper/paper.tex
@@
 \newcommand{\bs}[0]{{\bf {s}}}
-\newcommand{\dr}[1]{\text{d}{\bf r_{#1}}}
+\newcommand{\dr}[1]{\text{d}{\bf {#1}}}
 \newcommand{\psiex}[0]{\Psi^{\text{ex}}_0}
@@
 
-The paper is organized as follows. 
-In the first section, we derive the analytical form of a new Jastrow factor and the corresponding transcorrelated Hamiltonian. 
-The, we perform a detailed numerical study of the behaviour of the solution of $\tilde{H}[\mu]$ on the helium atom: 
-in the first part we analyze the speed of convergence of the ground state energy with respect to the basis set and the parameter $\mu$, 
-then we study the behaviour of the right eigenvectors in real space and compare it with the exact ground state wave function. 
-We show that the rapid convergence of the total energies coincides with a rapid convergence of the right eigenvectors in real space. 
-Based on such encouraging results, we study the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
-a value of $\mu$ which depends on the system and still provides a fast convergence of the total energies. 
-Eventually, we study the H$_2$ molecule and compare different regimes of correlation.
+\section{Brief overview of mathematical properties of similarity transformed Hamiltonian}
+\subsection{Definition of the similarity transformation}
+Assume an \textit{Hermitian operator} $H$ whose spectral representation reads 
+\begin{equation}
+ \label{eq:h_spectr}
+ H  = \sum_n E_n \ket{\Psi_n}\bra{\Psi_n}
+\end{equation}
+with $\ket{\Psi_n}$ being its orthonormal eigenvectors 
+\begin{equation}
+ \bra{\Psi_n} \Psi_m \rangle = \delta_{mn},
+\end{equation}
+and $E_n \in \R$ its real eigenvalues.
+
+Let us consider now an \textit{Hermitian} and \textit{invertible} operator $U$, \textit{i.e.} an operator $U$ such that there exists $U^{-1}$ such that 
+\begin{equation}
+ \label{eq:u_def_1}
+ U^{-1} U = U \, U^{-1} = 1,
+\end{equation}
+and that 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:u_def_2}
+ & U^\dagger = U \\
+ & \big(U^{-1}\big)^{\dagger} = U^{-1}.
+ \end{aligned}
+\end{equation}
+Then, the similarity transformed Hamiltonian $\tilde{H}$ is defined as
+\begin{equation}
+ \label{eq:def_htilde}
+ \tilde{H} = U^{-1}\, H \, U.
+\end{equation}
+\subsection{Eigenvalues ans eigenvectors of $\tilde{H}$}
+\subsubsection{Definition of left and right eigenvectors}
+Regarding the properties of $\tilde{H}$, a first remark is that it is not Hermitian anymore
+\begin{equation}
+ \begin{aligned}
+ \tilde{H}^\dagger & = \bigg(  U^{-1} \, H \,U \bigg)^\dagger \\
+                   & = U\, H \, U^{-1}  \\
+                   & \ne \tilde{H}.
+ \end{aligned}
+\end{equation}
+Even though $\tilde{H}$ is not hermitian, it conserves the same eigenvalues than the original Hamiltonian $H$. 
+The main difference with the original Hamiltonian are its eigenvectors: because $\tilde{H}$ is not Hermitian anymore, it possesses \textit{right} eigenvectors and \textit{left} eigenvectors. 
+The right eigenvectors of a given operator $A$ are defined by
+\begin{equation}
+ A \ket{\Phi_n} = A_n \ket{\Phi_n}, 
+\end{equation}
+whereas the left eigenvectors of such operator are defined through
+\begin{equation}
+ A^{\dagger} \ket{X_n} = A_n \ket{X_n}.
+\end{equation}
+Therefore, if $A$ is hermitian, $A = A^{\dagger}$ and therefore $\ket{\Phi_n} = \ket{X_n} $, but for a non hermitian operator, the left and right eigenvectors do not coincide.
+
+To find the right and left eigenvectors of $\tilde{H}$, one can insert the definition of $\tilde{H}$ (see Eq. \eqref{eq:def_htilde}) in Eq. \eqref{eq:h_spectr}
+\begin{equation}
+ \label{eq:tilde_1}
+ \begin{aligned}
+ \tilde{H} & = \sum_n E_n \, U^{-1} \, \ket{\Psi_n} \bra{\Psi_n}U.
+ \end{aligned}
+\end{equation}
+We can define the right eigenvectors $\ket{\Phi_n}$ as
+\begin{equation}
+ \label{eq:def_right}
+ \ket{\Phi_n} = U^{-1} \ket{\Psi_n},
+\end{equation}
+ because  from Eq. \eqref{eq:tilde_1}, we notice that the $\ket{\Phi_n}$ fulfil the right eigenvector relationship
+\begin{equation}
+ \begin{aligned}
+ \tilde{H} \ket{\Phi_n} & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U\ket{\Phi_n} \\
+                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} U \bigg( U^{-1} \ket{\Psi_n} \bigg) \\
+                        & = \sum_m E_m \,U^{-1} \, \ket{\Psi_m} \bra{\Psi_m} \Psi_n \rangle \\
+                        & = E_n          U^{-1} \ket{\Psi_n} \\
+                        & = E_n  \ket{\Phi_n} \\
+ \end{aligned}
+\end{equation}
+In a similar way, we can define the left eigenvectors $\ket{X_n}$ as 
+\begin{equation}
+ \label{eq:def_left}
+ \ket{X_n} = U \ket{\Psi_n},
+\end{equation}
+because they fulfil the left eigenvalue equation
+\begin{equation}
+ \begin{aligned}
+ \tilde{H}^{\dagger} \ket{X_n}  = E_n \, \ket{X_n}. 
+ \end{aligned}
+\end{equation}
+\subsubsection{Biorthogonality, spectral representation and loose of the variational principle}
+The left and right eigenvectors fulfill the so-called \textit{biorthogonal} property, as 
+from Eqs. \eqref{eq:def_right} and \eqref{eq:def_left} one obtains 
+\begin{equation}
+ \overlap{X_j}{\Phi_i} = \bigg(U \ket{\Psi_n} \bigg)^\dagger \bigg(U^{-1}\ket{\Psi_J}\bigg)
+\end{equation}
+which, according to the Hermitian property of $U$ (see Eq.\eqref{eq:u_def_2}) simply becomes 
+\begin{equation}
+ \begin{aligned}
+ \overlap{X_j}{\Phi_i} &= \matelem{\Psi_j}{U\,U^{-1}}{\Psi_i} \\
+                       &= \overlap{\Psi_j}{\Psi_i} \\
+                       &= \delta_{ji}.
+ \end{aligned}
+\end{equation}
+Nevertheless, the right and left eigenvectors among themselves are not orthonormal as 
+\begin{equation}
+ \begin{aligned}
+  \overlap{\Phi_j}{\Phi_i} & = \matelem{\Psi_j}{U^{-1}\,U^{-1}}{\Psi_i} \\
+                           & = \matelem{\Psi_j}{U^{-2}}{\Psi_i},  
+ \end{aligned}
+\end{equation}
+and 
+\begin{equation}
+ \begin{aligned}
+  \overlap{X_j}{X_i} & = \matelem{\Psi_j}{U\,U}{\Psi_i} \\
+                           & = \matelem{\Psi_j}{U^{2}}{\Psi_i}.  
+ \end{aligned}
+\end{equation}
+Having obtained biorthonormal left and right eigenvectors, one can then obtain a spectral representation of the similarity transformed Hamiltonian 
+\begin{equation}
+ \tilde{H} = \sum_i E_i \ket{\Phi_i} \bra{X_i}, 
+\end{equation}
+which is very useful to study the variational principle, an important aspect of quantum chemistry. 
+Let us consider a wave function $\Psi$ developed on the eigenvectors of $H$
+\begin{equation}
+ \ket{\Psi} = \sum_i c_i \ket{\Psi_i}.
+\end{equation}
+The expectation value of $H$ over $\Psi$ is then 
+\begin{equation}
+ \begin{aligned}
+  \matelem{\Psi}{H}{\Psi} & = \sum_{i,j} c_i c_j \matelem{\Psi_j}{H}{\Psi_i} \\
+                          & = \sum_{i,j} c_i c_j  E_i \overlap{\Psi_j}{\Psi_i} \\
+                          & = \sum_{i} |c_i|^2 E_i \\
+                          & \ge E_0
+ \end{aligned}
+\end{equation}
+which gives the variational principle because of the orthogonality of eigenvectors of an \textit{Hermitian} operator. 
+Now let us decompose the same wave function $\Psi$ on the right-eigenvectors of $\tilde{H}$ 
+\begin{equation}
+ \ket{\Psi} = \sum_i \tilde{c}_i \ket{\Phi_i},
+\end{equation}
+and consider the expectation value of $\tilde{H}$ over $\Psi$
+\begin{equation}
+ \begin{aligned}
+  \matelem{\Psi}{\tilde{H}}{\Psi} & = \sum_{i,j} \tilde{c}_i \tilde{c}_j \matelem{\Phi_j}{\tilde{H}}{\Phi_i} \\
+                                  & = \sum_{i,j} \tilde{c}_i \tilde{c}_j E_i \overlap{\Phi_j}{\Phi_i} 
+ \end{aligned}
+\end{equation}
+which has no reason to be an upper bound to $E_0$ as $\overlap{\Phi_j}{\Phi_i} \ne \delta_{i,j}$. 
+Therefore, we see that we cannot apply straightforwardly the variational principle 
+to similarity transformed Hamiltonians, because of the lack of orthonormality of the right eigenvectors.
 
 \section{A new form of Jastrow factor for transcorrelated Hamiltonian}
-This section is dedicated to the derivation of a new form of Jastrow factor mimicking at short range the correlation effects of RS-DFT. 
-For the sake of simplicity and to remain as close as possible to the physical picture of the electronic correlation problem, 
-we derive the equations of the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
-Thanks to the simplicity of the equations, we focus on the behaviour at small $r_{12}$ of different flavours of Hamiltonians 
-and the corresponding discontinuity in their eigenvectors. 
-We browse three different types of Hamiltonians: the usual physical Hamiltonian, the transcorrelated Hamiltonian together with the effective Hamiltonian used in RS-DFT.
-Then, we derive the general analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$, and its dependence as function of the parameter $\mu$.
-
-\subsection{A simple physical picture: the case of the helium atom}
-\subsubsection{The transcorrelated Hamiltonian for helium atom}
+\subsection{The similarity transformed Hamiltonian}
 Let us write the Hamiltonian of the He atom in the ${\bf r}_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
@@
 
-\subsubsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
+\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
 \label{sec:cusp}
@@
 the constraint of fulfilling the cusp condition. 
+%Another way to phrase Eq.\eqref{eq:cusp_phi_1} and Eq.\eqref{eq:cusp_phi_2} is that because of the Jastrow factor, the similarity transformed Hamiltonian exhibits an effective non-divergent electron-electron interaction, which does not impose any cusp condition to the eigenfunctions of $\tilde{H}[j]$.
 
@@
 
-\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
+\subsection{Explicit form of  $\tilde{H}[\mu]$ and some of its properties}
 \subsubsection{Explicit form of $\tilde{H}[\mu]$ }
-Having established the analytical expression of $j(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
-According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
-\begin{equation}
- \label{ht_def_g}
- e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
-\end{equation}
-where $\hat{\hat{\tau}} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j} \frac{1}{r_{ij}}$. 
-This leads to the following similarity transformed Hamiltonian 
-\begin{equation}
- \begin{aligned}
- \label{ht_def_gu}
- \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
-           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
- \end{aligned}
-\end{equation}
-where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
-\begin{equation}
- \begin{aligned}
- \label{def_k}
-  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
-                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
-                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1  \\
- \end{aligned}
-\end{equation}
-\begin{equation}
- \begin{aligned}
- \label{def_k}
-  \hat{L}(\bri{1},\bri{2},\bri{3}) ) = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
-                                     + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
- \end{aligned}
-\end{equation}
-Therefore, to obtain the general formulation of the $\tilde{H}[\mu]$ one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = j(r_{12},\mu)$.
-
-\subsection{Explicit form for the operators $\hat{K}(\bri{1},\bri{2}) )$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ }
-\subsubsection{Intermediate quantities}
-To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $j(r_{12},\mu)$ with respect to a $\bri{1}$ which, after some derivation reads
-\begin{equation}
- \label{eq:nabla_u}
- \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
- \end{aligned}
-\end{equation}
-Then, the terms $\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2$ is simply 
-\begin{equation}
- \begin{aligned}
- \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_2 u(\bri{1},\bri{2}) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
- \end{aligned}
-\end{equation}
-Then, to compute the  non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ one needs to compute 
-\begin{equation}
- \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
-                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg),
- \end{aligned}
-\end{equation}
-and as $\nabla_1 u(\br{}_1,\br{}_2) = - \nabla_2 u(\br{}_1,\br{}_2)$,   
-the total non hermitian operator in $\hat{K}(\bri{1},\bri{2})$ can be written as 
-\begin{equation}
- \begin{aligned}
- \label{def_non_hermit}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
-         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big)  \\
-&  +      (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg).
- \end{aligned}
-\end{equation}
-One can notice that the form of Eq. \eqref{def_non_hermit} provides an explicit form to compute analytical integrals with Gaussian types functions. 
-Nevertheless, one can notice that as 
-\begin{equation}
- \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
-\end{equation}
-one can write 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla0}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
- \end{aligned}
-\end{equation}
-Then, introducing the spherical coordinate system for $\br{}_1 - \br{}_2$ in terms of ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$ and the angle $\theta$ and $\phi$, one can write 
-\begin{equation}
- \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
-\end{equation}
-and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
-\begin{equation}
- \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
-\end{equation}
-and therefore 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla1}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
- = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
- \end{aligned}
-\end{equation}
-which is a more compact expression than Eq.\eqref{def_non_hermit}
-
-The computation of the Laplacian is a little more tedious, but after some derivations it comes  
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_2}
- &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})\\ 
- & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
- \end{aligned}
-\end{equation}
-\subsubsection{Explicit form of $\tilde{H}[\mu]$}
-Summing all terms to recombine $\hat{K}(\bri{1},\bri{2})$ reads 
-\begin{equation}
- \label{eq:k_final}
-  \begin{aligned}
-   \hat{K}(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
-  \end{aligned}
-\end{equation}
-Similarly, the computation of $\hat{L}(\bri{1},\bri{2},\bri{3}) $ 
-\begin{equation}
- \label{eq:l_final}
- \begin{aligned}
- \hat{L}_\mu(\bri{1},\bri{2},\bri{3}) = & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{12} \cdot \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{13} \\
-                                      + & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{21} \cdot \frac{1 - \text{erf}(\mu r_{23})}{2 r_{23}} \bri{23} \\
-                                      + & \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{31} \cdot \frac{1 - \text{erf}(\mu r_{32})}{2 r_{32}} \bri{32}
- \end{aligned}                    
-\end{equation}
-
-Having established the explicit form of $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
-look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $j(r_{12};\mu)$,  
-which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, which gives
+Having established the explicit form of $j(r_{12};\mu)$ and some of its properties, one can now 
+look at the explicit form of the transcorrelated Hamiltonian obtained with $j(r_{12};\mu)$,  
+which, by injecting the form of \eqref{eq:def_j} in Eq.\eqref{eq:ht_phi}, reads 
 \begin{equation}
@@
  \label{eq:exp_ht_mu}
-   \tilde{H}[\mu] = & h_c + \sum_{i<j} \bigg( \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) + \tilde{t}[\mu] \bigg) - \sum_{i<j<k} \hat{L}_\mu(\bri{1},\bri{2},\bri{3})
-  \end{aligned}
-\end{equation}
-where $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ is a scalar effective two-body potential
-\begin{equation}
- \begin{aligned}
- \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)  =  \frac{\text{erf}(\mu r_{ij})}{r_{ij}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{ij} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{ij}) \bigg)^2}{4}, 
- \end{aligned}
-\end{equation}
-and $\tilde{t}[\mu]$ is non hermitian two-body differential operator 
-\begin{equation}
- \begin{aligned}
- \tilde{t}[\mu] =  \bigg( \text{erf}(\mu r_{ij}) - 1\bigg) \deriv{}{r_{ij}}{}.
- \end{aligned}
-\end{equation}
-
-In order to have a pictorial representation of $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$, we illustrate in Fig\ref{fig_wee_mu} its shape for different values of $\mu$. 
+   \tilde{H}[\mu] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
+& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
+  \end{aligned}
+\end{equation}
+From Eq.\eqref{eq:exp_ht_mu}, one can define an effective scalar electron-electron interaction $\tilde{\mathcal{W}}_{ee}(r_{12}) $ 
+\begin{equation}
+ \label{eq:deff_w_new}
+ \tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4},
+\end{equation}
+whose shape is illustrated in Fig\ref{fig_wee_mu}. 
 \begin{figure*}
@@
 \end{figure*}
-From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ 
+From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential 
 is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT at large $r_{12}$. 
@@
 \label{sec:h_mu_lim}
-Regarding now the variation of $\tilde{H}[\mu]$, one expects as 
+Coming now to the limits of $\tilde{H}[\mu]$ when $\mu \rightarrow \infty$, one expects that as
 \begin{equation}
@@
 \end{equation}
-one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit
+one recovers the usual Hamiltonian in that limit
 \begin{equation}
@@
 \begin{equation}
- \label{eq:htilde_mu_low}
- \begin{aligned}
-&\lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \sum_{i<j}\deriv{}{r_{ij}}{} \\
- & - \sum_{i<j<k}  \bigg(\frac{1}{2 r_{ij}} \frac{1}{2 r_{ik}} \bri{ij} \cdot \bri{ik} + \frac{1}{2 r_{ji}} \frac{1}{2 r_{jk}} \bri{ji} \cdot \bri{jk}  + \frac{1}{2 r_{ki}} \frac{1}{2 r_{kj}} \bri{ki} \cdot \bri{kj} \bigg)
- \end{aligned}
-\end{equation}
-which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and an attractive three electron interaction. 
-It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ of Eq.
-\eqref{eq:htilde_mu_low} is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
+ \lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \partial{}{r_{12}}{}, 
+\end{equation}
+which means that all scalar electron-electron interaction have been replaced by a differential operator.
 
@@
 \section{General formulation of similarity transformed Hamiltonian}
-\subsection{General equations for a $N$-electron system}
-\subsubsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
-We need to compute the following integral 
-\begin{equation}
- \label{eq:l_ijmkln}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
- \end{aligned}
-\end{equation}
-where 
-\begin{equation}
- \hat{L}_1(\bri{1},\bri{2},\bri{3}) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
-\end{equation}
-with 
-\begin{equation}
- w_\mu(\bri{13}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
-\end{equation}
-Let us compute the first term of Eq. \eqref{eq:l_ijmkln}:
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
- &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
- \end{aligned}
-\end{equation}
-Such matrix element can be further decomposed into
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
- =& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
- \end{aligned}
-\end{equation}
-where 
-\begin{equation}
- \begin{aligned}
- \label{eq:l_1x}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
- &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
- \end{aligned}
-\end{equation}
-If we define the following function 
-\begin{equation}
- W_{mn}^x({\bf r})  = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}) (x - x'),  
-\end{equation}
-it can be calculated easily by
-\begin{equation}
- W_{mn}^x({\bf r})  = x \, w_{mn}({\bf r}) - w_{mn}^x({\bf r})
-\end{equation}
-with 
-\begin{equation}
- w_{mn}({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}), 
+\subsection{General equations for a two-electron system}
+According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
+\begin{equation}
+ \label{ht_def_g}
+ e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
+\end{equation}
+where $\hat{\hat{\tau}} = \sum_{i>j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i>j \frac{1}{r_{ij}}}$. 
+This leads to the following similarity transformed Hamiltonian 
+\begin{equation}
+ \begin{aligned}
+ \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
+           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{K}(\bri{i},\bri{j}) ) = \frac{1}{2} \bigg( &\nabla_i^2 u(\bri{i},\bri{j}) + \nabla_j^2u(\bri{i},\bri{j}) \\
+                                               + &\big(\nabla_i u(\bri{i},\bri{j}) \big) ^2 + \big(\nabla_i u(\bri{i},\bri{j}) \big) ^2 \bigg) \\
+                                               + &\nabla_i u(\bri{i},\bri{j}) \cdot \nabla_j + \nabla_j u(\bri{i},\bri{j}) \cdot \nabla_i  \\
+ \end{aligned}
+\end{equation}
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{L}(\bri{i},\bri{j},\bri{k}) ) = & \nabla_i u(\bri{i},\bri{j}) \cdot \nabla_i u(\bri{i},\bri{k}) + \nabla_j u(\bri{j},\bri{i}) \cdot \nabla_j u(\bri{j},\bri{k})  \\
+                                     + & \nabla_k u(\bri{k},\bri{i}) \cdot \nabla_k u(\bri{k},\bri{j})
+ \end{aligned}
+\end{equation}
+
+Of course, only the differential terms do not commute in Eq. \eqref{ht_def_g}. 
+Let us compute each terms, beginning with the action of $\big[ H,\hat{\tau} \big]$ on a function $\phi(\br{}_1,\hdots \br{}_N)$.
+\begin{equation}
+ \label{eq:com1_1}
+ \begin{aligned}
+ \bigg[ H,\hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
+  & = -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\
+  & +  \frac{1}{2} \sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \nabla^2_i \phi(\br{}_1,\hdots \br{}_N). 
+ \end{aligned}
+\end{equation}
+The first term in the right-hand side of Eq. \eqref{eq:com1_1} is 
+\begin{equation}
+ \label{eq:com1_2}
+ \begin{aligned}
+&  -\frac{1}{2} \sum_i \nabla^2_i\bigg( \sum_{j>k} u(\br{}_j,\br{}_k) \phi(\br{}_1,\hdots \br{}_N) \bigg) \\ 
+= &-\frac{1}{2}\sum_{j>k} u(\br{}_j,\br{}_k) \sum_i \bigg( \nabla^2_i \phi(\br{}_1,\hdots \br{}_N)\bigg) \\
+  &-\frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
+  &-\sum_i \bigg(\nabla_i \sum_{j>k}u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).
+ \end{aligned}
+\end{equation}
+Inserting Eq. \eqref{eq:com1_2} in Eq. \eqref{eq:com1_1} leads to cancellation of the terms involving $\nabla^2_i \phi(\br{}_1,\hdots \br{}_N)$
+\begin{equation}
+ \label{eq:com1_3}
+  \begin{aligned}
+ \big[ H,\hat{\tau} \big]\phi(\br{}_1,\hdots \br{}_N) & =  \frac{1}{2}\phi(\br{}_1,\hdots \br{}_N) \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
+  & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg)
+ \end{aligned}
+\end{equation}
+and therefore one can write the first commutator of Eq. \eqref{ht_def_g} as 
+\begin{equation}
+ \label{eq:com1_4}
+ \begin{aligned}
+  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \\
+                            & -\sum_i \bigg(\nabla_i \sum_{j>k} u(\br{}_j,\br{}_k) \bigg) \cdot \bigg( \nabla_i  \bigg),
+ \end{aligned}
+\end{equation}
+and as $\nabla_i f(\br{}_j) = \delta_{ij} \nabla_i f(\br{}_i)$ one obtains 
+\begin{equation}
+ \label{eq:com1_5}
+ \begin{aligned}
+  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg) \\
+                            & -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) \\
+                            & -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg).  
+ \end{aligned}
+\end{equation}
+Then, one has to compute the second-order commutator in Eq. \eqref{ht_def_g}: 
+\begin{equation}
+ \label{eq:com2_1}
+ \begin{aligned}
+ & \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] \phi(\br{}_1,\hdots \br{}_N) = \\
+ & \bigg[ -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i,\br{}_j) + \sum_j \nabla^2_j u(\br{}_i,\br{}_j) ) \bigg), \sum_{j>k} u(\br{}_j,\br{}_k)  \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
++& \bigg[ -\sum_i \bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N) \\
++& \bigg[ -\sum_i \bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg), \sum_{j>k} u(\br{}_j,\br{}_k) \bigg] \phi(\br{}_1,\hdots \br{}_N). 
+ \end{aligned}
+\end{equation}
+The first term in Eq. \eqref{eq:com2_1} is actually a potential term and therefore it cancels out, then it comes
+\begin{equation}
+ \label{eq:com2_2}
+ \begin{aligned}
+  \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 - \sum_j \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 
+ \end{aligned}
+\end{equation}
+and so the two commutators become
+\begin{equation}
+ \begin{aligned}
+ \label{eq:comtot}
+& \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\
+   &\sum_{i>j} -\frac{1}{2} \bigg( \nabla^2_i u(\br{}_i,\br{}_j) +  \nabla^2_j u(\br{}_i,\br{}_j) 
+    + \bigg( \nabla_i u(\br{}_i,\br{}_j) \bigg)^2 + \bigg( \nabla_j u(\br{}_i, \br{}_j) \bigg)^2  \bigg) \\
+   & -\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_i  \bigg) -\bigg(\nabla_j u(\br{}_i,\br{}_j)\bigg) \cdot \bigg( \nabla_j  \bigg). 
+ \end{aligned}
+\end{equation}
+
+\section{Computations of integrals}
+\subsection{$\nabla_i u(\br{}_i,\br{}_j)$}
+\begin{equation}
+ \nabla_1 u(\br{}_1,\br{}_2) = \deriv{}{x_1}{}u(r_{12}) {\bf e}_{x1} + \deriv{}{y_1}{}u(r_{12}) {\bf e}_{y1} + \deriv{}{z_1}{}u(r_{12}) {\bf e}_{z1},
 \end{equation}
@@
 \begin{equation}
-  w_{mn}^x({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'})  x'.
-\end{equation}
-Then, one can rewrite the matrix element of Eq. \eqref{eq:l_1x} as
-\begin{equation}
- \begin{aligned}
- \label{eq:l_1x_2}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
- \end{aligned}
-\end{equation}
-which can be easily evaluated numerically. 
-Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3})$ is simply 
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
- \end{aligned}
-\end{equation}
-which can be numerically evaluated easily. 
-The total matrix element of the full operator is then 
-\begin{equation}
- \label{eq:l_ijmkln_final}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
- + & \int \text{d}{\bf r}\phi_j({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
- + & \int \text{d}{\bf r} \phi_m({\bf r})  \phi_n({\bf r}) \bigg( W_{jl}^x({\bf r}) W_{ik}^x({\bf r}) + W_{jl}^y({\bf r}) W_{ik}^y({\bf r}) + W_{jl}^z({\bf r}) W_{ik}^z({\bf r})\bigg), 
- \end{aligned}
-\end{equation}
-which can be computed on the fly through a simple numerical integration.
-
+ \deriv{}{x_1}{}u(r_{12}) = \deriv{}{r_{12}}{}u(r_{12}) \deriv{r_{12}}{x_1}{},
+\end{equation}
+and as $r_{12} = \sqrt{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2} $ one has
+\begin{equation}
+ \deriv{r_{12}}{x_1}{} = \frac{x_1 - x_2}{r_{12}} = -\deriv{r_{12}}{x_2}{},
+\end{equation}
+and according to Eq. \eqref{def_j_0}
+\begin{equation}
+ \deriv{u}{r_{12}}{} = \frac{1 - \text{erf}(\mu r_{12})}{2},
+\end{equation}
+one obtains 
+\begin{equation}
+ \label{eq:dx1_u}
+ \deriv{}{x_1}{}u(r_{12}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
+\end{equation}
+Similarly, 
+\begin{equation}
+ \label{eq:dx2_u}
+ \deriv{}{x_2}{}u(r_{12}) = -\frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12} } \bigg(x_1 - x_2 \bigg).
+\end{equation}
+Therefore, 
+\begin{equation}
+ \label{eq:nabla_u}
+ \begin{aligned}
+ \nabla_1 u(\br{}_1,\br{}_2) = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
+ & \bigg( (x_1 - x_2) {\bf e}_{x1} + (y_1 - y_2) {\bf e}_{y1} + (z_1 - z_2) {\bf e}_{z1}\bigg) \\
+ &=  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big)
+ \end{aligned}
+\end{equation}
+
+\subsection{$\bigg(\nabla_i u(\br{}_i,\br{}_j)\bigg)^2$}
+According to Eq. \eqref{eq:nabla_u}, one obtains 
+\begin{equation}
+ \label{eq:nabla_u2_0}
+ \begin{aligned}
+ \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2 & = \bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg)^2\\
+ & \bigg( (x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2 \bigg) \\
+                                           &  \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4 \big(r_{12}\big)^2} \times \big(r_{12}\big)^2 \\
+                                           & = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
+ \end{aligned}
+\end{equation}
+and therefore 
+\begin{equation}
+ \label{eq:nabla_u2}
+ \bigg(\nabla_1 u(\br{}_1,\br{}_2)\bigg)^2  + \bigg(\nabla_2 u(\br{}_1,\br{}_2)\bigg)^2 = 2 \times \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}
+\end{equation}
+
+\subsection{$\nabla_i u(\br{}_i,\br{}_j) \cdot \bigg( \nabla_i   \bigg)$}
+According to Eq. \eqref{eq:nabla_u}, one obtains 
+Therefore, 
+\begin{equation}
+ \begin{aligned}
+ \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
+                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg).
+ \end{aligned}
+\end{equation}
+And noticing the minus sign coming from the derivative in $\br{}_2$, the total operator can be written as 
+\begin{equation}
+ \begin{aligned}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
+         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big) +
+         (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg),
+ \end{aligned}
+\end{equation}
+but as 
+\begin{equation}
+ \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
+\end{equation}
+one can rewrite as 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla0}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
+ \end{aligned}
+\end{equation}
+Then, introducing ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$, can notice that 
+\begin{equation}
+ \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
+\end{equation}
+and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
+\begin{equation}
+ \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
+\end{equation}
+and therefore 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla1}
+& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
+ = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{}. 
+ \end{aligned}
+\end{equation}
+
+\subsection{$\nabla^2_i u(\br{}_i,\br{}_j)$}
+\begin{equation}
+ \begin{aligned}
+ &\nabla^2_1 u(\br{}_1,\br{}_2) =  \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{y_{1}}{2}  u(\br{}_1,\br{}_2) + \deriv{}{z_{1}}{2}  u(\br{}_1,\br{}_2) \\
+                                 = & \deriv{}{x_{1}}{}\bigg( \deriv{}{x_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
+                                   \deriv{}{y_{1}}{}\bigg( \deriv{}{y_{1}}{}u(\br{}_1,\br{}_2) \bigg)  + 
+                                   \deriv{}{z_{1}}{}\bigg( \deriv{}{z_{1}}{}u(\br{}_1,\br{}_2) \bigg). 
+ \end{aligned}
+\end{equation}
+But according to Eq. \eqref{eq:dx1_u}, one obtains 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_0}
+& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{}\bigg(\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
+& = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
+ \end{aligned}
+\end{equation}
+Similarly, according to Eq. \eqref{eq:dx2_u} one obtains for the second order derivative in $x_2$
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x2_0}
+& \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{2}}{}\bigg(\frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}} \big(x_1 - x_2 \big) \bigg) \\
+& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) -  \frac{\text{erf}(\mu r_{12}) -1}{2 r_{12}} \\
+& = \bigg( \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -1 }{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{ 1 - \text{erf}(\mu r_{12})}{2 r_{12}}. 
+ \end{aligned}
+\end{equation}
+Also
+\begin{equation}
+ \label{eq:d2_x1_1}
+ \begin{aligned}
+ \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = & \deriv{}{r_{12}}{}\bigg( \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) \deriv{r_{12}}{x_1}{} \\
+      = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} 
+ \end{aligned}
+\end{equation}
+and similarly
+\begin{equation}
+ \label{eq:d2_x2_1}
+ \begin{aligned}
+ \deriv{}{x_2}{} \frac{\text{erf}(\mu r_{12}) -  1}{2 r_{12}}  = &\deriv{}{r_{12}}{}\bigg( \frac{\text{erf}(\mu r_{12}) - 1}{2 r_{12}}\bigg) \deriv{r_{12}}{x_2}{} \\
+              = & (-1) \frac{x_1 - x_2}{r_{12}} (-1)  \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+              = & \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+              = & \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}},
+ \end{aligned}
+\end{equation}
+which implies that 
+\begin{equation}
+  \label{eq:d2_x2_2}
+ \deriv{}{x_{2}}{2}  u(\br{}_1,\br{}_2) = \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2).
+\end{equation}
+
+To continue, as 
+\begin{equation}
+ \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} = -\frac{1}{r_{12}}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg),
+\end{equation}
+one obtains 
+\begin{equation}
+ \label{eq:d2_x1_2}
+ \begin{aligned}
+ \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} & = \frac{x_1 - x_2}{r_{12}} \deriv{}{r_{12}}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+ & =  -\frac{(x_1 - x_2)}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg). 
+ \end{aligned}
+\end{equation}
+
+Therefore, Eq. \eqref{eq:d2_x1_0} becomes 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_2}
+& \deriv{}{x_{1}}{2}  u(\br{}_1,\br{}_2) = \bigg( \deriv{}{x_1}{} \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}\bigg) (x_1 - x_2 ) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}  \\
+& = -\frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\bigg(\frac{1 - \text{erf}\big( \mu r_{12} \big)}{2 r_{12}}  + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \bigg) +  \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+& = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) 
+- \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
+ \end{aligned}
+\end{equation}
+implying that 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_3}
+ \bigg( \deriv{}{x_{1}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{z_{1}}{2} \bigg)  u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12}\big)^2},
+ \end{aligned}
+\end{equation}
+and therefore 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:lapl_u_final}
+ \bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} \bigg) u(\br{}_1,\br{}_2) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 1 - \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
+&- 2 \frac{(x_1 - x_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}.
+ \end{aligned}
+\end{equation}
+Therefore, 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_2}
+ &\bigg( \deriv{}{x_{1}}{2} + \deriv{}{x_{2}}{2} + \deriv{}{y_{1}}{2} + \deriv{}{y_{2}}{2} + \deriv{}{z_{1}}{2} + \deriv{}{z_{2}}{2} \bigg) u(\br{}_1,\br{}_2) \\ 
+ & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2} \bigg) \\ 
+&- 2 \frac{(x_1 - x_2)^2 + (y_1 - y_2)^2 + (z_1 - z_2)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
+ & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \bigg( 3 - \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2} \bigg) 
+- 2 \frac{\big(r_{12}\big)^2}{\big( r_{12} \big)^2}\frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
+ & =\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \times 2 - 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} \\
+ & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg)
+ \end{aligned}
+\end{equation}
+\subsection{Sum of all terms}
 According to Eq.

### 2020-12-02 cusp_j/paper/paper.tex

@@
 \newcommand{\muuegav}{\langle \mu_{\text{UEG}}\rangle}
+\newcommand{\muav}{\langle \mu\rangle}
 \newcommand{\mursc}{ \mu_{r_{s,c}}}
@@
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 
-full configuration Quantum Monte Carlo\cite{BooThoAla-JCP-09,BooAla-JCP-10,BooCleThoAla-JCP-11,GhaLozAla-JCP-19,VitAlaKat-JCTC-20} (FCI-QMC) or tensor product states\cite{ChaSha-AR-11,BaiRei-JCP-20}.
-These methods all have one thing in common: they manage to select, although through different mathematical forms, the dominant part of the exponentially growing Hilbert space that resulting from a $N$-electron problem among a given finite basis set.
+full configuration Quantum Monte Carlo\cite{BooThoAla-JCP-09,BooAla-JCP-10,BooCleThoAla-JCP-11,GhaLozAla-JCP-19,VitAlaKat-JCTC-20} (FCI-QMC) or matrix product states\cite{ChaSha-AR-11,BaiRei-JCP-20}.
+These methods all have one thing in common: they manage to select, although through different mathematical frameworks, the part of the exponentially growing Hilbert space which dominates the wave function.
 
@@
 Thanks to strong orthogonality,
-all redundant correlation effects of the geminal function are projected out of the wave function, 
-and therefore the geminal function only deals with correlation orthonormal to the basis set. 
+all redundant correlation effects between the geminal function and the basis set are projected out of the wave function, 
+and therefore the geminal function only deals with correlation effects orthonormal to the basis set. 
 The resulting F12 theories, mainly based on perturbation theory and coupled cluster theory, are therefore 
-extremely close to their parent theory, with additional integrals two- and three-body terms resulting from the use of the geminal function. 
+extremely close to their parent theory, with additional two- and three-body terms resulting from the use of the geminal function. 
 It is important to notice that because of the orthogonalization between the geminal and the basis set, 
@@
 Therefore, no strong compression of the electronic wave function is obtained by the F12 theory,
-but a fast convergence toward the complete basis set limit (CBS) is nevertheless obtained.
-
-An alternative point of view using a geminal function is the so-called transcorrelated (TC) approach where the full effect of the geminal function is incorporated into the calculation through a similarity transformation of the original Hamiltonian.
+but a fast convergence toward the complete basis set limit (CBS) is nevertheless obtained for correlation energies and other properties sensitive to the basis set.
+
+An alternative point of view using a geminal function is the so-called transcorrelated (TC) approach where the full effect of the geminal function is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the geminal function.
 The pioneers of such theory were Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} where they derive the equations of the general form of the TC Hamiltonian which is non hermitian and contains explicitly three-body interaction.
-Despite the loss of variational principle due to the non hermitian nature of the TC Hamiltonian, the parameters optimized by Boys and Handy were mainly the orbitals of a single Slater determinant together with the mathematical form of the geminal function with which one performs the similarity transformation of the Hamiltonian to obtain the TC Hamiltonian.
+Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, but Boys and Handy nevertheless managed to derive equations to optimize orbitals and geminal parameters for a single Slater determinant.
 
@@
 In Ref.\onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
-which allows to treat the non-hermitian TC Hamiltonian in a many-body framework which is therefore more suited 
+which allows to treat the non-hermitian TC Hamiltonian in a mathematical form more suited 
 to develop many-body perturbation theory approaches. 
@@
 For the sake of simplicity, we derive the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
-Then we focus on the behaviour at small $r_{12}$ of different flavours of Hamiltonians 
-and the corresponding discontinuity in their eigenvectors. 
-We browse three different types of Hamiltonians: the usual physical Hamiltonian, the transcorrelated Hamiltonian together with the effective Hamiltonian used in RS-DFT.
-Based on such consideration, we propose a new Jastrow factor mimicking RS-DFT Hamiltonian at small $r_{12}$. 
+Based on such a simple mathematical structure, we propose a new Jastrow factor mimicking RS-DFT Hamiltonian at small $r_{12}$. 
 Then, we derive the analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$ in the case of a general $N$-electron system, and study its physical content as a  function of the parameter $\mu$.
-
-\subsection{A simple physical picture: the case of the helium atom}
-\subsubsection{The transcorrelated Hamiltonian for helium atom}
+MAKE THE LINK WITH WORK OF TENNO AND ALAVI
+
+\subsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
 Let us write the Hamiltonian of the helium atom in the $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
@@
      &-\bigg( \frac{\bd{r_1}}{r_1} \cdot \frac{\bd{r_{12}} }{r_{12}}  \deriv{}{r_1}{} + 
-                \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg),
+                \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg).
  \end{aligned}
@@
 \end{equation}
-After some derivation, one can notice that by defining the following operators 
+By defining the following operators 
 \begin{equation}
@@
  \label{eq:ht_general}
- \tilde{H}[u] = h_c + \frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] + \tilde{t}[u] ,
+ \tilde{H}[u] = h_c + \frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] + \tilde{t}[u].
 \end{equation}
@@
 
-\subsubsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
-\label{sec:cusp}
-Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
-The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill.
-For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are general for any bounded eigenvectors.
-
-In the case of the usual Hamiltonian, the exact ground state wave function $\psiex$ must satisfy the Schroedinger equation in real space 
-\begin{equation}
- H \psiex(\br{}_1,\br{}_2) = E_0 \psiex(\br{}_1,\br{}_2)\quad \forall (\br{}_1,\br{}_2).
-\end{equation}
-When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
-\begin{equation}
- \label{eq:cusp_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
-\end{equation}
-or equivalently by multiplying Eq. \eqref{eq:cusp_0} by $r_{12}$
-\begin{equation}
- \lim_{r_{12}\rightarrow 0}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
-\end{equation}
-which translates into the famous cusp condition for antiparallel spins of Kato\cite{Kat-CPAM-57}, 
-\begin{equation}
- \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
-\end{equation} 
-For an excellent pedagogical and general derivation of the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.
-
-Regarding now the similarity transformed Hamiltonians, the exact ground state eigenvector must also satisfy an eigenvalue equation in real-space,
-\begin{equation}
- \label{eq:hpi0_ex}
- \tilde{H}[u] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
-\end{equation}
-Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
-which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
-\begin{equation}
- \label{eq:cusp_phi_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{u(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
-\end{equation}
-Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
-Therefore, as long as one imposes that 
-\begin{equation}
- \label{eq:cusp_phi_1}
-  \deriv{u(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
-\end{equation}
-which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
-Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
-\begin{equation}
- \label{eq:cusp_phi_2}
- \deriv{\phiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
-\end{equation}
-which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[u]$ is cuspless. 
-For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
-the constraint of fulfilling the cusp condition.
-
-Another form of effective Hamiltonians leading to cuspless eigenfunctions are those obtained from RS-DFT 
-where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively.
-The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ it gives back the usual Kohn-Sham theory.
-In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
-Applied to a two electron system and looking in regions where $r_{12}\approx 0$, the leading terms of the self-consistent Schroedinger-like equation of RS-DFT reads 
-\begin{equation}
- \label{eq:cusp_psi_mu_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
-\end{equation}
-and as the effective interaction $\frac{\text{erf}(\mu r_{12})}{r_{12}}$ is non divergent at $r_{12}=0$ for finite values of $\mu$
-\begin{equation}
- \lim_{r_{12} \rightarrow 0} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{2 \mu}{\sqrt{\pi}} , 
-\end{equation}
-one obtains that 
-\begin{equation}
- \label{eq:cusp_psi_mu_1}
- \deriv{\Psi^\mu(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
-\end{equation}
-which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.
-
-Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
-
 \subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
-In section \ref{sec:cusp} we reviewed the forms of limit conditions at $r_{12}=0$ involved in different eigenvalue equations, which of course depends on the nature of the interaction at $r_{12}=0$. 
+MAKE THE LINK WITH WORK OF TENNO AND ALAVI
 In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order in $1/r_{12}$.
@@
 \subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
-\subsubsection{Explicit form of $\tilde{H}[\mu]$ }
+\label{sec:ht_general}
+\subsubsection{General form of $\tilde{H}[\mu]$ }
 Having established the analytical expression of $u(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
@@
 
-\subsection{Explicit form for the operators $\hat{K}(\bri{1},\bri{2}) )$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ }
-\subsubsection{Intermediate quantities}
-To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to a $\bri{1}$ which reads 
+\subsection{Analytical form for the operators $\hat{K}(\bri{1},\bri{2}) $ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ }
+To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
 \begin{equation}
@@
  \label{eq:nabla_i_nabla1}
- \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} r_{12} \deriv{}{r_{12}}{} \\
- = & \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
+ \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
  \end{aligned}
@@
 \end{equation}
-\subsubsection{Explicit form of $\tilde{H}[\mu]$}
+
 Summing all terms to recombine $\hat{K}(\bri{1},\bri{2})$ reads 
@@
 
+\subsection{Analytical form of $\tilde{H}[\mu]$}
 Having established the explicit form of $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
@@
 whose solution is unknown to the best of the author knowledge. 
-\subsubsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
+\subsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
 \label{sec:h_mu_lim}
@@
 \section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
+\label{sec:total_he}
 The first part of our study concerns the convergence of the eigenvalues of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
@@
 \section{Study of the helium isoelectronic series}
-Having investigated the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with $\mu$ and basis set used on the helium atom, we now study the ground state energies of the isoelectronic series of the helium atom H$^{-}$ to Ne$^{8+}$.
-As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depend on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which  they  converge significantly faster with the basis set with respect to the usual Hamiltonian.
-Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on the isoelectronic series of the helium atom.
-All these systems are weakly correlated, but they cover a quite wide range of densities.
-
-\subsection{A systematic way to find an optimal value of $\mu$ }
+\label{sec:iso_elec}
+Having investigated in the case of the helium atom the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with both $\mu$ and the basis set used, we now study the ground state energies of the isoelectronic series of the helium atom H$^{-}$ to Ne$^{8+}$.
+As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depends on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which they converge significantly faster with the basis set with respect to the usual Hamiltonian.
+Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on this isoelectronic series which consist in weakly correlated covering a quite wide range of densities.
+As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given system, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
+
 In order to find a systematic way to determine a reasonable value of $\mu$, one must keep in mind the physical meaning of such quantity: it has the unit of an inverse distance, and determines, at leading order, the depth of the hole imposed by the Jastrow factor.
-Therefore, it must have the typical scale of the inverse of correlation effects, which of course strongly depends on the system.
+Therefore, it must have the typical scale of the inverse of correlation effects, which of course strongly depends on the system through its density for instance.
 In the context of RS-DFT, Toulouse \textit{et.
@@
 We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ as value of $\mu$ in $\tilde{H}[\mu]$.
+We also report in the column $\muav$ of the Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets vary by less than $0.1\%$.
 As one can observe from  Table \ref{table_conv_e_mu_iso}, the ground state energies of $\tilde{H}[\murscav]$ converge much faster than that of the usual Hamiltonian as the MAD for the ground state energies is of 2.64 mH, 0.48 mH and 0.26 mH in the double-, triple- and quadruple zeta quality basis sets (respectively) whereas it is of 12.16 mH, 4.71 mH and 1.64 mH for the usual Hamiltonian.
 Also, one can observe that, except for the low density systems such as the H${^-}$ and He species, it converges from below the exact ground state energy.
+Regarding now the value of $\murscav $, one can notice that it increases with the atomic number, which is expected as the density becomes more picked near the nucleus as the nuclear charge increases, and therefore the typical inter electronic distance lowers with $Z$.
 
@@
 This implies that the values of $\muuegav$ are in general larger than that of $\murscav$, which was observed in the present calculations.
+Also, one can see that $ \muuegav$ increases with the system size and that, except for H$^-$, it is always larger than $\murscav$. 
 Because the MAD are essentially the same but that the MSD are of opposite sign, it means that there exists an optimal value of $\mu$ between $\murscav$ and $\muuegav$ which might be optimal. 
@@
 The mean absolute deviation (MAD) and mean signed deviation (MSD) are also reported for each basis set and method.
+We also report the average value of the $\mu$ considered (referred as $\muav$) in the double-zeta basis.
 }
 \begin{ruledtabular}
-\begin{tabular}{l|rrr||rrr||rrr|}
-             &\multicolumn{3}{c}{H$^-$}      & \multicolumn{3}{c}{He}       & \multicolumn{3}{c}{Li$^+$}    \\
-             &   DZ    &  TZ      &   QZ     &  DZ     &   TZ     &  QZ     &   DZ    &   TZ     &  QZ      \\                   
+\begin{tabular}{l|rrr|r||rrr|r||rrr|r|}
+                         &\multicolumn{4}{c}{H$^-$}                & \multicolumn{4}{c}{He}                  & \multicolumn{4}{c}{Li$^+$}               \\
+                         &   DZ    &  TZ      &   QZ    & $\muav$&  DZ     &   TZ     &  QZ  & $\muav$   &   DZ    &   TZ     &  QZ    & $\muav$  \\
 \hline 
- FCI         &   3.72  &    1.19  &   0.61   &  14.18  &   3.13   &  1.19   &  10.72  &   3.35   &  1.58    \\      
-$\muueg$     &   1.69  &    0.60  &   0.38   &  5.28   &   0.44   &  0.12   &  0.9    &   0.09   & -0.02    \\      
-$\murscav$   &   2.30  &    0.67  &   0.39   &  4.87   &   0.37   &  0.12   &  -0.82  &  -0.38   & -0.14    \\      
-$\mursclda$  &   2.03  &    0.64  &   0.39   &  5.07   &   0.40   &  0.12   &  0.04   &  -0.12   & -0.08    \\      
+ FCI                     &   3.72  &    1.19  &   0.61  &$+\infty$ &  14.18  &   3.13   &  1.19&$+\infty$    &  10.72  &   3.35   &  1.58  &$+\infty$  \\      
+$E_0^{\basis}[\muuegav]$ &   1.69  &    0.60  &   0.38  & 0.350    &  5.28   &   0.44   &  0.12& 0.815       &  0.9    &   0.09   & -0.02  & 1.274     \\      
+$E_0^{\basis}[\murscav]$ &   2.30  &    0.67  &   0.39  & 0.479    &  4.87   &   0.37   &  0.12& 0.771       &  -0.82  &  -0.38   & -0.14  & 0.980     \\      
+$E_0^{\basis}[\mursclda]$&   2.03  &    0.64  &   0.39  & 0.410    &  5.07   &   0.40   &  0.12& 0.792       &  0.04   &  -0.12   & -0.08  & 1.127     \\      
 \hline              
-             &\multicolumn{3}{c}{Be$^{2+}$}  & \multicolumn{3}{c}{B$^{3+}$} & \multicolumn{3}{c}{C$^{4+}$}    \\
- FCI         &  11.35  &   3.62   &  1.41    &  11.91  &   4.21   &  1.53   &  12.46  &   4.76   &  1.67    \\  
-$\muueg$     &  1.2    &   0.17   & -0.02    &  1.41   &   0.43   &  -0.01  &  1.67   &   0.37   &  0.01    \\  
-$\murscav$   &  -1.5   &  -0.53   & -0.17    &  -2.16  &  -0.34   &  -0.22  &  -2.69  &  -0.4    & -0.25    \\  
-$\mursclda$  &  -0.08  &  -0.15   & -0.09    &  -0.18  &   0.09   &  -0.11  &  -0.19  &   0.01   &  -0.1    \\  
+                         &\multicolumn{4}{c}{Be$^{2+}$}            & \multicolumn{4}{c}{B$^{3+}$}            & \multicolumn{4}{c}{C$^{4+}$}    \\
+                         &   DZ    &  TZ      &   QZ    & $\muav$&  DZ     &   TZ     &  QZ     & $\muav$&   DZ    &   TZ     &  QZ    & $\muav$  \\
 \hline 
-             &\multicolumn{3}{c}{N$^{5+}$}   & \multicolumn{3}{c}{O$^{6+}$} & \multicolumn{3}{c}{F$^{7+}$}    \\
- FCI         &  13.1   &   5.71   &  1.79    &  13.84  &   6.47   &  2.02   &  14.68  &   7.06   &  2.25    \\  
-$\muueg$     &  2.06   &   0.45   &  0.01    &  2.54   &   0.77   & -0.02   &  3.14   &   1.15   & -0.02    \\  
-$\murscav$   &  -2.97  &  -0.64   &  -0.26   & -3.13   &  -0.70   & -0.31   & -3.10   &  -0.54   & -0.36    \\  
-$\mursclda$  &  -0.01  &  -0.15   &  -0.09   &  0.27   &  -0.04   & -0.12   &  0.69   &   0.23   & -0.14    \\  
+ FCI                     &  11.35  &   3.62   &  1.41   &$+\infty$ &  11.91  &   4.21   &  1.53   &$+\infty$ &  12.46  &   4.76   &  1.67  &$+\infty$    \\  
+$E_0^{\basis}[\muuegav]$ &  1.2    &   0.17   & -0.02   &1.727     &  1.41   &   0.43   &  -0.01  &2.179     &  1.67   &   0.37   &  0.01  &2.631        \\  
+$E_0^{\basis}[\murscav]$ &  -1.5   &  -0.53   & -0.17   &2.152     &  -2.16  &  -0.34   &  -0.22  &1.300     &  -2.69  &  -0.4    & -0.25  &1.434        \\  
+$E_0^{\basis}[\mursclda]$&  -0.08  &  -0.15   & -0.09   &1.440     &  -0.18  &   0.09   &  -0.11  &1.740     &  -0.19  &   0.01   &  -0.1  &2.032        \\  
 \hline              
-             &\multicolumn{3}{c}{Ne$^{8+}$}  & \multicolumn{3}{c}{MAD} & \multicolumn{3}{c}{MSD}    \\
- FCI         &  15.66  &   7.61   &  2.36    & 12.16   &    4.71  &    1.64   &  12.16   &   4.71   &    1.64   \\   
-$\muueg$     &  3.89   &   1.57   &  0.03    & 2.38    &    0.60  &    0.07   &   2.38   &   0.60   &    0.07   \\   
-$\murscav$   &  -2.85  &  -0.28   & -0.35    & 2.64    &    0.48  &    0.26   &  -1.21   &  -0.28   &   -0.16   \\   
-$\mursclda$  &  1.26   &   0.57   & -0.1     & 0.98    &    0.24  &    0.13   &   0.89   &   0.15   &   -0.03   \\   
+                         &\multicolumn{4}{c}{N$^{5+}$}   & \multicolumn{4}{c}{O$^{6+}$}            & \multicolumn{4}{c}{F$^{7+}$}    \\
+                         &   DZ    &  TZ      &   QZ     & $\muav$ &  DZ     &   TZ    &  QZ     & $\muav$&   DZ    &   TZ     &  QZ    & $\muav$  \\
+\hline              
+ FCI                     &  13.1   &   5.71   &  1.79    &$+\infty$  &  13.84  &   6.47  &  2.02   &$+\infty$ &  14.68  &   7.06   &  2.25   &$+\infty$   \\  
+$E_0^{\basis}[\muuegav]$ &  2.06   &   0.45   &  0.01    &3.082      &  2.54   &   0.77  & -0.02   &3.533     &  3.14   &   1.15   & -0.02   &3.984       \\  
+$E_0^{\basis}[\murscav]$ &  -2.97  &  -0.64   &  -0.26   &1.556      & -3.13   &  -0.70  & -0.31   &1.670     & -3.10   &  -0.54   & -0.36   &1.774       \\  
+$E_0^{\basis}[\mursclda]$&  -0.01  &  -0.15   &  -0.09   &2.318      &  0.27   &  -0.04  & -0.12   &2.600     &  0.69   &   0.23   & -0.14   &2.879       \\  
+\hline              
+                         &\multicolumn{4}{c}{Ne$^{8+}$}  & \multicolumn{4}{c}{MAD} & \multicolumn{4}{c}{MSD}    \\
+                         &   DZ    &  TZ      &   QZ     & $\muav$ &  DZ     &   TZ     &  QZ     &          &   DZ    &   TZ     &  QZ    &            \\
+\hline              
+ FCI                     &  15.66  &   7.61   &  2.36    &$+\infty$  & 12.16   &    4.71  &    1.64 &          &  12.16   &   4.71   &    1.64&             \\   
+$E_0^{\basis}[\muuegav]$ &  3.89   &   1.57   &  0.03    &4.434      & 2.38    &    0.60  &    0.07 &          &   2.38   &   0.60   &    0.07&             \\   
+$E_0^{\basis}[\murscav]$ &  -2.85  &  -0.28   & -0.35    &1.874      & 2.64    &    0.48  &    0.26 &          &  -1.21   &  -0.28   &   -0.16&             \\   
+$E_0^{\basis}[\mursclda]$&  1.26   &   0.57   & -0.1     &3.1543     & 0.98    &    0.24  &    0.13 &          &   0.89   &   0.15   &   -0.03&             \\   
 \end{tabular}
@@
 \end{table*}
+
+\section{Application on H$_2$}
+Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we study in the last part of the present study study the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$.
+As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
+We report in Figs \ref{}
+
+\begin{figure*}
+ \label{fig:mu_1.0_dz_3}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
+        \caption{
+        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
+}
+\end{figure*}
 
@@
 which corresponds precisely to Eq. \eqref{eq:h_tilde_r12}.
+
+\section{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
+\label{sec:cusp}
+Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
+The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill.
+For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are general for any bounded eigenvectors.
+
+In the case of the usual Hamiltonian, the exact ground state wave function $\psiex$ must satisfy the Schroedinger equation in real space 
+\begin{equation}
+ H \psiex(\br{}_1,\br{}_2) = E_0 \psiex(\br{}_1,\br{}_2)\quad \forall (\br{}_1,\br{}_2).
+\end{equation}
+When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
+\begin{equation}
+ \label{eq:cusp_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
+\end{equation}
+or equivalently by multiplying Eq. \eqref{eq:cusp_0} by $r_{12}$
+\begin{equation}
+ \lim_{r_{12}\rightarrow 0}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
+\end{equation}
+which translates into the famous cusp condition for antiparallel spins of Kato\cite{Kat-CPAM-57}, 
+\begin{equation}
+ \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
+\end{equation} 
+For an excellent pedagogical and general derivation of the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.
+
+Regarding now the similarity transformed Hamiltonians, the exact ground state eigenvector must also satisfy an eigenvalue equation in real-space,
+\begin{equation}
+ \label{eq:hpi0_ex}
+ \tilde{H}[u] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
+\end{equation}
+Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
+which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
+\begin{equation}
+ \label{eq:cusp_phi_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{u(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
+\end{equation}
+Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
+Therefore, as long as one imposes that 
+\begin{equation}
+ \label{eq:cusp_phi_1}
+  \deriv{u(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
+\end{equation}
+which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
+Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
+\begin{equation}
+ \label{eq:cusp_phi_2}
+ \deriv{\phiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
+\end{equation}
+which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[u]$ is cuspless. 
+For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
+the constraint of fulfilling the cusp condition.
+
+Another form of effective Hamiltonians leading to cuspless eigenfunctions are those obtained from RS-DFT 
+where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively.
+The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ it gives back the usual Kohn-Sham theory.
+In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
+Applied to a two electron system and looking in regions where $r_{12}\approx 0$, the leading terms of the self-consistent Schroedinger-like equation of RS-DFT reads 
+\begin{equation}
+ \label{eq:cusp_psi_mu_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
+\end{equation}
+and as the effective interaction $\frac{\text{erf}(\mu r_{12})}{r_{12}}$ is non divergent at $r_{12}=0$ for finite values of $\mu$
+\begin{equation}
+ \lim_{r_{12} \rightarrow 0} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{2 \mu}{\sqrt{\pi}} , 
+\end{equation}
+one obtains that 
+\begin{equation}
+ \label{eq:cusp_psi_mu_1}
+ \deriv{\Psi^\mu(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
+\end{equation}
+which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.
+
+Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
 

### 2020-12-02 cusp_j/paper/paper_draft.tex
added Ten No integrals

--- 2020-12-02 cusp_j/paper/paper.tex
@@
 Even if these selection schemes are extremely efficient to obtain a qualitative description of the wave function, a quantitative description is often out of reach as it implies the use of very large one-electron basis sets which are needed to recover the slowly converging correlation effects near the electron-electron coalescence point.
-These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance: the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
-As shown by the seminal works of Hylleraas \cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the size of the basis set is mainly due to the impossibility to represent the cusp in a finite basis set.
-To tackle this problem, the introduction of functions explicitly depending on the inter-electronic coordinate (F12) have emerged\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18}.
-In the F12 schemes, the geminal function depending on the inter-electronic coordinate is used to describe short-range correlation effects which are absent from the finite basis set.
+These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance ($r_{12}\approx 0$): the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
+As shown by the seminal works of Hylleraas \cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
+As the cusp conditions originate from the divergence of the Coulomb potential at $r_{12}=0$, an alternative approach would be to develop theories dealing with a smooth potential.
+Such a path was followed by three distinct branches:
+the explicitly correlated methods (F12), transcorrelated methods (TC) and the range-separated density functional theory (RS-DFT).
+
+In RS-DFT\cite{Sav-INC-96a,TouColSav-PRA-04}, the electron-electron interaction is split into a smooth long-range part and a complementary short-range diverging part, the former being treated explicitly by a wave function and the latter by a density functional.
+Such a splitting is done through the function $\text{erf}(\mu r_{12})$ where $\mu$ is the range separation parameter which allows one to continually move from Kohn-Sham DFT ($\mu=0$) to pure WFT ($\mu=\infty$).
+As the effective Hamiltonian is smooth at $r_{12}=0$ for a finite value of $\mu$, the corresponding eigenfunction has no electron-electron cusp\cite{GorSav-PRA-06} and therefore the convergence of the results with respect to the basis set are exponential\cite{FraMusLupTou-JCP-15}.
+A number of approximate RS-DFT schemes have been developed involving single-reference\cite{AngGerSavTou-PRA-05, GolWerSto-PCCP-05, TouGerJanSavAng-PRL-09,JanHenScu-JCP-09,TouZhuSavJanAng-JCP-11, MusReiAngTou-JCP-15,KalTou-JCP-18,KalMusTou-JCP-19} and multi-reference\cite{LeiStoWerSav-CPL-97, FroTouJen-JCP-07, FroCimJen-PRA-10, HedKneKieJenRei-JCP-15, HedTouJen-JCP-18, FerGinTou-JCP-18} WFT methods.
+Nevertheless, there are still some open issues in RSDFT, such as remaining fractional-charge and fractional-spin errors in the short-range density functionals \cite{MusTou-MP-17} or the dependence of the quality of the results on the value of the range-separation parameter $\mu$.
+
+Another approach to tackle the problems of WFT related to the electron cusp have been proposed by the F12 methods which introduce a function explicitly depending on the inter-electronic coordinate\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18} (called a Jastrow factor) to describe short-range correlation effects which are absent from the finite basis set.
 Thanks to strong orthogonality,
-all redundant correlation effects between the geminal function and the basis set are projected out of the wave function, 
-and therefore the geminal function only deals with correlation effects orthonormal to the basis set. 
+all redundant correlation effects between the Jastrow factor and the basis set are projected out of the wave function, 
+and therefore the Jastrow factor only deals with correlation effects orthonormal to the basis set. 
 The resulting F12 theories, mainly based on perturbation theory and coupled cluster theory, are therefore 
-extremely close to their parent theory, with additional two- and three-body terms resulting from the use of the geminal function. 
-It is important to notice that because of the orthogonalization between the geminal and the basis set, 
-the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and their usual parent.
-Therefore, no strong compression of the electronic wave function is obtained by the F12 theory,
+extremely close to their parent WFT theory, with additional contributions involving two- and three-body terms resulting from the use of the Jastrow factor. 
+It is important to notice that because of the orthogonalization between the Jastrow and the basis set, 
+the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and the usual theory in WFT.
+Therefore, no strong compression of the electronic wave function is obtained within a given basis set by the F12 theory,
 but a fast convergence toward the complete basis set limit (CBS) is nevertheless obtained for correlation energies and other properties sensitive to the basis set.
 
-An alternative point of view using a geminal function is the so-called transcorrelated (TC) approach where the full effect of the geminal function is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the geminal function.
-The pioneers of such theory were Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} where they derive the equations of the general form of the TC Hamiltonian which is non hermitian and contains explicitly three-body interaction.
-Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, but Boys and Handy nevertheless managed to derive equations to optimize orbitals and geminal parameters for a single Slater determinant.
-
-Later on, Ten-No\cite{Ten-No-CPL-00} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the geminal function, one uses a more elaborate many body theory (Moller-Plesset at second order in Refs.\onlinecite{Ten-No-CPL-00,HinTanTen-JCP-01} and coupled cluster in later works\cite{HinTanTen-CPL-02}) with a fixed universal geminal function.
-Such a geminal function, developed as a linear combination of gaussian functions, is optimized in order to remove the divergent character of the coulomb potential within the TC framework.
+An alternative point of view using a Jastrow factor is the so-called transcorrelated (TC) approach where the full effect of the Jastrow factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the Jastrow factor.
+The pioneers of such theory were Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} where they derive the equations of the general form of the TC Hamiltonian which contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.
+Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize orbitals and Jastrow parameters for a single Slater determinant.
+Nevertheless, such a constrained form of the wave function for the Slater part often leads to energies far below the exact one.
+
+Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a fixed universal Jastrow factor.
+This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}).
+As in F12 theories, the Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions, only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
+The use of gaussian functions to represent the Jastrow factor enabled Ten-No to develop a numerical scheme to evaluate exactly the three-electron integrals present in TC Hamiltonian\cite{TenNo-CPL-00-b}, which is an alternative to the density-fitting method proposed by Ten-No in the general context of F12 methods\cite{TenMan-JCP-03}.
 In Ref.\onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
@@
 the biorthogonal and usual orthogonal approaches give the same results. 
-Nevertheless, as approximations are necessary made in the wave function ansatz in realistic systems, 
+Nevertheless, as approximations are necessary done in the wave function ansatz for realistic systems, 
 the biorthogonal approach might improve the quality of the results.
@@
 An attempt to make TC equations variational have been proposed by Luo\cite{Luo-JCP-10,Luo-JCP-11} based on the empirical experience that in the original single determinant TC approach of Boys and Handy, the orbital optimization seemed to be the source of loss of the variational property.
-Luo therefore proposed to replace the original TC equations to optimize the orbitals by that of a general Jastrow-Slater ansatz.
-
-Yanai and Chan
+Luo therefore proposed to replace the original TC equations to optimize the orbitals by that of a general Jastrow-Slater ansatz in VMC.
+An alternative to the non hermitian nature of TC theory have been proposed by Yanai \textit{et.
+al.}\cite{YanShi-JCP-12}  where the Jastrow factor is expressed as an anti-hermitian operator, allowing one to obtain an hermitian effective Hamiltonian after the similarity transformation, which is then efficiently truncated through the use the canonical transformation\cite{NeuYanCha-MolPhys-10}.
+
+Further developments of the TC method towards the treatment of solid state systems have been carried by Ochi \textit{et.
+al.}\cite{OchSodSakTsu-JCP-12,OchTsu-JCTC-14,OchTsu-CPL-15,OchYamAriTsu-JCP-16}, which includes both ground states calculations within a single determinant wave function \cite{OchSodSakTsu-JCP-12,OchYamAriTsu-JCP-16} or at the MP2 level\cite{OchTsu-CPL-15}, together with excited states within configuration interaction\cite{OchTsu-JCTC-14}.
+The TC framework has also been used in the context of DFT to develop new approximations of density functionals\cite{ImaScu-JCP-03,UmeChi-PRA-06,Umezawa-JCP-17}.
 
 More recently, Alavi \textit{et.
-al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations to elaborate geminal functions explicitly taking into account for electron-electron correlation together with electron-electron-nucleus distance.
-The geminal function used in such work were obtained from the optimized Jastrow factors for He to Ne of Moskowitz \textit{et.
+al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations with the use of elaborate Jastrow factors obtained from quantum Monte Carlo calculations, and explicitly taking into account for electron-electron together with electron-electron-nucleus correlation.
+The Jastrow factor used in such work were obtained from the optimized Jastrow factors for He to Ne of Moskowitz \textit{et.
 al.}\cite{SchMos-JCP-90}.
-The main advantage of Alavi work relies on the fact that they allow a full flexibility to the Slater part of the wave function to adapt to the elaborated geminal functions.
-This is done through the use of a projective technique, the FCI-QMC, which allows to obtain the ground state of an operator, hermitian or not, through a stochastic sampling of the Hilbert space.
+In contrast to previous works where a constrained form was given to the wave function (such as coupled cluster for instance\cite{HinTanTen-CPL-02}),  Alavi \textit{et.
+al.} allow a full flexibility to the Slater part of the wave function to adapt to the elaborated Jastrow factors: they fully solve the $N$-electron problem corresponding to the TC Hamiltonian within a given basis set.
+This is done through the use of the FCI-QMC\cite{BooThoAla-JCP-09,BooAla-JCP-10,BooCleThoAla-JCP-11,GhaLozAla-JCP-19,VitAlaKat-JCTC-20} which is a projective technique allowing one to obtain the ground state of an operator, hermitian or not, through a stochastic sampling of the corresponding Hilbert space.
 Their approach share common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions,
@@
 
+In the present work, we derive a new form of Jastrow factor and corresponding TC Hamiltonian which are inspired by the RS-DFT effective Hamiltonian.
+As in RS-DFT, the new TC Hamiltonian and Jastrow factor are tuned by a unique range separation parameter $\mu$.
+The aim of this study is to establish the analytical form of the TC Hamiltonian and perform a numerical study on the ground state eigenvalues and eigenvectors on a set of two-electron atomic and molecular systems: the helium isoelectronic series from H$^-$ to Ne$^{8+}$ and H$_2$ molecule.
+In the context of the TC theory the interesting features of the present work are that i) the analytical form of the TC Hamiltonian is explicitly known and it turns out that all two-electron integrals can be performed analytically, ii) it is tuned by a unique parameter $\mu$ and therefore allows some flexibility, iii) there always exists a regime of $\mu$ which significantly improve the basis set convergence of WFT, iv) we propose schemes to find a value of $\mu$ which automatically adapts to the system and improves basis set convergence.
+
 The paper is organized as follows. 
-In the first section, inspired by the short-range behaviour of RS-DFT effective wave functions,  
+In the first section, inspired by the RS-DFT effective Hamiltonian,  
 we derive the analytical form of a new Jastrow factor tuned by a unique parameter $\mu$, and discuss the physical content of such a simple Jastrow factor. 
@@
 Based on such encouraging results, we study the ground state energy of the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
-a value of $\mu$ which depends on the system and still provides a fast convergence of the total energies. 
+a value of $\mu$ which automatically adapts to the system and still provides a fast convergence of the total energies. 
 Eventually, we study the H$_2$ molecule and compare different regimes of correlation.
 
-\section{A new form of Jastrow factor for transcorrelated Hamiltonian}
-This section is dedicated to the derivation of a new form of Jastrow factor mimicking at short range the correlation effects of RS-DFT. 
-For the sake of simplicity, we derive the transcorrelated Hamiltonian for the helium atom for a general Jastrow factor depending on the inter electronic distance.  
-Based on such a simple mathematical structure, we propose a new Jastrow factor mimicking RS-DFT Hamiltonian at small $r_{12}$. 
+\section{A new form of Jastrow factor for transcorrelated Hamiltonians}
+This section is dedicated to the derivation of a new form of Jastrow factor mimicking at short range the effective Hamiltonian of RS-DFT. 
+For the sake of simplicity, we derive the main equations in the case of the helium atom which have an explicit form in terms of the $r_{12}$ coordinate. 
 Then, we derive the analytical form of the corresponding new transcorrelated Hamiltonians $\tilde{H}[\mu]$ in the case of a general $N$-electron system, and study its physical content as a  function of the parameter $\mu$.
-MAKE THE LINK WITH WORK OF TENNO AND ALAVI
 
@@
 \subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
-MAKE THE LINK WITH WORK OF TENNO AND ALAVI
 In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order in $1/r_{12}$.
@@
 
+The main difference with the original proposal of the frozen Gaussian geminal of Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+we impose the structure of $u(r_{12};\mu)$ such that only the part of the scalar potential which is potentially diverging in $1/r_{12}$ (see Eq.\eqref{def_j_00}) compensates exactly the coulomb potential to provide an analytical smooth function $\frac{\text{erf}(\mu r_{12})}{r_{12}} $.
+
 \subsubsection{A few properties of $u(r_{12};\mu)$}
@@
  \label{ht_def_gu}
- \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
+ \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)^2  \bigg) \\
            & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{u}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{u},\bri{k}),
@@
    \hat{K}(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
+& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
   \end{aligned}
@@
                                       + & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{21} \cdot \frac{1 - \text{erf}(\mu r_{23})}{2 r_{23}} \bri{23} \\
-                                      + & \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{31} \cdot \frac{1 - \text{erf}(\mu r_{32})}{2 r_{32}} \bri{32}
+                                      + & \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{31} \cdot \frac{1 - \text{erf}(\mu r_{32})}{2 r_{32}} \bri{32}.
  \end{aligned}                    
@@
 
+\section{Integrals involved in TenNo work}
+The Jastrow factor of Ten-No is of the form
+\begin{equation}
+ u(r_{12})=\sum_{m=1}^{N_g} c_m e^{-\alpha_m \big(r_{12}\big)^2},
+\end{equation}
+where the $c_m$ and $\alpha_m$ are given in \cite{TenNo-CPL-00-a}. 
+To compute the transcorrelated Hamiltonian one needs to compute therefore 
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
+                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
+                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1.
+ \end{aligned}
+\end{equation}
+\subsection{Computation of the gradient}
+One can write that 
+\begin{equation}
+ u(r_{12})=\sum_{m=1}^{N_g} c_m v(r_{12},\alpha_m)
+\end{equation}
+with 
+\begin{equation}
+ v(r_{12},\alpha) = e^{-\alpha \big(r_{12}\big)^2}.
+\end{equation}
+The gradient with respect to $\br{1}$ is 
+\begin{equation}
+ \deriv{}{x_1}{} v(r_{12},\alpha) = -2 \alpha (x_1 - x_2) e^{-\alpha \big(r_{12}\big)^2},
+\end{equation}
+and one has of course 
+\begin{equation}
+ \deriv{}{x_2}{} v(r_{12},\alpha) = - \deriv{}{x_1}{} v(r_{12},\alpha). 
+\end{equation}
+\subsection{Computation of the non Hermitian term}
+One needs to compute 
+\begin{equation}
+ \nabla_1 v(r_{12},\alpha) \cdot \nabla_2 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_1,
+\end{equation}
+but as 
+\begin{equation}
+ \deriv{}{x_2}{} v(r_{12},\alpha) = - \deriv{}{x_1}{} v(r_{12},\alpha), 
+\end{equation}
+one has 
+\begin{equation}
+  \nabla_1 v(r_{12},\alpha) \cdot \nabla_2 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_1 = \nabla_1 u(r_{12},\alpha) \cdot  \big( \nabla_1 - \nabla_2 \big). 
+\end{equation}
+Let us introduce the following functions  
+\begin{equation}
+ w_{ij}(\alpha,\bri{1}) = \int \text{d}\br{} e^{-\alpha \big(\br{} - \bri{1} \big)^2} \phi_i(\br{}) \phi_j(\br{}),
+\end{equation}
+\begin{equation}
+ w_{ij}^x(\alpha,\bri{1}) = \int \text{d}\br{}  e^{-\alpha \big(\br{} - \bri{1} \big)^2} x\phi_i(\br{}) \phi_j(\br{}).
+\end{equation}
+Therefore, the integral of the form 
+\begin{equation}
+ \begin{aligned}
+ \matelem{kl}{\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2}  \phi_k(\bri{1}) \phi_l(\bri{2}) \\
+\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)  \phi_i(\bri{1}) \phi_j(\bri{2}) ,
+ \end{aligned}
+\end{equation}
+can be put into 
+\begin{equation}
+ \begin{aligned}
+ \matelem{kl}{\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)}{ij} = \matelem{kl}{\hat{t}_x(\alpha) + \hat{t}_y(\alpha) + \hat{t}_z(\alpha)}{ij},
+ \end{aligned}
+\end{equation}
+with 
+\begin{equation}
+ \begin{aligned}
+ \matelem{kl}{\hat{t}_x(\alpha)}{ij} =&  -2 \alpha \int \text{d}\bri{1} \phi_k(\bri{1}) x_1\big( \deriv{}{x_1}{} \phi_i(\bri{1})\big) w_{jl}(\alpha,\bri{1})  \\
+                                      &  -2 \alpha \int \text{d}\bri{1} \phi_l(\bri{1}) x_1\big( \deriv{}{x_1}{} \phi_j(\bri{j})\big) w_{ik}(\alpha,\bri{1})  \\
+                                      &  +2 \alpha \int \text{d}\bri{1} \phi_k(\bri{1}) \big( \deriv{}{x_1}{} \phi_i(\bri{j})\big) w_{jl}^x(\alpha,\bri{1})  \\
+                                      &  +2 \alpha \int \text{d}\bri{1} \phi_l(\bri{1}) \big( \deriv{}{x_1}{} \phi_j(\bri{j})\big) w_{ik}^x(\alpha,\bri{1})  \\
+ \end{aligned}
+\end{equation}
+\subsection{Computation of the square term}
+One needs to compute 
+\begin{equation}
+ \begin{aligned}
+ \bigg( \nabla_1 u(r_{12}) \bigg)^2 = \sum_{m,n=1}^{N_g} c_m c_n \nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n).
+ \end{aligned}
+\end{equation}
+The term $\nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n)$ is 
+\begin{equation}
+ \nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n) = 4 \alpha_m \alpha_n v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2.
+\end{equation}
+Therefore, the integral of type 
+\begin{equation}
+ \matelem{kl}{\bigg( \nabla_1 u(r_{12}) \bigg)^2}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_k(\bri{1}) \phi_l(\bri{2}) \big(\nabla_1 u(r_{12}) \big)^2
+\end{equation}
+can be written as  
+\begin{equation}
+ \matelem{kl}{\bigg( \nabla_1 u(r_{12}) \bigg)^2}{ij} = \sum_{m,n=1}^{N_g} c_m c_n  4 \alpha_m \alpha_n \matelem{kl}{v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2}{ij} 
+\end{equation}
+where 
+\begin{equation}
+ \begin{aligned}
+ &\matelem{kl}{v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2}{ij} \\& = \matelem{kl}{I_x(\alpha_m + \alpha_n) + I_y(\alpha_m + \alpha_n) + I_z(\alpha_m + \alpha_n)}{ij}
+ \end{aligned}
+\end{equation}
+where 
+\begin{equation}
+ \begin{aligned}
+ \matelem{kl}{I_x(\alpha)}{ij}=& \int \text{d}\bri{1} \phi_i(\bri{1}) \phi_k(\bri{1}) (x_1)^2 w_{jl}(\alpha,\bri{1}) \\
+                              +& \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) (x_1)^2 w_{ik}(\alpha,\bri{1}) \\
+                              -& \int \text{d}\bri{1} \phi_i(\bri{1}) \phi_k(\bri{1}) x_1 w_{jl}^x(\alpha,\bri{1}) \\
+                              -& \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) x_1 w_{ik}^x(\alpha,\bri{1}) \\
+ \end{aligned}
+\end{equation}
+\subsection{Computation of the Laplacian}
+One needs to compute 
+\begin{equation}
+ \begin{aligned}
+  \Delta_1 u(r_{12}) = \sum_{m} c_m \Delta_1  v(r_{12},\alpha_m).
+ \end{aligned}
+\end{equation}
+The Laplacian of $v(r_{12},\alpha)$ is 
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{x_1}{2} v(r_{12},\alpha) &= \deriv{}{x_2}{2} v(r_{12},\alpha) \\
+                           &= v(r_{12},\alpha) 2 \alpha \bigg( 2 \alpha \big( (x_1)^2 + (x_2)^2 \big) -4 \alpha x_1 x_2  -1\bigg)
+ \end{aligned}
+\end{equation}
+and so 
+\begin{equation}
+ \begin{aligned}
+ \Delta_1 v(r_{12},\alpha) &= v(r_{12},\alpha) 2 \alpha \bigg( 2 \alpha \big( (r_1)^2 + (r_2)^2 \big) -4 \alpha \bri{1}\cdot \bri{2}  -3\bigg).
+ \end{aligned}
+\end{equation}
+One can express the following integral 
+\begin{equation}
+ \matelem{kl}{\Delta_1 v(r_{12},\alpha)}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2} \Delta_1 v(r_{12},\alpha) 
+\phi_i(\bri{1}) \phi_j(\bri{2}) \phi_k(\bri{1}) \phi_l(\bri{2}),
+\end{equation}
+as 
+\begin{equation}
+ \begin{aligned}
+  \matelem{kl}{\Delta_1 v(r_{12},\alpha)}{ij} =&  4 \alpha^2 \int \text{d}\bri{1} (r_1)^2 \phi_i(\bri{1}) \phi_k(\bri{1}) w_{jl}(\alpha,\bri{1})  \\
+                                               +& 4 \alpha^2 \int \text{d}\bri{1} (r_1)^2 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}(\alpha,\bri{1})  \\
+                                               -& 6 \alpha \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}(\alpha,\bri{1})  \\
+                                               -& 8 \alpha^2 \int \text{d}\bri{1} x_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^x(\alpha,\bri{1})  \\
+                                               -& 8 \alpha^2 \int \text{d}\bri{1} y_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^y(\alpha,\bri{1})  \\
+                                               -& 8 \alpha^2 \int \text{d}\bri{1} z_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^z(\alpha,\bri{1})  \\
+ \end{aligned}
+\end{equation}
+
 \section{Numerical computation of integrals}
@@
 
+% f(x) = (3*erf(mu*x) - 1)/(2*x) + 1.5*mu/sqpi * exp(-(mu*x)**2.) - 0.25 * (1 - erf(mu*x))**2.
+
+\section{Form of the adjoint operator}
+One can write $\tilde{H}[\mu]$ in terms of its hermitian and non hermitian parts 
+\begin{equation}
+ \tilde{H}[\mu] = \tilde{H}^h[\mu] + \tilde{H}^{nh}[\mu]
+\end{equation}
+where the hermitian part is 
+\begin{equation}
+ \tilde{H}^h[\mu] = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) 
+\end{equation}
+with 
+\begin{equation}
+ \Delta_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
+\end{equation}
+\begin{equation}
+ \big( \nabla_1 u(r_{12},\mu)\big)^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}, 
+\end{equation}
+and 
+\begin{equation}
+ \tilde{H}^{nh}[\mu] = \nabla_{1}u(r_{12},\mu) \cdot \big(\nabla_1 - \nabla_2\big)
+\end{equation}
+The adjoint of the non hermitian operator $\tilde{H}^{nh}[\mu]$ is 
+\begin{equation}
+ \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger =  \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger - \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger,
+\end{equation}
+with 
+\begin{equation}
+ \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 
+                                                                - \nabla_1^2 u(r_{12},\mu)
+\end{equation}
+\begin{equation}
+ \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
+                                                                - \nabla_1 \cdot \nabla_2 u(r_{12},\mu)
+\end{equation}
+but as 
+\begin{equation}
+ \nabla_2 u(r_{12},\mu) = - \nabla_{1}u(r_{12},\mu)
+\end{equation}
+one has
+\begin{equation}
+ \nabla_1 \cdot \nabla_2 u(r_{12},\mu) = - \nabla_1^2 u(r_{12},\mu)
+\end{equation}
+and therefore 
+\begin{equation}
+ \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
+                                                                + \nabla_1^2 u(r_{12},\mu)
+\end{equation}
+which gives for the adjoint of the non hermitian operator 
+\begin{equation}
+ \bigg( \tilde{H}^{nh}[\mu]\bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu).
+\end{equation}
+Therefore the adjoint of the TC Hamiltonian is
+\begin{equation}
+ \begin{aligned}
+\bigg(\tilde{H}[\mu]\bigg)^\dagger & = \tilde{H}^h[\mu] + \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger \\
+                                   & = \tilde{H}^h[\mu]  - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu)  \\
+                                   & = \tilde{H}^h[\mu]  - \tilde{H}^{nh}[\mu] - 2 \nabla_1^2 u(r_{12},\mu) 
+ \end{aligned}
+\end{equation}
+Then 
+\begin{equation}
+ \begin{aligned}
+ \frac{\tilde{H}[\mu] + \bigg(\tilde{H}[\mu]\bigg)^\dagger}{2}& = \tilde{H}^h[\mu] - \nabla_1^2 u(r_{12},\mu) \\
+                                                              & = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) - \nabla_1^2 u(r_{12},\mu) \\
+                                                              & = H - \bigg( 2 \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) \\
+                                                              & = h_c + \frac{1}{r_{12}} - 2 \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} 
+                                                                 - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4} \\
+                                                              & = h_c - \frac{1 - 2 \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}
+ \end{aligned}
+\end{equation}
+
 \end{document}

### 2020-12-02 cusp_j/paper/prog.f90

@@ -1,3 +1,33 @@
+
+double precision function slater_fit_ten_no(x)
+ implicit none
+ double precision, intent(in) :: x
+ integer :: i
+ double precision :: coef_fit_ten_no_slat_gauss(6)
+ double precision :: expo_fit_ten_no_slat_gauss(6)
+ coef_fit_ten_no_slat_gauss(1) = 0.078215d0
+ coef_fit_ten_no_slat_gauss(2) = 0.132037d0
+ coef_fit_ten_no_slat_gauss(3) = 0.068633d0
+ coef_fit_ten_no_slat_gauss(4) = 0.029047d0
+ coef_fit_ten_no_slat_gauss(5) = 0.012063d0
+ coef_fit_ten_no_slat_gauss(6) = 0.004346d0
+
+ expo_fit_ten_no_slat_gauss(1) = 0.621698d0
+ expo_fit_ten_no_slat_gauss(2) = 3.371717d0
+ expo_fit_ten_no_slat_gauss(3) = 14.27116d0
+ expo_fit_ten_no_slat_gauss(4) = 82.76522d0
+ expo_fit_ten_no_slat_gauss(5) = 605.5295d0
+ expo_fit_ten_no_slat_gauss(6) = 6596.808d0
+
+ slater_fit_ten_no = 0.d0
+ do i = 1, 6
+  slater_fit_ten_no = slater_fit_ten_no - coef_fit_ten_no_slat_gauss(i) * dexp(-expo_fit_ten_no_slat_gauss(i) * x * x)
+ enddo                                                                                                                                       
+end
+
+
+
+
 double precision function shank3_f(array,n,nmax)
  implicit none
  integer, intent(in) :: n,nmax
@@ -167,7 +197,7 @@ program pouet
  double precision :: s_exp,g_exp,dl_exp,shank_exp,shank2_f
  double precision :: array(0:100), shank1(0:100),shank2(0:100),array_tmp(0:100)
  double precision :: contrib(0:100),shank3(0:100)
- double precision :: sum,mu
+ double precision :: sum,mu,slater_fit_ten_no
  integer :: n,nmax,k
  pi = dacos(-1.d0)
  xmax = 2.d0
@@ -208,11 +238,12 @@ program pouet
   write(33,'(100(F16.10,X))')x,dexp(f(x,mu0)),dexp(f(x,mu1)),dexp(f(x,mu2))& 
[…]

### 2020-12-03 cusp_j/paper/plots/jastrow/prog.f90
added graphs of TenNo

@@ -204,46 +204,26 @@ program pouet
  nx = 10000
  dx = xmax/dble(nx)
  print*,'0.5**0.25', 0.5d0**0.25d0
- mu0 = 0.05d0
- mu1 = 0.10d0
- mu2 = 0.20d0
- mu3 = 0.3d0
- mu4 = 0.4d0
- mu5 = 0.5d0
- mu6 = 0.6d0
- mu7 = 0.7071d0
- mu8 = 0.8d0
- mu9 = 0.9d0
- mu10= 1.0d0
- mu11= 1.5d0
- mu12= 3.0d0
- mu13= 5.0d0
-! mu15= 10.0d0
-
-! mu0 = 1.00d0
-! mu1 = 1.50d0
-! mu2 = 2.00d0
-! mu3 = 2.5d0
-! mu4 = 3.0d0
-! mu5 = 3.5d0
-! mu6 = 4.0d0
-! mu7 = 4.5000d0
-! mu8 = 5.0d0
-! mu9 = 5.5d0
-! mu10= 6.0d0
+ mu1 = 0.5d0
+ mu2 = 0.7d0
+ mu3 = 0.8d0
+ mu4 = 0.9d0
+ mu5 = 1.0d0
+ mu6 = 1.5d0
+ mu7 = 3.0d0
+ mu8 = 5.0d0
 
  write(33,'(A5,12X,100(F16.10,X))')"#  ", mu0, mu1, mu2, mu3, mu4, mu5, mu6,mu7, mu8, mu9, mu10
  x = dx
  do i = 1, nx
-  write(33,'(100(F16.10,X))')x,dexp(f(x,mu0)),dexp(f(x,mu1)),dexp(f(x,mu2))& 
-                              ,dexp(f(x,mu3)),dexp(f(x,mu4)),dexp(f(x,mu5)),dexp(f(x,mu6))&
-                              ,dexp(f(x,mu7)),dexp(f(x,mu8)),dexp(f(x,mu9)),dexp(f(x,mu10))& 
-                              ,dexp(f(x,mu11)),dexp(f(x,mu12)),dexp(f(x,mu13)),dexp(slater_fit_ten_no(x))
+  write(33,'(100(F16.10,X))')x,dexp(f(x,mu1)),dexp(f(x,mu2)),dexp(f(x,mu3)),dexp(f(x,mu4))  &
+                              ,dexp(f(x,mu5)),dexp(f(x,mu6)),dexp(f(x,mu7)),dexp(f(x,mu8))  &
[…]

### 2020-12-03 cusp_j/paper/paper.tex
added graphs of TenNo

@@
  \label{fig_j_mu}
-        \includegraphics[width=0.45\linewidth]{small_mu_j.pdf}
-        \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_j.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_exp_j.pdf}\\
         \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
@@
 As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
-We report in Figs \ref{}
+We report in Figs \ref{fig:H2} the difference with respect to the estimated exact ground state potential energy curve using several levels of calculations.
 
 \begin{figure*}
- \label{fig:mu_1.0_dz_3}
+ \label{fig:H2}
         \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
@@
 
-According to Eq.
-\eqref{eq:comtot}, Eq.
-\eqref{eq:nabla_i_nabla1}, Eq.
-\eqref{eq:nabla_u2} and Eq.
-\eqref{eq:lapl_u_final}, the additional terms arising from the commutators in $\tilde{H}[u]$ are (for a two-electron system)
-\begin{equation}
- \begin{aligned}
- \label{eq:comtot2}
- & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
- & -\frac{1}{2} 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}  \bigg) \\
-   &- \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
- \end{aligned}
-\end{equation}
-or equivalently
-\begin{equation}
- \begin{aligned}
- \label{eq:comtot2}
- & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
- & -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-   & + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
- \end{aligned}
-\end{equation}
-Therefore, the full similarity transformed Hamiltonian can be written as
-\begin{equation}
-  \begin{aligned}
-   \tilde{H}[u] = & \sum_{i = 1,2} \bigg( -\frac{1}{2} \big(\nabla_i\big)^2 + v(\br{}_i)  \bigg) + \frac{1}{r_{12}} \\
-&   -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
-  \end{aligned}
-\end{equation}
-or equivalently 
-\begin{equation}
-  \begin{aligned}
-   \tilde{H}[u] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
-  \end{aligned}
-\end{equation}
-which corresponds precisely to Eq. \eqref{eq:h_tilde_r12}.
-
 \section{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
@@
 
-\subsection{Computation of integrals with $\text{exp}(-\alpha r_{12}^2)$}
-As essentially all functions of $r_{12}$ involve directly or indirectly (\textit{i.e.} through a fit) gaussian functions, we will have to evaluate such integrals
-\begin{equation}
- \begin{aligned}
-  \int \text{d}\br{}_1  \text{d}\br{}_2& \big( x_1 - A_x \big)^{a_x}  \big( x_2 - B_x \big)^{b_x} 
-                                         \big( y_1 - A_y \big)^{a_y}  \big( y_2 - B_y \big)^{b_y} 
-                                         \big( z_1 - A_z \big)^{a_z}  \big( z_2 - B_z \big)^{b_z} \\
-                                       & \text{exp}(-\alpha \big(\br{}_1 - {\bf A} \big)^2)
-                                         \text{exp}(-\beta  \big(\br{}_2 - {\bf B} \big)^2)
-                                         \text{exp}(-\delta \big(\br{}_1 - \br{}_2 \big)^2)
- \end{aligned}
-\end{equation}
-which can be transformed into product of types 
-\begin{equation}
- \begin{aligned}
-  \int \text{d}x_1 \text{d}x_2 & \big( x_1 - A_x \big)^{a_x} \big( x_2 - B_x \big)^{b_x} \\ 
-  & \text{exp}(-\alpha \big(x_1 - A_x \big)^2) \text{exp}(-\alpha \big(x_2 - B_x \big)^2) \text{exp}(-\delta \big(x_1 - x_2 \big)^2)
- \end{aligned}
-\end{equation}
-
-\section{New form of jastrow factor}
-We want the jastrow factor $u(r_{12})$ to fulfil such equation
-\begin{equation}
- - \bigg[ \frac{2}{r_{12}} \deriv{u}{r_{12}}{}  + \deriv{u}{r_{12}}{2} \bigg] + \frac{1}{r_{12}} = \frac{\text{erf}\big( \mu r_{12} \big)}{r_{12}}.
-\end{equation}
-The solution for such an equation is 
-\begin{equation}
- u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2} + \frac{1}{4 r_{12}} \bigg(c_1 - \frac{\text{erf}\big(\mu r_{12} \big)}{\mu^2} \bigg).
-\end{equation}
-The constant $c_1$ can be found to impose that 
-\begin{equation}
- \lim_{r_{12} \rightarrow 0 } u(r_{12}) < \infty,
-\end{equation}
-which means $c_1 = 0$. Therefore the new jastrow factor is 
-\begin{equation}
- u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2}  - \frac{\text{erf}\big(\mu r_{12} \big)}{4 \mu^2 r_{12}}.
-\end{equation}
-
-\section{One body term jastrow}
-\subsection{The case of the Hydrogen atom}
-We want to find a Jastrow factor which will take care of the nuclear-electron cusp condition, and we will begin by the Hydrogen atom.
-
-Let us write the Hamiltonian of the hydrogenoid atom in the radial coordinate for the $l=0$ sector 
-\begin{equation}
- H = -\frac{1}{2} \big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\big) - \frac{Z}{r}.
-\end{equation}
-To do so, we have to compute the kinetic part acting on the Jastrow factor acting on a function depending only on the radial coordinate $\phi( r)$
-\begin{equation}
- \label{eq:h_atom_j}
- \begin{aligned}
- & -\frac{1}{2}e^{-u(r)}\big(\deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) e^{u(r)}\phi(r)  = \\
- & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) \phi(r) \\
- &-\deriv{u(r)}{r}{}\deriv{}{r}{}\phi(r) \\
- &-\frac{1}{r}\deriv{u(r)}{r}{}\phi(r)  - \frac{1}{2}\deriv{u(r)}{r}{2}\phi(r)  -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2 \phi(r).
- \end{aligned}
-\end{equation}
-Therefore the full similarity transformed Hamiltonian $\tilde{H}[u]$ is 
-\begin{equation}
- \begin{aligned}
- \label{eq:one_e_0}
- & e^{-u(r)}H\,e^{u(r)} = \\
- & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) -\deriv{u(r)}{r}{}\deriv{}{r}{}\\
- &-\frac{1}{r}\bigg(\deriv{u(r)}{r}{} + Z \bigg) \\ 
- & - \frac{1}{2}\deriv{u(r)}{r}{2} -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2.
- \end{aligned}
-\end{equation}
-Similarly to what have been proposed in Section \ref{sec:he_j}, we want to find the Jastrow factor $u(r,\mu,Z)$ such that 
-\begin{equation}
- \label{eq:one_e_01}
- -\frac{1}{r}\bigg(\deriv{u(r,\mu,Z)}{r}{} + Z \bigg) = -Z\frac{\text{erf}(\mu r)}{r},
-\end{equation}
-or equivalently
-\begin{equation}
- \label{eq:one_e_1}
- \deriv{}{r}{}u(r,\mu,Z) = Z\bigg( \text{erf}(\mu r) - 1\bigg).
-\end{equation}
-The Jastrow factor fulfilling Eq. \eqref{eq:one_e_1} is 
-\begin{equation}
- \label{eq:one_e_2}
- u(r,\mu,Z) = -Z r \bigg( 1 - \text{erf}\big(\mu r\big) \bigg) + \frac{Z}{\sqrt{\pi}\mu} e^{-\big(\mu r \big)^2}. 
-\end{equation}
-Now, we can plug $u(r,\mu,Z)$ into Eq. \eqref{eq:one_e_0} in order to compute the explicit form of the similarity transformed Hamiltonian. 
-To do so, we use Eq. \eqref{eq:one_e_1}, and also that 
-\begin{equation}
- \deriv{}{r}{2}u(r) = \frac{2 \mu Z }{\sqrt{\pi}} e^{-(\mu r)^2}.
-\end{equation}
-One obtains then the similarity transformed Hamiltonian 
-\begin{equation}
- \begin{aligned}
- \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
-              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) - \frac{Z}{r}  \\
-                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{} \\
-                & - Z \frac{\text{erf}(\mu r) - 1}{r} \\
-                & -Z \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
-                & - \frac{1}{2}Z^2 \bigg( \text{erf}(\mu r) -1 \bigg)^2,
- \end{aligned}
-\end{equation}
-and one can notice that the $\frac{-Z}{r}$ interaction cancels out to give
-\begin{equation}
- \label{eq:one_e_3}
- \begin{aligned}
- \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
-              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big)  \\
-                & -Z \bigg[ \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} + \frac{\text{erf}(\mu r)}{r} + \frac{1}{2}Z \bigg( \text{erf}(\mu r) -1 \bigg)^2 \bigg] \\
-                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{}. 
- \end{aligned}
-\end{equation}
-Therefore, compared to the usual Hamiltonian, the similarity transformed Hamiltonian contains a different local interaction which is clearly non divergent, but also a new short-range differential operator.
-
-\subsection{General equation}
-Now that we know the general form of the one-body Jastrow factor for a one electron system, we can generalize it 
-to an $N$-electron system and an $M$ nucleus system by just taking the following form 
-\begin{equation}
- e^{\hat{\tau}({\bf r}_1,\hdots , {\bf r}_i,{\bf r}_N)} = e^{-\sum_i^N u({\bf r}_i)} 
-\end{equation}
-where $u({\bf r}_i)$ has the following form 
-\begin{equation}
- u({\bf r}_i) = \sum_{A} u(r_{iA},\mu,Z_A) 
-\end{equation}
-where $u(r,\mu,Z)$ is given by Eq. \eqref{eq:one_e_2} and $r_{iA} = \big|{\bf r}_i - {\bf R}_A \big|$. 
-According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the equation of the similarity transformed Hamiltonian is similar  
-to that of Eq. \eqref{ht_def_g} but with a new form of Jastrow factor. 
-Therefore one needs to compute $\big[ H,\hat{\tau} \big]$ and $\frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]$. 
-Let us begin by $\big[ H,\hat{\tau} \big]$, and as before, we apply it to a general function $\phi(\br{}_1,\hdots \br{}_N)$:
-\begin{equation}
- \label{eq:one_com1_1}
- \begin{aligned}
- \bigg[ H, \hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{u} u(\br{}_j) \bigg]      \phi(\br{}_1,\hdots \br{}_N) \\    
-                                                        & = -\frac{1}{2} \sum_i \bigg( \big(\nabla^2_i u({\bf r}_i)\big) + 2\nabla_i u({\bf r}_i) \cdot \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).  
- \end{aligned}
-\end{equation}
-Therefore, one can write that term as
-\begin{equation}
- \label{eq:one_com1_2}
- \begin{aligned}
-  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg) \\
-                            & -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg).
- \end{aligned}
-\end{equation}
-After some math, the second-order commutator is simply 
-\begin{equation}
- \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
-\end{equation}
-So eventually, the similarity transformed operator becomes 
-\begin{equation}
- \begin{aligned}
-& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
-                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
-                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
- \end{aligned}
-\end{equation}
-Therefore, the addition of the jastrow operator does not add extra two-body terms. 
-\subsection{Computation of the total operator}
-\subsubsection{Computation of $\nabla_i u(\br{}_i)$}
-\begin{equation}
- \begin{aligned}
-&\nabla_i u(\br{}_i) = \sum_A \nabla_i u(r_{iA},Z_A) \\
-                    &= \sum_A \deriv{}{x_i}{} u(r_{iA},Z_A) {\bf e}_{x_i} + \deriv{}{y_i}{} u(r_{iA},Z_A) {\bf e}_{y_i} + \deriv{}{z_i}{} u(r_{iA},Z_A) {\bf e}_{z_i}, 
- \end{aligned}
-\end{equation}
-and 
-\begin{equation}
- \deriv{}{x_i}{}u(r_{iA}) = \deriv{}{r_{iA}}{}u(r_{iA}) \deriv{r_{iA}}{x_i}{},
-\end{equation}
-and as $r_{iA} = \sqrt{(x_1 - x_A)^2 + (y_1 - y_A)^2 + (z_1 - z_A)^2} $ 
-one has                                                              
-\begin{equation}
- \deriv{r_{iA}}{x_1}{} = \frac{x_1 - x_A}{r_{iA}}
-\end{equation}
-and therefore according to Eq. \eqref{eq:one_e_1}, one has 
-\begin{equation}
- \deriv{}{x_i}{} u(r_{iA},Z_A) = -\sum_A Z_A \big( x_i - x_A \big) \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}.
-\end{equation}
-\subsubsection{Computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$}
-The computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$ leads to 
-\begin{equation}
- \begin{aligned}
-  \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) =  \sum_{A,B} Z_B &Z_A \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
-                                                                      & +  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
-                                                                      & +  \big( z_i - z_A \big) \big( z_i - z_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}}.
- \end{aligned}
-\end{equation}
-The diagonal part of such integrals is simply
-\begin{equation}
- \begin{aligned}
- &  \sum_{A} (Z_A)^2 \bigg(\big( x_i - x_A \big)^2 +  \big( y_i - y_A \big)^2 + \big( z_i - z_A \big)^2\bigg) \frac{\bigg(\text{erf}(\mu r_{iA}) - 1\bigg)^2}{\big(r_{iA}\big)^2}\\ 
-  = & \sum_{A} (Z_A)^2 \bigg( \text{erf}(\mu r_{iA}) -1 \bigg)^2
- \end{aligned}
-\end{equation}
-
-\subsubsection{Computation of $\nabla^2_i u(\br{}_i) $}
-We need to compute 
-\begin{equation}
- \begin{aligned}
- \deriv{}{x_{i}}{2} u(\br{}_i) & = -\sum_A Z_A \deriv{}{x_i}{} \bigg[(x_i - x_A) \frac{1 - \text{erf}(\mu r)}{r_{iA}} \bigg] \\
-                               & = -\sum_A Z_A \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
- \end{aligned}
-\end{equation}
-But, one has that
-\begin{equation}
- \begin{aligned}
- \deriv{}{x_i}{} \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
- \end{aligned}
-\end{equation}
-Therefore, 
-\begin{equation}
- \label{eq:lapl_important}
- (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
-\end{equation}.
-Therefore, the Laplacian is 
-\begin{equation}
- \begin{aligned}
- \label{eq:lapl_interm_1}
-&  \deriv{}{x_{i}}{2} u(\br{}_i) + \deriv{}{y_{i}}{2} u(\br{}_i) + \deriv{}{z_{i}}{2} u(\br{}_i) =  - \sum_{A} Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \\
- & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
- \end{aligned}
-\end{equation}
-But according to Eq. \eqref{eq:lapl_important}, one has that 
-\begin{equation}
- \begin{aligned}
- & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
- &- \frac{(x_i - x_A)^2 + (y_i - y_A)^2 + (z_i - z_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
- \end{aligned}
-\end{equation}
-which is simply 
-\begin{equation}
- \begin{aligned}
- \label{eq:lapl_interm_2}
- & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
- & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
- &- \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
- \end{aligned}
-\end{equation}
-Then, coming back to Eq. \eqref{eq:lapl_interm_1} with Eq. \eqref{eq:lapl_interm_2} one has 
-\begin{equation}
- \Delta_i u(\br{}_i) = - \sum_{A}  Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg) \bigg]
-\end{equation}
-which becomes 
-\begin{equation}
- \Delta_i u(\br{}_i) = - \sum_{A}  2 \, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg]
-\end{equation}
-\subsubsection{Computation of the total operator}
-\begin{equation}
- \begin{aligned}
-& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],J\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
-                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
-                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
- \end{aligned}
-\end{equation}
-which becomes
-\begin{equation}
- \begin{aligned}
-  \tilde{H} = H +&  \sum_i \sum_{A}\, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg] \\
-           &+  \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \bigg[ (x_i - x_A) \deriv{}{x_i}{} + (y_i - y_A) \deriv{}{y_i}{} + (z_i - z_A) \deriv{}{z_i}{}\bigg] \\
-           - \frac{1}{2}\sum_{B} Z_B &\bigg[ \big( x_1 - x_A \big) \big( x_1 - x_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\
-           &+  \big( y_1 - y_A \big) \big( y_1 - y_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\ 
-           &+  \big( z_1 - z_A \big) \big( z_1 - z_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB} } \bigg].
- \end{aligned}
-\end{equation}
-and as $H = \sum_i -\frac{1}{2} \Delta_i - \sum_A \frac{Z_A}{r_{iA}} + \sum_{i>j} \frac{1}{r_{ij}} $ the total interaction becomes 
-\begin{equation}
- \label{eq:final_one_e_h}
- \tilde{H} =  \sum_i -\frac{1}{2} \Delta_i + \sum_A Z_A \tilde{v}_A({\bf r}_i)  + \sum_{i>j} \frac{1}{r_{ij}}
-\end{equation}
-where the new effective potential is 
-\begin{equation}
- \label{eq:final_one_e_v}
- \begin{aligned}
-  \tilde{v}_A({\bf r}_i) = & -\frac{\text{erf}(\mu r_{iA})}{r_{iA}} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} \\
-           &+  \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \bigg[ (x_i - x_A) \deriv{}{x_i}{} + (y_i - y_A) \deriv{}{y_i}{} + (z_i - z_A) \deriv{}{z_i}{}\bigg] \\
-           - \frac{1}{2}\sum_{B} Z_B\bigg[& \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\
-           +&  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\ 
-           +&  \big( z_i - z_A \big) \big( z_i - z_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}}\bigg].
- \end{aligned}
-\end{equation}
-\subsubsection{Verification with the Hydrogen atom}
-Let us apply the general equations (see Eqs.
-\eqref{eq:final_one_e_h} and \eqref{eq:final_one_e_v}) to the case of the Hydrogen atom, which is supposed to be in the center of the frame of reference (\textit{i.e.} ${\bf r}_A = \vec{0}$)
-\begin{equation}
- \begin{aligned}
-  \tilde{v}({\bf r}) = & -\frac{\text{erf}(\mu r)}{r} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
-           &+  \frac{1 - \text{erf}(\mu r)}{r} \bigg[ x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{}\bigg] \\
-           &- \frac{1}{2}Z \big(x^2 + y^2 + z^2 \big)  \frac{\big(\text{erf}(\mu r) - 1\big)^2}{r^2},
- \end{aligned}
-\end{equation}
-but as $r^2 = x^2+y^2+z^2$ one obtains that 
-\begin{equation}
- - \frac{1}{2}Z \big(x^2 + y^2 + z^2 \big)  \frac{\big(\text{erf}(\mu r) - 1\big)^2}{r^2} = - \frac{1}{2}Z\big(\text{erf}(\mu r) - 1\big)^2
-\end{equation}
-and also as 
-\begin{equation}
- \begin{aligned}
- x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{} & = {\bf r} \cdot \nabla \\
-                                                     & = r \deriv{}{r}{},
- \end{aligned}
-\end{equation}
-one obtains 
-\begin{equation}
-           +  \frac{1 - \text{erf}(\mu r)}{r} \bigg[ x \deriv{}{x}{} + y \deriv{}{y}{} + z \deriv{}{z}{}\bigg] = \bigg(1 - \text{erf}(\mu r)\bigg)\deriv{}{r}{},
-\end{equation}
-and therefore the total potential is 
-\begin{equation}
- \begin{aligned}
-  \tilde{v}({\bf r}) = & -\frac{\text{erf}(\mu r)}{r} - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
-           &+  \bigg(1 - \text{erf}(\mu r)\bigg)\deriv{}{r}{} \\
-           &- \frac{1}{2}Z\big(\text{erf}(\mu r) - 1\big)^2,
- \end{aligned}
-\end{equation}
-which coincides with Eq. \eqref{eq:one_e_3}.
-
-\section{Derivation with a varying $\mu({\bf r})$}
-Let us assume one has a range separation parameter varying in space $\mur{}$ and that one knows its gradients and Laplacian. 
-Therefore, one would like to derive the same equations as for the constant $\mu$. 
-The Jastrow factor is therefore expressed as
-\begin{equation}
- \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( u(r_{12};\mur{1}) + u(r_{12};\mur{2}) \bigg)
-\end{equation}
-where $u(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
-To derive properly the equations for such a new Jastrow factor, one needs to derive the different terms involving gradients and so on. 
-\subsection{Gradients of $\tilde{u}(\bd{r_1},\bd{r_2})$}
-A fundamental quantity is the gradient of $\tilde{u}(\bd{r_1},\bd{r_2})$ which is 
-\begin{equation}
- \nabla_1 \tilde{u}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
-\end{equation}
-Therefore one needs to compute $\deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2})$
-\begin{equation}
- \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{1}) 
-                                               +\frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{2}) .
-\end{equation}
-Let us begin with the first term 
-\begin{equation}
- \begin{aligned}
- \deriv{}{x_1}{} u(r_{12};\mur{1})=& \deriv{}{r_{12}}{} u(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} \\ 
-                                  +& \deriv{}{\mur{1}}{}u(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
- \end{aligned}
-\end{equation}
-but as 
-\begin{equation}
- \deriv{}{\mu}{}u(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2 \sqrt{\pi} \mu^2}
-\end{equation}
-one obtains 
-\begin{equation}
- \begin{aligned}
- \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
-                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
- \end{aligned}
-\end{equation}
-Similarly, as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
-of the condition determining $u(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
-\begin{equation}
- \deriv{}{x_1}{} u(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
-\end{equation}
-Therefore, one obtains finally that 
-\begin{equation}
- \label{eq:d_dx1_jtilde}
- \begin{aligned}
- \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
- \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
-                 & + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{},
- \end{aligned}
-\end{equation}
-and similarly,
-\begin{equation}
- \label{eq:d_dx2_jtilde}
- \begin{aligned}
- \deriv{}{x_2}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
- \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
-                 & + \frac{e^{-(\mur{2} r_{12})^2}}{2\sqrt{\pi} \mur{2}^2} \deriv{\mur{2}}{x_2}{},
- \end{aligned}
-\end{equation}
-
-\subsection{Computation of $\bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2$}
-Then one needs to compute 
-\begin{equation}
- \begin{aligned}
-& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = \\
-& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
-& \bigg(\deriv{}{y_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{y_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 +  \\
-& \bigg(\deriv{}{z_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{z_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2.
- \end{aligned}
-\end{equation}
-According to Eq.\eqref{eq:d_dx1_jtilde}, 
-and defining the complementary error function as 
-\begin{equation}
- \text{erfc}(x) = 1 - \text{erf}(x)
-\end{equation}
-one has that 
-\begin{equation}
- \begin{aligned}
-& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
- = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
- + & \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 \\
- + & \frac{\big(x_1 - x_2\big)}{r_{12}} \frac{e^{-\big(\mur{1} r_{12}\big)^2}}{2\sqrt{\pi} \big(\mur{1}\big)^2} \deriv{}{x_1}{}\mur{1} 
- \frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{2}.
- \end{aligned}
-\end{equation}
-Similarly 
-\begin{equation}
- \begin{aligned}
-& \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
- = & \frac{1}{4}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
- + & \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2 \\
- + & \frac{\big(x_2 - x_1\big)}{r_{12}} \frac{e^{-\big(\mur{2} r_{12}\big)^2}}{2\sqrt{\pi} \big(\mur{2}\big)^2} \deriv{}{x_2}{}\mur{2} 
- \frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{2}.
- \end{aligned}
-\end{equation}
-Therefore, 
-\begin{equation}
- \begin{aligned}
-& \bigg(\deriv{}{x_1}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2 + \bigg(\deriv{}{x_2}{}\tilde{u}(\bd{r_1},\bd{r_2}) \bigg)^2  \\
- = & \frac{1}{2}\frac{\big( x_1 - x_2 \big)^2}{4 \big(r_{12}\big)^2} \bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
- + & \frac{\big(x_1 - x_2\big)}{2 \sqrt{\pi}r_{12}}  \frac{\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)}{2} \\
-&\bigg(   \frac{e^{-\big(\mur{1} r_{12}\big)^2}}{\big(\mur{1}\big)^2} \deriv{}{x_1}{}\mur{1} 
-- \frac{e^{-\big(\mur{2} r_{12}\big)^2}}{\big(\mur{2}\big)^2} \deriv{}{x_2}{}\mur{2} \bigg) \\
- + & \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
- + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
- \end{aligned}
-\end{equation}
-
-Summing all terms and noticing that $\bigg(x_1 - x_2\bigg)^2 + \bigg(y_1 - y_2\bigg)^2 + \bigg(z_1 - z_2\bigg)^2 = \bigg(r_{12}\bigg)^2$ leads to 
-\begin{equation}
- \begin{aligned}
-& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = 
-  \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
-&+\frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{4 \sqrt{\pi}r_{12}}  \\
-& \big( \bri{1} - \bri{2}\big)\cdot
-\bigg(\frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
-  -   \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
-  &+ \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
- + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
- \end{aligned}
-\end{equation}
 \bibliography{srDFT_SC}

### 2020-12-07 dev/ten_no_ints/full_num.irp.f
working on TenNo

@@ -1,0 +1,137 @@
+subroutine full_num_deriv_ao
+ implicit none
+ integer :: ipoint,jpoint,i,j,k,l,m,pp
+ double precision :: r1(3), r2(3), weight1, weight2,r12 ,accu_tmp
+ double precision :: alpha, coef,contrib,accu
+ double precision, allocatable :: array_tmp(:,:,:,:)
+ allocate(array_tmp(ao_num,ao_num,ao_num,ao_num))
+ provide n_max_fit_ten_no_slat
+ array_tmp = 0.d0
+ do ipoint = 1, n_points_final_grid
+  r1(1) = final_grid_points(1,ipoint)
+  r1(2) = final_grid_points(2,ipoint)
+  r1(3) = final_grid_points(3,ipoint)
+  weight1 = final_weight_at_r_vector(ipoint)
+  do jpoint = 1, n_points_final_grid
+   r2(1) = final_grid_points(1,jpoint)
+   r2(2) = final_grid_points(2,jpoint)
+   r2(3) = final_grid_points(3,jpoint)
+   weight2 = final_weight_at_r_vector(jpoint)
+   r12 = (r1(1) - r2(1))**2.d0 + (r1(2) - r2(2))**2.d0 + (r1(3) - r2(3))**2.d0
+!   print*,ipoint,jpoint
+   do m = 1, 3
+    do j = 1, 1
+     do l = 1, 1
+      do i = 1, 1
+       do k = 1, 1
+        contrib =  weight1 * weight2 * aos_in_r_array_transp(ipoint,k) * aos_in_r_array_transp(jpoint,l)  & 
+                           !   x1 (dx1 phi_i(1)) phi_j(2)
+                           * ( r1(m) * aos_grad_in_r_array(i,ipoint,m) * aos_in_r_array_transp(jpoint,j)              &
+                           !   x2 (dx2 phi_j(2)) phi_i(2)
+                              +r2(m) * aos_grad_in_r_array(j,jpoint,m) * aos_in_r_array_transp(ipoint,i)              & 
+                           !   x1 phi_i(1) (dx2 phi_j(2))
+                              -r1(m) * aos_in_r_array_transp(ipoint,i) * aos_grad_in_r_array(j,jpoint,m)              & 
+                           !   x2 phi_j(2) (dx1 phi_i(1))
[…]

### 2020-12-07 dev/ten_no_ints/routines_test.irp.f

@@ -100,14 +100,14 @@ subroutine test_deriv_ints
      do pp = 1, n_max_fit_ten_no_slat
       alpha = expo_fit_ten_no_slat_gauss(pp)
       coef = coef_fit_ten_no_slat_gauss(pp)
-!      call gauss_int_x_ao(i,k,alpha,r,m,integral_x)
+      call gauss_int_x_ao(i,k,alpha,r,m,integral_x)
       integral = overlap_gauss_r12_ao(r,alpha,i,k)
       do j = 1, ao_num
        do l = 1, ao_num 
-        ! -2 alpha * x_1 * phi_k * d/dx phi_i * w_jl(r)
-        array_tmp(k,i,l,j) += -2.d0 * weight * coef * alpha * integral * aos_in_r_array_transp(ipoint,l) * r(m) * aos_grad_in_r_array(j,ipoint,m) * integral
-!        ! +2 alpha phi_k * d/dx phi_i * w_jl^x(r)
-!        array_tmp(l,j,k,i) +=  2.d0 * weight * coef * alpha * integral * aos_in_r_array_transp(ipoint,l)        * aos_grad_in_r_array(j,ipoint,m) * integral_x
+        ! -2 alpha * x_1 * phi_l * d/dx phi_j * w_ik(r)
+        array_tmp(k,i,l,j) += -2.d0 * weight * coef * alpha * aos_in_r_array_transp(ipoint,l) * r(m) * aos_grad_in_r_array(j,ipoint,m) * integral 
+!        ! +2 alpha phi_l * d/dx phi_j * w_ik^x(r)
+        array_tmp(l,j,k,i) +=  2.d0 * weight * coef * alpha * aos_in_r_array_transp(ipoint,l)        * aos_grad_in_r_array(j,ipoint,m) * integral_x
        enddo
       enddo
      enddo
@@ -116,43 +116,71 @@ subroutine test_deriv_ints
   enddo
  enddo
 
-! do m = 1, 3
-!  do i = 1, ao_num
-!    do k = 1, ao_num
-!      do ipoint = 1, n_points_final_grid
-!       r(1) = final_grid_points(1,ipoint)
-!       r(2) = final_grid_points(2,ipoint)
-!       r(3) = final_grid_points(3,ipoint)
-!       weight = final_weight_at_r_vector(ipoint)
[…]

### 2020-12-07 dev/ten_no_ints/semi_num_deriv.irp.f

@@ -1,10 +1,10 @@
 
-BEGIN_PROVIDER [double precision, ao_two_e_eff_dr12_pot_array_new_bis, (ao_num, ao_num, ao_num, ao_num)]
+BEGIN_PROVIDER [double precision, ao_ten_no_dr12_pot_old, (ao_num, ao_num, ao_num, ao_num)]
  implicit none
 BEGIN_DOC
 !                             1 1 2 2      1 2                                1 2 
 !
-! ao_two_e_eff_dr12_pot_array(k,i,l,j) = < k l | [erf( mu r12) - 1] d/d_r12 | i j > on the AO basis
+! ao_ten_no_dr12_pot_old(k,i,l,j) = < k l | [erf( mu r12) - 1] d/d_r12 | i j > on the AO basis
 END_DOC
  integer :: i,j,k,l,ipoint,m,pp
  double precision :: weight1,thr,r(3)
@@ -48,52 +48,150 @@ END_DOC
    enddo
   enddo
  enddo
-!
-! do m = 1, 3
-!  do ipoint = 1, n_points_final_grid
-!   r(1) = final_grid_points(1,ipoint)
-!   r(2) = final_grid_points(2,ipoint)
-!   r(3) = final_grid_points(3,ipoint)
-!   weight1 = final_weight_at_r_vector(ipoint)
-!   do i = 1, ao_num
-!    do k = 1, ao_num
-!     ! phi_k * d/dx phi_i
-!     b_mat(k,i,ipoint,m) = aos_in_r_array_transp(ipoint,k) * weight1 * aos_grad_in_r_array(i,ipoint,m) 
-!    enddo
-!   enddo
-!  enddo
-! enddo
 
-! do pp = 1, n_max_fit_ten_no_slat
-!  alpha = expo_fit_ten_no_slat_gauss(pp)
-!  coef = coef_fit_ten_no_slat_gauss(pp)
-!  do m = 1, 3
-!   do ipoint = 1, n_points_final_grid
-!    do j = 1, ao_num ! 2
-!     do l = 1, ao_num ! 2
-!      do i = 1, ao_num ! 1
-!       do k = 1, ao_num ! 1
-!        !      1 1 2 2                                     [k*x*i](1)       * [l *  grad_x j](2)
[…]

### 2020-12-07 dev/ten_no_ints/semi_num_deriv_mo.irp.f

@@ -1,0 +1,77 @@
+BEGIN_PROVIDER [double precision, mo_ten_no_dr12_pot_chemist, (mo_num, mo_num, mo_num, mo_num)]
+ implicit none
+ integer :: i,j,k,l,m,n,p,q
+ double precision, allocatable :: mo_tmp_1(:,:,:,:),mo_tmp_2(:,:,:,:),mo_tmp_3(:,:,:,:)
+ 
+ allocate(mo_tmp_1(mo_num,ao_num,ao_num,ao_num))
+ mo_tmp_1 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do q = 1, ao_num
+     do k = 1, mo_num
+      !       (k n|p m)    = sum_q c_qk * (q n|p m)
+      mo_tmp_1(k,n,p,m) += mo_coef_transp(k,q) * ao_ten_no_dr12_pot(q,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+ free ao_ten_no_dr12_pot 
+ allocate(mo_tmp_2(mo_num,mo_num,ao_num,ao_num))
+ mo_tmp_2 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do i = 1, mo_num
+     do k = 1, mo_num
+      !       (k i|p m) = sum_n c_ni * (k n|p m)
+      mo_tmp_2(k,i,p,m) += mo_coef_transp(i,n) * mo_tmp_1(k,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+ deallocate(mo_tmp_1)
+ allocate(mo_tmp_1(mo_num,mo_num,mo_num,ao_num))
+ mo_tmp_1 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do l = 1, mo_num
+    do i = 1, mo_num
+     do k = 1, mo_num
+      mo_tmp_1(k,i,l,m) += mo_coef_transp(l,p) * mo_tmp_2(k,i,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+ deallocate(mo_tmp_2)
+ mo_ten_no_dr12_pot_chemist = 0.d0
+ do m = 1, ao_num
+  do j = 1, mo_num
+   do l = 1, mo_num
+    do i = 1, mo_num
[…]

### 2020-12-07 dev/ten_no_ints/ten_no_ints.irp.f

@@ -6,5 +6,9 @@ program ten_no_ints
   print *, 'Hello world'
 ! call test_overlap_x_gauss_r12_ao
 ! call test_overlap_x_gauss_ten_no
- call test_deriv_ints
+! call test_deriv_ints
+! call test_dgemm 
+ print*,'n_max_fit_ten_no_slat = ',n_max_fit_ten_no_slat
+! call full_num_deriv_ao
+! call full_num_deriv_mo
 end

### 2020-12-07 dev/ten_no_ints/ten_no_jastrow.irp.f

@@ -1,7 +1,9 @@
 
  BEGIN_PROVIDER [integer, n_max_fit_ten_no_slat]
  implicit none
- n_max_fit_ten_no_slat = 6
+ n_max_fit_ten_no_slat = 1
+ print*,'n_max_fit_ten_no_slat = ',n_max_fit_ten_no_slat
+ pause
  END_PROVIDER
 
  BEGIN_PROVIDER [double precision, coef_fit_ten_no_slat_gauss, (n_max_fit_ten_no_slat)]
@@ -14,19 +16,21 @@
  !
  ! The coefficient are taken from the ano-rcc expansion of the hydrogen 1s orbital
  END_DOC
- coef_fit_ten_no_slat_gauss(1) = 0.078215d0
- coef_fit_ten_no_slat_gauss(2) = 0.132037d0
- coef_fit_ten_no_slat_gauss(3) = 0.068633d0
- coef_fit_ten_no_slat_gauss(4) = 0.029047d0
- coef_fit_ten_no_slat_gauss(5) = 0.012063d0
- coef_fit_ten_no_slat_gauss(6) = 0.004346d0
+ coef_fit_ten_no_slat_gauss(1) = 1.d0
+! coef_fit_ten_no_slat_gauss(1) = 0.078215d0
+! coef_fit_ten_no_slat_gauss(2) = 0.132037d0
+! coef_fit_ten_no_slat_gauss(3) = 0.068633d0
+! coef_fit_ten_no_slat_gauss(4) = 0.029047d0
+! coef_fit_ten_no_slat_gauss(5) = 0.012063d0
+! coef_fit_ten_no_slat_gauss(6) = 0.004346d0
 
- expo_fit_ten_no_slat_gauss(1) = 0.621698d0
- expo_fit_ten_no_slat_gauss(2) = 3.371717d0
- expo_fit_ten_no_slat_gauss(3) = 14.27116d0
- expo_fit_ten_no_slat_gauss(4) = 82.76522d0
- expo_fit_ten_no_slat_gauss(5) = 605.5295d0
- expo_fit_ten_no_slat_gauss(6) = 6596.808d0
+ expo_fit_ten_no_slat_gauss(1) = 1.d0
+! expo_fit_ten_no_slat_gauss(1) = 0.621698d0
+! expo_fit_ten_no_slat_gauss(2) = 3.371717d0
+! expo_fit_ten_no_slat_gauss(3) = 14.27116d0
[…]

### 2020-12-08 cusp_j/paper/paper.tex
working on TenNo
Writning paper

@@
 \newcommand{\bs}[0]{{\bf {s}}}
+\newcommand{\frogg}[0]{\text{FROGG}}
+\newcommand{\mfrogg}[0]{\mu^\text{FROGG}}
 \newcommand{\dr}[1]{\text{d}{\bf r_{#1}}}
@@
 \subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
-In that section we derive a new Jastrow factor inspired by the limit condition of the similarity transformed Hamiltonian (see Eq.\eqref{eq:cusp_phi_0}) which mimics that of RS-DFT (see Eq.\eqref{eq:cusp_psi_mu_0}), at least at leading order in $1/r_{12}$.
 \subsubsection{The working equation for $u(\mu,r_{12})$ }
 Eq. \eqref{eq:ht_general} gives the similarity transformed Hamiltonian for an arbitrary Jastrow factor, 
-and with respect to the usual Hamiltonian, $\tilde{H}[u]$ contains two new classes of terms: 
-a new electron-electron potential $1/r_{12} + \tilde{w}[u]+ \tilde{W}[u]$ and a new differential operator  $\tilde{t}[u]$. 
-Of course, these new terms depends on the explicit form of the Jastrow factor $u(r_{12})$ chosen. 
-Now, we impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction of RS-DFT. 
+and with respect to the usual Hamiltonian, $\tilde{H}[u]$ contains two types of additional terms which depend on the actual form of $u(r_{12})$: 
+a new electron-electron potential $1/r_{12} + \tilde{w}[u]+ \tilde{W}[u]$ and a new differential operator  $\tilde{t}[u] $.  
+Now, we impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT. 
 Mathematically, this conditions implies that 
@@
 
-The main difference with the original proposal of the frozen Gaussian geminal of Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
-we impose the structure of $u(r_{12};\mu)$ such that only the part of the scalar potential which is potentially diverging in $1/r_{12}$ (see Eq.\eqref{def_j_00}) compensates exactly the coulomb potential to provide an analytical smooth function $\frac{\text{erf}(\mu r_{12})}{r_{12}} $.
+The main difference with the original proposal of the frozen Gaussian geminal (FROGG) of Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
+ii) the analytical form of $u(r_{12};\mu)$ is obtained from analytical conditions and not by a fit as in the FROGG,  
+iii) the new Jastrow factor is more flexible than the FROGG as it is tuned by a unique parameter $\mu$.
 
@@
 
-Coming now to the behaviour of $u(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$.
+Coming now to the behaviour of $u(r_{12};\mu)$ as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, and we compare it with the FROGG.
 \begin{figure*}
@@
         \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_exp_j.pdf}\\
-        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
+        \caption{Shape of $u(r_{12};\mu)$ (left) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (right) for different values of $\mu$. 
+We also compare the FROGG (see Eq. \eqref{eq_frogg}) and the value of $\mu = 0.865$ which equals the FROGG at $r_{12}=0$ (see Eq. \eqref{mu_ten_no_1}). }
 \end{figure*}
 From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
+
+As the function $u(r_{12};\mu)$ contains a unique parameter, one can try to find the value of $\mfrogg$ such that 
+$u(r_{12};\mfrogg)$ qualitatively reproduces the FROGG. 
+To do so, we propose a one-point fit such that 
+\begin{equation}
+ \label{mu_ten_no_1}
+u(r_{12}=0;\mfrogg) = f_{\text{TN}}(r_{12}=0), 
+\end{equation}
+where $ f_{\text{TN}}(x)$ is the FROGG introduced by Ten-No
+\begin{equation}
+ \label{eq_frogg}
+ f_{\text{TN}}(x) = -\sum_{i=1}^6 c_i e^{-\alpha_i x^2 },
+\end{equation}
+with the coefficients $c_i$ and exponents $\alpha_i$ given in Table 1 of Ref. \onlinecite{TenNo-CPL-00-a}. 
+Eq. \eqref{mu_ten_no_1} gives 
+\begin{equation}
+ \label{mu_ten_no_2}
+ \mfrogg = -\frac{1}{2\sqrt{\pi}f_{\text{TN}}(0)},
+\end{equation}
+which gives $\mfrogg\approx0.86975$. 
+We represent on Fig \ref{fig_j_mu} the comparison between $u(r_{12};\mfrogg)$ and the FROGG, and it is clearly apparent  that $u(r_{12};\mfrogg)$ reproduces almost perfectly the FROGG, although it decays slightly faster at large $r_{12}$.
+Therefore, one can see the FROGG as a special case of $u(r_{12};\mu)$  with $\mu = \mfrogg$.
 
@@
  \label{fig_wee_mu}
-        \includegraphics[width=0.45\linewidth]{w_ee.pdf}
-        \includegraphics[width=0.45\linewidth]{w_ee_bis.pdf}\\
-        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (up) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (bottom) for different values of $\mu$.}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_small.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_erf.pdf}\\
+        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (left) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (right) for different values of $\mu$.}
 \end{figure*}
@@
 whose solution is unknown to the best of the author knowledge.
+
+As  $\mu=\mfrogg$ provides a Jastrow factor $u(r_{12},\mu)$ very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
+\begin{equation}
+ \label{eq:_wee_frogg}
+ \tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})= \frac{1}{r_{12}}-\nabla_1^2 f_{\text{TN}}(r_{12}) - \big(\nabla_1 f_{\text{TN}}(r_{12}) \big) ^2. 
+\end{equation}
+As apparent from Fig.
+\ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, the former strongly oscillates near $r_{12}=0$ while the latter is perfectly smooth for all $r_{12}$.
+\begin{figure*}
+ \label{fig_wee_frogg}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_frog.pdf}
+        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=\mfrogg$ and comparison with the effective potential $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ obtained with the FROGG (see Eq.\eqref{eq:_wee_frogg}).}
+\end{figure*}
 \subsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
@@
  \label{fig_conv_e_mu}
-        \includegraphics[width=0.45\linewidth]{E_conv_basis_small_mu.pdf}
-        \includegraphics[width=0.45\linewidth]{E_conv_basis_large_mu.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_small_mu.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_large_mu.pdf}\\
         \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$.}
@@
 \label{table_conv_e_mu}
-\caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.}
+\caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.
+The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq.
+\eqref{mu_ten_no}.
+}
 \begin{ruledtabular}
 \begin{tabular}{llllllllllll}
- Basis/$\mu$&0.05                 & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                   \\
+ Basis/$\mu$ & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                 & $\mfrogg=0.86975$    \\
 \hline                                                                                                                                                  
- AVDZ       &  -2.909031 (-5.31)  &    -2.906309 (-2.58)  &    -2.904172 (-0.45)  &    -2.903317 (0.41)   &    -2.901420 (2.3)   &    -2.899516 (4.21)   \\
- AVTZ       &  -2.905898 (-2.17)  &    -2.905278 (-1.55)  &    -2.904691 (-0.97)  &    -2.904468 (-0.74)  &    -2.903969 (-0.24) &    -2.903488 (0.24)   \\
- AVQZ       &  -2.904621 (-0.9)   &    -2.904325 (-0.6)   &    -2.903986 (-0.26)  &    -2.903879 (-0.15)  &    -2.903702 (0.02)  &    -2.903620 (0.1)     \\
- AV5Z       &  -2.904428 (-0.7)   &    -2.904229 (-0.51)  &    -2.903928 (-0.2)   &    -2.903834 (-0.11)  &    -2.903702 (0.02)  &    -2.903676 (0.05)   \\
+ AVDZ        &    -2.906309 (-2.58)  &    -2.904172 (-0.45)  &    -2.903317 (0.41)   &    -2.901420 (2.3)   &    -2.899516 (4.21) &  -2.897927 ( 5.80)    \\
+ AVTZ        &    -2.905278 (-1.55)  &    -2.904691 (-0.97)  &    -2.904468 (-0.74)  &    -2.903969 (-0.24) &    -2.903488 (0.24) &  -2.903214 ( 0.51)    \\
+ AVQZ        &    -2.904325 (-0.6)   &    -2.903986 (-0.26)  &    -2.903879 (-0.15)  &    -2.903702 (0.02)  &    -2.903620 (0.1)  &  -2.903589 ( 0.13)     \\
+ AV5Z        &    -2.904229 (-0.51)  &    -2.903928 (-0.2)   &    -2.903834 (-0.11)  &    -2.903702 (0.02)  &    -2.903676 (0.05) &  -2.903678 (-0.1)     \\
 \hline
- Basis/$\mu$ & 1.0                  & 1.6                  & 2.0                  & 3.0                  & $\infty$ (FCI)        & Exact NR              \\
+ Basis/$\mu$ & 1.0                   & 1.6                   & 2.0                   & 3.0                  & $\infty$ (FCI)       &     $\frogg$        \\
 \hline                                                                                                                                                   
- AVDZ        &    -2.896734 (6.99)  &    -2.892773 (10.95) &    -2.891477 (12.25) &    -2.890212 (13.51) &    -2.889548 (14.18)  & -2.903724             \\
- AVTZ        &    -2.903069 (0.66)  &    -2.902421 (1.3)   &    -2.901932 (1.79)  &    -2.901159 (2.56)  &    -2.900598 (3.13)   &                       \\
- AVQZ        &    -2.903558 (0.17)  &    -2.903359 (0.36)  &    -2.903244 (0.48)  &    -2.902951 (0.77)  &    -2.902534 (1.19)   &                       \\
- AV5Z        &    -2.903675 (0.05)  &    -2.903634 (0.09)  &    -2.903592 (0.13)  &    -2.903479 (0.24)  &    -2.903201 (0.52)   &                       \\
+ AVDZ        &    -2.896734 (6.99)   &    -2.892773 (10.95)  &    -2.891477 (12.25)  &    -2.890212 (13.51) &    -2.889548 (14.18) &    -2.897972 (5.75 )\\
+ AVTZ        &    -2.903069 (0.66)   &    -2.902421 (1.3)    &    -2.901932 (1.79)   &    -2.901159 (2.56)  &    -2.900598 (3.13)  &    -2.903919 (-0.20)\\
+ AVQZ        &    -2.903558 (0.17)   &    -2.903359 (0.36)   &    -2.903244 (0.48)   &    -2.902951 (0.77)  &    -2.902534 (1.19)  &    -2.903833 (-0.11)\\
+ AV5Z        &    -2.903675 (0.05)   &    -2.903634 (0.09)   &    -2.903592 (0.13)   &    -2.903479 (0.24)  &    -2.903201 (0.52)  &    -2.903825 (-0.10)\\
+\hline                                                                                                                                                   
+\multicolumn{7}{c}{Exact non relativistic: -2.903724}   \\
 \end{tabular}
@@
  \label{fig:mu_0.3_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He//He_mu_0_3_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_0_3_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
  \label{fig:mu_1.0_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_1_0_cusp_avdz_avtz_3.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
         \caption{
@@
 We also report the average value of the $\mu$ considered (referred as $\muav$) in the double-zeta basis.
-}
+The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten}}
+
 \begin{ruledtabular}
@@
 $E_0^{\basis}[\mursclda]$&   2.03  &    0.64  &   0.39  & 0.410    &  5.07   &   0.40   &  0.12& 0.792       &  0.04   &  -0.12   & -0.08  & 1.127     \\      
+$E_0^{\basis}[\frogg]$   &   3.22  &    0.91  &   0.45  &    -     &  5.75   &  -0.20   & -0.11&   -         & -4.08   &  -1.24   & -0.56  &   -       \\
+$E_0^{\basis}[\mfrogg]$  &   3.12  &    0.91  &   0.46  &    -     &  5.80   &   0.51   &  0.13&   -         & -1.52   &  -0.61   & -0.21  &   -       \\
 \hline              
@@
 $E_0^{\basis}[\mursclda]$&  -0.08  &  -0.15   & -0.09   &1.440     &  -0.18  &   0.09   &  -0.11  &1.740     &  -0.19  &   0.01   &  -0.1  &2.032        \\  
+$E_0^{\basis}[\frogg]$   &  -6.38  &  -1.63   & -0.53   &   -      &  -8.24  &  -1.45   &  -0.49  &    -     &  -9.95  &  -1.44   &  -0.48 &     -       \\
+$E_0^{\basis}[\mfrogg]$  &  -3.81  &  -1.02   & -0.32   &   -      &  -6.33  &  -1.05   &  -0.45  &    -     &  -8.48  &  -1.20   &  -0.58 &     -       \\
 \hline              
@@
 $E_0^{\basis}[\mursclda]$&  -0.01  &  -0.15   &  -0.09   &2.318      &  0.27   &  -0.04  & -0.12   &2.600     &  0.69   &   0.23   & -0.14   &2.879       \\  
+$E_0^{\basis}[\frogg]$   &  -11.35 &  -1.74   &  -0.39   &    -      & -12.60  &  -1.81  & -0.34   &   -      & -13.45  &  -1.55   & -0.32   &    - \\
+$E_0^{\basis}[\mfrogg]$  &   -9.98 &  -1.54   &  -0.68   &    -      & -11.09  &  -1.73  & -0.80   &   -      & -11.69  &  -1.63   & -0.90   &    - \\
 \hline              
@@
 $E_0^{\basis}[\mursclda]$&  1.26   &   0.57   & -0.1     &3.1543     & 0.98    &    0.24  &    0.13 &          &   0.89   &   0.15   &   -0.03&      \\   
+$E_0^{\basis}[\frogg]$   &  -13.79 &  -1.17,  & -0.26    &    -      & 8.88    &    1.31  &    0.39 &   -      & -7.09    &  -1.13   &   -0.30&    - \\
+$E_0^{\basis}[\mfrogg]$  &  -11.79 &  -1.41,  & -0.90    &    -      & 7.36    &    1.16  &    0.54 &   -      & -5.58    &  -0.88   &   -0.42&    - \\
 \end{tabular}
@@
 \begin{equation}
- \nabla_1 v(r_{12},\alpha) \cdot \nabla_2 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_1,
+ \nabla_1 v(r_{12},\alpha) \cdot \nabla_1 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_2,
 \end{equation}
@@
 \begin{equation}
-  \nabla_1 v(r_{12},\alpha) \cdot \nabla_2 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_1 = \nabla_1 u(r_{12},\alpha) \cdot  \big( \nabla_1 - \nabla_2 \big). 
+  \nabla_1 v(r_{12},\alpha) \cdot \nabla_1 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_2 = \nabla_1 u(r_{12},\alpha) \cdot  \big( \nabla_1 - \nabla_2 \big). 
 \end{equation}

### 2020-12-08 cusp_j/paper/plots/jastrow/prog.f90

@@ -182,7 +182,7 @@ program pouet
  implicit none
  integer :: i,nx
  double precision :: x, dx,xmax,f,mu0,mu1,mu2,mu3,mu4,mu5,mu6,shank3_f
- double precision :: mu7, mu8, mu9,mu10,mu11, mu12, mu13, mu14
+ double precision :: mu7, mu8, mu9,mu10,mu11, mu12, mu13, mu14,mu_ten_no
  double precision :: j,a,b
  double precision :: pi,f0,g,s,alpha,beta
  double precision :: alpha0,beta0
@@ -200,30 +200,28 @@ program pouet
  double precision :: sum,mu,slater_fit_ten_no
  integer :: n,nmax,k
  pi = dacos(-1.d0)
- xmax = 2.d0
+ xmax = 2.5d0
  nx = 10000
  dx = xmax/dble(nx)
  print*,'0.5**0.25', 0.5d0**0.25d0
- mu1 = 0.5d0
- mu2 = 0.7d0
- mu3 = 0.8d0
- mu4 = 0.9d0
- mu5 = 1.0d0
- mu6 = 1.5d0
- mu7 = 3.0d0
- mu8 = 5.0d0
+ mu2 = 0.5d0
+ mu3 = 0.7d0
+ mu4 = 1.5d0
+ mu5 = 3.0d0
+ mu6 = 5.0d0
+ mu7 = 0.86975d0
 
- write(33,'(A5,12X,100(F16.10,X))')"#  ", mu0, mu1, mu2, mu3, mu4, mu5, mu6,mu7, mu8, mu9, mu10
+ write(33,'(A5,12X,100(F16.10,X))')"# x", mu2, mu3, mu4, mu5, mu6,mu7
  x = dx
  do i = 1, nx
-  write(33,'(100(F16.10,X))')x,dexp(f(x,mu1)),dexp(f(x,mu2)),dexp(f(x,mu3)),dexp(f(x,mu4))  &
-                              ,dexp(f(x,mu5)),dexp(f(x,mu6)),dexp(f(x,mu7)),dexp(f(x,mu8))  &
+  write(33,'(100(F16.10,X))')x,dexp(f(x,mu2)),dexp(f(x,mu3)),dexp(f(x,mu4))  &
+                              ,dexp(f(x,mu5)),dexp(f(x,mu6)),dexp(f(x,mu7))  &
                               ,dexp(slater_fit_ten_no(x))
[…]

### 2020-12-08 cusp_j/paper/plots/jastrow/prog_bis.f90

@@ -4,36 +4,28 @@ program prog_bis
  integer :: i,nx
  double precision :: mu0,mu1,mu2,mu3,mu4,mu5,mu6,mu_tmp_5,mu_tmp_10
  double precision :: mu7, mu8, mu9,mu10,mu11, mu12, mu13, mu14
+ double precision :: mu_ten_no,ten_no_square,ten_no_lapl,ten_no_pot
  xmax = 15.d0
- nx = 1000
+ nx = 100000
  dx = xmax/dble(nx)
  x = dx
- mu0 = 0.05d0
- mu1 = 0.10d0
- mu2 = 0.20d0
- mu3 = 0.3d0
- mu4 = 0.4d0
- mu5 = 0.5d0
- mu6 = 0.6d0
- mu7 = 0.7071d0
- mu8 = 0.8d0
- mu9 = 0.9d0
- mu10= 1.0d0
- mu11= 1.5d0
- mu12= 3.0d0
- mu13= 5.0d0
- mu_tmp_5 = 0.5284432686368106d0
- mu_tmp_10 = 1.27844d0
+ mu_ten_no = 0.86975d0
+ mu2 = 0.3d0
+ mu3 = 0.5d0
+ mu4= 1.0d0
+ mu5 = 1.5d0
+ mu6 = 3.0d0
+ mu7 = 5.0d0
+ mu8 = mu_ten_no
+
  do i = 1, nx
-  write(38,'(100(F16.10,X))')x, w_ee_eff(x,mu0),w_ee_eff(x,mu1),w_ee_eff(x,mu2)& 
-                              ,w_ee_eff(x,mu3),w_ee_eff(x,mu4),w_ee_eff(x,mu5),w_ee_eff(x,mu6)&
-                              ,w_ee_eff(x,mu7),w_ee_eff(x,mu8),w_ee_eff(x,mu9),w_ee_eff(x,mu10)& 
-                              ,w_ee_eff(x,mu11),w_ee_eff(x,mu12),w_ee_eff(x,mu13),w_ee_eff(x,mu14)  
-  write(39,'(100(F16.10,X))')x, derf_mu_x(x,mu0),derf_mu_x(x,mu1),derf_mu_x(x,mu2)& 
-                              ,derf_mu_x(x,mu3),derf_mu_x(x,mu4),derf_mu_x(x,mu5),derf_mu_x(x,mu6)&
[…]

### 2020-12-09 cusp_j/paper/paper.tex
moving on on the paper

@@
 \begin{abstract}
-blabla
+TODO: investigate the non variationality on the He atom for instance and Ne8+
 
@@
 
-As  $\mu=\mfrogg$ provides a Jastrow factor $u(r_{12},\mu)$ very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
+As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ provides is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
 \begin{equation}
@@
 As apparent from Fig.
-\ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, the former strongly oscillates near $r_{12}=0$ while the latter is perfectly smooth for all $r_{12}$.
+\ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, while the latter is perfectly smooth for all $r_{12}$, the former strongly oscillates near $r_{12}=0$ between positive and negative values and is not bounded for $r_{12}=0$.
+Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that $f_{\text{TN}}(r_{12})$ is cusp-less as it is made of gaussian functions, \textit{i.e.} 
+\begin{equation}
+ \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}f_{\text{TN}}(r_{12}) = 0, 
+\end{equation}
+as a necessary condition of the to obtain a non divergent scalar potential is 
+\begin{equation}
+ \label{eq:cusp_phi_0}
+ \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u(r_{12}) = \frac{1}{2}, 
+\end{equation}
+as shown in the appendix \ref{sec:cusp} (see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1}). 
+Because the condition of Eq. \eqref{eq:cusp_phi_0} is fulfilled by $u(r_{12},\mu)$ for all $\mu < \infty$, 
+the effective potential obtained by the similarity transformation of $H$ by $u(r_{12},\mu)$ is necessary non divergent.
+
+Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ almost identical \textit{in average}, as they perfectly agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
+
 \begin{figure*}
@@
 \end{figure*}
+
 \subsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
@@
  \label{eq:lim_mu_1}
- \lim_{\mu \rightarrow \infty} \tilde{H}[\mu] = H.
-\end{equation}
-Nevertheless, in the large $\mu$ limit, one can notice that 
-\begin{equation}
- \label{eq:lim_mu_3}
- \lim_{\mu \rightarrow \infty} \tilde{\mathcal{W}}_{ee}(r_{12})  = \frac{1}{r_{12}} + \delta(r_{12}) 
-\end{equation}
-where $\delta(r_{12})$ is the Dirac distribution, and as the firs-order differential term vanishes in the large $\mu$ limit (see Eq.\eqref{eq:exp_ht_mu}), one could be tempted to write that 
-\begin{equation}
- \begin{aligned}
- \label{eq:lim_mu_4}
- \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = h_c + \frac{1}{r_{12}} + \delta(r_{12}) \\
-                                             & = H + \delta(r_{12})  \\
-                                             & \ne H,
- \end{aligned}
-\end{equation}
-which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
-
-Nevertheless, as the right hand side of Eq.\eqref{eq:lim_mu_4} contains a Delta distribution, it must be considered in the sense of distributions an not point wise. 
-Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
-\begin{equation}
- \label{eq:lim_mu_5}
- \begin{aligned}
-& \matelem{\psi}{H}{\psi} = \lim_{\mu \rightarrow \infty} \matelem{\psi}{\tilde{H}[\mu]}{\psi} \\
-& \Leftrightarrow H = \tilde{H}[\mu],
- \end{aligned}
-\end{equation}
-and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
-\begin{equation}
- \label{eq:lim_mu_6}
- \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
-\end{equation}
-To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
-\begin{equation}
- \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 
-\end{equation}
-where $\tilde{n_2}(x)$ is the function $n_2(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
-$|\br{}_1-\br{}_2| = x$. 
-As the pair density $n_2(\br{}_1,\br{}_2)$ remains finite and is integrable, the function $\tilde{n}_2(x)$ 
-cannot diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
-\begin{equation}
- \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
-\end{equation}
-which implies Eq.\eqref{eq:lim_mu_1}.
+ \lim_{\mu \rightarrow \infty} \tilde{H}[\mu] = H,
+\end{equation}
+although it is only in the sense of distributions (see Appendix \ref{sec:large_mu_lim} for a more detailed explanation).
 
@@
 \subsubsection{Computational details}
-We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual gaussian orbital basis set (see annexes for more details) together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual Gaussian orbital basis set (see appendix for more details) together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+We also implemented all necessary integrals to use the FROGG derived by Ten-No in Ref.
+\onlinecite{TenNo-CPL-00-a} in the context of the TC Hamiltonian.
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
@@
 We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_i^{\basis}[\mu]$ of $\tilde{H}[\mu]^{\basis}$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
+We also report in the tables and figures the results obtained with the FROGG.
 Several observations can be done from these data.
@@
 when enlarging the basis set.
-Also, qualitatively, one can observe that there are two regimes of $\mu$: $\mu \in[0.05,0.7]$ where the $E_0^\mu$ is always below $E_0$ and $\mu\ge 0.7$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
+Also, qualitatively, one can observe that there are two regimes of $\mu$: $\mu \in[0.2,0.35]$ where the $E_0^\mu$ is always below $E_0$ and $\mu\ge 0.7$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
 As $\mu$ increases, the difference between $E_0^\mu$ and $E_0^\text{FCI}$ in a given basis set diminishes, 
@@
 
-Coming now to the speed of convergence of $E_0^\mu$ with respect to the basis set, it is always faster than that of $E_0^\text{FCI}$ as long as $\mu \ge 0.2$. 
+Also, it is striking to see that the total energies obtained, in a given basis set, by the TC Hamiltonian obtained by the FROGG and that obtained by $\tilde{H}[\mu]$ with $\mu=\mfrogg$ coincide with less than 1 mH.
+The latter results confirms that as $u(r_{12},\mfrogg) \approx f_{\text{TN}}(r_{12})$ (see Fig \ref{fig_j_mu} and Eqs.
+\eqref{mu_ten_no_1} and \eqref{mu_ten_no_2}), the TC Hamiltonians obtained with the two Jastrow factor are very similar, as illustrated for instance by the effective potential in Fig.
+\ref{fig_wee_frogg}.
+
+Coming now to the speed of convergence of $E_0^\mu$ with respect to the basis set, it is always faster than that of $E_0^\text{FCI}$ for the whole range of values of $\mu$ selected here. 
 To quantify better such observations, one can identify the basis set from which the error with respect to the exact non relativistic energy is smaller, in absolute value, than 1mH. 
@@
 For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
-Therefore one can conclude that the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$.
+The quality of the results obtained with the FROGG are in between that obtained with $\mu=0.7$ and $\mu=1.0$.
+
+From the study of the ground state of the helium atom, one can conclude that i) the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$,
+ii) the results obtained with $\mu=\mfrogg$ reproduce essentially that obtained with the FROGG, 
+iii) for $\mu \in[ 0.35,0.7]$ the results obtained are always better than that obtained with the FROGG. 
 \begin{figure*}
@@
         \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_large_mu.pdf}\\
-        \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$.}
+        \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$. 
+We also compare with the results of the TC obtained with the $u(r_{12}) = f_{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg}), referred here after as FROGG. }
 \end{figure*}
@@
 \caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.
-The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq.
-\eqref{mu_ten_no}.
+We also compare with the results of the TC obtained with the $u(r_{12}) = f_{\text{TN}}(r_{12})$ (see Eq.
+\eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.86975$ is defined in Eq.
+\eqref{mu_ten_no_1}.
  }
@@
 
-\section{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians}
+\section{Appendix}
+\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians and related cusp conditions}
 \label{sec:cusp}
@@
 Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
+
+\subsection{Appendix: large $\mu$ limit of $\tilde{H}[\mu]$}
+\label{sec:large_mu_lim}
+Nevertheless, in the large $\mu$ limit, one can notice that 
+\begin{equation}
+ \label{eq:lim_mu_3}
+ \lim_{\mu \rightarrow \infty} \tilde{\mathcal{W}}_{ee}(r_{12})  = \frac{1}{r_{12}} + \delta(r_{12}) 
+\end{equation}
+where $\delta(r_{12})$ is the Dirac distribution, and as the firs-order differential term vanishes in the large $\mu$ limit (see Eq.\eqref{eq:exp_ht_mu}), one could be tempted to write that 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:lim_mu_4}
+ \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = h_c + \frac{1}{r_{12}} + \delta(r_{12}) \\
+                                             & = H + \delta(r_{12})  \\
+                                             & \ne H,
+ \end{aligned}
+\end{equation}
+which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
+
+Nevertheless, as the right hand side of Eq.\eqref{eq:lim_mu_4} contains a Delta distribution, it must be considered in the sense of distributions an not point wise. 
+Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
+\begin{equation}
+ \label{eq:lim_mu_5}
+ \begin{aligned}
+& \matelem{\psi}{H}{\psi} = \lim_{\mu \rightarrow \infty} \matelem{\psi}{\tilde{H}[\mu]}{\psi} \\
+& \Leftrightarrow H = \tilde{H}[\mu],
+ \end{aligned}
+\end{equation}
+and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
+\begin{equation}
+ \label{eq:lim_mu_6}
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
+\end{equation}
+To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
+\begin{equation}
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 
+\end{equation}
+where $\tilde{n_2}(x)$ is the function $n_2(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
+$|\br{}_1-\br{}_2| = x$. 
+As the pair density $n_2(\br{}_1,\br{}_2)$ remains finite and is integrable, the function $\tilde{n}_2(x)$ 
+cannot diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
+\begin{equation}
+ \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
+\end{equation}
+which implies Eq.\eqref{eq:lim_mu_1}.
 

### 2020-12-11 cusp_j/paper/paper.tex
modified biblio

@@
 Treating such effects in a black box way involves the use of very flexible wave functions such as
-selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 

### 2020-12-11 cusp_j/paper/paper.tex
modified biblio

@@
 Treating such effects in a black box way involves the use of very flexible wave functions such as
-selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,cele_cipsi_3_spaces,cele_cipsi_zeroth_order,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 

### 2020-12-11 cusp_j/paper/paper.tex
modified biblio

--- 2020-12-11 cusp_j/paper/paper.tex
@@
 Treating such effects in a black box way involves the use of very flexible wave functions such as
-selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,cele_cipsi_3_spaces,cele_cipsi_zeroth_order,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 

### 2020-12-14 cusp_j/paper/paper.tex
added H2_de_fci_mu_ten_no.pdf

--- 2020-12-11 cusp_j/paper/paper.tex
@@
 Treating such effects in a black box way involves the use of very flexible wave functions such as
-selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 
@@
 Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on this isoelectronic series which consist in weakly correlated covering a quite wide range of densities.
-As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given system, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
+As in the study of the helium atom of Sec \ref{sec:total_he}, in a given basis set $\basis$ and for a given system, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
 
@@
         \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_frogg.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_ten_no.pdf}\\
         \caption{

### 2020-12-14 cusp_j/paper/paper.tex

@@
 Treating such effects in a black box way involves the use of very flexible wave functions such as
-selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book,three_class_CIPSI,harrison,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
+selected CI\cite{bender,HurMalRan-JCP-73,buenker1,buenker-book,three_class_CIPSI,harrison,cele_cipsi_3_spaces,cele_cipsi_zeroth_order,GinSceCaf-CJC-13, GinSceCaf-JCP-15, ShaHolJeaAlaUmr-JCTC-17}, 
 %selected CI\cite{HurMalRan-JCP-73,bender,malrieu,buenker1,buenker-book}, 

### 2020-12-16 cusp_j/paper/paper.tex
conclusion almost finished

@@
 An alternative point of view using a Jastrow factor is the so-called transcorrelated (TC) approach where the full effect of the Jastrow factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the Jastrow factor.
-The pioneers of such theory were Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} where they derive the equations of the general form of the TC Hamiltonian which contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.
+Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and latter on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the general form of the TC Hamiltonian for an exponential form of the Jastrow factor.
+The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.
 Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize orbitals and Jastrow parameters for a single Slater determinant.
-Nevertheless, such a constrained form of the wave function for the Slater part often leads to energies far below the exact one.
-
-Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a fixed universal Jastrow factor.
+Nevertheless, such a constrained form of the wave function for the Slater together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.
+
+Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a frozen universal Jastrow factor.
 This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}).
-As in F12 theories, the Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions, only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
+The Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions and referred to as the frozen gaussian geminal (FROGG), only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
 The use of gaussian functions to represent the Jastrow factor enabled Ten-No to develop a numerical scheme to evaluate exactly the three-electron integrals present in TC Hamiltonian\cite{TenNo-CPL-00-b}, which is an alternative to the density-fitting method proposed by Ten-No in the general context of F12 methods\cite{TenMan-JCP-03}.
@@
 \subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
+\label{sec:new_j}
 \subsubsection{The working equation for $u(\mu,r_{12})$ }
@@
 We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
-%The study was performed using the augmented Dunning basis aug-cc-pVXZ (X=D,T,Q,5), hereafter referred as AVXZ.
 
@@
 \subsection{Study of the ground state eigenvector in real space}
+\label{sec:he_real_space}
 In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_i^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
@@
 
-iv) The fact that $\psimub(\br{}_1,\br{}_2)$ provides  such a good approximation of $\psiex(\br{}_1,\br{}_2)$ in real space can be investigate through the prism of the local energy. 
-The local energy $E_{\text{loc}}[\psi](\br{}_1,\br{}_2)$ associated to a given wave function $\psi$ is defined as 
-\begin{equation}
- E_{\text{loc}}[\psi](\br{}_1,\br{}_2) = \frac{H\psi(\br{}_1,\br{}_2)}{\psi(\br{}_1,\br{}_2)},
-\end{equation}
-and is such that 
-\begin{equation}
- \int \text{d}\br{}_1\,\,\text{d}\br{}_2\,\, E_{\text{loc}}[\psi](\br{}_1,\br{}_2) \big|\psi(\br{}_1,\br{}_2)\big|^2= \matelem{\psi}{H}{\psi}.
-\end{equation}
-Therefore, one can 
+%iv) The fact that $\psimub(\br{}_1,\br{}_2)$ provides  such a good approximation of $\psiex(\br{}_1,\br{}_2)$ in real space can be investigate through the prism of the local energy. 
+%The local energy $E_{\text{loc}}[\psi](\br{}_1,\br{}_2)$ associated to a given wave function $\psi$ is defined as 
+%\begin{equation}
+% E_{\text{loc}}[\psi](\br{}_1,\br{}_2) = \frac{H\psi(\br{}_1,\br{}_2)}{\psi(\br{}_1,\br{}_2)},
+%\end{equation}
+%and is such that 
+%\begin{equation}
+% \int \text{d}\br{}_1\,\,\text{d}\br{}_2\,\, E_{\text{loc}}[\psi](\br{}_1,\br{}_2) \big|\psi(\br{}_1,\br{}_2)\big|^2= \matelem{\psi}{H}{\psi}.
+%\end{equation}
+%Therefore, one can 
 \begin{figure*}
  \label{fig_wee_compare}
-        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_zoom.pdf}
         \caption{
@@
 where $n_{\text{HF}}({\bf r})$ is the HF density and $N_e$ the number of electrons in the system. 
-We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ as value of $\mu$ in $\tilde{H}[\mu]$.
-We also report in the column $\muav$ of the Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets vary by less than $0.1\%$.
+We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ in $\tilde{H}[\mu]$.
+We also report in Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets vary by less than $0.1\%$. 
 As one can observe from  Table \ref{table_conv_e_mu_iso}, the ground state energies of $\tilde{H}[\murscav]$ converge much faster than that of the usual Hamiltonian as the MAD for the ground state energies is of 2.64 mH, 0.48 mH and 0.26 mH in the double-, triple- and quadruple zeta quality basis sets (respectively) whereas it is of 12.16 mH, 4.71 mH and 1.64 mH for the usual Hamiltonian.
 Also, one can observe that, except for the low density systems such as the H${^-}$ and He species, it converges from below the exact ground state energy.
-Regarding now the value of $\murscav $, one can notice that it increases with the atomic number, which is expected as the density becomes more picked near the nucleus as the nuclear charge increases, and therefore the typical inter electronic distance lowers with $Z$.
-
-In the present context, we propose the derivation of another value of $\mu$ based on the mapping of the on-top pair density of the UEG and a model built with the Jastrow factor defined by \eqref{eq:def_j}.
+Regarding now the value of $\murscav $, one can notice that it increases with the atomic number.
+This is expected as the density becomes more picked near the nucleus while the nuclear charge increases, which induces necessary that the typical inter electronic distance lowers with $Z$.
+
+Still with the aim of finding good values of $\mu$, we propose here the derivation of another approach based on the mapping of the on-top pair density of the UEG and a model built with the Jastrow factor defined by \eqref{eq:def_j}.
 Assuming a single Slater determinant ansatz for a Jastrow Slater wave function with a Jastrow factor defined in \eqref{eq:def_j}, the on-top pair density is 
@@
 
+We can also compare the results obtained with $\muuegav$, $\murscav$ and $\mursclda$ to that obtained with the FROGG and $\mfrogg$, which are also reported in Table \ref{table_conv_e_mu_iso}. 
+From these data one can clearly observe several things: i) while for quite diffuse systems as H$^-$ and He the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
+These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system and the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
+
 \begin{table*}
@@
 We also report the average value of the $\mu$ considered (referred as $\muav$) in the double-zeta basis.
-The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten}}
+The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten_1}}
 
@@
 
-\section{Application on H$_2$}
-Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we study in the last part of the present study study the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$.
-As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
-We report in Figs \ref{fig:H2} the difference with respect to the estimated exact ground state potential energy curve using several levels of calculations.
+\section{The ground state potential energy curve H$_2$}
+Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we focus on the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$ in the last part of the present study as a test case for valence only molecular system.
+As in the study of the helium atom of Sec \ref{sec:total_he}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
+We report in Figs \ref{fig:H2} the difference with respect to the estimated exact ground state potential energy curve using several levels of calculations for the aug-cc-pVDZ and aug-cc-pVTZ basis sets.
+
+From the Figs \ref{fig:H2}, one can observe that i) all methods provide a near chemical accuracy from the AVTZ basis set, ii) the TC Hamiltonian obtained with the FROGG and that with $\mfrogg$ provide very similar results, iii) the values obtained with $\muuegav$ and $\murscav$ provide very similar results and improve accuracy over the FROGG for the AVDZ basis set, iv) a value of $\mu = 0.5$ provides a good description in the AVDZ basis set while remaining above the exact energy in the AVTZ basis set, which is not the case for $\mu=0.3$.
 
@@
  \label{fig:H2}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_frogg.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_ten_no.pdf}\\
         \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
         \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_frogg.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_ten_no.pdf}\\
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}
+        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
         \caption{
         H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
+R$_{eq}$ refers to the equilibrium distance of 1.401 a.u..
 }
 \end{figure*}
+
+\section{Conclusion}
+In the present paper, we derived a new form of Jastrow factor $u(r_{12},\mu)$ for the TC framework and performed the first numerical tests on a set of two electrons atomic and molecular systems. 
+In contrast to the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} which was obtained as a linear combination of Gaussians from a numerical fit, the analytical form of the new Jastrow factor proposed here has been derived from the analysis of the leading order terms in $\frac{1}{r_{12}}$ of the general TC Hamiltonian, such that it mimics the long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ used in the RS-DFT framework (see Sec.
+\ref{sec:new_j}).
+The Jastrow factor $u(r_{12},\mu)$ resulting from such mathematical conditions naturally imposes the cusp and digs the Coulomb hole over a range tuned by a unique parameter $\mu$: the smaller the $\mu$, the broader and deeper is the Coulomb hole dug by $u(r_{12},\mu)$, and in the $\mu \rightarrow \infty$ limit, $u(r_{12},\mu)=0$.
+The TC Hamiltonian $\tilde{H}[\mu]$ obtained from the similarity transformation of the usual Hamiltonian with $u(r_{12},\mu)$ is analytical and depends on a unique parameter $\mu$. 
+While varying $\mu$, the physical content of $\tilde{H}[\mu]$ significantly changes: one can continuously change from a repulsive non divergent Hamiltonian at large $\mu$, to a partially attractive Hamiltonian at intermediate values of $\mu$, and eventually to a purely attractive Hamiltonian at small values of $\mu$ (see Sec.
+\ref{sec:ht_general}).
+Also, in the $\mu \rightarrow \infty$ limit one recovers the usual physical Hamiltonian, just as in RS-DFT.
+
+The numerical investigation of the ground state of the helium atom indicates that for values of $\mu$ ranging from 0.2 to 1.0 one can strongly improve the convergence of the computed energies with respect to the basis set (see Sec.
+\ref{sec:total_he}).
+An investigation of the right eigenvectors in real space for different values of $\mu$ provided interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
+Nevertheless, when the right eigenvectors are multiplied by the corresponding Jastrow factor, one obtains a very good approximation of the numerically exact ground state wave function (see Sec.
+\ref{sec:he_real_space}).
+Also, we found a value of $\mu \approx 0.87$ which provides a Jastrow factor very close to the FROGG, and which produces essentially the same eigenvalues than the FROGG, indicating that one can see the FROGG as a special case of the more flexible Jastrow factor $u(r_{12},\mu)$.
+
+In order to study the performance of the present approach on a broader set of two-electron systems, we investigate the ground state energy of the helium isoelectronic series from H$^-$ to Ne$^{8+}$ (see Sec.
+\ref{sec:iso_elec}).
+As the density considerably vary among the isoelectronic series, we propose a very simple scheme to provide a value of $\mu$ which automatically adapts to the system, the value of which increases with the nuclear charge of the atom considered.
+The results obtained for this system dependent value of $\mu$ are found to be very accurate as the MAD t the exact ground state energies over this isoelectronic series in double-zeta quality is about 1 mH and keeps lowering while improving the quality of the basis set.
+In contrast, the MAD obtained with the FROGG is much higher: it is of about 7 mH in the double-zeta quality basis set, which can be understood by the fact that the typical range of the correlation effect imposed by the FROGG is less accurate for shrink densities than for typical valence densities.
+
+The last part of our study is dedicated to the study of the ground state energy curve of H$_2$ with different schemes, and we show that the present scheme provides an improvement of the convergence of the energy over the whole potential energy curve.
 

### 2020-12-17 cusp_j/paper/paper.tex
conclusion almost done

@@
 We show then that the corresponding transcorrelated Hamiltonian has a straightforward analytical structure, which is briefly reviewed as a function of the $\mu$ parameter. 
-Then, we perform a numerical study of the behaviour of the ground state eigenpair of $\tilde{H}[\mu]$ for the helium atom: 
+Then, we perform a numerical study of the behaviour of the ground state eigenpair of $\tilde{H}[\mu]$ in the case of the helium atom: 
 in the first part we analyze the speed of convergence of the ground state energy with respect to the basis set and the parameter $\mu$, 
@@
 Eventually, we study the H$_2$ molecule and compare different regimes of correlation. 
+Numerical comparison with the TC Hamiltonian obtained with the FROGG is also performed for all systems studied.
 
@@
 \subsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
-Let us write the Hamiltonian of the helium atom in the $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinate 
+Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates  
 \begin{equation}
@@
 \label{sec:he_j}
-Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a general Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
+Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
 \begin{equation}
@@
 \eqref{eq:ht_general} that the two electrons experience a modified scalar potential given by $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u]$, and an additional differential operator $\tilde{t}[u]$,
-the latter making $\tilde{H}[u]$ non-hermitian.
+the latter making $\tilde{H}[u]$ non-hermitian. It is important to notice that the fact that  $\tilde{H}[u]$ is non-hermitian implies the loose of variational principle.
 
@@
 a new electron-electron potential $1/r_{12} + \tilde{w}[u]+ \tilde{W}[u]$ and a new differential operator  $\tilde{t}[u] $.  
-Now, we impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT. 
+We impose now the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT (see Eq.
+\eqref{eq:cusp_psi_mu_0} in Appendix \ref{sec:cusp}).
 Mathematically, this conditions implies that 
@@
 \end{equation}
-which depends on a unique parameter $\mu$,  
-and the associated transcorrelated Hamiltonians obtained with $u(r_{12};\mu)$ is also controlled by $\mu$
+which defines the new Jastrow factor $u(r_{12};\mu)$ which depends on a unique parameter $\mu$.  
+The associated transcorrelated Hamiltonians obtained with $u(r_{12};\mu)$ is also controlled by $\mu$
 \begin{equation}
@@
 \end{equation}
-Therefore, the right eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the ground state eigenvector is defined by 
+Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the ground state right-eigenvector is defined by 
 \begin{equation}
@@
 
-The main difference with the original proposal of the frozen Gaussian geminal (FROGG) of Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+The main difference with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
 we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
-ii) the analytical form of $u(r_{12};\mu)$ is obtained from analytical conditions and not by a fit as in the FROGG,  
-iii) the new Jastrow factor is more flexible than the FROGG as it is tuned by a unique parameter $\mu$.
+ii) the analytical form of $u(r_{12};\mu)$ is obtained from analytical conditions and not by a fit as in the case of the FROGG,  
+iii) the new Jastrow factor $u(r_{12};\mu)$ is more flexible than the FROGG as it is tuned by a unique parameter $\mu$.
 
@@
 \end{equation}
-which leads for $\mathcal{J}(r_{12},\mu)$
+A first remark is that $u(r_{12};\mu)$ exactly restores the cusp as
+\begin{equation}
+ \label{eq:cusp_phi_0}
+ \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u(r_{12};\mu) = \frac{1}{2},
+\end{equation}
+implying that the right-eigenvector $\phimu(\br{}_{1},\br{}_{2})$ is cusp less (see Appendix \ref{sec:cusp}). 
+The Taylor expansion of Eq. \eqref{eq:j_dl} inserted in $\mathcal{J}(r_{12},\mu)$ leads to 
 \begin{equation}
@@
 
-As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ provides is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
+As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
 \begin{equation}
@@
 \end{equation}
-as a necessary condition of the to obtain a non divergent scalar potential is 
+and as a necessary condition of the to obtain a non divergent scalar potential is 
 \begin{equation}
@@
 \end{equation}
-as shown in the appendix \ref{sec:cusp} (see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1}). 
-Because the condition of Eq. \eqref{eq:cusp_phi_0} is fulfilled by $u(r_{12},\mu)$ for all $\mu < \infty$, 
-the effective potential obtained by the similarity transformation of $H$ by $u(r_{12},\mu)$ is necessary non divergent.
-
-Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ almost identical \textit{in average}, as they perfectly agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
+(see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}), $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.  
+%Because the condition of Eq. \eqref{eq:cusp_phi_0} is fulfilled by $u(r_{12},\mu)$ for all $\mu < \infty$, 
+%the effective potential obtained by the similarity transformation of $H$ by $u(r_{12},\mu)$ is necessary non divergent.
+
+Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ almost identical \textit{in average}, as they numerically agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
 
@@
 \label{sec:h_mu_lim}
-Regarding now the variation of $\tilde{H}[\mu]$, one expects that as 
+Regarding now the variation of $\tilde{H}[\mu]$, as 
 \begin{equation}
@@
 
-As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian at large $\mu$ (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
-As pointed in section \ref{sec:h_mu_lim}, even though $\tilde{H}[\mu]$ is still non hermitian as long as $\mu < \infty$, by varying $\mu$ one can change the nature of the electron-electron interaction in $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ from a repulsive and non divergent interaction at large $\mu$ (an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
-Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  
-its projection into a basis set $\tilde{H}[\mu]^{\basis}$ will behave differently as a function of $\mu$ 
-and so will the right eigenvectors $\ket{\phiimub}$ and the corresponding eigenvalues $E_i^{\basis}[\mu]$. 
-Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $u(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
+%As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian at large $\mu$ (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+%As pointed in section \ref{sec:h_mu_lim}, even though $\tilde{H}[\mu]$ is still non hermitian as long as $\mu < \infty$, by varying $\mu$ one can change the nature of the electron-electron interaction in $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ from a repulsive and non divergent interaction at large $\mu$ (an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
+%Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  
+%its projection into a basis set $\tilde{H}[\mu]^{\basis}$ will behave differently as a function of $\mu$ 
+%and so will the right eigenvectors $\ket{\phiimub}$ and the corresponding eigenvalues $E_i^{\basis}[\mu]$. 
+%Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $u(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
 \subsection{$\mu$ dependence of the convergence of the ground state eigenvalue with respect to the basis set }
@@
 Nevertheless, one can also observe that, for each $\mu$, the error with respect to the exact energy gets smaller  
-when enlarging the basis set.
-Also, qualitatively, one can observe that there are two regimes of $\mu$: $\mu \in[0.2,0.35]$ where the $E_0^\mu$ is always below $E_0$ and $\mu\ge 0.7$ where $E_0^\mu$ converges from above, as if the variational principle still applied.
-As $\mu$ increases, the difference between $E_0^\mu$ and $E_0^\text{FCI}$ in a given basis set diminishes, 
+when enlarging the basis set, which illustrates that in the limit of a complete basis set the eigenvalues of any TC Hamiltonian coincide with that of the physical Hamiltonian.
+
+Qualitatively, one can observe that there are two regimes of $\mu$: $\mu \in[0.2,0.35]$ where $E_0^{\basis}[\mu]$ is always below $E_0$ and $\mu\ge 0.7$ where $E_0^{\basis}[\mu]$ converges from above, as if the variational principle still applied.
+As $\mu$ increases, the difference between $E_0^{\basis}[\mu]$ and $E_0^{\basis}[\text{FCI}]$ in a given basis set diminishes, 
 which is expected as in the $\mu \rightarrow \infty$ limit, one obtains that  $\tilde{H}[\mu] \rightarrow H$.
 
-Also, it is striking to see that the total energies obtained, in a given basis set, by the TC Hamiltonian obtained by the FROGG and that obtained by $\tilde{H}[\mu]$ with $\mu=\mfrogg$ coincide with less than 1 mH.
+Also, it is striking to see that, in a given basis set, the ground state eigenvalue of the TC Hamiltonian obtained by the FROGG and that obtained by $\tilde{H}[\mu]$ with $\mu=\mfrogg$ coincide with less than 1 mH.
 The latter results confirms that as $u(r_{12},\mfrogg) \approx f_{\text{TN}}(r_{12})$ (see Fig \ref{fig_j_mu} and Eqs.
@@
 
-Coming now to the speed of convergence of $E_0^\mu$ with respect to the basis set, it is always faster than that of $E_0^\text{FCI}$ for the whole range of values of $\mu$ selected here. 
+Coming now to the speed of convergence of $E_0^{\basis}[\mu]$ with respect to the basis set, it is always faster than that of $E_0^{\basis}[\text{FCI}]$ for the whole range of values of $\mu$ selected here.
 To quantify better such observations, one can identify the basis set from which the error with respect to the exact non relativistic energy is smaller, in absolute value, than 1mH. 
@@
 For $1.6\ge \mu \ge 3.0$, such accuracy is reached at the aug-cc-pVQZ level, whenever such accuracy is reached at the aug-cc-pV5Z level using the regular FCI Hamiltonian.
-The quality of the results obtained with the FROGG are in between that obtained with $\mu=0.7$ and $\mu=1.0$.
+%The quality of the results obtained with the FROGG are in between that obtained with $\mu=0.7$ and $\mu=1.0$.
 
@@
 \label{sec:he_real_space}
-In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_i^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
+In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_0^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
@@
 
-Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = \tilde{H}[\mu]$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
+Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]^{\basis}$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = \tilde{H}[\mu]$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
 If one focusses now on the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$, it is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through
@@
 \end{equation}
-Therefore, in a given basis set $\basis$, the right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to estimate the exact ground state wave function $\psiex$ through 
+Therefore, in a given basis set $\basis$, the ground state right eigenvector $\phimub$ of $\tilde{H}[\mu]^{\basis}$ can be used to estimate the exact ground state wave function $\psiex$ through 
 \begin{equation}
@@
 \end{equation}
-Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$, in the $L^2$ sense for instance.
+Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$. 
+To illustrate that, 
+we plotted a cutting of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
+The cutting used is the following: we set two electrons on a circle of radius $r=0.5$ a.u.
+from the nucleus and look at the wave functions as a function of the angle $\theta_{12}$ between the $\bri{1}$ and $\bri{2}$.
 For this study, we approximate the exact ground state wave function $\psiex(\br{}_1,\br{}_2)$ of the helium atom by the wave function developed by Umrigar \textit{et.
 al.}\cite{UmrGon-PRA-94} which contains explicitly the $r_{12}$ coordinate and which provides a total energy accurate up to twelve digits.
-We plotted a cutting of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
-The cutting used is the following: we set two electrons on a circle of radius $r=0.5$ a.u.
-from the nucleus and look at the wave functions as a function of the angle $\theta_{12}$ between the $\bri{1}$ and $\bri{2}$.
 
@@
 
-The understanding of such observations can be provided by the mathematical and physical investigation of the construction of $\tilde{H}[\mu]$.
+A qualitative understanding of such observations can be provided by some physical considerations regarding $\tilde{H}[\mu]$ and its dependence with $\mu$.
 
@@
 As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depends on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which they converge significantly faster with the basis set with respect to the usual Hamiltonian.
-Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on this isoelectronic series which consist in weakly correlated covering a quite wide range of densities.
+Of course, the 'optimal' range of $\mu$ might depend on the system and we investigate here different approaches to systematically find a reasonable value of $\mu$ and test it on this isoelectronic series which consist in weakly correlated systems covering a quite wide range of densities.
 As in the study of the helium atom of Sec \ref{sec:total_he}, in a given basis set $\basis$ and for a given system, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
@@
 From these data, one can see that MAD is sensibly the same than that with the $\murscav$ but with a MSD of opposite sign with respect to the latter.
-This implies that the values of $\muuegav$ are in general larger than that of $\murscav$, which was observed in the present calculations.
-Also, one can see that $ \muuegav$ increases with the system size and that, except for H$^-$, it is always larger than $\murscav$. 
+This correlates with the fact that the values of $\muuegav$ are in general larger than that of $\murscav$, except for H$^-$.
 Because the MAD are essentially the same but that the MSD are of opposite sign, it means that there exists an optimal value of $\mu$ between $\murscav$ and $\muuegav$ which might be optimal. 
@@
 From these data one can clearly observe several things: i) while for quite diffuse systems as H$^-$ and He the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
-These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system and the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
+These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system, and therefore shows the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
 
@@
 \ref{sec:new_j}).
-The Jastrow factor $u(r_{12},\mu)$ resulting from such mathematical conditions naturally imposes the cusp and digs the Coulomb hole over a range tuned by a unique parameter $\mu$: the smaller the $\mu$, the broader and deeper is the Coulomb hole dug by $u(r_{12},\mu)$, and in the $\mu \rightarrow \infty$ limit, $u(r_{12},\mu)=0$.
+The Jastrow factor $u(r_{12},\mu)$ resulting from such mathematical conditions naturally imposes the cusp and digs the Coulomb hole over a typical length scale tuned by a unique parameter $\mu$: the smaller the $\mu$, the broader and deeper is the Coulomb hole dug by $u(r_{12},\mu)$, and in the $\mu \rightarrow \infty$ limit, $u(r_{12},\mu)=0$.
 The TC Hamiltonian $\tilde{H}[\mu]$ obtained from the similarity transformation of the usual Hamiltonian with $u(r_{12},\mu)$ is analytical and depends on a unique parameter $\mu$. 
@@
 \ref{sec:total_he}).
-An investigation of the right eigenvectors in real space for different values of $\mu$ provided interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
+An investigation of the right eigenvectors in real space for different values of $\mu$ have shown interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
 Nevertheless, when the right eigenvectors are multiplied by the corresponding Jastrow factor, one obtains a very good approximation of the numerically exact ground state wave function (see Sec.
@@
 As the density considerably vary among the isoelectronic series, we propose a very simple scheme to provide a value of $\mu$ which automatically adapts to the system, the value of which increases with the nuclear charge of the atom considered.
-The results obtained for this system dependent value of $\mu$ are found to be very accurate as the MAD t the exact ground state energies over this isoelectronic series in double-zeta quality is about 1 mH and keeps lowering while improving the quality of the basis set.
-In contrast, the MAD obtained with the FROGG is much higher: it is of about 7 mH in the double-zeta quality basis set, which can be understood by the fact that the typical range of the correlation effect imposed by the FROGG is less accurate for shrink densities than for typical valence densities.
+The results obtained for this system-dependent value of $\mu$ are found to be very accurate as the MAD with respect to the exact ground state energies over this isoelectronic series in double-zeta quality is about 1 mH and keeps lowering while improving the quality of the basis set.
+In contrast, the MAD obtained with the FROGG is much higher: it is of about 7 mH in the double-zeta quality basis set, which can be understood by the fact that the typical length scale of the correlation effect imposed by the FROGG is less adapted for core densities than for typical valence densities.
 
 The last part of our study is dedicated to the study of the ground state energy curve of H$_2$ with different schemes, and we show that the present scheme provides an improvement of the convergence of the energy over the whole potential energy curve.
+
+The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and tu explore the possibility of having a value of $\mu$ varying in space.
 

### 2020-12-17 cusp_j/paper/paper.tex
conclusion almost done

@@
 Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a frozen universal Jastrow factor.
-This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}).
+This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}.
 The Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions and referred to as the frozen gaussian geminal (FROGG), only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
@@
 Nevertheless, as approximations are necessary done in the wave function ansatz for realistic systems, 
-the biorthogonal approach might improve the quality of the results.
-
-In latter works, Umezawa \textit{et.
+the biorthogonal approach might improve the quality of the results in practice.
+
+In later works, Umezawa \textit{et.
 al.}\cite{UmeTsu-JCP-03,UmeTsuOhnShiChi-JCP-05} introduced a scheme to couple TC equations with the usual variational Monte Carlo (VMC) scheme in order to optimise the Jastrow factor through a variance miminization.
@@
 al.}\cite{YanShi-JCP-12}  where the Jastrow factor is expressed as an anti-hermitian operator, allowing one to obtain an hermitian effective Hamiltonian after the similarity transformation, which is then efficiently truncated through the use the canonical transformation\cite{NeuYanCha-MolPhys-10}.
+Recent applications of such method to the context of quantum computing have been recently published\cite{ValTak-PCCP-20}.
 
@@
 We show that the rapid convergence of the total energies coincides with a rapid convergence of the right eigenvectors in real space, and how to recover a very good approximation of the exact ground state wave function.
-Based on such encouraging results, we study the ground state energy of the helium isoelectronic series from Li$^+$ to Ne$^{8+}$ and compare different schemes to obtain 
+Based on such encouraging results, we study the ground state energy of the helium isoelectronic series from H$^-$ to Ne$^{8+}$ and compare different schemes to obtain 
 a value of $\mu$ which automatically adapts to the system and still provides a fast convergence of the total energies. 

### 2020-12-17 cusp_j/paper/paper.tex
conclusion almost finished

@@
 \begin{abstract}
-TODO: investigate the non variationality on the He atom for instance and Ne8+
+The present work introduces a new form of explicitly correlated factor in the context of the transcorrelated methods. 
+The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces at leading order in $1/r_{12}$ the long-range interaction of the range-separated density functional theory.
+The resulting correlation factor is then tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
+The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression and its physical contents depends on the same parameter $\mu$: one can continuously change from a non divergent repulsive Hamiltonian potential at large $\mu$ to a purely attractive one at small $\mu$.
+We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems.
+We found that the convergence towards the complete basis set is much faster for a quite wide range values of $\mu$.
+We also propose a computationally cheap way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.
+It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
 
@@
 \subsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
+\label{sec:he_htilde}
 Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates  
@@
  \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)^2  \bigg) \\
-           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{u}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{u},\bri{k}),
- \end{aligned}
-\end{equation}
-where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{u})$ and $\hat{L}(\bri{i},\bri{u},\bri{k})$ are defined as
+           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
 \begin{equation}
@@
 \end{equation}
-Then, the non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ contains 
+The non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ contains 
 \begin{equation}
@@
  \label{eq:d2_x1_2}
- &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})\\ 
+ &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})
  & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
@@
 
-\section{Computation of integrals}
-\subsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
-We need to compute the following integral 
-\begin{equation}
- \label{eq:l_ijmkln}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
- \end{aligned}
-\end{equation}
-where 
-\begin{equation}
- \hat{L}_1(\bri{1},\bri{2},\bri{3}) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
-\end{equation}
-with 
-\begin{equation}
- w_\mu(\bri{13}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
-\end{equation}
-Let us compute the first term of Eq. \eqref{eq:l_ijmkln}:
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
- &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
- \end{aligned}
-\end{equation}
-Such matrix element can be further decomposed into
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
- =& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
- \end{aligned}
-\end{equation}
-where 
-\begin{equation}
- \begin{aligned}
- \label{eq:l_1x}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
- &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
- \end{aligned}
-\end{equation}
-If we define the following function 
-\begin{equation}
- W_{mn}^x({\bf r})  = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}) (x - x'),  
-\end{equation}
-it can be calculated easily by
-\begin{equation}
- W_{mn}^x({\bf r})  = x \, w_{mn}({\bf r}) - w_{mn}^x({\bf r})
-\end{equation}
-with 
-\begin{equation}
- w_{mn}({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}), 
-\end{equation}
-and 
-\begin{equation}
-  w_{mn}^x({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'})  x'.
-\end{equation}
-Then, one can rewrite the matrix element of Eq. \eqref{eq:l_1x} as
-\begin{equation}
- \begin{aligned}
- \label{eq:l_1x_2}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
- \end{aligned}
-\end{equation}
-which can be easily evaluated numerically. 
-Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3})$ is simply 
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
- \end{aligned}
-\end{equation}
-which can be numerically evaluated easily. 
-The total matrix element of the full operator is then 
-\begin{equation}
- \label{eq:l_ijmkln_final}
- \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
- + & \int \text{d}{\bf r}\phi_u({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
- + & \int \text{d}{\bf r} \phi_m({\bf r})  \phi_n({\bf r}) \bigg( W_{jl}^x({\bf r}) W_{ik}^x({\bf r}) + W_{jl}^y({\bf r}) W_{ik}^y({\bf r}) + W_{jl}^z({\bf r}) W_{ik}^z({\bf r})\bigg), 
- \end{aligned}
-\end{equation}
-which can be computed on the fly through a simple numerical integration.
-
 \section{Appendix}
@@
 \label{sec:cusp}
-Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
+Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom in Sec.
+\ref{sec:he_htilde}, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
 The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill. 
-For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are general for any bounded eigenvectors.
+It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system .
+For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are valid for any bounded eigenvectors.
 
@@
 \end{equation}
-and as the effective interaction $\frac{\text{erf}(\mu r_{12})}{r_{12}}$ is non divergent at $r_{12}=0$ for finite values of $\mu$
+and 
 \begin{equation}
@@
 
-\subsection{Appendix: large $\mu$ limit of $\tilde{H}[\mu]$}
+\subsection{Large $\mu$ limit of $\tilde{H}[\mu]$}
 \label{sec:large_mu_lim}
-Nevertheless, in the large $\mu$ limit, one can notice that 
+As mentioned in Sec. \ref{sec:h_mu_lim}, one must recover the usual physical Hamiltonian in the large $\mu$ limit. 
+Nevertheless, one can notice that 
 \begin{equation}
@@
 \end{equation}
-where $\delta(r_{12})$ is the Dirac distribution, and as the firs-order differential term vanishes in the large $\mu$ limit (see Eq.\eqref{eq:exp_ht_mu}), one could be tempted to write that 
+with 
+\begin{equation}
+ \delta(x) = \lim_{\mu} \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu x \big)^2}, 
+\end{equation}
+being the Dirac distribution. Threfore, one could be tempted to write that 
 \begin{equation}
@@
  \label{eq:lim_mu_4}
- \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = h_c + \frac{1}{r_{12}} + \delta(r_{12}) \\
-                                             & = H + \delta(r_{12})  \\
+ \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = H + \delta(r_{12})  \\
                                              & \ne H,
@@
 
-Nevertheless, as the right hand side of Eq.\eqref{eq:lim_mu_4} contains a Delta distribution, it must be considered in the sense of distributions an not point wise. 
+Nevertheless, as Eq.\eqref{eq:lim_mu_4} deals with operators, the equality must be considered in the sense of distributions.  
 Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
@@
 
-\section{Integrals involved in TenNo work}
-The Jastrow factor of Ten-No is of the form
-\begin{equation}
- u(r_{12})=\sum_{m=1}^{N_g} c_m e^{-\alpha_m \big(r_{12}\big)^2},
-\end{equation}
-where the $c_m$ and $\alpha_m$ are given in \cite{TenNo-CPL-00-a}. 
-To compute the transcorrelated Hamiltonian one needs to compute therefore 
-\begin{equation}
- \begin{aligned}
- \label{def_k}
-  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
-                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
-                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1.
- \end{aligned}
-\end{equation}
-\subsection{Computation of the gradient}
-One can write that 
-\begin{equation}
- u(r_{12})=\sum_{m=1}^{N_g} c_m v(r_{12},\alpha_m)
+\subsection{Computation of $\hat{K}(\bri{1},\bri{2})$} 
+The only integrals involved of $\hat{K}(\bri{1},\bri{2})$ over Gaussian functions which are not analytical are of the types 
+\begin{equation}
+ \label{eq:k_ijkl}
+ v_{ij}^{kl} = \int \dr{1} \dr{2} \phi_i(\bri{1}) \phi_j(\bri{2}) \big( g(r_{12},\mu) \big)^2  \phi_k(\bri{1}) \phi_l(\bri{2}),  
 \end{equation}
@@
 \begin{equation}
- v(r_{12},\alpha) = e^{-\alpha \big(r_{12}\big)^2}.
-\end{equation}
-The gradient with respect to $\br{1}$ is 
-\begin{equation}
- \deriv{}{x_1}{} v(r_{12},\alpha) = -2 \alpha (x_1 - x_2) e^{-\alpha \big(r_{12}\big)^2},
-\end{equation}
-and one has of course 
-\begin{equation}
- \deriv{}{x_2}{} v(r_{12},\alpha) = - \deriv{}{x_1}{} v(r_{12},\alpha). 
-\end{equation}
-\subsection{Computation of the non Hermitian term}
-One needs to compute 
-\begin{equation}
- \nabla_1 v(r_{12},\alpha) \cdot \nabla_1 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_2,
-\end{equation}
-but as 
-\begin{equation}
- \deriv{}{x_2}{} v(r_{12},\alpha) = - \deriv{}{x_1}{} v(r_{12},\alpha), 
-\end{equation}
-one has 
-\begin{equation}
-  \nabla_1 v(r_{12},\alpha) \cdot \nabla_1 + \nabla_2 v(r_{12},\alpha) \cdot \nabla_2 = \nabla_1 u(r_{12},\alpha) \cdot  \big( \nabla_1 - \nabla_2 \big). 
-\end{equation}
-Let us introduce the following functions  
-\begin{equation}
- w_{ij}(\alpha,\bri{1}) = \int \text{d}\br{} e^{-\alpha \big(\br{} - \bri{1} \big)^2} \phi_i(\br{}) \phi_j(\br{}),
-\end{equation}
-\begin{equation}
- w_{ij}^x(\alpha,\bri{1}) = \int \text{d}\br{}  e^{-\alpha \big(\br{} - \bri{1} \big)^2} x\phi_i(\br{}) \phi_j(\br{}).
-\end{equation}
-Therefore, the integral of the form 
-\begin{equation}
- \begin{aligned}
- \matelem{kl}{\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2}  \phi_k(\bri{1}) \phi_l(\bri{2}) \\
-\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)  \phi_i(\bri{1}) \phi_j(\bri{2}) ,
- \end{aligned}
-\end{equation}
-can be put into 
-\begin{equation}
- \begin{aligned}
- \matelem{kl}{\nabla_1 u(\bri{1},\bri{2}) \cdot  \big( \nabla_1 - \nabla_2 \big)}{ij} = \matelem{kl}{\hat{t}_x(\alpha) + \hat{t}_y(\alpha) + \hat{t}_z(\alpha)}{ij},
- \end{aligned}
+ g(x, \mu)= \text{erf}(x \mu) - 1.
+\end{equation}
+To make integrals analytical, we first fit the function $\text{erfc}(x)$ with a simple Slater-Gaussian function 
+\begin{equation}
+ \text{erfc}(x) \approx h(x,\alpha,\beta,c)
 \end{equation}
@@
 \begin{equation}
- \begin{aligned}
- \matelem{kl}{\hat{t}_x(\alpha)}{ij} =&  -2 \alpha \int \text{d}\bri{1} \phi_k(\bri{1}) x_1\big( \deriv{}{x_1}{} \phi_i(\bri{1})\big) w_{jl}(\alpha,\bri{1})  \\
-                                      &  -2 \alpha \int \text{d}\bri{1} \phi_l(\bri{1}) x_1\big( \deriv{}{x_1}{} \phi_j(\bri{j})\big) w_{ik}(\alpha,\bri{1})  \\
-                                      &  +2 \alpha \int \text{d}\bri{1} \phi_k(\bri{1}) \big( \deriv{}{x_1}{} \phi_i(\bri{j})\big) w_{jl}^x(\alpha,\bri{1})  \\
-                                      &  +2 \alpha \int \text{d}\bri{1} \phi_l(\bri{1}) \big( \deriv{}{x_1}{} \phi_j(\bri{j})\big) w_{ik}^x(\alpha,\bri{1})  \\
- \end{aligned}
-\end{equation}
-\subsection{Computation of the square term}
-One needs to compute 
-\begin{equation}
- \begin{aligned}
- \bigg( \nabla_1 u(r_{12}) \bigg)^2 = \sum_{m,n=1}^{N_g} c_m c_n \nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n).
- \end{aligned}
-\end{equation}
-The term $\nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n)$ is 
-\begin{equation}
- \nabla_1 v(r_{12},\alpha_m) \cdot \nabla_1 v(r_{12},\alpha_n) = 4 \alpha_m \alpha_n v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2.
-\end{equation}
-Therefore, the integral of type 
-\begin{equation}
- \matelem{kl}{\bigg( \nabla_1 u(r_{12}) \bigg)^2}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_k(\bri{1}) \phi_l(\bri{2}) \big(\nabla_1 u(r_{12}) \big)^2
-\end{equation}
-can be written as  
-\begin{equation}
- \matelem{kl}{\bigg( \nabla_1 u(r_{12}) \bigg)^2}{ij} = \sum_{m,n=1}^{N_g} c_m c_n  4 \alpha_m \alpha_n \matelem{kl}{v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2}{ij} 
-\end{equation}
-where 
-\begin{equation}
- \begin{aligned}
- &\matelem{kl}{v(r_{12}, \alpha_m + \alpha_n) (\bri{1}- \bri{2})^2}{ij} \\& = \matelem{kl}{I_x(\alpha_m + \alpha_n) + I_y(\alpha_m + \alpha_n) + I_z(\alpha_m + \alpha_n)}{ij}
- \end{aligned}
-\end{equation}
-where 
-\begin{equation}
- \begin{aligned}
- \matelem{kl}{I_x(\alpha)}{ij}=& \int \text{d}\bri{1} \phi_i(\bri{1}) \phi_k(\bri{1}) (x_1)^2 w_{jl}(\alpha,\bri{1}) \\
-                              +& \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) (x_1)^2 w_{ik}(\alpha,\bri{1}) \\
-                              -& \int \text{d}\bri{1} \phi_i(\bri{1}) \phi_k(\bri{1}) x_1 w_{jl}^x(\alpha,\bri{1}) \\
-                              -& \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) x_1 w_{ik}^x(\alpha,\bri{1}) \\
- \end{aligned}
-\end{equation}
-\subsection{Computation of the Laplacian}
-One needs to compute 
-\begin{equation}
- \begin{aligned}
-  \Delta_1 u(r_{12}) = \sum_{m} c_m \Delta_1  v(r_{12},\alpha_m).
- \end{aligned}
-\end{equation}
-The Laplacian of $v(r_{12},\alpha)$ is 
-\begin{equation}
- \begin{aligned}
- \deriv{}{x_1}{2} v(r_{12},\alpha) &= \deriv{}{x_2}{2} v(r_{12},\alpha) \\
-                           &= v(r_{12},\alpha) 2 \alpha \bigg( 2 \alpha \big( (x_1)^2 + (x_2)^2 \big) -4 \alpha x_1 x_2  -1\bigg)
- \end{aligned}
-\end{equation}
-and so 
-\begin{equation}
- \begin{aligned}
- \Delta_1 v(r_{12},\alpha) &= v(r_{12},\alpha) 2 \alpha \bigg( 2 \alpha \big( (r_1)^2 + (r_2)^2 \big) -4 \alpha \bri{1}\cdot \bri{2}  -3\bigg).
- \end{aligned}
-\end{equation}
-One can express the following integral 
-\begin{equation}
- \matelem{kl}{\Delta_1 v(r_{12},\alpha)}{ij} = \int \text{d}\bri{1}  \text{d}\bri{2} \Delta_1 v(r_{12},\alpha) 
-\phi_i(\bri{1}) \phi_j(\bri{2}) \phi_k(\bri{1}) \phi_l(\bri{2}),
-\end{equation}
-as 
-\begin{equation}
- \begin{aligned}
-  \matelem{kl}{\Delta_1 v(r_{12},\alpha)}{ij} =&  4 \alpha^2 \int \text{d}\bri{1} (r_1)^2 \phi_i(\bri{1}) \phi_k(\bri{1}) w_{jl}(\alpha,\bri{1})  \\
-                                               +& 4 \alpha^2 \int \text{d}\bri{1} (r_1)^2 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}(\alpha,\bri{1})  \\
-                                               -& 6 \alpha \int \text{d}\bri{1} \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}(\alpha,\bri{1})  \\
-                                               -& 8 \alpha^2 \int \text{d}\bri{1} x_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^x(\alpha,\bri{1})  \\
-                                               -& 8 \alpha^2 \int \text{d}\bri{1} y_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^y(\alpha,\bri{1})  \\
-                                               -& 8 \alpha^2 \int \text{d}\bri{1} z_1 \phi_j(\bri{1}) \phi_l(\bri{1}) w_{ik}^z(\alpha,\bri{1})  \\
- \end{aligned}
-\end{equation}
-
-\section{Numerical computation of integrals}
-\subsection{Fit of functions}
-\subsubsection{Fit of $1-\text{erf}(x)$}
-At some point we would like to fit the following function
-\begin{equation}
- g(x) = 1-\text{erf}(x)
-\end{equation}
-which can be done, for instance by 
-\begin{equation}
  h(x,\alpha,\beta,c) = e^{-\alpha x - \beta x^2}
 \end{equation}
-with $\alpha=1.09529$ and $\beta = 0.756023$. 
-So by posing $y=\mu x$, $x=y/\mu$ then
+and $\alpha=1.09529$ and $\beta = 0.756023$. 
+Then, by posing $y=\mu x$, $x=y/\mu$ one obtains 
 \begin{equation}
@@
  \begin{aligned}
-  g(x,\mu)  =& 1 - \text{erf}(\mu x) \approx e^{-\alpha \mu x - \beta (\mu x)^2}\\ 
-        =& e^{-\alpha \mu x } e^{-\beta \mu^2 x^2} \\
+  g(x,\mu)  \approx & e^{-\alpha \mu x - \beta (\mu x)^2}\\ 
         =& h(x,\alpha \mu, \beta \mu^2).
@@
  \begin{aligned}
- g(x,\mu)^2 = \bigg( 1 - \text{erf}(\mu x) \bigg)^2\\
+ g(x,\mu)^2&= \bigg( 1 - \text{erf}(\mu x) \bigg)^2\\
            &= \bigg( e^{-\alpha \mu x } e^{-\beta \mu^2 x^2}\bigg)^2 \\
@@
 \end{equation}
-
-\subsubsection{Fit of $e^{-x}$}
-The fit of $1 - \text{erf}(\mu x)$ in Eq. \eqref{fit_erf} involves a Slater function, which is always rather complex to integrate. 
-Nevertheless, we can fit a Slater function with Gaussian functions (that is what quantum chemistry is about):
-\begin{equation}
- e^{-X} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m X^2}, 
-\end{equation}
-and, by posing $X=\gamma x$ one can fit any Slater function as
+Then we fit the Slater function as a linear combination of Gaussians 
+\begin{equation}
+ e^{-X} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m X^2}. 
+\end{equation}
+In the present work, we use $N_s=20$ and the $\{c_m,\zeta_m\}$ parameters are reported in Table \ref{gauss_fit}.
+\begin{table}
+\label{gauss_fit}
+\caption{Set of coefficients $c_m$ and exponents $\zeta_m$ for the fit of $e^{-X}$}
+\begin{ruledtabular}
+\begin{tabular}{ll}
+ $\zeta_m$ & $c_m$ \\
+\hline                 
+   30573.77073         & 0.00338925525  \\
+   5608.452381         & 0.00536433869  \\
+   1570.956734         & 0.00818702846  \\
+   541.3978511         & 0.01202047655  \\
+   212.4346963         & 0.01711289568  \\
+   91.31444574         & 0.02376001022  \\
+   42.04087246         & 0.03229121736  \\
+   20.43200443         & 0.04303646818  \\
+   10.37775161         & 0.05624657578  \\
+   5.468807545         & 0.07192311571  \\
+   2.973735292         & 0.08949389001  \\
+   1.661441902         & 0.10727599240  \\
+   0.9505256082        & 0.12178961750  \\
+   0.5552868397        & 0.12740141870  \\
+   0.3304336002        & 0.11759168160  \\
+   0.1998230323        & 0.08953504394  \\
+   0.1224684076        & 0.05066721317  \\
+   0.07575825322       & 0.01806363869  \\
+   0.04690146243       & 0.00305632563  \\
+   0.02834749861       & 0.00013317513  \\
+\end{tabular}
+\end{ruledtabular}
+\end{table}
+By posing $X=\gamma x$ one can fit any Slater function as
 \begin{equation}
@@
 \end{equation}
-To find the $\{c_m,\zeta_m\}$ parameters, I performed a Hartree Fock calculation on the Hydrogen atom using the $s$ functions of the ANO-RCC basis set which contains 8 gaussians.
+Eventually, the function $g(x,\mu)^2$ is obtained as a linear combination of Gaussian
+\begin{equation}
+ g(x,\mu)^2 \approx \sum_{m=1}^{N_s} c_m e^{-2\mu^2\big(2 \alpha \zeta_m + \beta\big) x^2},
+\end{equation}
+which makes then the integrals analytical
+\begin{equation}
+ v_{ij}^{kl} \approx \sum_{m=1}^{N_s} c_m \int \dr{1} \dr{2} \phi_i(\bri{1}) \phi_j(\bri{2}) e^{-2\mu^2\big(2 \alpha \zeta_m + \beta\big) (r_{12})^2} \phi_k(\bri{1}) \phi_l(\bri{2}).
+\end{equation}
+
+\subsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
+We need to compute the following integral 
+\begin{equation}
+ \label{eq:l_ijmkln}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
+ \end{aligned}
+\end{equation}
+where 
+\begin{equation}
+ \hat{L}_1(\bri{1},\bri{2},\bri{3}) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
+\end{equation}
+with 
+\begin{equation}
+ w_\mu(\bri{13}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
+\end{equation}
+Let us compute the first term of Eq. \eqref{eq:l_ijmkln}:
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
+ \end{aligned}
+\end{equation}
+Such matrix element can be further decomposed into
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
+ =& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
+ \end{aligned}
+\end{equation}
+where 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:l_1x}
+& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+ = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
+ \end{aligned}
+\end{equation}
+If we define the following function 
+\begin{equation}
+ W_{mn}^x({\bf r})  = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}) (x - x'),  
+\end{equation}
+it can be calculated easily by
+\begin{equation}
+ W_{mn}^x({\bf r})  = x \, w_{mn}({\bf r}) - w_{mn}^x({\bf r})
+\end{equation}
+with 
+\begin{equation}
+ w_{mn}({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'}), 
+\end{equation}
+and 
+\begin{equation}
+  w_{mn}^x({\bf r}) = \int \text{d}{\bf r'} \phi_m({\bf r}') \phi_n({\bf r}') w_{\mu}({\bf r} - {\bf r'})  x',
+\end{equation}
+which are analytical integrals.  
+Then, one can rewrite the matrix element of Eq. \eqref{eq:l_1x} as
+\begin{equation}
+ \begin{aligned}
+ \label{eq:l_1x_2}
+& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
+ \end{aligned}
+\end{equation}
+Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3})$ is simply 
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
+ \end{aligned}
+\end{equation}
+which can be numerically evaluated easily. 
+The total matrix element of the full operator is then 
+\begin{equation}
+ \label{eq:l_ijmkln_final}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
+ + & \int \text{d}{\bf r}\phi_u({\bf r})  \phi_l({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{ik}^x({\bf r}) + W_{mn}^y({\bf r}) W_{ik}^y({\bf r}) + W_{mn}^z({\bf r}) W_{ik}^z({\bf r})\bigg) \\
+ + & \int \text{d}{\bf r} \phi_m({\bf r})  \phi_n({\bf r}) \bigg( W_{jl}^x({\bf r}) W_{ik}^x({\bf r}) + W_{jl}^y({\bf r}) W_{ik}^y({\bf r}) + W_{jl}^z({\bf r}) W_{ik}^z({\bf r})\bigg), 
+ \end{aligned}
+\end{equation}
+which can be computed on the fly through a simple numerical integration.
 

### 2020-12-17 dev/ao_one_ints_slater/fit_slat_gauss.irp.f

@@ -20,26 +20,6 @@
  ! The coefficient are taken from the ano-rcc expansion of the hydrogen 1s orbital
  END_DOC
 
-! coef_fit_slat_gauss(1) =  2.6032524673598918d-002
-! coef_fit_slat_gauss(2) =  4.8538671362083070d-002
-! coef_fit_slat_gauss(3) =  8.1756487143886281d-002
-! coef_fit_slat_gauss(4) = 0.1220544746390489d0    
-! coef_fit_slat_gauss(5) = 0.1443695761749570d0    
-! coef_fit_slat_gauss(6) = 0.1056239657977568d0    
-! coef_fit_slat_gauss(7) =  2.3962067692955683d-002
-! coef_fit_slat_gauss(8) =  1.0571415716647108d-004
-!
-! coef_fit_slat_gauss *= sqpi ! for normalization
-!
-! expo_fit_slat_gauss(1)  = 188.61445d0    
-! expo_fit_slat_gauss(2)  =  28.276596d0  
-! expo_fit_slat_gauss(3)  =   6.4248300d0  
-! expo_fit_slat_gauss(4)  =   1.8150410d0 
-! expo_fit_slat_gauss(5)  =    .59106300d0 
-! expo_fit_slat_gauss(6)  =    .21214900d0 
-! expo_fit_slat_gauss(7)  =    .07989100d0 
-! expo_fit_slat_gauss(8)  =    .02796200d0 
-
 
       expo_fit_slat_gauss(01)=30573.77073000000
       coef_fit_slat_gauss(01)=0.00338925525

### 2020-12-18 cusp_j/paper/paper.tex
some modifs

@@
 \newcommand{\phimu}[0]{\Phi^{\text{ex},\mu}_0}
+\newcommand{\phimui}[0]{\Phi^{\text{ex},\mu}_i}
 \newcommand{\phimub}[0]{\Phi^{\mathcal{B},\mu}_0}
@@
 
-\subsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
+\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
+\label{sec:new_j}
+\subsubsection{A simple physical picture: the transcorrelated Hamiltonian for the helium atom}
 \label{sec:he_htilde}
@@
 \eqref{eq:ht_general} that the two electrons experience a modified scalar potential given by $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u]$, and an additional differential operator $\tilde{t}[u]$,
-the latter making $\tilde{H}[u]$ non-hermitian. It is important to notice that the fact that  $\tilde{H}[u]$ is non-hermitian implies the loose of variational principle.
-
-\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
-\label{sec:new_j}
-\subsubsection{The working equation for $u(\mu,r_{12})$ }
-Eq. \eqref{eq:ht_general} gives the similarity transformed Hamiltonian for an arbitrary Jastrow factor, 
-and with respect to the usual Hamiltonian, $\tilde{H}[u]$ contains two types of additional terms which depend on the actual form of $u(r_{12})$: 
-a new electron-electron potential $1/r_{12} + \tilde{w}[u]+ \tilde{W}[u]$ and a new differential operator  $\tilde{t}[u] $.  
-We impose now the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT (see Eq.
+the latter making $\tilde{H}[u]$ non-hermitian.
+
+\subsubsection{The working equation for $u(\mu,r_{12})$ inspired by RSDFT}
+Having established the form of $\tilde{H}[u] $ in Eq.
+\eqref{eq:ht_general}, one can notice that the leading order terms in $1/r_{12}$ are $\frac{1}{r_{12}}  + \tilde{W}[u]$.
+We want now to impose the form of $u(r_{12})$ such that it mimics, at leading order in $1/r_{12}$, the long-range effective interaction entering in the effective Hamiltonian of the RS-DFT (see Eq.
 \eqref{eq:cusp_psi_mu_0} in Appendix \ref{sec:cusp}).
@@
 \end{equation}
-Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the ground state right-eigenvector is defined by 
-\begin{equation}
- \tilde{H}[\mu] \phimu(\br{}_{1},\br{}_{2}) = E_0 \phimu(\br{}_{1},\br{}_{2}), 
-\end{equation}
-where $E_0$ is the exact ground state energy. 
-As $\tilde{H}[\mu]$ originates from a similarity transformation, it conserves the same spectrum as $H$ as long as it is developed in a complete basis set.
-
-The main difference with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
+\begin{equation}
+ \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
+\end{equation}
+where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian.
+The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation.
+Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.
+
+The main difference of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
 we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
@@
 \subsubsection{A few properties of $u(r_{12};\mu)$}
-The new Jastrow $u(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which controls the value of the leading term of the effective interaction at $r_{12}=0$ (see Eq.\eqref{def_j_00}). 
+The new Jastrow $u(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which have the unit of the inverse of a distance. 
 To understand the physical content together with the mathematical properties of $u(r_{12};\mu)$, 
@@
  \label{eq:bigJ_dl}
- \mathcal{J}(r_{12};\mu) = e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2} + o(r_{12}^4) .
+ \mathcal{J}(r_{12};\mu) \approx e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}. 
 \end{equation}
 From Eq.
-\eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, the effective wave function  $\phiex(\br{}_1,\br{}_2)$ has necessary a larger value at coalescence (\textit{i.e.} $\br{}_1=\br{}_2)$), which can be intuitively understood as the electrons in $\tilde{H}[\mu]$ experience an effective non divergent interaction;
+\eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, the effective wave function  $\phiex(\br{}_1,\br{}_2)$ has necessary a larger value at coalescence (\textit{i.e.} $\br{}_1=\br{}_2)$),
 b) the term in $e^{ \frac{1}{2}r_{12}} $ restores exactly the lack of cusp of $\phiex(\br{}_1,\br{}_2)$ (see Eq.
@@
 \end{figure*}
-From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
+From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper and broader is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
 
@@
 \subsubsection{General form of $\tilde{H}[\mu]$ }
-Having established the analytical expression of $u(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
+Having established the analytical expression of $u(r_{12};\mu)$, one can derive the expression of the associated transcorrelated Hamiltonian for a general $N$-electron system.  
 According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
@@
  \label{def_k}
-  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
+  \hat{K}(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
                                                + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
@@
  \label{def_k}
-  \hat{L}(\bri{1},\bri{2},\bri{3}) ) = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
+  \hat{L}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
                                      + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
@@
 
-\subsection{Analytical form for the operators $\hat{K}(\bri{1},\bri{2}) $ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ }
-To compute the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
+\subsection{Analytical form for the operators $\hat{K}_\mu(\bri{1},\bri{2}) $ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ }
+To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
 \begin{equation}
@@
  \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
- \end{aligned}
-\end{equation}
-Then, the term $\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2$ is simply 
-\begin{equation}
- \begin{aligned}
- \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_2 u(\bri{1},\bri{2}) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
- \end{aligned}
-\end{equation}
-The non hermitian operators in $\hat{K}(\bri{1},\bri{2})$ contains 
-\begin{equation}
- \begin{aligned}
- \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
+ \nabla_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
+ \end{aligned}
+\end{equation}
+Then, the term $\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2$ is simply 
+\begin{equation}
+ \begin{aligned}
+ \big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
+ \end{aligned}
+\end{equation}
+The non hermitian operators in $\hat{K}_\mu(\bri{1},\bri{2})$ contains 
+\begin{equation}
+ \begin{aligned}
+ \nabla_1 u(r_{12},\mu) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
                                           &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg),
@@
 \end{equation}
-and as $\nabla_1 u(\br{}_1,\br{}_2) = - \nabla_2 u(\br{}_1,\br{}_2)$,   
-the total non hermitian operator in $\hat{K}(\bri{1},\bri{2})$ can be written as 
+and as $\nabla_1 u(r_{12},\mu) = - \nabla_2 u(r_{12},\mu)$,   
+the total non hermitian operator in $\hat{K}_\mu(\bri{1},\bri{2})$ can be written as 
 \begin{equation}
@@
  \label{def_non_hermit}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
 & \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
@@
  \label{eq:nabla_i_nabla0}
-& \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
+& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
  \end{aligned}
@@
 \begin{equation}
- \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{},
-\end{equation}
-and therefore 
+ \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{}.
+\end{equation}
+Therefore 
 \begin{equation}
@@
  \label{eq:nabla_i_nabla1}
- \nabla_1 u(\br{}_1,\br{}_2) \cdot \nabla_1 + \nabla_2 u(\br{}_1,\br{}_2) \cdot \nabla_2 = \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
+ \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
  \end{aligned}
@@
 
-The computation of the Laplacian is a little more tedious, but after some derivations it comes  
+The computation of the Laplacian reads 
 \begin{equation}
@@
  \label{eq:d2_x1_2}
- &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2})
+ &\nabla_1^2 u(r_{12},\mu) + \nabla_2^2u(r_{12},\mu)
  & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
@@
 
-Summing all terms to recombine $\hat{K}(\bri{1},\bri{2})$ reads 
+Summing all terms to recombine $\hat{K}_\mu(\bri{1},\bri{2})$ reads 
 \begin{equation}
@@
   \begin{aligned}
-   \hat{K}(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
+   \hat{K}_\mu(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
 & - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
@@
 \end{equation}
-Similarly, the computation of $\hat{L}(\bri{1},\bri{2},\bri{3}) $ 
+Similarly, the explicit analytical form of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
 \begin{equation}
@@
 \subsection{Analytical form of $\tilde{H}[\mu]$}
-Having established the explicit form of $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
+Having established the explicit form of $\hat{K}\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
 look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $u(r_{12};\mu)$,  
-which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, which gives
+which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, gives
 \begin{equation}
@@
 \ref{fig_wee_frogg} where $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are represented, while the latter is perfectly smooth for all $r_{12}$, the former strongly oscillates near $r_{12}=0$ between positive and negative values and is not bounded for $r_{12}=0$.
-Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that $f_{\text{TN}}(r_{12})$ is cusp-less as it is made of gaussian functions, \textit{i.e.} 
+Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that,
+as it is made of gaussian functions, $f_{\text{TN}}(r_{12})$ is cusp-less \textit{i.e.} 
 \begin{equation}
@@
 \end{equation}
-and as a necessary condition of the to obtain a non divergent scalar potential is 
+and as a necessary condition to obtain a non divergent scalar potential is 
 \begin{equation}
@@
 
-Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ almost identical \textit{in average}, as they numerically agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
+Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are almost identical \textit{in average}, as they numerically agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
+This statement will be supported by numerical computations in the next sections.
 
@@
 
-\subsection{Variation of $\tilde{H}[\mu]$ with $\mu$}
+\subsection{Limit cases for $\tilde{H}[\mu]$ with $\mu$}
 \label{sec:h_mu_lim}
@@
 
-At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent, and can be repulsive or attractive at small $r_{12}$.
+%At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent, and can be repulsive or attractive at small $r_{12}$.
 One can therefore notice the diversity of physical content of $\tilde{H}[\mu]$ as a function of a unique parameter, $\mu$.
-Nevertheless, due to the property of the similarity transformation, in the limit of a complete basis set, the eigenvalues of $\tilde{H}[\mu]$, whatever the value of $\mu$ chosen, coincide with that of the physical Hamiltonian.
+%Nevertheless, due to the property of the similarity transformation, in the limit of a complete basis set, the eigenvalues of $\tilde{H}[\mu]$, whatever the value of $\mu$ chosen, coincide with that of the physical Hamiltonian.
 An important point then is the convergence with respect to the basis set of the family of $\tilde{H}[\mu]$ for different values of $\mu$, which is tested for wide variety of two-electron systems in the next sections.
@@
 \label{sec:total_he}
-The first part of our study concerns the convergence of the eigenvalues of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
+The first part of our numerical study study concerns the convergence of the eigenvalues of $\tilde{H}[\mu]$ with respect to the basis set, and more precisely the dependence on $\mu$ of such convergence.
 
@@
 
-%As pointed in section \ref{sec:h_mu_lim}, by varying $\mu$ one can go from a relatively usual repulsive Hamiltonian at large $\mu$ (even though it is non hermitian an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
-%As pointed in section \ref{sec:h_mu_lim}, even though $\tilde{H}[\mu]$ is still non hermitian as long as $\mu < \infty$, by varying $\mu$ one can change the nature of the electron-electron interaction in $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ from a repulsive and non divergent interaction at large $\mu$ (an non divergent), passing by an almost attractive Hamiltonian and even to a purely attractive Hamiltonian.
-%Considering such variation of $\tilde{H}[\mu]$ when varying $\mu$,  
-%its projection into a basis set $\tilde{H}[\mu]^{\basis}$ will behave differently as a function of $\mu$ 
-%and so will the right eigenvectors $\ket{\phiimub}$ and the corresponding eigenvalues $E_i^{\basis}[\mu]$. 
-%Therefore, we would like to study the behaviour of $\ket{\phiimub}$ and $E_i^{\basis}[\mu]$ as a function of both $\basis$ and $\mu$ to see whether the use of the new form of Jastrow factor $u(r_{12},\mu)$ can improve the convergence toward the exact energies  and eigenvectors.
 \subsection{$\mu$ dependence of the convergence of the ground state eigenvalue with respect to the basis set }
 \subsubsection{Computational details}
-We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual Gaussian orbital basis set (see appendix for more details) together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
+We implemented all integrals needed for the computation of the matrix elements of $\tilde{H}[\mu]$ on a usual Gaussian orbital basis set (see Appendix \ref{sec:integrals} for more details) together with the modification of the Slater rules due to the presence of the non hermitian term in $\tilde{H}[\mu]$.
 We also implemented all necessary integrals to use the FROGG derived by Ten-No in Ref.
@@
 \label{sec:total_e}
-We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_i^{\basis}[\mu]$ of $\tilde{H}[\mu]^{\basis}$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
+We report in Table \ref{table_conv_e_mu} the ground state eigenvalue $E_0^{\basis}[\mu]$ of $\tilde{H}[\mu]^{\basis}$ in the AVXZ basis sets (X=D,T,Q,5) for different values of $\mu$, and we report in Figure \ref{fig_conv_e_mu} the graphical representation of such data.
 We also report in the tables and figures the results obtained with the FROGG.
 Several observations can be done from these data.
-First, because of the loose of the variational principle, $E_0^{\mu}$ can take values below the exact non relativistic energy, and the smaller the $\mu$, the more pronounced is such effect.
+First, because of the loose of the variational principle, $E_0^{\basis}[\mu]$ can take values below the exact non relativistic energy, and the smaller the $\mu$, the more pronounced is such effect.
 Nevertheless, one can also observe that, for each $\mu$, the error with respect to the exact energy gets smaller  
@@
 \label{sec:he_real_space}
-In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_0^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=3.0$.
+In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_0^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
@@
 iii) the wave function $\phimub(\br{}_1,\br{}_2)$ is always larger that the FCI one when $r_{12}\approx 0$. 
-iv) that $\psimub(\br{}_1,\br{}_2)$ provides a remarkably good approximation to $\psiex(\br{}_1,\br{}_2)$ from the AVTZ basis set,
+iv) that $\psimub(\br{}_1,\br{}_2)$ provides a remarkably good approximation to $\psiex(\br{}_1,\br{}_2)$ from the AVTZ basis set.
 
@@
 \subsection{Computation of $\hat{K}(\bri{1},\bri{2})$} 
+\label{sec:integrals}
 The only integrals involved of $\hat{K}(\bri{1},\bri{2})$ over Gaussian functions which are not analytical are of the types 

### 2020-12-19 cusp_j/paper/paper.tex
modified stuffs

@@
 These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance ($r_{12}\approx 0$): the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
-As shown by the seminal works of Hylleraas \cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
+For a general and clear derivation of the cusp conditions for Coulombic systems up to second order, see Ref.\onlinecite{Tew-JCP-08}.
+As shown by the seminal works of Hylleraas\cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
 As the cusp conditions originate from the divergence of the Coulomb potential at $r_{12}=0$, an alternative approach would be to develop theories dealing with a smooth potential.
@@
  \label{mu_ten_no_1}
-u(r_{12}=0;\mfrogg) = f_{\text{TN}}(r_{12}=0), 
-\end{equation}
-where $ f_{\text{TN}}(x)$ is the FROGG introduced by Ten-No
+u(r_{12}=0;\mfrogg) = u^{\text{TN}}(r_{12}=0), 
+\end{equation}
+where $ u^{\text{TN}}(x)$ is the FROGG introduced by Ten-No
 \begin{equation}
  \label{eq_frogg}
- f_{\text{TN}}(x) = -\sum_{i=1}^6 c_i e^{-\alpha_i x^2 },
+ u^{\text{TN}}(x) = -\sum_{i=1}^6 c_i e^{-\alpha_i x^2 },
 \end{equation}
@@
  \label{mu_ten_no_2}
- \mfrogg = -\frac{1}{2\sqrt{\pi}f_{\text{TN}}(0)},
+ \mfrogg = -\frac{1}{2\sqrt{\pi}u^{\text{TN}}(0)},
 \end{equation}
@@
 \label{sec:ht_general}
-\subsubsection{General form of $\tilde{H}[\mu]$ }
+\subsubsection{General analytical form of $\tilde{H}[\mu]$ for a $N$-electron system}
 Having established the analytical expression of $u(r_{12};\mu)$, one can derive the expression of the associated transcorrelated Hamiltonian for a general $N$-electron system.  
-According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
-\begin{equation}
+Using the general form of the transcorrelated Hamiltonian of Eq. (2) in Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19} and using $u(r_{12},\mu)$ as Jastrow factor gives 
+\begin{equation}
+ \begin{aligned}
  \label{ht_def_g}
- e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
-\end{equation}
-where $\hat{\tau} = \sum_{i<j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
-This leads to the following similarity transformed Hamiltonian 
+ \tilde{H}[\mu] &\equiv e^{-\hat{\tau}_\mu} \hat{H} e^{\hat{\tau}_\mu} \\ 
+                &= H + \big[ H,\hat{\tau}_\mu \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}_\mu\big],\hat{\tau}_\mu\bigg],
+ \end{aligned}
+\end{equation}
+with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
+Eq. \eqref{ht_def_g} leads to the following transcorrelated Hamiltonian 
 \begin{equation}
@@
  \label{ht_def_gu}
- \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)^2  \bigg) \\
-           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k}),
- \end{aligned}
-\end{equation}
-where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{j})$ and $\hat{L}(\bri{i},\bri{j},\bri{k})$ are defined as
+ \tilde{H}[\mu] & = H - \sum_{i<j} \hat{K}_\mu(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}_\mu(\bri{i},\bri{j},\bri{k}),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ are defined as
 \begin{equation}
@@
  \label{def_k}
-  \hat{K}(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
-                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
-                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1,
+  \hat{K}_\mu(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu) \\
+                                               + &\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_1 u(r_{12},\mu) \big) ^2 \bigg) \\
+                                               + &\nabla_1 u(r_{12},\mu) \cdot \nabla_2 + \nabla_2 u(r_{12},\mu)\cdot \nabla_1,
  \end{aligned}
@@
  \label{def_k}
-  \hat{L}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
-                                     + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
- \end{aligned}
-\end{equation}
-Therefore, to obtain the analytical expression of the $\tilde{H}[\mu]$ for a general $N$-electron system, 
-one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = u(r_{12},\mu)$.
-
-\subsection{Analytical form for the operators $\hat{K}_\mu(\bri{1},\bri{2}) $ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ }
-To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
-\begin{equation}
- \label{eq:nabla_u}
- \begin{aligned}
- \nabla_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
- \end{aligned}
-\end{equation}
-Then, the term $\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2$ is simply 
-\begin{equation}
- \begin{aligned}
- \big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
- \end{aligned}
-\end{equation}
-The non hermitian operators in $\hat{K}_\mu(\bri{1},\bri{2})$ contains 
-\begin{equation}
- \begin{aligned}
- \nabla_1 u(r_{12},\mu) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
-                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg),
- \end{aligned}
-\end{equation}
-and as $\nabla_1 u(r_{12},\mu) = - \nabla_2 u(r_{12},\mu)$,   
-the total non hermitian operator in $\hat{K}_\mu(\bri{1},\bri{2})$ can be written as 
-\begin{equation}
- \begin{aligned}
- \label{def_non_hermit}
-& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
-& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
-         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big)  \\
-&  +      (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg).
- \end{aligned}
-\end{equation}
-One can notice that the form of Eq. \eqref{def_non_hermit} provides an explicit form to compute analytical integrals with Gaussian types functions. 
-Nevertheless, one can notice that as 
-\begin{equation}
- \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
-\end{equation}
-one can write 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla0}
-& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
- \end{aligned}
-\end{equation}
-Then, introducing the spherical coordinate system for $\br{}_1 - \br{}_2$ in terms of ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$ and the angle $\theta$ and $\phi$, one can write 
-\begin{equation}
- \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
-\end{equation}
-and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
-\begin{equation}
- \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{}.
-\end{equation}
-Therefore 
-\begin{equation}
- \begin{aligned}
- \label{eq:nabla_i_nabla1}
- \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
- \end{aligned}
-\end{equation}
-which is a more compact expression than Eq.\eqref{def_non_hermit}
-
-The computation of the Laplacian reads 
-\begin{equation}
- \begin{aligned}
- \label{eq:d2_x1_2}
- &\nabla_1^2 u(r_{12},\mu) + \nabla_2^2u(r_{12},\mu)
- & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
- \end{aligned}
-\end{equation}
-
-Summing all terms to recombine $\hat{K}_\mu(\bri{1},\bri{2})$ reads 
+  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 u(r_{12},\mu)  \\
+                                     + & \nabla_3 u(r_{12},\mu) \cdot \nabla_3 u(r_{12},\mu).
+ \end{aligned}
+\end{equation}
+
+As shown in the Appendix \ref{k_l_appendix}, the operator $\hat{K}_\mu(\bri{1},\bri{2})$ has a straightforward analytical expression which reads 
 \begin{equation}
@@
 \end{equation}
-Similarly, the explicit analytical form of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
+and similarly that of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
 \begin{equation}
@@
 
-\subsection{Analytical form of $\tilde{H}[\mu]$}
-Having established the explicit form of $\hat{K}\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$, one can now 
-look at the explicit analytical form of the transcorrelated Hamiltonian $\tilde{H}[\mu]$ obtained with $u(r_{12};\mu)$,  
-which, by injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, gives
+By injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, one obtains 
 \begin{equation}
@@
 
-As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the FROGG which is given by
+\subsubsection{A special case of $\tilde{H}[\mu]$ which mimics the FROGG}
+As the Jastrow factor $u(r_{12},\mu)$ for $\mu=\mfrogg$ is very close to the FROGG, we can also compare the scalar effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ with that obtained with the transcorrelated Hamiltonian obtained with the FROGG.
+The latter is simply defined as 
+\begin{equation}
+ \label{eq:tn_htilde}
+ \tilde{H}_{\text{TN}} = e^{-\hat{\tau}_{\text{TN}}}H e^{\hat{\tau}_{\text{TN}}},
+\end{equation}
+with $\hat{\tau}_{\text{TN}} = \sum_{i<j} u^\text{TN}(r_{ij})$. 
+This leads to the following transcorrelated Hamiltonian 
+\begin{equation}
+ \label{eq:tn_htilde_2}
+  \tilde{H}_{\text{TN}} = H + \sum_{i<j} \bigg( \tilde{\mathcal{W}}^\text{TN}_{ee}(r_{ij}) + \tilde{t}^\text{TN} \bigg) - \sum_{i<j<k} \hat{L}^\text{TN}(\bri{1},\bri{2},\bri{3})
+\end{equation}
+where 
 \begin{equation}
  \label{eq:_wee_frogg}
- \tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})= \frac{1}{r_{12}}-\nabla_1^2 f_{\text{TN}}(r_{12}) - \big(\nabla_1 f_{\text{TN}}(r_{12}) \big) ^2. 
+ \tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})= \frac{1}{r_{12}}-\Delta_1 u^{\text{TN}}(r_{12}) - \big(\nabla_1 u^{\text{TN}}(r_{12}) \big) ^2, 
+\end{equation}
+\begin{equation}
+ \begin{aligned}
+ \tilde{t}^\text{TN} = &\nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_2 + \nabla_2 u^\text{TN}(r_{12})\cdot \nabla_1,
+ \end{aligned}
+\end{equation}
+\begin{equation}
+ \begin{aligned}
+ \label{def_k}
+  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) + \nabla_2 u^\text{TN}(r_{12}) \cdot \nabla_2 u^\text{TN}(r_{12})  \\
+                                     + & \nabla_3 u^\text{TN}(r_{12}) \cdot \nabla_3 u^\text{TN}(r_{12}).
+ \end{aligned}
 \end{equation}
@@
 Such behaviour of $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ near $r_{12}=0$ comes from the fact that,
-as it is made of gaussian functions, $f_{\text{TN}}(r_{12})$ is cusp-less \textit{i.e.} 
-\begin{equation}
- \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}f_{\text{TN}}(r_{12}) = 0, 
+as it is made of gaussian functions, $u^{\text{TN}}(r_{12})$ is cusp-less \textit{i.e.} 
+\begin{equation}
+ \lim_{r_{12}\rightarrow 0} \deriv{}{r_{12}}{}u^{\text{TN}}(r_{12}) = 0, 
 \end{equation}
@@
 
-\subsection{Limit cases for $\tilde{H}[\mu]$ with $\mu$}
+\subsubsection{Limit cases for $\tilde{H}[\mu]$ with $\mu$}
 \label{sec:h_mu_lim}
@@
 Also, it is striking to see that, in a given basis set, the ground state eigenvalue of the TC Hamiltonian obtained by the FROGG and that obtained by $\tilde{H}[\mu]$ with $\mu=\mfrogg$ coincide with less than 1 mH.
-The latter results confirms that as $u(r_{12},\mfrogg) \approx f_{\text{TN}}(r_{12})$ (see Fig \ref{fig_j_mu} and Eqs.
+The latter results confirms that as $u(r_{12},\mfrogg) \approx u^{\text{TN}}(r_{12})$ (see Fig \ref{fig_j_mu} and Eqs.
 \eqref{mu_ten_no_1} and \eqref{mu_ten_no_2}), the TC Hamiltonians obtained with the two Jastrow factor are very similar, as illustrated for instance by the effective potential in Fig.
@@
         \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$. 
-We also compare with the results of the TC obtained with the $u(r_{12}) = f_{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg}), referred here after as FROGG. }
+We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg}), referred here after as FROGG. }
 \end{figure*}
@@
 \caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.
-We also compare with the results of the TC obtained with the $u(r_{12}) = f_{\text{TN}}(r_{12})$ (see Eq.
+We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq.
 \eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.86975$ is defined in Eq.
@@
 \section{Appendix}
+\subsection{Analytical form for the operators $\hat{K}_\mu(\bri{1},\bri{2}) $ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ }
+\label{k_l_appendix}
+To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
+\begin{equation}
+ \label{eq:nabla_u}
+ \begin{aligned}
+ \nabla_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \big( \br{}_1 - \br{}_2 \big).
+ \end{aligned}
+\end{equation}
+Then, the term $\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2$ is simply 
+\begin{equation}
+ \begin{aligned}
+ \big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_2 u(r_{12},\mu) \big) ^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{2}.
+ \end{aligned}
+\end{equation}
+The non hermitian operators in $\hat{K}_\mu(\bri{1},\bri{2})$ contains 
+\begin{equation}
+ \begin{aligned}
+ \nabla_1 u(r_{12},\mu) \cdot \nabla_1  = &\frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\ 
+                                          &\bigg( (x_1 - x_2) \deriv{}{x_1}{} + (y_1 - y_2) \deriv{}{y_1}{} + (z_1 - z_2) \deriv{}{z_1}{}\bigg),
+ \end{aligned}
+\end{equation}
+and as $\nabla_1 u(r_{12},\mu) = - \nabla_2 u(r_{12},\mu)$,   
+the total non hermitian operator in $\hat{K}_\mu(\bri{1},\bri{2})$ can be written as 
+\begin{equation}
+ \begin{aligned}
+ \label{def_non_hermit}
+& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \\
+& \bigg( (x_1 - x_2) \big( \deriv{}{x_1}{} - \deriv{}{x_2}{} \big) +
+         (y_1 - y_2) \big( \deriv{}{y_1}{} - \deriv{}{y_2}{} \big)  \\
+&  +      (z_1 - z_2) \big( \deriv{}{z_1}{} - \deriv{}{z_2}{} \big)\bigg).
+ \end{aligned}
+\end{equation}
+One can notice that the form of Eq. \eqref{def_non_hermit} provides an explicit form to compute analytical integrals with Gaussian types functions. 
+Nevertheless, one can notice that as 
+\begin{equation}
+ \deriv{}{r_{12}^x}{} = \frac{1}{2} \bigg( \deriv{}{x_1}{} - \deriv{}{x_2}{} \bigg),
+\end{equation}
+one can write 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla0}
+& \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}}.
+ \end{aligned}
+\end{equation}
+Then, introducing the spherical coordinate system for $\br{}_1 - \br{}_2$ in terms of ${\bf e}_u= \frac{\br{}_1 - \br{}_2}{r_{12}}$ and the angle $\theta$ and $\phi$, one can write 
+\begin{equation}
+ \nabla_{\br{}_{12}} = \deriv{}{r_{12}}{} {\bf e}_u + \frac{1}{r_{12}} \deriv{}{\theta}{} {\bf e}_{\theta} + \frac{1}{r_{12} \sin(\theta)} \deriv{}{\phi}{} {\bf e}_\phi,
+\end{equation}
+and as $\br{}_1 - \br{}_2 = r_{12} {\bf e}_u$ one obtains
+\begin{equation}
+ \big( \br{}_1 - \br{}_2 \big) \cdot \nabla_{\br{}_{12}} = r_{12} \deriv{}{r_{12}}{}.
+\end{equation}
+Therefore 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:nabla_i_nabla1}
+ \nabla_1 u(r_{12},\mu) \cdot \nabla_1 + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 = \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
+ \end{aligned}
+\end{equation}
+which is a more compact expression than Eq.\eqref{def_non_hermit}.
+
+The computation of the Laplacian reads 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:d2_x1_2}
+ &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu)
+ & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
+ \end{aligned}
+\end{equation}
+
 \subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians and related cusp conditions}
@@
 The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill. 
-It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system .
+It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system.
 For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are valid for any bounded eigenvectors.
@@
 \end{equation}
-For an excellent pedagogical and general derivation of the cusp conditions, see Ref.\onlinecite{Tew-JCP-08}.
 
@@
 For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
-the constraint of fulfilling the cusp condition.
+the constraint of fulfilling the cusp condition, and produces a non diverging effective potential for the TC Hamiltonian.
 
@@
 \begin{equation}
- \delta(x) = \lim_{\mu} \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu x \big)^2}, 
+ \delta(x) = \lim_{\mu \rightarrow \infty} \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu x \big)^2}, 
 \end{equation}
@@
 \begin{equation}
- g(x, \mu)= \text{erf}(x \mu) - 1.
+ g(x, \mu)= \text{erf}( \mu x) - 1.
 \end{equation}
@@
 and $\alpha=1.09529$ and $\beta = 0.756023$. 
-Then, by posing $y=\mu x$, $x=y/\mu$ one obtains 
+Then, by posing $y=\mu x$, one obtains 
 \begin{equation}
@@
 \end{equation}
+All numerical tests performed for $\mu > 0.1$ show that this fit is highly accurate.
 
@@
 \begin{equation}
- w_\mu(\bri{13}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
+ w_\mu(\bri{12}) = \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}}.
 \end{equation}
@@
  & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
- &\bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
+ &\qquad \qquad \qquad   \bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
  \end{aligned}

### 2020-12-19 cusp_j/paper/paper.tex
modified stuffs

@@
  \label{def_k}
-  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{12},\mu) \cdot \nabla_2 u(r_{12},\mu)  \\
-                                     + & \nabla_3 u(r_{12},\mu) \cdot \nabla_3 u(r_{12},\mu).
+  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
+                                     + & \nabla_3 u(r_{13},\mu) \cdot \nabla_3 u(r_{32},\mu).
  \end{aligned}
@@
    \hat{K}_\mu(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
-& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
-  \end{aligned}
-\end{equation}
-and similarly that of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
+& - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
+  \end{aligned}
+\end{equation}
+and similarly the analytical expression of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
 \begin{equation}
@@
  \label{def_k}
-  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) + \nabla_2 u^\text{TN}(r_{12}) \cdot \nabla_2 u^\text{TN}(r_{12})  \\
-                                     + & \nabla_3 u^\text{TN}(r_{12}) \cdot \nabla_3 u^\text{TN}(r_{12}).
+  \hat{L}^{\text{TN}}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) \\ 
+                                     + & \nabla_2 u^\text{TN}(r_{21}) \cdot \nabla_2 u^\text{TN}(r_{23})  \\
+                                     + & \nabla_3 u^\text{TN}(r_{31}) \cdot \nabla_3 u^\text{TN}(r_{32}).
  \end{aligned}
@@
 It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
-
-%At intermediate values of $\mu$, the scalar potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) $ is non divergent, and can be repulsive or attractive at small $r_{12}$.
-One can therefore notice the diversity of physical content of $\tilde{H}[\mu]$ as a function of a unique parameter, $\mu$.
-%Nevertheless, due to the property of the similarity transformation, in the limit of a complete basis set, the eigenvalues of $\tilde{H}[\mu]$, whatever the value of $\mu$ chosen, coincide with that of the physical Hamiltonian.
-An important point then is the convergence with respect to the basis set of the family of $\tilde{H}[\mu]$ for different values of $\mu$, which is tested for wide variety of two-electron systems in the next sections.
 
@@
 
-%iv) The fact that $\psimub(\br{}_1,\br{}_2)$ provides  such a good approximation of $\psiex(\br{}_1,\br{}_2)$ in real space can be investigate through the prism of the local energy. 
-%The local energy $E_{\text{loc}}[\psi](\br{}_1,\br{}_2)$ associated to a given wave function $\psi$ is defined as 
-%\begin{equation}
-% E_{\text{loc}}[\psi](\br{}_1,\br{}_2) = \frac{H\psi(\br{}_1,\br{}_2)}{\psi(\br{}_1,\br{}_2)},
-%\end{equation}
-%and is such that 
-%\begin{equation}
-% \int \text{d}\br{}_1\,\,\text{d}\br{}_2\,\, E_{\text{loc}}[\psi](\br{}_1,\br{}_2) \big|\psi(\br{}_1,\br{}_2)\big|^2= \matelem{\psi}{H}{\psi}.
-%\end{equation}
-%Therefore, one can 
 \begin{figure*}
@@
 \section{Appendix}
-\subsection{Analytical form for the operators $\hat{K}_\mu(\bri{1},\bri{2}) $ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ }
+\subsection{Analytical form for the operator $\hat{K}_\mu(\bri{1},\bri{2}) $}
 \label{k_l_appendix}
-To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
+To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
 \begin{equation}
@@
 
-\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians and related cusp conditions}
-\label{sec:cusp}
-Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom in Sec.
-\ref{sec:he_htilde}, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
-The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill. 
-It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system.
-For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are valid for any bounded eigenvectors.
-
-In the case of the usual Hamiltonian, the exact ground state wave function $\psiex$ must satisfy the Schroedinger equation in real space 
-\begin{equation}
- H \psiex(\br{}_1,\br{}_2) = E_0 \psiex(\br{}_1,\br{}_2)\quad \forall (\br{}_1,\br{}_2).
-\end{equation}
-When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
-\begin{equation}
- \label{eq:cusp_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
-\end{equation}
-or equivalently by multiplying Eq. \eqref{eq:cusp_0} by $r_{12}$
-\begin{equation}
- \lim_{r_{12}\rightarrow 0}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
-\end{equation}
-which translates into the famous cusp condition for antiparallel spins of Kato\cite{Kat-CPAM-57}, 
-\begin{equation}
- \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
-\end{equation}
-
-Regarding now the similarity transformed Hamiltonians, the exact ground state eigenvector must also satisfy an eigenvalue equation in real-space,
-\begin{equation}
- \label{eq:hpi0_ex}
- \tilde{H}[u] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
-\end{equation}
-Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
-which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
-\begin{equation}
- \label{eq:cusp_phi_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{u(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
-\end{equation}
-Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
-Therefore, as long as one imposes that 
-\begin{equation}
- \label{eq:cusp_phi_1}
-  \deriv{u(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
-\end{equation}
-which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
-Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
-\begin{equation}
- \label{eq:cusp_phi_2}
- \deriv{\phiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
-\end{equation}
-which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[u]$ is cuspless. 
-For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
-the constraint of fulfilling the cusp condition, and produces a non diverging effective potential for the TC Hamiltonian.
-
-Another form of effective Hamiltonians leading to cuspless eigenfunctions are those obtained from RS-DFT 
-where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively.
-The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ it gives back the usual Kohn-Sham theory.
-In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
-Applied to a two electron system and looking in regions where $r_{12}\approx 0$, the leading terms of the self-consistent Schroedinger-like equation of RS-DFT reads 
-\begin{equation}
- \label{eq:cusp_psi_mu_0}
- \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
-\end{equation}
-and 
-\begin{equation}
- \lim_{r_{12} \rightarrow 0} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{2 \mu}{\sqrt{\pi}} , 
-\end{equation}
-one obtains that 
-\begin{equation}
- \label{eq:cusp_psi_mu_1}
- \deriv{\Psi^\mu(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
-\end{equation}
-which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.
-
-Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
-
-\subsection{Large $\mu$ limit of $\tilde{H}[\mu]$}
-\label{sec:large_mu_lim}
-As mentioned in Sec. \ref{sec:h_mu_lim}, one must recover the usual physical Hamiltonian in the large $\mu$ limit. 
-Nevertheless, one can notice that 
-\begin{equation}
- \label{eq:lim_mu_3}
- \lim_{\mu \rightarrow \infty} \tilde{\mathcal{W}}_{ee}(r_{12})  = \frac{1}{r_{12}} + \delta(r_{12}) 
-\end{equation}
-with 
-\begin{equation}
- \delta(x) = \lim_{\mu \rightarrow \infty} \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu x \big)^2}, 
-\end{equation}
-being the Dirac distribution. Threfore, one could be tempted to write that 
-\begin{equation}
- \begin{aligned}
- \label{eq:lim_mu_4}
- \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = H + \delta(r_{12})  \\
-                                             & \ne H,
- \end{aligned}
-\end{equation}
-which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
-
-Nevertheless, as Eq.\eqref{eq:lim_mu_4} deals with operators, the equality must be considered in the sense of distributions.  
-Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
-\begin{equation}
- \label{eq:lim_mu_5}
- \begin{aligned}
-& \matelem{\psi}{H}{\psi} = \lim_{\mu \rightarrow \infty} \matelem{\psi}{\tilde{H}[\mu]}{\psi} \\
-& \Leftrightarrow H = \tilde{H}[\mu],
- \end{aligned}
-\end{equation}
-and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
-\begin{equation}
- \label{eq:lim_mu_6}
- \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
-\end{equation}
-To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
-\begin{equation}
- \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 
-\end{equation}
-where $\tilde{n_2}(x)$ is the function $n_2(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
-$|\br{}_1-\br{}_2| = x$. 
-As the pair density $n_2(\br{}_1,\br{}_2)$ remains finite and is integrable, the function $\tilde{n}_2(x)$ 
-cannot diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
-\begin{equation}
- \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
-\end{equation}
-which implies Eq.\eqref{eq:lim_mu_1}.
-
-\subsection{Computation of $\hat{K}(\bri{1},\bri{2})$} 
+\subsection{Computation of integrals involving $\hat{K}(\bri{1},\bri{2})$} 
 \label{sec:integrals}
@@
 
-\subsection{Computation of integrals of $\hat{L}(\bri{1},\bri{2},\bri{3})$}
+\subsection{Analytical form of $\hat{L}(\bri{1},\bri{2},\bri{3})$ and computation of related integrals }
 We need to compute the following integral 
@@
 
+\subsection{$r_{12} \rightarrow 0$ limits for different forms of Hamiltonians and related cusp conditions}
+\label{sec:cusp}
+Having established the analytical form of the transcorrelated Hamiltonian $\tilde{H}[u]$ for a general Jastrow factor $u(r_{12})$ in the case of the helium atom in Sec.
+\ref{sec:he_htilde}, one can then study the behaviour of $\tilde{H}[u]$ when $r_{12}\rightarrow 0$ and compare it to two other types of Hamiltonian: the usual physical Hamiltonian and that entering the RS-DFT framework.
+The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill. 
+It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system.
+For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are valid for any bounded eigenvectors.
+
+In the case of the usual Hamiltonian, the exact ground state wave function $\psiex$ must satisfy the Schroedinger equation in real space 
+\begin{equation}
+ H \psiex(\br{}_1,\br{}_2) = E_0 \psiex(\br{}_1,\br{}_2)\quad \forall (\br{}_1,\br{}_2).
+\end{equation}
+When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
+\begin{equation}
+ \label{eq:cusp_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
+\end{equation}
+or equivalently by multiplying Eq. \eqref{eq:cusp_0} by $r_{12}$
+\begin{equation}
+ \lim_{r_{12}\rightarrow 0}\bigg( 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2}) \bigg) = 0, 
+\end{equation}
+which translates into the famous cusp condition for antiparallel spins of Kato\cite{Kat-CPAM-57}, 
+\begin{equation}
+ \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
+\end{equation}
+
+Regarding now the similarity transformed Hamiltonians, the exact ground state eigenvector must also satisfy an eigenvalue equation in real-space,
+\begin{equation}
+ \label{eq:hpi0_ex}
+ \tilde{H}[u] \phiex(\br{}_1,\br{}_2) = E_0 \phiex(\br{}_1,\br{}_2) \quad \forall (\br{}_1,\br{}_2).
+\end{equation}
+Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
+which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
+\begin{equation}
+ \label{eq:cusp_phi_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg[ 1 - 2 \deriv{u(r_{12})}{r_{12}}{}\bigg]\bigg) \phiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty.
+\end{equation}
+Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
+Therefore, as long as one imposes that 
+\begin{equation}
+ \label{eq:cusp_phi_1}
+  \deriv{u(r_{12})}{r_{12}}{}\bigg|_{r_{12}=0} = \frac{1}{2},
+\end{equation}
+which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
+Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
+\begin{equation}
+ \label{eq:cusp_phi_2}
+ \deriv{\phiex(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
+\end{equation}
+which implies that as long as the Jastrow factor contains the cusp conditions, the eigenfunction of $\tilde{H}[u]$ is cuspless. 
+For instance, a simple Jastrow factor of the form $u(r_{12}) = \frac{1}{2} r_{12}$ releases $\phiex(\br{}_1,\br{}_2)$ from 
+the constraint of fulfilling the cusp condition, and produces a non diverging effective potential for the TC Hamiltonian.
+
+Another form of effective Hamiltonians leading to cuspless eigenfunctions are those obtained from RS-DFT 
+where the Coulomb interaction $1/r_{12}$ is split into a non-divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ and a complementary short-range interaction $\text{erfc}(\mu r_{12})/r_{12}$, where $\text{erf}(x)$ and $\text{erfc}(x)$ are the error and complementary error functions, respectively.
+The parameter which controls such a splitting is the so-called range separation parameter $\mu$:  RS-DFT reduces the usual WFT when $\mu \rightarrow \infty$, and $\mu \rightarrow 0$ it gives back the usual Kohn-Sham theory.
+In practice, RS-DFT introduces a self-consistent Schroedinger-like equation which must be fulfilled by an effective wave function  $\Psi^\mu$.
+Applied to a two electron system and looking in regions where $r_{12}\approx 0$, the leading terms of the self-consistent Schroedinger-like equation of RS-DFT reads 
+\begin{equation}
+ \label{eq:cusp_psi_mu_0}
+ \lim_{r_{12}\rightarrow 0}\bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{\text{erf}(\mu r_{12})}{r_{12}}\bigg) \Psi^\mu(\bd{r_1},\bd{r_2})  = c,\quad c<\infty,  
+\end{equation}
+and 
+\begin{equation}
+ \lim_{r_{12} \rightarrow 0} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{2 \mu}{\sqrt{\pi}} , 
+\end{equation}
+one obtains that 
+\begin{equation}
+ \label{eq:cusp_psi_mu_1}
+ \deriv{\Psi^\mu(\bd{r_1},\bd{r_2})}{r_{12}}{}\Bigr|_{r_{12}=0} = 0, 
+\end{equation}
+which means that the wave functions $\Psi^\mu$, just as $\phiex$ are cuspless, because they deal with an effective non-divergent interaction.
+
+Therefore, one can see that there is a similarity between the eigenvectors of RS-DFT and of the transcorrelated Hamiltonian: they are both cuspless as they originate from non divergent Hamiltonians.
+
+\subsection{Large $\mu$ limit of $\tilde{H}[\mu]$}
+\label{sec:large_mu_lim}
+As mentioned in Sec. \ref{sec:h_mu_lim}, one must recover the usual physical Hamiltonian in the large $\mu$ limit. 
+Nevertheless, one can notice that 
+\begin{equation}
+ \label{eq:lim_mu_3}
+ \lim_{\mu \rightarrow \infty} \tilde{\mathcal{W}}_{ee}(r_{12})  = \frac{1}{r_{12}} + \delta(r_{12}) 
+\end{equation}
+with 
+\begin{equation}
+ \delta(x) = \lim_{\mu \rightarrow \infty} \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu x \big)^2}, 
+\end{equation}
+being the Dirac distribution. Threfore, one could be tempted to write that 
+\begin{equation}
+ \begin{aligned}
+ \label{eq:lim_mu_4}
+ \lim_{\mu \rightarrow \infty} \tilde{H}[\mu]& = H + \delta(r_{12})  \\
+                                             & \ne H,
+ \end{aligned}
+\end{equation}
+which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
+
+Nevertheless, as Eq.\eqref{eq:lim_mu_4} deals with operators, the equality must be considered in the sense of distributions.  
+Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
+\begin{equation}
+ \label{eq:lim_mu_5}
+ \begin{aligned}
+& \matelem{\psi}{H}{\psi} = \lim_{\mu \rightarrow \infty} \matelem{\psi}{\tilde{H}[\mu]}{\psi} \\
+& \Leftrightarrow H = \tilde{H}[\mu],
+ \end{aligned}
+\end{equation}
+and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
+\begin{equation}
+ \label{eq:lim_mu_6}
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = 0.
+\end{equation}
+To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
+\begin{equation}
+ \int \text{d}\br{}_1 \text{d}\br{}_2 n_2(\br{}_1,\br{}_2) \delta(r_{12}) = \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 
+\end{equation}
+where $\tilde{n_2}(x)$ is the function $n_2(\br{}_1,\br{}_2)$ integrated over $(\br{}_1,\br{}_2)$ with the constraint that 
+$|\br{}_1-\br{}_2| = x$. 
+As the pair density $n_2(\br{}_1,\br{}_2)$ remains finite and is integrable, the function $\tilde{n}_2(x)$ 
+cannot diverge faster than $\frac{1}{x}$ when $x\rightarrow 0$ and therefore one obtains that 
+\begin{equation}
+ \int \text{d}r{}_{12}  \tilde{n}_2(r_{12}) \delta(r_{12}) r_{12}^2 = 0,
+\end{equation}
+which implies Eq.\eqref{eq:lim_mu_1}.
+
 \bibliography{srDFT_SC}

### 2020-12-20 cusp_j/paper/paper.tex
modified stuffs

@@
 The present work introduces a new form of explicitly correlated factor in the context of the transcorrelated methods. 
-The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces at leading order in $1/r_{12}$ the long-range interaction of the range-separated density functional theory.
+The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces the long-range interaction of the range-separated density functional theory at leading order in $1/r_{12}$.
 The resulting correlation factor is then tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
-The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression and its physical contents depends on the same parameter $\mu$: one can continuously change from a non divergent repulsive Hamiltonian potential at large $\mu$ to a purely attractive one at small $\mu$.
+The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression  depending on the same parameter $\mu$, and its physical contents continuously change by varying $\mu$ : one can change from a non divergent repulsive Hamiltonian at large $\mu$ to a purely attractive one at small $\mu$.
 We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems.
@@
 \label{sec:he_htilde}
-Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates  
+Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates\cite{Hylleraas-AdvQChem-64}  
 \begin{equation}
@@
 \eqref{eq:cusp_psi_mu_0} in Appendix \ref{sec:cusp}).
-Mathematically, this conditions implies that 
+Mathematically, this condition implies that 
 \begin{equation}
@@
 which defines the new Jastrow factor $u(r_{12};\mu)$ which depends on a unique parameter $\mu$.
-The associated transcorrelated Hamiltonians obtained with $u(r_{12};\mu)$ is also controlled by $\mu$
-\begin{equation}
- \label{eq:def_ht_mu}
- \tilde{H}[\mu] = e^{-u(r_{12};\mu)} H e^{u(r_{12};\mu)}. 
-\end{equation}
-Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
-\begin{equation}
- \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
-\end{equation}
-where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian.
-The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation.
-Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.
 
@@
 \subsubsection{General analytical form of $\tilde{H}[\mu]$ for a $N$-electron system}
+
 Having established the analytical expression of $u(r_{12};\mu)$, one can derive the expression of the associated transcorrelated Hamiltonian for a general $N$-electron system.  
@@
 with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
+Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
+\begin{equation}
+ \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
+\end{equation}
+where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian.
+The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation.
+Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.
+
 Eq. \eqref{ht_def_g} leads to the following transcorrelated Hamiltonian 
@@
 
+\subsubsection{Limit cases for $\tilde{H}[\mu]$ with $\mu$}
+\label{sec:h_mu_lim}
+Regarding now the variation of $\tilde{H}[\mu]$, as 
+\begin{equation}
+ \label{eq:lim_mu_0}
+ \lim_{\mu  \rightarrow \infty }u(\mu,r_{12}) = 0, 
+\end{equation}
+one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit:
+\begin{equation}
+ \label{eq:lim_mu_1}
+ \lim_{\mu \rightarrow \infty} \tilde{H}[\mu] = H,
+\end{equation}
+although it is only in the sense of distributions (see Appendix \ref{sec:large_mu_lim} for a more detailed explanation).
+
+In the $\mu \rightarrow 0$ limit, the transcorrelated Hamiltonian $\tilde{H}[\mu]$ becomes simply 
+\begin{equation}
+ \label{eq:htilde_mu_low}
+ \begin{aligned}
+&\lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \sum_{i<j}\deriv{}{r_{ij}}{} \\
+ & - \frac{1}{4}\sum_{i<j<k}  \bigg(\frac{\bri{ij} }{ r_{ij}} \cdot \frac{\bri{ik} }{ r_{ik}} + \frac{\bri{ji} }{ r_{ji}} \cdot \frac{\bri{jk}  }{ r_{jk}} + \frac{\bri{ki} }{ r_{ki}} \cdot  \frac{\bri{kj} }{ r_{kj}} \bigg),
+ \end{aligned}
+\end{equation}
+which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and a three electron interaction. 
+It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
+
 \subsubsection{A special case of $\tilde{H}[\mu]$ which mimics the FROGG}
@@
 (see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}), $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.
-%Because the condition of Eq. \eqref{eq:cusp_phi_0} is fulfilled by $u(r_{12},\mu)$ for all $\mu < \infty$, 
-%the effective potential obtained by the similarity transformation of $H$ by $u(r_{12},\mu)$ is necessary non divergent.
 
@@
 \end{figure*}
-
-\subsubsection{Limit cases for $\tilde{H}[\mu]$ with $\mu$}
-\label{sec:h_mu_lim}
-Regarding now the variation of $\tilde{H}[\mu]$, as 
-\begin{equation}
- \label{eq:lim_mu_0}
- \lim_{\mu  \rightarrow \infty }u(\mu,r_{12}) = 0, 
-\end{equation}
-one recovers the usual Hamiltonian in the ${\mu  \rightarrow \infty }$ limit:
-\begin{equation}
- \label{eq:lim_mu_1}
- \lim_{\mu \rightarrow \infty} \tilde{H}[\mu] = H,
-\end{equation}
-although it is only in the sense of distributions (see Appendix \ref{sec:large_mu_lim} for a more detailed explanation).
-
-In the $\mu \rightarrow 0$ limit, the transcorrelated Hamiltonian $\tilde{H}[\mu]$ becomes simply 
-\begin{equation}
- \label{eq:htilde_mu_low}
- \begin{aligned}
-&\lim_{\mu \rightarrow 0} \tilde{H}[\mu] = h_c - \frac{1}{4} - \sum_{i<j}\deriv{}{r_{ij}}{} \\
- & - \frac{1}{4}\sum_{i<j<k}  \bigg(\frac{\bri{ij} }{ r_{ij}} \cdot \frac{\bri{ik} }{ r_{ik}} + \frac{\bri{ji} }{ r_{ji}} \cdot \frac{\bri{jk}  }{ r_{jk}} + \frac{\bri{ki} }{ r_{ki}} \cdot  \frac{\bri{kj} }{ r_{kj}} \bigg),
- \end{aligned}
-\end{equation}
-which means that all scalar electron-electron repulsive interaction have been replaced by a differential operator and a three electron interaction. 
-It should be stressed that even if the $\mu \rightarrow 0$ limit of $\tilde{H}[\mu]$ is very unphysical, it conserves exactly the same spectrum than the usual Hamiltonian because it originates from a similarity transformation.
 
@@
 \eqref{mu_ten_no_1}.
+The exact non relativistic energy was obtained from Ref.
+\cite{Dav-ions-PRA-91}.
  }
@@
 We also report the average value of the $\mu$ considered (referred as $\muav$) in the double-zeta basis.
-The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq. \eqref{mu_ten_1}}
+The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq.
+\eqref{mu_ten_no_1}.
+The exact non relativistic energy of all systems studied here was obtained from Ref.
+\cite{Dav-ions-PRA-91}.}
 
@@
         H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
-R$_{eq}$ refers to the equilibrium distance of 1.401 a.u..
+R$_{eq}$ refers to the equilibrium distance of 1.401 a.u., and the estimated exact non relativistic potential energy curve was taken from Ref.
+\onlinecite{LieCle-JCP-74a}.
 }

### 2020-12-22 cusp_j/paper/paper.tex
final modifs

@@
 The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces the long-range interaction of the range-separated density functional theory at leading order in $1/r_{12}$.
-The resulting correlation factor is then tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
-The transcorrelated Hamiltonian obtained with such a new correlation factor as a straightforward analytical expression  depending on the same parameter $\mu$, and its physical contents continuously change by varying $\mu$ : one can change from a non divergent repulsive Hamiltonian at large $\mu$ to a purely attractive one at small $\mu$.
+The resulting correlation factor exactly imposes the cusp and is tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
+The transcorrelated Hamiltonian obtained with such a new correlation factor has a straightforward analytical expression  depending on the same parameter $\mu$, and its physical contents continuously change by varying $\mu$ : one can change from a non divergent repulsive Hamiltonian at large $\mu$ to a purely attractive one at small $\mu$.
 We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems.
 We found that the convergence towards the complete basis set is much faster for a quite wide range values of $\mu$.
-We also propose a computationally cheap way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.
+We also propose a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.
 It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
@@
 \section{Introduction}
-One of the most challenging problem in modern computational chemistry is the accurate simulation of the electronic structure of atomic and molecular systems, which implies solving the Schroedinger equation for a general $N$-body system.
+One of the most challenging problem in computational chemistry is the accurate simulation of the electronic structure of atomic and molecular systems, which implies solving the Schroedinger equation for a general $N$-body system.
 At the heart of the complexity of such a task relies the rapidly prohibitive computational cost of the wave function methods (WFT), which is induced by the exponential growth with the system size of the Hilbert space involved in the linear eigenvalue problem to be solved.
@@
 
-Even if these selection schemes are extremely efficient to obtain a qualitative description of the wave function, a quantitative description is often out of reach as it implies the use of very large one-electron basis sets which are needed to recover the slowly converging correlation effects near the electron-electron coalescence point.
+Even if these schemes are extremely efficient to obtain a qualitative description of the wave function through a meaningful selection in an exponentially growing Hilbert space, a quantitative description is often out of reach as it implies the use of very large one-electron basis sets which are needed to recover the slowly converging correlation effects near the electron-electron coalescence point.
 These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance ($r_{12}\approx 0$): the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
@@
 It is important to notice that because of the orthogonalization between the Jastrow and the basis set, 
-the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and the usual theory in WFT.
+the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and the parent theory in WFT.
 Therefore, no strong compression of the electronic wave function is obtained within a given basis set by the F12 theory,
@@
 The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.
-Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize orbitals and Jastrow parameters for a single Slater determinant.
+Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize both orbitals and Jastrow parameters for a single Slater determinant.
 Nevertheless, such a constrained form of the wave function for the Slater together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.
@@
 The Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions and referred to as the frozen gaussian geminal (FROGG), only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
-The use of gaussian functions to represent the Jastrow factor enabled Ten-No to develop a numerical scheme to evaluate exactly the three-electron integrals present in TC Hamiltonian\cite{TenNo-CPL-00-b}, which is an alternative to the density-fitting method proposed by Ten-No in the general context of F12 methods\cite{TenMan-JCP-03}.
+The use of gaussian functions to represent the Jastrow factor enabled Ten-No to develop a numerical scheme to evaluate exactly the three-electron integrals present in TC Hamiltonian\cite{TenNo-CPL-00-b}, which is an alternative to the density-fitting method proposed by the same author in the general context of F12 methods\cite{TenMan-JCP-03}.
 In Ref.\onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
 which allows to treat the non-hermitian TC Hamiltonian in a mathematical form more suited 
-to develop many-body perturbation theory approaches. 
+to develop approaches based on many-body perturbation theory. 
 It is also noteworthy that the eigenfunctions of the TC Hamiltonian are invariant by orbital rotation, 
@@
 More recently, Alavi \textit{et.
-al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations with the use of elaborate Jastrow factors obtained from quantum Monte Carlo calculations, and explicitly taking into account for electron-electron together with electron-electron-nucleus correlation.
+al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations with the use of elaborate Jastrow factors which explicitly taking into account for electron-electron together with electron-electron-nucleus correlation.
 The Jastrow factor used in such work were obtained from the optimized Jastrow factors for He to Ne of Moskowitz \textit{et.
-al.}\cite{SchMos-JCP-90}.
+al.}\cite{SchMos-JCP-90} in the context of quantum Monte Carlo.
 In contrast to previous works where a constrained form was given to the wave function (such as coupled cluster for instance\cite{HinTanTen-CPL-02}),  Alavi \textit{et.
@@
 \end{equation}
-The only additional terms arising in $\tilde{H}[u]$ with respect to $H$ are those coming from the action of the differential operator in $r_{12}$,
+With respect to $H$, the only additional terms arising in $\tilde{H}[u]$ are those coming from the action of the differential operator in $r_{12}$,
 \begin{equation}
@@
 
-The main difference of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor in terms of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+The main difference of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor as a linear combination of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
 we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
@@
 The new Jastrow $u(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which have the unit of the inverse of a distance. 
-To understand the physical content together with the mathematical properties of $u(r_{12};\mu)$, 
-one must keep in mind that the complete correlating factor $\mathcal{J}(r_{12};\mu)$ is 
-\begin{equation}
- \mathcal{J}(r_{12};\mu) = \text{exp}\big(u(r_{12};\mu)\big),
-\end{equation}
-and that the exact wave function $\psiex(\br{}_1,\br{}_2)$ is formally expressed as 
-\begin{equation}
- \psiex(\br{}_1,\br{}_2) = \mathcal{J}(r_{12};\mu) \phimu(\br{}_{1},\br{}_{2}).  
-\end{equation}
 From Eq.\eqref{eq:def_j} we can notice that 
@@
 \begin{equation}
- \lim_{r_{12} \rightarrow \infty}\mathcal{J}(r_{12};\mu) = 1,
+ \lim_{r_{12} \rightarrow \infty}e^{u(r_{12};\mu)} = 1,
 \end{equation}
@@
 \end{equation}
-implying that the right-eigenvector $\phimu(\br{}_{1},\br{}_{2})$ is cusp less (see Appendix \ref{sec:cusp}). 
-The Taylor expansion of Eq. \eqref{eq:j_dl} inserted in $\mathcal{J}(r_{12},\mu)$ leads to 
+implying that the right-eigenvectors of the TC Hamiltonian obtained with $u(r_{12};\mu)$ are cusp less (see Appendix \ref{sec:cusp}). 
+The Taylor expansion of Eq. \eqref{eq:j_dl} inserted in the exponential correlating Jastrow factor reads 
 \begin{equation}
  \label{eq:bigJ_dl}
- \mathcal{J}(r_{12};\mu) \approx e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}. 
-\end{equation}
-From Eq.
-\eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, the effective wave function  $\phiex(\br{}_1,\br{}_2)$ has necessary a larger value at coalescence (\textit{i.e.} $\br{}_1=\br{}_2)$),
-b) the term in $e^{ \frac{1}{2}r_{12}} $ restores exactly the lack of cusp of $\phiex(\br{}_1,\br{}_2)$ (see Eq.
-\eqref{eq:cusp_phi_2}); and eventually last term reshapes the curvature of the $\phiex(\br{}_1,\br{}_2)$.
+ e^{u(r_{12},\mu)}\approx e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{ \frac{1}{2}r_{12}} e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}. 
+\end{equation}
+From Eq. \eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, Jastrow factor digs the Coulomb hole, 
+b) the term in $e^{ \frac{1}{2}r_{12}} $ exactly imposes the cusp; c) and the last term $e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}$ reshapes the curvature of the Coulomb hole.
 
@@
         \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_exp_j.pdf}\\
-        \caption{Shape of $u(r_{12};\mu)$ (left) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (right) for different values of $\mu$. 
+        \caption{Shape of $u(r_{12};\mu)$ (left) and of $\text{exp}\big(u(r_{12};\mu) \big) $ (right) for different values of $\mu$. 
 We also compare the FROGG (see Eq. \eqref{eq_frogg}) and the value of $\mu = 0.865$ which equals the FROGG at $r_{12}=0$ (see Eq. \eqref{mu_ten_no_1}). }
 \end{figure*}
-From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper and broader is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
+From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper and broader is the hole imposed by $e^{u(r_{12},\mu)}$.
 
@@
 \end{equation}
-with the coefficients $c_i$ and exponents $\alpha_i$ given in Table 1 of Ref. \onlinecite{TenNo-CPL-00-a}. 
+with the coefficients $c_i$ and exponents $\alpha_i$ are given in Table 1 of Ref. \onlinecite{TenNo-CPL-00-a}. 
 Eq. \eqref{mu_ten_no_1} gives 
@@
 \end{equation}
-which gives $\mfrogg\approx0.86975$. 
+which gives $\mfrogg\approx0.87$. 
 We represent on Fig \ref{fig_j_mu} the comparison between $u(r_{12};\mfrogg)$ and the FROGG, and it is clearly apparent  that $u(r_{12};\mfrogg)$ reproduces almost perfectly the FROGG, although it decays slightly faster at large $r_{12}$.
@@
 with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
-Therefore, the right- and left-eigenvectors of $\tilde{H}[\mu]$ depends only on $\mu$, and the right-eigenvectors satisfy 
-\begin{equation}
- \tilde{H}[\mu] \phimui(\br{}_{1},\br{}_{2}) = E_i \phimui(\br{}_{1},\br{}_{2}), 
+Therefore, the right-eigenvectors $\ket{\phimui}$ depends on $\mu$ and satisfy the effective Schroedinger equation
+\begin{equation}
+ \tilde{H}[\mu] \ket{ \phimui}  = E_i \ket{\phimui}, 
 \end{equation}
@@
  \label{def_k}
-  \hat{L}^{\text{TN}}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{12}) \\ 
+  \hat{L}^{\text{TN}}(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u^\text{TN}(r_{12}) \cdot \nabla_1 u^\text{TN}(r_{13}) \\ 
                                      + & \nabla_2 u^\text{TN}(r_{21}) \cdot \nabla_2 u^\text{TN}(r_{23})  \\
@@
 \end{equation}
-and as a necessary condition to obtain a non divergent scalar potential is 
+and as a necessary condition to obtain a non divergent scalar potential is (see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}) 
 \begin{equation}
@@
 \end{equation}
-(see Eqs. \eqref{eq:cusp_phi_0}  and \eqref{eq:cusp_phi_1} in Appendix \ref{sec:cusp}), $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.
+$\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ is necessary not bounded at $r_{12}=0$.
 
@@
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
-We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors.
+We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors together with the eigenvalues.
 
@@
 
-From the study of the ground state of the helium atom, one can conclude that i) the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$,
+From the study of the ground state of the helium atom, one can conclude that i) the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$,
 ii) the results obtained with $\mu=\mfrogg$ reproduce essentially that obtained with the FROGG, 
@@
 We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq.
-\eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.86975$ is defined in Eq.
+\eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.87$ is defined in Eq.
 \eqref{mu_ten_no_1}.
@@
 \begin{tabular}{llllllllllll}
- Basis/$\mu$ & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                 & $\mfrogg=0.86975$    \\
+ Basis/$\mu$ & 0.2                   & 0.3                   & 0.35                  & 0.5                  & 0.7                 & $\mfrogg=0.87$    \\
 \hline                                                                                                                                                  
@@
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
-To answer that question, we investigate some properties of the ground state eigenvectors of different types of Hamiltonians in real space.
-
-Theoretically if, for a given value of $\mu$, $\tilde{H}[\mu]^{\basis}$ is perfectly well represented in a given basis set $\mathcal{B}$ (\textit{i.e.} $\tilde{H}[\mu]^{\basis} = \tilde{H}[\mu]$), then all its eigenvalues coincide with that of the exact Hamiltonian (\textit{i.e.} developed in a complete basis set).
-If one focusses now on the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$, it is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through
+To answer that question, we investigate some properties in real space of the ground state eigenvectors of different types of Hamiltonians. 
+For the sake of simplicity we perform the study on the ground state of the helium atom.
+
+The exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$ is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through 
 \begin{equation}
@@
 \end{equation}
-Then, the quality of a given basis set $\basis$ for a given $\mu$ can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$. 
+Then, the quality of a given basis set $\basis$ to represent $\tilde{H}[\mu]$  can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$.
 To illustrate that, 
@@
 
-ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ or the FCI wave function can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
 
@@
 \label{sec:iso_elec}
-Having investigated in the case of the helium atom the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with both $\mu$ and the basis set used, we now study the ground state energies of the isoelectronic series of the helium atom H$^{-}$ to Ne$^{8+}$.
+Having investigated in the case of the helium atom the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with both $\mu$ and the basis set used, we now study the ground state energies of the isoelectronic series of the helium atom for H$^{-}$ to Ne$^{8+}$.
 As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depends on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which they converge significantly faster with the basis set with respect to the usual Hamiltonian.
@@
 
-In order to find a systematic way to determine a reasonable value of $\mu$, one must keep in mind the physical meaning of such quantity: it has the unit of an inverse distance, and determines, at leading order, the depth of the hole imposed by the Jastrow factor.
+In order to find a systematic way to determine a reasonable value of $\mu$, one must keep in mind the physical meaning of such quantity: it has the unit of the inverse of a distance, and determines, at leading order, the depth of the hole imposed by the Jastrow factor.
 Therefore, it must have the typical scale of the inverse of correlation effects, which of course strongly depends on the system through its density for instance.
@@
 We report in Table \ref{table_conv_e_mu_iso} for different basis sets the error with respect to the exact ground state energy of $E_0^{\basis}[\muuegav]$ for the isoelectronic series studied here. 
-From these data, one can see that MAD is sensibly the same than that with the $\murscav$ but with a MSD of opposite sign with respect to the latter.
+From these data, one can see that the MAD is sensibly the same than that with the $\murscav$ but with a MSD of opposite sign with respect to the latter.
 This correlates with the fact that the values of $\muuegav$ are in general larger than that of $\murscav$, except for H$^-$.
@@
 We also report the average value of the $\mu$ considered (referred as $\muav$) in the double-zeta basis.
-The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.86975$ is defined in Eq.
+The method referred as $\frogg$ is the frozen gaussian geminal introduced by Ten-No\cite{TenNo-CPL-00-a}, and the value of $\mfrogg=0.87$ is defined in Eq.
 \eqref{mu_ten_no_1}.
@@
 \section{The ground state potential energy curve H$_2$}
-Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we focus on the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$ in the last part of the present study as a test case for valence only molecular system.
+Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we apply here the new TC Hamiltonian $ \tilde{H}[\mu]$ on the study of the ground state potential curve of H$_2$.
 As in the study of the helium atom of Sec \ref{sec:total_he}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$.
@@
 \section{Conclusion}
-In the present paper, we derived a new form of Jastrow factor $u(r_{12},\mu)$ for the TC framework and performed the first numerical tests on a set of two electrons atomic and molecular systems. 
+In the present paper, we derived a new form of Jastrow factor $u(r_{12},\mu)$ for the TC framework and performed the first numerical tests on a set of two electron atomic and molecular systems. 
 In contrast to the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} which was obtained as a linear combination of Gaussians from a numerical fit, the analytical form of the new Jastrow factor proposed here has been derived from the analysis of the leading order terms in $\frac{1}{r_{12}}$ of the general TC Hamiltonian, such that it mimics the long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ used in the RS-DFT framework (see Sec.
@@
 
-The numerical investigation of the ground state of the helium atom indicates that for values of $\mu$ ranging from 0.2 to 1.0 one can strongly improve the convergence of the computed energies with respect to the basis set (see Sec.
+The numerical investigation of the ground state of the helium atom indicates that for values of $\mu$ ranging from 0.2 to 1.6 one can strongly improve the convergence of the computed energies with respect to the basis set (see Sec.
 \ref{sec:total_he}).
 An investigation of the right eigenvectors in real space for different values of $\mu$ have shown interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
+These different behaviour can be understood as the effective potential entering TC Hamiltonian becomes more and more attractive as $\mu$ lowers.
 Nevertheless, when the right eigenvectors are multiplied by the corresponding Jastrow factor, one obtains a very good approximation of the numerically exact ground state wave function (see Sec.
@@
 
-The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and tu explore the possibility of having a value of $\mu$ varying in space.
+The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and to explore the possibility of having a value of $\mu$ varying in space.
 
@@
 The analysis of the $r_{12}\rightarrow 0$ behaviour leads to the different condition that the eigenvectors of such operators must fulfill. 
-It should be noticed that, although it was established in the case of the helium atom, the leading order of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system.
+It should be noticed that, although it was established in the case of the helium atom, the leading order analysis of the $r_{12} \rightarrow 0$ limit that will be carried out in that section are valid for a general $N$ electron system.
 For the sake of simplicity of the notations we focus on the ground state of these operators but the arguments are valid for any bounded eigenvectors.

### 2021-01-04 cusp_j/paper/paper.tex
Final version

@@
 \newcommand{\phiex}[0]{\Phi^{\text{ex}}_0}
-\newcommand{\phimu}[0]{\Phi^{\text{ex},\mu}_0}
-\newcommand{\phimui}[0]{\Phi^{\text{ex},\mu}_i}
-\newcommand{\phimub}[0]{\Phi^{\mathcal{B},\mu}_0}
-\newcommand{\xhimub}[0]{X^{\mathcal{B},\mu}_0}
-\newcommand{\psimub}[0]{\Psi^{\mathcal{B},\mu}_0}
-\newcommand{\phiimub}[0]{\Phi^{\mathcal{B},\mu}_i}
+\newcommand{\phimu}[0]{\Phi^{\text{ex}}_0[\mu]}
+\newcommand{\phimui}[0]{\Phi^{\text{ex}}_i[\mu]}
+\newcommand{\phimub}[0]{\Phi^{\mathcal{B}}_0[\mu]}
+\newcommand{\xhimub}[0]{X^{\mathcal{B}}_0[\mu]}
+\newcommand{\psimub}[0]{\Psi^{\mathcal{B}}_0[\mu]}
+\newcommand{\phiimub}[0]{\Phi^{\mathcal{B}}_i[\mu]}
 \newcommand{\basis}[0]{\mathcal{B}}
@@
 \author{Emmanuel Giner}
-\email{emmanuel.giner@lct.jussieu.fr}
+\email{eginer@lct.jussieu.fr}
 
@@
 The present work introduces a new form of explicitly correlated factor in the context of the transcorrelated methods. 
-The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the scalar part of the effective two-electron potential reproduces the long-range interaction of the range-separated density functional theory at leading order in $1/r_{12}$.
+The new correlation factor is obtained from the $r_{12} \approx 0$ mathematical analysis of the transcorrelated Hamiltonian, and its analytical form is obtained such that the leading order in $1/r_{12}$ of the scalar part of the effective two-electron potential reproduces the long-range interaction of the range-separated density functional theory.
 The resulting correlation factor exactly imposes the cusp and is tuned by a unique parameter $\mu$ which controls both the depth of the coulomb hole and its typical range in $r_{12}$. 
 The transcorrelated Hamiltonian obtained with such a new correlation factor has a straightforward analytical expression  depending on the same parameter $\mu$, and its physical contents continuously change by varying $\mu$ : one can change from a non divergent repulsive Hamiltonian at large $\mu$ to a purely attractive one at small $\mu$.
-We investigate the convergence of the eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems.
+We investigate the convergence of the ground state eigenvalues and right-eigenvectors of such new transcorrelated Hamiltonian as a function of the basis set and as a function of $\mu$ on a series of two-electron systems.
 We found that the convergence towards the complete basis set is much faster for a quite wide range values of $\mu$. 
-We also propose a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density.
+We also propose a specific value of $\mu$ which essentially reproduce the results obtained with the frozen Gaussian geminal introduced by Ten-No [CPL-330,169 (2000)]. 
+We introduce a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density, and show the benefit of such approach on the isoelectronic series of the helium atom.
 It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
@@
 These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance ($r_{12}\approx 0$): the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
-For a general and clear derivation of the cusp conditions for Coulombic systems up to second order, see Ref.\onlinecite{Tew-JCP-08}.
+For a clear and general derivation of the cusp conditions up to second order for Coulombic systems, see Ref.\onlinecite{Tew-JCP-08}.
 As shown by the seminal works of Hylleraas\cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
@@
 Such a splitting is done through the function $\text{erf}(\mu r_{12})$ where $\mu$ is the range separation parameter which allows one to continually move from Kohn-Sham DFT ($\mu=0$) to pure WFT ($\mu=\infty$).
-As the effective Hamiltonian is smooth at $r_{12}=0$ for a finite value of $\mu$, the corresponding eigenfunction has no electron-electron cusp\cite{GorSav-PRA-06} and therefore the convergence of the results with respect to the basis set are exponential\cite{FraMusLupTou-JCP-15}.
+As the effective Hamiltonian obtained in RS-DFT is smooth at $r_{12}=0$ for a finite value of $\mu$, the corresponding eigenfunction has no electron-electron cusp\cite{GorSav-PRA-06} and therefore the convergence of the results with respect to the basis set are exponential\cite{FraMusLupTou-JCP-15}.
 A number of approximate RS-DFT schemes have been developed involving single-reference\cite{AngGerSavTou-PRA-05, GolWerSto-PCCP-05, TouGerJanSavAng-PRL-09,JanHenScu-JCP-09,TouZhuSavJanAng-JCP-11, MusReiAngTou-JCP-15,KalTou-JCP-18,KalMusTou-JCP-19} and multi-reference\cite{LeiStoWerSav-CPL-97, FroTouJen-JCP-07, FroCimJen-PRA-10, HedKneKieJenRei-JCP-15, HedTouJen-JCP-18, FerGinTou-JCP-18} WFT methods.
@@
 An alternative point of view using a Jastrow factor is the so-called transcorrelated (TC) approach where the full effect of the Jastrow factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the Jastrow factor.
-Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and latter on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the general form of the TC Hamiltonian for an exponential form of the Jastrow factor.
+Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity.
 The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.
@@
 
-Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a frozen universal Jastrow factor.
+Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing both the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a frozen universal Jastrow factor.
 This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}.
@@
 the biorthogonal and usual orthogonal approaches give the same results. 
-Nevertheless, as approximations are necessary done in the wave function ansatz for realistic systems, 
+Nevertheless, as approximations and truncations are necessary done in the wave function ansatz for realistic systems, 
 the biorthogonal approach might improve the quality of the results in practice.
@@
 al.}\cite{YanShi-JCP-12}  where the Jastrow factor is expressed as an anti-hermitian operator, allowing one to obtain an hermitian effective Hamiltonian after the similarity transformation, which is then efficiently truncated through the use the canonical transformation\cite{NeuYanCha-MolPhys-10}.
-Recent applications of such method to the context of quantum computing have been recently published\cite{ValTak-PCCP-20}.
+Applications of such method in the context of quantum computing have been recently published\cite{ValTak-PCCP-20}.
 
@@
 More recently, Alavi \textit{et.
-al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations with the use of elaborate Jastrow factors which explicitly taking into account for electron-electron together with electron-electron-nucleus correlation.
+al}\cite{CohLuoGutDobTewAla-JCP-19} applied the TC equations with the use of elaborate Jastrow factors which explicitly takes into account the electron-electron together with electron-electron-nucleus coordinates.
 The Jastrow factor used in such work were obtained from the optimized Jastrow factors for He to Ne of Moskowitz \textit{et.
@@
 This is done through the use of the FCI-QMC\cite{BooThoAla-JCP-09,BooAla-JCP-10,BooCleThoAla-JCP-11,GhaLozAla-JCP-19,VitAlaKat-JCTC-20} which is a projective technique allowing one to obtain the ground state of an operator, hermitian or not, through a stochastic sampling of the corresponding Hilbert space.
-Their approach share common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions,
-even though the FCIQMC is certainly more flexible than the coupled cluster ansatz of Ten-No used in Ref. \onlinecite{HinTanTen-JCP-01}.
-
-In the present work, we derive a new form of Jastrow factor and corresponding TC Hamiltonian which are inspired by the RS-DFT effective Hamiltonian.
+The use of a TC Hamiltonian in the context of FCI-QMC has an important advantage: because the TC Hamiltonian already contains the effect of an elaborate Jastrow factor, the right-eigenvectors of the TC Hamiltonian are more compact and therefore the FCI-QMC procedure converges faster.
+This approach share common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions, 
+even though the FCIQMC is certainly more flexible than the linearised coupled cluster ansatz of Ten-No used in Ref. \onlinecite{HinTanTen-JCP-01}.
+
+In the present work, we derive a new form of Jastrow factor such that the leading $1/r_{12}$ terms of the corresponding TC Hamiltonian reproduce the RS-DFT effective Hamiltonian. 
 As in RS-DFT, the new TC Hamiltonian and Jastrow factor are tuned by a unique range separation parameter $\mu$. 
 The aim of this study is to establish the analytical form of the TC Hamiltonian and perform a numerical study on the ground state eigenvalues and eigenvectors on a set of two-electron atomic and molecular systems: the helium isoelectronic series from H$^-$ to Ne$^{8+}$ and H$_2$ molecule.
-In the context of the TC theory the interesting features of the present work are that i) the analytical form of the TC Hamiltonian is explicitly known and it turns out that all two-electron integrals can be performed analytically, ii) it is tuned by a unique parameter $\mu$ and therefore allows some flexibility, iii) there always exists a regime of $\mu$ which significantly improve the basis set convergence of WFT, iv) we propose schemes to find a value of $\mu$ which automatically adapts to the system and improves basis set convergence.
+In the context of the TC theory the interesting features of the present work are that 
+i) the analytical form of the TC Hamiltonian is explicitly known and it turns out that all two-electron integrals can be performed analytically and the three-electron integrals can be efficiently computed in mixed numerical-analytical way, ii) the new Jastrow factor and corresponding TC Hamiltonian are tuned by a unique parameter $\mu$ which allows some flexibility, iii) there always exists a regime of $\mu$ which significantly improve the basis set convergence of WFT, iv) we propose schemes to find a value of $\mu$ which automatically adapts to the system and improves basis set convergence.
 
@@
 In the first section, inspired by the RS-DFT effective Hamiltonian,  
-we derive the analytical form of a new Jastrow factor tuned by a unique parameter $\mu$, and discuss the physical content of such a simple Jastrow factor. 
-We show then that the corresponding transcorrelated Hamiltonian has a straightforward analytical structure, which is briefly reviewed as a function of the $\mu$ parameter. 
-Then, we perform a numerical study of the behaviour of the ground state eigenpair of $\tilde{H}[\mu]$ in the case of the helium atom: 
+we derive the analytical form of a new Jastrow factor tuned by a unique parameter $\mu$, and discuss the physical content of such a new Jastrow factor. 
+Then, we show that the corresponding TC Hamiltonian has a straightforward analytical structure, which is briefly reviewed as a function of the $\mu$ parameter. 
+We perform a numerical study of the behaviour of the ground state eigenpair of $\tilde{H}[\mu]$ in the case of the helium atom: 
 in the first part we analyze the speed of convergence of the ground state energy with respect to the basis set and the parameter $\mu$, 
@@
 \label{sec:he_htilde}
-Let us write the Hamiltonian of the helium atom using the $r_i = \big|{\bf r}_i\big|$ and $ r_{12} = \big|{\bf r}_1 - {\bf r}_2 \big|$ coordinates\cite{Hylleraas-AdvQChem-64}  
+Let us write the Hamiltonian of the helium atom using the $r_i = |{\bf r}_i|$ and $ r_{12} = |{\bf r}_1 - {\bf r}_2 |$ coordinates\cite{Hylleraas-AdvQChem-64}  
 \begin{equation}
@@
 \label{sec:he_j}
-Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by a similarity transformation of the usual Hamiltonian by a Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
+Now let us consider the transcorrelated Hamiltonian $\tilde{H}[u]$ obtained by the similarity transformation of the usual Hamiltonian by a Jastrow factor $u(r_{12})$ depending only on $r_{12}$: 
 \begin{equation}
@@
 
-The main difference of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor as a linear combination of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$,
+The main differences of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor as a linear combination of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$ through a least-square fit with an specific weighting function,
 we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
-ii) the analytical form of $u(r_{12};\mu)$ is obtained from analytical conditions and not by a fit as in the case of the FROGG,  
-iii) the new Jastrow factor $u(r_{12};\mu)$ is more flexible than the FROGG as it is tuned by a unique parameter $\mu$.
+ii) the new Jastrow factor $u(r_{12};\mu)$ is more flexible than the FROGG as it is tuned by a unique parameter $\mu$ which determines both the depth of the hole and its typical range in $r_{12}$.
 
@@
 \end{equation}
-implying that the right-eigenvectors of the TC Hamiltonian obtained with $u(r_{12};\mu)$ are cusp less (see Appendix \ref{sec:cusp}). 
+implying that the right-eigenvectors of the TC Hamiltonian obtained with $u(r_{12};\mu)$ are necessary cusp less (see Appendix \ref{sec:cusp}). 
 The Taylor expansion of Eq. \eqref{eq:j_dl} inserted in the exponential correlating Jastrow factor reads 
@@
 \end{equation}
-From Eq. \eqref{eq:bigJ_dl} one can analyze each term: a) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, Jastrow factor digs the Coulomb hole, 
-b) the term in $e^{ \frac{1}{2}r_{12}} $ exactly imposes the cusp; c) and the last term $e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}$ reshapes the curvature of the Coulomb hole.
-
-Coming now to the behaviour of $u(r_{12};\mu)$ as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, and we compare it with the FROGG.
+From Eq. \eqref{eq:bigJ_dl} one can analyze each term: i) as $e^{-\frac{1}{2\sqrt{\pi}\mu}}<1$, the Jastrow factor digs the Coulomb hole, 
+ii) the term in $e^{ \frac{1}{2}r_{12}} $ exactly imposes the cusp; iii) and the last term $e^{- \frac{\mu}{2\sqrt{\pi}} r_{12}^2}$ reshapes the curvature of the Coulomb hole.
+
+Coming now to the behaviour of $u(r_{12};\mu)$ as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence in $r_{12}$ for a set of values of $\mu$, and we compare it with the FROGG.
 \begin{figure*}
@@
 $u(r_{12};\mfrogg)$ qualitatively reproduces the FROGG. 
-To do so, we propose a one-point fit such that 
+To do so, we impose that $\mfrogg$ is such that the two Jastrow factors coincide at coalescence 
 \begin{equation}
@@
 We represent on Fig \ref{fig_j_mu} the comparison between $u(r_{12};\mfrogg)$ and the FROGG, and it is clearly apparent  that $u(r_{12};\mfrogg)$ reproduces almost perfectly the FROGG, although it decays slightly faster at large $r_{12}$.
-Therefore, one can see the FROGG as a special case of $u(r_{12};\mu)$  with $\mu = \mfrogg$.
+Therefore, one can see the FROGG as a special case of the new Jastrow factor $u(r_{12};\mu)$ with $\mu = \mfrogg$.
 
@@
  \label{def_k}
-  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = & \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) + \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
+  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = &   \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) \\
+                                          + & \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
                                           + & \nabla_3 u(r_{13},\mu) \cdot \nabla_3 u(r_{32},\mu).
@@
 from the long-range interaction at small $r_{12}$, 
-and it is not monotonic and attractive (\textit{i.e.} $\lim_{r_{12} \rightarrow 0} \deriv{}{r_{12}}{} \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) >0 $). 
+and it is not monotonic and attractive (\textit{i.e.} $\lim_{r_{12} \rightarrow 0} \deriv{}{r_{12}}{} \tilde{\mathcal{W}}_{ee}(r_{12},\mu) >0 $). 
 This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $u(r_{12},\mu)$ (see Eqs.\eqref{def_j_00} and \eqref{def_j_0}).
@@
 Nevertheless, as it will be shown by numerical computations, the effective potentials $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ and $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ are almost identical \textit{in average}, as they numerically agree for $r_{12}>1$ and that $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ essentially oscillates around $\tilde{\mathcal{W}}_{ee}(r_{12},\mfrogg)$ for small values of $r_{12}$.
-This statement will be supported by numerical computations in the next sections.
 
@@
 
-\section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of he He atom}
+\section{Detailed numerical study of $\tilde{H}[\mu]$ in the case of the helium atom}
 \label{sec:total_he}
@@
 \end{equation}
-As long as the basis set $\basis$ is incomplete, because of its non hermitian nature, $\tilde{H}[\mu]^{\basis}$ looses the variational principle and therefore its eigenvalues have no reasons to be bounded from below.
+As long as the basis set $\basis$ is incomplete, $E_i^{\basis}[\mu]$ might not coincide with $E_i$, and because of its non hermitian nature, $\tilde{H}[\mu]^{\basis}$ looses the variational principle and therefore its eigenvalues $E_i^{\basis}[\mu]$ have no reasons to be bounded from below.
 
@@
 As $\mu$ increases, the difference between $E_0^{\basis}[\mu]$ and $E_0^{\basis}[\text{FCI}]$ in a given basis set diminishes, 
-which is expected as in the $\mu \rightarrow \infty$ limit, one obtains that  $\tilde{H}[\mu] \rightarrow H$.
+which is expected as $\lim_{\mu \rightarrow \infty} \tilde{H}[\mu] \rightarrow H$.
 
@@
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
-To answer that question, we investigate some properties in real space of the ground state eigenvectors of different types of Hamiltonians. 
-For the sake of simplicity we perform the study on the ground state of the helium atom.
+To bring insights to these observations, we investigate the behaviour in real space of the ground state eigenvectors of the TC Hamiltonian and the usual physical Hamiltonian in the case of the helium atom.
 
@@
 
-From these figure, one can notice that: 
+From these figures, one can notice that: 
 i) the right eigenvector $\phimub(\br{}_1,\br{}_2)$ converges faster than the FCI wave function with respect to the basis set, 
@@
 \label{sec:iso_elec}
-Having investigated in the case of the helium atom the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with both $\mu$ and the basis set used, we now study the ground state energies of the isoelectronic series of the helium atom for H$^{-}$ to Ne$^{8+}$.
+Having investigated in the case of the helium atom the behaviour of both the eigenvalues and eigenvectors of $\tilde{H}[\mu]$ with both $\mu$ and the basis set used, we now study the ground state energies of the isoelectronic series of the helium atom from H$^{-}$ to Ne$^{8+}$.
 As seen from the previous study on the helium atom, the quality of the eigenvalues of $\tilde{H}[\mu]$ depends on the value of $\mu$ but there is a quite wide regimes of $\mu$ for which they converge significantly faster with the basis set with respect to the usual Hamiltonian.
@@
 \end{equation}
-with $\alpha = (9 \pi/4)^{-1/3}$ and $r_s = (4 \pi n/3)^{-1/3}$. 
+with $\alpha = (9 \pi/4)^{-1/3}$, $r_s = (n 4 \pi /3)^{-1/3}$ and $n$ being the density. 
 Such function $\mursc({\bf r})$ depends on the system and on the position in space through the density $n({\bf r})$ of the system at a given point ${\bf r}$. 
@@
 We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ in $\tilde{H}[\mu]$.
-We also report in Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets vary by less than $0.1\%$. 
+We also report in Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets varying by less than $0.1\%$. 
 As one can observe from  Table \ref{table_conv_e_mu_iso}, the ground state energies of $\tilde{H}[\murscav]$ converge much faster than that of the usual Hamiltonian as the MAD for the ground state energies is of 2.64 mH, 0.48 mH and 0.26 mH in the double-, triple- and quadruple zeta quality basis sets (respectively) whereas it is of 12.16 mH, 4.71 mH and 1.64 mH for the usual Hamiltonian.
@@
 Still with the aim of finding good values of $\mu$, we propose here the derivation of another approach based on the mapping of the on-top pair density of the UEG and a model built with the Jastrow factor defined by \eqref{eq:def_j}.
-Assuming a single Slater determinant ansatz for a Jastrow Slater wave function with a Jastrow factor defined in \eqref{eq:def_j}, the on-top pair density is 
-\begin{equation}
- n_2^\mu({\bf r}) = \frac{1}{2}\big(n({\bf r})\big)^2 e^{-\frac{1}{\sqrt{\pi}\mu}}
-\end{equation}
-and the exact on-top pair density can be estimated from the UEG through 
+Assuming a single Slater determinant ansatz for a Jastrow Slater wave function with a Jastrow factor defined in \eqref{eq:def_j} and neglecting the corresponding normalization factor, the on-top pair density is
+\begin{equation}
+ n_2^\mu({\bf r}) = \frac{1}{2}\big(n({\bf r})\big)^2 e^{-\frac{1}{\sqrt{\pi}\mu}}.
+\end{equation}
+Also, the exact on-top pair density can be estimated from the UEG through 
 \begin{equation}
@@
 \begin{equation}
- \muueg({\bf r}) = \frac{\text{log}\bigg(2 g_0(n({\bf r}))\bigg) }{\sqrt{\pi}}.
+ \begin{aligned}
+                  n_2^\mu({\bf r}) &= n_2^{\text{UEG}}({\bf r}) \\
+ \Leftrightarrow  \muueg({\bf r})  &= \frac{\text{log}\bigg(2 g_0(n({\bf r}))\bigg) }{\sqrt{\pi}}.
+ \end{aligned}
 \end{equation}
@@
 We can also compare the results obtained with $\muuegav$, $\murscav$ and $\mursclda$ to that obtained with the FROGG and $\mfrogg$, which are also reported in Table \ref{table_conv_e_mu_iso}. 
-From these data one can clearly observe several things: i) while for quite diffuse systems as H$^-$ and He the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
+From these data one can clearly observe several things: i) while for the quite diffuse systems as H$^-$ and He, the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
 These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system, and therefore shows the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
@@
 We report in Figs \ref{fig:H2} the difference with respect to the estimated exact ground state potential energy curve using several levels of calculations for the aug-cc-pVDZ and aug-cc-pVTZ basis sets.
+We do not report the values in the aug-cc-pVQZ because the FCI values are already near the CBS.
 
@@
 In the present paper, we derived a new form of Jastrow factor $u(r_{12},\mu)$ for the TC framework and performed the first numerical tests on a set of two electron atomic and molecular systems. 
-In contrast to the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} which was obtained as a linear combination of Gaussians from a numerical fit, the analytical form of the new Jastrow factor proposed here has been derived from the analysis of the leading order terms in $\frac{1}{r_{12}}$ of the general TC Hamiltonian, such that it mimics the long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ used in the RS-DFT framework (see Sec.
+In contrast to the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} which was obtained as a linear combination of Gaussians from a least-square fit with a fixed weighting function, the analytical form of the new Jastrow factor proposed here has been derived from the analysis of the leading order terms in $\frac{1}{r_{12}}$ of the general TC Hamiltonian, such that it mimics the long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ used in the RS-DFT framework (see Sec.
 \ref{sec:new_j}).
@@
 An investigation of the right eigenvectors in real space for different values of $\mu$ have shown interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
-These different behaviour can be understood as the effective potential entering TC Hamiltonian becomes more and more attractive as $\mu$ lowers.
+These different behaviour can be understood as the effective potential entering in the TC Hamiltonian becomes more and more attractive as $\mu$ lowers.
 Nevertheless, when the right eigenvectors are multiplied by the corresponding Jastrow factor, one obtains a very good approximation of the numerically exact ground state wave function (see Sec.
@@
 
-In order to study the performance of the present approach on a broader set of two-electron systems, we investigate the ground state energy of the helium isoelectronic series from H$^-$ to Ne$^{8+}$ (see Sec.
+In order to study the performance of the present approach on a broader set of two-electron systems, we investigated the ground state energy of the helium isoelectronic series from H$^-$ to Ne$^{8+}$ (see Sec.
 \ref{sec:iso_elec}).
@@
 The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and to explore the possibility of having a value of $\mu$ varying in space.
+
+\section{Acknowledgment}
+The author would like to thank Julien Toulouse and Andreas Savin for stimulating discussions.
 
@@
  &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu)
- & = 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
+ & = 2  \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  \bigg).
  \end{aligned}

### 2021-01-18 cusp_j/paper/paper.tex
final coutdown for the paper

@@
-\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
+%\documentclass[twocolumn]{revtex4}
+\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress,twocolumn]{revtex4-1}
 \usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amsmath,amssymb,amsfonts,physics,mhchem,xspace,subfigure}
+%\usepackage{graphicx,subfigure,amsmath,amssymb,braket,float}
 
@@
 
-\usepackage[
-	colorlinks=true,
-    citecolor=blue,
+\usepackage[colorlinks=true,citecolor=blue,
     breaklinks=true 
@@
 
-\definecolor{darkgreen}{HTML}{009900}
 \usepackage[normalem]{ulem}
+
 \newcommand{\sphi}[1]{\hat{{\bf S}}_{#1}}
@@
 These short-range correlation effects are mainly due to the diverging character of the coulomb potential, which induces a non analytical behaviour of the wave function at small inter-electronic distance ($r_{12}\approx 0$): the famous electronic cusp originally derived by Kato\cite{Kat-CPAM-57}.
-For a clear and general derivation of the cusp conditions up to second order for Coulombic systems, see Ref.\onlinecite{Tew-JCP-08}.
+For a clear and general derivation of the cusp conditions up to second order for Coulombic systems, see Ref.
+\onlinecite{Tew-JCP-08}.
 As shown by the seminal works of Hylleraas\cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
@@
 Later on, Ten-No\cite{TenNo-CPL-00-a} proposed to significantly change the paradigm of Boys and Handy: instead of using a single Slater determinant and optimizing both the orbitals and the Jastrow factor, one uses a more elaborate many body theory with a frozen universal Jastrow factor.
-This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}.
+This strategy was developed using as M{\o}ller-Plesset at second order (MP2) in Refs.
+\onlinecite{TenNo-CPL-00-a,HinTanTen-JCP-01} and a linearised coupled cluster ansatz in later work\cite{HinTanTen-CPL-02}.
 The Jastrow factor introduced by Ten-No, developed as a linear combination of gaussian functions and referred to as the frozen gaussian geminal (FROGG), only depends on the inter-electronic coordinate and is optimized such that the scalar effective two-electron  potential cancels on average the coulomb potential near $r_{12}=0$.
 The use of gaussian functions to represent the Jastrow factor enabled Ten-No to develop a numerical scheme to evaluate exactly the three-electron integrals present in TC Hamiltonian\cite{TenNo-CPL-00-b}, which is an alternative to the density-fitting method proposed by the same author in the general context of F12 methods\cite{TenMan-JCP-03}.
-In Ref.\onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
+In Ref. \onlinecite{HinTanTen-JCP-01}, Ten-No \textit{et. al.} introduced a biorthogonal approach, 
 which allows to treat the non-hermitian TC Hamiltonian in a mathematical form more suited 
@@
 As in RS-DFT, the new TC Hamiltonian and Jastrow factor are tuned by a unique range separation parameter $\mu$. 
-The aim of this study is to establish the analytical form of the TC Hamiltonian and perform a numerical study on the ground state eigenvalues and eigenvectors on a set of two-electron atomic and molecular systems: the helium isoelectronic series from H$^-$ to Ne$^{8+}$ and H$_2$ molecule.
+The aim of this paper is to establish the analytical form of the TC Hamiltonian and perform a numerical study on the ground state eigenvalues and eigenvectors on a set of two-electron atomic and molecular systems: the helium isoelectronic series from H$^-$ to Ne$^{8+}$ and H$_2$ molecule.
 In the context of the TC theory the interesting features of the present work are that 
@@
 
-\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ mimicking a long-range interaction}
+\subsection{A new form of Jastrow factor $u(\mu,r_{12})$ tuned by a single parameter $\mu$}
 \label{sec:new_j}
@@
 
-The main differences of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor as a linear combination of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$ through a least-square fit with an specific weighting function,
+The main differences of the present approach with the FROGG introduced by Ten-No\cite{TenNo-CPL-00-a} is that instead of optimizing the Jastrow factor as a linear combination of Gaussian functions such that $\frac{1}{r_{12}}  + \tilde{W}[u] + \tilde{w}[u] \approx 0$ when $r_{12}=0$ through a least-square fit with a specific weighting function,
 we impose the analytical structure of $u(r_{12};\mu)$ such that i) the sum of all terms in $1/r_{12}$ (\textit{i.e.} $\tilde{W}[u] + \frac{1}{r_{12}}$) exactly provides the non divergent long-range interaction $\text{erf}(\mu r_{12})/r_{12}$ for all $r_{12}$,
@@
 The new Jastrow $u(r_{12};\mu)$ factor is tuned by a unique parameter, $\mu$, which have the unit of the inverse of a distance. 
-From Eq.\eqref{eq:def_j} we can notice that 
+From Eq. \eqref{eq:def_j} we can notice that 
 \begin{equation}
@@
 and therefore $u(r_{12};\mu)$ impacts only the small $r_{12}$ behaviour,  
-which is expected since the equation determining $u(r_{12},\mu)$ is obtained from the small $r_{12}$ limit of the Schroedinger equation (see Eq.\eqref{def_j_00}).
+which is expected since the equation determining $u(r_{12},\mu)$ is obtained from the small $r_{12}$ limit of the Schroedinger equation (see Eq. \eqref{def_j_00}).
 
@@
 \begin{figure*}
- \label{fig_j_mu}
         \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_j.pdf}
@@
 We also compare the FROGG (see Eq. \eqref{eq_frogg}) and the value of $\mu = 0.865$ which equals the FROGG at $r_{12}=0$ (see Eq. \eqref{mu_ten_no_1}). }
+ \label{fig_j_mu}
 \end{figure*}
@@
 
-As the function $u(r_{12};\mu)$ contains a unique parameter, one can try to find the value of $\mfrogg$ such that 
+As the function $u(r_{12};\mu)$ contains a unique parameter $\mu$, one can try to find the value $\mfrogg$ such that 
 $u(r_{12};\mfrogg)$ qualitatively reproduces the FROGG. 
-To do so, we impose that $\mfrogg$ is such that the two Jastrow factors coincide at coalescence 
+To do so, we impose that $\mfrogg$ is such that the two Jastrow factors coincide at coalescence, \textit{i.e.}  
 \begin{equation}
@@
 which gives $\mfrogg\approx0.87$. 
-We represent on Fig \ref{fig_j_mu} the comparison between $u(r_{12};\mfrogg)$ and the FROGG, and it is clearly apparent  that $u(r_{12};\mfrogg)$ reproduces almost perfectly the FROGG, although it decays slightly faster at large $r_{12}$.
+We represent on Fig.
+\ref{fig_j_mu} the comparison between $u(r_{12};\mfrogg)$ and the FROGG, and it is clearly apparent  that $u(r_{12};\mfrogg)$ reproduces almost perfectly the FROGG, although it decays slightly faster at large $r_{12}$.
 Therefore, one can see the FROGG as a special case of the new Jastrow factor $u(r_{12};\mu)$ with $\mu = \mfrogg$.
@@
 with $\hat{\tau}_\mu = \sum_{i<j}u(r_{ij},\mu)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
-Therefore, the right-eigenvectors $\ket{\phimui}$ depends on $\mu$ and satisfy the effective Schroedinger equation
+Therefore, the \textit{i-th} right-eigenvectors $\ket{\phimui}$ depends on $\mu$ and satisfy the effective Schroedinger equation
 \begin{equation}
@@
 where $E_i$ is the exact $i$-th eigenvalue of the physical Hamiltonian.
-The fact that $\tilde{H}[\mu]$ and $H$ have the same spectrum originates from the properties of the similarity transformation.
+The fact that $\tilde{H}[\mu]$ and $H$ share the same spectrum originates from the properties of the similarity transformation.
 Nevertheless, once projected in an incomplete basis set, $\tilde{H}[\mu]$ and $H$ might not have the same eigenvalues.
@@
 
-By injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq.\eqref{ht_def_gu}, one obtains 
+By injecting the form of Eqs. \eqref{eq:k_final} and \eqref{eq:l_final} in Eq. \eqref{ht_def_gu}, one obtains 
 \begin{equation}
@@
 
-In order to have a pictorial representation of $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$, we illustrate in Fig\ref{fig_wee_mu} its shape for different values of $\mu$. 
+As the present study is devoted to two-electron systems, the physics of $\tilde{H}[\mu]$ can be qualitatively understood by looking at $\tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$, which is illustrated in Fig.
+\ref{fig_wee_mu} for different values of $\mu$ and compared with the usual long-range interaction of the RS-DFT framework.
 \begin{figure*}
- \label{fig_wee_mu}
         \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_small.pdf}
@@
         \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (left) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (right) for different values of $\mu$.}
+ \label{fig_wee_mu}
 \end{figure*}
-From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ 
+From  Fig. \ref{fig_wee_mu} we can see that the scalar effective potential $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ 
 is non divergent, increases when $\mu$ increases and globally resembles the long-range interaction used in RS-DFT at large $r_{12}$. 
-Nevertheless, as observed from Fig.\ref{fig_wee_mu}, it is significantly different 
+Nevertheless, as observed from Fig. \ref{fig_wee_mu}, it is significantly different 
 from the long-range interaction at small $r_{12}$, 
 and it is not monotonic and attractive (\textit{i.e.} $\lim_{r_{12} \rightarrow 0} \deriv{}{r_{12}}{} \tilde{\mathcal{W}}_{ee}(r_{12},\mu) >0 $). 
-This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $u(r_{12},\mu)$ (see Eqs.\eqref{def_j_00} and \eqref{def_j_0}).
+This difference with respect to the long-range interaction can be understood as the equation obtained to derive the Jastrow factor only takes into account the first-order derivative of $u(r_{12},\mu)$ (see Eqs.
+\eqref{def_j_00} and \eqref{def_j_0}).
 If one desires to impose that $\tilde{\mathcal{W}}_{ee}(r_{12},\mu) = \frac{\text{erf}(\mu r_{12})}{r_{12}}$, one would have to solve the non-linear differential equation 
@@
 \end{equation}
-with $\hat{\tau}_{\text{TN}} = \sum_{i<j} u^\text{TN}(r_{ij})$. 
+with $\hat{\tau}_{\text{TN}} = \sum_{i<j} u^\text{TN}(r_{ij})$ and $u^\text{TN}(r_{ij})$ given in Eq. \eqref{eq_frogg}. 
 This leads to the following transcorrelated Hamiltonian 
@@
 \begin{figure*}
+        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_frog.pdf}
+        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=\mfrogg$ and comparison with the effective potential $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ obtained with the FROGG (see Eq.
+\eqref{eq:_wee_frogg}).}
  \label{fig_wee_frogg}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_frog.pdf}
-        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=\mfrogg$ and comparison with the effective potential $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ obtained with the FROGG (see Eq.\eqref{eq:_wee_frogg}).}
 \end{figure*}
@@
 All implementation was done as a plugin of the program quantum package\cite{QP2}. 
-We use the RHF molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors together with the eigenvalues.
+We use the restricted Hartree-Fock (RHF) molecular orbitals to build all matrix elements of $\tilde{H}[\mu]$, and then we solve the two-body problem giving full flexibility to $\phiimub$ (\textit{i.e.} $\phiimub$ is expressed as a linear combination of all possible Slater determinants within a given basis set $\basis$) with a non hermitian eigensolver to obtain both right and left eigenvectors together with the eigenvalues.
 
@@
 Also, it is striking to see that, in a given basis set, the ground state eigenvalue of the TC Hamiltonian obtained by the FROGG and that obtained by $\tilde{H}[\mu]$ with $\mu=\mfrogg$ coincide with less than 1 mH.
-The latter results confirms that as $u(r_{12},\mfrogg) \approx u^{\text{TN}}(r_{12})$ (see Fig \ref{fig_j_mu} and Eqs.
+The latter results confirms that as $u(r_{12},\mfrogg) \approx u^{\text{TN}}(r_{12})$ (see Fig.
+\ref{fig_j_mu} and Eqs.
 \eqref{mu_ten_no_1} and \eqref{mu_ten_no_2}), the TC Hamiltonians obtained with the two Jastrow factor are very similar, as illustrated for instance by the effective potential in Fig.
@@
 \begin{figure*}
- \label{fig_conv_e_mu}
         \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_small_mu.pdf}
@@
 We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq. \eqref{eq_frogg}), referred here after as FROGG. }
+ \label{fig_conv_e_mu}
 \end{figure*}
@@
 \begin{table*}
-\label{table_conv_e_mu}
 \caption{Ground state eigenvalue (in Hartree) of $\tilde{H}[\mu]$ for the He atom with the AVXZ (X=D,T,Q,5) basis sets for different values of $\mu$, and error (in mH) with respect to the exact non relativistic energy.
 We also compare with the results of the TC obtained with the $u(r_{12}) = u^{\text{TN}}(r_{12})$ (see Eq.
-\eqref{eq_frogg} and Ref.\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.87$ is defined in Eq.
+\eqref{eq_frogg} and Ref.
+\onlinecite{TenNo-CPL-00-a}), referred here as FROGG, and the value of $\mfrogg=0.87$ is defined in Eq.
 \eqref{mu_ten_no_1}.
@@
 \end{ruledtabular}
+\label{table_conv_e_mu}
 \end{table*}
@@
 \label{sec:he_real_space}
-In Sec.\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_0^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
+In Sec.
+\ref{sec:total_e} we shown the improvement of the speed of convergence of the ground state energies $E_0^{\basis}[\mu]$ of the helium atom, which was effective for a quite large range of $\mu$ starting from $\mu=0.2$ to $\mu=1.6$.
 Nevertheless, one can wonder if this good behavior results from a kind of error cancellation or if there is indeed a deeper mathematical reason for such an improvement of speed of convergence. 
@@
 
-The exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$ is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through 
+For a two-electron system, the exact ground state eigenvector $\phimu$ of $\tilde{H}[\mu]$ is directly related to the exact ground state wave function $\psiex$ by the Jastrow factor $u(r_{12},\mu)$ through
 \begin{equation}
@@
 Then, the quality of a given basis set $\basis$ to represent $\tilde{H}[\mu]$  can be also quantified from the vicinity between $\psimub(\br{}_1,\br{}_2)$ and the exact wave function $\psiex(\br{}_1,\br{}_2)$.
-To illustrate that, 
+To illustrate these ideas, 
 we plotted a cutting of $\psiex(\br{}_1,\br{}_2)$ and  $\psimub(\br{}_1,\br{}_2) $ with different basis sets and values of $\mu$.
@@
 \begin{figure*}
- \label{fig:mu_0.3_dz_3}
         \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_0_3_cusp_avdz_avtz_3.pdf}
@@
 }
+ \label{fig:mu_0.3_dz_3}
 \end{figure*}
@@
 \begin{figure*}
- \label{fig:mu_1.0_dz_3}
         \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_1_0_cusp_avdz_avtz_3.pdf}
@@
 }
+ \label{fig:mu_1.0_dz_3}
 \end{figure*}
@@
 
-ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig \ref{fig_wee_compare} for a graphical representation).
+ii) The fact that the wave function $\phimub(\br{}_1,\br{}_2)$ presents a maximum at $r_{12}=0$ for $\mu=0.3$ whereas it provides a minimum for $\mu=1.0$ can be explained by the shape of the effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$: the latter is much more attractive when $r_{12}\approx 0$ for $\mu=0.3$ than for $\mu = 1.0$ (see Fig.
+\ref{fig_wee_compare} for a graphical representation).
 
@@
 \begin{figure*}
- \label{fig_wee_compare}
         \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_zoom.pdf}
@@
         Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
+ \label{fig_wee_compare}
 \end{figure*}
@@
 where $n_{\text{HF}}({\bf r})$ is the HF density and $N_e$ the number of electrons in the system. 
-We report in Table \ref{table_conv_e_mu_iso} the convergence with respect to the basis set $\basis$ the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ in $\tilde{H}[\mu]$.
+We report in Table \ref{table_conv_e_mu_iso} the convergence with the basis set $\basis$ of the error with respect to the exact ground state energies of the isoelectronic series of the helium atom using $\murscav$ in $\tilde{H}[\mu]$.
 We also report in Table \ref{table_conv_e_mu_iso} the value of $\murscav$ in the double-zeta quality basis for each system, the value in larger basis sets varying by less than $0.1\%$. 
@@
 \end{equation}
-Therefore one can define an average UEG value of $\mu$ 
+Then, one can define an average value of $\muueg({\bf r})$ over the HF density
 \begin{equation}
@@
 and the results obtained are represented in Table \ref{table_conv_e_mu_iso}.
-From this data, one can clearly see that $\mursclda$ gives a better MAD and MSD as it is below 1 mH from the aug-cc-pVDZ basis set and still improve when enlarging the basis set.
+From this data, one can clearly see that $\mursclda$ gives a better MAD and MSD as it is below 1 mH from the double-zeta quality basis set and still improve when enlarging the basis set.
 
 We can also compare the results obtained with $\muuegav$, $\murscav$ and $\mursclda$ to that obtained with the FROGG and $\mfrogg$, which are also reported in Table \ref{table_conv_e_mu_iso}. 
-From these data one can clearly observe several things: i) while for the quite diffuse systems as H$^-$ and He, the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
+From these data one can clearly observe several things: i) while for the quite diffuse systems as H$^-$ and He, the energy obtained with the FROGG are of comparable quality that that with $\muuegav$, $\murscav$ and $\mursclda$, the situation deteriorates in a monotonic way from Li$^+$ to Ne$^{8+}$, ii) from Li$^+$ to Ne$^{8+}$, the FROGG converges from below the exact energies, and the larger the $Z$, the more pronounced is the error with respect to the exact ground state energy, specially in the double-zeta quality basis, iii) the results obtained with $\mfrogg$ show a similar behaviour with respect to that of using the FROGG, iv) the MAD obtained with the FROGG is significantly higher, specially for the double-zeta quality, than that obtained with $\muuegav$, $\murscav$ and $\mursclda$.
 These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system, and therefore shows the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
@@
 \begin{table*}
-\label{table_conv_e_mu_iso}
 \caption{Error (in mH) with respect to the exact non relativistic energies of the ground state eigenvalue of the usual Hamiltonian and $\tilde{H}[\mu]$ for the helium isoelectronic series with Dunning basis sets basis sets for different flavour of $\mu$.
@@
 \end{ruledtabular}
+\label{table_conv_e_mu_iso}
 \end{table*}
@@
 \begin{figure*}
- \label{fig:H2}
         \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_frogg.pdf}
@@
 }
+ \label{fig:H2}
 \end{figure*}
@@
 An investigation of the right eigenvectors in real space for different values of $\mu$ have shown interesting behaviour: while for $\mu=1$ the right-eigenvectors provide a depletion of the probability of finding electrons near $r_{12}=0$, for $\mu=0.3$ one obtains an increase of such a probability.
-These different behaviour can be understood as the effective potential entering in the TC Hamiltonian becomes more and more attractive as $\mu$ lowers.
+These different behaviours can be understood as the effective potential entering in the TC Hamiltonian becomes more and more attractive as $\mu$ lowers.
 Nevertheless, when the right eigenvectors are multiplied by the corresponding Jastrow factor, one obtains a very good approximation of the numerically exact ground state wave function (see Sec.
@@
 \end{equation}
-which is a more compact expression than Eq.\eqref{def_non_hermit}.
+which is a more compact expression than Eq. \eqref{def_non_hermit}.
 
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
+ &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
  \end{aligned}
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
  &\qquad \qquad \qquad   \bri{12} \cdot \bri{13}  \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
- =& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
+ &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
+ =& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
  \end{aligned}
@@
  \label{eq:l_1x}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
- = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_u(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
+& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+ = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
  &(x_1 - x_2) (x_1 - x_3) \phi_k(\bri{1}) \phi_l(\bri{2}) \phi_n(\bri{3}).
@@
  \label{eq:l_1x_2}
-& \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_k \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\
@@
 \end{equation}
-When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq.\eqref{def:h_c}, translates into
+When looking at $r_{12}\approx 0$, all terms multiplying $\frac{1}{r_{12}}$ in $H \psiex(\br{}_1,\br{}_2)$ must remain finite, which, according to Eq. \eqref{def:h_c}, translates into
 \begin{equation}
@@
 Similarly to Eq. \eqref{eq:cusp_0}, when looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ in $\tilde{H}[u]\phiex(\br{}_1,\br{}_2)$ must remain finite, 
-which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.\eqref{eq:def_wt}). Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.\eqref{eq:hpi0_ex} translates into
+which involves also the term $\tilde{W}[u]$ in $\tilde{H}[u]$ (see Eq.
+\eqref{eq:def_wt}).
+Therefore, imposing the finiteness of the limit $r_{12}\rightarrow 0$ of Eq.
+\eqref{eq:hpi0_ex} translates into
 \begin{equation}
@@
 \end{equation}
-Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
+Then, the term $\frac{1}{r_{12}}\bigg[ 1 - 2\deriv{u(r_{12})}{r_{12}}{}\bigg]$ in Eq.
+\eqref{eq:cusp_phi_0} looks like an effective electron electron interaction induced by the presence of the Jastrow factor in $\tilde{H}[u]$.
 Therefore, as long as one imposes that 
@@
 \end{equation}
-which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
-Within the condition of Eq.\eqref{eq:cusp_phi_1}, the general condition of Eq.\eqref{eq:cusp_phi_0} becomes 
+which is nothing but the cusp condition for the Jastrow factor $u(r_{12})$, the scalar term proportional to $\frac{1}{r_{12}}$ in Eq.
+\eqref{eq:cusp_phi_0} vanishes at $r_{12}=0$, and then one obtains a non-divergent effective electron-electron interaction.
+Within the condition of Eq. \eqref{eq:cusp_phi_1}, a sufficient condition for $\phiex(\bd{r_1},\bd{r_2})$ to fulfill the general condition of Eq. \eqref{eq:cusp_phi_0} is
 \begin{equation}
@@
 \end{equation}
-and 
+and as
 \begin{equation}
@@
 \end{equation}
-which seems to contradict the intuitive limit of Eq.\eqref{eq:lim_mu_1}.
-
-Nevertheless, as Eq.\eqref{eq:lim_mu_4} deals with operators, the equality must be considered in the sense of distributions.  
+which seems to contradict the intuitive limit of Eq. \eqref{eq:lim_mu_1}.
+
+Nevertheless, as Eq. \eqref{eq:lim_mu_4} deals with operators, the equality must be considered in the sense of distributions.  
 Therefore, considering a generic bounded square integrable wave function $\psi(\br{}_1,\hdots,\br{}_N)$ yielding to a integrable pair density $n_2(\br{}_1,\br{}_2)$, the equality between $\tilde{H}[\mu]$ and $H$ is, in the sense of distributions, defined by the following equality
@@
 \end{equation}
-and considering the limit for of $\tilde{H}[\mu]$ (see Eq.\eqref{eq:lim_mu_4}), it implies that 
+and considering the limit for of $\tilde{H}[\mu]$ (see Eq. \eqref{eq:lim_mu_4}), it implies that 
 \begin{equation}
@@
 \end{equation}
-To intuitively show Eq.\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
+To intuitively show Eq.
+\eqref{eq:lim_mu_6}, one can perform a series of change of variable $(\br{}_1,\br{}_2)\rightarrow (\br{}_{12},\frac{1}{2}(\br{}_1 + \br{}_2))$ and then use the spherical coordinates for $\br{}_{12}$
 \begin{equation}
@@
 \end{equation}
-which implies Eq.\eqref{eq:lim_mu_1}.
+which implies Eq. \eqref{eq:lim_mu_1}.
 

### 2021-01-18 cusp_j/paper/submit/paper.tex
Publishable version

--- 2021-01-18 cusp_j/paper/paper.tex
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_j.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_exp_j.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig1a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig1b.pdf}\\
         \caption{Shape of $u(r_{12};\mu)$ (left) and of $\text{exp}\big(u(r_{12};\mu) \big) $ (right) for different values of $\mu$. 
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_small.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_erf.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig2a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig2b.pdf}\\
         \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (left) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (right) for different values of $\mu$.}
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_frog.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig3.pdf}
         \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=\mfrogg$ and comparison with the effective potential $\tilde{\mathcal{W}}_{ee}^\text{TN}(r_{12})$ obtained with the FROGG (see Eq.
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_small_mu.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/Energy/He_E_conv_basis_large_mu.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig4a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig4b.pdf}\\
         \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$. 
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_0_3_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig5a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig5b.pdf}\\
         \caption{
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_1_0_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/cusp/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig6a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig6b.pdf}\\
         \caption{
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/jastrow/w_ee_zoom.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig7.pdf}
         \caption{
@@
 \begin{figure*}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_frogg.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_ten_no.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig8a.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig8b.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig8c.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig8d.pdf}\\
+        \includegraphics[width=0.45\linewidth]{Fig8e.pdf}
+        \includegraphics[width=0.45\linewidth]{Fig8f.pdf}
         \caption{

### 2021-01-18 cusp_j/paper/letter/CoverLetter.tex
added letter

\documentclass[10pt]{letter}
\usepackage{UPS_letterhead,color}
%\usepackage{xcolor,mhchem,mathpazo,ragged2e}
\newcommand{\alert}[1]{\textcolor{red}{#1}}

\begin{document}

\begin{letter}%
{To the Editors of the Journal of Chemical Physics}

\opening{Dear Editors,}

%\justifying
Please find enclosed my manuscript entitled
\begin{quote}
\textit{``A new form of transcorrelated Hamiltonian inspired by range-separated DFT''}, 
\end{quote}
which I would like you to consider as a full article in the \textit{Journal of Chemical Physics}.
%This contribution fits nicely in the section \textit{``Spectroscopy and Photochemistry; General theory''}.

One of the most fundamental drawbacks of conventional wave function methods is the slow convergence of energies and properties with respect to the one-electron basis set.
As proposed by Kutzelnigg more than thirty years ago, one can introduce a Jastrow factor explicitly depending on the interelectronic distance $r_{12}$ to significantly speed up the convergence. 
In this framework, one can take into account the effect of such Jastrow factor directly into an effective Hamiltonian: the transcorrelated Hamiltonian. The generic form of such an effective Hamiltonian have been established in the late 60's by Boys and Handy, but a renewal of interest have emerged recently due to the fast convergence of its eigenvalues with respect to the basis set.

In the present work, we propose the analytical derivation and first numerical test of a new universal Jastrow factor specially designed for the transcorrelated framework. The equations leading to this new Jastrow factor are inspired by the range-separated DFT effective Hamiltonian. Such a Jastrow factor has several advantages: it is tuned by a unique parameter allowing to simply adapt to a typical scale-length, the explicit analytical form of the transcorrelated Hamiltonian is directly known and its eigenvalues converge extremely fast toward the complete basis set limit, all two-electron integrals can be easily performed analytically, the expensive three-body terms can be computed efficiently through a mixed numerical-analytical approach.

Because of the large impact of our work, we expect it to be of interest to a wide audience within the theoretical chemistry community and beyond.
We suggest Seiichiro L. Ten-No, Ali Alavi, David Tew and Naoto Umezawa as potential referees.
This contribution has never been submitted in total nor in parts to any other journal. 
We look forward to hearing from you soon.

\closing{Sincerely, the author.}

\end{letter}
\end{document}

### 2021-01-19 cusp_j/paper/letter/CoverLetter.tex
modified paper

@@
 
-In the present work, we propose the analytical derivation and first numerical test of a new universal Jastrow factor specially designed for the transcorrelated framework.
+In the present work, I propose the analytical derivation and first numerical test of a new universal Jastrow factor specially designed for the transcorrelated framework.
 The equations leading to this new Jastrow factor are inspired by the range-separated DFT effective Hamiltonian.
@@
 
-Because of the large impact of our work, we expect it to be of interest to a wide audience within the theoretical chemistry community and beyond.
-We suggest Seiichiro L. Ten-No, Ali Alavi, David Tew and Naoto Umezawa as potential referees.
+Because of its new results in the context of fundamental electronic structure theory, I expect this work to be of interest to a wide audience within the theoretical chemistry community.  
+I suggest Seiichiro L. Ten-No, Ali Alavi, David Tew and Naoto Umezawa as potential referees.
 This contribution has never been submitted in total nor in parts to any other journal. 
-We look forward to hearing from you soon.
+I look forward to hearing from you soon.
 
-\closing{Sincerely, the author.}
+\closing{Sincerely, Emmanuel Giner.}
 

### 2021-01-19 cusp_j/paper/submit/paper.tex
modified paper

@@
 We also propose a specific value of $\mu$ which essentially reproduce the results obtained with the frozen Gaussian geminal introduced by Ten-No [CPL-330,169 (2000)]. 
-We introduce a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density, and show the benefit of such approach on the isoelectronic series of the helium atom.
-It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
+%We introduce a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density, and show the benefit of such approach on the isoelectronic series of the helium atom.
+%It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
 
@@
 The exact non relativistic energy was obtained from Ref.
-\cite{Dav-ions-PRA-91}.
+\onlinecite{Dav-ions-PRA-91}.
  }
@@
 The exact non relativistic energy of all systems studied here was obtained from Ref.
-\cite{Dav-ions-PRA-91}.}
+\onlinecite{Dav-ions-PRA-91}.}
 
@@
         \caption{
-        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
+        H$_2$ molecule: Error (in m a.u.) with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
 R$_{eq}$ refers to the equilibrium distance of 1.401 a.u., and the estimated exact non relativistic potential energy curve was taken from Ref.
@@
 The author would like to thank Julien Toulouse and Andreas Savin for stimulating discussions.
+
+\section{Data availability}
+The data that supports the findings of this study are available within the article and from the corresponding author upon reasonable request.
 

### 2021-01-21 cusp_j/paper/submit/paper.tex
minor modifs from Julien

@@
 \onlinecite{Tew-JCP-08}.
-As shown by the seminal works of Hylleraas\cite{Hyl-ZP-29} and further developed byKutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
+As shown by the seminal works of Hylleraas\cite{Hyl-ZP-29} and further developed by Kutzelnigg and coworkers, \cite{Kut-TCA-85,KutKlo-JCP-91, NogKut-JCP-94} the slow convergence of the correlation energy with respect to the quality of the basis set is mainly due to the impossibility to represent the cusp in a finite one-electron basis set.
 As the cusp conditions originate from the divergence of the Coulomb potential at $r_{12}=0$, an alternative approach would be to develop theories dealing with a smooth potential.
@@
 
-In RS-DFT\cite{Sav-INC-96a,TouColSav-PRA-04}, the electron-electron interaction is split into a smooth long-range part and a complementary short-range diverging part, the former being treated explicitly by a wave function and the latter by a density functional.
+In RS-DFT\cite{Sav-INC-95,TouColSav-PRA-04}, the electron-electron interaction is split into a smooth long-range part and a complementary short-range diverging part, the former being treated explicitly by a wave function and the latter by a density functional.
 Such a splitting is done through the function $\text{erf}(\mu r_{12})$ where $\mu$ is the range separation parameter which allows one to continually move from Kohn-Sham DFT ($\mu=0$) to pure WFT ($\mu=\infty$).
@@
 Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize both orbitals and Jastrow parameters for a single Slater determinant.
-Nevertheless, such a constrained form of the wave function for the Slater together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.
+Nevertheless, such a constrained form for the Slater part of the wave function together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.
 
@@
 In the context of the TC theory the interesting features of the present work are that 
-i) the analytical form of the TC Hamiltonian is explicitly known and it turns out that all two-electron integrals can be performed analytically and the three-electron integrals can be efficiently computed in mixed numerical-analytical way, ii) the new Jastrow factor and corresponding TC Hamiltonian are tuned by a unique parameter $\mu$ which allows some flexibility, iii) there always exists a regime of $\mu$ which significantly improve the basis set convergence of WFT, iv) we propose schemes to find a value of $\mu$ which automatically adapts to the system and improves basis set convergence.
+i) the analytical form of the TC Hamiltonian is explicitly known and it turns out that all two-electron integrals can be performed analytically and the three-electron integrals can be efficiently computed in mixed numerical-analytical way, ii) the new Jastrow factor and corresponding TC Hamiltonian are tuned by a unique parameter $\mu$ which allows some flexibility, iii) there always exists a regime of $\mu$ which significantly improves the basis set convergence of WFT, iv) we propose schemes to find a value of $\mu$ which automatically adapts to the system and improves basis set convergence.
 
@@
  \label{eq:j_dl}
- u(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + o(r_{12}^4).
+ u(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + O(r_{12}^4).
 \end{equation}
@@
  \label{ht_def_gu}
- \tilde{H}[\mu] & = H - \sum_{i<j} \hat{K}_\mu(\bri{i},\bri{j}) - \sum_{i<j<k} \hat{L}_\mu(\bri{i},\bri{j},\bri{k}),
- \end{aligned}
-\end{equation}
-where the effective two- and three-body operators $\hat{K}_\mu(\bri{1},\bri{2})$ and $\hat{L}_\mu(\bri{1},\bri{2},\bri{3})$ are defined as
+ \tilde{H}[\mu] & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{j},\mu) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{j},\bri{k},\mu),
+ \end{aligned}
+\end{equation}
+where the effective two- and three-body operators $\hat{K}(\bri{1},\bri{2},\mu)$ and $\hat{L}(\bri{1},\bri{2},\bri{3},\mu)$ are defined as
 \begin{equation}
@@
  \label{def_k}
-  \hat{K}_\mu(\bri{1},\bri{2})  = \frac{1}{2} \bigg( &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu) \\
+  \hat{K}(\bri{1},\bri{2},\mu)  = \frac{1}{2} \bigg( &\Delta_1 u(r_{12},\mu) + \Delta_2 u(r_{12},\mu) \\
                                                + &\big(\nabla_1 u(r_{12},\mu) \big) ^2 + \big(\nabla_1 u(r_{12},\mu) \big) ^2 \bigg) \\
@@
  \label{def_k}
-  \hat{L}_\mu(\bri{1},\bri{2},\bri{3})  = &   \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) \\
+  \hat{L}(\bri{1},\bri{2},\bri{3},\mu)  = &   \nabla_1 u(r_{12},\mu) \cdot \nabla_1 u(r_{13},\mu) \\
                                           + & \nabla_2 u(r_{21},\mu) \cdot \nabla_2 u(r_{23},\mu)  \\
@@
 
-As shown in the Appendix \ref{k_l_appendix}, the operator $\hat{K}_\mu(\bri{1},\bri{2})$ has a straightforward analytical expression which reads 
+As shown in the Appendix \ref{k_l_appendix}, the operator $\hat{K}(\bri{1},\bri{2},\mu)$ has a straightforward analytical expression which reads 
 \begin{equation}
@@
   \begin{aligned}
-   \hat{K}_\mu(\bri{1},\bri{2}) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
+   \hat{K}(\bri{1},\bri{2},\mu) = & \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
 & - \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
@@
 \end{equation}
-and similarly the analytical expression of $\hat{L}_\mu(\bri{1},\bri{2},\bri{3}) $ reads 
+and similarly the analytical expression of $\hat{L}(\bri{1},\bri{2},\bri{3},\mu) $ reads 
 \begin{equation}
@@
  \begin{aligned}
- \hat{L}_\mu(\bri{1},\bri{2},\bri{3}) = & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{12} \cdot \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{13} \\
+ \hat{L}(\bri{1},\bri{2},\bri{3},\mu) = & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{12} \cdot \frac{1 - \text{erf}(\mu r_{13})}{2 r_{13}} \bri{13} \\
                                       + & \frac{1 - \text{erf}(\mu r_{12})}{2 r_{12}} \bri{21} \cdot \frac{1 - \text{erf}(\mu r_{23})}{2 r_{23}} \bri{23} \\
@@
  \label{eq:exp_ht_mu}
-   \tilde{H}[\mu] = & h_c + \sum_{i<j} \bigg( \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) + \tilde{t}[\mu] \bigg) - \sum_{i<j<k} \hat{L}_\mu(\bri{1},\bri{2},\bri{3})
+   \tilde{H}[\mu] = & h_c + \sum_{i<j} \bigg( \tilde{\mathcal{W}}_{ee}(r_{ij},\mu) + \tilde{t}[\mu] \bigg) - \sum_{i<j<k} \hat{L}(\bri{1},\bri{2},\bri{3},\mu)
   \end{aligned}
@@
 This is expected as the density becomes more picked near the nucleus while the nuclear charge increases, which induces necessary that the typical inter electronic distance lowers with $Z$.
+In a similar fashion, we tried another definition of $\mu$ based on the work of Toulouse \textit{et.
+al.}\cite{TouColSav-JCP-05} which was proportional to $\frac{1}{r_s({\bf r})}$ and found that it leads to values of $\mu$ that are too large and therefore do not lead to significant improvement of the basis set convergence.
 
@@
 From the Figs \ref{fig:H2}, one can observe that i) all methods provide a near chemical accuracy from the AVTZ basis set, ii) the TC Hamiltonian obtained with the FROGG and that with $\mfrogg$ provide very similar results, iii) the values obtained with $\muuegav$ and $\murscav$ provide very similar results and improve accuracy over the FROGG for the AVDZ basis set, iv) a value of $\mu = 0.5$ provides a good description in the AVDZ basis set while remaining above the exact energy in the AVTZ basis set, which is not the case for $\mu=0.3$.
+It should also be noticed that when the system becomes strongly correlated (\textit{i.e.} when the bond is stretched), the TC eigenvalues, whatever the Jastrow chosen, do not show any pathological behaviour.
 
@@
 \section{Appendix}
-\subsection{Analytical form for the operator $\hat{K}_\mu(\bri{1},\bri{2}) $}
+\subsection{Analytical form for the operator $\hat{K}(\bri{1},\bri{2},\mu) $}
 \label{k_l_appendix}
-To compute the operators $\hat{K}_\mu(\bri{1},\bri{2})$ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
+To compute the operators $\hat{K}(\bri{1},\bri{2},\mu)$ one needs to compute first the gradient of $u(r_{12},\mu)$ with respect to $\bri{1}$ which reads 
 \begin{equation}
@@
 \end{equation}
-The non hermitian operators in $\hat{K}_\mu(\bri{1},\bri{2})$ contains 
+The non hermitian operators in $\hat{K}(\bri{1},\bri{2},\mu)$ contains 
 \begin{equation}
@@
 and as $\nabla_1 u(r_{12},\mu) = - \nabla_2 u(r_{12},\mu)$,   
-the total non hermitian operator in $\hat{K}_\mu(\bri{1},\bri{2})$ can be written as 
+the total non hermitian operator in $\hat{K}(\bri{1},\bri{2},\mu)$ can be written as 
 \begin{equation}
@@
 
-\subsection{Analytical form of $\hat{L}(\bri{1},\bri{2},\bri{3})$ and computation of related integrals }
+\subsection{Analytical form of $\hat{L}(\bri{1},\bri{2},\bri{3},\mu)$ and computation of related integrals }
 We need to compute the following integral 
@@
  \begin{aligned}
- &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
- +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
- +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} 
+ &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} = \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_2(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\
+ +& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_3(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} 
  \end{aligned}
@@
 \begin{equation}
- \hat{L}_1(\bri{1},\bri{2},\bri{3}) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
+ \hat{L}_1(\bri{1},\bri{2},\bri{3},\mu) = w_\mu(\bri{12}) w_\mu(\bri{13}) \bri{12} \cdot \bri{13}
 \end{equation}
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} = \\
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} = \\
  & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
@@
  \begin{aligned}
- &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n}  \\
- =& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
-+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n},  
+ &  \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n}  \\
+ =& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^y(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\  
++ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^z(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n},  
  \end{aligned}
@@
  \label{eq:l_1x}
-& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\  
  = & \int \dr{1} \dr{2} \dr{3} \phi_i(\bri{1}) \phi_j(\bri{2}) \phi_m(\bri{3}) w_{\mu}(r_{12}) w_{\mu}(r_{13}) \\ 
@@
  \label{eq:l_1x_2}
-& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\  
+& \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1^x(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\  
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) W_{mn}^x({\bf r}) W_{jl}^x({\bf r}),
@@
 \end{equation}
-Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3})$ is simply 
-\begin{equation}
- \begin{aligned}
- & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+Therefore, the matrix element of the $\hat{L}_1(\bri{1},\bri{2},\bri{3},\mu)$ is simply 
+\begin{equation}
+ \begin{aligned}
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}_1(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg),
@@
  \begin{aligned}
- & \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3})}{\phi_k \phi_l \phi_n} \\
+ & \matelem{\phi_i \phi_j \phi_m}{\hat{L}(\bri{1},\bri{2},\bri{3},\mu)}{\phi_k \phi_l \phi_n} \\
  = & \int \text{d}{\bf r} \phi_i({\bf r})  \phi_k({\bf r}) \bigg( W_{mn}^x({\bf r}) W_{jl}^x({\bf r}) + W_{mn}^y({\bf r}) W_{jl}^y({\bf r}) + W_{mn}^z({\bf r}) W_{jl}^z({\bf r})\bigg) \\

### 2021-01-29 dev/slat_rules_trans/htilde_matrix.irp.f
added some lapack diag for non hermitian matrix

@@ -76,9 +76,8 @@ END_PROVIDER
   character*1 :: JOBVL,JOBVR
   JOBVL = "V" ! computes the left  eigenvectors 
   JOBVR = "V" ! computes the right eigenvectors 
-  integer     :: n,lda,ldvl,ldvr,LWORK,INFO
+  integer     :: n
   double precision, allocatable :: A(:,:),WR(:),WI(:),Vl(:,:),VR(:,:)
-  double precision, allocatable :: WORK(:)
   integer :: i,j,k
   integer :: n_good
   integer, allocatable :: list_good(:), iorder(:)
@@ -86,28 +85,8 @@ END_PROVIDER
   ! Eigvalue(n) = WR(n) + i * WI(n)
   n = n_det
   allocate(A(n,n),WR(n),WI(n),VL(n,n),VR(n,n))
-  lda  = n
-  ldvl = n
-  ldvr = n
   A = htilde_matrix_elmt
-  allocate(WORK(1))
-  LWORK = -1 ! to ask for the optimal size of WORK
-  call dgeev('V','V',n,A,lda,WR,WI,VL,ldvl,VR,ldvr,WORK,LWORK,INFO)
-  if(INFO.gt.0)then
-   print*,'dgeev failed !!',INFO
-   stop
-  endif
-  LWORK = max(int(work(1)), 1) ! this is the optimal size of WORK 
-  deallocate(WORK)
-  allocate(WORK(LWORK))
-  ! Actual diagonalization 
-  A = htilde_matrix_elmt
-  call dgeev('V','V',n,A,lda,WR,WI,VL,ldvl,VR,ldvr,WORK,LWORK,INFO)
-  if(INFO.ne.0)then
-   print*,'dgeev failed !!',INFO
-   stop
-  endif
- 
+  call lapack_diag_non_sym(n,A,WR,WI,VL,VR)
   ! You track the real eigenvalues 
   n_good = 0
   do i = 1, n

### 2021-01-29 dev/slat_rules_trans/lapack_diag_non_hermit.irp.f

@@ -1,0 +1,33 @@
+subroutine lapack_diag_non_sym(n,A,WR,WI,VL,VR)
+ implicit none
+ integer, intent(in) :: n
+ double precision, intent(in) :: A(n,n)
+ double precision, intent(out):: WR(n),WI(n),VL(n,n),VR(n,n)
+  print*,'Computing the left/right eigenvectors ...'
+  character*1 :: JOBVL,JOBVR
+  JOBVL = "V" ! computes the left  eigenvectors 
+  JOBVR = "V" ! computes the right eigenvectors 
+  integer     :: lda,ldvl,ldvr,LWORK,INFO
+  double precision, allocatable :: WORK(:)
+  integer :: n_good
+  ! Eigvalue(n) = WR(n) + i * WI(n)
+  lda  = n
+  ldvl = n
+  ldvr = n
+  allocate(WORK(1))
+  LWORK = -1 ! to ask for the optimal size of WORK
+  call dgeev('V','V',n,A,lda,WR,WI,VL,ldvl,VR,ldvr,WORK,LWORK,INFO)
+  if(INFO.gt.0)then
+   print*,'dgeev failed !!',INFO
+   stop
+  endif
+  LWORK = max(int(work(1)), 1) ! this is the optimal size of WORK 
+  deallocate(WORK)
+  allocate(WORK(LWORK))
+  ! Actual diagonalization 
+  call dgeev('V','V',n,A,lda,WR,WI,VL,ldvl,VR,ldvr,WORK,LWORK,INFO)
+  if(INFO.ne.0)then
+   print*,'dgeev failed !!',INFO
+   stop
+  endif
+end 

### 2021-02-03 cusp_j/paper/revised/paper.tex
added revised

--- 2021-01-21 cusp_j/paper/submit/paper.tex
@@
 
+\newcommand{\corr}[1]{{\color{red} #1}}
+
 \begin{document}
@@
 
-Another approach to tackle the problems of WFT related to the electron cusp have been proposed by the F12 methods which introduce a function explicitly depending on the inter-electronic coordinate\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18} (called a Jastrow factor) to describe short-range correlation effects which are absent from the finite basis set.
+Another approach to tackle the problems of WFT related to the electron cusp have been proposed by the F12 methods which introduce a function explicitly depending on the inter-electronic coordinate\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18} (called a \corr{correlation} factor) to describe short-range correlation effects which are absent from the finite basis set.
 Thanks to strong orthogonality,
-all redundant correlation effects between the Jastrow factor and the basis set are projected out of the wave function, 
-and therefore the Jastrow factor only deals with correlation effects orthonormal to the basis set. 
+all redundant correlation effects between the \corr{correlation} factor and the basis set are projected out of the wave function, 
+and therefore the \corr{correlation} factor only deals with correlation effects orthonormal to the basis set. 
 The resulting F12 theories, mainly based on perturbation theory and coupled cluster theory, are therefore 
-extremely close to their parent WFT theory, with additional contributions involving two- and three-body terms resulting from the use of the Jastrow factor. 
-It is important to notice that because of the orthogonalization between the Jastrow and the basis set, 
+extremely close to their parent WFT theory, with additional contributions involving two- and three-body terms resulting from the use of the \corr{correlation} factor. 
+It is important to notice that because of the orthogonalization between the \corr{correlation} and the basis set, 
 the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and the parent theory in WFT.
@@
 
-An alternative point of view using a Jastrow factor is the so-called transcorrelated (TC) approach where the full effect of the Jastrow factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the Jastrow factor.
+An alternative point of view using a \corr{correlation} factor is the so-called transcorrelated (TC) approach where the full effect of the \corr{correlation} factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the \corr{correlation} factor.
+\corr{As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
 Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity.
@@
 The use of a TC Hamiltonian in the context of FCI-QMC has an important advantage: because the TC Hamiltonian already contains the effect of an elaborate Jastrow factor, the right-eigenvectors of the TC Hamiltonian are more compact and therefore the FCI-QMC procedure converges faster.
-This approach share common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions, 
+\corr{ This have been illustrated in the context of the Hubbard model\cite{DobLuoAla-PRB-19} for which Alavi \textit{et.
+al.} found that the weight of the Hartree-Fock Slater determinant in the right eigenvector of the TC Hamiltonian obtained with the Gutzwiller Ansatz\cite{Gutzwiller-PRL-63,BriRic-PRB-70}  significantly increases with respect to that in the eigenfunction of the usual Hubbard Hamiltonian.
+}
+The approach of Alavi \textit{et.
+al.} of Ref.
+\onlinecite{CohLuoGutDobTewAla-JCP-19} which uses a real-space Jastrow factor shares common points with that of Ten-No in the sense that they both use a fixed Jastrow factor and use a flexible form of wave functions,
 even though the FCIQMC is certainly more flexible than the linearised coupled cluster ansatz of Ten-No used in Ref. \onlinecite{HinTanTen-JCP-01}.
@@
 ii) the new Jastrow factor $u(r_{12};\mu)$ is more flexible than the FROGG as it is tuned by a unique parameter $\mu$ which determines both the depth of the hole and its typical range in $r_{12}$.
+
+\corr{
+It should be noticed that the method proposed here to generate a Jastrow factor based on an effective interaction is very general,
+as one can write                                                                          
+\begin{equation}
+ \label{def_general}
+ \deriv{u(r_{12})}{r_{12}}{} = \frac{h(r_{12})}{2},
+\end{equation}
+where $h(r_{12})$ is a general function satisfying
+\begin{equation}
+ \lim_{r_{12} \rightarrow 0} h(r_{12}) = 1.
+\end{equation}
+
+For instance, the Jastrow factor $u(r_{12},\mu)$ derived in Eq. (10) corresponds to the solution of Eq. \eqref{def_general} with $h(r_{12})  =   \text{erfc}(\mu r_{12})$. 
+There are of course as many solutions to Eq. \eqref{def_general} as there are functions $h(r_{12})$.
+An other interesting example is when $h(r_{12},\alpha) = \text{exp}(-\alpha      r_{12})$, which corresponds to an effective Yukawa          potential and yields to the following Jastrow factor
+\begin{equation}
+ \label{eq_yukawa}
+ u^{\text{Y}}(r_{12},\alpha) = \frac{1 - e^{-\alpha r_{12}}}{2 \alpha},
+\end{equation}
+which is nothing but the Slater type geminal (STG) originally introduced by Ten-No\cite{Ten-CPL-04,Ten-JCP-04,Ten-JCP-07} and widely used in the F12 theory.  
+Similarly the solution of Eq. \eqref{def_general} with $h(r_{12},\alpha) = \text{exp}\big(-(\beta r_{12})^2\big)$ gives the following        Jastrow factor
+\begin{equation}
+ \label{eq_gauss}
+ u^{\text{G}}(r_{12},\beta) = -\frac{\sqrt{\pi}\text{erfc}(\beta r_{12})}{4 \beta},
+\end{equation}
+which have a very similar form to that introduced by Tew \textit{et.
+al.} in Ref.
+\cite{Tew-Klo-JCP-05} and whose performance have been      tested in Ref.
+\onlinecite{JohHirTen-CPL-17} in the context of the F12 theory.
+Therefore, the generality of equation Eq.
+\eqref{def_general} can help the understanding between the analytical form of the Jastrow factors and the corresponding effective potential in the TC Hamiltonian.
+}
 
@@
 These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system, and therefore shows the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
+\corr{It should be noticed that the typical range of the FROGG can be tuned by varying the exponent of the Gaussian weight function involved in   the least-square fit of Eq.
+(9) of Ref.
+\cite{TenNo-CPL-00-a}.
+Increasing the exponent of the Gaussian weight function would probably lead   to a more short-range FROGG which would be more efficient to treat very dense systems such as the positive ions of the He isoelectronic series.
+}
 
@@
 The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and to explore the possibility of having a value of $\mu$ varying in space. 
+\corr{The latter can be considered as way to include some of the flexibility of the electron-electron-nucleus terms present in the Jastrow factor developed by Moskowitz \textit{et.
+al.}\cite{SchMos-JCP-90} and used by Alavi \textit{et.
+al.}\cite{CohLuoGutDobTewAla-JCP-19} in the context of the TC Hamiltonian.
+}
 
@@
 \end{equation}
-being the Dirac distribution. Threfore, one could be tempted to write that 
+being the Dirac distribution. Therefore, one could be tempted to write that 
 \begin{equation}
@@
 
-\bibliography{srDFT_SC}
+%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{89}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Bender}\ and\ \citenamefont
+  {Davidson}(1969)}]{bender}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+  {Bender}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+  {Davidson}},\ }\href {\doibase 10.1103/PhysRev.183.23} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {183}},\
+  \bibinfo {pages} {23} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huron}, \citenamefont {Malrieu},\ and\ \citenamefont
+  {Rancurel}(1973)}]{HurMalRan-JCP-73}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Huron}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Malrieu}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Rancurel}},\ }\href
+  {\doibase 10.1063/1.1679199} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {5745}
+  (\bibinfo {year} {1973})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Buenker}\ and\ \citenamefont
+  {Peyerimholf}(1974)}]{buenker1}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {Buenker}}\ and\ \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Peyerimholf}},\ }\href {https://doi.org/10.1007/BF02394557} {\bibfield
+  {journal} {\bibinfo  {journal} {Theor. Chim. Acta}\ }\textbf {\bibinfo
+  {volume} {35}},\ \bibinfo {pages} {33} (\bibinfo {year} {1974})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Buenker}, \citenamefont {Peyerimholf},\ and\
+  \citenamefont {Bruna}(1981)}]{buenker-book}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {Buenker}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Peyerimholf}}, \ and\ \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont
+  {Bruna}},\ }\href@noop {} {\emph {\bibinfo {title} {Comp. Theor. Org.
+  Chem.}}}\ (\bibinfo  {publisher} {Reidel},\ \bibinfo {address} {Dordrecht},\
+  \bibinfo {year} {1981})\ p.~\bibinfo {pages} {55}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Evangelisti}, \citenamefont {Daudey},\ and\
+  \citenamefont {Malrieu}(1983)}]{three_class_CIPSI}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Evangelisti}}, \bibinfo {author} {\bibfnamefont {J.-P.}\ \bibnamefont
+  {Daudey}}, \ and\ \bibinfo {author} {\bibfnamefont {J.-P.}\ \bibnamefont
+  {Malrieu}},\ }\href {\doibase https://doi.org/10.1016/0301-0104(83)85011-3}
+  {\bibfield  {journal} {\bibinfo  {journal} {Chemical Physics}\ }\textbf
+  {\bibinfo {volume} {75}},\ \bibinfo {pages} {91 } (\bibinfo {year}
+  {1983})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Harrison}(1991)}]{harrison}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {Harrison}},\ }\href {\doibase 10.1063/1.460537} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {94}},\ \bibinfo {pages} {5021} (\bibinfo {year}
+  {1991})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Angeli}\ \emph {et~al.}(1997)\citenamefont {Angeli},
+  \citenamefont {Cimiraglia}, \citenamefont {Persico},\ and\ \citenamefont
+  {Toniolo}}]{cele_cipsi_3_spaces}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Angeli}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Cimiraglia}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Persico}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toniolo}},\ }\href
+  {https://doi.org/10.1007/s002140050278} {\bibfield  {journal} {\bibinfo
+  {journal} {Theo. Chem. Acc.}\ }\textbf {\bibinfo {volume} {98}},\ \bibinfo
+  {pages} {57} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Angeli}\ and\ \citenamefont
+  {Persico}(1997)}]{cele_cipsi_zeroth_order}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Angeli}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Persico}},\ }\href {https://doi.org/10.1007/s002140050285} {\bibfield
+  {journal} {\bibinfo  {journal} {Theor. Chem. Acc.}\ }\textbf {\bibinfo
+  {volume} {98}},\ \bibinfo {pages} {117} (\bibinfo {year} {1997})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Giner}, \citenamefont {Scemama},\ and\ \citenamefont
+  {Caffarel}(2013)}]{GinSceCaf-CJC-13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Giner}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scemama}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Caffarel}},\ }\href
+  {\doibase 10.1139/cjc-2013-0017} {\bibfield  {journal} {\bibinfo  {journal}
+  {Can. J. Chem.}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo {pages} {879}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Giner}, \citenamefont {Scemama},\ and\ \citenamefont
+  {Caffarel}(2015)}]{GinSceCaf-JCP-15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Giner}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scemama}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Caffarel}},\ }\href
+  {\doibase 10.1063/1.4905528} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {142}},\ \bibinfo {pages} {044115}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sharma}\ \emph {et~al.}(2017)\citenamefont {Sharma},
+  \citenamefont {Holmes}, \citenamefont {Jeanmairet}, \citenamefont {Alavi},\
+  and\ \citenamefont {Umrigar}}]{ShaHolJeaAlaUmr-JCTC-17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Sharma}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Holmes}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Jeanmairet}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {C.~J.}\ \bibnamefont {Umrigar}},\ }\href {\doibase
+  10.1021/acs.jctc.6b01028} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Theory Comput.}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages}
+  {1595} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Booth}, \citenamefont {Thom},\ and\ \citenamefont
+  {Alavi}(2009)}]{BooThoAla-JCP-09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont
+  {Booth}}, \bibinfo {author} {\bibfnamefont {A.~J.~W.}\ \bibnamefont {Thom}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}},\ }\href
+  {https://doi.org/10.1063/1.3193710} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {{131}}} (\bibinfo
+  {year} {{2009}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Booth}\ and\ \citenamefont
+  {Alavi}(2010)}]{BooAla-JCP-10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont
+  {Booth}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}},\
+  }\href {\doibase 10.1063/1.3407895} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {132}},\ \bibinfo
+  {pages} {174104} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Booth}\ \emph {et~al.}(2011)\citenamefont {Booth},
+  \citenamefont {Cleland}, \citenamefont {Thom},\ and\ \citenamefont
+  {Alavi}}]{BooCleThoAla-JCP-11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~H.}\ \bibnamefont
+  {Booth}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cleland}},
+  \bibinfo {author} {\bibfnamefont {A.~J.~W.}\ \bibnamefont {Thom}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}},\ }\href
+  {https://doi.org/10.1063/1.3624383} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {135}},\ \bibinfo
+  {pages} {084104} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ghanem}, \citenamefont {Lozovoi},\ and\ \citenamefont
+  {Alavi}(2019)}]{GhaLozAla-JCP-19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Ghanem}}, \bibinfo {author} {\bibfnamefont {A.~Y.}\ \bibnamefont {Lozovoi}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}},\ }\href
+  {\doibase 10.1063/1.5134006} {\bibfield  {journal} {\bibinfo  {journal} {The
+  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {151}},\ \bibinfo
+  {pages} {224108} (\bibinfo {year} {2019})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.5134006}
+  {https://doi.org/10.1063/1.5134006} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vitale}, \citenamefont {Alavi},\ and\ \citenamefont
+  {Kats}(2020)}]{VitAlaKat-JCTC-20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Vitale}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}}, \
+  and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kats}},\ }\href
+  {\doibase 10.1021/acs.jctc.0c00470} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Chemical Theory and Computation}\ }\textbf {\bibinfo
+  {volume} {16}},\ \bibinfo {pages} {5621} (\bibinfo {year} {2020})},\ \bibinfo
+  {note} {pMID: 32786911},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/acs.jctc.0c00470}
+  {https://doi.org/10.1021/acs.jctc.0c00470} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chan}\ and\ \citenamefont
+  {Sharma}(2011)}]{ChaSha-AR-11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~K.-L.}\
+  \bibnamefont {Chan}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Sharma}},\ }\href {\doibase 10.1146/annurev-physchem-032210-103338}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Physical
+  Chemistry}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {465}
+  (\bibinfo {year} {2011})},\ \bibinfo {note} {pMID: 21219144},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1146/annurev-physchem-032210-103338}
+  {https://doi.org/10.1146/annurev-physchem-032210-103338} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Baiardi}\ and\ \citenamefont
+  {Reiher}(2020)}]{BaiRei-JCP-20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Baiardi}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Reiher}},\ }\href {\doibase 10.1063/1.5129672} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {152}},\ \bibinfo {pages} {040903} (\bibinfo {year} {2020})},\
+  \Eprint {http://arxiv.org/abs/https://doi.org/10.1063/1.5129672}
+  {https://doi.org/10.1063/1.5129672} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kato}(1957)}]{Kat-CPAM-57}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kato}},\ }\href {\doibase 10.1002/cpa.3160100201} {\bibfield  {journal}
+  {\bibinfo  {journal} {Comm. Pure Appl. Math.}\ }\textbf {\bibinfo {volume}
+  {10}},\ \bibinfo {pages} {151} (\bibinfo {year} {1957})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Tew}(2008)}]{Tew-JCP-08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Tew}},\ }\href {\doibase 10.1063/1.2945900} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {129}},\ \bibinfo {pages} {014104} (\bibinfo {year} {2008})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hylleraas}(1929)}]{Hyl-ZP-29}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~A.}\ \bibnamefont
+  {Hylleraas}},\ }\href {\doibase 10.1007/BF01375457} {\bibfield  {journal}
+  {\bibinfo  {journal} {Z. Phys.}\ }\textbf {\bibinfo {volume} {54}},\ \bibinfo
+  {pages} {347} (\bibinfo {year} {1929})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kutzelnigg}(1985)}]{Kut-TCA-85}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Kutzelnigg}},\ }\href {\doibase 10.1007/BF00527669} {\bibfield  {journal}
+  {\bibinfo  {journal} {Theor. Chim. Acta}\ }\textbf {\bibinfo {volume} {68}},\
+  \bibinfo {pages} {445} (\bibinfo {year} {1985})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kutzelnigg}\ and\ \citenamefont
+  {Klopper}(1991)}]{KutKlo-JCP-91}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Kutzelnigg}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Klopper}},\ }\href {\doibase 10.1063/1.459921} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {94}},\
+  \bibinfo {pages} {1985} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Noga}\ and\ \citenamefont
+  {Kutzelnigg}(1994)}]{NogKut-JCP-94}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Noga}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Kutzelnigg}},\ }\href {\doibase 10.1063/1.468266} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {101}},\
+  \bibinfo {pages} {7738} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Savin}(1995)}]{Sav-INC-95}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Savin}},\ }in\ \href {\doibase 10.1142/9789812830586_0004} {\emph {\bibinfo
+  {booktitle} {Recent Advances in Density Functional Theory}}},\ \bibinfo
+  {editor} {edited by\ \bibinfo {editor} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Chong}}}\ (\bibinfo  {publisher} {World Scientific},\ \bibinfo {year}
+  {1995})\ pp.\ \bibinfo {pages} {129--153}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Toulouse}, \citenamefont {Colonna},\ and\
+  \citenamefont {Savin}(2004)}]{TouColSav-PRA-04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Colonna}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}},\ }\href
+  {\doibase 10.1103/PhysRevA.70.062505} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {70}},\ \bibinfo
+  {pages} {062505} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gori-Giorgi}\ and\ \citenamefont
+  {Savin}(2006)}]{GorSav-PRA-06}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Gori-Giorgi}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Savin}},\ }\href {\doibase 10.1103/PhysRevA.73.032506} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {73}},\
+  \bibinfo {pages} {032506} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Franck}\ \emph {et~al.}(2015)\citenamefont {Franck},
+  \citenamefont {Mussard}, \citenamefont {Luppi},\ and\ \citenamefont
+  {Toulouse}}]{FraMusLupTou-JCP-15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Franck}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Mussard}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Luppi}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},\ }\href {\doibase
+  10.1063/1.4907920} {\bibfield  {journal} {\bibinfo  {journal} {J. Chem.
+  Phys.}\ }\textbf {\bibinfo {volume} {142}},\ \bibinfo {pages} {074107}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {\'Angy\'an}\ \emph {et~al.}(2005)\citenamefont
+  {\'Angy\'an}, \citenamefont {Gerber}, \citenamefont {Savin},\ and\
+  \citenamefont {Toulouse}}]{AngGerSavTou-PRA-05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~G.}\ \bibnamefont
+  {\'Angy\'an}}, \bibinfo {author} {\bibfnamefont {I.~C.}\ \bibnamefont
+  {Gerber}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},\ }\href
+  {\doibase 10.1103/PhysRevA.72.012510} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {72}},\ \bibinfo
+  {pages} {012510} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goll}, \citenamefont {Werner},\ and\ \citenamefont
+  {Stoll}(2005)}]{GolWerSto-PCCP-05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Goll}}, \bibinfo {author} {\bibfnamefont {H.-J.}\ \bibnamefont {Werner}}, \
+  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Stoll}},\ }\href
+  {\doibase 10.1039/B509242F} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Chem. Chem. Phys.}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
+  {3917} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Toulouse}\ \emph {et~al.}(2009)\citenamefont
+  {Toulouse}, \citenamefont {Gerber}, \citenamefont {Jansen}, \citenamefont
+  {Savin},\ and\ \citenamefont {\'Angy\'an}}]{TouGerJanSavAng-PRL-09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}}, \bibinfo {author} {\bibfnamefont {I.~C.}\ \bibnamefont
+  {Gerber}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Jansen}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.~G.}\ \bibnamefont {\'Angy\'an}},\ }\href
+  {\doibase 10.1103/PhysRevLett.102.096404} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo
+  {pages} {096404} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Janesko}, \citenamefont {Henderson},\ and\
+  \citenamefont {Scuseria}(2009)}]{JanHenScu-JCP-09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont
+  {Janesko}}, \bibinfo {author} {\bibfnamefont {T.~M.}\ \bibnamefont
+  {Henderson}}, \ and\ \bibinfo {author} {\bibfnamefont {G.~E.}\ \bibnamefont
+  {Scuseria}},\ }\href {\doibase 10.1063/1.3090814} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {130}},\
+  \bibinfo {pages} {081105} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Toulouse}\ \emph {et~al.}(2011)\citenamefont
+  {Toulouse}, \citenamefont {Zhu}, \citenamefont {Savin}, \citenamefont
+  {Jansen},\ and\ \citenamefont {\'Angy\'an}}]{TouZhuSavJanAng-JCP-11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Zhu}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {Jansen}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.~G.}\ \bibnamefont {\'Angy\'an}},\ }\href {\doibase
+  10.1063/1.3626551} {\bibfield  {journal} {\bibinfo  {journal} {J. Chem.
+  Phys.}\ }\textbf {\bibinfo {volume} {135}},\ \bibinfo {pages} {084119}
+  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mussard}\ \emph {et~al.}(2015)\citenamefont
+  {Mussard}, \citenamefont {Reinhardt}, \citenamefont {\'Angy\'an},\ and\
+  \citenamefont {Toulouse}}]{MusReiAngTou-JCP-15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Mussard}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Reinhardt}},
+  \bibinfo {author} {\bibfnamefont {J.~G.}\ \bibnamefont {\'Angy\'an}}, \ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},\ }\href
+  {\doibase 10.1063/1.4918710} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {142}},\ \bibinfo {pages} {154123}
+  (\bibinfo {year} {2015})},\ \bibinfo {note} {erratum: J. Chem. Phys. {\bf
+  142}, 219901 (2015)}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kalai}\ and\ \citenamefont
+  {Toulouse}(2018)}]{KalTou-JCP-18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Kalai}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}},\ }\href {\doibase 10.1063/1.5025561} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {148}},\
+  \bibinfo {pages} {164105} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kalai}, \citenamefont {Mussard},\ and\ \citenamefont
+  {Toulouse}(2019)}]{KalMusTou-JCP-19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Kalai}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Mussard}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},\ }\href
+  {\doibase 10.1063/1.5108536} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {151}},\ \bibinfo {pages} {074102}
+  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Leininger}\ \emph {et~al.}(1997)\citenamefont
+  {Leininger}, \citenamefont {Stoll}, \citenamefont {Werner},\ and\
+  \citenamefont {Savin}}]{LeiStoWerSav-CPL-97}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Leininger}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Stoll}},
+  \bibinfo {author} {\bibfnamefont {H.-J.}\ \bibnamefont {Werner}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}},\ }\href
+  {\doibase 10.1016/S0009-2614(97)00758-6} {\bibfield  {journal} {\bibinfo
+  {journal} {Chem. Phys. Lett.}\ }\textbf {\bibinfo {volume} {{275}}},\
+  \bibinfo {pages} {151} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fromager}, \citenamefont {Toulouse},\ and\
+  \citenamefont {Jensen}(2007)}]{FroTouJen-JCP-07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Fromager}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},
+  \ and\ \bibinfo {author} {\bibfnamefont {H.~J.~A.}\ \bibnamefont {Jensen}},\
+  }\href {\doibase 10.1063/1.2566459} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {126}},\ \bibinfo
+  {pages} {074111} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fromager}, \citenamefont {Cimiraglia},\ and\
+  \citenamefont {Jensen}(2010)}]{FroCimJen-PRA-10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Fromager}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Cimiraglia}}, \ and\ \bibinfo {author} {\bibfnamefont {H.~J.~A.}\
+  \bibnamefont {Jensen}},\ }\href {\doibase 10.1103/PhysRevA.81.024502}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo
+  {volume} {81}},\ \bibinfo {pages} {024502} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hedeg{\aa}rd}\ \emph {et~al.}(2015)\citenamefont
+  {Hedeg{\aa}rd}, \citenamefont {Knecht}, \citenamefont {Kielberg},
+  \citenamefont {Jensen},\ and\ \citenamefont
+  {Reiher}}]{HedKneKieJenRei-JCP-15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~D.}\ \bibnamefont
+  {Hedeg{\aa}rd}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Knecht}}, \bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
+  {Kielberg}}, \bibinfo {author} {\bibfnamefont {H.~J.~A.}\ \bibnamefont
+  {Jensen}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Reiher}},\ }\href {\doibase 10.1063/1.4922295} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {142}},\
+  \bibinfo {pages} {224108} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hedeg{\aa}rd}, \citenamefont {Toulouse},\ and\
+  \citenamefont {Jensen}(2018)}]{HedTouJen-JCP-18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~D.}\ \bibnamefont
+  {Hedeg{\aa}rd}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}}, \ and\ \bibinfo {author} {\bibfnamefont {H.~J.~A.}\ \bibnamefont
+  {Jensen}},\ }\href {\doibase 10.1063/1.5013306} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {148}},\
+  \bibinfo {pages} {214103} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fert{\'e}}, \citenamefont {Giner},\ and\
+  \citenamefont {Toulouse}(2019)}]{FerGinTou-JCP-18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Fert{\'e}}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Giner}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Toulouse}},\ }\href
+  {\doibase 10.1063/1.5082638} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {150}},\ \bibinfo {pages} {084103}
+  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mussard}\ and\ \citenamefont
+  {Toulouse}(2017)}]{MusTou-MP-17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Mussard}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}},\ }\href {\doibase 10.1080/00268976.2016.1213910} {\bibfield
+  {journal} {\bibinfo  {journal} {Mol. Phys.}\ }\textbf {\bibinfo {volume}
+  {115}},\ \bibinfo {pages} {161} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2012)}]{Ten-TCA-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase 10.1007/s00214-011-1070-1} {\bibfield  {journal}
+  {\bibinfo  {journal} {Theor. Chem. Acc.}\ }\textbf {\bibinfo {volume}
+  {131}},\ \bibinfo {pages} {1070} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ten-no}\ and\ \citenamefont
+  {Noga}(2012)}]{TenNog-WIREs-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Noga}},\
+  }\href {\doibase 10.1002/wcms.68} {\bibfield  {journal} {\bibinfo  {journal}
+  {WIREs Comput. Mol. Sci.}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo
+  {pages} {114} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hattig}\ \emph {et~al.}(2012)\citenamefont {Hattig},
+  \citenamefont {Klopper}, \citenamefont {Kohn},\ and\ \citenamefont
+  {Tew}}]{HatKloKohTew-CR-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Hattig}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Klopper}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kohn}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {D.~P.}\ \bibnamefont {Tew}},\ }\href {\doibase
+  10.1021/cr200168z} {\bibfield  {journal} {\bibinfo  {journal} {Chem. Rev.}\
+  }\textbf {\bibinfo {volume} {112}},\ \bibinfo {pages} {4} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kong}, \citenamefont {Bischo},\ and\ \citenamefont
+  {Valeev}(2012)}]{KonBisVal-CR-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Kong}}, \bibinfo {author} {\bibfnamefont {F.~A.}\ \bibnamefont {Bischo}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Valeev}},\
+  }\href {\doibase 10.1021/cr200204r} {\bibfield  {journal} {\bibinfo
+  {journal} {Chem. Rev.}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo {pages}
+  {75} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gr\"uneis}\ \emph {et~al.}(2017)\citenamefont
+  {Gr\"uneis}, \citenamefont {Hirata}, \citenamefont {Ohnishi},\ and\
+  \citenamefont {Ten-no}}]{GruHirOhnTen-JCP-17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Gr\"uneis}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Hirata}},
+  \bibinfo {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {Ohnishi}}, \ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Ten-no}},\ }\href
+  {\doibase 10.1063/1.4976974} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Phys.}\ }\textbf {\bibinfo {volume} {146}},\ \bibinfo {pages} {080901}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ma}\ and\ \citenamefont
+  {Werner}(2018)}]{MaWer-WIREs-18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
+  {Ma}}\ and\ \bibinfo {author} {\bibfnamefont {H.-J.}\ \bibnamefont
+  {Werner}},\ }\href {\doibase 10.1002/wcms.1371} {\bibfield  {journal}
+  {\bibinfo  {journal} {WIREs Comput. Mol. Sci.}\ }\textbf {\bibinfo {volume}
+  {8}},\ \bibinfo {pages} {e1371} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hirschfelder}(1963)}]{Hirschfelder-JCP-63}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~O.}\ \bibnamefont
+  {Hirschfelder}},\ }\href {\doibase 10.1063/1.1734157} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {39}},\ \bibinfo {pages} {3145} (\bibinfo {year}
+  {1963})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Boys}\ and\ \citenamefont
+  {Handy}(1969)}]{BoyHan-PRSLA-69}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~S.}\ \bibnamefont
+  {Boys}}\ and\ \bibinfo {author} {\bibfnamefont {C.~N.}\ \bibnamefont
+  {Handy}},\ }\href {\doibase 10.1098/rspa.1969.0038} {\bibfield  {journal}
+  {\bibinfo  {journal} {Proc. R. Soc. Lond. A.}\ }\textbf {\bibinfo {volume}
+  {309}},\ \bibinfo {pages} {209} (\bibinfo {year} {1969})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Boys}, \citenamefont {Handy},\ and\ \citenamefont
+  {Linnett}(1969{\natexlab{a}})}]{BoyHanLin-1-PRSLA-69}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~S.}\ \bibnamefont
+  {Boys}}, \bibinfo {author} {\bibfnamefont {C.~N.}\ \bibnamefont {Handy}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont {Linnett}},\
+  }\href {\doibase 10.1098/rspa.1969.0061} {\bibfield  {journal} {\bibinfo
+  {journal} {Proc. R. Soc. Lond. A.}\ }\textbf {\bibinfo {volume} {310}},\
+  \bibinfo {pages} {43} (\bibinfo {year} {1969}{\natexlab{a}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Boys}, \citenamefont {Handy},\ and\ \citenamefont
+  {Linnett}(1969{\natexlab{b}})}]{BoyHanLin-2-PRSLA-69}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~S.}\ \bibnamefont
+  {Boys}}, \bibinfo {author} {\bibfnamefont {C.~N.}\ \bibnamefont {Handy}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont {Linnett}},\
+  }\href {\doibase 10.1098/rspa.1969.0062} {\bibfield  {journal} {\bibinfo
+  {journal} {Proc. R. Soc. Lond. A.}\ }\textbf {\bibinfo {volume} {310}},\
+  \bibinfo {pages} {63} (\bibinfo {year} {1969}{\natexlab{b}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Handy}(1971)}]{Handy-MolPhys-71}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~C.}\ \bibnamefont
+  {Handy}},\ }\href {\doibase 10.1080/00268977100101961} {\bibfield  {journal}
+  {\bibinfo  {journal} {Molecular Physics}\ }\textbf {\bibinfo {volume} {21}},\
+  \bibinfo {pages} {817} (\bibinfo {year} {1971})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1080/00268977100101961}
+  {https://doi.org/10.1080/00268977100101961} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2000{\natexlab{a}})}]{TenNo-CPL-00-a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase https://doi.org/10.1016/S0009-2614(00)01066-6}
+  {\bibfield  {journal} {\bibinfo  {journal} {Chemical Physics Letters}\
+  }\textbf {\bibinfo {volume} {330}},\ \bibinfo {pages} {169 } (\bibinfo {year}
+  {2000}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hino}, \citenamefont {Tanimura},\ and\ \citenamefont
+  {Ten-no}(2001)}]{HinTanTen-JCP-01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Hino}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Tanimura}}, \
+  and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Ten-no}},\ }\href
+  {\doibase 10.1063/1.1408299} {\bibfield  {journal} {\bibinfo  {journal} {The
+  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {115}},\ \bibinfo
+  {pages} {7865} (\bibinfo {year} {2001})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.1408299}
+  {https://doi.org/10.1063/1.1408299} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hino}, \citenamefont {Tanimura},\ and\ \citenamefont
+  {Ten-no}(2002)}]{HinTanTen-CPL-02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+  {Hino}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Tanimura}}, \
+  and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Ten-no}},\ }\href
+  {\doibase https://doi.org/10.1016/S0009-2614(02)00042-8} {\bibfield
+  {journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
+  {volume} {353}},\ \bibinfo {pages} {317 } (\bibinfo {year}
+  {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2000{\natexlab{b}})}]{TenNo-CPL-00-b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase 10.1016/S0009-2614(00)01067-8} {\bibfield
+  {journal} {\bibinfo  {journal} {Chem. Phys. Lett.}\ }\textbf {\bibinfo
+  {volume} {330}},\ \bibinfo {pages} {175} (\bibinfo {year}
+  {2000}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ten-no}\ and\ \citenamefont
+  {Manby}(2003)}]{TenMan-JCP-03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}}\ and\ \bibinfo {author} {\bibfnamefont {F.~R.}\ \bibnamefont
+  {Manby}},\ }\href {\doibase 10.1063/1.1600431} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {119}},\
+  \bibinfo {pages} {5358} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Umezawa}\ and\ \citenamefont
+  {Tsuneyuki}(2003)}]{UmeTsu-JCP-03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Umezawa}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Tsuneyuki}},\ }\href {\doibase 10.1063/1.1617274} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {119}},\ \bibinfo {pages} {10015} (\bibinfo {year} {2003})},\
+  \Eprint {http://arxiv.org/abs/https://doi.org/10.1063/1.1617274}
+  {https://doi.org/10.1063/1.1617274} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Umezawa}\ \emph {et~al.}(2005)\citenamefont
+  {Umezawa}, \citenamefont {Tsuneyuki}, \citenamefont {Ohno}, \citenamefont
+  {Shiraishi},\ and\ \citenamefont {Chikyow}}]{UmeTsuOhnShiChi-JCP-05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Umezawa}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Tsuneyuki}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohno}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Shiraishi}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Chikyow}},\ }\href {\doibase
+  10.1063/1.1924597} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+  Chemical Physics}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
+  {224101} (\bibinfo {year} {2005})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.1924597}
+  {https://doi.org/10.1063/1.1924597} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Luo}(2010)}]{Luo-JCP-10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Luo}},\ }\href {\doibase 10.1063/1.3505037} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {133}},\ \bibinfo
+  {pages} {154109} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Luo}(2011)}]{Luo-JCP-11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Luo}},\ }\href {\doibase 10.1063/1.3607990} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {135}},\ \bibinfo {pages} {024109} (\bibinfo {year} {2011})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.3607990}
+  {https://doi.org/10.1063/1.3607990} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yanai}\ and\ \citenamefont
+  {Shiozaki}(2012)}]{YanShi-JCP-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Yanai}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Shiozaki}},\ }\href {\doibase 10.1063/1.3688225} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {136}},\
+  \bibinfo {pages} {084107} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Neuscamman}, \citenamefont {Yanai},\ and\
+  \citenamefont {Chan}(2010)}]{NeuYanCha-MolPhys-10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Neuscamman}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Yanai}}, \
+  and\ \bibinfo {author} {\bibfnamefont {G.~K.-L.}\ \bibnamefont {Chan}},\
+  }\href {\doibase 10.1080/01442351003620540} {\bibfield  {journal} {\bibinfo
+  {journal} {International Reviews in Physical Chemistry}\ }\textbf {\bibinfo
+  {volume} {29}},\ \bibinfo {pages} {231} (\bibinfo {year} {2010})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1080/01442351003620540}
+  {https://doi.org/10.1080/01442351003620540} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Motta}\ \emph {et~al.}(2020)\citenamefont {Motta},
+  \citenamefont {Gujarati}, \citenamefont {Rice}, \citenamefont {Kumar},
+  \citenamefont {Masteran}, \citenamefont {Latone}, \citenamefont {Lee},
+  \citenamefont {Valeev},\ and\ \citenamefont {Takeshita}}]{ValTak-PCCP-20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Motta}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Gujarati}},
+  \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont {Rice}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Kumar}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Masteran}}, \bibinfo {author}
+  {\bibfnamefont {J.~A.}\ \bibnamefont {Latone}}, \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont
+  {E.~F.}\ \bibnamefont {Valeev}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {T.~Y.}\ \bibnamefont {Takeshita}},\ }\href {\doibase 10.1039/D0CP04106H}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Chem. Chem. Phys.}\
+  }\textbf {\bibinfo {volume} {22}},\ \bibinfo {pages} {24270} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ochi}\ \emph {et~al.}(2012)\citenamefont {Ochi},
+  \citenamefont {Sodeyama}, \citenamefont {Sakuma},\ and\ \citenamefont
+  {Tsuneyuki}}]{OchSodSakTsu-JCP-12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Ochi}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sodeyama}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sakuma}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Tsuneyuki}},\ }\href {\doibase
+  10.1063/1.3689440} {\bibfield  {journal} {\bibinfo  {journal} {J. Chem.
+  Phys.}\ }\textbf {\bibinfo {volume} {136}},\ \bibinfo {pages} {094108}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ochi}\ and\ \citenamefont
+  {Tsuneyuki}(2014)}]{OchTsu-JCTC-14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Ochi}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Tsuneyuki}},\ }\href {\doibase 10.1021/ct500485b} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Theory Comput.}\ }\textbf {\bibinfo {volume}
+  {10}},\ \bibinfo {pages} {4098} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ochi}\ and\ \citenamefont
+  {Tsuneyuki}(2015)}]{OchTsu-CPL-15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Ochi}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Tsuneyuki}},\ }\href {\doibase 10.1016/j.cplett.2015.01.009} {\bibfield
+  {journal} {\bibinfo  {journal} {Chem. Phys. Lett.}\ }\textbf {\bibinfo
+  {volume} {621}},\ \bibinfo {pages} {177} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ochi}\ \emph {et~al.}(2016)\citenamefont {Ochi},
+  \citenamefont {Yamamoto}, \citenamefont {Arita},\ and\ \citenamefont
+  {Tsuneyuki}}]{OchYamAriTsu-JCP-16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Ochi}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Yamamoto}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Arita}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Tsuneyuki}},\ }\href {\doibase
+  10.1063/1.4943117} {\bibfield  {journal} {\bibinfo  {journal} {J. Chem.
+  Phys.}\ }\textbf {\bibinfo {volume} {144}},\ \bibinfo {pages} {104109}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Imamura}\ and\ \citenamefont
+  {Scuseria}(2003)}]{ImaScu-JCP-03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Imamura}}\ and\ \bibinfo {author} {\bibfnamefont {G.~E.}\ \bibnamefont
+  {Scuseria}},\ }\href {\doibase 10.1063/1.1535442} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {118}},\
+  \bibinfo {pages} {2464} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Umezawa}\ and\ \citenamefont
+  {Chikyow}(2006)}]{UmeChi-PRA-06}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Umezawa}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Chikyow}},\ }\href {\doibase 10.1103/PhysRevA.73.062116} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {73}},\ \bibinfo {pages} {062116} (\bibinfo {year} {2006})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Umezawa}(2017)}]{Umezawa-JCP-17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Umezawa}},\ }\href {\doibase 10.1063/1.5001260} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {147}},\
+  \bibinfo {pages} {104104} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cohen}\ \emph {et~al.}(2019)\citenamefont {Cohen},
+  \citenamefont {Luo}, \citenamefont {Guther}, \citenamefont {Dobrautz},
+  \citenamefont {Tew},\ and\ \citenamefont
+  {Alavi}}]{CohLuoGutDobTewAla-JCP-19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Cohen}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Luo}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Guther}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Dobrautz}}, \bibinfo {author}
+  {\bibfnamefont {D.~P.}\ \bibnamefont {Tew}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Alavi}},\ }\href {\doibase
+  10.1063/1.5116024} {\bibfield  {journal} {\bibinfo  {journal} {The Journal of
+  Chemical Physics}\ }\textbf {\bibinfo {volume} {151}},\ \bibinfo {pages}
+  {061101} (\bibinfo {year} {2019})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.5116024}
+  {https://doi.org/10.1063/1.5116024} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schmidt}\ and\ \citenamefont
+  {Moskowitz}(1990)}]{SchMos-JCP-90}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~E.}\ \bibnamefont
+  {Schmidt}}\ and\ \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont
+  {Moskowitz}},\ }\href {\doibase 10.1063/1.458750} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {93}},\ \bibinfo {pages} {4172} (\bibinfo {year} {1990})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.458750}
+  {https://doi.org/10.1063/1.458750} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dobrautz}, \citenamefont {Luo},\ and\ \citenamefont
+  {Alavi}(2019)}]{DobLuoAla-PRB-19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Dobrautz}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Luo}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alavi}},\ }\href
+  {\doibase 10.1103/PhysRevB.99.075119} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {99}},\ \bibinfo
+  {pages} {075119} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gutzwiller}(1963)}]{Gutzwiller-PRL-63}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~C.}\ \bibnamefont
+  {Gutzwiller}},\ }\href {\doibase 10.1103/PhysRevLett.10.159} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {10}},\ \bibinfo {pages} {159} (\bibinfo {year} {1963})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Brinkman}\ and\ \citenamefont
+  {Rice}(1970)}]{BriRic-PRB-70}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
+  {Brinkman}}\ and\ \bibinfo {author} {\bibfnamefont {T.~M.}\ \bibnamefont
+  {Rice}},\ }\href {\doibase 10.1103/PhysRevB.2.4302} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {2}},\
+  \bibinfo {pages} {4302} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hylleraas}(1964)}]{Hylleraas-AdvQChem-64}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~A.}\ \bibnamefont
+  {Hylleraas}}\ }(\bibinfo  {publisher} {Academic Press},\ \bibinfo {year}
+  {1964})\ pp.\ \bibinfo {pages} {1 -- 33}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2004{\natexlab{a}})}]{Ten-CPL-04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase 10.1016/j.cplett.2004.09.041} {\bibfield
+  {journal} {\bibinfo  {journal} {Chem. Phys. Lett.}\ }\textbf {\bibinfo
+  {volume} {398}},\ \bibinfo {pages} {56} (\bibinfo {year}
+  {2004}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2004{\natexlab{b}})}]{Ten-JCP-04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase 10.1063/1.1757439} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {121}},\
+  \bibinfo {pages} {117} (\bibinfo {year} {2004}{\natexlab{b}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ten-no}(2007)}]{Ten-JCP-07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Ten-no}},\ }\href {\doibase 10.1063/1.2403853} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {126}},\
+  \bibinfo {pages} {014108} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tew}\ and\ \citenamefont
+  {Klopper}(2005)}]{Tew-Klo-JCP-05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Tew}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Klopper}},\
+  }\href {\doibase 10.1063/1.1999632} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {123}},\ \bibinfo
+  {pages} {074101} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Johnson}, \citenamefont {Hirata},\ and\ \citenamefont
+  {Ten-no}(2017)}]{JohHirTen-CPL-17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+  {Johnson}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Hirata}}, \
+  and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Ten-no}},\ }\href
+  {\doibase 10.1016/j.cplett.2017.02.072} {\bibfield  {journal} {\bibinfo
+  {journal} {Chem. Phys. Lett.}\ }\textbf {\bibinfo {volume} {683}},\ \bibinfo
+  {pages} {247} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Garniron}\ \emph {et~al.}(2019)\citenamefont
+  {Garniron}, \citenamefont {Gasperich}, \citenamefont {Applencourt},
+  \citenamefont {Benali}, \citenamefont {Fert{\'e}}, \citenamefont {Paquier},
+  \citenamefont {Pradines}, \citenamefont {Assaraf}, \citenamefont {Reinhardt},
+  \citenamefont {Toulouse}, \citenamefont {Barbaresco}, \citenamefont {Renon},
+  \citenamefont {David}, \citenamefont {Malrieu}, \citenamefont {V{\'e}ril},
+  \citenamefont {Caffarel}, \citenamefont {Loos}, \citenamefont {Giner},\ and\
+  \citenamefont {Scemama}}]{QP2}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Garniron}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Gasperich}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Applencourt}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Benali}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Fert{\'e}}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Paquier}}, \bibinfo {author} {\bibfnamefont
+  {B.}~\bibnamefont {Pradines}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Assaraf}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Reinhardt}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Toulouse}}, \bibinfo {author} {\bibfnamefont
+  {P.}~\bibnamefont {Barbaresco}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Renon}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {David}}, \bibinfo {author} {\bibfnamefont {J.~P.}\
+  \bibnamefont {Malrieu}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {V{\'e}ril}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Caffarel}},
+  \bibinfo {author} {\bibfnamefont {P.~F.}\ \bibnamefont {Loos}}, \bibinfo
+  {author} {\bibfnamefont {E.}~\bibnamefont {Giner}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Scemama}},\ }\href {\doibase
+  10.1021/acs.jctc.9b00176} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Chem. Theory Comput.}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages}
+  {3591} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Davidson}\ \emph {et~al.}(1991)\citenamefont
+  {Davidson}, \citenamefont {Hagstrom}, \citenamefont {Chakravorty},
+  \citenamefont {Umar},\ and\ \citenamefont {Fischer}}]{Dav-ions-PRA-91}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+  {Davidson}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+  {Hagstrom}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+  {Chakravorty}}, \bibinfo {author} {\bibfnamefont {V.~M.}\ \bibnamefont
+  {Umar}}, \ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+  {Fischer}},\ }\href {\doibase 10.1103/PhysRevA.44.7071} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {44}},\
+  \bibinfo {pages} {7071} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Umrigar}\ and\ \citenamefont
+  {Gonze}(1994)}]{UmrGon-PRA-94}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Umrigar}}\ and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Gonze}},\ }\href {\doibase 10.1103/PhysRevA.50.3827} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {50}},\
+  \bibinfo {pages} {3827} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Toulouse}, \citenamefont {Colonna},\ and\
+  \citenamefont {Savin}(2005)}]{TouColSav-JCP-05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Toulouse}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Colonna}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Savin}},\ }\href
+  {\doibase 10.1063/1.1824896} {\bibfield  {journal} {\bibinfo  {journal} {The
+  Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo
+  {pages} {014110} (\bibinfo {year} {2005})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1063/1.1824896}
+  {https://doi.org/10.1063/1.1824896} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lie}\ and\ \citenamefont
+  {Clementi}(1974)}]{LieCle-JCP-74a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~C.}\ \bibnamefont
+  {Lie}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Clementi}},\
+  }\href {\doibase https://doi.org/10.1063/1.1681192} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {60}},\
+  \bibinfo {pages} {1275} (\bibinfo {year} {1974})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2021-02-03 dev/slat_rules_trans/lapack_diag_non_hermit.irp.f

@@ -1,16 +1,27 @@
 subroutine lapack_diag_non_sym(n,A,WR,WI,VL,VR)
  implicit none
+  BEGIN_DOC
+! You enter with a general non hermitian matrix A(n,n) 
+!
+! You get out with the real WR and imaginary part WI of the eigenvalues 
+!
+! Eigvalue(n) = WR(n) + i * WI(n)
+!
+! And the left VL and right VR eigenvectors 
+!
+! VL(i,j) = <i|Psi_left(j)>  :: projection on the basis element |i> on the jth left  eigenvector 
+!
+! VR(i,j) = <i|Psi_right(j)> :: projection on the basis element |i> on the jth right eigenvector 
+  END_DOC
  integer, intent(in) :: n
  double precision, intent(in) :: A(n,n)
  double precision, intent(out):: WR(n),WI(n),VL(n,n),VR(n,n)
-  print*,'Computing the left/right eigenvectors ...'
   character*1 :: JOBVL,JOBVR
   JOBVL = "V" ! computes the left  eigenvectors 
   JOBVR = "V" ! computes the right eigenvectors 
   integer     :: lda,ldvl,ldvr,LWORK,INFO
   double precision, allocatable :: WORK(:)
   integer :: n_good
-  ! Eigvalue(n) = WR(n) + i * WI(n)
   lda  = n
   ldvl = n
   ldvr = n

### 2021-02-08 cusp_j/paper/revised/paper.tex
minor modifs

@@
 \usepackage[normalem]{ulem}
+
+\newcommand{\LCT}{Laboratoire de Chimie Th\'eorique (UMR 7616), Sorbonne Universit\'e, CNRS, 4 place Jussieu, Paris, 75005, France}
 
@@
 
-\newcommand{\corr}[1]{{\color{red} #1}}
-
 \begin{document}
@@
 \author{Emmanuel Giner}
-\email{eginer@lct.jussieu.fr}
+\email{emmanuel.giner@lct.jussieu.fr}
+\affiliation{\LCT}
 
@@
 We also propose a specific value of $\mu$ which essentially reproduce the results obtained with the frozen Gaussian geminal introduced by Ten-No [CPL-330,169 (2000)].
-%We introduce a way to find a reasonable value of $\mu$ that automatically adapts to the system through its density, and show the benefit of such approach on the isoelectronic series of the helium atom.
-%It should be pointed out that all two-electron integrals can be carried analytically within such approach and the three-electrons terms can be performed using a mixed analytical-numerical integration approach.
 
@@
 
-Another approach to tackle the problems of WFT related to the electron cusp have been proposed by the F12 methods which introduce a function explicitly depending on the inter-electronic coordinate\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18} (called a \corr{correlation} factor) to describe short-range correlation effects which are absent from the finite basis set.
+Another approach to tackle the problems of WFT related to the electron cusp have been proposed by the F12 methods which introduce a function explicitly depending on the inter-electronic coordinate\cite{Ten-TCA-12,TenNog-WIREs-12,HatKloKohTew-CR-12, KonBisVal-CR-12, GruHirOhnTen-JCP-17, MaWer-WIREs-18} (called a {correlation} factor) to describe short-range correlation effects which are absent from the finite basis set.
 Thanks to strong orthogonality,
-all redundant correlation effects between the \corr{correlation} factor and the basis set are projected out of the wave function, 
-and therefore the \corr{correlation} factor only deals with correlation effects orthonormal to the basis set. 
+all redundant correlation effects between the {correlation} factor and the basis set are projected out of the wave function, 
+and therefore the {correlation} factor only deals with correlation effects orthonormal to the basis set. 
 The resulting F12 theories, mainly based on perturbation theory and coupled cluster theory, are therefore 
-extremely close to their parent WFT theory, with additional contributions involving two- and three-body terms resulting from the use of the \corr{correlation} factor. 
-It is important to notice that because of the orthogonalization between the \corr{correlation} and the basis set, 
+extremely close to their parent WFT theory, with additional contributions involving two- and three-body terms resulting from the use of the {correlation} factor. 
+It is important to notice that because of the orthogonalization between the {correlation} and the basis set, 
 the complexity of the $N$-body problem within a given basis set is essentially the same between a F12 theory and the parent theory in WFT.
@@
 
-An alternative point of view using a \corr{correlation} factor is the so-called transcorrelated (TC) approach where the full effect of the \corr{correlation} factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the \corr{correlation} factor.
-\corr{As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
+An alternative point of view using a {correlation} factor is the so-called transcorrelated (TC) approach where the full effect of the {correlation} factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the {correlation} factor.
+{As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
 Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity.
@@
 The use of a TC Hamiltonian in the context of FCI-QMC has an important advantage: because the TC Hamiltonian already contains the effect of an elaborate Jastrow factor, the right-eigenvectors of the TC Hamiltonian are more compact and therefore the FCI-QMC procedure converges faster.
-\corr{ This have been illustrated in the context of the Hubbard model\cite{DobLuoAla-PRB-19} for which Alavi \textit{et.
+{ This have been illustrated in the context of the Hubbard model\cite{DobLuoAla-PRB-19} for which Alavi \textit{et.
 al.} found that the weight of the Hartree-Fock Slater determinant in the right eigenvector of the TC Hamiltonian obtained with the Gutzwiller Ansatz\cite{Gutzwiller-PRL-63,BriRic-PRB-70}  significantly increases with respect to that in the eigenfunction of the usual Hubbard Hamiltonian.
@@
 
-\corr{
+{
 It should be noticed that the method proposed here to generate a Jastrow factor based on an effective interaction is very general,
@@
 
-For instance, the Jastrow factor $u(r_{12},\mu)$ derived in Eq. (10) corresponds to the solution of Eq. \eqref{def_general} with $h(r_{12})  =   \text{erfc}(\mu r_{12})$. 
+For instance, the Jastrow factor $u(r_{12},\mu)$ derived in Eq. \eqref{def_j_0} corresponds to the solution of Eq. \eqref{def_general} with $h(r_{12})  =   \text{erfc}(\mu r_{12})$. 
 There are of course as many solutions to Eq. \eqref{def_general} as there are functions $h(r_{12})$.
@@
 These results illustrates that the Jastrow factor must adapt to the typical length-scale of the system, and therefore shows the benefit of using an easily tunable Jastrow factor such as $u(r_{12},\mu)$.
-\corr{It should be noticed that the typical range of the FROGG can be tuned by varying the exponent of the Gaussian weight function involved in   the least-square fit of Eq.
+{It should be noticed that the typical range of the FROGG can be tuned by varying the exponent of the Gaussian weight function involved in   the least-square fit of Eq.
 (9) of Ref.
@@
 The perspective of this work are mainly to study more realistic systems which will includes the expensive three-body terms, and to explore the possibility of having a value of $\mu$ varying in space. 
-\corr{The latter can be considered as way to include some of the flexibility of the electron-electron-nucleus terms present in the Jastrow factor developed by Moskowitz \textit{et.
+{The latter can be considered as way to include some of the flexibility of the electron-electron-nucleus terms present in the Jastrow factor developed by Moskowitz \textit{et.
 al.}\cite{SchMos-JCP-90} and used by Alavi \textit{et.
@@
 \begin{equation}
- g(x, \mu)= \text{erf}( \mu x) - 1.
+ g(x, \mu)= 1 - \text{erf}( \mu x).
 \end{equation}

### 2021-02-08 dev/slat_rules_trans/psi_exact.irp.f

@@ -55,6 +55,24 @@ BEGIN_PROVIDER [double precision, psi_fci_array, (ntheta_psi_ex,nr1_psi_ex)]
  enddo
 END_PROVIDER 
 
+BEGIN_PROVIDER [double precision, psi_hf_array, (ntheta_psi_ex,nr1_psi_ex)]
+ implicit none
+ integer :: i , j
+!call diagonalize_CI
+ double precision :: mos_array_r1(mo_num), mos_array_r2(mo_num)
+ double precision :: r1(3), r2(3)
+ do j = 1, nr1_psi_ex
+  do i = 1, ntheta_psi_ex
+   call give_all_mos_at_r(r1,mos_array_r1)
+   call give_all_mos_at_r(r2,mos_array_r2)
+   r1(:) = r1_psi_ex(:,j)
+   r2(:) = r2_psi_ex(:,i,j)
+   psi_hf_array(i,j) = dabs(mos_array_r1(1)*mos_array_r2(1))
+  enddo
+ enddo
+END_PROVIDER 
+
+
  BEGIN_PROVIDER [double precision, psi_right_array, (ntheta_psi_ex,nr1_psi_ex)]
 &BEGIN_PROVIDER [double precision, psi_right_jastrow_array, (ntheta_psi_ex,nr1_psi_ex)]
 &BEGIN_PROVIDER [double precision, psi_right_jastrow_norm_array, (ntheta_psi_ex,nr1_psi_ex)]
@@ -95,6 +113,31 @@ BEGIN_TEMPLATE
                                         psi_fci_array(i,$X), &
                                         psi_right_array(i,$X), &
                                         psi_right_jastrow_array(i,$X),psi_right_jastrow_norm_array(i,$X)
+ enddo
+SUBST [ X]
+ 1;; 
+ 2;;
+ 3;;
+ 4;;
+ 5;;
+END_TEMPLATE
+
+
+end
+
+subroutine print_psi_hf_psi_trans
+ implicit none
+ integer :: i
+ integer                        :: i_unit_output,getUnitAndOpen
+ character*(128)                :: output
+ PROVIDE ezfio_filename
+
+BEGIN_TEMPLATE
+ output=trim(ezfio_filename)//'.cusp_wf_$X'
+ print*,'output = ',trim(output)
+ i_unit_output = getUnitAndOpen(output,'w')
+ do i = 1, ntheta_psi_ex
[…]

### 2021-02-26 cusp_j/paper/revised/paper.tex
modified Yuan plugins

@@
 {As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
-Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity.
+Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHan-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity.
 The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator.

### 2021-02-26 stable/yuan_plugins/read_and_write_rdm.irp.f

@@ -1,9 +1,46 @@
+BEGIN_PROVIDER [ integer*8, dim_two_rdm  ]
+  implicit none
+  BEGIN_DOC
+! number of elements in two-rdm
+  END_DOC
+
+  logical                        :: has
+  PROVIDE ezfio_filename
+  if (mpi_master) then
+    
+    call ezfio_has_yuan_plugins_dim_two_rdm(has)
+    if (has) then
+      write(6,'(A)') '.. >>>>> [ IO READ: dim_two_rdm ] <<<<< ..'
+      call ezfio_get_yuan_plugins_dim_two_rdm(dim_two_rdm)
+    else
+      print *, 'yuan_plugins/dim_two_rdm not found in EZFIO file'
+      stop 1
+    endif
+  endif
+  IRP_IF MPI_DEBUG
+    print *,  irp_here, mpi_rank
+    call MPI_BARRIER(MPI_COMM_WORLD, ierr)
+  IRP_ENDIF
+  IRP_IF MPI
+    include 'mpif.h'
+    integer :: ierr
+    call MPI_BCAST( dim_two_rdm, 1, MPI_INTEGER8, 0, MPI_COMM_WORLD, ierr)
+    if (ierr /= MPI_SUCCESS) then
+      stop 'Unable to read dim_two_rdm with MPI'
+    endif
+  IRP_ENDIF
+
+  call write_time(6)
+
+END_PROVIDER
 
 subroutine read_two_rdm_and_write_to_ezfio(n,n_mo_tmp)
  implicit none
- integer, intent(in) :: n,n_mo_tmp
+ integer, intent(in) :: n_mo_tmp
+ integer*8, intent(in) :: n
 
- integer :: i,j,k,l,m
+ integer :: i,j,k,l
+ integer*8 :: m
  double precision :: value_rdm
  double precision, allocatable :: two_rdm(:,:,:,:,:)
  character*(128) :: name_file 
@@ -14,7 +51,7 @@ subroutine read_two_rdm_and_write_to_ezfio(n,n_mo_tmp)
  character*(1) :: coma
  open(1, file = 'two_rdm') 
  two_rdm = 0.d0
- do m = 1, n
+ do m = 1_8, n
    ! a^{l}a^{k} a_i a_j
 !  read(1,'(4(I3,A1),F16.13)')l,coma, k, coma, j, coma, i,coma,value_rdm
   read(1,*)l, k,  j,  i,value_rdm

### 2021-03-25 cusp_j/paper/paper_draft.tex
conclusion almost finished
beginning to parallelize

@@
 Coming now to the behaviour of $u(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$.
-\begin{figure*}
- \label{fig_j_mu}
-        \includegraphics[width=0.45\linewidth]{small_mu_j.pdf}
-        \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
-        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
-\end{figure*}
+%\begin{figure*}
+% \label{fig_j_mu}
+%        \includegraphics[width=0.45\linewidth]{small_mu_j.pdf}
+%        \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
+%        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
+%\end{figure*}
 From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.
@@
 In order to have a pictorial representation of $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$, we illustrate in Fig\ref{fig_wee_mu} its shape for different values of $\mu$. 
-\begin{figure*}
- \label{fig_wee_mu}
-        \includegraphics[width=0.45\linewidth]{w_ee.pdf}
-        \includegraphics[width=0.45\linewidth]{w_ee_bis.pdf}\\
-        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (up) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (bottom) for different values of $\mu$.}
-\end{figure*}
+%\begin{figure*}
+% \label{fig_wee_mu}
+%        \includegraphics[width=0.45\linewidth]{w_ee.pdf}
+%        \includegraphics[width=0.45\linewidth]{w_ee_bis.pdf}\\
+%        \caption{Shape of $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ (up) and comparison with $\frac{\text{erf}(\mu r_{12}}{r_{12}}$ (bottom) for different values of $\mu$.}
+%\end{figure*}
 From  Fig.\ref{fig_wee_mu} we can see that the scalar effective potential $ \tilde{\mathcal{W}}_{ee}(r_{ij},\mu)$ 
@@
 Therefore one can conclude that the use of a simple Jastrow factor such as $u(r_{12};\mu)$ within the transcorrelated framework can strongly improve the speed of convergence of the total energy of the helium atom with a quite wide range of values of $\mu$ ranging from $\mu=0.2$ to $\mu=1.6$.
-\begin{figure*}
- \label{fig_conv_e_mu}
-        \includegraphics[width=0.45\linewidth]{E_conv_basis_small_mu.pdf}
-        \includegraphics[width=0.45\linewidth]{E_conv_basis_large_mu.pdf}\\
-        \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$.}
-\end{figure*}
+%\begin{figure*}
+% \label{fig_conv_e_mu}
+%        \includegraphics[width=0.45\linewidth]{E_conv_basis_small_mu.pdf}
+%        \includegraphics[width=0.45\linewidth]{E_conv_basis_large_mu.pdf}\\
+%        \caption{Convergence of the ground state eigenvalue of $\tilde{H}[\mu]$ with respect to the AVXZ basis set series (X=D,T,Q,5) for different values of $\mu$.}
+%\end{figure*}
 
@@
 We report in Figs \ref{fig:mu_0.3_dz_3} and \ref{fig:mu_1.0_dz_3} the plot of the right eigenvector $\phimub(\br{}_1,\br{}_2)$, estimated exact wave function $\psimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ and $\mu=1.0$ (respectively) and compared to the exact wave function $\psiex(\br{}_1,\br{}_2)$ and FCI wave function for $r=0.5\,a.u.$.
-\begin{figure*}
- \label{fig:mu_0.3_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He//He_mu_0_3_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
-        \caption{
-        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
+%\begin{figure*}
+% \label{fig:mu_0.3_dz_3}
+%        \includegraphics[width=0.45\linewidth]{plots/He//He_mu_0_3_cusp_avdz_avtz_3.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_0_3_cusp_avqz_av5z_3.pdf}\\
+%        \caption{
+%        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=0.3$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
 Comparison with the FCI wave function in the same basis sets and the estimated exact wave function $\psiex(\br{}_1,\br{}_2)$.
 }
-\end{figure*}
-
-\begin{figure*}
- \label{fig:mu_1.0_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avdz_avtz_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
-        \caption{
-        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=1.0$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
+%\end{figure*}
+
+%\begin{figure*}
+% \label{fig:mu_1.0_dz_3}
+%        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avdz_avtz_3.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/He/He_mu_1_0_cusp_avqz_av5z_3.pdf}\\
+%        \caption{
+%        Helium atom, radius $r=0.5$ a.u.: approximation of the exact wave function $\psimub(\br{}_1,\br{}_2)$ and right eigenvector $\phimub(\br{}_1,\br{}_2)$ for $\mu=1.0$ in the AVDZ and AVTZ basis sets (left) and AVQZ and AV5Z (right).
 Comparison with the FCI wave function in the same basis sets and the estimated exact wave function $\psiex(\br{}_1,\br{}_2)$.
 }
-\end{figure*}
+%\end{figure*}
 
@@
 Therefore, one can 
-\begin{figure*}
- \label{fig_wee_compare}
-        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
-        \caption{
-        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
-\end{figure*}
+%\begin{figure*}
+% \label{fig_wee_compare}
+%        \includegraphics[width=1.00\linewidth]{w_ee_compare.pdf}
+%        \caption{
+%        Effective potential $\tilde{\mathcal{W}}_{ee}(r_{12},\mu)$ for $\mu=0.3$ and $\mu=1.0$, compared to the usual $1/r_{12}$ Coulomb interaction.}
+%\end{figure*}
 
@@
 
-\begin{figure*}
- \label{fig:mu_1.0_dz_3}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
-        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
-        \caption{
-        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
-}
-\end{figure*}
+%\begin{figure*}
+% \label{fig:mu_1.0_dz_3}
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
+%        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
+%        \caption{
+%        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.
+%}
+%\end{figure*}
 

### 2021-03-25 dev/ao_one_ints_slater/ao_one_ints_slater.irp.f

@@ -6,6 +6,6 @@ program ao_one_ints_slater
   print *, 'Hello world'
 
 !  call test_int_bis
-!  call test_int_full_j
- call test_overlap_gauss_r12_ao
+  call test_int_full_j
+! call test_overlap_gauss_r12_ao
 end

### 2021-03-25 dev/ao_one_ints_slater/routines_test.irp.f

@@ -314,10 +314,14 @@ subroutine test_int_full_j
  double precision :: abs_error_av, relat_error_av,icount
  double precision :: abs_error_c_av, relat_error_c_av,slater_fit_gam
  double precision :: full_jastrow,exp_dl,zeta
+ double precision :: exponent_exp
  integer :: n_taylor
  n_taylor = 10
  double precision, allocatable :: array_ints_overlap(:),array_ints_erf(:)
  allocate(array_ints_overlap(0:n_taylor),array_ints_erf(0:n_taylor))
+
+ ! 
+ exponent_exp = -1.d0
  ! C    :: center of the Coulomb 
  zeta = 1.d0
  mu = 1.d0
@@ -356,7 +360,7 @@ subroutine test_int_full_j
       beta = ao_expo_ordered_transp(k,j)     
    
        ! analytical integral 
-       call exp_dl_ovlp_stg_phi_ij(zeta,D_center,gama,delta,A_center,B_center,power_A,power_B,alpha,beta,n_taylor,array_ints_overlap,analytical)
+       call exp_dl_ovlp_stg_phi_ij(zeta,D_center,gama,delta,A_center,B_center,power_A,power_B,alpha,beta,n_taylor,array_ints_overlap,analytical,exponent_exp)
        call exp_dl_erf_stg_phi_ij(zeta, D_center,gama,delta,A_center,B_center,power_A,power_B,alpha,beta,C_center,mu,n_taylor,array_ints_erf,analytical_c)
 
        ! numerical  integral 
@@ -383,7 +387,7 @@ subroutine test_int_full_j
 !        full_jastrow = dexp(-jastrow)
         gauss_a = primitive_value_explicit(power_A,A_center,alpha,r)
         gauss_b = primitive_value_explicit(power_B,B_center,beta ,r)
-        numerical += weight * full_jastrow * gauss_a * gauss_b 
+        numerical   += weight / full_jastrow * gauss_a * gauss_b 
         numerical_c += weight * full_jastrow * gauss_a * gauss_b * coulomb
        enddo
        abs_error_av += dabs(analytical - numerical)

### 2021-03-25 dev/ao_one_ints_slater/taylor_exp.irp.f

@@ -24,13 +24,13 @@ subroutine exp_dl_rout(x,n, array)
  enddo
 end
 
-subroutine exp_dl_ovlp_stg_phi_ij(zeta,D_center,gam,delta,A_center,B_center,power_A,power_B,alpha,beta,n_taylor,array_ints,integral_taylor)
+subroutine exp_dl_ovlp_stg_phi_ij(zeta,D_center,gam,delta,A_center,B_center,power_A,power_B,alpha,beta,n_taylor,array_ints,integral_taylor,exponent_exp)
   BEGIN_DOC
   ! Computes the following integrals : 
   !
   ! .. math::
   ! 
-  !   array(i) = \int dr exp(-gam*i (r - D)) exp(-delta*i * (r -D)^2) (x-A_x)^a (x-B_x)^b \exp(-\alpha (x-A_x)^2 - \beta (x-B_x)^2 )
+  !   array(i) = \int dr EXP{exponent_exp * [exp(-gam*i (r - D)) exp(-delta*i * (r -D)^2)] (x-A_x)^a (x-B_x)^b \exp(-\alpha (x-A_x)^2 - \beta (x-B_x)^2 )
   !
   !
   ! and gives back the Taylor expansion of the exponential in integral_taylor
@@ -42,6 +42,7 @@ subroutine exp_dl_ovlp_stg_phi_ij(zeta,D_center,gam,delta,A_center,B_center,powe
  double precision, intent(in)    :: D_center(3), gam ! pure Slater "D" in r-r_D
  double precision, intent(in)    :: delta            ! gaussian        in r-r_D
  double precision, intent(in)    :: A_center(3),B_center(3),alpha,beta ! gaussian/polynoms "A" and "B"
+ double precision, intent(in)    :: exponent_exp
  integer, intent(in)             :: power_A(3),power_B(3)
  double precision, intent(out)   :: array_ints(0:n_taylor),integral_taylor
 
@@ -56,7 +57,7 @@ subroutine exp_dl_ovlp_stg_phi_ij(zeta,D_center,gam,delta,A_center,B_center,powe
   delta_exp = dble(i) * delta
   gam_exp   = dble(i) * gam
   array_ints(i) = ovlp_stg_gauss_int_phi_ij(D_center,gam_exp,delta_exp,A_center,B_center,power_A,power_B,alpha,beta)
-  integral_taylor += (-zeta)**dble(i) * fact_inv(i) * array_ints(i)
[…]

### 2021-03-25 dev/ao_two_e_eff_pot/potential.irp.f

@@ -39,12 +39,16 @@ END_PROVIDER
  do i = 1, n_max_fit_slat
   expo_gauss_eff_pot(i) = expo_gauss_1_erf_x_2(i) 
   coef_gauss_eff_pot(i) = -0.25d0 * coef_gauss_1_erf_x_2(i) ! -1/4 * (1 - erf(mu*x))^2
-!  coef_gauss_eff_pot(i) = 0.d0
  enddo
-
- ! then you have the \mu/sqrt(pi) * exp(-mu^2*x^2)
+ ! Analytical Gaussian part of the potential 
  expo_gauss_eff_pot(n_max_fit_slat+1) = mu_erf * mu_erf
- coef_gauss_eff_pot(n_max_fit_slat+1) = mu_erf * inv_sq_pi
+ if(adjoint_tc_h)then
+  ! then you have the " - \mu/sqrt(pi) * exp(-mu^2*x^2) " for the adjoint 
+  coef_gauss_eff_pot(n_max_fit_slat+1) = -1.d0 * mu_erf * inv_sq_pi
+ else
+!  ! then you have the " + \mu/sqrt(pi) * exp(-mu^2*x^2) " for the adjoint 
+  coef_gauss_eff_pot(n_max_fit_slat+1) =  1.d0 * mu_erf * inv_sq_pi
+ endif
 
 END_PROVIDER 
 

### 2021-03-25 dev/coll_salv_fun/coll_salv_fun.irp.f

@@ -9,7 +9,8 @@ program coll_salv_fun
 !  call test_int_f_tilde
 ! call test_shank
   call test_int_f_special
-! call routine_test_n2_j
+!  call routine_test_n2_j
+!  call routine_test_n2_inv_j
 ! call routine_test_n2_j_full
 ! call print_energy
 end

### 2021-03-25 dev/coll_salv_fun/two_elec_wf.irp.f

@@ -15,9 +15,9 @@ BEGIN_PROVIDER [integer, occ_two_e_psi, (2, N_det)]
 
 END_PROVIDER 
 
-subroutine get_two_e_psi_at_r1r2(r1,r2,psi)
+subroutine get_two_e_psi_at_r1r2(r1,r2,psi,coef_psi)
  implicit none
- double precision, intent(in) :: r1(3),r2(3)
+ double precision, intent(in) :: r1(3),r2(3),coef_psi(N_det,N_states)
  double precision, intent(out):: psi(N_states)
  double precision, allocatable :: mos_array_r2(:),mos_array_r1(:)
  allocate(mos_array_r1(mo_num),mos_array_r2(mo_num))
@@ -29,7 +29,7 @@ subroutine get_two_e_psi_at_r1r2(r1,r2,psi)
   do i = 1, N_det
    i_up   = occ_two_e_psi(1,i)
    i_down = occ_two_e_psi(2,i)
-   psi(istate) += mos_array_r1(i_up) * mos_array_r2(i_down) * psi_coef(i,istate)
+   psi(istate) += mos_array_r1(i_up) * mos_array_r2(i_down) * coef_psi(i,istate)
   enddo
  enddo
 

### 2021-03-25 dev/plot_tc_wf/norm_full_psi.irp.f

@@ -1,0 +1,124 @@
+
+ BEGIN_PROVIDER [double precision, norm_n2_jastrow_cst_mu_on_grid, (n_points_final_grid,N_states)]
+&BEGIN_PROVIDER [double precision, norm_n2_jastrow_cst_mu, (N_states)]
+ implicit none
+ BEGIN_DOC
+! norm_n2_jastrow_cst_mu_on_grid(ipoint) = \int dr2 n2(ipoint,r2)J^2(mu(ipoint)
+! 
+! norm_n2_jastrow_cst_mu(ipoint) = \int dr1 \int dr2 n2(ipoint,r2)J^2(mu(ipoint)
+ END_DOC
+ integer :: ipoint,istate,i,j,k,l
+ double precision :: weight
+ norm_n2_jastrow_cst_mu = 0.d0
+ norm_n2_jastrow_cst_mu_on_grid = 0.d0
+ do i = 1, N_det
+  psi_coef(i,1) = reigvec_trans(i,1)/dsqrt(reigvec_trans_norm(1))
+ enddo
+ touch psi_coef
+
+ do istate =1, N_states
+  do ipoint = 1, n_points_final_grid
+   weight = final_weight_at_r_vector(ipoint)
+   do i = 1, mo_num ! 1
+    do k = 1, mo_num ! 1 
+     do j = 1, mo_num ! 2 
+      do l = 1, mo_num ! 2
+       norm_n2_jastrow_cst_mu_on_grid(ipoint,istate) += mos_in_r_array(i,ipoint) * mos_in_r_array(k,ipoint) * & 
+                          ovlp_jastrow2_ij_cst_mu_mo(l,j,ipoint) * full_occ_2_rdm_ab_chemist_mo(l,j,k,i,istate)
+      enddo
+     enddo
+    enddo
+   enddo
+   norm_n2_jastrow_cst_mu(istate) += norm_n2_jastrow_cst_mu_on_grid(ipoint,istate) * weight
+  enddo
+ enddo
+END_PROVIDER 
+
+
+BEGIN_PROVIDER [double precision, ovlp_jastrow2_ij_cst_mu_mo, (mo_num,mo_num,n_points_final_grid)]
+ implicit none
+ BEGIN_DOC
+! \int dr2 phi_i(r2) \phi_j(r2) e^{J(r1,r2,\mu(r1))}
+ END_DOC
+ integer :: i,j,ipoint,n_taylor
[…]

### 2021-03-25 dev/three_body_ints/semi_num_ints_mo.irp.f

@@ -25,9 +25,16 @@ BEGIN_PROVIDER [ double precision, mo_v_ij_erf_rk, ( mo_num, mo_num,n_points_fin
 ! int dr phi_i(r) phi_j(r) (erf(mu(R) |r - R|) - 1)/(2|r - R|) on the MO basis
  END_DOC
  integer :: ipoint
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (ipoint) & 
+ !$OMP SHARED (n_points_final_grid,v_ij_erf_rk,mo_v_ij_erf_rk)
+ !$OMP DO SCHEDULE (dynamic)
  do ipoint = 1, n_points_final_grid
    call ao_to_mo(v_ij_erf_rk(1,1,ipoint),size(v_ij_erf_rk,1),mo_v_ij_erf_rk(1,1,ipoint),size(mo_v_ij_erf_rk,1))
  enddo
+ !$OMP END DO
+ !$OMP END PARALLEL
  mo_v_ij_erf_rk = mo_v_ij_erf_rk * 0.5d0
 END_PROVIDER 
 
@@ -76,11 +83,18 @@ BEGIN_PROVIDER [ double precision, mo_x_v_ij_erf_rk, ( mo_num, mo_num,3,n_points
 ! int dr x * phi_i(r) phi_j(r) (erf(mu(R) |r - R|) - 1)/|r - R| on the MO basis
  END_DOC
  integer :: ipoint,m
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (ipoint,m) & 
+ !$OMP SHARED (n_points_final_grid,x_v_ij_erf_rk_transp,mo_x_v_ij_erf_rk)
+ !$OMP DO SCHEDULE (dynamic)
  do ipoint = 1, n_points_final_grid
   do m = 1, 3
    call ao_to_mo(x_v_ij_erf_rk_transp(1,1,m,ipoint),size(x_v_ij_erf_rk_transp,1),mo_x_v_ij_erf_rk(1,1,m,ipoint),size(mo_x_v_ij_erf_rk,1))
   enddo
  enddo
+ !$OMP END DO
+ !$OMP END PARALLEL
  mo_x_v_ij_erf_rk = 0.5d0 * mo_x_v_ij_erf_rk
 
 END_PROVIDER 
[…]

### 2021-03-25 dev/three_body_ints/three_body_tensor.irp.f

@@ -14,6 +14,11 @@ BEGIN_PROVIDER [ double precision, three_body_ints, (mo_num, mo_num, mo_num, mo_
   print*,'Reading three_body_ints from disk ...'
   call read_array_6_index_tensor(mo_num,three_body_ints,name_file)
  else
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (i,j,k,l,m,n,integral) & 
+ !$OMP SHARED (mo_num,three_body_ints)
+ !$OMP DO SCHEDULE (dynamic)
   do n = 1, mo_num
    do l = 1, mo_num
     do k = 1, mo_num
@@ -29,6 +34,8 @@ BEGIN_PROVIDER [ double precision, three_body_ints, (mo_num, mo_num, mo_num, mo_
     enddo
    enddo
   enddo
+ !$OMP END DO
+ !$OMP END PARALLEL
  endif
  if(write_six_index_tensor)then
   print*,'Writing three_body_ints on disk ...'

### 2021-03-25 dev/transcorr_h/htilde_matrix.irp.f

@@ -61,8 +61,8 @@ END_PROVIDER
   double precision, allocatable :: reigvec_trans_tmp(:,:),leigvec_trans_tmp(:,:)
   allocate(reigvec_trans_tmp(N_det,N_states),leigvec_trans_tmp(N_det,N_states))
   print*,'Reading the right/left eigenvectors in the EZFIO....'
-   call ezfio_get_slat_rules_trans_reigvec_trans(reigvec_trans_tmp)
-   call ezfio_get_slat_rules_trans_leigvec_trans(leigvec_trans_tmp)
+   call ezfio_get_transcorr_h_reigvec_trans(reigvec_trans_tmp)
+   call ezfio_get_transcorr_h_leigvec_trans(leigvec_trans_tmp)
    reigvec_trans_norm = 0.d0
    leigvec_trans_norm = 0.d0
    do i = 1, N_states
@@ -132,8 +132,8 @@ subroutine write_left_right
    reigvec_trans_tmp(j,i) = reigvec_trans(j,i)
   enddo
  enddo
- call ezfio_set_slat_rules_trans_reigvec_trans(reigvec_trans_tmp)
- call ezfio_set_slat_rules_trans_leigvec_trans(leigvec_trans_tmp)
+ call ezfio_set_transcorr_h_reigvec_trans(reigvec_trans_tmp)
+ call ezfio_set_transcorr_h_leigvec_trans(leigvec_trans_tmp)
 end
 
 subroutine test_left_right_eigenvalues(ith)

### 2021-03-25 dev/transcorr_h/plot_density_tc.irp.f

@@ -1,0 +1,82 @@
+program plot_density_tc
+ implicit none
+ read_wf = .True.
+ touch read_wf
+ call routine_check_tm
+ call routine_print_density
+end
+
+subroutine routine_check_tm
+ implicit none
+ integer :: i
+ print*,''
+ print*,''
+ print*,'one_e_tm_mo_norm   = ',one_e_tm_mo_norm
+ print*,'left_right_overlap = ',left_right_overlap(1,1)
+ print*,'tmp                = ',left_right_overlap_read
+ print*,'norm/overlap       = ',one_e_tm_mo_norm / left_right_overlap(1,1)
+ print*,'elec_num           = ',elec_num_tab(1) + elec_num_tab(2)
+ print*,''
+ print*,''
+ print*,'right_overlap_read = ',right_overlap_read
+ print*,'left_overlap_read  = ',left_overlap_read
+ print*,''
+ print*,'Printing the one_e_tm_mo'
+ do i = 1, mo_num
+  write(*,'(1000(F16.10,X))')one_e_tm_mo(i,:,1)
+ enddo
+ print*,''
+ print*,''
+ print*,''
+end 
+
+subroutine routine_print_density
+ implicit none
+ integer :: ipoint,i,j,m1,m2
+ integer :: nx
+ double precision :: x,dx,xmax,xmin,r(3)
+ double precision :: density_from_matrix,dm_r,dm_l, tm_lr
+ double precision, allocatable :: dm_mo(:,:,:)
+ allocate(dm_mo(mo_num, mo_num, N_states)) ! state 1 == Right, state 2 == Left
+ do i = 1, mo_num
+  do j = 1, mo_num
+   dm_mo(j,i,1) = one_e_dm_mo_alpha(j,i,1) + one_e_dm_mo_beta(j,i,1)
+   dm_mo(j,i,2) = one_e_dm_mo_alpha(j,i,2) + one_e_dm_mo_beta(j,i,2)
+  enddo
+ enddo
+ xmax = 5.d0
+ nx = 10000
+ dx = xmax / dble(nx)
+ xmin = -0.5d0 * xmax
+ r = 0.d0
+ r(1) = xmin
+
+ character*(128) :: output
+ integer :: i_unit_output,getUnitAndOpen
+ output=trim(ezfio_filename)//'.tc_density'
+ i_unit_output = getUnitAndOpen(output,'w')
+
+ do ipoint = 1, nx
[…]

### 2021-03-25 dev/transcorr_h/plot_density_wf.irp.f

@@ -1,0 +1,46 @@
+program plot_density_w
+ implicit none
+ read_wf = .True.
+ touch read_wf
+ call routine_print_density
+end
+
+subroutine routine_print_density
+ implicit none
+ integer :: ipoint,nx
+ double precision :: x,dx,xmax,xmin,r(3)
+ double precision :: dm_a,dm_b
+ xmax = 5.d0
+ nx = 10000
+ dx = xmax / dble(nx)
+ xmin = -0.5d0 * xmax
+ r = 0.d0
+ r(1) = xmin
+
+ character*(128) :: output
+ integer :: i_unit_output,getUnitAndOpen
+ output=trim(ezfio_filename)//'.density'
+ i_unit_output = getUnitAndOpen(output,'w')
+
+ do ipoint = 1, nx
+  call dm_dft_alpha_beta_at_r(r,dm_a,dm_b)
+  write(i_unit_output,'(100(F16.10,X))')r(1),dm_a + dm_b
+  r(1) += dx
+ enddo
+
+end
+
+
+double precision function density_from_matrix(matrix,r)
+ implicit none
+ double precision, intent(in) :: matrix(mo_num, mo_num), r(3)
+ double precision :: mos_array(mo_num)
+ call give_all_mos_at_r(r,mos_array)
+ density_from_matrix = 0.d0
+ integer :: i,j
+ do i = 1, mo_num
+  do j = 1, mo_num
+   density_from_matrix += mos_array(i) * mos_array(j) * matrix(j,i)
+  enddo
+ enddo
+end

### 2021-03-25 dev/transcorr_h/routines_to_print.irp.f

@@ -1,5 +1,5 @@
 
-subroutine print_energy
+subroutine print_energy_tc
  implicit none
  use bitmasks
  integer :: i

### 2021-03-25 dev/transcorr_h/save_right_left.irp.f

@@ -1,0 +1,23 @@
+program save_right_eigv
+ implicit none
+ read_wf = .True.
+ touch read_wf 
+ read_rl_eigv = .True.
+ touch read_rl_eigv
+
+ call routine_save
+end
+
+subroutine routine_save
+implicit none
+ double precision, allocatable :: coef_tmp(:,:)
+ N_states = 2
+
+ allocate(coef_tmp(N_det, 2))
+ integer :: i
+ do i = 1, N_det
+  coef_tmp(i,1) = reigvec_trans(i,1)
+  coef_tmp(i,2) = leigvec_trans(i,1)
+ enddo
+ call save_wavefunction_general(N_det,N_states,psi_det,size(coef_tmp,1),coef_tmp(1,1))
+end

### 2021-03-25 dev/transcorr_h/slat_rules_trans.irp.f

@@ -11,7 +11,9 @@ subroutine diag_htilde_mu_mat(key_i,hmono,herf,heff,hderiv,hthree,htot)
   integer                        :: occ(N_int*bit_kind_size,2)
   integer                        :: Ne(2),i,j,ii,jj,ispin,jspin,k,kk
   double precision :: get_mo_two_e_integral_erf,mo_two_e_integral_eff_pot
-
+  double precision :: get_two_e_integral
+  PROVIDE mo_two_e_integrals_in_map mo_integrals_map big_array_exchange_integrals 
+  PROVIDE mo_two_e_integrals_eff_pot_in_map mo_two_e_integrals_erf_in_map
   call bitstring_to_list_ab(key_i,occ,Ne,N_int)
 
   hmono = 0.d0
@@ -29,103 +31,142 @@ subroutine diag_htilde_mu_mat(key_i,hmono,herf,heff,hderiv,hthree,htot)
   enddo
 
 
-  ! alpha/beta two-body
-  ispin = 1
-  jspin = 2 
-  do i = 1, Ne(ispin) 
-   ii = occ(i,ispin) 
-   do j = 1, Ne(jspin)
-    jj = occ(j,jspin) 
-    herf += get_mo_two_e_integral_erf(ii,jj,ii,jj,mo_integrals_erf_map)
-    heff += mo_two_e_integral_eff_pot(ii,jj,ii,jj) 
-    hderiv += mo_two_e_eff_dr12_pot_array_physicist(ii,jj,ii,jj) 
+  if(.not.adjoint_tc_h)then ! Usual transcorrelated Hamiltonian 
+   ! alpha/beta two-body
+   ispin = 1
+   jspin = 2 
+   do i = 1, Ne(ispin) 
+    ii = occ(i,ispin) 
+    do j = 1, Ne(jspin)
+     jj = occ(j,jspin) 
+     herf += get_mo_two_e_integral_erf(ii,jj,ii,jj,mo_integrals_erf_map)
+     heff += mo_two_e_integral_eff_pot(ii,jj,ii,jj) 
+     hderiv += mo_two_e_eff_dr12_pot_array_physicist(ii,jj,ii,jj) 
+    enddo
    enddo
-  enddo
-
-  ! alpha/alpha two-body
-  do i = 1, Ne(ispin)
-   ii = occ(i,ispin) 
-   do j = i+1, Ne(ispin)
[…]

### 2021-03-25 dev/transcorr_h/transcorr_general.irp.f

@@ -8,7 +8,7 @@ program transcorr_h
  touch  my_grid_becke my_n_pt_r_grid my_n_pt_a_grid 
 
  call provide_all
- call print_energy
+ call print_energy_tc
  call print_e_comp_transcorr
  call print_eigv
  call print_pert

### 2021-03-25 dev/transcorr_h/transition_dm.irp.f

@@ -1,0 +1,180 @@
+
+ BEGIN_PROVIDER [ double precision, one_e_tm_mo_alpha, (mo_num,mo_num,N_states) ]
+&BEGIN_PROVIDER [ double precision, one_e_tm_mo_beta,  (mo_num,mo_num,N_states) ]
+  implicit none
+  BEGIN_DOC
+  ! $\alpha$ and $\beta$ one-body density matrix for each state
+  END_DOC
+
+  integer                        :: j,k,l,m1,m2,k_a,k_b
+  integer                        :: occ(N_int*bit_kind_size,2)
+  double precision               :: ck, cl, ckl
+  double precision               :: phase
+  integer                        :: h1,h2,p1,p2,s1,s2, degree
+  integer(bit_kind)              :: tmp_det(N_int,2), tmp_det2(N_int)
+  integer                        :: exc(0:2,2),n_occ(2)
+  double precision, allocatable  :: tmp_a(:,:,:), tmp_b(:,:,:)
+  integer                        :: krow, kcol, lrow, lcol
+
+  PROVIDE psi_det
+
+  one_e_tm_mo_alpha = 0.d0
+  one_e_tm_mo_beta  = 0.d0
+  !$OMP PARALLEL DEFAULT(NONE)                                      &
+      !$OMP PRIVATE(j,k,k_a,k_b,l,m1,m2,occ,ck, cl, ckl,phase,h1,h2,p1,p2,s1,s2, degree,exc,&
+      !$OMP  tmp_a, tmp_b, n_occ, krow, kcol, lrow, lcol, tmp_det, tmp_det2)&
+      !$OMP SHARED(psi_det,psi_coef,N_int,N_states,elec_alpha_num,  &
+      !$OMP  elec_beta_num,one_e_tm_mo_alpha,one_e_tm_mo_beta,N_det,&
+      !$OMP  mo_num,psi_bilinear_matrix_rows,psi_bilinear_matrix_columns,&
+      !$OMP  psi_bilinear_matrix_transp_rows, psi_bilinear_matrix_transp_columns,&
+      !$OMP  psi_bilinear_matrix_order_reverse, psi_det_alpha_unique, psi_det_beta_unique,&
+      !$OMP  psi_bilinear_matrix_values, psi_bilinear_matrix_transp_values,&
[…]

### 2021-04-07 stable/yuan_plugins/plot_on_top_z.irp.f
added plot_on_top_z.irp.f in Yuan

@@ -1,0 +1,65 @@
+program print_on_top_z
+ implicit none
+ io_two_body_rdm_ab = "Read"
+ touch io_two_body_rdm_ab 
+ no_core_density = .True.
+ touch no_core_density
+ call write_on_top_in_real_space 
+ call integrated_on_top
+end
+
+
+subroutine write_on_top_in_real_space
+ implicit none
+ BEGIN_DOC
+! This routines is a simple example of how to plot the on-top pair density on a simple 1D grid 
+ END_DOC
+ double precision :: zmax,dz,r(3),on_top_in_r,total_density,zcenter,dist
+ double precision :: core_dens, inact_dens,act_dens(2,1)
+
+ integer :: nz,i,istate
+ character*(128)                :: output
+ integer                        :: i_unit_output,getUnitAndOpen
+ PROVIDE ezfio_filename
+ output=trim(ezfio_filename)//'.on_top'
+ print*,'output = ',trim(output)
+ i_unit_output = getUnitAndOpen(output,'w')
+
+
+ zmax = 5.0d0
+ print*,'nucl_coord(1,3) = ',nucl_coord(1,3)
+ print*,'nucl_coord(2,3) = ',nucl_coord(2,3)
+ dist = dabs(nucl_coord(1,3) - nucl_coord(2,3))
+ zmax += dist
+ zcenter = (nucl_coord(1,3) + nucl_coord(2,3))*0.5d0
+ print*,'zcenter = ',zcenter
+ print*,'zmax    = ',zmax
+ nz = 1000
+ dz = zmax / dble(nz)
+ r(:) = 0.d0
+ r(3) = zcenter -zmax * 0.5d0                                                                                                                                          
+ print*,'r(3)    = ',r(3)
+ istate = 1
+
+  write(i_unit_output,*)" z,    on-top(z)"
+ do i = 1, nz
+  call give_on_top_in_r_one_state(r,istate,on_top_in_r)
+!  call give_cas_density_in_r(core_dens,inact_dens,act_dens,total_density,r)
+  write(i_unit_output,*)r(3),on_top_in_r
+  r(3) += dz
+ enddo
+
+end
+
+subroutine integrated_on_top
+ implicit none
+ integer :: ipoint, istate
+ double precision :: weight,accu
+ istate = 1
+ accu = 0.d0
+ do ipoint = 1, n_points_final_grid
+  weight = final_weight_at_r_vector(ipoint)
[…]

### 2021-04-13 cusp_j/paper/paper_draft.tex
added plot_on_top_z.irp.f in Yuan
fixed a stupid bug in fcidump_tc_h_3_body_sym.irp.f with active indices

@@
  \begin{aligned}
+  \label{eq:grad_mur_1}
  \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
@@
 & \big( \bri{1} - \bri{2}\big)\cdot
-\bigg(\frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
-  -   \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
+\bigg(\frac{e^{- \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
+  -   \frac{e^{- \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
   &+ \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
@@
 % f(x) = (3*erf(mu*x) - 1)/(2*x) + 1.5*mu/sqpi * exp(-(mu*x)**2.) - 0.25 * (1 - erf(mu*x))**2.
-
-\section{Form of the adjoint operator}
-One can write $\tilde{H}[\mu]$ in terms of its hermitian and non hermitian parts 
-\begin{equation}
- \tilde{H}[\mu] = \tilde{H}^h[\mu] + \tilde{H}^{nh}[\mu]
-\end{equation}
-where the hermitian part is 
-\begin{equation}
- \tilde{H}^h[\mu] = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) 
-\end{equation}
-with 
-\begin{equation}
- \Delta_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
-\end{equation}
-\begin{equation}
- \big( \nabla_1 u(r_{12},\mu)\big)^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}, 
-\end{equation}
-and 
-\begin{equation}
- \tilde{H}^{nh}[\mu] = \nabla_{1}u(r_{12},\mu) \cdot \big(\nabla_1 - \nabla_2\big)
-\end{equation}
-The adjoint of the non hermitian operator $\tilde{H}^{nh}[\mu]$ is 
-\begin{equation}
- \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger =  \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger - \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger,
-\end{equation}
-with 
-\begin{equation}
- \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 
-                                                                - \nabla_1^2 u(r_{12},\mu)
-\end{equation}
-\begin{equation}
- \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
-                                                                - \nabla_1 \cdot \nabla_2 u(r_{12},\mu)
-\end{equation}
-but as 
-\begin{equation}
- \nabla_2 u(r_{12},\mu) = - \nabla_{1}u(r_{12},\mu)
-\end{equation}
-one has
-\begin{equation}
- \nabla_1 \cdot \nabla_2 u(r_{12},\mu) = - \nabla_1^2 u(r_{12},\mu)
-\end{equation}
-and therefore 
-\begin{equation}
- \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
-                                                                + \nabla_1^2 u(r_{12},\mu)
-\end{equation}
-which gives for the adjoint of the non hermitian operator 
-\begin{equation}
- \bigg( \tilde{H}^{nh}[\mu]\bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu).
-\end{equation}
-Therefore the adjoint of the TC Hamiltonian is
-\begin{equation}
- \begin{aligned}
-\bigg(\tilde{H}[\mu]\bigg)^\dagger & = \tilde{H}^h[\mu] + \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger \\
-                                   & = \tilde{H}^h[\mu]  - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu)  \\
-                                   & = \tilde{H}^h[\mu]  - \tilde{H}^{nh}[\mu] - 2 \nabla_1^2 u(r_{12},\mu) 
- \end{aligned}
-\end{equation}
-Then 
-\begin{equation}
- \begin{aligned}
- \frac{\tilde{H}[\mu] + \bigg(\tilde{H}[\mu]\bigg)^\dagger}{2}& = \tilde{H}^h[\mu] - \nabla_1^2 u(r_{12},\mu) \\
-                                                              & = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) - \nabla_1^2 u(r_{12},\mu) \\
-                                                              & = H - \bigg( 2 \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) \\
-                                                              & = h_c + \frac{1}{r_{12}} - 2 \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} 
-                                                                 - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4} \\
-                                                              & = h_c - \frac{1 - 2 \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}
+\subsection{Proposal of an ad-hoc symmetrization}
+Let us assume that we only take a non symmetric form 
+\begin{equation}
+ \tilde{u}(\bd{r_1},\bd{r_2}) = u(r_{12};\mur{1}), 
+\end{equation}
+and we will see afterwards how to symmetrize the Hamiltonian.
+\subsubsection{Computation of $\bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2$ }
+therefore, according to Eq. \eqref{eq:grad_mur_1} one has 
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
+                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
+ \end{aligned}
+\end{equation}
+Therefore, the computation of $\big( \deriv{}{x_1}{} u(r_{12};\mur{1}) \big)^2$ yields 
+\begin{equation}
+ \begin{aligned}
+ \bigg( \deriv{}{x_1}{} u(r_{12};\mur{1}) \bigg)^2 = & \frac{\bigg(1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)\bigg)^2}{4 \big(r_{12}\big)^2}\big( x_1 - x_2)^2 \\
+ + & \frac{e^{-2(\mu(\bri{1}) r_{12})^2}}{4 \pi \mu(\bri{1})^4} \bigg(\deriv{\mur{1}}{x_1}{} \bigg)^2 \\ 
+ + & \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{r_{12}}\big( x_1 - x_2) \frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.
+ \end{aligned}
+\end{equation}
+Therefore, the computation of $\bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2$ yields 
+\begin{equation}
+ \begin{aligned}
+  \bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2  = &\frac{\bigg(1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)\bigg)^2}{4} 
+   +   \frac{e^{-2(\mu(\bri{1}) r_{12})^2}}{4 \pi \mu(\bri{1})^4} \bigg( \nabla_1  \mur{1}\bigg)^2 \\ 
+   + & \nabla_1  \mur{1} \, \cdot \, \big( \br{}_1 - \br{}_2\big) \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{r_{12}} \frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi}\mu(\bri{1})^2} 
+ \end{aligned}
+\end{equation}
+
+\subsubsection{Computation of $\nabla_1^2  u(r_{12};\mur{1})$ }
+One has to perform first 
+\begin{equation}
+ \begin{aligned}
+  \deriv{}{x_1}{2} u(r_{12};\mur{1}) =  & \deriv{}{x_1}{}  \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \bigg) \\ 
+      + & \deriv{}{x_1}{}  \bigg(\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{} \bigg).
+ \end{aligned}
+\end{equation}
+Let us begin with the first term 
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{x_1}{}  \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \bigg)  = 
+&  \big( x_1 - x_2 \big) \deriv{}{x_1}{} \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \bigg) \\
++ & \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}.
+ \end{aligned}
+\end{equation}
+Then on has that 
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{x_1}{} \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \bigg) &= 
+ \deriv{}{r_{12}}{} \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{r_{12}}{x_1}{} \\  
+ & + \deriv{}{\mur{1}}{}\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{\mur{1}}{x_1}{}.
+ \end{aligned}
+\end{equation}
+The first term reads 
+\begin{equation}
+ \begin{aligned}
+& \deriv{}{r_{12}}{} \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{r_{12}}{x_1}{} = \\
+& -\frac{(x_1 - x_2)}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mu(\br{}_1) r_{12}\big)^2}\bigg).  
  \end{aligned}

### 2021-04-13 dev/three_body_ints/fcidump_tc_h_3_body.irp.f

@@ -38,7 +38,7 @@ subroutine fcidump_3_tc
         integral = three_body_ints(i,j,m,k,l,n)
         integral = integral * 1.d0/3.d0 !!!! For NECI convention 
         if(dabs(integral).lt.1.d-12)cycle
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i, j, m, k, l, n
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, ii, jj, mm, kk, ll, nn
        enddo
       enddo
      enddo

### 2021-04-13 dev/three_body_ints/fcidump_tc_h_3_body_sym.irp.f

@@ -37,17 +37,17 @@ subroutine fcidump_3_tc
         call give_integrals_3_body(i,j,m,k,l,n,integral)
         integral = -integral * 1.d0/3.d0 !!!! For NECI convention 
         if(dabs(integral).lt.1.d-12)cycle
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i, j, m, k, l, n
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,j,m,i,l,n
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,l,m,i,j,n
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,j,n,i,l,m
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,l,n,i,j,m
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i,l,m,k,j,n
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,l,m,i,j,n
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i,l,n,k,j,m
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i,j,n,k,l,m
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, k,j,n,i,l,m
-        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, i,l,n,k,j,m
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, ii,jj,mm,kk,ll,nn
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, kk,jj,mm,ii,ll,nn
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, kk,ll,mm,ii,jj,nn
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, kk,jj,nn,ii,ll,mm
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, kk,ll,nn,ii,jj,mm
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, ii,ll,mm,kk,jj,nn
+        write(i_unit_output_physicist,'(E20.10,6(I3,X))') integral, kk,ll,mm,ii,jj,nn
[…]

### 2021-04-26 cusp_j/paper/paper_draft.tex
added rsdft_cipsi

@@
 % f(x) = (3*erf(mu*x) - 1)/(2*x) + 1.5*mu/sqpi * exp(-(mu*x)**2.) - 0.25 * (1 - erf(mu*x))**2.
-\subsection{Proposal of an ad-hoc symmetrization}
-Let us assume that we only take a non symmetric form 
-\begin{equation}
- \tilde{u}(\bd{r_1},\bd{r_2}) = u(r_{12};\mur{1}), 
-\end{equation}
-and we will see afterwards how to symmetrize the Hamiltonian.
+\subsection{Proposal of different symmetrization}
+Let us assume that we only take the following form as a Jastrow factor 
+\begin{equation}
+ J(\br_1,\br_2) = \frac{e^{ u(r_{12};\mur{1})} + e^{u(r_{12};\mur{2})}}{2}. 
+\end{equation}
+
 \subsubsection{Computation of $\bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2$ }
@@
 \begin{equation}
+ \label{eq:_d_x_11}
  \begin{aligned}
@@
 & \deriv{}{r_{12}}{} \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{r_{12}}{x_1}{} = \\
-& -\frac{(x_1 - x_2)}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mu(\br{}_1) r_{12}\big)^2}\bigg).  
+& -\frac{(x_1 - x_2)}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mu(\br{}_1) r_{12}\big)^2}\bigg),  
+ \end{aligned}
+\end{equation}
+and the second term reads
+\begin{equation}
+ \begin{aligned}
+ \deriv{}{\mur{1}}{}\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{\mur{1}}{x_1}{}  = \\
+ - \deriv{\mur{1}}{x_1}{} \frac{e^{-\big(\mur{1} r_{12}\big)^2}}{\sqrt{\pi}},
+ \end{aligned}
+\end{equation}
+and eventually 
+\begin{equation}
+ \begin{aligned}
+& \deriv{}{x_1}{} \bigg(\frac{1 - \text{erf}\big(\mur{1} r_{12} \big)}{2 r_{12}} \bigg) = 
+- \deriv{\mur{1}}{x_1}{} \frac{e^{-\big(\mur(1) r_{12}\big)^2}}{\sqrt{\pi}}\\
+& -\frac{(x_1 - x_2)}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mur{1} r_{12}\big)^2}\bigg)
+ \end{aligned} 
+\end{equation}
+and therefore Eq. \eqref{eq:_d_x_11} becomes 
+\begin{equation}
+ \begin{aligned}
+& \deriv{}{x_1}{}  \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \bigg)  = 
+\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \\
+&- \deriv{\mur{1}}{x_1}{} \frac{(x_1 - x_2)e^{-\big(\mur{1} r_{12}\big)^2}}{\sqrt{\pi}}\\
+& -\frac{(x_1 - x_2)^2}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mur{1} r_{12}\big)^2}\bigg)
  \end{aligned}

### 2021-04-26 stable/rsdft_cipsi/test.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+
+# Check if the QP_ROOT environment variable is set. 
+if [[ -z ${QP_ROOT} ]]
+then
+  print "The QP_ROOT environment variable is not set."
+  print "Please reload the quantum_package.rc file."
+  exit -1
+fi
+ 
+# Get the absolute path of the current directory.
+currdir=${PWD}
+
+file_list="`ls ../func_ecmd/*.irp.f`"
+
+# Make a symbolic link for all scripts to be used in the ${QP_ROOT}/scripts/
+# directory. 
+ for i in $file_list
+ do 
+  echo $i
+  ln --symbolic  ${currdir}/$i  ${QP_ROOT}/src/functionals/
+ done

### 2021-05-13 cusp_j/He_wf/psi2morgan.f90
Gauss ints with mu(r)

@@ -1,0 +1,150 @@
+program pouet 
+ implicit none
+ integer :: ntheta,i
+ double precision, allocatable  :: theta(:), r12_array(:), psi_ex(:)
+ double precision :: r1,r2,r12,psimorgan,psi,psi2, a0,dtheta
+ double precision, allocatable :: r1_array(:), r2_array(:,:)
+ ntheta = 100
+ allocate(theta(ntheta), r12_array(ntheta), psi_ex(ntheta),r1_array(3),r2_array(3,ntheta))
+ dtheta = 2.d0 * dacos(-1.d0)/dble(ntheta)
+ theta(1) = -dacos(-1.d0)
+ do i = 2, ntheta
+  theta(i) = theta(i-1) + dtheta
+ enddo
+ r1 = 2.00d0
+ r2 = r1
+ r1_array = 0.d0 
+ r1_array(1) = r1
+ do i = 1, ntheta
+  r2_array(3,i) = r1_array(3)
+  r2_array(1,i) = r1 * dcos(theta(i))
+  r2_array(2,i) = r1 * dsin(theta(i))
+  r12_array(i) = (r1_array(1) - r2_array(1,i))**2.d0 
+  r12_array(i) = r12_array(i) + (r1_array(2) - r2_array(2,i))**2.d0 
+  r12_array(i) = r12_array(i) + (r1_array(3) - r2_array(3,i))**2.d0 
+  r12_array(i) = dsqrt(r12_array(i))
+ enddo
+
+ do i = 1, ntheta
+  r12 = r12_array(i) 
+  psi = psi2(r1,r2,r12)
+  write(33,'(100(F16.10,X))')theta(i),r12,dsqrt(psi),r2_array(1,i),r2_array(2,i),r2_array(3,i)
+  write(34,*)'theta_array_psi_ex(',i,',7) = dble(',theta(i),')'
+  write(34,*)'array_psi_ex(',i,',7) = dble(',dsqrt(psi),')'
+ enddo
+
+ close(2)
+end
+
+
+      double precision function psi2(r1,r2,r12)
+      implicit none
+      integer j,l,m,maxci,maxcin,n,paramsread
+      double precision chi, r1,r12,r2, psimorgan, scale, z
+      parameter (maxci=418)
+      common/frankoi/j(maxci),l(maxci),m(maxci),n(maxci),paramsread
+      common/frankor/chi(maxci),scale,z
+!     paramsread assumed to be initialized to !=1
[…]

### 2021-05-13 dev/ao_one_ints_slater/gauss_ints.irp.f

@@ -115,6 +115,9 @@ end
 
 double precision function overlap_gauss_r12_ao(D_center,delta,i,j)
  implicit none
+ BEGIN_DOC
+! \int dr AO_i(r) AO_j(r) e^{-delta |r-D_center|^2}
+ END_DOC
  integer, intent(in) :: i,j
  double precision, intent(in) :: D_center(3), delta
 

### 2021-05-13 dev/deriv_r12_ints/deriv_one_e_ints.irp.f

@@ -85,7 +85,7 @@ subroutine phi_j_erf_mu_r_dxyz_phi(i,j,mu_in, C_center, dxyz_ints)
      power_B_tmp(mm) += 1
      contrib = NAI_pol_mult_erf(A_center,B_center,power_A,power_B_tmp,alpha,beta,C_center,n_pt_in,mu_in)  
      dxyz_ints(mm) += contrib * (-2.d0 * beta )  * ao_coef_normalized_ordered_transp(l,j)             &
-                                                  * ao_coef_normalized_ordered_transp(m,i) 
+                                                 * ao_coef_normalized_ordered_transp(m,i) 
     enddo
   enddo
  enddo

### 2021-05-13 dev/mu_of_r_tc_ints/gauss_int_mu.irp.f

@@ -1,0 +1,123 @@
+BEGIN_PROVIDER [ double precision, gauss_ij_rk,  ( ao_num, ao_num,n_points_final_grid)]
+ implicit none
+ BEGIN_DOC
+! mu_of_r_gauss(j,i,R) = int dr phi_i(r) phi_j(r) exp(-\mu(R) |r - R|^2)
+ END_DOC
+ integer :: i,j,ipoint
+ double precision :: mu,r(3),overlap_gauss_r12_ao
+ double precision :: int_mu, delta
+ provide mu_erf final_grid_points constant_mu 
+ double precision :: wall0, wall1
+ call wall_time(wall0)
+ if(constant_mu)then
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (i,j,ipoint,mu,r,int_mu,delta) & 
+ !$OMP SHARED (ao_num,n_points_final_grid,mu_erf,gauss_ij_rk,final_grid_points)
+ !$OMP DO SCHEDULE (dynamic)
+ do ipoint = 1, n_points_final_grid
+   do i = 1, ao_num
+    do j = i, ao_num
+     mu = mu_erf 
+     r(1) = final_grid_points(1,ipoint)
+     r(2) = final_grid_points(2,ipoint)
+     r(3) = final_grid_points(3,ipoint)
+     delta = mu * mu
+     int_mu = overlap_gauss_r12_ao(r,delta,i,j)
+     gauss_ij_rk(j,i,ipoint)= int_mu 
+   enddo
+  enddo
+ enddo
+ !$OMP END DO
+ !$OMP END PARALLEL
+
+ else 
+  provide mu_of_r_prov
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (i,j,ipoint,mu,r,int_mu,delta) & 
+ !$OMP SHARED (ao_num,n_points_final_grid,mu_of_r_prov,gauss_ij_rk,final_grid_points)
+ !$OMP DO SCHEDULE (dynamic)
+ do ipoint = 1, n_points_final_grid
+   do i = 1, ao_num
+    do j = i, ao_num
+     mu = mu_of_r_prov(ipoint,1)
+     delta = mu * mu
+     r(1) = final_grid_points(1,ipoint)
+     r(2) = final_grid_points(2,ipoint)
[…]

### 2021-05-13 dev/mu_of_r_tc_ints/mu_of_r_tc_ints.irp.f

@@ -1,0 +1,9 @@
+program mu_of_r_tc_ints
+  implicit none
+  BEGIN_DOC
+! TODO : Put the documentation of the program here
+  END_DOC
+  constant_mu = .False.
+  touch constant_mu
+  call test_gauss_ij_rk
+end

### 2021-05-13 dev/ao_one_ints_slater/gauss_ints.irp.f
added some stuffs

@@ -315,34 +315,6 @@ double precision function overlap_gauss_xyz_r12_ao_specific(D_center,delta,i,j,m
 end
 
 
-!double precision function overlap_gauss_r12_ao(D_center,delta,i,j)
-! implicit none
-! BEGIN_DOC
-! \int dr AO_i(r) AO_j(r) e^{-delta |r-D_center|^2}
-! END_DOC
-! integer, intent(in) :: i,j
-! double precision, intent(in) :: D_center(3), delta
-!
-! integer :: num_a,num_b,power_A(3), power_B(3),l,k
-! double precision :: A_center(3), B_center(3),overlap_gauss_r12,alpha,beta,analytical_j
-! num_A = ao_nucl(i)
-! power_A(1:3)= ao_power(i,1:3)
-! A_center(1:3) = nucl_coord(num_A,1:3)
-! num_B = ao_nucl(j)
-! power_B(1:3)= ao_power(j,1:3)
-! B_center(1:3) = nucl_coord(num_B,1:3)
-! overlap_gauss_r12_ao = 0.d0
-! do l=1,ao_prim_num(i)
-!  alpha = ao_expo_ordered_transp(l,i)     
-!  do k=1,ao_prim_num(j)
-!   beta = ao_expo_ordered_transp(k,j)     
-!   analytical_j = overlap_gauss_r12(D_center,delta,A_center,B_center,power_A,power_B,alpha,beta)
-!   overlap_gauss_r12_ao += analytical_j *  ao_coef_normalized_ordered_transp(l,i)             &
-!                                        *  ao_coef_normalized_ordered_transp(k,j) 
-!  enddo 
-! enddo
-!end
-
 subroutine overlap_gauss_r12_all_ao(D_center,delta,aos_ints)
  implicit none
  double precision, intent(in) :: D_center(3), delta
@@ -433,31 +405,4 @@ double precision function overlap_gauss_r12_ao(D_center,delta,i,j)
  enddo
 end
 
-!subroutine overlap_gauss_r12_all_ao(D_center,delta,aos_ints)
-! implicit none
-! double precision, intent(in) :: D_center(3), delta
-! double precision, intent(out):: aos_ints(ao_num,ao_num)
-!
-! integer :: num_a,num_b,power_A(3), power_B(3),l,k,i,j
[…]

### 2021-05-13 dev/deriv_r12_ints/deriv_one_e_ints.irp.f

@@ -125,3 +125,125 @@ double precision function phi_j_erf_mu_r_phi(i,j,mu_in, C_center)
  enddo
 end
 
+
+subroutine erf_mu_gauss_xyz_ij_ao(i,j,mu, C_center, delta,gauss_ints)
+ implicit none
+ BEGIN_DOC
+  ! gauss_ints(m) =   \int dr exp(-delta (r - C)^2 ) x/y/z * erf(mu |r-r'|)/ |r-r'| * AO_i(r') * AO_j(r')
+  !
+  ! with m = 1 ==> x, m = 2, m = 3 ==> z
+  !
+  !      m = 4 ==> no x/y/z
+ END_DOC
+ integer, intent(in) :: i,j
+ double precision, intent(in) :: mu, C_center(3),delta
+ double precision, intent(out):: gauss_ints(4)
+
+ integer :: num_A,power_A(3), num_b, power_B(3)
+ double precision :: alpha, beta, A_center(3), B_center(3),contrib,NAI_pol_mult_erf
+ double precision :: xyz_ints(4)
+ integer :: n_pt_in,l,m,mm
+ n_pt_in = n_pt_max_integrals
+ ! j 
+ num_A = ao_nucl(j)
+ power_A(1:3)= ao_power(j,1:3)
+ A_center(1:3) = nucl_coord(num_A,1:3)
+ ! i 
+ num_B = ao_nucl(i)
+ power_B(1:3)= ao_power(i,1:3)
+ B_center(1:3) = nucl_coord(num_B,1:3)
+
+ gauss_ints = 0.d0
+ do l=1,ao_prim_num(j)
+  alpha = ao_expo_ordered_transp(l,j)
+  do m=1,ao_prim_num(i)
+    beta = ao_expo_ordered_transp(m,i)
+    call erf_mu_gauss_xyz(C_center,delta,mu,A_center,B_center,power_A,power_B,alpha,beta,n_pt_in,xyz_ints)
+    do mm = 1, 4
+     gauss_ints(mm) += xyz_ints(mm)  * ao_coef_normalized_ordered_transp(l,j)             &
+                                     * ao_coef_normalized_ordered_transp(m,i) 
+    enddo
+  enddo
+ enddo
+end
+
+
+
+
+subroutine erf_mu_gauss_xyz(D_center,delta,mu,A_center,B_center,power_A,power_B,alpha,beta,n_pt_in,xyz_ints)
+  BEGIN_DOC
[…]

### 2021-05-13 dev/deriv_r12_ints/routines_test.irp.f

@@ -1,0 +1,73 @@
+program test_stufff
+ implicit none
+ call test_erf_mu_gauss_xyz
+end
+
+subroutine test_erf_mu_gauss_xyz
+ implicit none
+ integer :: ipoint,i,j,m,jpoint
+ double precision :: r1(3),derf_mu_x
+ double precision :: C_center(3), weight1,mu,r12,integrals(4),integral_tmp(3,ao_num,ao_num),delta, num_int
+ double precision :: integral
+ double precision, allocatable :: aos_array_r1(:),ao_mat_xyz(:,:,:)
+ allocate(ao_mat_xyz(3,ao_num,ao_num),aos_array_r1(ao_num))
+ do jpoint = 1, n_points_final_grid
+  mu = mu_of_r_prov(jpoint,1)
+  delta = mu * mu
+  C_center(:) = final_grid_points(:,jpoint)
+  do i = 1, ao_num
+   do j = 1, ao_num
+    call erf_mu_gauss_xyz_ij_ao(i,j,mu, C_center, delta,integrals)
+    do m = 1, 3
+     integral_tmp(m,j,i) = integrals(4) * C_center(m) - integrals(m) 
+    enddo
+   enddo
+  enddo
+  ao_mat_xyz = 0.d0
+  do ipoint = 1, n_points_final_grid
+   r1(1) = final_grid_points(1,ipoint)
+   r1(2) = final_grid_points(2,ipoint)
+   r1(3) = final_grid_points(3,ipoint)
+   call give_all_aos_at_r(r1,aos_array_r1)
+   weight1 = final_weight_at_r_vector(ipoint)
+   r12 = (r1(1) - C_center(1))**2.d0 + (r1(2) - C_center(2))**2.d0 + (r1(3) - C_center(3))**2.d0 
+   r12 = dsqrt(r12)
+   if(r12.lt.1.d-6)cycle
+   do i = 1, ao_num
+    do j = 1, ao_num
+     do m = 1, 3
+      ao_mat_xyz(m,j,i)  += aos_array_r1(i) * aos_array_r1(j) * weight1 * dexp(-mu*mu*r12*r12) * (1.d0 / r12 - derf_mu_x(mu,r12)) * (r1(m) - C_center(m))
+     enddo
+    enddo
+   enddo
+  enddo
+
+
+ double precision :: accu1relat,accu1
+  accu1 = 0.d0
+  accu1relat = 0.d0
+  print*,'jpoint = ',jpoint
+  do i = 1, ao_num
[…]

### 2021-05-13 dev/mu_of_r_tc_ints/erf_mu_squared.irp.f

@@ -1,5 +1,8 @@
 subroutine fit_erf_mu_squared(mu, expo_fit, coef_fit)
  implicit none
+ BEGIN_DOC
+! fit of (erf(mu * |r - r'|) - 1)^2 with a linear combination of Gaussians
+ END_DOC
  double precision, intent(in) :: mu
  double precision, intent(out):: expo_fit(n_max_fit_slat)
  double precision, intent(out):: coef_fit(n_max_fit_slat)
@@ -16,6 +19,11 @@ end
 
 BEGIN_PROVIDER [double precision, erf_mu_squared_ij_rk,( ao_num, ao_num,n_points_final_grid)]
  implicit none
+ BEGIN_DOC
+! erf_mu_squared_ij_rk(i,j,r) = \int dr' phi_i(r') phi_j(r') (erf(mu(r) * |r - r'|) - 1)^2
+!
+! it is fitted with fit_erf_mu_squared
+ END_DOC
  double precision :: expo_fit(n_max_fit_slat)
  double precision :: coef_fit(n_max_fit_slat),overlap_gauss_r12_ao
  double precision :: mu,r(3),int_mu,delta,wall0,wall1

### 2021-05-13 dev/mu_of_r_tc_ints/erf_r12_r12.irp.f

@@ -1,0 +1,88 @@
+
+BEGIN_PROVIDER [double precision, erf_mu_r12_inv_r12_rk,( ao_num, ao_num,n_points_final_grid)]
+ implicit none
+ BEGIN_DOC
+! erf_mu_r12_inv_r12_rk(i,j,r) = \int dr' phi_i(r') phi_j(r') erf(mu(r) |r - r'|)/|r-r'|
+ END_DOC
+ double precision :: mu,r(3),int_mu,delta,wall0,wall1
+ integer :: i,j,ipoint
+  provide mu_of_r_prov
+ call wall_time(wall0)
+ !$OMP PARALLEL                  &
+ !$OMP DEFAULT (NONE)            &
+ !$OMP PRIVATE (i,j,ipoint,mu,r,int_mu,delta) & 
+ !$OMP SHARED (ao_num,n_points_final_grid,mu_of_r_prov,erf_mu_r12_inv_r12_rk,final_grid_points)
+ !$OMP DO SCHEDULE (dynamic)
+ do ipoint = 1, n_points_final_grid
+  do i = 1, ao_num
+   do j = i, ao_num
+    mu = mu_of_r_prov(ipoint,1)
+    r(1) = final_grid_points(1,ipoint)
+    r(2) = final_grid_points(2,ipoint)
+    r(3) = final_grid_points(3,ipoint)
+    int_mu = phi_j_erf_mu_r_phi(i,j,mu, r)
+    erf_mu_r12_inv_r12_rk(j,i,ipoint) = int_mu 
+   enddo
+  enddo
+ enddo
+ !$OMP END DO
+ !$OMP END PARALLEL
+
+
+ do ipoint = 1, n_points_final_grid
+  do i = 1, ao_num
+   do j = 1, i-1
+    erf_mu_r12_inv_r12_rk(j,i,ipoint)= erf_mu_squared_ij_rk(i,j,ipoint)
+   enddo
+  enddo
+ enddo
+
+ call wall_time(wall1)
+ print*,'wall time for erf_mu_r12_inv_r12_rk  ',wall1 - wall0
+
+END_PROVIDER 
+
+
+BEGIN_PROVIDER [double precision, coulomb_rk,( ao_num, ao_num,n_points_final_grid)]
+ implicit none
+ BEGIN_DOC
+! coulomb_rk(i,j,r) = \int dr' phi_i(r') phi_j(r') 1/|r-r'|
+ END_DOC
[…]

### 2021-05-20 dev/mu_of_r_tc_ints/subr_deriv_pot_ao.irp.f
subr_deriv_pot_ao.irp.f is working but with transposed matrices ...

@@ -23,6 +23,8 @@ BEGIN_PROVIDER [ double precision, deriv_mu_r_pot_chemist_ao, (ao_num, ao_num, a
  deriv_mu_r_pot_chemist_ao = 0.d0
 
  call lapl_gamm_r1(deriv_mu_r_pot_chemist_ao)
+! call gamma_nabla_r1(deriv_mu_r_pot_chemist_ao)
+
  call wall_time(wall1)
  print*,''
  print*,''
@@ -51,7 +53,7 @@ subroutine lapl_gamm_r1(big_mat)
  double precision, allocatable :: a_mat(:,:,:)
  double precision :: cst
 
- print*,'computing all_gauss_r12_big_mat ...'
+ print*,'computing lapl_gamm_r1 ...'
  call wall_time(wall0)
  double precision :: wall0,wall1
  cst = 0.25d0 * inv_sq_pi 
@@ -70,12 +72,59 @@ subroutine lapl_gamm_r1(big_mat)
      enddo
     enddo
    enddo
-   call dgemm("N","N",ao_num*ao_num,ao_num*ao_num,n_points_final_grid,1.d0,gauss_ij_rk(1,1,1),ao_num*ao_num & 
-                     ,a_mat(1,1,1),n_points_final_grid,1.d0,big_mat,ao_num*ao_num)
+!   call dgemm("N","N",ao_num*ao_num,ao_num*ao_num,n_points_final_grid,1.d0,gauss_ij_rk(1,1,1),ao_num*ao_num & 
+!                     ,a_mat(1,1,1),n_points_final_grid,1.d0,big_mat,ao_num*ao_num)
+   call dgemm("T","T",ao_num*ao_num,ao_num*ao_num,n_points_final_grid,1.d0,a_mat(1,1,1),n_points_final_grid & 
+                     ,gauss_ij_rk(1,1,1),ao_num*ao_num,1.d0,big_mat,ao_num*ao_num)
 
  enddo
   call wall_time(wall1)
-  print*,'wall time for all_gauss_r12_big_mat ',wall1 - wall0   
+  print*,'wall time for lapl_gamm_r1 ',wall1 - wall0   
+end
+
+
+subroutine gamma_nabla_r1(big_mat)
+ implicit none
+ BEGIN_DOC
+! enters with the array big_mat and add the following integrals 
+!
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/big_array_ints.irp.f
added the physicist MOs integrals

@@ -105,243 +105,4 @@ BEGIN_PROVIDER [ double precision, big_array_naive, (ao_num, ao_num, ao_num, ao_
 END_PROVIDER 
 
 
-subroutine test_big_array
- implicit none
- integer :: i,j,k,l
- double precision :: accu1, accu2,contrib,exact,ao_two_e_integral_erf,ao_two_e_integral_eff_pot
- accu1 = 0.d0
- accu2 = 0.d0
-  do l = 1, ao_num
-   do j = 1, ao_num
-    do k = 1, ao_num
-     do i = 1, ao_num
-      exact = ao_two_e_integral_erf(i,k,j,l) 
-      exact += ao_two_e_integral_eff_pot(i,k,j,l)
 
-      contrib = dabs(exact - big_array_naive(i,k,j,l))
-      accu1 += contrib
-      if(contrib .gt. 1.d-10)then
-       print*,'naive'
-       print*,'i,k,j,l',i,k,j,l
-       print*,contrib,exact, big_array_naive(i,k,j,l)
-      endif
-
-      contrib = dabs(scalar_mu_r_pot_chemist_ao(i,k,j,l) - exact)
-      accu2 += contrib
-      if(contrib .gt. 1.d-10)then
-       print*,'dgemm'
-       print*,'i,k,j,l',i,k,j,l
-       print*,contrib,exact, scalar_mu_r_pot_chemist_ao(i,k,j,l)
-      endif
-     enddo
-    enddo
-   enddo
-  enddo
-  print*,'accu naive  = ',accu1/dble(ao_num**4)
-  print*,'accu dgemm  = ',accu2/dble(ao_num**4)
-
-end
-
-subroutine test_int_r6
- implicit none
- include 'constants.include.F'
- integer :: ipoint,i,j,k,l,m,jpoint
- double precision :: r1(3),r2(3),weight1,weight2,weight_tot
- double precision :: nabla_sq_term,cst_nabla,ao_prod_r1,ao_prod_r2,nabla_r12_1,erf_mu_sq,nabla_r12_2
- double precision :: thr, sq_thr,cst_nabla_r12_1,cst_gauss_r12,gauss_r12_mu_r1,erf_mur1,cst_nabla_r12_2
- double precision, allocatable :: accu(:,:,:,:)
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/long_range_int_mu_r.irp.f

@@ -1,45 +1,4 @@
 
- BEGIN_PROVIDER[double precision, aos_in_r_extra_grid_array, (ao_num,n_points_extra_final_grid)]
- implicit none
- BEGIN_DOC
- ! aos_in_r_extra_grid_array(i,j)        = value of the ith ao on the jth grid point
- END_DOC
- integer :: i,j
- double precision :: aos_array(ao_num), r(3)
- !$OMP PARALLEL DO &
- !$OMP DEFAULT (NONE)  &
- !$OMP PRIVATE (i,r,aos_array,j) & 
- !$OMP SHARED(aos_in_r_extra_grid_array,n_points_extra_final_grid,ao_num,final_grid_points_extra)
- do i = 1, n_points_extra_final_grid
-  r(1) = final_grid_points_extra(1,i)
-  r(2) = final_grid_points_extra(2,i)
-  r(3) = final_grid_points_extra(3,i)
-  call give_all_aos_at_r(r,aos_array)
-  do j = 1, ao_num
-   aos_in_r_extra_grid_array(j,i) = aos_array(j)
-  enddo
- enddo
- !$OMP END PARALLEL DO
-
- END_PROVIDER
-
-
- BEGIN_PROVIDER[double precision, aos_in_r_extra_grid_array_transp, (n_points_extra_final_grid,ao_num)]
- implicit none
- BEGIN_DOC
- ! aos_in_r_extra_grid_array_transp(i,j) = value of the jth ao on the ith grid point
- END_DOC
- integer :: i,j
- double precision :: aos_array(ao_num), r(3)
- do i = 1, n_points_extra_final_grid
-  do j = 1, ao_num
-   aos_in_r_extra_grid_array_transp(i,j) = aos_in_r_extra_grid_array(j,i) 
-  enddo
- enddo
-
- END_PROVIDER
-
-
 
 subroutine all_erf_mu_r1_lr_int_big_mat(big_mat)
  implicit none

### 2021-06-01 dev/mu_of_r_tc_ints/subr_deriv_pot_ao.irp.f

@@ -2,7 +2,7 @@
 BEGIN_PROVIDER [ double precision, deriv_mu_r_pot_chemist_ao, (ao_num, ao_num, ao_num, ao_num)]
  implicit none
  BEGIN_DOC
-! deriv_mu_r_pot_chemist_ao(i,k,j,l) = \int dr1 \int dr2 \phi_i(r1) \phi_k(r1) deriv_op \phi_j(r2) \phi_l(r2)
+! deriv_mu_r_pot_chemist_ao(i,k,j,l) = \int dr1 \int dr2  \phi_l(r2) \phi_k(r1) deriv_op [\phi_j(r2) \phi_i(r1)]
 !
 ! ALSO :: it is non hermitian !! BY convention the differential operators are applied to i(r1) ,j(r2)  
 !
@@ -22,8 +22,8 @@ BEGIN_PROVIDER [ double precision, deriv_mu_r_pot_chemist_ao, (ao_num, ao_num, a
 
  deriv_mu_r_pot_chemist_ao = 0.d0
 
-! call lapl_gamm_r1(deriv_mu_r_pot_chemist_ao)
-! call gamma_nabla_r1(deriv_mu_r_pot_chemist_ao)
+ call lapl_gamm_r1(deriv_mu_r_pot_chemist_ao)
+ call gamma_nabla_r1(deriv_mu_r_pot_chemist_ao)
  call non_hermit_r1(deriv_mu_r_pot_chemist_ao)
  call wall_time(wall1)
  print*,''
@@ -145,7 +145,7 @@ subroutine non_hermit_r1(big_mat)
  double precision, allocatable :: a_mat(:,:,:)
  double precision :: cst,r1(3)
 
- print*,'computing gamma_nabla_r1 ...'
+ print*,'computing non_hermit_r1 ...'
  call wall_time(wall0)
  double precision :: wall0,wall1
  cst = 0.5d0
@@ -208,12 +208,12 @@ subroutine non_hermit_r1(big_mat)
                      ,x_v_ij_erf_rk_transp_bis(1,1,1,m),n_points_final_grid,1.d0,big_mat,ao_num*ao_num)
  enddo
   call wall_time(wall1)
-  print*,'wall time for gamma_nabla_r1 ',wall1 - wall0   
+  print*,'wall time for non_hermit_r1 ',wall1 - wall0   
 end
 
 
 
-subroutine test_lapl_gamm_r1
+subroutine test_num_deriv_pot 
  implicit none
  include 'constants.include.F'
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/subr_deriv_pot_mo.irp.f

@@ -1,0 +1,331 @@
+
+BEGIN_PROVIDER [ double precision, deriv_mu_r_pot_chemist_mo, (mo_num, mo_num, mo_num, mo_num)]
+ implicit none
+ BEGIN_DOC
+! deriv_mu_r_pot_chemist_mo(i,k,j,l) = \int dr1 \int dr2 \phi_l(r2) \phi_k(r1) deriv_op [\phi_j(r2) \phi_i(r1)]
+!
+! ALSO :: it is non hermitian !! BY convention the differential operators are applied to i(r1) ,j(r2)  
+!
+! NOTICE THAT : because of mu(r1) and the non symmetric form of the Jastrow factor, the integrals ARE NOT SYMMETRIC in r1, r2 
+!
+! deriv_mu_r_pot_chemist_mo(i,k,j,l) NOT EQUAL TO deriv_mu_r_pot_chemist_mo(j,l,i,k) for instance 
+ END_DOC
+ integer :: i,j,k,l,m,n,p,q
+ double precision, allocatable :: mo_tmp_1(:,:,:,:),mo_tmp_2(:,:,:,:),mo_tmp_3(:,:,:,:)
+
+ allocate(mo_tmp_1(mo_num,ao_num,ao_num,ao_num))
+ mo_tmp_1 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do q = 1, ao_num
+     do k = 1, mo_num                                                                                                                        
+      !       (k n|p m)    = sum_q c_qk * (q n|p m)
+      mo_tmp_1(k,n,p,m) += mo_coef_transp(k,q) * deriv_mu_r_pot_chemist_ao(q,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+
+ free deriv_mu_r_pot_chemist_ao
+ allocate(mo_tmp_2(mo_num,mo_num,ao_num,ao_num))
+ mo_tmp_2 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do i = 1, mo_num
+     do k = 1, mo_num
+      !       (k i|p m) = sum_n c_ni * (k n|p m)
+      mo_tmp_2(k,i,p,m) += mo_coef_transp(i,n) * mo_tmp_1(k,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/subr_scalar_pot_ao.irp.f

@@ -18,8 +18,8 @@ BEGIN_PROVIDER [ double precision, scalar_mu_r_pot_chemist_ao, (ao_num, ao_num, 
 
  scalar_mu_r_pot_chemist_ao = 0.d0
 
- call all_erf_mu_r1_lr_int_big_mat_bis(scalar_mu_r_pot_chemist_ao)! 1/r12 analytically, erfc(mu(r1)r12)/r12 semi analytic
-! call all_erf_mu_r1_lr_int_big_mat(scalar_mu_r_pot_chemist_ao) 
+! call all_erf_mu_r1_lr_int_big_mat_bis(scalar_mu_r_pot_chemist_ao)! 1/r12 analytically, erfc(mu(r1)r12)/r12 semi analytic
+ call all_erf_mu_r1_lr_int_big_mat(scalar_mu_r_pot_chemist_ao) 
  call all_gauss_r12_big_mat(scalar_mu_r_pot_chemist_ao)
  call all_erf_r12_sq_big_mat(scalar_mu_r_pot_chemist_ao)
  call all_nabla_mu_r1_sq_big_mat(scalar_mu_r_pot_chemist_ao)
@@ -257,5 +257,249 @@ subroutine all_nabla_mu_r1_cdot_r12_erfc_r12_big_mat(big_mat)
   enddo
   call wall_time(wall1)
   print*,'wall time for all_nabla_mu_r1_cdot_r12_erfc_r12_big_mat ',wall1 - wall0   
+
+end
+
+
+subroutine test_num_scal_pot
+ implicit none
+ include 'constants.include.F'
+ integer :: ipoint,i,j,k,l,m,jpoint
+ double precision :: r1(3),r2(3),weight1,weight2,weight_tot
+ double precision :: nabla_sq_term,cst_nabla,ao_prod_r1,ao_prod_r2,nabla_r12_1,erf_mu_sq,nabla_r12_2
+ double precision :: thr, sq_thr,cst_nabla_r12_1,cst_gauss_r12,gauss_r12_mu_r1,erf_mur1,cst_nabla_r12_2
+ double precision, allocatable :: accu(:,:,:,:)
+ allocate(accu(ao_num, ao_num, ao_num, ao_num))
+ thr = 1.d-15
+ sq_thr = dsqrt(thr)
+ cst_nabla = -1.d0/(8.d0 * pi)
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/subr_scalar_pot_mo.irp.f

@@ -1,0 +1,233 @@
+BEGIN_PROVIDER [ double precision, scalar_mu_r_pot_chemist_mo, (mo_num, mo_num, mo_num, mo_num)]
+ implicit none
+ BEGIN_DOC
+! scalar_mu_r_pot_chemist_mo(i,k,j,l) = \int dr1 \int dr2 \phi_i(r1) \phi_k(r1) W_ee(r12,\mu(r1)) \phi_j(r2) \phi_l(r2)
+!
+! NOTICE THAT : because of mu(r1) and the non symmetric form of the Jastrow factor, the integrals ARE NOT SYMMETRIC in r1, r2 
+!
+! scalar_mu_r_pot_chemist_mo(i,k,j,l) NOT EQUAL TO scalar_mu_r_pot_chemist_mo(j,l,i,k) for instance 
+ END_DOC
+ integer :: i,j,k,l,m,n,p,q
+ double precision, allocatable :: mo_tmp_1(:,:,:,:),mo_tmp_2(:,:,:,:),mo_tmp_3(:,:,:,:)
+
+ allocate(mo_tmp_1(mo_num,ao_num,ao_num,ao_num))
+ mo_tmp_1 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do q = 1, ao_num
+     do k = 1, mo_num                                                                                                                        
+      !       (k n|p m)    = sum_q c_qk * (q n|p m)
+      mo_tmp_1(k,n,p,m) += mo_coef_transp(k,q) * scalar_mu_r_pot_chemist_ao(q,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+
+ free scalar_mu_r_pot_chemist_ao
+ allocate(mo_tmp_2(mo_num,mo_num,ao_num,ao_num))
+ mo_tmp_2 = 0.d0
+ do m = 1, ao_num
+  do p = 1, ao_num
+   do n = 1, ao_num
+    do i = 1, mo_num
+     do k = 1, mo_num
+      !       (k i|p m) = sum_n c_ni * (k n|p m)
+      mo_tmp_2(k,i,p,m) += mo_coef_transp(i,n) * mo_tmp_1(k,n,p,m)
+     enddo
+    enddo
+   enddo
+  enddo
+ enddo
+ deallocate(mo_tmp_1)
+ allocate(mo_tmp_1(mo_num,mo_num,mo_num,ao_num))
+ mo_tmp_1 = 0.d0
[…]

### 2021-06-01 dev/mu_of_r_tc_ints/test_mu_of_r_tc_ints.irp.f

@@ -8,8 +8,13 @@ program test_mu_of_r_tc_ints
 !  call test_gauss_ij_rk
 ! call test_erf_mu_squared_ij_rk
 ! call test_big_array
-! call test_int_r6
-! call test_big
- call test_big_array_3
- call test_lapl_gamm_r1
+! call test_big_array_3
+! call test_num_scal_pot
+! call test_num_deriv_pot
+! call test_big_array_mo
+! call test_big_array_mo_scal
+ call test_big_array_mo_deriv
+! call test_big_array_ao
+! call test_num_scal_pot_mo
+! call test_num_deriv_pot_mo
 end

### 2021-06-01 dev/one_e_ints_mu_of_r/erf_mu_squared.irp.f

@@ -29,7 +29,7 @@ BEGIN_PROVIDER [double precision, erf_mu_squared_ij_rk,(n_points_final_grid, ao_
  double precision :: mu,r(3),int_mu,delta,wall0,wall1,thr
  integer :: l,j,ipoint,ifit
   provide mu_of_r_for_ints
-  thr = 1.d-12
+  thr = 0.d0
   call fit_erf_mu_squared(1.d0, expo_fit, coef_fit)
  call wall_time(wall0)
   !$OMP PARALLEL                  &

### 2021-06-01 dev/one_e_ints_mu_of_r/erf_r12_r12.irp.f

@@ -99,7 +99,7 @@ BEGIN_PROVIDER [ double precision, gauss_erfc_mu_r12_inv_r12_rk_tmp,  (4,n_point
  double precision :: int_mu(3), delta, thr
  provide mu_erf final_grid_points 
  double precision :: wall0, wall1
- thr = 1.d-12
+ thr = 0.d0
  call wall_time(wall0)
   provide mu_of_r_for_ints
   print*,'Providing gauss_erfc_mu_r12_inv_r12_rk_tmp ...'

### 2021-06-01 dev/one_e_ints_mu_of_r/erfc_extra_grid.irp.f

@@ -1,4 +1,45 @@
 
+ BEGIN_PROVIDER[double precision, aos_in_r_extra_grid_array, (ao_num,n_points_extra_final_grid)]
+ implicit none
+ BEGIN_DOC
+ ! aos_in_r_extra_grid_array(i,j)        = value of the ith ao on the jth grid point
+ END_DOC
+ integer :: i,j
+ double precision :: aos_array(ao_num), r(3)
+ !$OMP PARALLEL DO &
+ !$OMP DEFAULT (NONE)  &
+ !$OMP PRIVATE (i,r,aos_array,j) & 
+ !$OMP SHARED(aos_in_r_extra_grid_array,n_points_extra_final_grid,ao_num,final_grid_points_extra)
+ do i = 1, n_points_extra_final_grid
+  r(1) = final_grid_points_extra(1,i)
+  r(2) = final_grid_points_extra(2,i)
+  r(3) = final_grid_points_extra(3,i)
+  call give_all_aos_at_r(r,aos_array)
+  do j = 1, ao_num
+   aos_in_r_extra_grid_array(j,i) = aos_array(j)
+  enddo
+ enddo
+ !$OMP END PARALLEL DO
+
+ END_PROVIDER
+
+
+ BEGIN_PROVIDER[double precision, aos_in_r_extra_grid_array_transp, (n_points_extra_final_grid,ao_num)]
+ implicit none
+ BEGIN_DOC
+ ! aos_in_r_extra_grid_array_transp(i,j) = value of the jth ao on the ith grid point
+ END_DOC
+ integer :: i,j
+ double precision :: aos_array(ao_num), r(3)
+ do i = 1, n_points_extra_final_grid
+  do j = 1, ao_num
+   aos_in_r_extra_grid_array_transp(i,j) = aos_in_r_extra_grid_array(j,i) 
+  enddo
+ enddo
+
+ END_PROVIDER
+
+
 BEGIN_PROVIDER [ double precision, erfc_extra_grid_rk, ( n_points_extra_final_grid , ao_num, ao_num)]
  implicit none
  BEGIN_DOC
@@ -8,22 +49,22 @@ BEGIN_PROVIDER [ double precision, erfc_extra_grid_rk, ( n_points_extra_final_gr
  double precision :: mu,r(3),NAI_pol_mult_erf_ao
  double precision :: int_mu, int_coulomb
  double precision :: thr
[…]

### 2021-06-01 dev/one_e_ints_mu_of_r/gauss_int_mu.irp.f

@@ -8,7 +8,7 @@ BEGIN_PROVIDER [ double precision, gauss_ij_rk,  (n_points_final_grid ,ao_num, a
  double precision :: int_mu, delta,thr
  provide mu_erf final_grid_points 
  double precision :: wall0, wall1
- thr = 1.d-12
+ thr = 0.d0
  call wall_time(wall0)
   provide mu_of_r_for_ints
  !$OMP PARALLEL                  &
@@ -56,7 +56,7 @@ BEGIN_PROVIDER [ double precision, gauss_2_ij_rk,  (n_points_final_grid ,ao_num,
  integer :: l,j,ipoint
  double precision :: mu,r(3),overlap_gauss_r12_ao
  double precision :: int_mu, delta,thr
- thr = 1.d-12
+ thr = 0.d0
  provide mu_erf final_grid_points 
  double precision :: wall0, wall1
  call wall_time(wall0)
@@ -112,7 +112,7 @@ BEGIN_PROVIDER [ double precision, gauss_ij_xyz_rk_tmp,  (3,n_points_final_grid,
  double precision :: int_mu(3), delta
  provide mu_erf final_grid_points 
  double precision :: wall0, wall1,thr
- thr = 1.d-12
+ thr = 0.d0
  call wall_time(wall0)
   provide mu_of_r_for_ints
  !$OMP PARALLEL                  &

### 2021-06-01 dev/one_e_ints_mu_of_r/mu_of_r_ints.irp.f

@@ -58,3 +58,48 @@
  call wall_time(wall1)
  print*,'Time to provide mu_of_r_for_ints = ',wall1-wall0
  END_PROVIDER 
+
+
+ BEGIN_PROVIDER [double precision, mu_of_r_extra_grid_for_ints, (n_points_extra_final_grid,N_states) ]
+ implicit none 
+ BEGIN_DOC
+ !
+ ! mu(r) and its gradient for evaluation f integrals for the TC hamiltonian
+ END_DOC
+ integer :: ipoint,istate,mm
+ double precision :: wall0,wall1
+ print*,'providing mu_of_r_extra_grid ...'
+! PROVIDE mo_two_e_integrals_in_map mo_integrals_map big_array_exchange_integrals 
+ call wall_time(wall0)
+
+ if(.not.constant_mu)then
+  do istate = 1, N_states
+   do ipoint = 1, n_points_extra_final_grid
+    if(mu_of_r_tc_ints.EQ."basis")then
+     mu_of_r_extra_grid_for_ints(ipoint,istate) =  mu_of_r_extra_grid_hf(ipoint)
+    else if(mu_of_r_tc_ints.EQ."rsc")then
+     mu_of_r_extra_grid_for_ints(ipoint,istate) =  mu_of_r_extra_grid_rs_c(ipoint,istate)
+    else if(mu_of_r_tc_ints.EQ."lda")then
+     mu_of_r_extra_grid_for_ints(ipoint,istate) =  mu_of_r_extra_grid_lda(ipoint,istate)
+    else 
+     print*,'you requested the following mu_of_r_extra_grid_tc_ints'
+     print*,mu_of_r_tc_ints
+     print*,'which does not correspond to any of the options for such keyword'
+     stop
+    endif
+   enddo
+  enddo
+ else
+  do istate = 1, N_states
+   do ipoint = 1, n_points_extra_final_grid
+    mu_of_r_extra_grid_for_ints(ipoint,istate) =  mu_erf 
+   enddo
+  enddo
+ endif
+
+
+ call wall_time(wall1)
+ print*,'Time to provide mu_of_r_extra_grid_for_ints = ',wall1-wall0
+ END_PROVIDER 
+
+

### 2021-06-01 dev/one_e_ints_mu_of_r/mu_rsc_lda.irp.f

@@ -94,6 +94,7 @@ end
 
 END_PROVIDER 
 
+
 double precision function mu_rs_c(rho)
  implicit none
  double precision, intent(in) :: rho
@@ -106,3 +107,92 @@ double precision function mu_rs_c(rho)
  mu_rs_c =  alpha_rs/dsqrt(rs) 
 
 end
+
+ BEGIN_PROVIDER [double precision, mu_of_r_extra_grid_rs_c, (n_points_extra_final_grid,N_states) ]
+ implicit none
+ integer :: ipoint,i,m
+ include 'constants.include.F'
+ double precision :: weight, rho_a_hf, rho_b_hf, rho_hf, mu_rs_c
+ average_mu_rs_c    = 0.d0
+ double precision :: elec_a,elec_b,r(3)
+ double precision :: mu_plus, mu_minus, dx,mu_lda
+ dx = 1.d-4
+ elec_a = 0.d0
+ elec_b = 0.d0
+ do ipoint = 1, n_points_extra_final_grid
+  weight = final_weight_at_r_vector_extra(ipoint)
+  r(:) = final_grid_points_extra(:,ipoint)
+  call dm_dft_alpha_beta_at_r(r,rho_a_hf,rho_b_hf)
+  rho_hf = rho_a_hf + rho_b_hf
+  mu_of_r_extra_grid_rs_c(ipoint,1) = mu_rs_c(rho_hf) 
+  elec_a += rho_a_hf * weight
+  elec_b += rho_b_hf * weight
+ enddo 
+
+END_PROVIDER 
+
+
+ BEGIN_PROVIDER [double precision, mu_of_r_extra_grid_lda , (n_points_extra_final_grid,N_states) ]
+ implicit none
+ integer :: ipoint,i,m
+ double precision :: weight, rho_a_hf, rho_b_hf, g0,rho_hf
+ double precision :: rs,grad_n
+ double precision :: g0_UEG_mu_inf
+ double precision :: cst_rs,alpha_rs
+ double precision :: elec_a,elec_b
+ double precision :: mu_plus, mu_minus, r(3),dx,mu_lda
+ dx = 1.d-4
+ average_mu_lda     = 0.d0
+ elec_a = 0.d0
+ elec_b = 0.d0
+ do ipoint = 1, n_points_extra_final_grid
+  weight = final_weight_at_r_vector_extra(ipoint)
[…]

### 2021-07-01 dev/finite_difference_method/write_eff_basis_ints_electric_field_x.irp.f
update dev irp files

@@ -1,0 +1,31 @@
+program write_effective_x_electric_field_hamiltonian
+ implicit none
+ BEGIN_DOC
+ !
+ ! The next programs that will run unto the EZFIO folder will, by default, 
+ !
+ ! have the one- and two-body integrals loaded from the EZFIO data. 
+ END_DOC
+ ! total one-e integrals 
+ io_mo_one_e_integrals = "None"
+ touch io_mo_one_e_integrals  
+ ! Vne integrals on the MO basis 
+ io_mo_integrals_n_e = "None"
+ touch io_mo_integrals_n_e
+ ! kinetic integrals on the MO basis 
+ io_mo_integrals_kinetic = "None"
+ touch io_mo_integrals_kinetic 
+ ! Vne integrals on the AO basis 
+ io_ao_integrals_n_e = "None"
+ touch io_ao_integrals_n_e 
+ ! kinetic integrals on the AO basis 
+ io_ao_integrals_kinetic = "None"
+ touch io_ao_integrals_kinetic 
+ io_ao_one_e_integrals = "None"
+ touch io_ao_one_e_integrals  
+
+ call save_v_ne_and_x_electric_filed_ao_ints
+end
+
+
+

### 2021-07-01 dev/pot_ecmd/print_tot_dipole.irp.f

@@ -1,0 +1,7 @@
+program print_tot_dipole
+ implicit none
+ read_wf = .True.
+ touch read_wf 
+ call print_tot_dipole_moment_only
+
+end

### 2021-07-01 dev/finite_difference_method/rout_write_int_electric_field.irp.f
added some components for dipole moments

@@ -1,25 +1,56 @@
-subroutine save_v_ne_and_electric_filed_ao_ints
+subroutine save_v_ne_and_x_electric_filed_ao_ints
  implicit none
  BEGIN_DOC 
 
  END_DOC
 
- call ezfio_set_ao_one_e_ints_ao_integrals_n_e(ao_one_e_potential_n_e_and_electric_field) ! ao_integrals_n_e - epsilon_<mu_z>_ao 
+ call ezfio_set_ao_one_e_ints_ao_integrals_n_e(ao_one_e_potential_n_e_and_electric_field_x) ! ao_integrals_n_e - epsilon_<mu_x>_ao 
  call ezfio_set_ao_one_e_ints_io_ao_integrals_n_e("Read")
 end
 
- BEGIN_PROVIDER [ double precision, ao_one_e_integrals_tot_electric_field,(ao_num,ao_num)]
-&BEGIN_PROVIDER [ double precision, ao_one_e_potential_n_e_and_electric_field,(ao_num,ao_num)]
+subroutine save_v_ne_and_y_electric_filed_ao_ints
+ implicit none
+ BEGIN_DOC 
+
+ END_DOC
+
+ call ezfio_set_ao_one_e_ints_ao_integrals_n_e(ao_one_e_potential_n_e_and_electric_field_y) ! ao_integrals_n_e - epsilon_<mu_y>_ao 
+ call ezfio_set_ao_one_e_ints_io_ao_integrals_n_e("Read")
+end
+
+subroutine save_v_ne_and_z_electric_filed_ao_ints
+ implicit none
+ BEGIN_DOC 
+
+ END_DOC
+
+ call ezfio_set_ao_one_e_ints_ao_integrals_n_e(ao_one_e_potential_n_e_and_electric_field_z) ! ao_integrals_n_e - epsilon_<mu_z>_ao 
+ call ezfio_set_ao_one_e_ints_io_ao_integrals_n_e("Read")
+end
+
+ BEGIN_PROVIDER [ double precision, ao_one_e_integrals_tot_electric_field_x,(ao_num,ao_num)]
+ &BEGIN_PROVIDER [ double precision, ao_one_e_integrals_tot_electric_field_y,(ao_num,ao_num)]
+ &BEGIN_PROVIDER [ double precision, ao_one_e_integrals_tot_electric_field_z,(ao_num,ao_num)]
+&BEGIN_PROVIDER [ double precision, ao_one_e_potential_n_e_and_electric_field_x,(ao_num,ao_num)]
[…]

### 2021-07-01 dev/finite_difference_method/write_eff_basis_ints_electric_field.irp.f

@@ -1,55 +1,0 @@
-program write_effective_electric_field_hamiltonian
- implicit none
- BEGIN_DOC
- !
- ! The next programs that will run unto the EZFIO folder will, by default, 
- !
- ! have the one- and two-body integrals loaded from the EZFIO data. 
- END_DOC
- read_wf = .true.
- touch read_wf
- ! total one-e integrals 
- io_mo_one_e_integrals = "None"
- touch io_mo_one_e_integrals  
- ! Vne integrals on the MO basis 
- io_mo_integrals_n_e = "None"
- touch io_mo_integrals_n_e
- ! kinetic integrals on the MO basis 
- io_mo_integrals_kinetic = "None"
- touch io_mo_integrals_kinetic 
- ! Vne integrals on the AO basis 
- io_ao_integrals_n_e = "None"
- touch io_ao_integrals_n_e 
- ! kinetic integrals on the AO basis 
- io_ao_integrals_kinetic = "None"
- touch io_ao_integrals_kinetic 
-
- ! regular 1/r12 integrals  on the MO basis
- io_mo_two_e_integrals = "None"
- touch io_mo_two_e_integrals
- ! regular 1/r12 integrals  on the AO basis
- io_ao_two_e_integrals = "None"
- touch io_ao_two_e_integrals
- ! integral of the effective potential 
- io_mo_int_mu_of_r = "None" 
- touch io_mo_int_mu_of_r
- call write_all_ints_basis_electric_field
- call routines_compute_energy
-end
-
-subroutine routines_compute_energy
- implicit none
- BEGIN_DOC
-! routine that computes the variational energy of the current wave function 
-!
-! and saves the current one-body density matrix into the aux_quantities folder the EZFIO folder
- END_DOC
-! density_for_dft = "WFT" 
-! touch density_for_dft 
- call print_variational_energy
- call ezfio_set_aux_quantities_data_one_e_dm_alpha_mo(one_e_dm_mo_alpha)
- call ezfio_set_aux_quantities_data_one_e_dm_beta_mo(one_e_dm_mo_beta)
-
-end
-
-

### 2021-07-01 dev/pot_ecmd/print_utils_pot.irp.f

@@ -28,12 +28,94 @@
   print*,  '****************************************'
   print*, ''
   print*,  '****************************************'
+  print*, 'x_dipole_moment                  = ',x_dipole_moment
+  print*, 'y_dipole_moment                  = ',y_dipole_moment
   print*, 'z_dipole_moment                  = ',z_dipole_moment
   print*,  '****************************************'
-
+  print*, 'total_dipole_moment                  = ',total_dipole_moment
  end
 
+ BEGIN_PROVIDER [double precision, x_dipole_moment, (N_states)]
+&BEGIN_PROVIDER [double precision, x_dipole_moment_diag, (N_states)]
+&BEGIN_PROVIDER [double precision, x_dipole_moment_off_diag, (N_states)]
+ implicit none
+ BEGIN_DOC
+ ! blablabla 
+ END_DOC
+ integer :: ipoint,istate,i,j 
+ double precision :: weight, r(3)  
+ double precision :: cpu0,cpu1,nuclei_part
 
+ call cpu_time(cpu0)
+ x_dipole_moment = 0.d0
+ x_dipole_moment_diag = 0.d0
+ x_dipole_moment_off_diag= 0.d0
+ do istate = 1, N_states
+  do i = 1, mo_num  
+   x_dipole_moment_diag(istate) += -(one_e_dm_mo_alpha(i,i,istate)+one_e_dm_mo_beta(i,i,istate)) *  mo_dipole_x(i,i)
+   do j = i+1, mo_num  
+    x_dipole_moment_off_diag(istate) += - 2.d0 * (one_e_dm_mo_alpha(j,i,istate)+one_e_dm_mo_beta(j,i,istate)) *  mo_dipole_x(j,i) 
+   enddo
+  enddo
+  x_dipole_moment(istate) = x_dipole_moment_diag(istate) + x_dipole_moment_off_diag(istate)
+ enddo
+ 
+ print*,'electron part for x_dipole = ',x_dipole_moment
+ 
+ nuclei_part = 0.d0
+ do i = 1,nucl_num 
+  nuclei_part += nucl_charge(i) * nucl_coord(i,1) 
+ enddo
+ print*,'nuclei   part for x_dipole = ',nuclei_part
+
+ do istate = 1, N_states
+  x_dipole_moment(istate) += nuclei_part
+ enddo
+
+ call cpu_time(cpu1)
+ print*,'Time for the x_dipole_moment integration :',cpu1-cpu0
+END_PROVIDER
+
[…]

### 2021-07-01 dev/spin_dens_analysis/delta_rho.irp.f

@@ -16,11 +16,11 @@
 &BEGIN_PROVIDER [double precision, z_max]
  implicit none
 !cucl2
- z_min = -5.d0
- z_max = 8.d0
+! z_min = -5.d0
+! z_max = 8.d0
 !BH
-!z_min = -4.d0
-!z_max = 7.d0
+ z_min = -4.d0
+ z_max = 7.d0
  delta_z = 0.005d0
 END_PROVIDER
 
@@ -34,7 +34,7 @@ END_PROVIDER
 BEGIN_PROVIDER [double precision, integrated_delta_rho_all_points, (N_z_pts)]
  BEGIN_DOC
 ! 
-! integrated_rho(alpha,z) - integrated_rho(beta,z) for all the z points 
+! integrated_rho(alpha,z) + integrated_rho(beta,z) for all the z points 
 ! chosen
 !
  END_DOC
@@ -78,13 +78,13 @@ END_PROVIDER
 BEGIN_PROVIDER [double precision, integrated_rho_tot_all_points, (N_z_pts)]
  BEGIN_DOC
 ! 
-! integrated_rho(alpha,z) - integrated_rho(beta,z) for all the z points 
+! integrated_rho(alpha,z) + integrated_rho(beta,z) for all the z points 
 ! chosen
 !
  END_DOC
  implicit none
  integer :: i,j,k,l,i_z,h
- double precision :: z,function_integrated_delta_rho,c_k,c_j,n_i_h,accu
+ double precision :: z,function_integrated_delta_rho,c_k,c_j,n_i_h,accu, accu_2
  integrated_rho_tot_all_points = 0.d0
  do i_z = 1, N_z_pts
   do i = 1, mo_num
@@ -105,12 +105,14 @@ BEGIN_PROVIDER [double precision, integrated_rho_tot_all_points, (N_z_pts)]
 
  z = z_min
  accu = 0.d0
+ accu_2 = 0.d0
  do i = 1, N_z_pts
   accu += integrated_rho_tot_all_points(i)
-  write(i_unit_integrated_rho_tot,*)z,integrated_rho_tot_all_points(i),accu
+  accu_2 +=  integrated_rho_tot_all_points(i)*z
+  write(i_unit_integrated_rho_tot,*)z,integrated_rho_tot_all_points(i),accu, accu_2
   z += delta_z
  enddo
- print*,'sum of integrated_delta_rho = ',accu
+ print*,'sum of integrated_rho = ',accu
 
 END_PROVIDER
 

### 2021-07-01 stable/sc_basis_corr/eff_pot_total.irp.f

@@ -26,7 +26,7 @@
    enddo
   enddo
  enddo
-END_PROVIDER
+ END_PROVIDER
 
 
  BEGIN_PROVIDER [double precision, ao_tot_eff_pot_basis, (ao_num, ao_num,N_states)]

### 2021-07-30 cusp_j/jastrow.tex

\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amsmath,amssymb,amsfonts,physics,mhchem,xspace,subfigure}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\definecolor{darkgreen}{HTML}{009900}
\usepackage[normalem]{ulem}
\newcommand{\sphi}[1]{\hat{{\bf S}}_{#1}}
\newcommand{\overlap}[2]{\langle #1 | #2 \rangle}
\newcommand{\matelem}[3]{\langle #1 | #2 | #3 \rangle}
\newcommand{\deriv}[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand{\bd}[1]{{\bf {#1}}}
\newcommand{\br}[0]{{\bf {r}}}
\newcommand{\bs}[0]{{\bf {s}}}
\newcommand{\dr}[1]{\text{d}{\bf {#1}}}
\newcommand{\psiex}[0]{\Psi^{\text{ex}}}
\newcommand{\energyex}[0]{E^{\text{ex}}}

\begin{document}

\title{On the general mapping between effective two-electron interaction and Jastrow factors.}

\author{Emmanuel Giner}
\email{emmanuel.giner@lct.jussieu.fr}

\begin{abstract}
blabla

\end{abstract}

\maketitle
\section{Position of the problem: the cusp of the helium atom}
Consider the Hamiltonian of He atom: 
\begin{equation}
 \label{eq:h_he}
 \begin{aligned}
 H = &-\frac{1}{2} \sum_{i=1}^2 \bigg(\deriv{}{r_i}{2} + \frac{2}{r_i} \deriv{}{r_i}{} + \frac{2 Z}{r_i}\bigg) \\
     &-\bigg( \deriv{}{r_{12}}{2} + \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \\
     &-\bigg( \frac{\bd{r_1}}{r_1} \cdot \frac{\bd{r_{12}} }{r_{12}}  \deriv{}{r_1}{} + 
              \frac{\bd{r_2}}{r_2} \cdot \frac{\bd{r_{21}} }{r_{21}}  \deriv{}{r_2}{} \bigg).
 \end{aligned}
\end{equation}
The exact wave function $\psiex(\bd{r_1},\bd{r_2})$ must satisfy the Schrodinger equation for all points $(\bd{r_1},\bd{r_2})$, which means that 
\begin{equation}
 H \psiex(\bd{r_1},\bd{r_2}) = \energyex \psiex(\bd{r_1},\bd{r_2}) \quad \forall (\bd{r_1},\bd{r_2}).
\end{equation}
When looking at $r_{12}\approx 0$, the terms multiplying $\frac{1}{r_{12}}$ must remain finite, which translates into 
\begin{equation}
 \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) \psiex(\bd{r_1},\bd{r_2})  = c,\quad c<\infty 
\end{equation}
which translates into
\begin{equation}
 2 \deriv{\psiex(\bd{r_1},\bd{r_2})}{r_{12}}{} -\psiex(\bd{r_1},\bd{r_2})  = c\times r_{12}. 
\end{equation}
At $r_{12}=0$, one obtains the famous cusp condition
\begin{equation}
 \deriv{\psiex}{r_{12}}{}\Bigr|_{r_{12}=0} = \frac{1}{2} \psiex(r_{12}=0). 
\end{equation}
%Nevertheless, imposing $c=0$ is just a choice, as long as $c<\infty$ one can satisfies the Schrodinger equation. 
%In the next section, we will focus on imposing a finite value.

\section{Wave function with a Jastrow factor}
Let us assume now that we have an approximate wave function $\Psi(r_{12)}$ which is obtained from a Jastrow factor $f(r_{12})$ and a wave function $\psi(r_{12})$
\begin{equation}
  \Psi(r_{12)} = e^{f(r_{12})} \phi(r_{12}). 
\end{equation}
Let us plug such a wave function in the previous equation
\begin{equation}
 \begin{aligned}
 & \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) e^{f(r_{12})} \phi(r_{12}) \\
 = & e^{f(r_{12})} \bigg[ \frac{2}{r_{12}} \deriv{\phi}{r_{12}}{} - \left( \frac{1}{r_{12}} - \frac{2}{r_{12}}\deriv{f}{r_{12}}{} \right) \phi(r_{12}) \bigg].
 \end{aligned}
\end{equation}
Therefore, by multiplying by $e^{-f(r_{12})}$ one obtains a similarity transformed Hamiltonian and therefore 
\begin{equation}
 \label{eq:eff_h}
 \begin{aligned}
 & e^{-f(r_{12})} \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) e^{f(r_{12})} \phi(r_{12}) \\ 
=& \frac{2}{r_{12}} \deriv{\phi}{r_{12}}{} - \left( \frac{1}{r_{12}} -  \frac{2}{r_{12}}\deriv{f}{r_{12}}{} \right) \phi(r_{12}) \\
=& \frac{2}{r_{12}} \deriv{\phi}{r_{12}}{} - \frac{1}{r_{12}} \left( 1-  2 \deriv{f}{r_{12}}{} \right) \phi(r_{12}). 
 \end{aligned}
\end{equation}
As before, one imposes that such quantity remains finite at $r_{12} = 0$, which translates into
\begin{equation}
 2 \deriv{\phi}{r_{12}}{} = \left( 1-  2 \deriv{f}{r_{12}}{} \right) \phi(r_{12}). 
\end{equation}
Now let us impose that $\phi(r_{12})$ is cusp-less, \textit{i.e.}
\begin{equation}
 \deriv{\phi}{r_{12}}{} = 0, 
\end{equation}
this translates into 
\begin{equation}
 \deriv{f}{r_{12}}{} = \frac{1}{2}, 
\end{equation}
or 
\begin{equation}
 f(r_{12}) = f(0) + \frac{1}{2} r_{12} + \hdots 
\end{equation}
Therefore, a Jastrow factor of form $e^{\alpha + \frac{1}{2} r_{12}}$ can fulfill the conditions.

\section{Link with an effective non divergent interaction}
Let us rewrite Eq. \eqref{eq:eff_h} as 
\begin{equation}
 \label{eq:eff_h}
 \begin{aligned}
 & e^{-f(r_{12})} \bigg( \frac{2}{r_{12}} \deriv{}{r_{12}}{} -\frac{1}{r_{12}}\bigg) e^{f(r_{12})} \phi(r_{12}) \\ 
 =& \frac{2}{r_{12}} \deriv{\phi}{r_{12}}{} - \frac{w(r_{12})}{r_{12}} \phi(r_{12}),
 \end{aligned}
\end{equation}
with 
\begin{equation}
 \label{eq:dev_wr12}
 w(r_{12}) =  1-  2 \deriv{f}{r_{12}}{}.
\end{equation}
This equation can be seen as a piece of an effective Hamiltonian of the form of Eq. \eqref{eq:h_he} but where the regular coulomb interaction $1/r_{12}$ would be replaced by $w(r_{12})/r_{12}$.

Therefore, one can have a \textit{quantitative and constructive} mapping between a general two-electron interaction, and a general Jastrow factor. 
One can notice that one can choose $w(r_{12})$ such that 
\begin{equation}
 \label{eq:wr12}
 \lim_{r_{12}\rightarrow 0} \frac{w(r_{12})}{r_{12}} < \infty,
\end{equation}
which helps therefore in designing a Jastrow factor which makes the effective interaction non divergent.

\section{The case of the long-range interaction of RS-DFT}
As a special case of Eq. \eqref{eq:wr12}, one can choose the long-range interaction of RS-DFT, which is nothing but imposing 
\begin{equation}
 w(r_{12}) = \text{erf}(\mu r_{12}). 
\end{equation}
Therefore, thanks to Eq. \eqref{eq:dev_wr12}, we can obtain the form of the Jastrow factor which would give an effective interaction of of the form 
\begin{equation}
 \frac{w(r_{12})}{r_{12}} = \frac{\text{erf}(\mu r_{12})}{r_{12}}. 
\end{equation}
This translates into 
\begin{equation}
 1-  2 \deriv{f}{r_{12}}{} = \text{erf}(\mu r_{12}), 
\end{equation}
which is a differential equation which can be integrated (thank God for Wolfram Alpha) and gives
\begin{equation}
 \label{eq:def_f}
 f(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2} + cst
\end{equation}
where $cst$ is a constant. Here we take the $cst$ such that $\lim_{\mu \rightarrow \infty} f(r_{12};\mu) = 0$ in order to have a Jastrow factor becoming $1$ at large $r_{12}$.

\section{Study of the Jastrow factor as a function of $\mu$ and $r_{12}$}
Let us call the $\mu$-dependent Jastrow factor $J(r_{12};\mu)$
\begin{equation}
 J(r_{12};\mu) = \text{exp}(f(r_{12};\mu))
\end{equation}
with of course 
\begin{equation}
 f(r_{12};\mu) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) - \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2}.
\end{equation}
\subsection{Some limits in terms of $\mu$}
\subsubsection{$\mu \rightarrow \infty$}
In that case one has
\begin{equation}
 \lim_{\mu \rightarrow \infty} \text{erf}(\mu r_{12}) = 1,
\end{equation}
which means that the effective interaction in that limit is the full Coulomb interaction
\begin{equation}
 \lim_{\mu \rightarrow \infty} \frac{\text{erf}(\mu r_{12})}{r_{12}} = \frac{1}{r_{12}}.
\end{equation}
Regarding now the function $f(r_{12};\mu)$, one has 
\begin{equation}
 \lim_{\mu \rightarrow \infty} \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12})  \bigg) = 0,
\end{equation}
\begin{equation}
 \lim_{\mu \rightarrow \infty} \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2} = 0
\end{equation}
and therefore 
\begin{equation}
 \lim_{\mu \rightarrow \infty} f(r_{12};\mu) = 0,
\end{equation}
which implies that 
\begin{equation}
 \lim_{\mu \rightarrow \infty} J(r_{12};\mu) = 1. 
\end{equation}
This limit can be interpreted as follows: if you have no Jastrow factor (\textit{i.e.}$J(r_{12})=1$), the cusp-less wave function sees the full interaction.

\subsubsection{$\mu \rightarrow 0$}
This suggests that there is no Coulomb interaction in the Hamiltonian 
\begin{equation}
  \lim_{\mu \rightarrow 0} \text{erf}(\mu r_{12}) = 0. 
\end{equation}
Therefore, even if 
\begin{equation}
  \lim_{\mu \rightarrow 0} \frac{1}{2\sqrt{\pi}\mu}e^{-(r_{12}\mu)^2} = \infty
\end{equation}
\begin{equation}
 \lim_{\mu \rightarrow 0} f(r_{12};\mu) = -\infty,
\end{equation}
we chose the $cst$ such that the $f(r_{12};\mu) = 0$, which implies 
\begin{equation}
 \lim_{\mu \rightarrow 0} J(r_{12};\mu) = 1. 
\end{equation}
This suggests that, in the case of a vanishing effective two-electron interaction, there is no Jastrow factor as there is no cusp in the wave function. This can be seen as the Hartree-Fock or Kohn-Sham limit.

\subsection{Some limits in terms of $r_{12}$ for different $\mu$}
For a finite value of $\mu$ and small value of $r_{12}$, let us Taylor expand the function $f(r_{12};\mu)$
\begin{equation}
 \label{eq:f_dl}
 f(r_{12};\mu) = -\frac{1}{2\sqrt{\pi}\mu} + \frac{1}{2}r_{12} - \frac{\mu}{2\sqrt{\pi}} r_{12}^2 + o(r_{12}^4).
\end{equation}
Therefore, it is interesting to analyze the first three terms. 
\subsubsection{The zeroth-order term: digging the Coulomb hole}
The term of order $0$ in $r_{12}$ in Eq. \eqref{eq:f_dl} corresponds in the Jastrow factor to 
\begin{equation}
 \label{eq:g0_mu}
 J(r_{12};\mu) \approx  e^{-\frac{1}{2\sqrt{\pi}\mu}},
\end{equation}
which means that this term directly lowers the on-top pair density of the cusp-less wave function $\phi(r_{12})$. 
It is interesting to develop this function in powers of $\mu^{-1} $:
\begin{equation}
 \label{eq:g0_mu_dl}
 e^{-\frac{1}{2\sqrt{\pi}\mu}} = 1 - \frac{1}{2\sqrt{\pi}\mu} + o(\mu^{-2}).
\end{equation}
The Eq. \eqref{eq:g0_mu_dl} has exactly the same development in $\mu^{-1} $ than the extrapolation of the on-top pair density derived in the context of RS-DFT by Savin and Gori-Giorgi\cite{GorSav-PRA-06}
\begin{equation}
 \frac{1}{1+\frac{1}{2\sqrt{\pi}\mu}} =  1 - \frac{1}{2\sqrt{\pi}\mu} + o(\mu^{-2}).
\end{equation}
Nevertheless, the form of Eq. ~\eqref{eq:g0_mu} could be more precise (to be tested) ...

\subsubsection{The first-order term: restoring the cusp}
The term of order 1 in $r_{12}$ in Eq. \eqref{eq:f_dl} directly restores the cusp of the full wave function
\begin{equation}
 \begin{aligned}
  J(r_{12};\mu) \approx  & e^{-\frac{1}{2\sqrt{\pi}\mu}} e^{\frac{1}{2}r_{12}} \\
                \approx  & e^{-\frac{1}{2\sqrt{\pi}\mu}} \bigg( 1 + \frac{1}{2} r_{12} + \hdots \bigg).
 \end{aligned}
\end{equation}
Interestingly, this term does not depend on $\mu$, which means that with the form of Eq. \eqref{eq:def_f} for the Jastrow factor, one obtains systematically the good cusp, whatever the $\mu$ value.

\subsubsection{The second-order term: reshaping the hole}
The term of order 2 in $r_{12}$ in Eq. \eqref{eq:f_dl} drives the shape of the hole
\begin{equation}
  \frac{1}{2} \deriv{f(r_{12};\mu)}{r_{12}}{2} = - \frac{\mu}{2\sqrt{\pi}} 
\end{equation}
and is negative.

\subsection{A few plots for different values of $\mu$}
Let us begin the graphical study for small values of $\mu$. In Fig. \ref{fig_small_mu} I report the value of the shape of the Jastrow factor $J(r_{12};\mu)$ for small values of $\mu$. As expected,  as $\mu$ increases the Jastrow factor becomes of shorter range, and the value at $r_{12}=0$ increases. This last statement implies that the closer you are from the exact Coulomb interaction, the lower is the on-top pair density of $\phi(r_{12})$, and therefore the Jastrow factor has less work to do. 
In Fig \ref{fig_large_mu} we report the shape of the Jastrow factor for relatively large values of $\mu$. 
\begin{figure*}
 \label{fig_small_mu}
        \includegraphics[width=1.00\linewidth]{small_mu.pdf}
        \caption{Shape of $J(r_{12};\mu)$ for small values of $\mu$.}
\end{figure*}
\begin{figure*}
 \label{fig_large_mu}
        \includegraphics[width=1.00\linewidth]{large_mu.pdf}
        \caption{Shape of $J(r_{12};\mu)$ for large values of $\mu$.}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical stuffs: integration of the Jastrow factor}
\subsection{Fit of the Jastrow factor with usual functions}
\subsubsection{The fit of $f(r_{12},\mu)$}
We want to be able to fit $f(r_{12},\mu)$ with simple Slater and Gaussian type functions of the type 
\begin{equation}
 h(r_{12},\gamma,\delta) = e^{-\gamma r_{12} - \delta r_{12}^2}. 
\end{equation}
First we define the rescaled $\tilde{f}(r_{12},\mu)$ function as
\begin{equation}
 \begin{aligned}
 \tilde{f}(r_{12},\mu) & = f(r_{12},\mu)\times 2\sqrt{\pi}\mu  \\
                       & = \sqrt{\pi}\mu r_{12} \bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - e^{-(\mu  r_{12})^2},
 \end{aligned}
\end{equation}
which has the advantage to take values in $[-1:0]$. 
The Taylor expansion of $\tilde{f}(r_{12},\mu)$ up to second order in $r_{12}$ is simply
\begin{equation}
 \tilde{f}(r_{12},\mu) = -1 + \sqrt{\pi}\mu r_{12} - \mu^2 (r_{12})^2 + o\big((r_{12})^2\big). 
\end{equation}
Then, we Taylor expand at second order the function $-h(r_{12},\gamma,\delta)$
\begin{equation}
 -h(r_{12},\gamma,\delta) = - 1 + \gamma r_{12} + \big( \delta - \frac{\gamma^2}{2} \big) (r_{12})^2.
\end{equation}
and the fit of $\tilde{f}(r_{12},\mu)$ by $h(r_{12},\gamma,\delta)$ is done by imposing the equality of the functions up to second order in $r_{12}$. 
This gives the following relationships
\begin{equation}
 \gamma(\mu) = \sqrt{\pi} \mu
\end{equation}
\begin{equation}
 \delta(\mu) = -\mu^2 + \frac{\gamma(\mu)^2}{2}.
\end{equation}
Therefore, we propose to fit the function $\tilde{f}(r_{12},\mu)$ by $h(r_{12},\gamma(\mu),\delta(\mu))$ 
\begin{equation}
 \label{fit_f_h}
  \tilde{f}(r_{12},\mu) = h(r_{12},\gamma,\delta) + O\big((r_{12})^2\big)
\end{equation}
As one can see from Fig. \ref{fit_small_mu} and \ref{fit_large_mu}, the agreement is pretty good between $\tilde{f}(r_{12},\mu)$ and $h(r_{12},\gamma,\delta)$, even for large values of $r_{12}$ and $\mu$. 
\begin{figure*}
 \label{fit_small_mu}
        \includegraphics[width=1.00\linewidth]{fit_f_small.pdf}
        \caption{Fit of the function $\tilde{f}(r_{12},\mu)$ with the function $h(r_{12},\gamma(\mu),\delta(\mu))$, for small values of $\mu$. }
\end{figure*}
\begin{figure*}
 \label{fit_large_mu}
        \includegraphics[width=1.00\linewidth]{fit_f_large.pdf}
        \caption{Fit of the function $\tilde{f}(r_{12},\mu)$ with the function $h(r_{12},\gamma(\mu),\delta(\mu))$, for large values of $\mu$. }
\end{figure*}

\subsubsection{Fit of the full Jastrow factor $J(r_{12},\mu)$}
Now we want to be able to represent the full Jastrow factor $J(r_{12},\mu)$ as a Taylor series of $\tilde{f}(r_{12},\mu)$. 
To do so we write
\begin{equation}
 \begin{aligned}
 \label{def_fit_j}
 J(r_{12},\mu) & = e^{f(r_{12},\mu)} \\
               & = e^{\frac{\tilde{f}(r_{12},\mu)}{2\sqrt{\pi}\mu}} \\
               & \approx e^{\frac{-h(r_{12},\gamma(\mu),\delta(\mu))}{2\sqrt{\pi}\mu}}. 
 \end{aligned}
\end{equation}
Then, as the function $-h(r_{12},\gamma(\mu),\delta(\mu)) \in [-1:0]$, we can Taylor expand the function $e^{-h(r_{12},\gamma(\mu),\delta(\mu))}$
\begin{equation}
 e^{-h(r_{12},\gamma(\mu),\delta(\mu))} = \sum_{n=0}^{\infty} \frac{1}{n!}\bigg(\frac{-h(r_{12},\gamma(\mu),\delta(\mu))}{2\sqrt{\pi}\mu}\bigg)^n. 
\end{equation}
By defining 
\begin{equation}
 a_n = \frac{1}{n!}\bigg(\frac{-1}{2\sqrt{\pi}\mu}\bigg)^n
\end{equation}
and because of the shape of the function $h(r_{12},\gamma,\delta)$ one obtains 
\begin{equation}
 \begin{aligned}
 \label{h_r_dl}
 e^{-h(r_{12},\gamma(\mu),\delta(\mu))} & = \sum_{n=0}^{\infty} a_n e^{-n\gamma(\mu)r_{12}} e^{-n\delta(\mu)(r_{12})^2} \\
                                      & = \sum_{n=0}^{\infty} a_n h\bigg( r_{12}, n\gamma(\mu),n\delta(\mu)\bigg).
 \end{aligned}
\end{equation}

\subsection{Important integrals with the Jastrow factor}
\subsubsection{Generic integrals}
We need two types of integrals. 
The first type are the normalization integrals 
\begin{equation}
 \label{def_big_sij}
 \mathcal{S}_{ij}^{kl}(\mu) = \int \int \dr{r_1}\dr{r_2} e^{f(r_{12},\mu)} \phi_i(\bd{r_1}) \phi_j(\bd{r_2}) \phi_k(\bd{r_1}) \phi_l(\bd{r_2})
\end{equation}
needed to normalize the wave function to unity or the pair density to the number of electron pairs. 
The second type of integrals are the interaction integrals 
\begin{equation}
 \label{def_big_vij}
 \mathcal{V}_{ij}^{kl}(\mu) = \int \int \dr{r_1}\dr{r_2} e^{f(r_{12},\mu)} \frac{\text{erf}(\mu r_{12})}{r_{12}}\phi_i(\bd{r_1}) \phi_j(\bd{r_2}) \phi_k(\bd{r_1}) \phi_l(\bd{r_2})
\end{equation}
needed to compute energy contributions.

As computing analytical integrals of the type \eqref{def_big_sij} or \eqref{def_big_vij} is hard, we propose to compute analytical integrals of the type
\begin{equation}
 \label{def_s_ij}
 S_{jl}(\mu,\bd{r_1}) = \int \dr{r_2} e^{f(r_{12},\mu)} \phi_j(\bd{r_2}) \phi_l(\bd{r_2})
\end{equation}
and 
\begin{equation}
 \label{def_v_ij}
 V_{jl}(\mu,\bd{r_1}) = \int \dr{r_2} e^{f(r_{12},\mu)}\frac{\text{erf}(\mu r_{12})}{r_{12}}\phi_j(\bd{r_2}) \phi_l(\bd{r_2}).
\end{equation}
Therefore, we can compute $\mathcal{S}_{ij}^{kl}(\mu)$ and $\mathcal{V}_{ij}^{kl}(\mu)$ as
\begin{equation}
 \label{def_big_sij_bis}
 \mathcal{S}_{ij}^{kl}(\mu) = \int \dr{r_1} \phi_i(\bd{r_1})  \phi_k(\bd{r_1})S_{jl}(\mu,\bd{r_1})
\end{equation}
\begin{equation}
 \label{def_big_sij_bis}
 \mathcal{V}_{ij}^{kl}(\mu) = \int \dr{r_1} \phi_i(\bd{r_1})  \phi_k(\bd{r_1})V_{jl}(\mu,\bd{r_1})
\end{equation}
where the integration over $\bd{r_1}$ is performed using a regular DFT grid. 
The computation of \eqref{def_s_ij} and \eqref{def_v_ij} are not analytical in practice as the function $e^{f(r_{12},\mu)}$ might be hard to integrate. 
Nevertheless, as shown in Figs. \ref{fig_small_mu} and \ref{fig_large_mu},  and the function $\tilde{f}(r_{12},\mu)$ take values in $[-1:0]$, and therefore one can approximate the exponential by a Taylor development as in \eqref{def_fit_j}, and then use a Shank transformation to even gain in accuracy.

\subsubsection{Basic framework to compute $S_{jl}(\mu,\bd{r_1})$ and $V_{jl}(\mu,\bd{r_1})$}
Assuming that the fit of of \eqref{def_fit_j} is valid, one can write $S_{jl}(\mu,\bd{r_1})$ as 
\begin{equation}
 \label{def_s_ij_dl_1} 
 \begin{aligned}
 S_{jl}(\mu,\bd{r_1})& = \int \dr{r_2} e^{f(r_{12},\mu)} \phi_j(\bd{r_2}) \phi_l(\bd{r_2}) \\
                     & =\int \dr{r_2} e^{\frac{-h(r_{12},\gamma(\mu),\delta(\mu))}{2\sqrt{\pi}\mu}}  \phi_j(\bd{r_2}) \phi_l(\bd{r_2}), 
 \end{aligned}
\end{equation}
which, according to \eqref{h_r_dl} becomes 
\begin{equation}
 \label{def_s_ij_dl_2} 
 \begin{aligned}
 S_{jl}(\mu,\bd{r_1})& = \int \dr{r_2} e^{f(r_{12},\mu)} \phi_j(\bd{r_2}) \phi_l(\bd{r_2}) \\
                     & =\int \dr{r_2} 
 \sum_{n=0}^{\infty} a_n h\big( r_{12}, n\gamma(\mu),n\delta(\mu)\big)
 \phi_j(\bd{r_2}) \phi_l(\bd{r_2}).
 \end{aligned}
\end{equation}
As in practice, we will truncate the sum in Eq. \eqref{def_s_ij_dl_2} up to some $N$ order, we can invert the discrete summation and integral. Therefore, we define the function $s_{ij}(\gamma,\delta)$ as 
\begin{equation} 
 \label{def_s_ij_atom}
 s_{jl}(\gamma,\delta,\bd{r_1}) = \int \dr{r_2} h( r_{12}, \gamma,\delta) \phi_j(\bd{r_2}) \phi_l(\bd{r_2}), 
\end{equation} 
and we write $S_{jl}(\mu,\bd{r_1})$ as 
\begin{equation}
 \label{def_s_ij_dl_3} 
 \begin{aligned}
 S_{jl}(\mu,\bd{r_1}) \approx & \sum_{n=0}^{N}  a_n 
                     & s_{ij}(n  \gamma(\mu),n  \delta(\mu),\bd{r_1}).
 \end{aligned}
\end{equation}
Here, the dependence in $\bd{r_1}$ of $S_{jl}(\mu,\bd{r_1})$ is within the function $h( r_{12}, \gamma,\delta)$ which can be written as a function of $\bd{r_2}$ depending on a vectorial parameter $\bd{r_1}$
\begin{equation}
 \begin{aligned}
  h( r_{12}, \gamma,\delta) = & h(\bd{r_1},\bd{r_2},\gamma,\delta) \\
                              & e^{-\gamma |\bd{r_1} - \bd{r_2}|} e^{-\delta |\bd{r_1} - \bd{r_2}|^2} 
 \end{aligned}
\end{equation}

Similarly, we can define the function 
\begin{equation} 
 \label{def_v_ij_atom}
 v_{jl}(\gamma,\delta,\mu,\bd{r_1}) = \int \dr{r_2} \frac{\text{erf}(\mu r_{12})}{r_{12}}h( r_{12}, \gamma,\delta) \phi_j(\bd{r_2}) \phi_l(\bd{r_2}), 
\end{equation}
and approximate the function $V_{jl}(\mu,\bd{r_1}) $ as
\begin{equation}
 \label{def_v_ij_dl}
 V_{jl}(\mu,\bd{r_1}) \approx \sum_{n=0}^{N}  a_n 
    v_{jl}(n  \gamma(\mu),n  \delta(\mu),\mu,\bd{r_1}).
\end{equation}

\subsubsection{Computation of $s_{ij}(\gamma,\delta,\bd{r_1})$ and $v_{ij}(\gamma,\delta,\mu,\bd{r_1})$}
The computation of $s_{ij}(\gamma,\delta,\bd{r_1})$ is \textit{a priori} not trivial as it contains a Slater function. 
Nevertheless, we can fit a Slater function with Gaussian functions (that is what quantum chemistry is about):
\begin{equation}
 e^{-X} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m X^2}, 
\end{equation}
and, by posing $X=\gamma x$ one can fit any Slater function as
\begin{equation}
 e^{-\gamma x} = \sum_{m=1}^{N_s} c_m e^{-\zeta_m \gamma^2 x^2}. 
\end{equation}
To find the $\{c_m,\zeta_m\}$ parameters, I performed a Hartree Fock calculation on the Hydrogen atom using the $s$ functions of the ANO-RCC basis set which contains 8 gaussians.  
Therefore, computing $s_{jl}(\gamma,\delta,\bd{r_1})$ is nothing but a proper linear combination of Gaussian integrals.

Of course, the same thing is valid for the computation of the $v_{ij}(\gamma,\delta,\mu,\bd{r_1})$.

\section{Further thoughts ...}
Some stuffs to approximate maybe at second order ...
Higher order cusp condition
\begin{equation}
 \lim_{r_{12}\rightarrow 0}\deriv{\psiex}{r_{12}}{2} = \frac{1}{2} \deriv{\psiex}{r_{12}}{} = \frac{1}{4}\psiex(r_{12}=0)
\end{equation}
Now assume that $\psiex = e^{f}\phi$, then
\begin{equation}
 \deriv{e^{f}\phi }{r_{12}}{2} = \deriv{f}{r_{12}}{2} e^f \phi + \bigg(\deriv{f}{r_{12}}{} \bigg)^2 e^f\phi  
                               + \deriv{\phi}{r_{12}}{2}e^f
\end{equation}

\section{Derivation of Tew and applications to the Jastrow factor}
The present section provides some details about the very insightful derivations by Tew\cite{Tew-JCP-08} where the cusp conditions up to third order are proven. 
\subsection{The derivation by Tew}
Let us take a general Hamiltonian for $n$ particle within Coulomb interaction
\begin{equation}
 \bigg( -\sum_{i=1}^n \frac{\nabla_i^2}{m_i} + \sum_{i>j=1}^n \frac{Z_i Z_j}{r_{ij}}\bigg) \Psi = E \Psi .
\end{equation}
Here, the particles can be either protons and/or electrons, and therefore the wave function $\Psi$ depends on all coordinates \textit{i.e.} $\Psi(\bd{r}_1,\hdots,\bd{r}_n)$. 
Let us consider now the regions in configurational space where $0\le r_{12}\le\epsilon$ and $r_{i1},r_{i2}\gg \epsilon$ $(i>2)$, $r_{ij}\gg \epsilon$, $(i,j)>2$.

We transform the coordinate spaces from $\bd{r}_1$, $\bd{r}_2$ to $\br = \bd{r}_1 - \bd{r}_2$ and $\bs = (m_1 \bd{r}_1 + m_2 \bd{r}_2)/M$ with $M=m_1+m_2$. 
The derivative operator over $x_1$ becomes
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} = & \deriv{}{r_x}{} \deriv{r_x}{x_1}{} + \deriv{}{s_x}{} \deriv{s_x}{x_1}{} \\
                 = & \deriv{}{r_x}{} \deriv{x_1 - x_2}{x_1}{} + \deriv{}{s_x}{} \frac{1}{M}\deriv{m_1 x_1 + m_2 x_2}{x_1}{} \\
                 = & \deriv{}{r_x}{}                          + \deriv{}{s_x}{} \frac{m_1}{M}
 \end{aligned}
\end{equation}
and so
\begin{equation}
 \begin{aligned}
  \deriv{}{x_1}{2} = & \deriv{}{r_x}{2} + \bigg(\frac{m_1}{M} \bigg)^2 \deriv{}{s_x}{2} + 2\frac{m_1}{M}  \deriv{}{r_x}{}\deriv{}{s_x}{}.
 \end{aligned}
\end{equation}
Similarly, 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_2}{} = - \deriv{}{r_x}{}    + \deriv{}{s_x}{} \frac{m_2}{M}
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
  \deriv{}{x_2}{2} = & \deriv{}{r_x}{2} + \bigg(\frac{m_2}{M} \bigg)^2 \deriv{}{s_x}{2} - 2\frac{m_2}{M}  \deriv{}{r_x}{}\deriv{}{s_x}{}.
 \end{aligned}
\end{equation}
Therefore, 
\begin{equation}
 \frac{1}{m_1} \deriv{}{x_1}{2}  + \frac{1}{m_2} \deriv{}{x_2}{2} = \frac{1}{M} \deriv{}{s_x}{2} + \frac{1}{\lambda} \deriv{}{r_x}{2}, 
\end{equation}
where $\lambda = m_1 m_2/M$.
Using the same change of variables for $(y_1,y_2)$ and $(z_1,z_2)$, the kinetic operator becomes then 
\begin{equation}
 \hat{T} = -\frac{\nabla^2_{\bs}}{2M} -\frac{\nabla^2_{\br}}{2\lambda} - \sum_{i=3}^n \frac{\nabla_i^2}{m_i}.
\end{equation}
In order to express the potential operator in terms of $\br$ and $\bs$, we introduce the cosines $\text{cos}(\theta_i)$ between the vectors $\bd{r}_{is} = \bd{r}_i - \bs$ and $\br$. 
To do so, we note that
\begin{equation}
 \begin{aligned}
 & \bd{r}_1 = \frac{m_2}{M}\br + \bs\\
 & \bd{r}_2 = \frac{m_1}{M}\br - \bs,
 \end{aligned}
\end{equation}
and 
\begin{equation}
 \begin{aligned}
 \bd{r}_{i1}& = \bd{r}_i - \bd{r}_1 = \bd{r}_i - \bd{s} - \frac{m_2}{M}\bd{r}\\
            & = \bd{r}_{is} - \frac{m_2}{M}\bd{r},
 \end{aligned}
\end{equation}
so 
\begin{equation}
 \begin{aligned}
 r_{i1}^2 &  = \bd{r_{i1}} \cdot \bd{r_{i1}} = r_{is}^2 + \bigg(\frac{m_2 r}{M}\bigg)^2 - 2\frac{m_2}{M} \bd{r}_{i1} \cdot \bd{r} \\
            & = r_{is}^2 + \bigg(\frac{m_2}{M}\bigg)^2 r^2 - 2\frac{m_2}{M} r_{is} r\, \text{cos}(\theta_i).
 \end{aligned}
\end{equation}
Similarly, we find for $r_{i2}^2$
\begin{equation}
 \begin{aligned}
 r_{i2}^2 &  = r_{is}^2 + \bigg(\frac{m_1}{M}\bigg)^2 r^2 + 2\frac{m_2}{M} r_{is} r\, \text{cos}(\theta_i).
 \end{aligned}
\end{equation}
In the region of interest, we can replace the potential in $1/r_{i1}$ by its partial wave expansion in terms of Legendre polynomials 
\begin{equation}
  \frac{1}{r_{i1}} = \frac{1}{r_{is}} \sum_{l=0}^\infty \bigg( \frac{m_2 r}{Mr_{is}} \bigg)^l P_l(\cos(\theta_i))
\end{equation}
which can be seen as a smart Taylor expansion of the annoying function $1/(1+X^2 -2 \alpha X)$. 
The same thing holds for $r_{i2}^{-1}$ by replacing $1$ by $2$ in the indices, and $\cos(\theta_i)$ by $-\cos(\theta_i)$. 
Therefore, the full Schroedinger equation becomes
\begin{equation}
 \begin{aligned}
  \bigg(&  -\frac{\nabla_{s}^2}{2 M}- \frac{\nabla_r^2}{2\lambda} - \sum_{i=3}^n \frac{\nabla_i^2}{m_i} + \frac{Z_1 Z_2}{r} 
   + \sum_{i>j=3}^n \frac{Z_i Z_j}{r_{ij}} \\
  &+ \sum_{i=3}^n \frac{Z_i}{r_{is}} \sum_{l=0}^\infty \bigg[Z_1 \bigg( \frac{m_2 r}{Mr_{is}}  \bigg)^l 
                                                            +Z_2 \bigg( -\frac{m_1 r}{Mr_{is}} \bigg)^l\bigg]P_l(\cos(\theta_i)) \bigg) \Psi = E \Psi.
 \end{aligned}
\end{equation}
We can then assign an order in $\epsilon$ to each term in the Hamiltonian, and we shall consider the terms of order 0 or less in $\epsilon$. 
Therefore, we have 
\begin{equation}
 \label{eq:schro_0}
 \bigg( - \frac{\nabla_r^2}{2\lambda} + \frac{Z_1 Z_2}{r} + \hat{S} + \mathcal{O}(\epsilon) \bigg) \Psi = E \Psi
\end{equation}
with the operator $\hat{S}$ being of zeroth order in $\epsilon$, which contains the kinetic energy of all particles except the inter particle kinetic term between 1 and 2, together with the zeroth order development of the Coulomb interaction minus that of particle 1 and 2
\begin{equation}
 \hat{S} = -\frac{\nabla_{s}^2}{2 M}  - \sum_{i=3}^n \frac{\nabla_i^2}{m_i}  + \sum_{i>j=3}^n \frac{Z_i Z_j}{r_{ij}} 
 + \sum_{i=3}^n \frac{Z_i}{r_{is}} \big( Z_1+Z_2 \big). 
\end{equation}
The terms in the Hamiltonian of order $\epsilon$ is 
\begin{equation}
 \mathcal{O}(\epsilon) = \sum_{i=3}^n \frac{Z_i}{r_{is}} \bigg[Z_1 \frac{m_2 r}{Mr_{is}}-Z_2 \frac{m_1 r}{Mr_{is}}\bigg],
\end{equation}
which vanishes for identical particles such as our dear electrons. 
The most general solution to Eq. \eqref{eq:schro_0} is given by 
\begin{equation}
 \label{eq:psi_gen}
 \Psi\big(\br,\bs \bd{r}_3, \hdots ,\bd{r}_n\big) = \sum_{l=0}^{\infty} \sum_{l=-m}^{+m} 
 r^l f_{lm}\big(r,\bs,\bd{r}_3, \hdots ,\bd{r}_n\big) Y_{lm}(\theta,\phi). 
\end{equation}
The differential operator $\nabla_r^2$ can be written in spherical coordinate as
\begin{equation}
 \begin{aligned}
 \nabla_r^2 f(r,\theta,\phi) = & \frac{1}{r} \deriv{}{r}{2} \bigg( r\,\, f(r,\theta,\phi) \bigg) \\
  &+ \frac{1}{r^2 \sin(\theta)}  \deriv{}{\theta}{} \bigg(\sin(\theta) \deriv{f(r,\theta,\phi)}{\theta}{} \bigg) \\
  &+ \frac{1}{r^2 \sin(\theta)}  \deriv{}{\phi}{2} f(r,\theta,\phi). 
 \end{aligned}
\end{equation}
Let us begin with $\frac{1}{r} \deriv{}{r}{2} \bigg( r\,\, \Psi(r,\theta,\phi,\hdots) \bigg)$.
First, $r\Psi(r,\theta,\phi,\hdots)$
\begin{equation}
 \Psi(r,\theta,\phi,\hdots) = \sum_{l=0}^{\infty} \sum_{l=-m}^{+m} r^{l+1}f_{lm}\big(r,\bs,\bd{r}_3, \hdots ,\bd{r}_n\big) Y_{lm}(\theta,\phi),
\end{equation}
and therefore, 
\begin{equation}
 \begin{aligned}
 \deriv{r\Psi}{r}{}  = & \sum_{l=0}^{\infty} \sum_{l=-m}^{+m}  Y_{lm}(\theta,\phi)\\  
  & \bigg[ (l+1) r^l f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) + r^{l+1} \deriv{}{r}{} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big)\bigg]. 
 \end{aligned}
\end{equation}
Then, 
\begin{equation}
 \begin{aligned}
 &\deriv{r\Psi}{r}{2}  = \sum_{l=0}^{\infty} \sum_{l=-m}^{+m}  Y_{lm}(\theta,\phi)\\   
 & \bigg[ l(l+1) r^{l-1} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) + (l+1) r^l \deriv{}{r}{} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) \\
+& (l+1) r^l  \deriv{}{r}{} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) + r^{l+1} \deriv{}{r}{2} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) \bigg],
 \end{aligned}
\end{equation}
and therefore 
\begin{equation}
 \label{eq:lapl}
 \begin{aligned}
 \frac{1}{r}\deriv{r\Psi}{r}{2}  =& \sum_{l=0}^{\infty} \sum_{l=-m}^{+m}  Y_{lm}(\theta,\phi) \, \, r^l\\
 & \bigg[  \deriv{}{r}{2} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) 
 + \frac{2(l+1)}{r} \deriv{}{r}{} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) \\
 & + \frac{l(l+1)}{r^2} f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) \bigg].
 \end{aligned}
\end{equation}
Unfortunatly, I don't find back the results of Eq. (16) of Ref. \onlinecite{Tew-JCP-08}, but this might be because the last term of equation \eqref{eq:lapl} involving $\frac{l(l+1)}{r^2}$ cancels out with the derivatives in $\theta$ and $\phi$. 
In any cases, we want to develop such an equation for $l=0$, which means that the last term in \eqref{eq:lapl} involving $\frac{l(l+1)}{r^2}$ vanishes, and that the part of the Laplacian involving angular derivatives vanishes also as $Y_0^0 = \frac{1}{\sqrt{4\pi}}$. 
Anyway, before taking the specific case of $l=0$, we will assume the result of Eq. (16) of Ref. \onlinecite{Tew-JCP-08}, which is  that the Schroedinger equation of \eqref{eq:schro_0} becomes
\begin{equation}
 \begin{aligned}
& \sum_{l=0}^\infty \sum_{m=-l}^{+l} r^l\bigg( \frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2(l+1)}{r} \deriv{}{r}{}\bigg] \\ 
&- \frac{Z_1 Z_2}{r}  - \hat{S} + E \bigg) Y_{lm}(\theta,\phi) f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) =0.
 \end{aligned}
\end{equation}
Because of completeness and linear independence of the $Y_{lm}(\theta,\phi)$, this equation must stand for each value of $l,m$. Therefore, one obtains 
\begin{equation}
 \label{eq:schro_l}
 \begin{aligned}
& \bigg( \frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2(l+1)}{r} \deriv{}{r}{}\bigg] 
&- \frac{Z_1 Z_2}{r}  - \hat{S} + E \bigg) f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) =0.
 \end{aligned}
\end{equation}
Now, we can Taylor expand up to some order $v$ the functions $f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big) $ 
\begin{equation}
 \label{eq:tayl_flm}
 f_{lm}\big(r,\bs,\bd{r}_3, \hdots \bd{r}_n\big)  = \sum_{k=0}^v r^k f_{lm}^k\big(\bs,\bd{r}_3, \hdots \bd{r}_n\big), 
\end{equation}
and what has derived Tew in Ref. \onlinecite{Tew-JCP-08} is essentially the derivation of the three first terms $f_{lm}^k\big(\bs,\bd{r}_3, \hdots \bd{r}_n\big)$ for general $l$ and $k=0,1,2$. We will focus on $l=0$ for the rest of the section.

\subsection{The case $l=0$}
From thereon, we focus on the part $l=0$ as it consists in two opposite spin electrons at coalescence. 
For the sake of compactness, we will use the following notations 
\begin{equation}
 f(\bd{R}) \equiv f\big(\bs,\bd{r}_3, \hdots \bd{r}_n\big)
\end{equation}
where $\bd{R}$ symbolises all other variables than $(r,\theta,\phi)$. 
Our goal is therefore to find the function $f_{00}\big(r,\bd{R})$,  which can be Taylor expanded as
\begin{equation}
 f_{00}\big(r,\bd{R}\big)  = \sum_{k=0}^v r^k f_{00}^k\big(\bd{R}\big). 
\end{equation}
Let us compute the action of the differential operator on $f_{00}\big(r,\bd{R}\big)$
\begin{equation}
 \begin{aligned}
 \frac{2}{r}\deriv{}{r}{} f_{00}\big(r,\bd{R}\big) = & \sum_{k=1}^v r^{k-2} 2 k\,f_{00}^k\big(\bd{R}\big)\\
 = & \frac{2}{r}f_{00}^1\big(\bd{R}\big) +  \sum_{k=2}^v r^{k-2} 2 k\,f_{00}^k\big(\bd{R}\big), 
 \end{aligned}
\end{equation}
\begin{equation}
 \deriv{}{r}{2} f_{00}\big(r,\bd{R}\big) = \sum_{k=2}r^{k-2} k(k-1) f_{00}^k\big(\bd{R}\big),
\end{equation}
which ads up to 
\begin{equation}
 \begin{aligned}
& \big( \deriv{}{r}{2} + \frac{2}{r}\deriv{}{r}{}  \big) f_{00}\big(r,\bd{R}\big) =  \frac{2}{r}f_{00}^1\big(\bd{R}\big) +
  \sum_{k=2}^v r^{k-2} (2 k + k(k-1)) f_{00}^k\big(\bd{R}\big). 
 \end{aligned}
\end{equation}
The potential operator acting on $f_{00}\big(r,\bd{R}\big)$ is simply
\begin{equation}
 \begin{aligned}
 \frac{Z_1 Z_2}{r} f_{00}\big(r,\bd{R}\big) = & \frac{Z_1 Z_2}{r} f_{00}^0\big(\bd{R}\big)+  & Z_1 Z_2 \sum_{k=1}^v r^{k-1} f_{00}^k\big(\bd{R}\big).  
 \end{aligned}
\end{equation}
We can then recompose the action of the Hamiltonian on the $l=0$ sector 
\begin{equation}
 \begin{aligned}
 \label{eq:power_exp}
&\frac{1}{\lambda r}f_{00}^1\big(\bd{R}\big) - \frac{Z_1 Z_2}{r} f_{00}^0\big(\bd{R}\big)
- Z_1 Z_2 \sum_{k=1}^v r^{k-1} f_{00}^k\big(\bd{R}\big) + \\ 
& \sum_{k=2}^v r^{k-2} (2 k + k(k-1)) f_{00}^k\big(\bd{R}\big) +
\big( E - \hat{S} \big) \sum_{k=0}^v r^k f_{00}^k\big(\bd{R}\big) = 0, 
 \end{aligned}
\end{equation}
and one can identify all terms having the same power of $r$. 
\subsection{The cusp conditions}
The term in $r^{-1}$ in \eqref{eq:power_exp} gives
\begin{equation}
 \frac{1}{\lambda} f_{00}^1\big(\bd{R}\big) - Z_1 Z_2 f_{00}^0\big(\bd{R}\big) = 0,
\end{equation}
or equivalently
\begin{equation}
 f_{00}^1\big(\bd{R}\big) = \lambda Z_1 Z_2 f_{00}^0\big(\bd{R}\big), 
\end{equation}
which for electrons, as $m_1 = m_2 = 1$ and $Z_1 = Z_2 = 1$, one obtains $ \lambda = \frac{1}{2}$, leading therefore to the famous cusp condition
\begin{equation}
 \label{eq:cusp_1}
 f_{00}^1\big(\bd{R}\big) = \frac{1}{2} f_{00}^0\big(\bd{R}\big). 
\end{equation}
The term in $r^0$ gives 
\begin{equation}
 \begin{aligned}
& -Z_1 Z_2 f_{00}^1\big(\bd{R}\big) + 6 f_{00}^2\big(\bd{R}\big) + \\
& \big( E - \hat{S} \big) f_{00}^0\big(\bd{R}\big) = 0, 
 \end{aligned}
\end{equation}
or equivalently
\begin{equation}
 \begin{aligned}
  6 f_{00}^2\big(\bd{R}\big) = Z_1 Z_2 f_{00}^1\big(\bd{R}\big) + \big( \hat{S} -E \big) f_{00}^0\big(\bd{R}\big)
 \end{aligned}
\end{equation}
which, thanks to Eq. \eqref{eq:cusp_1}, can be recast as 
\begin{equation}
 \begin{aligned}
 \label{eq:cusp_2}
  f_{00}^2\big(\bd{R}\big) = \frac{1}{6}\bigg( \lambda \big(Z_1 Z_2\big)^2  + \big( \hat{S} -E \big)\bigg) f_{00}^0\big(\bd{R}\big)
 \end{aligned}
\end{equation}
which coincides with the case $l=0$ of Eq. (20) of Ref. \onlinecite{Tew-JCP-08} which gives the second order derivative $f_{lm}^2\big(\bd{R}\big)$ for the general case $(l,m)$
\begin{equation}
 f_{00}^2\big(\bd{R}\big) = \frac{\lambda}{2l+3}\bigg( \frac{\lambda^2}{\lambda(l+1)} + \hat{S} -E \bigg) f_{00}^0\big(\bd{R}\big). 
\end{equation}

For electrons, $\lambda=1/2$ and therefore
\begin{equation}
 \label{eq:cusp_2_e}
f_{00}^2\big(\bd{R}\big) = \frac{1}{12} f_{00}^0\big(\bd{R}\big) + 
 \frac{1}{6} \big( \hat{S} -E \big) f_{00}^0\big(\bd{R}\big). 
\end{equation}

Eq. \eqref{eq:cusp_2_e} contains two type of contribution: the universal $\frac{1}{12} f_{00}^0\big(\bd{R}\big)$ contribution, and the system- and state-specific contribution of $\frac{1}{6} \big( \hat{S} -E \big) f_{00}^0\big(\bd{R}\big)$.

\section{Using Tew's path for Jastrow factors}
\subsection{Position of the problem}
Let us assume now that the exact wave function can be written as 
\begin{equation}
 \label{eq:phi_j}
 \Psi\big(\br,\bd{R}\big) = e^{j(r)}\phi\big(\br,\bd{R}\big).
\end{equation}
As we impose that the correlation factor $j(r)$ only depends on $r$ (and not on $\theta$ or $\phi$), its expansion in terms of $Y_{lm}(\theta,\phi)$ is straightforward as it consists in the $l=0$ sector
\begin{equation}
 j(r) = r^0 j_{0}(r)Y_{00}(\theta,\phi).
\end{equation}
Nevertheless, the wave function $\phi\big(\br,\bd{R}\big)$ is expanded as in Eq. \eqref{eq:psi_gen}
\begin{equation} 
 \phi\big(\br,\bd{R}\big) = \sum_{l=0}^{\infty} \sum_{l=-m}^{+m} 
 r^l \phi_{lm}\big(r,\bd{R}\big) Y_{lm}(\theta,\phi), 
\end{equation}
Also, as $j(r) =$ coincides with the $l=0$ sector, so does $e^{j(r)}$, and therefore, focussing on the $l=0$ sector of Eq. \eqref{eq:schro_l},  we can write the Schroedinger equation for the wave function of type Eq. \eqref{eq:phi_j} 
\begin{equation}
 \label{eq:schro_phi_j}
 \begin{aligned}
& \bigg( \frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg] 
&- \frac{Z_1 Z_2}{r}  - \hat{S} + E \bigg) e^{j(r)}\phi_{00}\big(r,\bd{R}\big) =0.
 \end{aligned}
\end{equation}
Therefore, by identification with the $l=0$ sector of \eqref{eq:schro_l}, one can easily see that
\begin{equation}
 f_{00}\big(r,\bd{R}\big) = e^{j(r)}\phi_{00}\big(r,\bd{R}\big)
\end{equation}
as they solve the same partial differential equation. 
Therefore, we can identify term by term the cups conditions found by Tew and see how does it translate with the form of Eq. \eqref{eq:phi_j}.

\subsection{Identifications term by term}
As in Eq. \eqref{eq:tayl_flm}, one can Taylor expand the functions $j(r)$ and $\phi_{00}\big(r,\bd{R}\big)$ in terms of powers of $r$
\begin{equation}
 \label{eq:tayl_phi00}
 \phi_{00}\big(r,\bd{R}\big)  = \sum_{k=0}^v r^k \phi_{00}^k\big(\bd{R}\big), 
\end{equation}
\begin{equation}
 \label{eq:tayl_j}
 j(r) = \sum_{k=0}^v r^k j^k.  
\end{equation}
As we are interested in the cusp condition up to second order, we will take $v=2$ and Taylor expand the function $e^j\phi$
\begin{equation}
 \label{eq:tayl_j_phi}
  e^{j(r)}\phi_{00}\big(r,\bd{R}\big) = e^{j^0 + j^1 r^1 + j^2 r^2}\bigg( \sum_{k=0}^2 r^k \phi_{00}^k\big(\bd{R}\big) \bigg). 
\end{equation}
With these notations, stopping the Taylor expansion at second order of Eq. \eqref{eq:tayl_j_phi} gives
\begin{equation}
 \begin{aligned}
 e^{j(r)}\phi_{00}\big(r,\bd{R}\big) = & e^{j^0}\bigg(\phi_0^0(\bd{R}) + r \big(\phi_0^0(\bd{R}) j^1 + \phi_0^1(\bd{R})\big) \\
 +& \frac{1}{2} r^2\big(\phi_0^0(\bd{R}) \big[ (j^1)^2 + 2j^2 \big] + 2 \phi_0^1(\bd{R}) j^1 + 2 \phi_0^2(\bd{R}) \big).  
 \end{aligned}
\end{equation}

Therefore, one can identify each terms
\begin{equation}
 \label{eq:f0_jphi}
 f_{00}^0(\bd{R}) = e^{j^0} \phi_0^0(\bd{R}),
\end{equation}
\begin{equation}
 \label{eq:f1_jphi}
 f_{00}^1(\bd{R}) = e^{j^0}\big(\phi_0^0(\bd{R}) j^1 + \phi_0^1(\bd{R})\big),
\end{equation}
\begin{equation}
 \label{eq:f2_jphi}
 f_{00}^2(\bd{R}) = e^{j^0}\frac{1}{2}\big(\phi_0^0(\bd{R}) \big[ (j^1)^2 + 2j^2 \big] + 2 \phi_0^1(\bd{R}) j^1 + 2 \phi_0^2(\bd{R}) \big).
\end{equation}

\subsubsection{Developing the first-order cusp condition}
Eq. \eqref{eq:f0_jphi} allows us to write the exact wave function at coalescence, and therefore one can rewrite the 
first order cusp condition of Eq. \eqref{eq:f1_jphi} as 
\begin{equation}
 \begin{aligned}
 f_{00}^1(\bd{R}) = & e^{j^0} \phi_0^0(\bd{R}) \bigg( j^1 + \frac{\phi_0^1(\bd{R})}{\phi_0^0(\bd{R})} \bigg) \\
                  = & f_{00}^0(\bd{R})         \bigg( j^1 + \frac{\phi_0^1(\bd{R})}{\phi_0^0(\bd{R})} \bigg) 
 \end{aligned}
\end{equation}
or equivalently
\begin{equation}
 \begin{aligned}
 \frac{f_{00}^1(\bd{R})}{f_{00}^0(\bd{R})} = j^1 + \frac{\phi_0^1(\bd{R})}{\phi_0^0(\bd{R})}. 
 \end{aligned}
\end{equation}
Therefore, if one assumes that the wave function $\phi_0(\br,\bd{R})$ is cusp-less, one finds 
\begin{equation}
 \begin{aligned}
  j^1 = \lambda Z_1 Z_2, 
 \end{aligned}
\end{equation}
which is equivalent to the usual cusp condition of Eq. \eqref{eq:cusp_1}.

\subsubsection{Developing the second-order cusp condition}
The second order cusp condition of Eq. \eqref{eq:cusp_2} can be combined with Eq. \eqref{eq:f2_jphi} as 
\begin{equation}
  \begin{aligned}
& \frac{1}{6}\bigg( \lambda \big(Z_1 Z_2\big)^2  + \big( \hat{S} -E \big)\bigg) e^{j^0}\phi_0^0(\bd{R}) = \\
& e^{j^0}\frac{1}{2}\big(\phi_0^0(\bd{R}) \big[ (j^1)^2 + 2j^2 \big] + 2 \phi_0^1(\bd{R}) j^1 + 2 \phi_0^2(\bd{R}) \big),
  \end{aligned}
\end{equation}
which can be recombined as 
\begin{equation}
  \begin{aligned}
& \frac{1}{6}\lambda \big(Z_1 Z_2\big)^2 \phi_0^0(\bd{R}) - \frac{1}{2}\phi_0^0(\bd{R}) \big[ (j^1)^2 + 2j^2 \big] - \phi_0^1(\bd{R}) j^1  = \\
& \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) ,
  \end{aligned}
\end{equation}
Note that if we set the jastrow factor to zero, we obtain 
\begin{equation}
  \begin{aligned}
 \phi_0^2(\bd{R}) =  \frac{1}{6}\lambda \big(Z_1 Z_2\big)^2 \phi_0^0(\bd{R}) + \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}),
  \end{aligned}
\end{equation}
which is equivalent to Eq. \eqref{eq:cusp_2_e}.

Now let us assume that $\phi_0^1(\bd{R}) = 0$ and that $j^1 = \lambda Z_1 Z_2$, 
\begin{equation}
  \begin{aligned}
& \phi_0^0(\bd{R}) \bigg( \lambda \big(Z_1 Z_2\big)^2 \big( \frac{1}{6} - \frac{1}{2} \lambda\big) - j^2 \bigg) = \\
& \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) ,
  \end{aligned}
\end{equation}
or equivalently
\begin{equation}
  \begin{aligned}
& \lambda \big(Z_1 Z_2\big)^2 \big( \frac{1}{6} - \frac{1}{2} \lambda\big) - j^2  = \\
& \frac{1}{\phi_0^0(\bd{R})} \bigg( \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) \bigg) ,
  \end{aligned}
\end{equation}
with $Z_1 = Z_2 = 1$, $\lambda = \frac{1}{2}$ 
\begin{equation}
  \begin{aligned}
& \frac{1}{2}\big( \frac{1}{6} - \frac{1}{4} \big) - j^2  = \\
& \frac{1}{\phi_0^0(\bd{R})} \bigg( \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) \bigg) ,
  \end{aligned}
\end{equation}
\begin{equation}
 \label{eq:j2}
  \begin{aligned}
& -\frac{1}{24} - j^2  = \\
& \frac{1}{\phi_0^0(\bd{R})} \bigg( \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) \bigg) .
  \end{aligned}
\end{equation}
An important point of Eq. \eqref{eq:j2}, is that the left part is independent of $\bd{R}$ whereas the right hand side is dependent on $\bd{R}$. Therefore, one must have
\begin{equation}
 \label{eq:univ}
 \phi_0^2(\bd{R}) - \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}) = 0, 
\end{equation}
or 
\begin{equation}
 \label{eq:phi02}
 \phi_0^2(\bd{R}) = \frac{1}{6}\big( \hat{S} -E \big) \phi_0^0(\bd{R}), 
\end{equation}
but Eq. \eqref{eq:univ} also implies that 
\begin{equation}
 \label{eq:j02}
 j^2 = -\frac{1}{24},
\end{equation}
which coincides with the result of Tew in Ref. \onlinecite{Tew-JCP-08} regarding the minimal Jastrow factor on-top of a HF wave function.

The Eqs. \eqref{eq:phi02} and \eqref{eq:j02} suggest two important things: if one uses a cusp-less wave function of type $\phi_0(\bd{r},\bd{R})$ multiplied by a general Jastrow factor $j(r)$ only depending on the inter-electronic distance $r$, then the analysis up to zeroth-order in $r$ provides you the first and second order derivatives of the Jastrow factor which are $1/2$ and $-1/24$. 
The Eq. \eqref{eq:phi02} also tells you that, provided that you take the Jastrow factor with the correct first and second derivatives, then the second order in a given configurational point $\bd{R}$ obeys a mean-field equation like.

\subsection{Eigenequation for $\phi$: the similarity transformed Hamiltonian}
\subsubsection{Expression of the similarity transformed Hamiltonian}
Another way to see the problem is to multiply Eq. \eqref{eq:schro_phi_j} by $e^{-j(r)}$ to obtain a similarity transformed or trans-correlated Hamiltonian
\begin{equation}
 \label{eq:schro_tilde_phi_j}
 \begin{aligned}
 e^{-j(r)} \bigg( \frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg] - \frac{Z_1 Z_2}{r}  - \hat{S} + E \bigg) e^{j(r)}\phi_{00}\big(r,\bd{R}\big) =0, 
 \end{aligned}
\end{equation}
which can be written as 
\begin{equation}
 \label{eq:htilde_phi}
 \bigg(E -\tilde{\mathcal{H}}[j]\bigg) \phi_{00}\big(r,\bd{R}\big) = 0,
\end{equation}
with the similarity transformed Hamiltonian $ \tilde{\mathcal{H}}[j] $ defined by
\begin{equation}
  \tilde{\mathcal{H}}[j]  = e^{-j(r)} \bigg( -\frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg] 
+ \frac{Z_1 Z_2}{r}  + \hat{S}  \bigg) e^{j(r)}.
\end{equation}

An important consequence of the choice of $f(r)$ (which only depends on $r$), is that the operator $\hat{S}$, which depends on all variables but $r,\theta,\phi$, leaves $f(r)$ untouched, \textit{i.e.}
\begin{equation}
 \hat{S} f(r) = f(r).
\end{equation}
Therefore, the similarity transformed Hamiltonian can be written as
\begin{equation}
  \tilde{\mathcal{H}}[j]  =  -\frac{1}{2\lambda} e^{-j(r)} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)}
+ \frac{Z_1 Z_2}{r}  + \hat{S},
\end{equation}
and Eq. \eqref{eq:schro_tilde_phi_j} can be written as
\begin{equation}
 \frac{1}{2\lambda} e^{-j(r)} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)}\phi_{00}(r,\bd{R}) 
- \bigg( \frac{Z_1 Z_2}{r}  + \hat{S} -E \bigg) \phi_{00}(r,\bd{R}) = 0.
\end{equation}
Doing the math one obtains that 
\begin{equation}
 e^{-j(r)} \frac{2}{r} \deriv{}{r}{} e^{j(r)} \cdot = \frac{2}{r}\bigg( \deriv{}{r}{} + \deriv{j}{r}{} \bigg),
\end{equation}
\begin{equation}
 e^{-j(r)} \deriv{}{r}{2} e^{j(r)} \cdot = \deriv{j}{r}{2} + \bigg( \deriv{j}{r}{} \bigg)^2 + 2 \deriv{j}{r}{} \deriv{}{r}{} + \deriv{}{r}{2},
\end{equation}
and therefore the action on a given $\phi(r)$ of the similarity transformed kinetic operator can be written as 
\begin{equation}
 \begin{aligned}
  e^{-j(r)} \bigg[ \deriv{}{r}{2} + &\frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)} \phi(r) =  \deriv{\phi}{r}{2} + \frac{2}{r} \bigg( \deriv{\phi}{r}{}+ \deriv{j}{r}{}\phi(r) \bigg) \\ 
& + 2 \deriv{j}{r}{} \deriv{\phi}{r}{} + \bigg[\deriv{j}{r}{2} + \bigg( \deriv{j}{r}{} \bigg)^2\bigg] \phi(r). 
 \end{aligned}
\end{equation}
Therefore, one can recombine the right hand side of Eq. \eqref{eq:htilde_phi} in 
\begin{equation}
 \label{eq:tilde_2}
 \begin{aligned}
  \bigg(E -\tilde{\mathcal{H}}[j]\bigg) \phi_{00}\big(r,\bd{R}\big) = & \frac{1}{2\lambda} \bigg( \deriv{\phi_{00}\big(r,\bd{R}\big)}{r}{2} +   \deriv{\phi_{00}\big(r,\bd{R}\big)}{r}{} \bigg[ \frac{2}{r}+ 2 \deriv{j(r)}{r}{}\bigg] \bigg)  \\
& - \frac{1}{r} \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg) \phi_{00}\big(r,\bd{R}\big) \\
& + \bigg( \frac{1}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \bigg(\deriv{j(r)}{r}{}\bigg)^2\bigg] + E  - \hat{S} \bigg)\phi_{00}\big(r,\bd{R}\big).
 \end{aligned}
\end{equation}
Therefore, one can write an explicit form of $\tilde{\mathcal{H}}[j]$ as 
\begin{equation}
 \label{def:htilde}
 \begin{aligned}
 \tilde{\mathcal{H}}[j] = & - \frac{1}{2\lambda} \bigg( \deriv{}{r}{2} + \bigg[ \frac{2}{r}+  2 \deriv{j(r)}{r}{}\bigg] \deriv{}{r}{} \bigg) \\
 & + \frac{1}{r} \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg) \\
 &- \bigg( \frac{1}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \bigg(\deriv{j(r)}{r}{}\bigg)^2\bigg] - \hat{S} \bigg). 
 \end{aligned}
\end{equation}

\subsubsection{Taylor expansion of $\tilde{\mathcal{H}}[j]$}
By introducing the Taylor expansion of the function $j(r)$, one obtains 
\begin{equation}
 \label{eq:sim_h}
 \begin{aligned}
 e^{-j(r)} \bigg[ \deriv{}{r}{2} + & \frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)} \phi(r) = \deriv{\phi}{r}{2} + \frac{2}{r}\bigg( \deriv{\phi}{r}{} + \phi(r)\sum_{k=1}^v k\, r^{k-1} j^k \bigg) \\
 + & 2 \bigg( \sum_{k=1}^v k \, r^{k-1} j^k  \bigg) \deriv{\phi}{r}{} \\
 + & \bigg(\sum_{k=2}^v k(k-1) r^{k-2} j^k + \sum_{k=1}^v\sum_{n=1}^v n \, k \, r^{k+n-2} j^k j^n\bigg)\phi(r) \, .
 \end{aligned}
\end{equation}
As proposed by Tew in Eq. \eqref{eq:schro_0}, we only keep the terms of order smaller or equal to zero in $r$. 
Therefore, sorting by importance in terms of $r$ and stopping at $r^0$, equation Eq. \eqref{eq:sim_h} becomes
\begin{equation}
 \label{eq:sim_kin_1}
 \begin{aligned}
 e^{-j(r)} \bigg[ \deriv{}{r}{2} + & \frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)} \phi(r) =  r^{-1} 2 \bigg( \deriv{\phi}{r}{} + j^1 \phi(r)\bigg)\\
& + r^0 \bigg( \deriv{\phi}{r}{2} + 2 j^1 \deriv{\phi}{r}{} + \bigg[  6 j^2  + \big(j^1\big)^2\bigg] \phi(r) \bigg) \, .
 \end{aligned}
\end{equation}
which, by dividing by $2\lambda$ gives
\begin{equation}
 \label{eq:sim_kin_2}
 \begin{aligned}
 \frac{1}{2\lambda}e^{-j(r)} \bigg[ \deriv{}{r}{2} + & \frac{2}{r} \deriv{}{r}{}\bigg]  e^{j(r)} \phi(r) =  r^{-1} \frac{1}{\lambda}\bigg( \deriv{\phi}{r}{} + j^1 \phi(r)\bigg)\\
& + r^0 \frac{1}{\lambda}\bigg( \frac{1}{2}\deriv{\phi}{r}{2} + j^1 \deriv{\phi}{r}{} + \bigg[  3 j^2  + \frac{\big(j^1\big)^2}{2}\bigg] \phi(r) \bigg) \, .
 \end{aligned}
\end{equation}
Then, one can compute the action of the pure potential part of $\tilde{\mathcal{H}}[f]$ 
\begin{equation}
 \label{eq:pot}
 \begin{aligned}
& - \frac{1}{\lambda}\bigg( \frac{\lambda Z_1 Z_2}{r}  + \lambda\big(\hat{S} -E\big) \bigg) \phi_{00}(r,\bd{R})  
 \end{aligned}
\end{equation}
Eventually, one can recombine Eqs. \eqref{eq:pot} and \eqref{eq:sim_kin} 
\begin{equation}
 \label{eq:sim_tot}
 \begin{aligned}
& r^{-1} \frac{1}{\lambda}\bigg( \deriv{\phi_{00}(r,\bd{R})}{r}{} + \bigg[j^1-\lambda Z_1 Z_2\bigg]\phi_{00}(r,\bd{R})\bigg)  \\
& + r^0 \frac{1}{\lambda} \bigg( \frac{1}{2}\deriv{\phi_{00}(r,\bd{R})}{r}{2} + j^1 \deriv{\phi_{00}(r,\bd{R})}{r}{}\bigg) \\
& + r^0 \frac{1}{\lambda} \bigg( j^2  + \frac{\big(j^1\big)^2}{2} + \lambda \big( E - \hat{S} \big) \bigg) \phi_{00}(r,\bd{R}) = 0.
 \end{aligned}
\end{equation}
Before determining the cusp conditions, let us discuss some clues about the validity domain of Eq. \eqref{eq:sim_tot}. 
Eq. \eqref{eq:sim_tot} must hold for all  $\bd{R}$ and $r$ such that $r\ll r_{is},\,i=3,n $, which means when two electrons are well isolated from the rest of the other particles.

\subsubsection{Cusp conditions}
We are going now to focus on the cusp conditions with the similarity transformed Hamiltonian. 
Starting from Eq. \eqref{eq:sim_tot}, one can introduce the Taylor expansion of Eq. \eqref{eq:tayl_phi00} and identify the terms in $r^{-1}$, which gives 
\begin{equation}
 \begin{aligned}
  \phi_{00}^1(\bd{R}) +  \bigg( j^1 - \lambda Z_1 Z_2\bigg) \phi_{00}^0(\bd{R}) = 0, 
 \end{aligned}
\end{equation}
which is nothing but
\begin{equation}
 \phi_{00}^1(\bd{R}) = \phi_{00}^0(\bd{R}) \bigg( \lambda Z_1 Z_2 - j^1\bigg). 
\end{equation}
Therefore, if we impose that $j(r)$ has the correct cusp (\textit{i.e.} $j^1 = Z_1 Z_2 \lambda$) then one obtains 
\begin{equation}
 \phi_{00}^{1}(\bd{R}) = 0, 
\end{equation}
which means that the wave function $\phi_{00}(r,\bd{R})$ is cusp-less. The other way around is also true: if we impose that the wave function $\phi_{00}(r,\bd{R})$ is cusp-less, then the Jastrow factor must recover the cusp. 
Also, if we set the jastrow factor to zero, then one obtains the usual cusp condition, \textit{i.e.} $\phi_{00}^1(\bd{R}) = \lambda Z_1 Z_2 \phi_{00}^0(\bd{R}) $.

We can do the same thing and look at all terms of order $0$ in $r$, 
\begin{equation}
 \begin{aligned}
& 3 \phi_{00}^2(\bd{R}) + 2 j^1 \phi_{00}^1(\bd{R}) -\lambda Z_1 Z_2 \phi^1_{00}(\bd{R}) \\
+& \big( j^2 + \frac{\big(j^1\big)^2}{2}\big)\phi_{00}^0(\bd{R}) + \lambda\big( E - \hat{S} \big)\phi_{00}^0(\bd{R}) = 0. 
 \end{aligned}
\end{equation}
or 
\begin{equation}
 \phi_{00}^2(\bd{R}) = \frac{\lambda}{3}\bigg( \phi_{00}^1(\bd{R}) \big(  Z_1 Z_2 - 2 \frac{j^1}{\lambda} \big) + \phi_{00}^0(\bd{R}) \bigg[ \hat{S} - E - \frac{1}{\lambda}\bigg( j^2 + \frac{\big(j^1\big)^2}{2}\bigg) \bigg] \bigg).
\end{equation}

If we set $j(r)=0$, we  find 
\begin{equation}
 \phi_{00}^2(\bd{R}) = \frac{\lambda}{3} \bigg( Z_1 Z_2 \phi^1_{00}(\bd{R}) + \big( \hat{S} - E\big)\phi_{00}^0(\bd{R}) \bigg) = 0.
\end{equation}
By using the first-order cusp condition, one finds 
\begin{equation}
 \phi_{00}^2(\bd{R}) = \frac{\lambda}{3} \bigg( \lambda (Z_1 Z_2)^2 \phi^0_{00}(\bd{R}) + \big( \hat{S} - E\big)\phi_{00}^0(\bd{R}) \bigg) = 0.
\end{equation}
which corresponds to the original second-order cusp condition.

\subsection{Analysis of a Hamiltonian with a long-range interaction}
\subsubsection{The main equations}
Let us now take the case of an Hamiltonian with a long-range interaction $\text{erf}(\mu r)/r$ as those used in RS-DFT. 
The effective Schroedinger equation is then 
\begin{equation}
 \begin{aligned}
& \tilde{H}^\mu \Phi^{\mu} = \tilde{E} \Phi^{\mu} \Leftrightarrow \\
& \bigg( -\sum_{i=1}^n \frac{\nabla_i^2}{m_i} + \sum_{i=1}^n v_{\text{Hxc}}(\bd{r}_i) + \sum_{i>j=1}^n Z_i Z_j \frac{\text{erf}(\mu r_{ij})}{r_{ij}}\bigg) \Phi^{\mu} = \tilde{E} \Phi^{\mu}
 \end{aligned}
\end{equation}
where $v_{\text{Hxc}}(\bd{r})$ is the short-range potential maintaining the exact density, \textit{i.e.} $n_{\Phi_{\mu}} = n_{\Psi}$, and $\tilde{E}$ is the effective eigenvalue equation which is not physical. 
Following the path of Tew, we Taylor expand the effective Hamiltonian in term of $r$ and keep the term of order inferior or equal to zero. 
%The long-range interaction becomes
%\begin{equation}
% \frac{\text{erf}(\mu_{ij})}{r_{ij}} = \frac{2 \mu}{\sqrt{\pi}},
%\end{equation}
The effective potentials $v_{\text{Hxc}}(\bd{r}_i)$ for $i=1,2$ become 
\begin{equation}
 v_{\text{Hxc}}(\bd{r}_1) = v_{\text{Hxc}}(\bs) + \nabla_{\bd{r}} v_{\text{Hxc}}(\frac{m_2}{M}\br + \bs) \bigg|_{\br = {\bd{0}}} \cdot \text{d}\br
\end{equation}
\begin{equation}
 v_{\text{Hxc}}(\bd{r}_2) = v_{\text{Hxc}}(-\bs) + \nabla_{\bd{r}} v_{\text{Hxc}}(\frac{m_1}{M}\br - \bs) \bigg|_{\br = {\bd{0}}}  \cdot \text{d}\br 
\end{equation}
The terms involving the gradients with respect to $\bd{r}$ are necessary of order 1 in $r$ and therefore can be ignored. 
We end up with the following effective Hamiltonian $\tilde{H}^\mu $ at order lower or equal to 0 in $r$ 
\begin{equation}
 \label{eq:hmu}
 \bigg( - \frac{\nabla_r^2}{2\lambda} + Z_1 Z_2\frac{\text{erf}(\mu r)}{r} + \hat{S}^\mu + \mathcal{O}(\epsilon) \bigg) \Phi^{\mu} = \tilde{E} \Phi^\mu
\end{equation}
with the effective operator $\hat{S}^\mu$ being
\begin{equation}
 \begin{aligned}
 \hat{S}^\mu = &-\frac{\nabla_{s}^2}{2 M}  - \sum_{i=3}^n \frac{\nabla_i^2}{m_i}  + \sum_{i>j=3}^n Z_i Z_j\frac{\text{erf}(\mu r_{ij})}{r_{ij}}  \\ 
& + \sum_{i=3}^n Z_i\frac{\text{erf}(\mu r_{is})}{r_{is}} \big( Z_1+Z_2 \big) \\ 
&+ v_{\text{Hxc}}(\bs) + v_{\text{Hxc}}(-\bs) + \sum_{i=3}^n v_{\text{Hxc}}(\bd{r}_i). 
 \end{aligned}
\end{equation}
We can then do the same analysis as before, which is expand the wave function $\Phi^{\mu}$ in spherical harmonics 
\begin{equation}
 \Phi^{\mu}(\br,\bd{R}) = \sum_{l=0}^\infty r^l \sum_{m=-l}^{+l} \Phi_{lm}^{\mu}(r,\bd{R})Y_{lm}(\theta,\phi), 
\end{equation}
then inject in the Schroedinger-like equation Eq. \eqref{eq:hmu}, and then focus on the $l=0$ sector, which gives
\begin{equation}
 \begin{aligned}
 \label{eq:hmu_2}
 \bigg( \frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\bigg] & - Z_1 Z_2 \frac{\text{erf}(\mu r)}{r}
- \hat{S}^\mu + \tilde{E} \bigg) \Phi_{00}^{\mu}\big(r,\bd{R}\big) = 0. 
 \end{aligned}
\end{equation}

\subsubsection{The cusp conditions}
One can then Taylor expand in powers of $r$ the solution $\Phi_{00}^{\mu}\big(r,\bd{R}\big)$ 
\begin{equation}
 \Phi_{00}^{\mu}\big(r,\bd{R}\big) = \sum_{k=0}^v r^k \Phi_{00}^{k,\mu}\big(\bd{R}\big),
\end{equation}
and then plug into Eq. \eqref{eq:hmu_2}, which, according the Taylor development of $\text{erf}(\mu r)/r$ gives
\begin{equation}
 \begin{aligned}
 r^{-1} \frac{1}{\lambda} & \sum_{k=1}^v k r^{k-1} \Phi_{00}^{k,\mu}\big(\bd{R}\big) + \frac{1}{2\lambda} \sum_{k=2}^v r^{k-2} k(k-1) \Phi_{00}^{k,\mu}\big(\bd{R}\big)\\ 
& + \bigg( - Z_1 Z_2 \frac{2 \mu}{\sqrt{\pi}}  - \hat{S}^\mu + \tilde{E} \bigg)  \sum_{k=0}^v r^k \Phi_{00}^{k,\mu}\big(\bd{R}\big) = 0.
 \end{aligned}
\end{equation}
The identification for $r^{-1}$ gives
\begin{equation}
 \frac{1}{\lambda} \Phi_{00}^{1,\mu}\big(\bd{R}\big) = 0
\end{equation}
which says that the wave function $\Phi_{00}^{\mu}\big(r,\bd{R}\big)$ has no cusp.

Then, the terms in $r^0$ are 
\begin{equation}
 \frac{1}{\lambda}2 \Phi_{00}^{2,\mu}\big(\bd{R}\big) + \frac{1}{2 \lambda} 2 \Phi_{00}^{2,\mu}\big(\bd{R}\big) 
 + \bigg( - Z_1 Z_2 \frac{2 \mu}{\sqrt{\pi}} - \hat{S}^\mu + \tilde{E}   \bigg) \Phi_{00}^{0,\mu}\big(\bd{R}\big) = 0,
\end{equation}
which translates into 
\begin{equation}
 \Phi_{00}^{2,\mu}\big(\bd{R}\big) = \frac{\lambda}{3}\bigg( Z_1 Z_2 \frac{2 \mu}{\sqrt{\pi}} + \hat{S}^\mu - E\bigg) \Phi_{00}^{0,\mu}\big(\bd{R}\big). 
\end{equation}
Therefore, the second-order derivative in $r$ depends on $\mu$ but also on $\bd{R}$.

\subsubsection{Linking RS-DFT and jastrows}
We wan to make a mapping between the effective trans-correlated Hamiltonian $\tilde{\mathcal{H}}[j]$ of Eq. \eqref{def:htilde} and that of $\tilde{H}^\mu$ of Eq. \eqref{eq:hmu_2}. 
More precisely, we want to find the conditions on $j(r)$ such that the eigenfunction $\Phi_{00}\big(r,\bd{R}\big)$ of $\tilde{\mathcal{H}}[j]$ coincide with the eigenfunction $\Phi_{00}^{\mu}\big(r,\bd{R}\big)$ of $\tilde{H}^\mu$. 
Let us rewrite the two equations 
\begin{equation}
 \label{def:htilde2}
 \begin{aligned}
& \bigg(\tilde{\mathcal{H}}[j] - E \bigg) \Phi_{00}\big(r,\bd{R}\big) = 0 \Leftrightarrow \\ 
& - \frac{1}{2\lambda} \bigg( \deriv{}{r}{2}\Phi_{00}\big(r,\bd{R}\big) + \bigg[ \frac{2}{r}+  2 \deriv{j(r)}{r}{}\bigg] \deriv{}{r}{}\Phi_{00}\big(r,\bd{R}\big) \bigg) \\
 & + \frac{1}{r} \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg) \Phi_{00}\big(r,\bd{R}\big) \\
 & - \frac{1}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \bigg(\deriv{j(r)}{r}{}\bigg)^2\bigg]\Phi_{00}\big(r,\bd{R}\big)  \\ 
& + \big( \hat{S} - E\big) \Phi_{00}\big(r,\bd{R}\big) = 0, 
 \end{aligned}
\end{equation}
and 
\begin{equation}
 \begin{aligned}
 \label{eq:hmu_3}
& \bigg( \tilde{H}^\mu - \tilde{E} \bigg) \Phi_{00}^{\mu}\big(r,\bd{R}\big) = 0 \Leftrightarrow\\
& -\frac{1}{2\lambda} \bigg[ \deriv{}{r}{2} \Phi_{00}^{\mu}\big(r,\bd{R}\big) + \frac{2}{r} \deriv{}{r}{}\Phi_{00}^{\mu}\big(r,\bd{R}\big) \bigg] \\ 
& + Z_1 Z_2 \frac{\text{erf}(\mu r)}{r}\Phi_{00}^{\mu}\big(r,\bd{R}\big) \\
&+ \big(\hat{S}^\mu - \tilde{E}\big) \Phi_{00}^{\mu}\big(r,\bd{R}\big) = 0. 
 \end{aligned}
\end{equation}
In Eq. \eqref{eq:hmu_3} and \eqref{def:htilde2} there are two types of terms: the universal terms only depending in $r$ and the terms depending on the wave function and the coordinates of the other electrons $\bd{R}$.  
We want to make a mapping only in terms of the universal terms, and therefore we propose the following statement 
\begin{equation}
 \big(\hat{S}^\mu - \tilde{E}\big) \Phi_{00}^{\mu}\big(r,\bd{R}\big) = \big( \hat{S} - E\big) \Phi_{00}\big(r,\bd{R}\big) - \frac{1}{\lambda} \deriv{j(r)}{r}{} \Phi_{00}\big(r,\bd{R}\big). 
\end{equation}

Under that assumption, the match between Eq. \eqref{eq:hmu_3} and Eq. \eqref{def:htilde2} implies 
\begin{equation}
 \begin{aligned}
& + \frac{1}{r} \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg) \Phi_{00}\big(r,\bd{R}\big) \\
& - \frac{1}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \bigg(\deriv{j(r)}{r}{}\bigg)^2\bigg]\Phi_{00}\big(r,\bd{R}\big) \\
& = Z_1 Z_2 \frac{\text{erf}(\mu r)}{r}\Phi_{00}\big(r,\bd{R}\big),
 \end{aligned}
\end{equation}
or equivalently
\begin{equation}
 \begin{aligned}
 \label{eq_diff_j}
& - \frac{r}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \bigg(\deriv{j(r)}{r}{}\bigg)^2\bigg] \\
& + \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg)  \\
& = Z_1 Z_2 \text{erf}(\mu r).
 \end{aligned}
\end{equation}
The resolution of Eq. \eqref{eq_diff_j} is rather complex as it involves $\bigg(\deriv{j(r)}{r}{}\bigg)^2$ which makes it non-linear. 
Nevertheless, one can focus on the leading order $r^0$, which gives
\begin{equation}
 Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j_0(r)}{r}{} = Z_1 Z_2 \text{erf}(\mu r)
\end{equation}
or 
\begin{equation}
 \label{eq_diff_j0}
   \deriv{j_0(r)}{r}{} = Z_1 Z_2 \lambda \big( 1 - \text{erf}(\mu r)\big). 
\end{equation}
This gives the same equation than initially found, and provides qualitative behaviour of the short-range Jastrow factor. 
Therefore, we know that $j_0(r)$ is a qualitative solution of Eq. \eqref{eq_diff_j} and we can use it to remove the non-linearity
\begin{equation}
 \begin{aligned}
 \label{eq_diff_j1}
& - \frac{r}{2\lambda}\bigg[ \deriv{j(r)}{r}{2} + \big( Z_1 Z_2 \lambda\big)^2 \big( 1 - \text{erf}(\mu r)\big)^2\bigg] \\
& + \bigg( Z_1 Z_2 - \frac{1}{\lambda}  \deriv{j(r)}{r}{} \bigg)  \\
& = Z_1 Z_2 \text{erf}(\mu r),
 \end{aligned}
\end{equation}
and by taking $Z_1 = Z_2 = 1$, $\lambda = 1/2$ one obtains 
\begin{equation}
 \begin{aligned}
& - r \bigg[ \deriv{j(r)}{r}{2} + \frac{1}{4} \big( 1 - \text{erf}(\mu r)\big)^2\bigg] + \bigg( 1 - 2 \deriv{j(r)}{r}{} \bigg)   = \text{erf}(\mu r),
 \end{aligned}
\end{equation}
or equivalently 
\begin{equation}
 \begin{aligned}
 \label{eq_diff_j1_erf2}
& r \deriv{j(r)}{r}{2} + 2 \deriv{j(r)}{r}{}  =  1 - \text{erf}(\mu r) - \frac{1}{4} r \big( 1 - \text{erf}(\mu r)\big)^2.
 \end{aligned}
\end{equation}
The function $\big( 1 - \text{erf}(\mu r)\big)^2$ is a bit nasty but we can fit it according to Eq. \eqref{eq:fit_erf2}
\begin{equation}
 \big(1 - \text{erf}(x)\big)^2 \approx 2\big( 1 - \text{erf}(x)\big) - e^{-\frac{4}{\pi} x^2}.
\end{equation}
Therefore, one obtains 
\begin{equation}
 \begin{aligned}
 \label{eq_diff_j1_fit}
& r \deriv{j(r)}{r}{2} + 2 \deriv{j(r)}{r}{}  =  1 - \text{erf}(\mu r) - \frac{1}{2} r \big( 1 - \text{erf}(\mu r)\big) + \frac{r}{4}e^{-\frac{4}{\pi} (\mu r)^2}. 
 \end{aligned}
\end{equation}
If we take the $r\approx 0$  behaviour, one re-obtain Eq. \eqref{eq_diff_j0} which guarantees the small $r$ behaviour. 
Interestingly, Eq. \eqref{eq_diff_j1_fit} has an analytical solution of the form 
\begin{equation}
 \label{eq:j2_start}
 \begin{aligned}
  j(r) = & \frac{1}{2 r}\bigg( c_1 - \frac{\text{erf}\big(\mu r\big)}{2 \mu^2} - \frac{\pi^2 \text{erf}\big(2\sqrt{\pi}\mu r\big) }{64 \pi \mu^3} - \frac{e^{-\big(\mu r \big)^2}}{3\sqrt{\pi}\mu^3} \bigg) \\
       + & r^0 \bigg( c_2 - \frac{\text{erf}(\mu r)}{8 \mu^2} - \frac{e^{-\big( \mu^r \big)^2}}{2 \sqrt{\pi} \mu} \bigg)\\
       + & \frac{r}{2} \bigg( 1 - \text{erf}(\mu r) \bigg) \\
       + & \frac{r^2}{12} \bigg( \text{erf}(\mu r) -1 \bigg).
 \end{aligned}
\end{equation}
WARNING THERE MUST BE AN ERROR AS WE WANT THE SECOND ORDER DERIVATIVE TO BE -1/24 at r12=0.
Let us now take some limits to fix the constants $c_1$ and $c_2$. 
\subsubsection{Small $r$ limit}
The first limit is that when $r \rightarrow 0$ we want the function $j(r)$ to be finite and therefore we want the terms in $r^{-1}$ to be finite in Eq. \eqref{eq:j2_start}. 
If we take the limit of these terms one has 
\begin{equation}
 \begin{aligned}
  \lim_{r\rightarrow 0} &\frac{1}{r}\bigg( c_1 - \frac{\text{erf}\big(\mu r\big)}{4 \mu^2} -\frac{\text{erf}\big(2\sqrt{\pi}\mu r\big)}{128 \pi \mu^3} - \frac{e^{-\big(\mu r \big)^2}}{6\sqrt{\pi}\mu^3} \bigg) \\
 = & \frac{1}{r} \bigg( c_1 - \frac{1}{4\mu^2}\frac{2\mu}{\sqrt{\pi}} r - \frac{4\mu }{128 \pi \mu^3} r - \frac{1}{6\sqrt{\pi}\mu^3} \bigg) \\
 = & \frac{1}{r} \bigg( c_1 - \frac{1}{2\sqrt{\pi}\mu} r - \frac{1}{32 \pi \mu^2} r - \frac{1}{6\sqrt{\pi}\mu^3} \bigg) \\
 = & \frac{1}{r}\bigg( c_1 - \frac{1}{6\sqrt{\pi}\mu^3} \bigg) - \frac{1}{2\sqrt{\pi}\mu} \bigg( 1 + \frac{1}{16\sqrt{\pi}\mu} \bigg).
 \end{aligned}
\end{equation}
Therefore

\section{Garbage}
\subsection{Fit of functions}
At some point we would like to fit the following function
\begin{equation}
 g(x) = 1-\text{erf}(x)
\end{equation}
which can be done, for instance by 
\begin{equation}
 u(x,\alpha,\beta,c) = e^{-\alpha x - \beta x^2}
\end{equation}
with $\alpha=1.09529$ and $\beta = 0.756023$. 
So by posing $y=\mu x$, $x=y/\mu$ then
\begin{equation}
 \label{fit_erf}
 \begin{aligned}
  g(x,\mu)  =& 1 - \text{erf}(\mu x) \approx e^{-\alpha \mu x - \beta (\mu x)^2}\\ 
        =& e^{\alpha \mu x } e^{-\beta \mu^2 x^2} \\
        =& u(x,\alpha \mu, \beta \mu^2).
 \end{aligned}
\end{equation}
Therefore, one can fit $g(x)^2$ as 
\begin{equation}
 \begin{aligned}
 g(x,\mu)^2 = \bigg( 1 - \text{erf}(\mu x) \bigg)^2\\
           &= \bigg( e^{\alpha \mu x } e^{-\beta \mu^2 x^2}\bigg)^2 \\
           &= e^{\alpha 2 \mu x } e^{-2 \beta \mu^2 x^2} \\
           &= u(x,2 \alpha \mu, 2 \beta \mu^2).
 \end{aligned}
\end{equation}

\subsection{Other fit of functions}
We want to fit the function $\bigg(1 - \text{erf}(x)\bigg)^2$.
As $\text{erf}(x)$ is an integral in 1d, the function $\big(\text{erf}(x)\big)^2$ can be written as 
\begin{equation}
 \big(\text{erf}(x)\big)^2 = \frac{4}{\pi}\int_{0}^{x} \text{d}u \int_{0}^{x} \text{d}v e^{-(u^2+v^2)}, 
\end{equation}
which is the integral of $e^{-(u^2+v^2)}$ over a square of lattice $x$. 
Then, one can approximate the area over the square by the area over the disk of radius $x$, which involves the function $1 - e^{-a x^2}$ with $a=1$. Then, by imposing that the functions $\big(\text{erf}(x)\big)^2$ and $1 - e^{-a x^2}$ coincides at second order near $r=0$, one finds 
\begin{equation}
 \label{eq:fit_erf2}
 \big(\text{erf}(x)\big)^2 \approx 1 - e^{-\frac{4}{\pi} x^2}.
\end{equation}
In Fig. \ref{fig_fit_erf2} we represent the quality of the fit of Eq. \eqref{eq:fit_erf2}, which is quite convincing I guess. 
\begin{figure*}
 \label{fig_fit_erf2}
        \includegraphics[width=1.00\linewidth]{fit_erf2.pdf}
        \caption{$\big(\text{erf}(x)\big)^2$ and its fit with $1 - e^{-\frac{4}{\pi} x^2}$.}
\end{figure*}

\bibliography{srDFT_SC}
\end{document}

### 2023-09-21 dev/fcidump_for_vbarb/PYSCF_EOMCC_from_fcidump.py
added scripts for EOMCC PySCF

@@ -1,0 +1,43 @@
+#!/usr/bin/env python
+#
+# Author: Qiming Sun <osirpt.sun@gmail.com>
+#
+
+'''
+Writing FCIDUMP file for given integrals or SCF orbitals
+'''
+
+import os
+import sys
+from functools import reduce
+import numpy
+import pyscf
+
+
+from pyscf import gto, scf, ao2mo, cc
+from pyscf.cc import ccsd_t
+from pyscf import symm
+from pyscf.tools import fcidump
+
+#basis_sets = ['aug-cc-pvdz', 'aug-cc-pvtz', 'aug-cc-pvqz', 'aug-cc-pv5z']
+basis =str(sys.argv[1])
+
+
+mol = gto.Mole()
+mol.atom = 'O  0.00000000 0.00000000 -0.13209669; H  0.00000000 1.43152878 0.97970006; H  0.00000000 -1.43152878 0.97970006' #Angstrom
+mol.unit = 'B'
+mol.basis = basis
+mol.build()
+
+FCIDUMP=str(sys.argv[2])
+print('reading the following FCIDUMP '+ FCIDUMP)
+
+ctx = fcidump.read(FCIDUMP)
+mf = fcidump.to_scf(FCIDUMP, molpro_orbsym=True)
+mf.run()
+
+mf.mol.verbose = 4
+
+mycc = cc.CCSD(mf,frozen=0).run()
+
+e_ee, c_ee = mycc.eeccsd(nroots=10)

### 2023-09-21 dev/fcidump_for_vbarb/fcidump_for_vbarb.irp.f

@@ -1,4 +1,40 @@
 program fcidump_pbe
+ implicit none
+ read_wf = .true.
+ touch read_wf
+ ! total one-e integrals 
+ io_mo_one_e_integrals = "None"
+ touch io_mo_one_e_integrals  
+ ! Vne integrals on the MO basis 
+ io_mo_integrals_n_e = "None"
+ touch io_mo_integrals_n_e
+ ! kinetic integrals on the MO basis 
+ io_mo_integrals_kinetic = "None"
+ touch io_mo_integrals_kinetic 
+ ! Vne integrals on the AO basis 
+ io_ao_integrals_n_e = "None"
+ touch io_ao_integrals_n_e 
+ ! kinetic integrals on the AO basis 
+ io_ao_integrals_kinetic = "None"
+ touch io_ao_integrals_kinetic 
+
+ ! regular 1/r12 integrals  on the MO basis
+ io_mo_two_e_integrals = "None"
+ touch io_mo_two_e_integrals
+ ! regular 1/r12 integrals  on the AO basis
+ io_ao_two_e_integrals = "None"
+ touch io_ao_two_e_integrals
+ ! integral of the effective potential 
+! io_mo_int_mu_of_r = "None" 
+! touch io_mo_int_mu_of_r
+
+ no_core_density = .True.
+ touch no_core_density
+
+ call write_fcidump
+end
+
+subroutine write_fcidump
   implicit none
   BEGIN_DOC
 ! Produce a regular `FCIDUMP` file from the |MOs| stored in the |EZFIO|
@@ -20,7 +56,7 @@ program fcidump_pbe
   END_DOC
   character*(128) :: output
   integer :: i_unit_output,getUnitAndOpen
-  output=trim(ezfio_filename)//'.FCIDUMP'
+  output=trim(ezfio_filename)//'.vbarb_FCIDUMP'
   i_unit_output = getUnitAndOpen(output,'w')
 
   integer :: i,j,k,l

### 2023-09-21 dev/fcidump_for_vbarb/script_water_eomcc.sh

@@ -1,0 +1,21 @@
+source /home/eginer/qp2/quantum_package.rc
+basis=aug-cc-pvtz
+sys=water
+
+qp create_ezfio -b $basis ${sys}.xyz -a -o ${sys}_$basis
+qp run scf | tee ${EZFIO_FILE}.scf.out
+qp set_frozen_core 
+
+#### FIRST SANITY CHECK FOR CCSD CALCULATIONS WITH BARE HAMILTONIAN
+qp run ccsd | tee ${EZFIO_FILE}.ccsd_qp.out
+qp run fcidump_pyscf | tee ${EZFIO_FILE}.fcidump_pyscf.out 
+fcidump=${EZFIO_FILE}.FCIDUMP
+python PYSCF_EOMCC_from_fcidump.py $basis ${fcidump} | tee ${EZFIO_FILE}.PySCF_EOM_bare_H.out 
+
+
+#### PBE-UEG CALCULATIONS 
+qp set sc_basis_corr basis_cor_func pbe_ueg
+qp run basis_correction | tee ${EZFIO_FILE}.basiscorr.out 
+qp run fcidump_for_vbarb | tee ${EZFIO_FILE}.fcidump_for_vbarb.out
+fcidump=${EZFIO_FILE}.vbarb_FCIDUMP
+python PYSCF_EOMCC_from_fcidump.py $basis ${fcidump} | tee ${EZFIO_FILE}.PySCF_EOM_vbarb.out 

### 2023-09-21 cusp_j/3_body/three_body_mat.tex

\documentclass[aip,jcp,reprint,noshowkeys,superscriptaddress]{revtex4-1}
\usepackage{graphicx,dcolumn,bm,xcolor,microtype,multirow,amsmath,amssymb,amsfonts,physics,mhchem,xspace,subfigure}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}

\usepackage[
	colorlinks=true,
    citecolor=blue,
    breaklinks=true
	]{hyperref}
\urlstyle{same}

\definecolor{darkgreen}{HTML}{009900}
\usepackage[normalem]{ulem}
\newcommand{\sphi}[1]{\hat{{\bf S}}_{#1}}
\newcommand{\overlap}[2]{\langle #1 | #2 \rangle}
\newcommand{\matelem}[3]{\langle #1 | #2 | #3 \rangle}
\newcommand{\deriv}[3]{\frac{\partial^{#3} #1}{\partial {#2}^{#3}}}
\newcommand{\bd}[1]{{\bf {#1}}}
\newcommand{\br}[0]{{\bf {r}}}
\newcommand{\bs}[0]{{\bf {s}}}
\newcommand{\dr}[1]{\text{d}{\bf {#1}}}
\newcommand{\psiex}[0]{\Psi^{\text{ex}}}
\newcommand{\energyex}[0]{E^{\text{ex}}}
\newcommand{\opr}[1]{\,\hat{#1}}
\newcommand{\oprd}[1]{\,\hat{#1}^\dagger}

\begin{document}

\title{Computing matrix element of the three-body operator for parallel spins}

\author{Emmanuel Giner}
\email{emmanuel.giner@lct.jussieu.fr}

\maketitle
\section{What we need to compute}
\subsection{General matrix element}
We need to compute the matrix elements of this nasty operator
\begin{equation}
 O^3 = \frac{1}{6} \sum_{ijm} \sum_{kln} \overlap{ijm}{kln} \oprd{k} \oprd{l} \oprd{n}  \opr{m} \opr{j} \opr{i}.
\end{equation}
Therefore, it is the product of $\oprd{k} \oprd{l} \oprd{n}$ by $\opr{m} \opr{j} \opr{i}$, and each term posses a 6-fold permutation symmetry with $\pm 1$ signature. 
Starting from $\oprd{k} \oprd{l} \oprd{n}$ there are two symmetric pertumations 
\begin{equation}
 \begin{aligned}
   & \oprd{k} \oprd{l} \oprd{n} = \oprd{l} \oprd{n} \oprd{k} = \oprd{n} \oprd{k} \oprd{l}, \\
 \end{aligned}
\end{equation}
and three anti-symmetric permutations 
\begin{equation}
 \begin{aligned}
  \oprd{l} \oprd{k} \oprd{n}  =   \oprd{n} \oprd{l} \oprd{k} =  \oprd{k} \oprd{n} \oprd{l},
 \end{aligned}
\end{equation}
which fulfill 
\begin{equation}
 \begin{aligned}
 \oprd{k} \oprd{l} \oprd{n} = - \oprd{l} \oprd{k} \oprd{n}. 
 \end{aligned}
\end{equation}
Therefore, one can express a $6\times 6$ matrix that is the product all possible permutations for $(k,l,n)$ and $(i,j,m)$, rearrange everything in terms of the original $\oprd{k} \oprd{l} \oprd{n}  \opr{m} \opr{j} \opr{i}$ operator and obtain the following terms 
\begin{equation}
 \begin{aligned}
 & \frac{1}{6} \mathcal{P}_{ijm}^{kln}\overlap{ijm}{kln} \oprd{k} \oprd{l} \oprd{n}  \opr{m} \opr{j} \opr{i}= &\oprd{k} \oprd{l} \oprd{n}  \opr{m} \opr{j} \opr{i} \bigg( \\
 &+ \big( \overlap{ijm}{kln} + \overlap{ijm}{lnk}  + \overlap{ijm}{nkl} \big) \\
 &- \big( \overlap{ijm}{lkn} + \overlap{ijm}{nlk}  + \overlap{ijm}{knl} \big) \bigg),
 \end{aligned}
\end{equation}
where $\mathcal{P}_{ijm}^{kln}$ contains the sum over the 36 permutations of the 6 indices with the corresponding signs.

\subsection{Diagonal term}
For a diagonal term, one has that 
\begin{equation}
 \begin{aligned}
  i = k \\
  j = l \\
  m = n \\
 \end{aligned}
\end{equation}
and therefore one obtains 
\begin{equation}
 \begin{aligned}
 \bra{I}O^3\ket{I} = \sum_{i>j>m\in \ket{I}}&+ \big(  \overlap{ijm}{ijm} + \overlap{ijm}{jmi}  + \overlap{ijm}{mij} \big) \\
                                 &- \big(  \overlap{ijm}{jim} + \overlap{ijm}{mji}  + \overlap{ijm}{imj} \big)
 \end{aligned}
\end{equation}
where the summation $\sum_{i>j>m\in \ket{I}}$ means running over all orbitals occupied in $\ket{I}$ in a unique way. 
\subsection{Single excitation term}
For a single excitation term, one has that 
\begin{equation}
 \begin{aligned}
  i \ne k \\
  j = l \\
  m = n \\
 \end{aligned}
\end{equation}
and then 
\begin{equation}
 \begin{aligned}
 \bra{I}O^3 \oprd{k} \opr{i} \ket{I} = (-1)^{\mathcal{P}_{IJ}}
 \sum_{j>m\in \ket{I}} 
 &+ \big( \overlap{ijm}{kjm} + \overlap{ijm}{jmk}  + \overlap{ijm}{mkj} \big) \\
 &- \big( \overlap{ijm}{jkm} + \overlap{ijm}{mjk}  + \overlap{ijm}{kmj} \big) \bigg).
 \end{aligned}
\end{equation}

\subsection{Double excitation term}
For a double excitation term, one has that 
\begin{equation}
 \begin{aligned}
  i \ne k \\
  j \ne l \\
  m = n \\
 \end{aligned}
\end{equation}
and then 
\begin{equation}
 \begin{aligned}
 \bra{I}O^3 \oprd{k}\oprd{l} \opr{j} \opr{i} \ket{I} = (-1)^{\mathcal{P}_{IJ}}
 \sum_{m\in \ket{I}} 
 &+ \big( \overlap{ijm}{klm} + \overlap{ijm}{lmk}  + \overlap{ijm}{mkl} \big) \\
 &- \big( \overlap{ijm}{lkm} + \overlap{ijm}{mlk}  + \overlap{ijm}{kml} \big) \bigg).
 \end{aligned}
\end{equation}

\end{document}
